### 2017-12-08 LRDraft.tex
Update on Overleaf.

\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Critical assessment of Linear-Response Excitations in Molecular system\\
or \\
On the Localization of the Linear-Response excitations in Open Systems}
\author{You}

\begin{document}
\maketitle

\begin{abstract}
By performing linear-response (LR)-TDDFT calculation of molecular systems within a highly complete real-space basis set, we analyse how the behaviour of the dynamical polarizability is influenced by
the discretization conditions of the computational treatment.
We show that optical excitations of energy below the LR ionization potential behave as observable, localized quantities, that can be studied with high precision, provided an adequate level of completeness.
We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated in any discretization scheme.
Under this light, we also show that 
excitation energies above ionization threshold do not exhibit such observable features and \emph{cannot} be considered as poles of the dynamical polarizability.
This result is a inherent behaviour of the system's Liouvillian, and does not depend on computational treatment of the unoccupied subspace.
\end{abstract}

\section{Reboot with recent considerations}
\begin{itemize}
\item Write the excitations as the eigenstates of the Liouvillian:
\begin{itemize}
\item The Casida Matrix provides the eigenvectors in the basis of the unperturbed transitions
\item From the Casida eigenproblem we 
get the poles of the dynamical polarizability and we may reconstruct the perturbed wavefunctions
\item Lot of solution in state of 
the art to express \emph{the same information}, still by avoiding the explicit diagonalization of the problem
\end{itemize}
\item Such transitions might also be written in terms of the solutions of the eigenproblem for the perturbed hamiltonian
\begin{itemize}
\item There are therefore excitations which correspond to localized solutions of the above eigenproblems
\item There is a \emph{energy threshold} above which the eigenfunction associated \emph{cannot be anymore} localized
\end{itemize}
\item Below threshold, the eigenfunction are localized and the energy values are \emph{observable} quantities (there is a convergence in terms of the simulation parameters)
\begin{itemize}
\item Casida treatments for different
basis sets exhibit convergence of the low-energy excitations
\item Still, even for such localized excitations, non-trivial dependence on the empty states on some of excitation value is observed (energies converge relatively slowly wrt $N_\alpha$)
\item The locality of the excitation can be \emph{measured}
{\bf NEW idea for the SoB: why not to consider}
$$
\int \mathrm d \mathbf r
\rho(\mathbf r) |\phi_p^E(\mathbf r)|^2
$$
or similar quantities, that are independent on the number of empty and  bound states
\item Localized Excitation are the  only one with an observable character (this is surely already known)
\item The spectrum of the Loiuvillian in this regime is a \emph{discrete} spectrum; the excitation energies are \emph{poles} of the dynamical polarizability
nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very intersting remark in my opinion: the physics of the optical excitation is observable (and therefore localized) only if the energies are not higher than the energy needed to ionize the system. After this point, it seems normal to me that the ``optical'' excitations with real value of the energy are not  meant to be observable anymore.
\item Optical Excitations below threshold have therefore a (very) long lifetime (poles on the real axis), and they contribute to the analytic structure of the dynamical polarizability.
\end{itemize}
\item Above this threshold the energies have a strong dependence on the computational treatment
\begin{itemize}
\item The high-energy part of the 
spectrum does not converge with the 
boundary conditions, even though they converge wrt the empty states (established techniques \emph{do not solve} such problem)
\item This is \emph{not} a problem that is related to the continuum collapse of the empty states.
\item They belong to the continuum of  the Liouvillian $\rightarrow$ they collapse, or depend strongly on the basis set adopted
\item They cannot be considered separately \emph{even when they are expressed in localized basis} as 
their shape is dependent on the treatment
\item They energies are not \emph{true} poles of the dynamical polarizability (the spectra converge only by superposition of deltas)
\end{itemize}
\item Optical excitation above Ionization threshold are therefore observable \emph{only} if they possess a lifetime (the peaks of the spectrum have a well-defined broadening). In this way they might be expressed in terms of resonant wavefunctions
\end{itemize}

\section{Draft of the paper - old notes}

\begin{itemize}
\item Aim of the paper: Compute the electronic properties of a molecular system with the formalism of linear scaling using a LR-TDDFT inside BigDFT code. 
%We also want to define a set of computational tools that allow to check the reliability of the computation.  
\end{itemize}

\begin{itemize}
\item Motivation: the DFT code have reached reliable features of precision for the computation of the GS. The same probletic are instead needed in order to achieve the same type of results for spectroscopic properties in large systems
\begin{itemize}
\item Quantify the impact of several modelling of a given systems (environment, disorder)
\item Systematic approach has proven its effectiveness for GS calculations (easy to handle)~\cite{deltatest2016}. The quality of localized basis function is therefore easy to quantify (variational theorem)
\item A challenge is represented by large scale computation for \emph{molecular} systems
\end{itemize}
\item State-of-the-art 
\begin{itemize}
\item localized basis set for representing the Hamiltonians (e.g. Fiesta (Blase, Olevano), FHI-Aims, GWMol)
\item This approach has been also generalized to LR calculation in the case of ONETEP \cite{Ratcliff2013}. However little is said about the reliability of the results in terms of the convergence of the spectra
\end{itemize}
\item Content of the paper: 
\begin{itemize}
\item Brief illustration of the support function approach in wavelets (Large systems are  accessible for the structure (Energy, Forces,\ldots)
\item We want to exploit the wavelet properties in the context of LR, \emph{by also providing some criteria} which may be of interest for the evaluation of the quality of the LR results.
\end{itemize}
\item Conclusions and implications
\begin{itemize}
\item We might apply this formalism also in the contect of MBPT and inspect the validity of the linear response functional for e.g. GW calcualtions (the perturbation operator will be different from the dipole)
\end{itemize}
\end{itemize}

\section{Introduction}

\subsection{How to add Comments}

Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2016-07-03T09:54:16.211Z:
%
% Here's an example comment!
%
To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.

Comments can also be added to the margins of the compiled PDF using the todo command\todo{Here's a comment in the margin!}, as shown in the example on the right. You can also add inline comments:

\todo[inline, color=green!40]{This is an inline comment.}

\subsection{How to add Tables}

Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example.

\begin{table}
\centering
\begin{tabular}{l|r}
Item & Quantity \\\hline
Widgets & 42 \\
Gadgets & 13
\end{tabular}
\caption{\label{tab:widgets}An example table.}
\end{table}

\subsection{How to add Citations and a References List}

You can upload a \verb|.bib| file containing your BibTeX entries, created with JabRef; or import your \href{https://www.overleaf.com/blog/184}{Mendeley}, CiteULike or Zotero library as a \verb|.bib| file. You can then cite entries from it, like this: \cite{greenwade93}. Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.

You can find a \href{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}{video tutorial here} to learn more about BibTeX.

We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above --- or use the contact form at \url{https://www.overleaf.com/contact}!

\bibliographystyle{alpha}
\bibliography{sample}

\end{document}

### 2017-12-15 LRDraft.tex
update

@@
 \usepackage{graphicx}
+\usepackage{amsmath,amsfonts,amssymb,amsthm}
+\usepackage{mathtools,braket}
+\usepackage{xifthen}
 \usepackage[colorinlistoftodos]{todonotes}
 \usepackage[colorlinks=true, allcolors=blue]{hyperref}
+
+% notation for standard math
+\renewcommand{\d}{\partial}
+\newcommand{\half}{\frac{1}{2}}
+\newcommand{\dd}{{\rm d}}
+\renewcommand{\r}{{\bf r}}
+\newcommand{\x}{{\bf x}}
+\newcommand{\ii}{\mathrm{i}}
+\newcommand{\intdef}[3]{\int_{#1}^{#2} \dd {#3}}
+\newcommand{\intover}[1]{\int_{-\infty}^{+\infty} \dd {#1}}
+\newcommand{\sint}{\mathrlap{\displaystyle\int}
+\mathrlap{\textstyle\sum}
+\phantom{\mathrlap{\displaystyle
+\int}\textstyle\sum}}
+
+% notatiotion for equation environments
+\newcommand{\be}{\begin{equation}}
+\newcommand{\ee}{\end{equation}}
+\newcommand{\ba}{\begin{eqnarray}}
+\newcommand{\ea}{\end{eqnarray}}
+\newcommand{\baa}{\begin{align}}
+\newcommand{\eaa}{\end{align}}
+\newcommand{\nn}{\notag}
+\newcommand{\qq}{\qquad}
+\newcommand{\lb}{\label}
+\newcommand{\mat}[1]{\begin{pmatrix} #1\end{pmatrix}}
+
+% notation for the operators
+\newcommand{\op}[1]{\hat {#1}}
+\newcommand{\sop}[1]{\op{\op {#1}}}
+\newcommand{\commutator}[2]{\left[ {#1} , {#2} \right]}
+\newcommand{\trace}[1]{\mathrm{tr}\left(#1\right)}
+\newcommand{\argument}[1]{\ifthenelse{\isempty{#1}{}}{}{(#1)}}
+\newcommand{\matop}[1]{\mathbf{#1}}
+\newcommand{\optr}[1]{\check #1}
+
+% notation for the states
+\newcommand{\tket}[1]{| \tilde #1 \rangle}
+\newcommand{\tbra}[1]{\langle \tilde #1 |}
+\newcommand{\brket}[2]{\langle  #1 | #2 \rangle} %standard braket
+\newcommand{\tbraket}[2]{\langle \tilde #1 | #2 \rangle}
+\newcommand{\ketbra}[2]{| #1 \rangle \langle #2 |}
+\newcommand{\tketbra}[2]{| #1 \rangle \langle \tilde #2 |}
+\newcommand{\sket}[2]{| #2)^{#1}}
+\newcommand{\sbra}[2]{( #2|_{#1}}
+\newcommand{\sketor}[2]{| #2]^{#1}}
+\newcommand{\sbraor}[2]{[ #2|_{#1}}
+\newcommand{\sbraket}[2]{\braket{\op{#1} | \op{#2}}}
+\newcommand{\dket}[1]{\Bigl| #1 \Bigr)}
+\newcommand{\dbra}[1]{\Bigl(#1 \Bigr|}
+\newcommand{\dbraket}[2]{\Bigl(#1 \Bigl| #2 \Bigr)}
+\newcommand{\dketor}[1]{\Bigl| #1 \Bigr]}
+\newcommand{\dbraor}[1]{\Bigl[#1 \Bigr|}
+\newcommand{\hket}[1]{| #1 ]}
+\newcommand{\hbra}[1]{[ #1 |}
+\newcommand{\hbraket}[2]{[#1 | #2 ]}
+
+% special operators
+\newcommand{\dmnot}{\op{\rho}_0}
+\newcommand{\dm}{\op{\rho}}
+\newcommand{\hnot}{\op{H}_0}
+\newcommand{\hone}[1]{\op{H}_1\argument{#1}}
+\newcommand{\transition}[1]{\op T_{#1}}
+\newcommand{\excite}[2]{\op e_{{#1}{#2}}}
+\newcommand{\decay}[2]{\op d_{{#1}{#2}}}
+\newcommand{\honetmp}[1][]{\op{H_1}\argument{#1}} 
+\newcommand{\identity}{\op{\mathbb I}}
+\newcommand{\rmat}[1]{\optr R}
 
@@
 \item The spectrum of the Loiuvillian in this regime is a \emph{discrete} spectrum; the excitation energies are \emph{poles} of the dynamical polarizability
-nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very intersting remark in my opinion: the physics of the optical excitation is observable (and therefore localized) only if the energies are not higher than the energy needed to ionize the system.
+nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very intersting remark in my opinion: the physics of the optical excitation is observable 
+(and therefore localized) only if the energies are not higher than the energy needed to ionize the system.
 After this point, it seems normal to me that the ``optical'' excitations with real value of the energy are not  meant to be observable anymore.
@@
 \end{itemize}
+
+\section{THEORY}
+
+\subsection{Basic definitions}
+
+We consider a generic one-body quantum mechanical problem described by the hermitian Hamiltonian $\hnot$  written in terms of the standard 
+kinetic operator $\op T$ plus a one-body potential $\op V$, which we assume to be completely general, i.e. possibly nonlocal.
+We consider open systems, so that $\hnot$ is defined on $\mathbb L_2(\mathbb R_3)$ and the basis of its eigenfunctions spans this 
+functional space. Therefore, together with the discrete part of its spectrum $\epsilon_p$, the Hamiltonian may have an essential spectrum 
+$\epsilon(\alpha)$, parametrized by the continuum label $\alpha$.
+
+A generic state $\ket{f} \in \mathbb L_2(\mathbb R_3)$ can be expanded in the basis of the eigenstates of $\hnot$, that is:
+\be\lb{ketBasisExpDef1}
+\ket{f} = \sum_p f_p \ket{\psi_p} + \int \dd \alpha f(\alpha) \ket{\psi(\alpha)}  = 
+\sint \dd s f(s) \ket{\psi(s)} \;,
+\ee
+where we have introduced the compact multi-index $s$ that collect both the discrete and continuum part of the spectrum of $\hnot$.
+The normalization of the basis can be chosen so that the standard orthonormality condition holds, that is: 
+\be
+\brket{\psi(s)}{\psi(s')} = \delta(s-s') \;,
+\ee
+and the completeness condition is written as:
+\be\lb{completenessH0basis1}
+\identity = \sint \dd s \ketbra{\psi(s)}{\psi(s)} = \sum_{p} \ketbra{\psi_p}{\psi_p} + \int \dd\alpha \ketbra{\psi(\alpha)}{\psi(\alpha)} \;. 
+\ee
+Thanks to this condition the coefficients of the expansion \eqref{ketBasisExpDef1} can be expressed via a scalar products, namely $f_{p} = 
+\brket{\psi_p}{f}$ and $f(\alpha) = \brket{\psi(\alpha)}{f}$.
+
+\subsection{Time evolution of states in the linear response regime}
+
+We discuss the time evolution of a generic state vector in the case in which a hermitian time dependent perturbation $\hone{t}$ is added to $\hnot$. 
+To achieve this task we have to solve the time dependent Schroedinger equation supplied by the knowledge of the state at the ``initial'' time $t_0$.
+We seek for a solution of the form:
+\be\lb{ketTimeEvol1}
+\ket{\psi(t_{0},t)} = e^{-\ii \hnot t} \op{U}_{I}(t,t_0) e^{\ii \hnot t_0}\ket{\psi_0} \; . 
+\ee
+where $\op{U}_I(t,t_0)$ is the time evolution operator induced by $\hone{}$ that satisfies the ``initial'' time condition $\op{U}_I(t_0,t_0)=1$. 
+Plugging the expression \eqref{ketTimeEvol1} in the Schroedinger equation we obtain a differential equation for $\op{U}_I$ that can be solved 
+iteratively as a power series in $\hone{}$. Limiting to the linear order provides:
+\be \lb{UiLinOrderSol1}
+\op{U}_I(t,t_0) = \identity - \ii \intdef{t_0}{t}{t'} e^{\ii \hnot t'} \hone{t'} e^{-\ii \hnot t'} \; .
+\ee
+So, at the first order in $\hone{}$ equation \eqref{ketTimeEvol1} can thus be written as:
+\be \lb{ketTimeEvol2} 
+\ket{\psi(t_{0},t)} = \left( \op{U}_0(t-t_0) - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \hone{t'} 
+\op{U}_0(t'-t_0) \right)\ket{\psi_0} \; ,
+\ee
+were we have defined the time evolution operator of the unperturbed Hamiltonian by
+\be
+\op{U}_0(t-t_0)\equiv e^{-\ii \hnot(t -t_0)} \;.
+\ee
+The time evolution of left vectors can be derived in the same way. We can express the temporal evolution of the left 
+vectors in the form:
+\be \lb{braTimeEvol1}
+\bra{\psi(t_{0},t)} = \bra{\psi_0} e^{-\ii \hnot t_0} \op{U}_{I}(t_0,t) e^{\ii \hnot t} \;,
+\ee
+plugging this equation in the conjugate Schroedinger equation and pursuing the same procedure defined above, we obtain the 
+linear order expression of time evolution of left vectors:
+\be\lb{leftVectTimeEvol2}
+\bra{\psi(t_{0},t)} = \bra{\psi_0} \left( \op{U}_0(t_0-t) + \ii \intdef{t_0}{t}{t'} \op{U}_0(t_0-t') 
+\hone{t'} \op{U}_0(t'-t) \right) 
+\ee
+It is immediate to check that, in order to preserve the norm vectors during the time evolution, it is sufficient that $\op{U}_I$ 
+possesses the  semi-group structure $\op{U}_I(t_2,t_1) \op{U}_I(t_1,t_0) = \op{U}_I(t_2,t_0)$. An inspection of \eqref{UiLinOrderSol1}
+evidences that this condition is satisfied in the linear response regime.
+
+\subsubsection{Evolution of the eigenstates of $\hnot$. Adiabatic limit vs finite time switch-on procedure}
+
+% \be \label{SchroedingerKet1}
+% \ii \partial_t \ket{\psi(t)}  = \left( \hnot + \hone{t}\right) \ket{\psi(t)}  \;,
+% \ee
+
+\subsection{Linear response on the density operator. Liouville equation in the time domain}
+
+\subsection{Self-consistent Hamiltonians. Generalized Liouville operator}
+
+\subsection{Formulation in the frequency domain}
+
+\subsection{Analysis of the excitations}
 
@@
 
-\section{Introduction}
-
-\subsection{How to add Comments}
-
-Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2016-07-03T09:54:16.211Z:
+% \section{Introduction}
 % 
-% Here's an example comment!
+% \subsection{How to add Comments}
 % 
-To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.
-
-Comments can also be added to the margins of the compiled PDF using the todo command\todo{Here's a comment in the margin!}, as shown in the example on the right. You can also add inline comments:
-
-\todo[inline, color=green!40]{This is an inline comment.}
-
-\subsection{How to add Tables}
-
-Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example.
-
-\begin{table}
-\centering
-\begin{tabular}{l|r}
-Item & Quantity \\\hline
-Widgets & 42 \\
-Gadgets & 13
-\end{tabular}
-\caption{\label{tab:widgets}An example table.}
-\end{table}
-
-\subsection{How to add Citations and a References List}
-
-You can upload a \verb|.bib| file containing your BibTeX entries, created with JabRef; or import your \href{https://www.overleaf.com/blog/184}{Mendeley}, CiteULike or Zotero library as a \verb|.bib| file.
+% Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2016-07-03T09:54:16.211Z:
+% %
+% % Here's an example comment!
+% %
+% To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.
+% 
+% Comments can also be added to the margins of the compiled PDF using the todo command\todo{Here's a comment in the margin!}, as shown in the example on the right. You can also add inline comments:
+% 
+% \todo[inline, color=green!40]{This is an inline comment.}
+% 
+% \subsection{How to add Tables}
+% 
+% Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. 
+% 
+% \begin{table}
+% \centering
+% \begin{tabular}{l|r}
+% Item & Quantity \\\hline
+% Widgets & 42 \\
+% Gadgets & 13
+% \end{tabular}
+% \caption{\label{tab:widgets}An example table.}
+% \end{table}
+% 
+% \subsection{How to add Citations and a References List}
+% 
+% You can upload a \verb|.bib| file containing your BibTeX entries, created with JabRef; or import your \href{https://www.overleaf.com/blog/184}{Mendeley}, CiteULike or Zotero library as a \verb|.bib| file.
 You can then cite entries from it, like this: \cite{greenwade93}.
 Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.
-
-You can find a \href{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}{video tutorial here} to learn more about BibTeX.
-
-We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above --- or use the contact form at \url{https://www.overleaf.com/contact}!
+% 
+% You can find a \href{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}{video tutorial here} to learn more about BibTeX.
+% 
+% We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above --- or use the contact form at \url{https://www.overleaf.com/contact}!
 

### 2017-12-17 LRDraft.tex
update

@@
 
+We are interested in determining the time evolution of an eigenstate of $\hnot$ under the action of the perturbation $\hone{t}$ in the linear 
+response regime. A proper statement of the problem requires the specification of the way in which the perturbation is switched on.
+Possible choice of the switching on protocol are, for instance, the \emph{adiabatic limit} and the \emph{sudden limit} case. In the first
+case the perturbation is switched on at $t_0=-\infty$, but the intrinsic time structure of $\hone{}$ is modified by the damping function 
+$e^{-\eta_a |t|}$. In the second protocol the perturbation is abruptly switched on at the finite time $t_0$, so that the time structure of
+$\hone{}$ is multiplied times the $\theta$-function $\theta(t-t_0)$.
+
+It is possible to write:
+\be \lb{ketTimeEvol3} 
+\ket{\psi_p(t)} = e^{-\ii E_p t}\left( \identity - \ii \op A(t_0,t)  \right)\ket{\psi_p} \; ,
+\ee
+where: 
+\be
+\op A(t_0,t) = \intdef{t_0}{t}{t'} \op{U}_0(t-t') \hone{t'} \op{U}_0(t'-t)
+\ee
+we can write:
+\be
+\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{-}_0(t-t') \Phi^{a.l,s.l}(t') \op{U}^{+}_0(t'-t)
+\ee
+where:
+\be
+\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
+\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
+\ee
+
 % \be \label{SchroedingerKet1}

### 2017-12-18 LRDraft.tex
update

--- 2017-12-15 LRDraft.tex
@@
 \newcommand{\x}{{\bf x}}
+\newcommand{\eps}{\epsilon}
 \newcommand{\ii}{\mathrm{i}}
@@
 \begin{abstract}
-By performing linear-response (LR)-TDDFT calculation of molecular systems within a highly complete real-space basis set, we analyse how the behaviour of the dynamical polarizability is influenced by
-the discretization conditions of the computational treatment.
-We show that optical excitations of energy below the LR ionization potential behave as observable, localized quantities, that can be studied with high precision, provided an adequate level of completeness.
-We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated in any discretization scheme.
-Under this light, we also show that 
-excitation energies above ionization threshold do not exhibit such observable features and \emph{cannot} be considered as poles of the dynamical polarizability.
-This result is a inherent behaviour of the system's Liouvillian, and does not depend on computational treatment of the unoccupied subspace.
+By performing linear-response (LR)-TDDFT calculation of molecular systems within a highly complete real-space basis set, we analyze how the behavior of the dynamical 
+polarizability is influenced by the discretization conditions of the computational treatment.
+We show that optical excitations of energy below the LR ionization potential behave as observable, localized quantities, that can be studied with high precision, 
+provided an adequate level of completeness. We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
+in any discretization scheme. Under this light, we also show that excitation energies above ionization threshold do not exhibit such observable features and \emph{cannot} be 
+considered as poles of the dynamical polarizability. This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
+unoccupied subspace.
 \end{abstract}
@@
 \item Localized Excitation are the  only one with an observable character (this is surely already known)
-\item The spectrum of the Loiuvillian in this regime is a \emph{discrete} spectrum; the excitation energies are \emph{poles} of the dynamical polarizability
-nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very intersting remark in my opinion: the physics of the optical excitation is observable 
-(and therefore localized) only if the energies are not higher than the energy needed to ionize the system.
-After this point, it seems normal to me that the ``optical'' excitations with real value of the energy are not  meant to be observable anymore.
+\item The spectrum of the Liouvillian in this regime is a \emph{discrete} spectrum; the excitation energies are \emph{poles} of the dynamical polarizability
+nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very interesting remark in my opinion: the physics of the optical excitation is observable 
+(and therefore localized) only if the energies are not higher than the energy needed to ionize the system. After this point, it seems normal to me that the ``optical'' excitations with 
+real value of the energy are not  meant to be observable anymore.
 \item Optical Excitations below threshold have therefore a (very) long lifetime (poles on the real axis), and they contribute to the analytic structure of the dynamical polarizability.
@@
 We consider open systems, so that $\hnot$ is defined on $\mathbb L_2(\mathbb R_3)$ and the basis of its eigenfunctions spans this 
-functional space. Therefore, together with the discrete part of its spectrum $\epsilon_p$, the Hamiltonian may have an essential spectrum 
-$\epsilon(\alpha)$, parametrized by the continuum label $\alpha$.
+functional space. Therefore, together with the discrete part of its spectrum $\eps_p$, the Hamiltonian may have an essential spectrum 
+$\eps(\alpha)$, parametrized by the continuum label $\alpha$.
 
@@
 
-\subsubsection{Evolution of the eigenstates of $\hnot$. Adiabatic limit vs finite time switch-on procedure}
+\subsubsection{Time evolution of stationary states. Adiabatic limit vs finite time switch-on procedure}
 
-% \be \label{SchroedingerKet1}
-% \ii \partial_t \ket{\psi(t)}  = \left( \hnot + \hone{t}\right) \ket{\psi(t)}  \;,
-% \ee
+We are interested in determining the time evolution of an eigenstate of $\hnot$ under the action of the perturbation $\hone{t}$ in the linear 
+response regime. A proper statement of the problem requires the specification of the way in which the perturbation is switched on.
+Possible choice of the switching on protocol are, for instance, the \emph{adiabatic limit} and the \emph{sudden limit} protocols. In the first
+case the perturbation is switched on at $t_0=-\infty$, but the intrinsic time structure of $\hone{}$ is modified by the damping function 
+$e^{-\eta_a |t|}$. In the second one the perturbation is abruptly switched on at the finite time $t_0$, so that the time structure of
+$\hone{}$ is multiplied times the $\theta$-function $\theta(t-t_0)$.
+
+Starting from the generic time evolution equation \eqref{ketTimeEvol2} and choosing the initial condition in the form 
+$\ket{\psi_0} = e^{-\\i \eps_p t_0}\ket{\psi_p}$, we can write the time evolution of a (discrete) eigenvector of $\hnot$ as:
+\be \lb{ketTimeEvol3} 
+\ket{\psi_p(t)} = e^{-\ii \eps_p t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_p} \; ,
+\ee
+where we have introduced the \emph{perturbing field operators}: 
+\be
+\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
+\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
+\ee
+that codify the effective of the perturbing Hamiltonian in the specific switch-on procedure. Making usage of elementary properties of $\theta$ functions allows us
+to rewrite the former time integral as:
+\be\lb{AopDef1}
+\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{+}_0(t-t') \Phi^{a.l,s.l}(t') \op{U}^{-}_0(t'-t) \;,
+\ee
+so that the effect of the switch-on protocol are completely reabsorbed in the perturbing field. In the subsequent analysis we will omit the apex in the fields $\Phi$, 
+unless explicitly needed, to keep notations as simple as possible. Thanks to this definition we can express the time evolution of the eigenvectors of $\hnot$ in the 
+compact form:
+\be\lb{ketBraTimeEvol1}
+\ket{\psi_p(t)} = e^{-\ii \eps_p t}\left( \identity - \ii \op A(t)  \right)\ket{\psi_p} \; , \qq 
+\bra{\psi_p(t)} = \bra{\psi_p} \left( \identity + \ii \op A(t)  \right) e^{\ii \eps_p t} \; .
+\ee
 
@@
 
+We introduce the \emph{density operator} defined as the sum of the densities of all the occupied states having energy $\epsilon_p$ lower than the \emph{chemical potential} 
+(Fermi energy):
+\be\label{rhodef1}
+\dmnot = \sum_p^{n_{occ}} \ket{\psi_p} \bra{\psi_p}  \;. 
+\ee
+Clearly $\dmnot$ commutes with $\hnot$ and in the unperturbed case is a time-independent operator. When the perturbation is switched the system starts to evolve
+and we indicate with $\dm(t)$ the modified density of the perturbed system. We introduce the shorthand notation:
+\be\lb{rhodef2}
+\dm(t)  =  \dmnot + \dm'(t)\;,
+\ee
+where $\dm'(t)$ is called the \emph{response density operator} and represents the time dependent modification of the ground state density induced by the perturbation.
+Here we are assuming that the highest occupied energy level and the lowest unoccupied one will never intersect during the time evolution. Thanks to this condition, the 
+linear response regime the expression of $\dm'(t)$ can be readily derived using equations \eqref{ketBraTimeEvol1} and reads:  
+\be\lb{rhoTimeEvolutionDef3}
+\dm'(t) = \ii \commutator{\dmnot}{\op A(t)} \;.
+\ee
+The equation of motion (Liouville equation) for $\dm'$ is obtained by performing the time derivative of the previous equation. The derivative of $\op A(t)$ can be 
+computed starting from its definition and reads:
+\be
+\d_t\op A(t) = \op\Phi(t) -\\i \commutator{\hnot}{\op A(t)} \nn \;,
+\ee
+and using the Jacobi identity we have:
+\be\lb{LiouvilleRhoDef1}
+\ii \d_t \dm'(t) = \commutator{\op\Phi(t)}{\dmnot} + \ii\commutator{\hnot}{\commutator{\dmnot}{\op A(t)}} = 
+\commutator{\op\Phi(t)}{\dmnot} + \commutator{\hnot}{\dm'(t)} \;.
+\ee
+It is useful to introduce the \emph{Liouvillian} superoperator:
+\be
+\sop{\mathcal L_0} \equiv \commutator{\hnot}{\cdot} \;,
+\ee
+so that the Liouville equation can be written as:
+\be\lb{LiouvilleRhoDef2}
+\ii \d_t \dm'(t) = \sop{\mathcal L_0} \dm'(t) + \commutator{\op\Phi(t)}{\dmnot} \;.
+\ee
+
 \subsection{Self-consistent Hamiltonians. Generalized Liouville operator}
+
+Let us extend the the former analysis to self-consistent systems, \emph{i.e.} to the case in which the unperturbed Hamiltonian is itself a function of the density.
+In this case the perturbing field $\Phi$ has also the effect of adding a further perturbation operator to the perturbing Hamiltonian. In the linear response framework, 
+this latter quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel (evaluated at $\dm=\dmnot$) times the value of the
+induced density modification, that is:
+\be\label{V'tspacedef1}
+\op V'(t)= 
+\int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
+\trace{\dm'(t) \ket{\r} \bra{\r'}} \;.
+\ee
+The Liouville equation for self-consistent systems can be written by adding the contribution of $\op V'$ to $\op\Phi$ in \eqref{LiouvilleRhoDef2}. 
+It reads:
+\be\lb{LiouvilleRhoSelfDef1}
+\ii \d_t \dm'(t) = \sop{\mathcal L_0} \dm'(t) + \commutator{\op V'(t)}{\dmnot} + \commutator{\op \Phi(t)}{\dmnot} \;.
+\ee
+We point out that the response density operator obeys a self-consistent equation, since the  induced perturbing field $\op V'$ is itself a function of $\dm'$. 
+It is possible to formally recast \eqref{LiouvilleRhoSelfDef1} in the same form of \eqref{LiouvilleRhoDef2} by introducing the \emph{coupling}
+superoperator:
+\be
+\sop{\mathcal K} = 
+\int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
+\trace{\cdot \ket{\r} \bra{\r'}} \;,
+\ee
+in this way the first commutator in \eqref{LiouvilleRhoSelfDef1} can be written as the formal action of the coupling superoperator to $\dm'$ and \eqref{LiouvilleRhoSelfDef1}
+can be written as:
+\be\lb{LiouvilleRhoSelfDef2}
+\ii \d_t \dm'(t) = \sop{\mathcal L} \dm'(t) + \commutator{\op \Phi(t)}{\dmnot} \;, \qq
+\sop{\mathcal L} = \sop{\mathcal L_0} + \sop{\mathcal K} \;.
+\ee
 

### 2017-12-19 LRDraft.tex
update

@@
 \be \lb{ketTimeEvol3} 
-\ket{\psi_p(t)} = e^{-\ii \eps_p t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_p} \; ,
+\ket{\psi_p(t)} = e^{-\ii \eps_p t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_p} \; ,
 \ee
@@
 \be
-\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
-\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
+\op\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
+\op\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
 \ee
@@
 \be\lb{AopDef1}
-\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{+}_0(t-t') \Phi^{a.l,s.l}(t') \op{U}^{-}_0(t'-t) \;,
+\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{+}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}^{-}_0(t'-t) \;,
 \ee
@@
 It is useful to introduce the \emph{Liouvillian} superoperator:
-\be
+\be\lb{L0sopDef1}
 \sop{\mathcal L_0} \equiv \commutator{\hnot}{\cdot} \;,
@@
 \subsection{Formulation in the frequency domain}
+
+We reformulate the Liouville equation \eqref{LiouvilleRhoSelfDef2} in the frequency domain. In order to achieve this task it is
+preferable to directly compute the action of the Liouville operator on the Fourier transform of the response density, since in this
+way some subtleties that concerns the analytic structure in the $\omega$ complex plane can be properly taken into account.
+We first define the response density in the frequency domain that, staring from \eqref{rhoTimeEvolutionDef3}, is given by:
+\be\label{rhoPrimeOmegaDef1}
+\dm'(\omega) \equiv \intover{t} e^{\ii \omega t} \dm'(t)
+= \ii \commutator{\dmnot}{\op A(\omega)} \;,
+\ee
+where $\op A(\omega)$ is The Fourier transform of \eqref{AopDef1} and reads:
+\be \label{AomegaDef1}
+\op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
+\op G_0^+(\omega') \op \Phi(\omega) \op G_0^-(\omega'-\omega)\;.
+\ee
+The action of $\sop{\mathcal L_0}$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
+\be\label{LiouvillianF'def1}
+\sop{\mathcal L_0} \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
+\ii \commutator{\dmnot}{\commutator{\hnot}{\op A(\omega)}}
+\;,
+\ee
+\be\label{eoma}
+\commutator{\hnot }{\op A(\omega)} = \bar{\bar\omega} \op A(\omega) - \ii \op \Phi(\omega)\;.
+\ee
+where $\bar{\bar\omega} = \omega + 2\ii\eta$
 

### 2017-12-19 LRDraft.tex
update

@@
 \newcommand{\eps}{\epsilon}
+\newcommand{\bbomega}{{\bar{\bar\omega}}}
 \newcommand{\ii}{\mathrm{i}}
@@
 
-\subsection{Basic definitions}
+\subsection{Basic definitions}\lb{BasicDef}
 
@@
 We consider open systems, so that $\hnot$ is defined on $\mathbb L_2(\mathbb R_3)$ and the basis of its eigenfunctions spans this 
-functional space. Therefore, together with the discrete part of its spectrum $\eps_p$, the Hamiltonian may have an essential spectrum 
-$\eps(\alpha)$, parametrized by the continuum label $\alpha$.
+functional space. Therefore, together with the discrete (bound) part of its spectrum $\eps_b$, the Hamiltonian may have an essential spectrum 
+$\eps(c)$, parametrized by the continuum label $c$.
 
@@
 \be\lb{ketBasisExpDef1}
-\ket{f} = \sum_p f_p \ket{\psi_p} + \int \dd \alpha f(\alpha) \ket{\psi(\alpha)}  = 
+\ket{f} = \sum_b f_b \ket{\psi_b} + \int \dd c f(c) \ket{\psi(c)}  = 
 \sint \dd s f(s) \ket{\psi(s)} \;,
@@
 \be\lb{completenessH0basis1}
-\identity = \sint \dd s \ketbra{\psi(s)}{\psi(s)} = \sum_{p} \ketbra{\psi_p}{\psi_p} + \int \dd\alpha \ketbra{\psi(\alpha)}{\psi(\alpha)} \;. 
+\identity = \sint \dd s \ketbra{\psi(s)}{\psi(s)} = \sum_{b} \ketbra{\psi_b}{\psi_b} + \int \dd c \ketbra{\psi(c)}{\psi(c)} \;. 
 \ee
-Thanks to this condition the coefficients of the expansion \eqref{ketBasisExpDef1} can be expressed via a scalar products, namely $f_{p} = 
-\brket{\psi_p}{f}$ and $f(\alpha) = \brket{\psi(\alpha)}{f}$.
+Thanks to this condition the coefficients of the expansion \eqref{ketBasisExpDef1} can be expressed via a scalar products, namely $f_{b} = 
+\brket{\psi_b}{f}$ and $f(c) = \brket{\psi(c)}{f}$.
 
@@
 Starting from the generic time evolution equation \eqref{ketTimeEvol2} and choosing the initial condition in the form 
-$\ket{\psi_0} = e^{-\\i \eps_p t_0}\ket{\psi_p}$, we can write the time evolution of a (discrete) eigenvector of $\hnot$ as:
+$\ket{\psi_0} = e^{-\\i \eps_b t_0}\ket{\psi_b}$, we can write the time evolution of the generic $\ket{\psi_b}$ eigenvector of $\hnot$ as:
 \be \lb{ketTimeEvol3} 
-\ket{\psi_p(t)} = e^{-\ii \eps_p t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_p} \; ,
+\ket{\psi_b(t)} = e^{-\ii \eps_b t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_b} \; ,
 \ee
@@
 \ee
-so that the effect of the switch-on protocol are completely reabsorbed in the perturbing field. In the subsequent analysis we will omit the apex in the fields $\Phi$, 
+so that the effect of the switch-on protocol are completely reabsorbed in the perturbing field. In the subsequent analysis we will omit the apex in the fields $\op\Phi$, 
 unless explicitly needed, to keep notations as simple as possible. Thanks to this definition we can express the time evolution of the eigenvectors of $\hnot$ in the 
@@
 \be\lb{ketBraTimeEvol1}
-\ket{\psi_p(t)} = e^{-\ii \eps_p t}\left( \identity - \ii \op A(t)  \right)\ket{\psi_p} \; , \qq 
-\bra{\psi_p(t)} = \bra{\psi_p} \left( \identity + \ii \op A(t)  \right) e^{\ii \eps_p t} \; .
+\ket{\psi_b(t)} = e^{-\ii \eps_b t}\left( \identity - \ii \op A(t)  \right)\ket{\psi_b} \; , \qq 
+\bra{\psi_b(t)} = \bra{\psi_b} \left( \identity + \ii \op A(t)  \right) e^{\ii \eps_b t} \; .
 \ee
@@
 
-We introduce the \emph{density operator} defined as the sum of the densities of all the occupied states having energy $\epsilon_p$ lower than the \emph{chemical potential} 
+We introduce the \emph{density operator} defined as the sum of the one-particle densities of all the states with energy lower than the \emph{chemical potential} 
 (Fermi energy):
 \be\label{rhodef1}
-\dmnot = \sum_p^{n_{occ}} \ket{\psi_p} \bra{\psi_p}  \;. 
+\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
 \ee
+where the index $p$ labels the occupied state, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi energy.
 Clearly $\dmnot$ commutes with $\hnot$ and in the unperturbed case is a time-independent operator. When the perturbation is switched the system starts to evolve
@@
 Let us extend the the former analysis to self-consistent systems, \emph{i.e.} to the case in which the unperturbed Hamiltonian is itself a function of the density.
-In this case the perturbing field $\Phi$ has also the effect of adding a further perturbation operator to the perturbing Hamiltonian. In the linear response framework, 
+In this case the perturbing field $\op\Phi$ has also the effect of adding a further perturbation operator to the perturbing Hamiltonian. In the linear response framework, 
 this latter quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel (evaluated at $\dm=\dmnot$) times the value of the
@@
 We first define the response density in the frequency domain that, staring from \eqref{rhoTimeEvolutionDef3}, is given by:
-\be\label{rhoPrimeOmegaDef1}
+\be\lb{rhoPrimeOmegaDef1}
 \dm'(\omega) \equiv \intover{t} e^{\ii \omega t} \dm'(t)
@@
 where $\op A(\omega)$ is The Fourier transform of \eqref{AopDef1} and reads:
-\be \label{AomegaDef1}
+\be \lb{AomegaDef1}
 \op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
@@
 The action of $\sop{\mathcal L_0}$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
-\be\label{LiouvillianF'def1}
+\be\lb{LiouvillianRho'omegaDef1}
 \sop{\mathcal L_0} \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
-\ii \commutator{\dmnot}{\commutator{\hnot}{\op A(\omega)}}
-\;,
+\ii \commutator{\dmnot}{\commutator{\hnot}{\op A(\omega)}} \;,
 \ee
-\be\label{eoma}
-\commutator{\hnot }{\op A(\omega)} = \bar{\bar\omega} \op A(\omega) - \ii \op \Phi(\omega)\;.
+and the commutator between the unperturbed Hamiltonian and $\op A(\omega)$ can be directly computed starting from \eqref{AomegaDef1}: 
+\be
+\commutator{\hnot }{\op A(\omega)} = \bbomega \op A(\omega) - \ii \op \Phi(\omega)\;, \nn
 \ee
-where $\bar{\bar\omega} = \omega + 2\ii\eta$
+where $\bbomega \equiv \omega + 2\ii\eta$, so that:
+\be\lb{LiouvillianRho'omegaDef2}
+\sop{\mathcal L_0} \dm'(\omega) =  \bbomega\dm'(\omega) + \commutator{\dmnot}{\op\Phi(\omega)}\;.
+\ee
+The coupling superoperator has the same formal action on the response density both in the time and in the frequency domain, so the complete
+Liouville equation in $\omega$ space can be written as:
+\be\lb{LiouvillianRho'omegaDef3}
+\left(\bbomega - \sop{\mathcal L}\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;.
+\ee
 
 \subsection{Analysis of the excitations}
+
+\subsubsection{Definition of the basis of transitions}
+
+We now introduce the notion of \emph{basis of transitions} and identify the operators than can be expanded in such a basis.
+
+We split the complete
+set of eigenstates of $\hnot$ in two sets. The first one is composed by the eigenvectors of $\hnot$ in the subspace of the occupied orbitals. The second 
+one is composed by the remaining eigenvectors, both in the bound and in the continuum region, and its elements are denoted as $\ket{\psi(\alpha)}$, where $\alpha$ 
+is a multi-index in the sense described in \ref{BasicDef}. The elements of these sets satisfy the following orthonormality relation: 
+\be\lb{orthonormalityDef1}
+\brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq \brket{\psi_p}{\psi_q} = \delta_{pq} \;, \qq
+\brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;.
+\ee
+Obviously, the direct sum of these two sets coincides with the complete set of eigenstates of $\hnot$ and thus 
+constitute a complete basis. 
+A generic operator can be decomposed in this basis and its formal expansion contains four distinct contribution of the form $\ketbra{\psi_p}{\psi_q}$, 
+$\ketbra{\psi(\alpha)}{\psi(\beta)}$, $\ketbra{\psi(\alpha)}{\psi_p}$, $\ketbra{\psi_p}{\psi(\alpha)}$. However an inspection of equations \eqref{rhoPrimeOmegaDef1}
+and \eqref{LiouvillianRho'omegaDef3} evidences that the relevant operators in the contest of the linear response are expressed as a commutator with $\dmnot$. 
+For this class of operators the only non vanishing contribution comes from the \emph{transition operators}:
+\be
+\excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
+\decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;.
+\ee
+The orthonormality conditions \eqref{orthonormalityDef1} imply that:
+\be\lb{transitionOpOrthonormalityDef1}
+\trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
+\trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;,
+\ee
+so that the expansion of a suitable operator $\op O$ in the basis of transitions reads:
+\be\lb{OperatorTransBasisExpDef1}
+\op O = \sum_p\sint \dd \alpha\left(
+\excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
+\right)
+\ee
+In order to recast this expansion in a simpler expression it turns out to be useful to define the rank-2 vectors of the transition basis: 
+\be
+\sbra{p\alpha}{\cdot} \equiv 
+\mat{ \excite{p}{\alpha} \;, & \decay{\alpha}{p} }\;,
+\ee
+as well as a different representation for the trace between the operators and the above mentioned transitions:
+\be
+\sket{p\alpha}{\op O}  \equiv \mat{ \trace{ \op O \decay{\alpha}{p}} \\ 
+\trace{\op O \excite{p}{\alpha}}} \; .
+\ee
+Thanks to this formalism we have that equation \eqref{OperatorTransBasisExpDef1} can be expressed as:
+\be\lb{OperatorTransBasisExpDef2}
+\op O = \sum_p\sint \dd \alpha \sbra{p\alpha}{\cdot}\sket{p\alpha}{\op O} = 
+\dbraket{\cdot}{\op O} \;,
+\ee
+where the last equality implicitly define the index-less ``big-shaped'' vectors and the sum over unwritten indexes is understood.
+
+\subsubsection{OPE of the Liouville operator}
 

### 2017-12-20 LRDraft.tex
update

@@
 \newcommand{\decay}[2]{\op d_{{#1}{#2}}}
+\newcommand{\Liouv}{\sop{\mathcal L}}
+\newcommand{\Liouvnot}{\sop{\mathcal L_0}}
+\newcommand{\coupl}{\sop{\mathcal K}}
 \newcommand{\honetmp}[1][]{\op{H_1}\argument{#1}} 
@@
 \be\lb{L0sopDef1}
-\sop{\mathcal L_0} \equiv \commutator{\hnot}{\cdot} \;,
+\Liouvnot \equiv \commutator{\hnot}{\cdot} \;,
 \ee
@@
 \be\lb{LiouvilleRhoDef2}
-\ii \d_t \dm'(t) = \sop{\mathcal L_0} \dm'(t) + \commutator{\op\Phi(t)}{\dmnot} \;.
+\ii \d_t \dm'(t) = \Liouvnot \dm'(t) + \commutator{\op\Phi(t)}{\dmnot} \;.
 \ee
@@
 \be\lb{LiouvilleRhoSelfDef1}
-\ii \d_t \dm'(t) = \sop{\mathcal L_0} \dm'(t) + \commutator{\op V'(t)}{\dmnot} + \commutator{\op \Phi(t)}{\dmnot} \;.
+\ii \d_t \dm'(t) = \Liouvnot \dm'(t) + \commutator{\op V'(t)}{\dmnot} + \commutator{\op \Phi(t)}{\dmnot} \;.
 \ee
@@
 \be
-\sop{\mathcal K} = 
+\coupl = 
 \int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
@@
 \be\lb{LiouvilleRhoSelfDef2}
-\ii \d_t \dm'(t) = \sop{\mathcal L} \dm'(t) + \commutator{\op \Phi(t)}{\dmnot} \;, \qq
-\sop{\mathcal L} = \sop{\mathcal L_0} + \sop{\mathcal K} \;.
+\ii \d_t \dm'(t) = \Liouv \dm'(t) + \commutator{\op \Phi(t)}{\dmnot} \;, \qq
+\Liouv = \Liouvnot + \coupl \;.
 \ee
@@
 \ee
-The action of $\sop{\mathcal L_0}$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
+The action of $\Liouvnot$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
 \be\lb{LiouvillianRho'omegaDef1}
-\sop{\mathcal L_0} \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
+\Liouvnot \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
 \ii \commutator{\dmnot}{\commutator{\hnot}{\op A(\omega)}} \;,
@@
 \be\lb{LiouvillianRho'omegaDef2}
-\sop{\mathcal L_0} \dm'(\omega) =  \bbomega\dm'(\omega) + \commutator{\dmnot}{\op\Phi(\omega)}\;.
+\Liouvnot \dm'(\omega) =  \bbomega\dm'(\omega) + \commutator{\dmnot}{\op\Phi(\omega)}\;.
 \ee
@@
 \be\lb{LiouvillianRho'omegaDef3}
-\left(\bbomega - \sop{\mathcal L}\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;.
+\left(\bbomega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;.
 \ee
@@
 as well as a different representation for the trace between the operators and the above mentioned transitions:
-\be
-\sket{p\alpha}{\op O}  \equiv \mat{ \trace{ \op O \decay{\alpha}{p}} \\ 
-\trace{\op O \excite{p}{\alpha}}} \; .
+\be\lb{OperatorTransitionCoeffDef1}
+\sket{p\alpha}{\op O}  \equiv \mat{ \trace{\decay{\alpha}{p}\op O } \\ 
+\trace{\excite{p}{\alpha}\op O}} \; .
 \ee
@@
 \subsubsection{OPE of the Liouville operator}
+
+The Liouville equation \eqref{LiouvillianRho'omegaDef3} can be written in the basis of transititions and becomes a linear matrix equation for the rank-2 vectors
+of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
+\be
+\omega\mat{ \trace{\decay{\alpha}{p}\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\dm'(\omega)}} - 
+\mat{ \trace{\decay{\alpha}{p}\Liouv\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\Liouv\dm'(\omega)}} =
+\mat{ \trace{\decay{\alpha}{p}\commutator{\op\Phi(\omega)}{\dmnot}} \\ \trace{\excite{p}{\alpha}\commutator{\op\Phi(\omega)}{\dmnot}}}
+\;.\nn
+\ee
+The second addend in the l.h.s can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. Performing this procedure
+we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
+\be\lb{LiouvilleTransBasisDef1}
+\sum_q\sint\dd\beta \left[\omega\delta_q^p\delta(\alpha-\beta)- \optr{L}^{p \alpha}_{q\beta} \right]\sket{q\beta}{\dm'(\omega)} =
+\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} \;.
+\ee
+with:
+\be
+\optr{L}^{p \alpha}_{q\beta} \equiv \mat{\trace{\decay{\alpha}{p}\, \Liouv\, \excite{q}{\beta}} &
+\trace{\decay{\alpha}{p}\, \Liouv\, \decay{\beta}{q}} \\
+\trace{\excite{p}{\alpha}\, \Liouv\, \excite{q}{\beta}} &
+\trace{\excite{p}{\alpha}\, \Liouv\, \decay{\beta}{q}}} \;.
+\ee
 

### 2017-12-20 LRDraft.tex
update

@@
 
-The Liouville equation \eqref{LiouvillianRho'omegaDef3} can be written in the basis of transititions and becomes a linear matrix equation for the rank-2 vectors
-of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
+The Liouville equation \eqref{LiouvillianRho'omegaDef3} can be consistently written in the transition basis. Indeed, its r.h.s is explicitly written
+as a commutator with $\dmnot$, while an inspection of the formal definition of the response density and of the Liouville superoperator evidences that
+they both contain a commutator with $\dmnot$. Written in the basis of transitions Liouville equation becomes a linear matrix equation for the rank-2 
+vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
 \be
@@
 with:
-\be
+\be\lb{LiouvilleMatrixTransBasisDef1}
 \optr{L}^{p \alpha}_{q\beta} \equiv \mat{\trace{\decay{\alpha}{p}\, \Liouv\, \excite{q}{\beta}} &
@@
 \ee
+This formulation of the Liouville equation is the starting point for the derivation of the spectral decomposition of the response density operator
+in terms of the eigenvectors if the Liouville operator. 
+The first step in the achievement of this result is provided by the construction of the eigenvectors of the matrix \eqref{LiouvilleMatrixTransBasisDef1}.
+Following the notation previously defined we introduce the rank-2 vectors $\sket{p\alpha}{E}$ and $\sbra{p\alpha}{\tilde E}$ that represent, by definition,
+the right and left eigenvectors $\optr{L}$, respectively, so that:
+\be\lb{LiouvMatrixEigenvectorDef1}
+\sum_q \sint \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q \beta}{E} = E \sket{p\alpha}{E} \;, \quad
+\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \optr{L}^{p \alpha}_{q\beta} = E \sbra{q\beta}{\tilde E}\;.
+\ee
+In general, left and right eigenvectors do not coincide, but it is always possible to choose they normalization so that a orthonormality conditions among the
+elements of left and right spaces holds, namely:
+\be
+\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E}\sket{p\alpha}{E'} \equiv \dbraket{\tilde E}{E'} = \delta(E-E') \;.
+\ee
+Once that the eigenvectors are known, the spectral decomposition of the resolvent of $\optr{L}$ can be provided:  
+\be
+\left[\left(\bbomega-\optr{L}\right)^{-1}\right]^{p\alpha}_{q\beta} =\sint\dd E
+\frac{\sket{p\alpha}{E}\sbra{q\beta}{\tilde E}}{\bbomega-E} \;,
+\ee
+so equation \eqref{LiouvilleTransBasisDef1} can be inverted:
+\be
+\sket{p\alpha}{\dm'(\omega)} = 
+\sint\dd E \sket{p\alpha}{E}
+\frac{\sum_q \sint \dd \beta\sbra{q\beta}{\tilde E}
+\sket{q\beta}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
+\ee
+that can be compactly rewritten by using the index-less notation:
+\be
+\sket{p\alpha}{\dm'(\omega)} = 
+\sint\dd E \sket{p\alpha}{E}
+\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
+\ee
+
+% \be
+% \sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}}
+% \;,
+% \quad
+% \sbra{p\alpha}{\tilde E} \equiv \mat{\tilde X_{E\,p\alpha} & \tilde Y_{E\,p\alpha}}
+% \ee
 

### 2017-12-21 LRDraft.tex
update

@@
 
-\subsubsection{OPE of the Liouville operator}
+\subsubsection{Spectral decompositionof the response density in the transitions basis}
 
@@
 \be
-\sket{p\alpha}{\dm'(\omega)} = 
-\sint\dd E \sket{p\alpha}{E}
+\sket{p\alpha}{\dm'(\omega)} = \sint\dd E \sket{p\alpha}{E}
 \frac{\sum_q \sint \dd \beta\sbra{q\beta}{\tilde E}
@@
 \sint\dd E \sket{p\alpha}{E}
-\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
+\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
 \ee
 
-% \be
-% \sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}}
-% \;,
-% \quad
-% \sbra{p\alpha}{\tilde E} \equiv \mat{\tilde X_{E\,p\alpha} & \tilde Y_{E\,p\alpha}}
-% \ee
+\subsubsection{Excitation operators}
+
+We introduce the explicit representation of the eigenvectors op $\optr{L}$:
+\be
+\sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}} \;, \qq
+\sbra{p\alpha}{\tilde E} \equiv \mat{\tilde X_{E\,p\alpha} & \tilde Y_{E\,p\alpha}} \;,
+\ee
+and on the basis of these elements we define the \emph{excitation operators}:
+\be\lb{ExctitationOperatorsDef1}
+\op E = 
+\sum_p \sint \dd \alpha \left(\excite{p}{\alpha} X_E^{p\alpha} + \decay{\alpha}{p} Y_E^{p\alpha}\right) 
+\;, \qq
+\op{\tilde E} = \sum_p \sint \dd \alpha \left(\decay{\alpha}{p} \tilde X_{E\,p\alpha} + 
+\excite{p}{\alpha}\tilde Y_{E\,p\alpha}  \right)\;.
+\ee
+Excitation operators are the right and left eigenvectors of the Liouville superoperator, as directly follows from their
+definition. Indeed for $\op E$ we have:
+\begin{align}
+\sop{\mathcal L} \op E & = \sum_p \sint \dd \alpha \left(\trace{\decay{\alpha}{p} \sop{\mathcal L} \op E} \excite{p}{\alpha} + 
+\decay{\alpha}{p} \trace{ \excite{p}{\alpha} \sop{\mathcal L} \op E}  \right) = \nn \\
+&= \sum_p \sint  \dd \alpha \sbra{p\alpha}{\cdot} \sum_q \sint  \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q\beta}{E} 
+= E \sum_p \sint \dd \alpha \sbra{p\alpha}{\cdot} \sket{p\alpha}{E} = E \, \op E \;,	
+\end{align}
+whereas the left action on $\op{\tilde E}$ provides:
+\begin{align}
+ \op{\tilde E} \sop{\mathcal L} &= E \op{\tilde E}
+\end{align}
 

### 2017-12-23 LRDraft.tex
update

@@
 induced density modification, that is:
-\be\label{V'tspacedef1}
+\be\label{Vptspacedef1}
 \op V'(t)= 
@@
 The action of $\Liouvnot$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
-\be\lb{LiouvillianRho'omegaDef1}
+\be\lb{LiouvillianRhopomegaDef1}
 \Liouvnot \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
@@
 where $\bbomega \equiv \omega + 2\ii\eta$, so that:
-\be\lb{LiouvillianRho'omegaDef2}
+\be\lb{LiouvillianRhopomegaDef2}
 \Liouvnot \dm'(\omega) =  \bbomega\dm'(\omega) + \commutator{\dmnot}{\op\Phi(\omega)}\;.
@@
 Liouville equation in $\omega$ space can be written as:
-\be\lb{LiouvillianRho'omegaDef3}
+\be\lb{LiouvillianRhopomegaDef3}
 \left(\bbomega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;.
@@
 $\ketbra{\psi(\alpha)}{\psi(\beta)}$, $\ketbra{\psi(\alpha)}{\psi_p}$, $\ketbra{\psi_p}{\psi(\alpha)}$. However an inspection of equations \eqref{rhoPrimeOmegaDef1}
-and \eqref{LiouvillianRho'omegaDef3} evidences that the relevant operators in the contest of the linear response are expressed as a commutator with $\dmnot$. 
+and \eqref{LiouvillianRhopomegaDef3} evidences that the relevant operators in the contest of the linear response are expressed as a commutator with $\dmnot$. 
 For this class of operators the only non vanishing contribution comes from the \emph{transition operators}:
@@
 \excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
-\right)
+\right) \;.
 \ee
-In order to recast this expansion in a simpler expression it turns out to be useful to define the rank-2 vectors of the transition basis: 
+In order to recast this expansion in a simpler expression it turns out to be useful to define the rank-2 row vectors of the transition basis: 
 \be
@@
 \ee
-as well as a different representation for the trace between the operators and the above mentioned transitions:
+and we also introduce a vectorial notation to deal with the coefficients of the expansion of an operator in the transition basis, that is: 
 \be\lb{OperatorTransitionCoeffDef1}
@@
 \ee
-where the last equality implicitly define the index-less ``big-shaped'' vectors and the sum over unwritten indexes is understood.
+where the last equality implicitly define the ulterior compact notation of the ``big-shaped'' vectors in which the summed indexes are omitted.  
+In the same fashion it will be also useful for the subsequent analysis to introduce a ``conjugate'' notation, in which the basis operators are expressed
+as column vector and the coefficients of the expanded operator as row ones, that is: 
+\be\lb{TransitionBasisConjugateDef1}
+\sket{p\alpha}{\cdot} \equiv 
+\mat{\decay{\alpha}{p} \\  \excite{p}{\alpha}} \;, \qq
+\sbra{p\alpha}{\op O}  \equiv 
+\mat{ \trace{\excite{\alpha}{p}\op O } \;, & \trace{\decay{p}{\alpha}\op O} }
+\;,
+\ee
+where the flip in the role of $\op e$ and $\op d$ in \eqref{TransitionBasisConjugateDef1} follows from the properties of excitation and decay operators
+under hermitian-conjugate operation. The expansion of a suitable operator in the transition basis using the conjugate description reads: 
+\be\lb{OperatorTransBasisConjugateExpDef1}
+\op O = \sum_p\sint \dd \alpha \sbra{p\alpha}{\op O}\sket{p\alpha}{\cdot} = 
+\dbraket{\op O}{\cdot} \;.
+\ee
 
-\subsubsection{Spectral decompositionof the response density in the transitions basis}
+\subsubsection{Spectral decomposition of the response density in the transitions basis}
 
-The Liouville equation \eqref{LiouvillianRho'omegaDef3} can be consistently written in the transition basis. Indeed, its r.h.s is explicitly written
+The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis. Indeed, its r.h.s is explicitly written
 as a commutator with $\dmnot$, while an inspection of the formal definition of the response density and of the Liouville superoperator evidences that
@@
 so equation \eqref{LiouvilleTransBasisDef1} can be inverted:
-\be
+\be\lb{RhopExcitationTransBasisDef1}
 \sket{p\alpha}{\dm'(\omega)} = \sint\dd E \sket{p\alpha}{E}
@@
 that can be compactly rewritten by using the index-less notation:
-\be
+\be\lb{RhopExcitationTransBasisDef2}
 \sket{p\alpha}{\dm'(\omega)} = 
@@
 and on the basis of these elements we define the \emph{excitation operators}:
-\be\lb{ExctitationOperatorsDef1}
-\op E = 
+\begin{align}\lb{ExctitationOperatorsDef1}
+\op E &\equiv \dbraket{\cdot}{E} = 
 \sum_p \sint \dd \alpha \left(\excite{p}{\alpha} X_E^{p\alpha} + \decay{\alpha}{p} Y_E^{p\alpha}\right) 
-\;, \qq
-\op{\tilde E} = \sum_p \sint \dd \alpha \left(\decay{\alpha}{p} \tilde X_{E\,p\alpha} + 
+\;,\nn \\
+\op{\tilde E} &\equiv \dbraket{\tilde E}{\cdot} = \sum_p \sint \dd \alpha \left(\decay{\alpha}{p} \tilde X_{E\,p\alpha} + 
 \excite{p}{\alpha}\tilde Y_{E\,p\alpha}  \right)\;.
-\ee
+\end{align}
 Excitation operators are the right and left eigenvectors of the Liouville superoperator, as directly follows from their
@@
 \begin{align}
-\sop{\mathcal L} \op E & = \sum_p \sint \dd \alpha \left(\trace{\decay{\alpha}{p} \sop{\mathcal L} \op E} \excite{p}{\alpha} + 
-\decay{\alpha}{p} \trace{ \excite{p}{\alpha} \sop{\mathcal L} \op E}  \right) = \nn \\
+\Liouv \op E & = \sum_p \sint \dd \alpha \left(\trace{\decay{\alpha}{p} \Liouv \op E} \excite{p}{\alpha} + 
+\decay{\alpha}{p} \trace{ \excite{p}{\alpha} \Liouv \op E}  \right) = \nn \\
 &= \sum_p \sint  \dd \alpha \sbra{p\alpha}{\cdot} \sum_q \sint  \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q\beta}{E} 
@@
 \begin{align}
- \op{\tilde E} \sop{\mathcal L} &= E \op{\tilde E}
+ \op{\tilde E} \Liouv &=  \sum_p \sint \dd \alpha \left(
+\trace{\op{\tilde E}\Liouv\excite{p}{\alpha}}\decay{\alpha}{p} +  
+\trace{\op{\tilde E}\sop{\mathcal L}\decay{\alpha}{p}} \excite{p}{\alpha} \right) = 
+\nn \\ &= \sum_p \sint  \dd \alpha  \sum_q \sint  \dd \beta
+\sbra{q\beta}{\tilde E}\optr{L}^{q\beta}_{p\alpha}\sket{p\alpha}{\cdot} = 
+E\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \sket{p\alpha}{\cdot}  =
+E \op{\tilde E} \;.
 \end{align}
+The introduction of the excitation operators allows to provided a complete operator version of equation \eqref{RhopExcitationTransBasisDef2}
+\be\lb{RhopExcitationDef1}
+\dm'(\omega) = 
+\sint\dd E \op E
+\frac{\trace{\op{\tilde E}\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
+\ee
+where the algebraic equivalence between the trace written in \eqref{RhopExcitationDef1} and the numerator of \eqref{RhopExcitationTransBasisDef2}
+can be easily proved.
 

### 2017-12-26 LRDraft.tex
update

@@
 We introduce the explicit representation of the eigenvectors op $\optr{L}$:
-\be
+\be\lb{XYcoeffDef1}
 \sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}} \;, \qq
@@
 definition. Indeed for $\op E$ we have:
-\begin{align}
+\begin{align}\lb{opEeigenvalueDef1}
 \Liouv \op E & = \sum_p \sint \dd \alpha \left(\trace{\decay{\alpha}{p} \Liouv \op E} \excite{p}{\alpha} + 
@@
 whereas the left action on $\op{\tilde E}$ provides:
-\begin{align}
+\begin{align}\lb{optildeEeigenvalueDef1}
  \op{\tilde E} \Liouv &=  \sum_p \sint \dd \alpha \left(
@@
 can be easily proved.
+
+\subsubsection{Schroedinger-like equation for excitonic states}
+
+We introduce the excitonic states defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
+coefficients that appears in \eqref{XYcoeffDef1}, that is:
+\begin{align}
+\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
+\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
+\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
+\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
+\end{align}
+Thanks to these definitions we can express the excitation operators as follows:
+\be
+\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
+\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
+\ee
+The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated in Schroedinger-like equations
+for the excitonic states.
 

### 2017-12-27 LRDraft.tex
updatte

@@
 Thanks to these definitions we can express the excitation operators as follows:
-\be
+\be\lb{ExctitationOperatorsDef2}
 \op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
@@
 for the excitonic states.
+
+\vspace{0.5cm}
+\emph{Solution for $\coupl = 0$}
+\vspace{0.5cm}
+
+\noindent In this case the $\optr{L}_{q\beta}^{p\alpha}$ matrix has only diagonal non-vanishing elements, given by: 
+\be
+\trace{\decay{\alpha}{p}\Liouv\excite{q}{\beta}} = H_{0\alpha\beta}\delta_{pq} - \eps_p\delta_{pq}\delta(\alpha-\beta) \;, \qq
+\trace{\excite{\alpha}{p}\Liouv\decay{q}{\beta}} = \eps_p\delta_{pq}\delta(\alpha-\beta) - H_{0\beta\alpha}\delta_{pq} \;, 
+\ee
+where $H_{0\alpha\beta} = \bra{\psi(\alpha)}\hnot\ket{\psi(\beta)}$. The eigenvalue conditions \eqref{LiouvMatrixEigenvectorDef1} imply
+that the $Y$ and $\tilde Y$ coefficients introduced in \eqref{XYcoeffDef1} vanish so that both $\tket{\chi^E_p}$ and $\bra{\chi^E_p}$ do not
+contribute to the excitation operators \eqref{ExctitationOperatorsDef2}. The eigenvalue operator equation for $\op E$ reduces to:
+\be
+\sum_q\left(\hnot - \eps_q\right)\ket{\phi^E_q}\bra{\psi_q} = E \sum_q \ket{\phi^E_q}\bra{\psi_q} \;,
+\ee
+and projecting on $\ket{\psi_q}$ provides the eigenvalue condition for the excitonic $\ket{\phi^E_p}$ state:
+\be
+\left(\hnot - \eps_p\right)\ket{\phi^E_p} = E \ket{\phi^E_p} \;.
+\ee
+In the same way we can derive an analogous equation for $\tbra{\phi^E_p}$ by using the eigenvalue condition for $\op{\tilde E}$. To achieve this
+result we need the expression of the left action of the (unperturbed) Liouville superoperator defined in \eqref{L0sopDef1}, that can be derived by
+observing that:
+\be
+\trace{\op O' (\Liouvnot \op O)} = \trace{(\op O' \Liouvnot) \op O } =
+\trace{\commutator{\op O'}{\op H_0} \op O} \quad \Rightarrow \quad \op O \Liouvnot = 
+- \Liouvnot \op O \;.
+\ee
+So, the eigenvalue operator equation for $\op{\tilde E}$ provides:
+\be
+\sum_q  \ket{\psi_q} \tbra{\phi^E_q} \left( \hnot - \eps_q \right) =
+E \sum_q  \ket{\psi_q} \tbra{\phi^E_q} \;,
+\ee
+so that:
+\be
+\tbra{\phi^E_p} \left( \hnot - \eps_p \right) = E \tbra{\phi^E_p} \;.
+\ee
+In other terms we find that the perturbation states must be left and right eigenvectors of  $\hnot$.
+
+The operators $\op E$ and $\op{\tilde E}$ have an important physical meaning:
+if they are used as perturbation operators they would generate a response density 
+with a well-defined energy:
+\be
+\commutator{\op E}{\dmnot} = E \;, \qquad \commutator{\op{\tilde E}}{\dmnot} = -\op{\tilde E}
+\ee
+The above equations show that we would have, respectively:
+\be
+\dm'(\omega) = \frac{1}{\bbomega - E} \op E\;,\qquad
+\dm'(\omega) = \frac{1}{\bbomega + E} \op{\tilde E}
+\ee
+In other terms, they constitute the \emph{resonant channels} of the excitation of the
+density. The decomposition of the perturbation operator $\op \Phi$ among these channels
+would provide $\dm'(\omega)$.
 

### 2017-12-29 LRDraft.tex
update

@@
 \end{align}
-The introduction of the excitation operators allows to provided a complete operator version of equation \eqref{RhopExcitationTransBasisDef2}
+The introduction of the excitation operators allows to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef2}, that is:
 \be\lb{RhopExcitationDef1}
@@
 
-We introduce the excitonic states defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
+We introduce the \emph{excitonic states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
 coefficients that appears in \eqref{XYcoeffDef1}, that is:
@@
 \ee
-and projecting on $\ket{\psi_q}$ provides the eigenvalue condition for the excitonic $\ket{\phi^E_p}$ state:
+and projecting on $\ket{\psi_q}$ provides the eigenvalue condition for the excitonic state $\ket{\phi^E_p}$:
 \be
@@
 \ee
-In the same way we can derive an analogous equation for $\tbra{\phi^E_p}$ by using the eigenvalue condition for $\op{\tilde E}$. To achieve this
+In the same way, by using the eigenvalue condition for $\op{\tilde E}$, we can derive an analogous equation for $\tbra{\phi^E_p}$. To achieve this
 result we need the expression of the left action of the (unperturbed) Liouville superoperator defined in \eqref{L0sopDef1}, that can be derived by
@@
 \ee
-In other terms we find that the perturbation states must be left and right eigenvectors of  $\hnot$.
+So we find that the excitonic states are the left and right eigenvectors of $\hnot$ (that actually coincide since we are considering
+hermitian Hamiltonians). The energy eigenvalue is shifted by $\eps_p$, that is the energy of the occupied states involved in the 
+excitation.
 
-The operators $\op E$ and $\op{\tilde E}$ have an important physical meaning:
-if they are used as perturbation operators they would generate a response density 
-with a well-defined energy:
+A last interesting comment regards the expression of the response density when the excitation operator $\op E$ itself is used as the source of the
+perturbation. In this case, denoting as $\op E'$ the given perturbing excitation, it is easy to see that:
 \be
-\commutator{\op E}{\dmnot} = E \;, \qquad \commutator{\op{\tilde E}}{\dmnot} = -\op{\tilde E}
+\trace{\op{\tilde E}\commutator{\op E'}{\dmnot}} = \trace{\op{\tilde E}\op E'} = \delta(E-E') \;, \nn 
 \ee
-The above equations show that we would have, respectively:
+and the response density generated by this perturbation is given by: 
 \be
-\dm'(\omega) = \frac{1}{\bbomega - E} \op E\;,\qquad
-\dm'(\omega) = \frac{1}{\bbomega + E} \op{\tilde E}
+\dm'(\omega) = \frac{1}{\bbomega - E'} \op E'\;,
 \ee
-In other terms, they constitute the \emph{resonant channels} of the excitation of the
-density. The decomposition of the perturbation operator $\op \Phi$ among these channels
-would provide $\dm'(\omega)$.
+which represents a monochromatic term of energy $E'$. Under this perspective we can state that excitations constitute
+the \emph{resonant channels} for the construction  of the response density.
 

### 2018-01-05 LRDraft.tex
update

@@
 \ee
-The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated in Schroedinger-like equations
+The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated into a Schroedinger-like equations
 for the excitonic states.

### 2018-01-08 LRDraft.tex
update

@@
 \renewcommand{\r}{{\bf r}}
+\newcommand{\br}{\bar{\bf r}}
 \newcommand{\x}{{\bf x}}
@@
 superoperator:
-\be
+\be\lb{couplingSopDef1}
 \coupl = 
@@
 \vspace{0.5cm}
-\emph{Solution for $\coupl = 0$}
+\emph{Equations for $\coupl = 0$}
 \vspace{0.5cm}
@@
 observing that:
-\be
+\be\lb{leftActionLouv0Def1}
 \trace{\op O' (\Liouvnot \op O)} = \trace{(\op O' \Liouvnot) \op O } =
@@
 the \emph{resonant channels} for the construction  of the response density.
+
+\vspace{0.5cm}
+\emph{Generic equations for $\coupl \neq 0$}
+\vspace{0.5cm}
+
+To explicitly write the generic eigenvalue equations for the excitonic states it is useful to introduce some further formalism to express the 
+self-consistent part of the perturbing Hamiltonian \eqref{Vptspacedef1}. We start by expanding $\op V'$ in the coordinate representation, that is:
+\be
+\op V'(t)= 
+\int \dd \br \dd \br' \dd \r \dd \r' \bra{\br'}\frac{\delta\hnot}{\delta \rho_0(\r,\r')}\ket{\br}
+\trace{\dm'(t) \ket{\r} \bra{\r'}} \ketbra{\br}{\br'}\;, \nn
+\ee
+then we introduce the \emph{coupling kernel}, defined as:
+\be\lb{couplingKernelDef1}
+U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
+} \trace{\op O' \ket{\r} \bra{\r'}} \;,
+\ee
+using this quantity we can express $\op V'$ as:
+\be\lb{Vptspacedef2}
+\op V'(t)= 
+\int \dd \br \dd \br' U\left[\ketbra{\br}{\br'};\dm'(t)\right] \ketbra{\br}{\br'}\;,
+\ee
+and consequently the formal action of the coupling superoperator \eqref{couplingSopDef1} can be expressed as: 
+\be\lb{couplingSopDef2}
+\coupl = 
+\int \dd \br \dd \br' \commutator{\ketbra{\br}{\br'}}{\dmnot} U\left[\ketbra{\br}{\br'};\cdot\right] \;.
+\ee
+Using this formalism we can define the left action of the coupling superoperator, in analogous way of what done in \eqref{leftActionLouv0Def1}, 
+that is:
+\be\lb{leftActionCouplingDef1}
+\trace{\op O' (\coupl \op O)} = \int \dd\br\dd\br'\trace{\ketbra{\br}{\br'}\commutator{\dmnot}{\op O'}}
+U\left[\ketbra{\br}{\br'};\op O\right] \doteq \trace{(\op O' \coupl) \op O } \;,
+\ee
+and so we have:
+\be\lb{leftActionCouplingDef2}
+(\op O' \coupl) = \int \dd\br\dd\br'\trace{\ketbra{\br}{\br'}\commutator{\dmnot}{\op O'}}
+U\left[\ketbra{\br}{\br'};\op O\right] \;.
+\ee
 

### 2018-01-09 LRDraft.tex
update

@@
 \be
-\d_t\op A(t) = \op\Phi(t) -\\i \commutator{\hnot}{\op A(t)} \nn \;,
+\d_t\op A(t) = \op\Phi(t) -\ii \commutator{\hnot}{\op A(t)} \nn \;,
 \ee
@@
 elements of left and right spaces holds, namely:
-\be
+\be\lb{ExcitationOrthonormalityDef1}
 \sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E}\sket{p\alpha}{E'} \equiv \dbraket{\tilde E}{E'} = \delta(E-E') \;.
@@
 \end{align}
+The orthonormality condition \eqref{ExcitationOrthonormalityDef1} implies that:
+\be
+\trace{\op{\tilde E} \op E'} = \sum_p\sint \dd\alpha \left(\tilde X_E^{p\alpha} X_{E'\,p\alpha} +
+\tilde Y_E^{p\alpha} Y_{E'\,p\alpha}\right) = \delta(E-E') \;. 
+\ee
 Excitation operators are the right and left eigenvectors of the Liouville superoperator, as directly follows from their
@@
 \int \dd \br \dd \br' \dd \r \dd \r' \bra{\br'}\frac{\delta\hnot}{\delta \rho_0(\r,\r')}\ket{\br}
-\trace{\dm'(t) \ket{\r} \bra{\r'}} \ketbra{\br}{\br'}\;, \nn
+\trace{\dm'(t) \ket{\r} \bra{\r'}} \ketbra{\br'}{\br}\;, \nn
 \ee
@@
 \op V'(t)= 
-\int \dd \br \dd \br' U\left[\ketbra{\br}{\br'};\dm'(t)\right] \ketbra{\br}{\br'}\;,
+\int \dd \br \dd \br' U\left[\ketbra{\br}{\br'};\dm'(t)\right] \ketbra{\br'}{\br}\;,
 \ee
@@
 \be\lb{couplingSopDef2}
-\coupl = 
-\int \dd \br \dd \br' \commutator{\ketbra{\br}{\br'}}{\dmnot} U\left[\ketbra{\br}{\br'};\cdot\right] \;.
+\coupl\op O = 
+\int \dd \r \dd \r' \commutator{\ketbra{\r'}{\r}}{\dmnot} U\left[\ketbra{\r}{\r'};\op O\right] \;.
 \ee
@@
 that is:
-\be\lb{leftActionCouplingDef1}
-\trace{\op O' (\coupl \op O)} = \int \dd\br\dd\br'\trace{\ketbra{\br}{\br'}\commutator{\dmnot}{\op O'}}
-U\left[\ketbra{\br}{\br'};\op O\right] \doteq \trace{(\op O' \coupl) \op O } \;,
+\begin{align}\lb{leftActionCouplingDef1}
+\trace{\op O' (\coupl \op O)} &= \int \dd\r\dd\r'\trace{\ketbra{\r'}{\r}\commutator{\dmnot}{\op O'}}
+U\left[\ketbra{\r}{\r'};\op O\right]  = \nn \\ &= 
+U\left[\commutator{\dmnot}{\op O'};\op O\right] \doteq \trace{(\op O' \coupl) \op O } \;,
+\end{align}
+where the second equality follows from the linearity of the coupling kernel. The right action of the coupling superoperator consistent with this result is:
+\be\lb{leftActionCouplingDef2}
+(\op O \coupl) = \int \dd\r\dd\r'
+U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;.
 \ee
-and so we have:
-\be\lb{leftActionCouplingDef2}
-(\op O' \coupl) = \int \dd\br\dd\br'\trace{\ketbra{\br}{\br'}\commutator{\dmnot}{\op O'}}
-U\left[\ketbra{\br}{\br'};\op O\right] \;.
-\ee
+This formalism allows us to provide a compact expression for the action of the Liouville superoperator on the excitation operators. For the left action we have:
+\begin{align}
+\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi_p}{\psi_p} - \sum_p\ket{\psi_p} \bra{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
+&+ \sum_p \sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ketbra{\psi(\alpha)}{\psi_p}
+- \sum_p \sint \dd\alpha U[\excite{p}{\alpha}; \op E] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;,
+\end{align}
+where the action of the coupling superoperator on $\op E$ has been computed imposing its expansion in the transition basis and computing the coefficients with formula 
+\eqref{leftActionCouplingDef1}. Projecting out the previous equation by multiplication with an occupied eigenstates from both the left and right provides the equations:
+\begin{align}
+\left(\hnot-\eps_p\right)\ket{\phi_p} +\sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ket{\psi(\alpha)} &= E\ket{\phi_p} \nn \\
+\bra{\chi_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U[\excite{p}{\alpha}; \op E] &= -E\bra{\chi_p} 
+\end{align}
 

### 2018-01-09 LRDraft.tex
update

@@
 coefficients that appears in \eqref{XYcoeffDef1}, that is:
-\begin{align}
+\begin{align}\lb{ExcitonicStatesDef1}
 \ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
@@
 \begin{align}
-\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi_p}{\psi_p} - \sum_p\ket{\psi_p} \bra{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
+\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi^E_p}{\psi_p} - \sum_p\ketbra{\psi_p}{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
 &+ \sum_p \sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ketbra{\psi(\alpha)}{\psi_p}
-- \sum_p \sint \dd\alpha U[\excite{p}{\alpha}; \op E] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;,
+- \sum_p \sint \dd\alpha U[\excite{p}{\alpha}; \op E] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;, \nn
 \end{align}
@@
 \eqref{leftActionCouplingDef1}. Projecting out the previous equation by multiplication with an occupied eigenstates from both the left and right provides the equations:
+\begin{align}\lb{PhipChipEqDef1}
+\left(\hnot-\eps_p\right)\ket{\phi^E_p} +\sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ket{\psi(\alpha)} &= E\ket{\phi^E_p} \;,\nn \\
+\bra{\chi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U[\excite{p}{\alpha}; \op E] &= -E\bra{\chi^E_p} \;.
+\end{align}
+We observe that the coupling kernel behaves as a (non-local) potential that depends on both the $X_{E}^{p \alpha}$ and $Y_{E}^{p \alpha}$ coefficients of \eqref{ExcitonicStatesDef1}
+thus introducing a coupling between the $\phi$ and $\chi$ states.
+
+In the same way the right action provides:
 \begin{align}
-\left(\hnot-\eps_p\right)\ket{\phi_p} +\sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ket{\psi(\alpha)} &= E\ket{\phi_p} \nn \\
-\bra{\chi_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U[\excite{p}{\alpha}; \op E] &= -E\bra{\chi_p} 
+\op{\tilde E}\Liouv &= \sum_p\tketbra{\psi_p}{\phi^E_p}\left(\hnot-\eps_p\right) - \sum_p\left(\hnot-\eps_p\right)\tketbra{\chi^E_p}{\psi^E_p} + \nn \\
+&+ \sum_p \sint \dd\alpha  U[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}] \ketbra{\psi(\alpha)}{\psi_p}
++ \sum_p \sint \dd\alpha U[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}] \ketbra{\psi_p}{\psi(\alpha)} = E\op{\tilde E} \;, \nn
 \end{align}

### 2018-01-10 LRDraft.tex
update

--- 2018-01-09 LRDraft.tex
@@
 
+\subsection{Localization properties of the response density}
+
+We present an ulterior expression of the response density operator in the frequency space with the aim to establish its (spatial) localization properties.
+The starting point of this analysis is the expression of the response density in terms of the commutator of \eqref{rhoPrimeOmegaDef1}. We observe that, for any 
+operator $\op O$, we may write:  
+\be
+\commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
+\ee
+where $\op Q_0= \identity - \dmnot$ projects the operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
+\be
+\dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
+\ee
+This equation suggests us to define the \emph{fluctuation states}:
+\be\lb{fluctuationStateDef1}
+\ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \qq
+\bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
+\ee
+where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by definition,
+orthogonal to the occupied eigenstates of $\hnot$, so that:
+\be
+\brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall p,q,\omega
+\ee
+The response density written in terms of the fluctuation states reads:
+\be\lb{rhoPrimeFluctuationStateDef1}
+\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
+\ee
+Applying the Liouville equation \eqref{LiouvillianRhopomegaDef3} to \eqref{rhoPrimeFluctuationStateDef1} allows us to derive a set of equation of motion for the
+fluctuation states. The following equations are useful for this task:
+\begin{align}
+\Liouvnot\dm'(\omega) & = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)}\left(\eps_p-\hnot\right) + \left(\hnot-\eps_p\right)\ketbra{f_p(\omega)}{\psi_p}\right) \;, \nn \\
+\coupl\dm'(\omega) &= \commutator{\op V'(\omega)}{\dmnot} = \op Q_0 \op V'(\omega) \dmnot - \dmnot \op V'(\omega) \op Q_0 = \nn \\
+& = \sum_p\left( \op Q_0 \op V'(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op V'(\omega) \op Q_0 \right) \;, \nn \\
+\commutator{\op \Phi(\omega)}{\dmnot} & =  \sum_p\left( \op Q_0 \op \Phi(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op \Phi(\omega) \op Q_0 \right) \;, \nn
+\end{align} 
+so that:
+\begin{align}
+\left[\bbomega - \left(\hnot-\eps_p\right)\right]\ket{f_p(\omega)} &= \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;, \nn \\
+\bra{f_p(\omega)}\left[\bbomega + \left(\eps_p-\hnot\right)\right] &= \bra{\psi_p}\left(\op V'(-\omega) + \op \Phi(-\omega)\right)\op Q_0 \;.
+\end{align}
+
 \subsection{Analysis of the excitations}
@@
 \ee
-and consequently the formal action of the coupling superoperator \eqref{couplingSopDef1} can be expressed as: 
+and consequently the formal action of the coupling superoperator \eqref{couplingSopDef1} on a generic operator $\op O$ can be expressed as: 
 \be\lb{couplingSopDef2}
@@
 \begin{align}
-\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi_p}{\psi_p} - \sum_p\ket{\psi_p} \bra{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
-&+ \sum_p \sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ketbra{\psi(\alpha)}{\psi_p}
-- \sum_p \sint \dd\alpha U[\excite{p}{\alpha}; \op E] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;,
+\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi^E_p}{\psi_p} - \sum_p\ketbra{\psi_p}{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
+&+ \sum_p \sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ketbra{\psi(\alpha)}{\psi_p}
+- \sum_p \sint \dd\alpha U\left[\excite{p}{\alpha}; \op E\right] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;, \nn
 \end{align}
-where the action of the coupling superoperator on $\op E$ has been computed imposing its expansion in the transition basis and computing the coefficients with formula 
+here the action of the coupling superoperator on $\op E$ has been computed imposing its expansion in the transition basis and computing the coefficients with formula 
 \eqref{leftActionCouplingDef1}. Projecting out the previous equation by multiplication with an occupied eigenstates from both the left and right provides the equations:
+\begin{align}\lb{PhipChipEqDef1}
+\left(\hnot-\eps_p\right)\ket{\phi^E_p} +\sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ket{\psi(\alpha)} &= E\ket{\phi^E_p} \;,\nn \\
+\bra{\chi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\excite{p}{\alpha}; \op E\right] &= -E\bra{\chi^E_p} \;.
+\end{align}
+We observe that the coupling kernel behaves as a (non-local) potential that depends on both the $X_{E}^{p \alpha}$ and $Y_{E}^{p \alpha}$ coefficients of \eqref{ExcitonicStatesDef1}
+thus introducing a coupling between the $\phi$ and $\chi$ states.
+
+In the same way the right action provides:
 \begin{align}
-\left(\hnot-\eps_p\right)\ket{\phi_p} +\sint \dd\alpha  U[\decay{\alpha}{p}; \op E] \ket{\psi(\alpha)} &= E\ket{\phi_p} \nn \\
-\bra{\chi_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U[\excite{p}{\alpha}; \op E] &= -E\bra{\chi_p} 
+\op{\tilde E}\Liouv &= \sum_p\tketbra{\psi_p}{\phi^E_p}\left(\hnot-\eps_p\right) - \sum_p\left(\hnot-\eps_p\right)\tket{\chi^E_p}\bra{\psi^E_p} + \nn \\
+&+ \sum_p \sint \dd\alpha  U\left[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}\right] \ketbra{\psi(\alpha)}{\psi_p}
++ \sum_p \sint \dd\alpha U\left[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}\right] \ketbra{\psi_p}{\psi(\alpha)} = E\op{\tilde E} \;, \nn
+\end{align}
+so that:
+\begin{align}\lb{TildePhipChipEqDef1}
+\tbra{\phi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}\right]  &= E\tbra{\phi^E_p} \;,\nn \\
+\left(\hnot-\eps_p\right)\tket{\chi^E_p} -\sint \dd\alpha \bra{\psi(\alpha)} U\left[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}\right] &= -E\tket{\chi^E_p} \;.
 \end{align}
 
-\section{Draft of the paper - old notes}
-
-\begin{itemize}
-\item Aim of the paper: Compute the electronic properties of a molecular system with the formalism of linear scaling using a LR-TDDFT inside BigDFT code. 
-%We also want to define a set of computational tools that allow to check the reliability of the computation.  
-\end{itemize}
-
-\begin{itemize}
-\item Motivation: the DFT code have reached reliable features of precision for the computation of the GS.
-The same probletic are instead needed in order to achieve the same type of results for spectroscopic properties in large systems
-\begin{itemize}
-\item Quantify the impact of several modelling of a given systems (environment, disorder)
-\item Systematic approach has proven its effectiveness for GS calculations (easy to handle)~\cite{deltatest2016}.
+% \section{Draft of the paper - old notes}
+% 
+% \begin{itemize}
+% \item Aim of the paper: Compute the electronic properties of a molecular system with the formalism of linear scaling using a LR-TDDFT inside BigDFT code. 
+% %We also want to define a set of computational tools that allow to check the reliability of the computation.  
+% \end{itemize}
+% 
+% \begin{itemize}
+% \item Motivation: the DFT code have reached reliable features of precision for the computation of the GS.
+The same probletic are instead needed in order to achieve the same type of results for spectroscopic
+% properties in large systems
+% \begin{itemize}
+% \item Quantify the impact of several modelling of a given systems (environment, disorder)
+% \item Systematic approach has proven its effectiveness for GS calculations (easy to handle)~\cite{deltatest2016}.
 The quality of localized basis function is therefore easy to quantify (variational theorem)
-\item A challenge is represented by large scale computation for \emph{molecular} systems
-\end{itemize}
-\item State-of-the-art 
-\begin{itemize}
-\item localized basis set for representing the Hamiltonians (e.g. Fiesta (Blase, Olevano), FHI-Aims, GWMol)
-\item This approach has been also generalized to LR calculation in the case of ONETEP \cite{Ratcliff2013}.
+% \item A challenge is represented by large scale computation for \emph{molecular} systems
+% \end{itemize}
+% \item State-of-the-art 
+% \begin{itemize}
+% \item localized basis set for representing the Hamiltonians (e.g. Fiesta (Blase, Olevano), FHI-Aims, GWMol)
+% \item This approach has been also generalized to LR calculation in the case of ONETEP \cite{Ratcliff2013}.
 However little is said about the reliability of the results in terms of the convergence of the spectra
-\end{itemize}
-\item Content of the paper: 
-\begin{itemize}
-\item Brief illustration of the support function approach in wavelets (Large systems are  accessible for the structure (Energy, Forces,\ldots)
-\item We want to exploit the wavelet properties in the context of LR, \emph{by also providing some criteria} which may be of interest for the evaluation of the quality of the LR results.
-\end{itemize}
-\item Conclusions and implications
-\begin{itemize}
-\item We might apply this formalism also in the contect of MBPT and inspect the validity of the linear response functional for e.g.
+% \end{itemize}
+% \item Content of the paper: 
+% \begin{itemize}
+% \item Brief illustration of the support function approach in wavelets (Large systems are  accessible for the structure (Energy, Forces,\ldots)
+% \item We want to exploit the wavelet properties in the context of LR, \emph{by also providing some criteria} which may be of interest for the evaluation of the quality of the LR results.
+% \end{itemize}
+% \item Conclusions and implications
+% \begin{itemize}
+% \item We might apply this formalism also in the contect of MBPT and inspect the validity of the linear response functional for e.g.
 GW calcualtions (the perturbation operator will be different from the dipole)
-\end{itemize}
-\end{itemize}
+% \end{itemize}
+% \end{itemize}
 
@@
 
-\bibliographystyle{alpha}
-\bibliography{sample}
+%\bibliographystyle{alpha}
+%\bibliography{sample}
 

### 2018-01-15 LRDraft.tex
update

@@
 
-\section{THEORY}
+\section{General theoretical setup}
 
@@
 
-\subsection{Localization properties of the response density}
+\section{Critical Analysis of the linear response results}
 
-We present an ulterior expression of the response density operator in the frequency space with the aim to establish its (spatial) localization properties.
-The starting point of this analysis is the expression of the response density in terms of the commutator of \eqref{rhoPrimeOmegaDef1}. We observe that, for any 
+The main aim of this section is to discuss the reliability in the assessment of the results provided by the linear response formalism. In particular we are interested in 
+analyzing the \emph{linear response functional} defined as:
+\be\lb{LinearResponseFunctDef1}
+{\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
+\ee
+that represents the perturbation-induced modification of the expectation value of an observable $\op O$. Here, for a sake of concreteness, we are limiting our considerations 
+to observables that do not explicitly depend on time.
+
+We start this analysis by deriving an ulterior expression of the response density operator in the frequency space. We consider equation \eqref{rhoPrimeOmegaDef1} and observe that, for any 
 operator $\op O$, we may write:  
@@
 \ee
-where $\op Q_0= \identity - \dmnot$ projects the operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
+where $\op Q_0= \identity - \dmnot$ is the projection operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
 \be
@@
 \ee
-where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by definition,
-orthogonal to the occupied eigenstates of $\hnot$, so that:
+where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. An inspection of equation \eqref{ketBraTimeEvol1} 
+evidence that formulas \eqref{fluctuationStateDef1} are equivalent to the action of the $\op Q_0$ projector acting on the time evolution of the (occupied) eigenstates of $\hnot$, written 
+in the $\omega$ domain. Fluctuation states are, by definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
 \be
-\brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall p,q,\omega
+\brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega \;.
 \ee
@@
 \be\lb{rhoPrimeFluctuationStateDef1}
-\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
+\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
 \ee
-Applying the Liouville equation \eqref{LiouvillianRhopomegaDef3} to \eqref{rhoPrimeFluctuationStateDef1} allows us to derive a set of equation of motion for the
-fluctuation states. The following equations are useful for this task:
+and consequently the linear response functional can be expressed as:
+\be\lb{LinearResponseFunctDef2}
+{\cal R}_{\op O}(\omega) = 
+\sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
+\ee
+The task of the linear response formalism to provided reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
+expression for the fluctuation states in the domain in which $\op O\ket{\psi_p}$ (and its hermitian conjugate) are not vanishing.
+
+\subsection{Localization argument for the fluctuation states}
+
+Starting from the Liouville equation \eqref{LiouvillianRhopomegaDef3} it is possible to derive a set of equation of motion for the fluctuation states. 
+The following equations are useful for this task: 
 \begin{align}
-\Liouvnot\dm'(\omega) & = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)}\left(\eps_p-\hnot\right) + \left(\hnot-\eps_p\right)\ketbra{f_p(\omega)}{\psi_p}\right) \;, \nn \\
+\Liouvnot\dm'(\omega) & = \sum_p\left(-\ketbra{\psi_p}{f_p(-\omega)}\left(\hnot-\eps_p\right) + \left(\hnot-\eps_p\right)\ketbra{f_p(\omega)}{\psi_p}\right) \;, \nn \\
 \coupl\dm'(\omega) &= \commutator{\op V'(\omega)}{\dmnot} = \op Q_0 \op V'(\omega) \dmnot - \dmnot \op V'(\omega) \op Q_0 = \nn \\
 & = \sum_p\left( \op Q_0 \op V'(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op V'(\omega) \op Q_0 \right) \;, \nn \\
-\commutator{\op \Phi(\omega)}{\dmnot} & =  \sum_p\left( \op Q_0 \op \Phi(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op \Phi(\omega) \op Q_0 \right) \;, \nn
+\commutator{\op \Phi(\omega)}{\dmnot} & =  \sum_p\left( \op Q_0 \op \Phi(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op \Phi(\omega) \op Q_0 \right) \;. \nn
 \end{align} 
-so that:
-\begin{align}
+Liouville equation written in this fashion implies the following equations for the fluctuation states, that can be extracted by multiplying from left and right for the 
+occupied eigenstates of $\hnot$:
+\begin{align}\lb{fluctuationStateEqMotion1}
 \left[\bbomega - \left(\hnot-\eps_p\right)\right]\ket{f_p(\omega)} &= \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;, \nn \\
-\bra{f_p(\omega)}\left[\bbomega + \left(\eps_p-\hnot\right)\right] &= \bra{\psi_p}\left(\op V'(-\omega) + \op \Phi(-\omega)\right)\op Q_0 \;.
+\bra{f_p(-\omega)}\left[-\bbomega - \left(\hnot-\eps_p\right)\right] &= \bra{\psi_p}\left(\op V'(\omega) + \op \Phi(\omega)\right)\op Q_0 \;.
 \end{align}
+These equations allows us to present a localization argument for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of 
+\eqref{fluctuationStateEqMotion1}, but the same argument holds also for the left ones.
+
+We split the unperturbed Hamiltonian as the kinetic $\op T$ plus the potential $\op V$ term, so that the equation of motion for $\ket{f_p(\omega)}$ is recasted as:
+\be\lb{fluctuationStateEqMotion}
+\left(\bbomega+\eps_p -\op T\right)\ket{f_p(\omega)} = \op V\ket{f_p(\omega)} + \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;.
+\ee
+
+% We present an ulterior expression of the response density operator in the frequency space with the aim to establish its (spatial) localization properties.
+% The starting point of this analysis is the expression of the response density in terms of the commutator of \eqref{rhoPrimeOmegaDef1}. We observe that, for any 
+% operator $\op O$, we may write:  
+% \be
+% \commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
+% \ee
+% where $\op Q_0= \identity - \dmnot$ projects the operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
+% \be
+% \dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
+% \ee
+% This equation suggests us to define the \emph{fluctuation states}:
+% \be%\lb{fluctuationStateDef1}
+% \ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \qq
+% \bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
+% \ee
+% where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by definition,
+% orthogonal to the occupied eigenstates of $\hnot$, so that:
+% \be
+% \brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega
+% \ee
+% The response density written in terms of the fluctuation states reads:
+% \be\lb{rhoPrimeFluctuationStateDef1}
+% \dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
+% \ee
 

### 2018-01-16 LRDraft.tex
update

@@
 \ee
+This equation has the formal structure of an inhomogeneous Helmholtz equation and can be written in the coordinate representation as:
+\be
+\left(k_p(\omega)^2+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k_p(\omega)^2 = 2(\omega+\eps_p) \;,
+\ee
+and admits an integral representation in the form
+\be\lb{fluctuationStateIntEq1}
+f_p(\omega,\r) = \int \dd\r' g_H(\r-\r')s(\r') \;,
+\ee
+where $g_H(\r)$ is the Green function of the Helmholtz operator in three dimensions. This integral representation allows us to assess the localization character 
+of the fluctuation states, \emph{i.e.} the behavior of $f_p(\omega,\r)$ when $\r$ becomes large. Indeed, assuming that the support of the source term is compact
+we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing:
+\be\lb{fluctuationStateIntEq2}
+f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k_p(\omega)^2} |\r|}}{|\r|} \;,
+\ee
+so the asymptotic character of the fluctuation states depends on the sign of $k_p(\omega)^2$. In particular equation \eqref{fluctuationStateIntEq2} describes an
+exponential damping for $\omega < |\eps_p|$ and an oscillating power law behavior for $\omega \geq |\eps_p|$ ().
+
+This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef2}. We conclude that
+the linear response functional is built in terms of pure localized functions for $\omega < |\eps_h|$, instead in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
+contributions from local and non-local quantities and, finally is composed only by non-local fluctuation states for $\omega\geq|\eps_0|$.
 

### 2018-01-17 LRDraft.tex
update

@@
 so the asymptotic character of the fluctuation states depends on the sign of $k_p(\omega)^2$. In particular equation \eqref{fluctuationStateIntEq2} describes an
-exponential damping for $\omega < |\eps_p|$ and an oscillating power law behavior for $\omega \geq |\eps_p|$ ().
+exponential damping for $\omega < |\eps_p|$ and an oscillating power law behavior for $\omega \geq |\eps_p|$.
 
@@
 
-% We present an ulterior expression of the response density operator in the frequency space with the aim to establish its (spatial) localization properties.
-% The starting point of this analysis is the expression of the response density in terms of the commutator of \eqref{rhoPrimeOmegaDef1}. We observe that, for any 
-% operator $\op O$, we may write:  
-% \be
-% \commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
-% \ee
-% where $\op Q_0= \identity - \dmnot$ projects the operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
-% \be
-% \dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
-% \ee
-% This equation suggests us to define the \emph{fluctuation states}:
-% \be%\lb{fluctuationStateDef1}
-% \ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \qq
-% \bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
-% \ee
-% where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by definition,
-% orthogonal to the occupied eigenstates of $\hnot$, so that:
-% \be
-% \brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega
-% \ee
-% The response density written in terms of the fluctuation states reads:
-% \be\lb{rhoPrimeFluctuationStateDef1}
-% \dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
-% \ee
+\subsection{Criterion for the choice of the underlying computational basis}
+
+Let us further investigate formula \eqref{LinearResponseFunctDef2} pointing out some computation aspects. We introduce a computational basis $\{\ket{\mu}\}$, composed by a \emph{finite}
+set of functions on which we expand the formal scalar products appearing in \eqref{LinearResponseFunctDef2} as follows:
+\be
+\bra{f_p(-\omega)}\op O\ket{\psi_p} = \sum_\mu \brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} \;.
+\ee
+The quality of the basis can be evaluated by the requirement that the numerical coefficients appearing in the r.h.s provide a reliable reconstruction of the formal scalar product. 
+Here we are assuming that the ground state properties of the unperturbed system have been computed in the same basis introduced above. This means that the feature of the basis, 
+that for instance for real space basis are given by the grid spacing and number of points (that determines the dimension simulation box), are chosen so that the coefficients
+$\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, by assuming 
+that $\op O$ acts as a local operator on the occupied orbitals.
+
+The most interesting point of this discussion concerns the assessment of the reliable sampling of the fluctuation states through the coefficients $\brket{f_p(-\omega)}{\mu}$ and
+$\brket{\mu}{f_p(\omega)}$. The question is non-trivial, as the behavior of the fluctuation states strongly depends on $\omega$, as previously explained.
+The first step needed to address this problem concerns with the evaluation of the reliability of the $\{\ket{\mu}\}$ basis for $\omega=0$, \emph{i.e.} for a perturbing field that does 
+not depend on time. In this case the fluctuation states, as well as the expectation value of a given observable, can be computed performing a ground state calculation in which the perturbing 
+field $\op\Phi$ is added to the external potential of $\hnot$\footnote{We are interested in the linear response, so the magnitude of $\op\Phi$ has to be chosen in a way that respects this 
+regime. To check this point we can compute the perturbation-induced modification of an observable an verify that its value scales linearly with the magnitude of the field}. %, without
+
+%In order to address this aspects it is possible to assess the reali
+%We propose an operative procedure to perform a direct measurement of the
+
+%An explicit check can be performed at $\omega=0$.
+
+%This condition implies that the coefficients
+%$\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals and also the matrix elements $\bra{\mu}\op O\ket{\psi_p}$ can assumed to be well sampled, assuming that
+%$\op O$ acts as a local operator on the occupied orbitals.
 

### 2018-01-17 LRDraft.tex
update

@@
 set of functions on which we expand the formal scalar products appearing in \eqref{LinearResponseFunctDef2} as follows:
-\be
+\be\lb{LinearResponseFunctDef3}
 \bra{f_p(-\omega)}\op O\ket{\psi_p} = \sum_\mu \brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} \;.
 \ee
-The quality of the basis can be evaluated by the requirement that the numerical coefficients appearing in the r.h.s provide a reliable reconstruction of the formal scalar product. 
-Here we are assuming that the ground state properties of the unperturbed system have been computed in the same basis introduced above. This means that the feature of the basis, 
-that for instance for real space basis are given by the grid spacing and number of points (that determines the dimension simulation box), are chosen so that the coefficients
-$\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, by assuming 
+The quality of the basis can be evaluated by the requirement that the numerical coefficients appearing in the r.h.s of \eqref{LinearResponseFunctDef3} provide a reliable reconstruction 
+of the formal scalar product. Here we are assuming that the ground state properties of the unperturbed system have been computed in the same basis introduced above. This means that the 
+feature of the basis, that for instance for real space basis are given by the grid spacing and number of points (that determines the dimension simulation box), are chosen so that the 
+coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, by assuming 
 that $\op O$ acts as a local operator on the occupied orbitals.
 
-The most interesting point of this discussion concerns the assessment of the reliable sampling of the fluctuation states through the coefficients $\brket{f_p(-\omega)}{\mu}$ and
+The most interesting point of this discussion concerns with the assessment of the reliable sampling of the fluctuation states through the coefficients $\brket{f_p(-\omega)}{\mu}$ and
 $\brket{\mu}{f_p(\omega)}$. The question is non-trivial, as the behavior of the fluctuation states strongly depends on $\omega$, as previously explained.
@@
 field $\op\Phi$ is added to the external potential of $\hnot$\footnote{We are interested in the linear response, so the magnitude of $\op\Phi$ has to be chosen in a way that respects this 
-regime. To check this point we can compute the perturbation-induced modification of an observable an verify that its value scales linearly with the magnitude of the field}. %, without
+regime. To check this point we can compute the perturbation-induced modification of an observable an verify that its value scales linearly with the magnitude of the field}. 
+The goodness of the $\{\ket{\mu}\}$ basis can thus be verified as in the standard ground state calculation, for instance by checking that, given a certain level of completeness of the basis,
+the energy of the occupied (perturbed) orbitals is stable with respect to further refinements.
 
-%In order to address this aspects it is possible to assess the reali
-%We propose an operative procedure to perform a direct measurement of the
+Once that a basis with acceptable features has been chosen and verified for $\omega=0$ we can reasonably extend its reliability to $\omega>0$ by using the localization argument presented above. 
+Indeed, we have argued that fluctuation states retain a local behavior up to $\omega=|\eps_h|$ and so we can expect that, up to this threshold value, the $\{\ket{\mu}\}$ basis represents an 
+effective tool for a precise discretization of \eqref{LinearResponseFunctDef3}, thus providing a reliable estimate of the linear response.
 
-%An explicit check can be performed at $\omega=0$.
+On the contrary, the situation becomes very less predictable for $\omega$ higher than the threshold $|\eps_h|$ since in this regime the fluctuation states start to delocalize in all the 
+accessible space and the spatial cutoff is provided only by the ground state matrix elements $\bra{\mu}\op O\ket{\psi_p}$.  
+In this case formula \eqref{LinearResponseFunctDef3} provides basis independent results only if the (partial) sampling of the fluctuation states is reconstructed in the domain in which
+$\bra{\mu}\op O\ket{\psi_p}$ are non vanishing. As we shall see through explicit computations this requirement turns out to be quite severe and choices of the basis that provide precise
+results below $|\eps_p|$ fails in the high-$\omega$ regime.
 
-%This condition implies that the coefficients
-%$\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals and also the matrix elements $\bra{\mu}\op O\ket{\psi_p}$ can assumed to be well sampled, assuming that
-%$\op O$ acts as a local operator on the occupied orbitals.
+\subsection{Excitation operator and the analytic structure of the linear response}
 
-\subsection{Analysis of the excitations}
+%The linear response presented so far is expressed in functions of the fluctuation states. These objects essentially describe the modification of the occupied eigenstates of 
+%$\hnot$ induced by the perturbation. They exhibit an explicit dependence on the perturbing field and their $\omega$ dependence is a complicated combination of the intrinsic
+%feature of the system
+
+The linear response presented so far is expressed in functions of the fluctuation states. These objects essentially describe the modification of the occupied eigenstates of 
+$\hnot$ induced by the perturbation and, by definition, explicitly depend on the perturbing field. As a consequence, the $\omega$ dependence of fluctuation states is a complicated 
+combination of the one of $\op\Phi(\omega)$ and of the intrinsic energetic feature of the system.
+
+For these reason it is preferable to present an equivalent but alternative formula for the linear response functional \eqref{LinearResponseFunctDef2}...
+
+%They exhibit an explicit dependence on the perturbing field and their $\omega$ dependence is a complicated combination of the intrinsic
+%eature of the system
 

### 2018-01-19 LRDraft.tex
update

@@
 \subsection{Localization argument for the fluctuation states}
+\lb{LocalizationFluctuationStates}
 
@@
 \be
-\left(k_p(\omega)^2+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k_p(\omega)^2 = 2(\omega+\eps_p) \;,
+\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k^2_p(\omega) = 2(\omega+\eps_p) \;,
 \ee
@@
 \be\lb{fluctuationStateIntEq2}
-f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k_p(\omega)^2} |\r|}}{|\r|} \;,
+f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)} |\r|}}{|\r|} \;,
 \ee
-so the asymptotic character of the fluctuation states depends on the sign of $k_p(\omega)^2$. In particular equation \eqref{fluctuationStateIntEq2} describes an
+so the asymptotic character of the fluctuation states depends on the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an
 exponential damping for $\omega < |\eps_p|$ and an oscillating power law behavior for $\omega \geq |\eps_p|$.
@@
 
-%The linear response presented so far is expressed in functions of the fluctuation states. These objects essentially describe the modification of the occupied eigenstates of 
-%$\hnot$ induced by the perturbation. They exhibit an explicit dependence on the perturbing field and their $\omega$ dependence is a complicated combination of the intrinsic
-%feature of the system
+The linear response presented so far is expressed in functions of the fluctuation states, that essentially describe the modification of the occupied eigenstates of $\hnot$ induced by 
+the perturbation. Fluctuation states depend explicitly on the perturbing field $\op\Phi(\omega)$ and, consequently, the analytic structure of the linear response written as in formula 
+\eqref{LinearResponseFunctDef2} emerge through a combination of the $\omega$ dependence of the perturbing field an on the intrinsic response of the system under inspection.
 
-The linear response presented so far is expressed in functions of the fluctuation states. These objects essentially describe the modification of the occupied eigenstates of 
-$\hnot$ induced by the perturbation and, by definition, explicitly depend on the perturbing field. As a consequence, the $\omega$ dependence of fluctuation states is a complicated 
-combination of the one of $\op\Phi(\omega)$ and of the intrinsic energetic feature of the system.
+It is however possible to present and equivalent but alternative formulation of the linear response that allows us to express the response density operator in term of the spectral
+decomposition of the Liouville superoperator. This approach naturally leads to the concept of \emph{excitation operators}, defined through a self-consistent operator eigenvalue equation,
+that codify the intrinsic capability of the system to respond to an arbitrary perturbation. Excitations behave as singularity of the response density operator and their knowledge provides a 
+deeper insight into the analytic structure of the linear response.
 
-For these reason it is preferable to present an equivalent but alternative formula for the linear response functional \eqref{LinearResponseFunctDef2}...
-
-%They exhibit an explicit dependence on the perturbing field and their $\omega$ dependence is a complicated combination of the intrinsic
-%eature of the system
+The material presented in this section discusses a complete re-derivation of the linear response written in terms of excitation operators. Moreover, we will evidence that a \emph{localization 
+argument}, analogous to the one presented in section \ref{LocalizationFluctuationStates} for the fluctuation states, holds also for the excited states of the systems below a specific energetic
+threshold. This analysis has relevant consequence both under theoretical and computational point of view. Indeed, it provides a deeper understanding in the role of both localized and de-localized 
+excitations in determining the analytic structure of the linear response and it gives us clear indication in the level of refinement of the computational setup needed to obtain reliable results 
+from a linear response calculation.
 

### 2018-01-23 LRDraft.tex
update

@@
 \usepackage[colorlinks=true, allcolors=blue]{hyperref}
+\usepackage{authblk}
 
@@
 On the Localization of the Linear-Response excitations in Open Systems}
-\author{You}
+\author[1]{Luigi Genovese}
+\author[2]{Marco D'Alessandro}
+\affil[1]{Laboratoire de Simulation Atomistique (LSim), SP2M, INAC, CEA-UJF, 17 Av. des Martyrs,
+38054 Grenoble, France}
+\affil[2]{Istituto di Struttura della Materia-CNR (ISM-CNR), Via del Fosso del Cavaliere 100, 00133 Roma, Italia}
 
@@
 \ee
-The task of the linear response formalism to provided reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
-expression for the fluctuation states in the domain in which $\op O\ket{\psi_p}$ (and its hermitian conjugate) are not vanishing.
+Let us further investigate this formula pointing out some of the  computational aspects needed to explicitly perform the scalar products appearing in 
+\eqref{LinearResponseFunctDef2}. 
+We introduce a computational $\mu$-basis, composed by a finite set of $n_\mu$ basis elements $\{\ket{\mu}\}$, and assume that a reliable solution of the ground state problem has 
+been provided in this basis. This means that the feature of the basis (that, for instance, for real space basis are given by the grid spacing and number of points) are chosen so 
+that the coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, 
+under the hypothesis that the observable $\op O$ acts as a local operator on the occupied orbitals.
 
-\subsection{Localization argument for the fluctuation states}
+The formal scalar products that express the linear response functional \eqref{LinearResponseFunctDef1} can be evaluated in the same basis introduced above, that is: 
+%For instance the first addend of \eqref{LinearResponseFunctDef2} reads: 
+%\be\lb{LinearResponseFunctDef3}
+%\bra{f_p(-\omega)}\op O\ket{\psi_p} = \sum_\mu \brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} \;.
+%\ee
+\be\lb{LinearResponseFunctDef3}
+{\cal R}_{\op O}(\omega) = 
+\sum_p\sum_\mu\left(\brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{\mu}\brket{\mu}{f_p(\omega)}\right) \;.
+\ee
+The task of the linear response formalism to provide reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
+expression for the numerical coefficients appearing in \eqref{LinearResponseFunctDef3}. The features of the computational basis described above ensures that this requirement should
+be satisfied for $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian conjugates). 
+On the contrary, the problem of the reliable reconstruction of the fluctuation states through the sampling of the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$
+turns out to be highly non-trivial, since the behavior of the fluctuation states strongly depends on $\omega$, as will be readily clarified in the next section.
+
+%On the contrary, the most interesting point of this discussion concerns with the assessment of the 
+%reliable sampling of the fluctuation states through the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$. The problem turns out to be highly is non-trivial 
+%since the behavior of the fluctuation states strongly depends on $\omega$, as will be readily clarified in the next section.
+
+%$\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$ in the domain in which the matrix elements $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian 
+%conjugates) are not vanishing. 
+%The task of the linear response formalism to provide reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
+%expression for the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$ in the domain in which the matrix elements $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian 
+%conjugates) are not vanishing.
+
+% We assume that the ground state problem has been already solved and that the occupied orbitals  introduce a computational basis $\{\ket{\mu}\}$, composed by a \emph{finite}
+% set of functions
+% 
+% Here we are dealing with a linear response problem and
+
+% The quality of the basis can be evaluated by the requirement that the numerical coefficients appearing in the r.h.s of \eqref{LinearResponseFunctDef3} provide a reliable reconstruction 
+% of the formal scalar product.
+
+% Here we are assuming that the ground state properties of the unperturbed system have been computed in the same basis introduced above. This means that the 
+% feature of the basis, that for instance for real space basis are given by the grid spacing and number of points (that determines the dimension simulation box), are chosen so that the 
+% coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, by assuming 
+% that $\op O$ acts as a local operator on the occupied orbitals.
+
+% aggiungere un preambolo a quello che segue. Soluzione usando le equazioni di Sternheimer e approccio con le eccitazioni....
+
+\subsection{Sternheimer equations and localization properties of the fluctuation states}
+%\subsection{Localization argument for the fluctuation states}
 \lb{LocalizationFluctuationStates}
@@
 \end{align}
-These equations allows us to present a localization argument for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of 
-\eqref{fluctuationStateEqMotion1}, but the same argument holds also for the left ones.
+Equations \eqref{fluctuationStateEqMotion1} have the form of a Sternheimer equation. Once projected in the $\{\ket{\mu}\}$ basis, and fixed the value of $\omega$, they can be solved 
+using a self-consistent procedure (add references). This approach provides a direct evaluation of the fluctuation states and thus the linear response functional \eqref{LinearResponseFunctDef3}
+can be computed.
 
-We split the unperturbed Hamiltonian as the kinetic $\op T$ plus the potential $\op V$ term, so that the equation of motion for $\ket{f_p(\omega)}$ is recasted as:
+Much more interestingly for the main topic of the present discussion, and regardless from the detailed strategy of their solutions, equations \eqref{fluctuationStateEqMotion1} 
+allow us to present a \emph{localization argument} for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of \eqref{fluctuationStateEqMotion1}, 
+but the same argument holds also for the left ones. We split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term, so that the equation of motion 
+for $\ket{f_p(\omega)}$ is recasted as:
 \be\lb{fluctuationStateEqMotion}
@@
 \be
-\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k^2_p(\omega) = 2(\omega+\eps_p) \;,
+\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k^2_p(\omega) = 2(\omega+\eps_p) \;.
 \ee
-and admits an integral representation in the form
+The solution of this equation admits an integral representation in the form:
 \be\lb{fluctuationStateIntEq1}
@@
 of the fluctuation states, \emph{i.e.} the behavior of $f_p(\omega,\r)$ when $\r$ becomes large. Indeed, assuming that the support of the source term is compact
-we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing:
+we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing, the leading contribution of the fluctuation states
+is given by:
 \be\lb{fluctuationStateIntEq2}
-f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)} |\r|}}{|\r|} \;,
+f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \;.
 \ee
-so the asymptotic character of the fluctuation states depends on the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an
-exponential damping for $\omega < |\eps_p|$ and an oscillating power law behavior for $\omega \geq |\eps_p|$.
-
-This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef2}. We conclude that
-the linear response functional is built in terms of pure localized functions for $\omega < |\eps_h|$, instead in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
+We observe that the presence of the regularization parameter $\eta$ ensures a (slow) asymptotic convergence to zero, nonetheless the qualitative $\r$-dependence of the fluctuation 
+states is determined by the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an exponential damping for $\omega < |\eps_p|$ and an oscillating 
+power law behavior for $\omega \geq |\eps_p|$.
+This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef3}, so we conclude that
+the linear response functional is built in terms of localized fluctuation states for $\omega < |\eps_h|$. Instead, in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
 contributions from local and non-local quantities and, finally is composed only by non-local fluctuation states for $\omega\geq|\eps_0|$.
 
-\subsection{Criterion for the choice of the underlying computational basis}
+\subsubsection{Criterion for the choice of the computational basis} %underlying
 
-Let us further investigate formula \eqref{LinearResponseFunctDef2} pointing out some computation aspects. We introduce a computational basis $\{\ket{\mu}\}$, composed by a \emph{finite}
-set of functions on which we expand the formal scalar products appearing in \eqref{LinearResponseFunctDef2} as follows:
-\be\lb{LinearResponseFunctDef3}
-\bra{f_p(-\omega)}\op O\ket{\psi_p} = \sum_\mu \brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} \;.
-\ee
-The quality of the basis can be evaluated by the requirement that the numerical coefficients appearing in the r.h.s of \eqref{LinearResponseFunctDef3} provide a reliable reconstruction 
-of the formal scalar product. Here we are assuming that the ground state properties of the unperturbed system have been computed in the same basis introduced above. This means that the 
-feature of the basis, that for instance for real space basis are given by the grid spacing and number of points (that determines the dimension simulation box), are chosen so that the 
-coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, by assuming 
-that $\op O$ acts as a local operator on the occupied orbitals.
-
-The most interesting point of this discussion concerns with the assessment of the reliable sampling of the fluctuation states through the coefficients $\brket{f_p(-\omega)}{\mu}$ and
-$\brket{\mu}{f_p(\omega)}$. The question is non-trivial, as the behavior of the fluctuation states strongly depends on $\omega$, as previously explained.
-The first step needed to address this problem concerns with the evaluation of the reliability of the $\{\ket{\mu}\}$ basis for $\omega=0$, \emph{i.e.} for a perturbing field that does 
+The capability of the computational basis to express the results of the linear response can be discussed on the localization argument previously presented. 
+The first step needed to address this problem concerns with the evaluation of the reliability of the $\mu$-basis for $\omega=0$, \emph{i.e.} for a perturbing field that does 
 not depend on time. In this case the fluctuation states, as well as the expectation value of a given observable, can be computed performing a ground state calculation in which the perturbing 
@@
 regime. To check this point we can compute the perturbation-induced modification of an observable an verify that its value scales linearly with the magnitude of the field}. 
-The goodness of the $\{\ket{\mu}\}$ basis can thus be verified as in the standard ground state calculation, for instance by checking that, given a certain level of completeness of the basis,
+The goodness of the $\mu$-basis can thus be verified as in the standard ground state calculation, for instance by checking that, given a certain level of completeness of the basis,
 the energy of the occupied (perturbed) orbitals is stable with respect to further refinements.
 
-Once that a basis with acceptable features has been chosen and verified for $\omega=0$ we can reasonably extend its reliability to $\omega>0$ by using the localization argument presented above. 
-Indeed, we have argued that fluctuation states retain a local behavior up to $\omega=|\eps_h|$ and so we can expect that, up to this threshold value, the $\{\ket{\mu}\}$ basis represents an 
+Once that a basis with acceptable features has been chosen and verified for $\omega=0$ we can reasonably extend its reliability to $\omega>0$ by using the localization argument. 
+Indeed, we have argued that fluctuation states retain a local behavior up to $\omega=|\eps_h|$ and so we can expect that, up to this threshold value, the $\mu$-basis represents an 
 effective tool for a precise discretization of \eqref{LinearResponseFunctDef3}, thus providing a reliable estimate of the linear response.
@@
 
-\subsection{Excitation operator and the analytic structure of the linear response}
+%\subsection{Excitation operator and the analytic structure of the linear response}
+\subsection{Linear response \emph{via} the construction of the excitation operators}
 
@@
 
-\subsubsection{Definition of the basis of transitions}
+%\subsubsection{Definition of the basis of transitions}
+\subsubsection{Explicit sampling of the empty-states subspace}
 
-We now introduce the notion of \emph{basis of transitions} and identify the operators than can be expanded in such a basis.
+We introduce a set of basis vectors $\{\ket{\psi(\alpha)}\}$ in the subspace of the empty-states, \emph{i.e.} in the subspace orthogonal to the occupied eigenstates of $\hnot$. 
+The elements of this set satisfy, by definition, the following orthonormality relation: 
+\be\lb{psiAlphaDef1}%{orthonormalityDef1}
+\brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq
+\brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;,
+\ee
+where we have parametrized the basis element through the multi-index $\alpha$, in the sense described in \ref{BasicDef}, since the associated vector can describe both a localized or a 
+de-localized state. The $\op Q_0$ projector as well as the completeness relation can be easily written in function of this basis: 
+\be\lb{psiAlphaQ0}
+\op Q_0 = \sint\dd\alpha\ketbra{\psi(\alpha)}{\psi(\alpha)} \;, \;\; 
+\identity = \sum_p\ketbra{\psi_p}{\psi_p} + \sint\dd\alpha\ketbra{\psi(\alpha)}{\psi(\alpha)} \;.
+\ee
+The dimension $n_\alpha$ of the $\alpha$-basis can be determined by expressing its elements $\{\ket{\psi(\alpha)}\}$ in the same $\mu$-basis used to perform the ground states calculation. 
+%both with and without the explicit time-independent perturbing field. 
+%Denoting with $n_{occ}$ the number of occupied orbitals  
+Since the orthogonality condition with respect to the occupied orbitals imposes $n_{occ}$ constraints we conclude that $n_\alpha=n_\mu-n_{occ}$.
 
-We split the complete
-set of eigenstates of $\hnot$ in two sets. The first one is composed by the eigenvectors of $\hnot$ in the subspace of the occupied orbitals. The second 
-one is composed by the remaining eigenvectors, both in the bound and in the continuum region, and its elements are denoted as $\ket{\psi(\alpha)}$, where $\alpha$ 
-is a multi-index in the sense described in \ref{BasicDef}. The elements of these sets satisfy the following orthonormality relation: 
-\be\lb{orthonormalityDef1}
-\brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq \brket{\psi_p}{\psi_q} = \delta_{pq} \;, \qq
-\brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;.
-\ee
-Obviously, the direct sum of these two sets coincides with the complete set of eigenstates of $\hnot$ and thus 
-constitute a complete basis. 
+% We now introduce the notion of \emph{basis of transitions} and identify the operators than can be expanded in such a basis. 
+% 
+% We split the complete
+% set of eigenstates of $\hnot$ in two sets. The first one is composed by the eigenvectors of $\hnot$ in the subspace of the occupied orbitals. The second 
+% one is composed by the remaining eigenvectors, both in the bound and in the continuum region, and its elements are denoted as $\ket{\psi(\alpha)}$, where $\alpha$ 
+% is a multi-index in the sense described in \ref{BasicDef}. The elements of these sets satisfy the following orthonormality relation: 
+% \be\lb{orthonormalityDef1}
+% \brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq \brket{\psi_p}{\psi_q} = \delta_{pq} \;, \qq
+% \brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;.
+% \ee
+% Obviously, the direct sum of these two sets coincides with the complete set of eigenstates of $\hnot$ and thus 
+% constitute a complete basis.
+
+\subsubsection{Linear response in the basis of transitions}
+
 A generic operator can be decomposed in this basis and its formal expansion contains four distinct contribution of the form $\ketbra{\psi_p}{\psi_q}$, 
@@
 \ee
-The orthonormality conditions \eqref{orthonormalityDef1} imply that:
+The orthonormality conditions \eqref{psiAlphaDef1} imply that:
 \be\lb{transitionOpOrthonormalityDef1}
@@
 
-\subsubsection{Spectral decomposition of the response density in the transitions basis}
+%\subsubsection{Spectral decomposition of the response density in the transitions basis}
 
@@
 \ee
+
+\subsubsection{Spectral decomposition of the response density in the transitions basis}
+
 This formulation of the Liouville equation is the starting point for the derivation of the spectral decomposition of the response density operator
@@
 
-\subsubsection{Excitation operators}
+\subsubsection{Definition of excitation operators}
 
@@
 
-\subsubsection{Schroedinger-like equation for excitonic states}
+\subsubsection{Sternheimer equation for excitonic states. Localization argument revisited}
 

### 2018-01-24 LRDraft.tex
update

@@
 
-The capability of the computational basis to express the results of the linear response can be discussed on the localization argument previously presented. 
+The capability of the computational basis to express the results of the linear response can be analyzed using the localization argument previously discussed. 
 The first step needed to address this problem concerns with the evaluation of the reliability of the $\mu$-basis for $\omega=0$, \emph{i.e.} for a perturbing field that does 
@@
 
-We introduce a set of basis vectors $\{\ket{\psi(\alpha)}\}$ in the subspace of the empty-states, \emph{i.e.} in the subspace orthogonal to the occupied eigenstates of $\hnot$. 
-The elements of this set satisfy, by definition, the following orthonormality relation: 
-\be\lb{psiAlphaDef1}%{orthonormalityDef1}
+We now introduce the notion of $\alpha$-basis, that is a set of orthonormal vectors $\{\ket{\psi(\alpha)}\}$ that form a basis in the subspace of the empty-states, \emph{i.e.} in the subspace 
+orthogonal to the occupied eigenstates of $\hnot$. The elements of this set satisfy, by definition, the following orthonormality relation: 
+\be\lb{psiAlphaDef1}
 \brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq
@@
 \ee
-The dimension $n_\alpha$ of the $\alpha$-basis can be determined by expressing its elements $\{\ket{\psi(\alpha)}\}$ in the same $\mu$-basis used to perform the ground states calculation. 
-%both with and without the explicit time-independent perturbing field. 
-%Denoting with $n_{occ}$ the number of occupied orbitals  
-Since the orthogonality condition with respect to the occupied orbitals imposes $n_{occ}$ constraints we conclude that $n_\alpha=n_\mu-n_{occ}$.
+The $\alpha$-basis, defined through equations \eqref{psiAlphaDef1} and \eqref{psiAlphaQ0}, formally spans an infinite dimensional domain. However, for obvious computational reason it is 
+interesting to express the $\{\ket{\psi(\alpha)}\}$ in the same $\mu$-basis used to perform the ground states calculations. The discretization conditions imposed by the $\mu$-basis reduce 
+the $\{\ket{\psi(\alpha)}\}$ to a finite dimensional set. The dimension $n_\alpha$ of the basis can be computed by subtracting to the $n_\mu$ degrees of freedom the $n_{occ}$ constraints 
+needed to imposes the orthonormality of the $\{\ket{\psi(\alpha)}\}$ to the occupied states, so that $n_\alpha=n_\mu-n_{occ}$.
+
+\vspace{0.4cm}
+\emph{Quality assessment of the reduced $\alpha$-basis}
+\vspace{0.4cm}
+
+When the sampling of the empty state subspace is needed to perform practical calculations in realistic systems the construction of a complete $\alpha$-basis typically turns out to be 
+computationally unaffordable. In these cases it is possible to introduce a \emph{reduced} basis, denoted as $r\alpha$-basis, composed of a subset of dimension $n_{r\alpha}$ of the 
+$\{\ket{\psi(\alpha)}\}$ elements of the complete basis.
+
+The capability of the reduced basis to express the results of the linear response can be evaluated by using the results of a ground state calculation in which the time-independent 
+perturbing field $\op\Phi$ is added to the external potential of $\hnot$. We denote with $\ket{\psi_p^\Phi}$ the occupied eigenstate of the perturbed Hamiltonian and, using the 
+completeness relation of \eqref{psiAlphaQ0}, we can write the following expansion:
+\be\lb{PertPsiExpansion1}
+\ket{\psi_p^{\Phi}} = \sum_q a_{pq}\ket{\psi_q} + \sint\dd\alpha \,a_{p\alpha}\ket{\psi(\alpha)} \;,
+\ee
+where $a_{pq} = \brket{\psi_q}{\psi_p^{\Phi}}$ and $a_{p\alpha} = \brket{\psi(\alpha)}{\psi_p^{\Phi}}$. Equation \eqref{PertPsiExpansion1} holds exactly since the sum over the empty states
+is extended to the complete $\alpha$-basis. Taking the norm of $\ket{\psi_p^\Phi}$ and summing over $p$ provides:
+\be\lb{PertPsiExpansion2}
+n_{occ} = \sum_{pq} |a_{pq}|^2 + \sum_p\sint\dd\alpha\,|a_{p\alpha}|^2 \;,
+\ee
+the two addend of this equation measure the distribution of the total electronic charge of the perturbed system between the occupied and empty subspaces. Furthermore, we can use
+equation \eqref{PertPsiExpansion2} to build an estimator $C(n_{r\alpha})$ of the capability of the $r\alpha$-basis to describe the modification of the ground state density induced 
+by the time-independent perturbation. We define this estimator as follows:
+\be\lb{Cestimator1}
+C(n_{r\alpha}) = 1 - \frac{\sum_p\sum_\alpha^{n_{r\alpha}}|a_{p\alpha}|^2}{n_{occ} - \sum_{pq} |a_{pq}|^2} \;,
+\ee
+$C(n_{r\alpha})$ is by construction a positive function with values between 1, achieved when the sampling of the empty-states subspace is absent and 0, obtained when the reduced basis
+is complete. The normalization adopted in \eqref{Cestimator1} ensures that $C(n_{r\alpha})$ is an intensive estimator, so that its value does not depend on the number of occupied
+orbitals of the system.
 
@@
 
-A generic operator can be decomposed in this basis and its formal expansion contains four distinct contribution of the form $\ketbra{\psi_p}{\psi_q}$, 
-$\ketbra{\psi(\alpha)}{\psi(\beta)}$, $\ketbra{\psi(\alpha)}{\psi_p}$, $\ketbra{\psi_p}{\psi(\alpha)}$. However an inspection of equations \eqref{rhoPrimeOmegaDef1}
-and \eqref{LiouvillianRhopomegaDef3} evidences that the relevant operators in the contest of the linear response are expressed as a commutator with $\dmnot$. 
-For this class of operators the only non vanishing contribution comes from the \emph{transition operators}:
+The defining equation of the linear response can be reformulated using the explicit sampling of the empty states defined above. The fundamental observation on the basis
+of this procedure regards the fact that both the response density operator \eqref{rhoPrimeOmegaDef1} and all the operators appearing in the Liouville equation 
+\eqref{LiouvillianRhopomegaDef3} are expressed as a commutator with $\dmnot$. This observation implies that all the operators $\op O$ appearing in the contest of the linear 
+response satisfy the formal relation:
 \be
-\excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
-\decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;.
+\op O = \dmnot\op O\op Q_0 + \op Q_0\op O\dmnot \;.
 \ee
-The orthonormality conditions \eqref{psiAlphaDef1} imply that:
-\be\lb{transitionOpOrthonormalityDef1}
-\trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
-\trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;,
-\ee
-so that the expansion of a suitable operator $\op O$ in the basis of transitions reads:
+Plugging the operator expression of $\dmnot$ and $\op Q_0$ in terms of basis vector in the occupied and empty subspace provides:
 \be\lb{OperatorTransBasisExpDef1}
@@
 \excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
-\right) \;.
+\right) \;,
 \ee
+where we have defined the \emph{transition operators}:
+\be
+\excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
+\decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;,
+\ee
+that thanks to \eqref{psiAlphaDef1} satisfy the orthonormality conditions:
+\be\lb{transitionOpOrthonormalityDef1}
+\trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
+\trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;.
+\ee
+% \vspace{2cm}
+% A generic operator can be decomposed in this basis and its formal expansion contains four distinct contribution of the form $\ketbra{\psi_p}{\psi_q}$, 
+% $\ketbra{\psi(\alpha)}{\psi(\beta)}$, $\ketbra{\psi(\alpha)}{\psi_p}$, $\ketbra{\psi_p}{\psi(\alpha)}$. However an inspection of equations \eqref{rhoPrimeOmegaDef1}
+% and \eqref{LiouvillianRhopomegaDef3} evidences that the relevant operators in the contest of the linear response are expressed as a commutator with $\dmnot$. 
+% For this class of operators the only non vanishing contribution comes from the \emph{transition operators}:
+% \be
+% \excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
+% \decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;.
+% \ee
+% The orthonormality conditions \eqref{psiAlphaDef1} imply that:
+% \be\lb{transitionOpOrthonormalityDef1}
+% \trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
+% \trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;,
+% \ee
+% so that the expansion of a suitable operator $\op O$ in the basis of transitions reads:
+% \be\lb{OperatorTransBasisExpDef1}
+% \op O = \sum_p\sint \dd \alpha\left(
+% \excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
+% \right) \;.
+% \ee
+Here we are assuming that the complete $\alpha$-basis is used, so the operator expansion in the basis of transition \eqref{OperatorTransBasisExpDef1} is exact. The effect of
+the adoption of a reduced basis will be analyzed when needed. 
 In order to recast this expansion in a simpler expression it turns out to be useful to define the rank-2 row vectors of the transition basis: 
@@
 where the last equality implicitly define the ulterior compact notation of the ``big-shaped'' vectors in which the summed indexes are omitted.  
-In the same fashion it will be also useful for the subsequent analysis to introduce a ``conjugate'' notation, in which the basis operators are expressed
+In the same fashion it will be also useful for the subsequent analysis to introduce a conjugate notation, in which the basis operators are expressed
 as column vector and the coefficients of the expanded operator as row ones, that is: 
@@
 where the flip in the role of $\op e$ and $\op d$ in \eqref{TransitionBasisConjugateDef1} follows from the properties of excitation and decay operators
-under hermitian-conjugate operation. The expansion of a suitable operator in the transition basis using the conjugate description reads: 
+under hermitian-conjugate operation. The expansion of an operator in the transition basis using the conjugate description reads: 
 \be\lb{OperatorTransBasisConjugateExpDef1}
@@
 \ee
-
 %\subsubsection{Spectral decomposition of the response density in the transitions basis}
-
-The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis. Indeed, its r.h.s is explicitly written
-as a commutator with $\dmnot$, while an inspection of the formal definition of the response density and of the Liouville superoperator evidences that
-they both contain a commutator with $\dmnot$. Written in the basis of transitions Liouville equation becomes a linear matrix equation for the rank-2 
-vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
+%The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis. 
+% Indeed, its r.h.s is explicitly written
+% as a commutator with $\dmnot$, while an inspection of the formal definition of the response density and of the Liouville superoperator evidences that
+% they both contain a commutator with $\dmnot$. Written in the basis of transitions Liouville equation becomes a linear matrix equation for the rank-2 
+% vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
+The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis where it becomes a linear matrix equation for the 
+rank-2 vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side, that is:
 \be
@@
 that can be compactly rewritten by using the index-less notation:
+% \be\lb{RhopExcitationTransBasisDef2}
+% \sket{p\alpha}{\dm'(\omega)} = 
+% \sint\dd E \sket{p\alpha}{E}
+% \frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
+% \ee
 \be\lb{RhopExcitationTransBasisDef2}
-\sket{p\alpha}{\dm'(\omega)} = 
-\sint\dd E \sket{p\alpha}{E}
+\dket{\dm'(\omega)} = 
+\sint\dd E \dket{E}
 \frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.

### 2018-01-25 LRDraft.tex
update

@@
 \ee
-so equation \eqref{LiouvilleTransBasisDef1} can be inverted:
+so equation \eqref{LiouvilleTransBasisDef1} can be inverted and we obtain the response density written in basis of transistion, in the form:
+% \be\lb{RhopExcitationTransBasisDef1}
+% \sket{p\alpha}{\dm'(\omega)} = \sint\dd E \sket{p\alpha}{E}
+% \frac{\sum_q \sint \dd \beta\sbra{q\beta}{\tilde E}
+% \sket{q\beta}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
+% \ee
+% that can be compactly rewritten by using the index-less notation:
 \be\lb{RhopExcitationTransBasisDef1}
-\sket{p\alpha}{\dm'(\omega)} = \sint\dd E \sket{p\alpha}{E}
-\frac{\sum_q \sint \dd \beta\sbra{q\beta}{\tilde E}
-\sket{q\beta}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
-\ee
-that can be compactly rewritten by using the index-less notation:
+\sket{p\alpha}{\dm'(\omega)} = 
+\sint\dd E \sket{p\alpha}{E}
+\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
+\ee
 % \be\lb{RhopExcitationTransBasisDef2}
-% \sket{p\alpha}{\dm'(\omega)} = 
-% \sint\dd E \sket{p\alpha}{E}
+% \dket{\dm'(\omega)} = 
+% \sint\dd E \dket{E}
 % \frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
 % \ee
-\be\lb{RhopExcitationTransBasisDef2}
-\dket{\dm'(\omega)} = 
-\sint\dd E \dket{E}
-\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
-\ee
 
@@
 \end{align}
-The introduction of the excitation operators allows to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef2}, that is:
+The introduction of the excitation operators allows to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef1}, that is:
 \be\lb{RhopExcitationDef1}
@@
 \ee
-where the algebraic equivalence between the trace written in \eqref{RhopExcitationDef1} and the numerator of \eqref{RhopExcitationTransBasisDef2}
+where the algebraic equivalence between the trace written in \eqref{RhopExcitationDef1} and the numerator of \eqref{RhopExcitationTransBasisDef1}
 can be easily proved.
 
-\subsubsection{Sternheimer equation for excitonic states. Localization argument revisited}
-
-We introduce the \emph{excitonic states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
+\subsubsection{Excitation expansion of the fluctuation states. A localization argument for the excited states}
+
+We introduce the \emph{excited states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
 coefficients that appears in \eqref{XYcoeffDef1}, that is:
@@
 \ee
+Starting from these equation we can derive the excitation expansion of the fluctuation states. Indeed an inspection of formula \eqref{rhoPrimeFluctuationStateDef1}
+show that fluctuation states can be extracted from the response density operator as follows:
+\be
+\ket{f_p(\omega)} = \dm'(\omega)\ket{\psi_p} \;, \qq
+\bra{f_p(-\omega)} = \bra{\psi_p}\dm'(\omega) \;, \nn
+\ee
+so plugging equations \eqref{ExctitationOperatorsDef2} in the formula \eqref{RhopExcitationDef1} and performing these operations we obtain:
+\be\lb{FluctStateExcitationDef1}
+\ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \ket{\phi^E_p} \;, \qq
+\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} 
+\ee
+
+\subsubsection{Excitation expansion of the linear response functional}
+
+We have that:
+\be
+\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} = \sum_q\sint\dd\beta\, \optr{J}^{p\alpha}_{q\beta}
+\sket{q\beta}{\op\Phi(\omega)} \;\;, \;{\rm with} \;\;
+\optr{J}^{p\alpha}_{q\beta} = \delta_{pq}\delta(\alpha-\beta)\mat{1 & 0 \\ 0 & -1}
+\ee
+and the linear response functional \eqref{LinearResponseFunctDef1} can be written as:
+\be
+{\cal R}_{\op O}(\omega) = 
+\sint\dd E \dbraket{\op O}{E}
+\frac{\dbra{\tilde E}\optr{J}\dket{\op\Phi(\omega)}}{\bbomega-E} \;.
+\ee
+
+%\subsubsection{Sternheimer equation for excitonic states. Localization argument revisited}
+\subsubsection{Sternheimer equation for excited states. Localization argument revisited}
+
+% We introduce the \emph{excitonic states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
+% coefficients that appears in \eqref{XYcoeffDef1}, that is:
+% \begin{align}\lb{ExcitonicStatesDef1}
+% \ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
+% \tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
+% \bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
+% \tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
+% \end{align}
+% Thanks to these definitions we can express the excitation operators as follows:
+% \be\lb{ExctitationOperatorsDef2}
+% \op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
+% \op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
+% \ee
 The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated into a Schroedinger-like equations

### 2018-01-29 LRDraft.tex
update

@@
 \newcommand{\optr}[1]{\check #1}
+\newcommand{\opskew}[1]{{\op {#1}}_{\perp}}
 
@@
 The formal scalar products that express the linear response functional \eqref{LinearResponseFunctDef1} can be evaluated in the same basis introduced above, that is: 
-%For instance the first addend of \eqref{LinearResponseFunctDef2} reads: 
-%\be\lb{LinearResponseFunctDef3}
-%\bra{f_p(-\omega)}\op O\ket{\psi_p} = \sum_\mu \brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} \;.
-%\ee
 \be\lb{LinearResponseFunctDef3}
@@
 
-%On the contrary, the most interesting point of this discussion concerns with the assessment of the 
-%reliable sampling of the fluctuation states through the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$. The problem turns out to be highly is non-trivial 
-%since the behavior of the fluctuation states strongly depends on $\omega$, as will be readily clarified in the next section.
-
-%$\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$ in the domain in which the matrix elements $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian 
-%conjugates) are not vanishing. 
-%The task of the linear response formalism to provide reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
-%expression for the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$ in the domain in which the matrix elements $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian 
-%conjugates) are not vanishing.
-
-% We assume that the ground state problem has been already solved and that the occupied orbitals  introduce a computational basis $\{\ket{\mu}\}$, composed by a \emph{finite}
-% set of functions
-% 
-% Here we are dealing with a linear response problem and
-
-% The quality of the basis can be evaluated by the requirement that the numerical coefficients appearing in the r.h.s of \eqref{LinearResponseFunctDef3} provide a reliable reconstruction 
-% of the formal scalar product.
-
-% Here we are assuming that the ground state properties of the unperturbed system have been computed in the same basis introduced above. This means that the 
-% feature of the basis, that for instance for real space basis are given by the grid spacing and number of points (that determines the dimension simulation box), are chosen so that the 
-% coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, by assuming 
-% that $\op O$ acts as a local operator on the occupied orbitals.
-
-% aggiungere un preambolo a quello che segue. Soluzione usando le equazioni di Sternheimer e approccio con le eccitazioni....
-
 \subsection{Sternheimer equations and localization properties of the fluctuation states}
-%\subsection{Localization argument for the fluctuation states}
 \lb{LocalizationFluctuationStates}
@@
 
-\subsubsection{Criterion for the choice of the computational basis} %underlying
+\subsubsection{Criterion for the choice of the computational basis}
 
@@
 
-%\subsection{Excitation operator and the analytic structure of the linear response}
 \subsection{Linear response \emph{via} the construction of the excitation operators}
@@
 
-%\subsubsection{Definition of the basis of transitions}
 \subsubsection{Explicit sampling of the empty-states subspace}
@@
 
-% We now introduce the notion of \emph{basis of transitions} and identify the operators than can be expanded in such a basis. 
-% 
-% We split the complete
-% set of eigenstates of $\hnot$ in two sets. The first one is composed by the eigenvectors of $\hnot$ in the subspace of the occupied orbitals. The second 
-% one is composed by the remaining eigenvectors, both in the bound and in the continuum region, and its elements are denoted as $\ket{\psi(\alpha)}$, where $\alpha$ 
-% is a multi-index in the sense described in \ref{BasicDef}. The elements of these sets satisfy the following orthonormality relation: 
-% \be\lb{orthonormalityDef1}
-% \brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq \brket{\psi_p}{\psi_q} = \delta_{pq} \;, \qq
-% \brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;.
-% \ee
-% Obviously, the direct sum of these two sets coincides with the complete set of eigenstates of $\hnot$ and thus 
-% constitute a complete basis.
-
 \subsubsection{Linear response in the basis of transitions}
@@
 \ee
-% \vspace{2cm}
-% A generic operator can be decomposed in this basis and its formal expansion contains four distinct contribution of the form $\ketbra{\psi_p}{\psi_q}$, 
-% $\ketbra{\psi(\alpha)}{\psi(\beta)}$, $\ketbra{\psi(\alpha)}{\psi_p}$, $\ketbra{\psi_p}{\psi(\alpha)}$. However an inspection of equations \eqref{rhoPrimeOmegaDef1}
-% and \eqref{LiouvillianRhopomegaDef3} evidences that the relevant operators in the contest of the linear response are expressed as a commutator with $\dmnot$. 
-% For this class of operators the only non vanishing contribution comes from the \emph{transition operators}:
-% \be
-% \excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
-% \decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;.
-% \ee
-% The orthonormality conditions \eqref{psiAlphaDef1} imply that:
-% \be\lb{transitionOpOrthonormalityDef1}
-% \trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
-% \trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;,
-% \ee
-% so that the expansion of a suitable operator $\op O$ in the basis of transitions reads:
-% \be\lb{OperatorTransBasisExpDef1}
-% \op O = \sum_p\sint \dd \alpha\left(
-% \excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
-% \right) \;.
-% \ee
 Here we are assuming that the complete $\alpha$-basis is used, so the operator expansion in the basis of transition \eqref{OperatorTransBasisExpDef1} is exact. The effect of
@@
 \ee
-%\subsubsection{Spectral decomposition of the response density in the transitions basis}
-%The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis. 
-% Indeed, its r.h.s is explicitly written
-% as a commutator with $\dmnot$, while an inspection of the formal definition of the response density and of the Liouville superoperator evidences that
-% they both contain a commutator with $\dmnot$. Written in the basis of transitions Liouville equation becomes a linear matrix equation for the rank-2 
-% vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side:
 The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis where it becomes a linear matrix equation for the 
 rank-2 vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side, that is:
-\be
+\be\lb{LiouvillianRhopomegaDef4}
 \omega\mat{ \trace{\decay{\alpha}{p}\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\dm'(\omega)}} - 
 \mat{ \trace{\decay{\alpha}{p}\Liouv\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\Liouv\dm'(\omega)}} =
-\mat{ \trace{\decay{\alpha}{p}\commutator{\op\Phi(\omega)}{\dmnot}} \\ \trace{\excite{p}{\alpha}\commutator{\op\Phi(\omega)}{\dmnot}}}
-\;.\nn
+\mat{ \trace{\decay{\alpha}{p}\opskew{\Phi}(\omega)} \\ \trace{\excite{p}{\alpha}\opskew{\Phi}(\omega)}}
+\;,\nn
 \ee
-The second addend in the l.h.s can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. Performing this procedure
-we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
+where we have introduced a compact notation to deal with the commutator of on operator with the unperturbed density: 
+\be
+\opskew{O} = \commutator{\op O}{\dmnot}\;.
+\ee
+The second addend in the l.h.s of \eqref{LiouvillianRhopomegaDef4} can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. 
+Performing this procedure we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
 \be\lb{LiouvilleTransBasisDef1}
 \sum_q\sint\dd\beta \left[\omega\delta_q^p\delta(\alpha-\beta)- \optr{L}^{p \alpha}_{q\beta} \right]\sket{q\beta}{\dm'(\omega)} =
-\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} \;.
+\sket{p\alpha}{\opskew{\Phi}(\omega)} \;.
 \ee
@@
 
-\subsubsection{Spectral decomposition of the response density in the transitions basis}
+\subsubsection{Spectral decomposition of the response density in the transitions basis. Definition of excitation operators}
 
-This formulation of the Liouville equation is the starting point for the derivation of the spectral decomposition of the response density operator
-in terms of the eigenvectors if the Liouville operator. 
-The first step in the achievement of this result is provided by the construction of the eigenvectors of the matrix \eqref{LiouvilleMatrixTransBasisDef1}.
-Following the notation previously defined we introduce the rank-2 vectors $\sket{p\alpha}{E}$ and $\sbra{p\alpha}{\tilde E}$ that represent, by definition,
-the right and left eigenvectors $\optr{L}$, respectively, so that:
+The formulation of the Liouville equation in the basis of transitions is the starting point for the derivation of the spectral decomposition of the response density operator
+in terms of the eigenvectors if the Liouville operator. The first step in the achievement of this result is provided by the construction of the eigenvectors of the matrix 
+\eqref{LiouvilleMatrixTransBasisDef1}. Following the notation previously defined we introduce the rank-2 vectors $\sket{p\alpha}{E}$ and $\sbra{p\alpha}{\tilde E}$ that represent, 
+by definition, the right and left eigenvectors $\optr{L}$, respectively, so that:
 \be\lb{LiouvMatrixEigenvectorDef1}
@@
 \ee
-so equation \eqref{LiouvilleTransBasisDef1} can be inverted and we obtain the response density written in basis of transistion, in the form:
-% \be\lb{RhopExcitationTransBasisDef1}
-% \sket{p\alpha}{\dm'(\omega)} = \sint\dd E \sket{p\alpha}{E}
-% \frac{\sum_q \sint \dd \beta\sbra{q\beta}{\tilde E}
-% \sket{q\beta}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
-% \ee
-% that can be compactly rewritten by using the index-less notation:
+so equation \eqref{LiouvilleTransBasisDef1} can be inverted and we obtain the response density written in basis of transition, in the form:
 \be\lb{RhopExcitationTransBasisDef1}
@@
 \sint\dd E \sket{p\alpha}{E}
-\frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
+\frac{\dbraket{\tilde E}{\opskew{\Phi}(\omega)}}{\bbomega-E} \;.
 \ee
-% \be\lb{RhopExcitationTransBasisDef2}
-% \dket{\dm'(\omega)} = 
-% \sint\dd E \dket{E}
-% \frac{\dbraket{\tilde E}{\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;.
-% \ee
-
-\subsubsection{Definition of excitation operators}
-
-We introduce the explicit representation of the eigenvectors op $\optr{L}$:
+%\subsubsection{Definition of excitation operators}
+It is possible to express formula \eqref{RhopExcitationTransBasisDef1} as a true operator equation. First of all we show that the rank-2 vectors $\sket{p\alpha}{E}$ 
+and $\sbra{p\alpha}{\tilde E}$ can be interpreted as the transition basis coefficients of the right and left \emph{eigenstates} of the Liouville superoperator.   
+In order to do so we introduce the explicit representation of the eigenvectors op $\optr{L}$:
 \be\lb{XYcoeffDef1}
@@
 \ee
-and on the basis of these elements we define the \emph{excitation operators}:
+and, on the basis of these elements, we define the \emph{excitation operators}:
 \begin{align}\lb{ExctitationOperatorsDef1}
@@
 \end{align}
-The introduction of the excitation operators allows to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef1}, that is:
+The introduction of the excitation operators allows us to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef1}, that is:
 \be\lb{RhopExcitationDef1}
-\dm'(\omega) = 
+\dm'(\omega) = \dbraket{\cdot}{\dm'(\omega)} =
 \sint\dd E \op E
-\frac{\trace{\op{\tilde E}\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \;,
+\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \;,
 \ee
@@
 can be easily proved.
+
+Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitations $\op E$. The perturbing field 
+determines the relative contribution of each excitation through the weighting coefficients in the numerator of \eqref{RhopExcitationDef1}.
+The fundamental question raised in the present paper, namely the ....reliable assessment of the results of the linear response can thus be reformulated in this language.
 
@@
 \be\lb{FluctStateExcitationDef1}
-\ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} \ket{\phi^E_p} \;, \qq
-\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\commutator{\op\Phi(\omega)}{\dmnot}}}{\bbomega-E} 
-\ee
-
-\subsubsection{Excitation expansion of the linear response functional}
-
-We have that:
-\be
-\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} = \sum_q\sint\dd\beta\, \optr{J}^{p\alpha}_{q\beta}
-\sket{q\beta}{\op\Phi(\omega)} \;\;, \;{\rm with} \;\;
-\optr{J}^{p\alpha}_{q\beta} = \delta_{pq}\delta(\alpha-\beta)\mat{1 & 0 \\ 0 & -1}
-\ee
-and the linear response functional \eqref{LinearResponseFunctDef1} can be written as:
-\be
-{\cal R}_{\op O}(\omega) = 
-\sint\dd E \dbraket{\op O}{E}
-\frac{\dbra{\tilde E}\optr{J}\dket{\op\Phi(\omega)}}{\bbomega-E} \;.
+\ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \ket{\phi^E_p} \;, \qq
+\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} 
 \ee
@@
 
+\subsubsection{Excitation expansion of the linear response functional}
+
+We have that:
+\be
+\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} = \sum_q\sint\dd\beta\, \optr{J}^{p\alpha}_{q\beta}
+\sket{q\beta}{\op\Phi(\omega)} \;\;, \;{\rm with} \;\;
+\optr{J}^{p\alpha}_{q\beta} = \delta_{pq}\delta(\alpha-\beta)\mat{1 & 0 \\ 0 & -1}
+\ee
+and the linear response functional \eqref{LinearResponseFunctDef1} can be written as:
+\be
+{\cal R}_{\op O}(\omega) = 
+\sint\dd E \dbraket{\op O}{E}
+\frac{\dbra{\tilde E}\optr{J}\dket{\op\Phi(\omega)}}{\bbomega-E} \;.
+\ee
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 % \section{Draft of the paper - old notes}
@@
 
-% \section{Introduction}
-% 
-% \subsection{How to add Comments}
-% 
-% Comments can be added to your project by clicking on the comment icon in the toolbar above. % * <john.hammersley@gmail.com> 2016-07-03T09:54:16.211Z:
-% %
-% % Here's an example comment!
-% %
-% To reply to a comment, simply click the reply button in the lower right corner of the comment, and you can close them when you're done.
-% 
-% Comments can also be added to the margins of the compiled PDF using the todo command\todo{Here's a comment in the margin!}, as shown in the example on the right. You can also add inline comments:
-% 
-% \todo[inline, color=green!40]{This is an inline comment.}
-% 
-% \subsection{How to add Tables}
-% 
-% Use the table and tabular commands for basic tables --- see Table~\ref{tab:widgets}, for example. 
-% 
-% \begin{table}
-% \centering
-% \begin{tabular}{l|r}
-% Item & Quantity \\\hline
-% Widgets & 42 \\
-% Gadgets & 13
-% \end{tabular}
-% \caption{\label{tab:widgets}An example table.}
-% \end{table}
-% 
-% \subsection{How to add Citations and a References List}
-% 
-% You can upload a \verb|.bib| file containing your BibTeX entries, created with JabRef; or import your \href{https://www.overleaf.com/blog/184}{Mendeley}, CiteULike or Zotero library as a \verb|.bib| file.
-You can then cite entries from it, like this: \cite{greenwade93}.
-Just remember to specify a bibliography style, as well as the filename of the \verb|.bib|.
-% 
-% You can find a \href{https://www.overleaf.com/help/97-how-to-include-a-bibliography-using-bibtex}{video tutorial here} to learn more about BibTeX.
-% 
-% We hope you find Overleaf useful, and please let us know if you have any feedback using the help menu above --- or use the contact form at \url{https://www.overleaf.com/contact}!
-
 %\bibliographystyle{alpha}

### 2018-01-31 LRDraft.tex
update

@@
 
-Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitations $\op E$. The perturbing field 
-determines the relative contribution of each excitation through the weighting coefficients in the numerator of \eqref{RhopExcitationDef1}.
-The fundamental question raised in the present paper, namely the ....reliable assessment of the results of the linear response can thus be reformulated in this language.
+Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitation operators. Now 
+we are interested in analyzing this restatement of the linear response under the perspective of the main topic of the paper, namely the critical assessment 
+of the results provided by the linear response formalism in a given computational setup. Our interests are mainly twofold. First, to analyze the localization 
+properties of the excitations, in a analogous fashion of what done in section \ref{LocalizationFluctuationStates} for the fluctuation states. Second, to determine 
+the precise nature of the formal sum over excitations written in \eqref{RhopExcitationDef1}, in order to be able to discriminate between the discrete and the 
+continuum sector of the excitation spectrum.
 
@@
 
-We introduce the \emph{excited states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
-coefficients that appears in \eqref{XYcoeffDef1}, that is:
-\begin{align}\lb{ExcitonicStatesDef1}
+%Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitations $\op E$. Now
+We push this formalism a little bit forward and derive the expansion of the fluctuation states \eqref{fluctuationStateDef1} in terms of the \emph{excited states} of the 
+system . Firstly, we introduce excited states, defined via the linear combination of the elements of the $\alpha$-basis with the coefficients that appears in 
+\eqref{XYcoeffDef1}, that is:
+\begin{align}\lb{ExcitedStatesDef1}
 \ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
@@
 \bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
-\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
+\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;,
 \end{align}
-Thanks to these definitions we can express the excitation operators as follows:
-\be\lb{ExctitationOperatorsDef2}
+due to these definitions we can express excitation operators as follows:
+\be\lb{ExcitationOperatorsDef2}
 \op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
@@
 \ee
-Starting from these equation we can derive the excitation expansion of the fluctuation states. Indeed an inspection of formula \eqref{rhoPrimeFluctuationStateDef1}
-show that fluctuation states can be extracted from the response density operator as follows:
+Formulas \eqref{ExcitationOperatorsDef2} provides a clear representation of the physical meaning of excited states \eqref{ExcitedStatesDef1}, as can be seen by applying
+the excitation operators on the occupied eigenstates of the systems:
+\be
+\op E\ket{\psi_p} = \ket{\phi^E_p} \;, \quad \bra{\psi_p} \op E = \bra{\chi^E_p} \;, \quad
+\op {\tilde E}\ket{\psi_p} = \tket{\chi^E_p} \;, \quad \bra{\psi_p} \op {\tilde E} = \tbra{\phi^E_p} \;.
+\nn
+\ee
+The excited states expansion of fluctuation states can be easily derived.  Indeed an inspection of formula \eqref{rhoPrimeFluctuationStateDef1} show that fluctuation 
+states can be extracted from the response density operator as follows:
 \be
@@
 \ee
-so plugging equations \eqref{ExctitationOperatorsDef2} in the formula \eqref{RhopExcitationDef1} and performing these operations we obtain:
+so plugging the expression \eqref{ExcitationOperatorsDef2} inside \eqref{RhopExcitationDef1} and applying the response density to a occupied state provides:
 \be\lb{FluctStateExcitationDef1}
 \ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \ket{\phi^E_p} \;, \qq
-\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} 
+\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \;.
+\ee
+Fluctuation states emerge as a linear superposition of excited states. The $\omega$-dependent coefficients codify the effect of the perturbing field in determining the 
+relative contribution of each addend through the weighting coefficients in the numerators of \eqref{FluctStateExcitationDef1}.
+
+We perform a particular choice of the perturbing field:
+\be
+\op\Phi = \commutator{\op E}{\dmnot} \; \longrightarrow \; \opskew{\Phi} = 
+\commutator{\commutator{\op E}{\dmnot}}{\dmnot} = \op E
 \ee
 
-%\subsubsection{Sternheimer equation for excitonic states. Localization argument revisited}
 \subsubsection{Sternheimer equation for excited states. Localization argument revisited}
 
-% We introduce the \emph{excitonic states} defined via the linear combination of the basis set orthogonal to $\dmnot$ with the
-% coefficients that appears in \eqref{XYcoeffDef1}, that is:
-% \begin{align}\lb{ExcitonicStatesDef1}
-% \ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
-% \tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
-% \bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
-% \tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;.
-% \end{align}
-% Thanks to these definitions we can express the excitation operators as follows:
-% \be\lb{ExctitationOperatorsDef2}
-% \op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
-% \op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
-% \ee
 The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated into a Schroedinger-like equations
@@
 that the $Y$ and $\tilde Y$ coefficients introduced in \eqref{XYcoeffDef1} vanish so that both $\tket{\chi^E_p}$ and $\bra{\chi^E_p}$ do not
-contribute to the excitation operators \eqref{ExctitationOperatorsDef2}. The eigenvalue operator equation for $\op E$ reduces to:
+contribute to the excitation operators \eqref{ExcitationOperatorsDef2}. The eigenvalue operator equation for $\op E$ reduces to:
 \be
@@
 \end{align}
-We observe that the coupling kernel behaves as a (non-local) potential that depends on both the $X_{E}^{p \alpha}$ and $Y_{E}^{p \alpha}$ coefficients of \eqref{ExcitonicStatesDef1}
+We observe that the coupling kernel behaves as a (non-local) potential that depends on both the $X_{E}^{p \alpha}$ and $Y_{E}^{p \alpha}$ coefficients of \eqref{ExcitedStatesDef1}
 thus introducing a coupling between the $\phi$ and $\chi$ states.

### 2018-02-15 LRDraft.tex
update
Update on Overleaf.

@@
 \section{Reboot with recent considerations}
+Given a approximate eigenvector $\ket{\psi}$ we approximate its energy by $E=\bra{\psi} \op H \ket{\psi}$.
+This energy is an approximation of the true eigenvalue.
+We assume that the wavefunction gradient $\ket{g(E)}\equiv \left(\op H -E\right)\ket{\psi}$ indicates the distance from the solution of the Schroedinger Equation (SE) in a complete basis set.
+By imposing the solution of the SE for a better approximation of the wavefunction $\psi + \Delta \psi$
+we should obtain, self-consistently:
+\begin{align}
+\left(E -\op H \right)\ket{\Delta \psi} &= \ket{g(E+ \Delta E)}\;,\\
+\Delta E &= 2 \bra{\psi} \op H \ket{\Delta \psi}\;.
+\end{align}
+From the expression of $\Delta \psi$ we can recalculate another approximation for the wavefunction and, correspondingly, for the eigenvalue.
+By definition, the exact solution is reached only when $\ket{g}=0$, which implies that the norm of $\Delta \psi$ must decrease during the perturbative process.
+
+\textbf{Theorem:} Only the eigenstates with negative energy might have a finite-size correction that can be expressed perturbatvely.
+
+\textbf{Proof}: 
+If we apply this process to estimate the finite-size correction to a numerical solution of the Schroedinger equation, as the eigenvalue should converge faster than the eigenvector, we conclude that the gradient $g$ becomes nonzero only in regions that  should be located far from the potential region.
+If this is true, at the next iteration the gradient would become $g + \op H \Delta \psi + \mathcal{O}(\Delta E)$.
+Therefore, for having a convergent perturbative process, also the ket $\ket{\Delta \psi}$ solution of the above equation should be localized far from the support of the potential.
+In other terms, the relation between $g$ and $\Delta \psi$ should be local in space.
+
+The Lippmann-Schwinger relation defines the Dyson series of the resolvent of the Hamiltonian in terms of the Helmholtz Green's function $\op G_0(E)$:
+\be 
+\op G(E) \equiv (E- \op H)^{-1} = \op G_0(E) + \op G_0(E) \op V \op G(E)\;.
+\ee
+We have therefore 
+\be 
+\ket{\Delta \psi} = 
+\sum_{p=0}^\infty \op G_0(E) 
+\left(\op V \op G_0(E)\right)^p \ket{g}\;.
+\ee
+For the properties of the Helmholtz equation, locality in space of $\Delta \psi$ might only be recovered for negative energy values.
+This equation proves that for positive values of the energy the finite-size corrections will \emph{always} provide fully delocalized corrections: it would be impossible to observe a convergence of the wavefunction in the interior region by simply increasing the size of the simulation domain.
+If the value of the approximate energy does not become negative during the perturbative process, 
+a modification of the domain boundaries will impact the wavefunction in the entire simulation region.
+In this case, convergence might only be achieved uniformly and there is no guarantee that a larger domain will provide similar energies.
+$\square$
 \begin{itemize}
@@
 \be\lb{fluctuationStateIntEq2}
-f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \;.
+f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \simeq 
+e^{-\frac{\eta}{2}|\r|} \frac{e^{\ii \sqrt{k^2_p(\omega)} |\r|}}{|\r|} \;.
 \ee
@@
 \ee
+...to be continued...we have to state precisely the time-dependence of $\hone{t}$...
 

### 2018-03-05 LRDraft.tex
Update on Overleaf.

@@
 \newcommand{\eps}{\epsilon}
-\newcommand{\bbomega}{{\bar{\bar\omega}}}
+\newcommand{\bomega}{\bar\omega}
+\newcommand{\bbomega}{\bar{\bomega}}
 \newcommand{\ii}{\mathrm{i}}
@@
 On the Localization of the Linear-Response excitations in Open Systems}
+\author[2]{Marco D'Alessandro}
 \author[1]{Luigi Genovese}
-\author[2]{Marco D'Alessandro}
 \affil[1]{Laboratoire de Simulation Atomistique (LSim), SP2M, INAC, CEA-UJF, 17 Av. des Martyrs,
@@
 
+\section{On the analytic structure linear response susceptibility}
+\begin{itemize}
+\item People want converged quantities related to systems properties. How to obtain them?
+\item FS naturally emerges as the minimal building block for the evaluation of physical quantities in LR formalism . For a given Phi, I need to express O and FS.
+\item We imposing a pertubation of the system, it is easay to see that the FS are also  functional of the Perturbation potential applied on the response function of the system.
+FS = R Phi for the same omega.
+\item the fundamental objet is therefore R.
+\item[$\Rightarrow$] EoM of FS evidence two distinct regimes of \emph{locality}; 
+below threshold FS are localized quantities and can be expressed explicitly;
+above threshold they behave as plane waves and the only physical meaning is inside the scalar product, which requires bith  the evaluation of $\op \Phi$ and $\op O$.
+\item this fact reflect the physical effect that a low-energy excitation is not able to ionize the molecule.
+\item As by hypothesis we are much more capable to express localized quantities it is therefore likely that it easier to converge LR quantities in the infrared regime.
+Let us show why this fact happens.
+\item If I have the correct DoF to express the FS as a genuinely localized quantity I have the LR for \emph{any} observable $\op O$. This fact would not be possible above threshold.
+\item The capability of expressing the FS below threshold reflects the capability of expressing the LR kernel. Therefore \emph{the same} localization argument should be reformulated in term of R
+\item Let us discuss how this observations are related to the analytic structure of the LR.
+\item FS are explicitly dependent on the perturbation potential. The LR would be (formally) completely defined in terms of free oscillation of the system (eigenoperators of the Liouvillian).
+\item The FS can be also expressed as a sum over excitations
+%\item As the imaginary part of the FS should be also localized below threshold this implies that also the excitations are localized quantities when E is below threshold
+\item [$\Rightarrow$]Such sum over the excitation must be such as to express a localized quantity below threshold, (at least when applied to localized potentials).
+\item[$\Rightarrow$] In addition, also the excited states undergo two different regimes of locality, but this time their EoM implies \emph{also} conditions on the discreteness of the energies.
+Above threshold the excitations belong to a \emph{continuum}
+\item Such continuum of excitation is formed by a set of ldelocalized excitations that are nontheless important to express the localized infomration below threshold.
+\item However this implies that \emph{also} the analytic structure of the LR undergo two different regimes.
+%\item The absorption spectra, which are only dependent by the imaginary part of R, are therefore well expressed only for discrete energies
+\item[$\Rightarrow$] We might therefore show that below threshold the analytic structure of the LR is given in terms of localized quantities that are at discrete, observable and physically meaningful energies.
+\item[$\Rightarrow$] The spectral function of the LR, which would be written as a sum of delta, only converges when the ecxitation are dense enough in the continuum sector, wheras convergence in the infrared regimes only requires identification of the discrete excitation energies
+\item There are multiple thresholds, one for any QP energy. The first threshold is the ionization potential.
+\item[$\Rightarrow$] in a computational setup that is able to capture localized information, the analytic structure of the LR can be expressed with arbitrary good convergence \textbf{only} below the first threshold, as localized information it is more easily expressed in computational treatments that are initially performed for the Ground state.
+\item For this reason it is easier to have convergence in the optical properties for energy sector below the first threshold
+\item Above each of the threshold (therefore after the first), there is a continuum of delocalized excited states that have to be expressed if we want to abandon the representation in terms of scalar product between FS and O.
+\item Such representation in terms of O, FS and Phi is still the most convenient to have accurate evaluation of the LR above threshold.
+
+\end{itemize}
 \section{Reboot with recent considerations}
+\subsection{Perturbative approach to finite-size corrections}
 Given a approximate eigenvector $\ket{\psi}$ we approximate its energy by $E=\bra{\psi} \op H \ket{\psi}$.
@@
 \ee
+
+\subsection{Spectral representation of Susceptibility Functional}
+The Liouvillian expressed the excitation modes of the system $\op E$.
+A free excitation of the system might therefore be expressed by the operator $\op E$.
+The scalar product between the perturbed state and the excitation $\op E$ is provided by the quantity
+\be
+a_{\Phi \rightarrow E} = \sum_p \bra{\phi_p^E} \op \Phi \ket{\psi_p} = \trace{\op{\tilde E} \op \Phi}
+\ee
+the rate of probability of being into an excited state after the application of a perturbation $\op \Phi$ is therefore
+\begin{multline}
+\sint \dd E\Gamma_{\op\Phi, \op E}(t) = \sint \dd E a_{\Phi \rightarrow E} \cdot a_{E \rightarrow \Phi} = \\=  \sint \dd E \trace{\op \Phi E } \trace{ \op{\tilde E} \op \Phi} \frac{\sin(E t)}{E}
+\simeq \int \dd \omega' \sin(\omega' t) \trace{\op \Phi \sop R(\omega')\op \Phi}
+\end{multline}
+To calculate this rate of probability we need the spectral function of $\sop R(\omega)$.
+
+Taking into account that, for the Kramers-Kronig relation
+\be
+\sop R(\omega)=1+ \frac{1}{\pi}\mathcal P \int \dd \omega' \frac{B(\omega')}{\omega -\omega'} + \ii B(\omega)
+\ee
+where $B$ is a real operator, the Susceptibility functional might be expressed in two ways:
+\begin{itemize}
+\item By considering the eigenvectors of the Liouvillian superoperator:
+\be
+\sop R(\omega) = \sint \dd E \op E \frac{\trace{\op{\tilde E}_\perp \cdot }}{\bbomega -E}
+\ee
+which would lead to the condition
+\begin{align}
+\left(\hnot-\eps_p\right)\ket{\phi^E_p} +\sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ket{\psi(\alpha)} &= E\ket{\phi^E_p} \;,\nn \\
+\bra{\chi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\excite{p}{\alpha}; \op E\right] &= -E\bra{\chi^E_p} \;.
+\end{align}
+In this case we are identifying 
+\be
+B(\omega) = \sint \dd E \op E \trace{\op{\tilde E}_\perp \cdot } \delta(\omega - E)
+\ee
+Such conditions should bring us to the observation:
+\begin{itemize}
+\item The representation in terms of excitation is related to the linear response properties of the 
+system
+\item Excitation energies below threshold are \emph{discrete};
+\item Excitation states above threshold belong to a \emph{continuum} of states and are \emph{delocalized} in space, and they collapse with the incresing of the computational domain;
+\item The absorbtion spectra are therefore expressed in two different regimes: below the ionization threshold, where the excitation are well-defined quantities (discrete energies, localized excited states), and the high-energy range where the only well defined quantity is the spectral function.
+In this regime a \emph{single} excitation lose its physical significance as they belong to a continuum (we are above the ionization energy for a optical excitation)  and are simply \emph{tools} 
+for expressing the action of $\sop B(\omega)$
+\item By watching naively at this representation it seems that to have a converged real part of the polarizability we should have a converged spectral function in a large part of the high energy sector (above threshold).
+\item When expressing the spectrum in terms of excited states above threshold we approximate the spectral function in terms of a sum of dirac deltas centered at the \emph{single}, ``unphysical'' excitation; we should therefore express a \textbf{density} of excitations which is sufficiently converged, in terms of the smearing function that is used for the expression of the spectral function.
+\item This is more and more difficult to obtain for  increasing of the energy, as the sizes of the computationa domain should be large to ensure a converged density of excitation, which would imply a collapse of the continuum of excited states as written in the above equations.
+\end{itemize}
+\item By considering the fluctuation state
+via the equation
+\be
+{\cal R}_{\op O}(\omega) = 
+2 \sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
+\ee
+% {\cal R}_{\op O}(\omega) = 
+%  \ii \sum_p\left(\bra{\psi_p}\op A(\omega)\op Q_0\op O\ket{\psi_p} - \bra{\psi_p}\op O\op Q_0\op A(\omega)\ket{\psi_p}\right) =\\ =
+% \ii \sum_p\left(\bra{\psi_p} \op \Phi(\omega) \op G_0^-(\epsilon_p - \bomega)  \op Q_0 \op O\ket{\psi_p} - 
+% \bra{\psi_p}\op O\op Q_0\op G_0^+(\bomega + \epsilon_p) \op \Phi(\omega) \ket{\psi_p}\right) = \\ 
+% % \ii \int \dd \omega' \sum_p\left(\frac{\bra{\psi_p} \op \Phi(\omega) \op B(\omega')  \op Q_0 \op O\ket{\psi_p}}{\epsilon_p - \bbomega - \omega'} - 
+% % \frac{
+% % \bra{\psi_p}\op O\op Q_0\op B(\omega') \op \Phi(\omega) \ket{\psi_p}}
+% % {\epsilon_p + \bbomega - \omega'}\right) = \\ 
+% \;.
+that will lead to the condition
+\be
+\left(\bbomega+\eps_p -\op T\right)\ket{f_p(\omega)} = \op V\ket{f_p(\omega)} + \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;.
+\ee
+which implies
+\begin{itemize}
+\item Also the fluctuation states and therefore \emph{both} the real and imaginary part of the linear susceptibility may be localized \emph{only} below the energy threshold.
+\item By expressing the FS in term of sum of excitation we obtain \emph{localized wavepackets} written in terms of both localized and delocalized excitation
+\be
+\ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \ket{\phi^E_p} = \sum_\alpha \braket{\alpha|f_p(\omega)} \ket{\alpha}
+\ee
+\item The description provided by a FS written in a given computational basis is \emph{strictly} equivalent to the one provided by its decomposition in the maximal set of computational excitation.
+\item it seems that \emph{either} I have the description in temrs of excitations, which would prevent to assess the qaulity of the real part of the susceptivity, or I have the fluctuation states that provide correct susceptivity
+
+\item Below threashold we therefore have the possiblity to express efficiently the fluctuation states instead of the high energy excitations, which would have been needed to express its real part.
+This would provide a converged and physically meaningful susceptivity (both real and imaginary part) even though the spectral function in the high energy sector will not be converged.
+It appears convenient to write:
+\be
+\sop R(\omega)= \sop C(\omega) - \frac{\ii}{\pi}\mathcal P \int \dd \omega' \frac{\sop C(\omega')-1}{\omega -\omega'}
+\ee
+for the range of $\omega$ for which we are if we are able to write
+\be
+\sop C(\omega) = \mathcal P \sint \dd E   \op E \trace{\op{\tilde E}_\perp \cdot } \frac{1}{\omega -E }\;,
+\ee
+then we would be sure that the spectral function of the susceptivity is correct for energies that belong to the same range, as in this regime the excitation energies are discrete and observable.
+\item The real part of the linear susceptibility has a localized behaviour even though it might be expressed as an integral of delaoclized quantities
+\item If we are interested in expressing quantities which are below ionization threshold we might optimize the computational degrees of freedom by using the corresponding fluctuation states as reference objects.
+In this case the resultin excitation will be i) such as to produce the desired behaviour on the referecne fluctuation state (example of static polarizability) ii) have a reasonable behaviour for the excitations close to the optimization energy range (observable character of the excited energies).
+The computational degrees of freedom are likely to express with good quality excitations close to the target energy.
+\item Such minimal basis approach is valid only for energies below threshold: we cannot assess the quality of the fluctuation state above 
+\end{itemize}
+
+\end{itemize}
+
+\subsection{Computational realization of Eq.~\eqref{LinearResponseFunctDef2}}
 Let us further investigate this formula pointing out some of the  computational aspects needed to explicitly perform the scalar products appearing in 

### 2018-03-05 main.tex
Update on Overleaf.

--- 2018-01-31 LRDraft.tex
@@
 
-\title{Critical assessment of Linear-Response Excitations in Molecular system\\
-or \\
-On the Localization of the Linear-Response excitations in Open Systems}
+\title{On the analytic structure of linear response susceptibility in open systems}
+\author[2]{Marco D'Alessandro}
 \author[1]{Luigi Genovese}
-\author[2]{Marco D'Alessandro}
 \affil[1]{Laboratoire de Simulation Atomistique (LSim), SP2M, INAC, CEA-UJF, 17 Av. des Martyrs,
@@
 
-\section{Reboot with recent considerations}
-\begin{itemize}
-\item Write the excitations as the eigenstates of the Liouvillian:
-\begin{itemize}
-\item The Casida Matrix provides the eigenvectors in the basis of the unperturbed transitions
-\item From the Casida eigenproblem we 
-get the poles of the dynamical polarizability and we may reconstruct the perturbed wavefunctions
-\item Lot of solution in state of 
-the art to express \emph{the same information}, still by avoiding the explicit diagonalization of the problem
-\end{itemize}
-\item Such transitions might also be written in terms of the solutions of the eigenproblem for the perturbed hamiltonian
-\begin{itemize}
-\item There are therefore excitations which correspond to localized solutions of the above eigenproblems
-\item There is a \emph{energy threshold} above which the eigenfunction associated \emph{cannot be anymore} localized
-\end{itemize}
-\item Below threshold, the eigenfunction are localized and the energy values are \emph{observable} quantities (there is a convergence in terms of the simulation parameters)
-\begin{itemize}
-\item Casida treatments for different
-basis sets exhibit convergence of the low-energy excitations
-\item Still, even for such localized excitations, non-trivial dependence on the empty states on some of excitation value is observed (energies converge relatively slowly wrt $N_\alpha$)
-\item The locality of the excitation can be \emph{measured}
-{\bf NEW idea for the SoB: why not to consider}
-$$
-\int \mathrm d \mathbf r
-\rho(\mathbf r) |\phi_p^E(\mathbf r)|^2
-$$
-or similar quantities, that are independent on the number of empty and  bound states
-\item Localized Excitation are the  only one with an observable character (this is surely already known)
-\item The spectrum of the Liouvillian in this regime is a \emph{discrete} spectrum; the excitation energies are \emph{poles} of the dynamical polarizability
-nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very interesting remark in my opinion: the physics of the optical excitation is observable 
-(and therefore localized) only if the energies are not higher than the energy needed to ionize the system. After this point, it seems normal to me that the ``optical'' excitations with 
-real value of the energy are not  meant to be observable anymore.
-\item Optical Excitations below threshold have therefore a (very) long lifetime (poles on the real axis), and they contribute to the analytic structure of the dynamical polarizability.
-\end{itemize}
-\item Above this threshold the energies have a strong dependence on the computational treatment
-\begin{itemize}
-\item The high-energy part of the 
-spectrum does not converge with the 
-boundary conditions, even though they converge wrt the empty states (established techniques \emph{do not solve} such problem)
-\item This is \emph{not} a problem that is related to the continuum collapse of the empty states.
-\item They belong to the continuum of  the Liouvillian $\rightarrow$ they collapse, or depend strongly on the basis set adopted
-\item They cannot be considered separately \emph{even when they are expressed in localized basis} as 
-their shape is dependent on the treatment
-\item They energies are not \emph{true} poles of the dynamical polarizability (the spectra converge only by superposition of deltas)
-\end{itemize}
-\item Optical excitation above Ionization threshold are therefore observable \emph{only} if they possess a lifetime (the peaks of the spectrum have a well-defined broadening). 
-In this way they might be expressed in terms of resonant wavefunctions
-\end{itemize}
-
-\section{General theoretical setup}
-
-\subsection{Basic definitions}\lb{BasicDef}
-
-We consider a generic one-body quantum mechanical problem described by the hermitian Hamiltonian $\hnot$  written in terms of the standard 
-kinetic operator $\op T$ plus a one-body potential $\op V$, which we assume to be completely general, i.e. possibly nonlocal.
-We consider open systems, so that $\hnot$ is defined on $\mathbb L_2(\mathbb R_3)$ and the basis of its eigenfunctions spans this 
-functional space. Therefore, together with the discrete (bound) part of its spectrum $\eps_b$, the Hamiltonian may have an essential spectrum 
-$\eps(c)$, parametrized by the continuum label $c$.
-
-A generic state $\ket{f} \in \mathbb L_2(\mathbb R_3)$ can be expanded in the basis of the eigenstates of $\hnot$, that is:
-\be\lb{ketBasisExpDef1}
-\ket{f} = \sum_b f_b \ket{\psi_b} + \int \dd c f(c) \ket{\psi(c)}  = 
-\sint \dd s f(s) \ket{\psi(s)} \;,
-\ee
-where we have introduced the compact multi-index $s$ that collect both the discrete and continuum part of the spectrum of $\hnot$.
-The normalization of the basis can be chosen so that the standard orthonormality condition holds, that is: 
-\be
-\brket{\psi(s)}{\psi(s')} = \delta(s-s') \;,
-\ee
-and the completeness condition is written as:
-\be\lb{completenessH0basis1}
-\identity = \sint \dd s \ketbra{\psi(s)}{\psi(s)} = \sum_{b} \ketbra{\psi_b}{\psi_b} + \int \dd c \ketbra{\psi(c)}{\psi(c)} \;. 
-\ee
-Thanks to this condition the coefficients of the expansion \eqref{ketBasisExpDef1} can be expressed via a scalar products, namely $f_{b} = 
-\brket{\psi_b}{f}$ and $f(c) = \brket{\psi(c)}{f}$.
-
-\subsection{Time evolution of states in the linear response regime}
-
-We discuss the time evolution of a generic state vector in the case in which a hermitian time dependent perturbation $\hone{t}$ is added to $\hnot$. 
-To achieve this task we have to solve the time dependent Schroedinger equation supplied by the knowledge of the state at the ``initial'' time $t_0$.
-We seek for a solution of the form:
-\be\lb{ketTimeEvol1}
-\ket{\psi(t_{0},t)} = e^{-\ii \hnot t} \op{U}_{I}(t,t_0) e^{\ii \hnot t_0}\ket{\psi_0} \; . 
-\ee
-where $\op{U}_I(t,t_0)$ is the time evolution operator induced by $\hone{}$ that satisfies the ``initial'' time condition $\op{U}_I(t_0,t_0)=1$. 
-Plugging the expression \eqref{ketTimeEvol1} in the Schroedinger equation we obtain a differential equation for $\op{U}_I$ that can be solved 
-iteratively as a power series in $\hone{}$. Limiting to the linear order provides:
-\be \lb{UiLinOrderSol1}
-\op{U}_I(t,t_0) = \identity - \ii \intdef{t_0}{t}{t'} e^{\ii \hnot t'} \hone{t'} e^{-\ii \hnot t'} \; .
-\ee
-So, at the first order in $\hone{}$ equation \eqref{ketTimeEvol1} can thus be written as:
-\be \lb{ketTimeEvol2} 
-\ket{\psi(t_{0},t)} = \left( \op{U}_0(t-t_0) - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \hone{t'} 
-\op{U}_0(t'-t_0) \right)\ket{\psi_0} \; ,
-\ee
-were we have defined the time evolution operator of the unperturbed Hamiltonian by
-\be
-\op{U}_0(t-t_0)\equiv e^{-\ii \hnot(t -t_0)} \;.
-\ee
-The time evolution of left vectors can be derived in the same way. We can express the temporal evolution of the left 
-vectors in the form:
-\be \lb{braTimeEvol1}
-\bra{\psi(t_{0},t)} = \bra{\psi_0} e^{-\ii \hnot t_0} \op{U}_{I}(t_0,t) e^{\ii \hnot t} \;,
-\ee
-plugging this equation in the conjugate Schroedinger equation and pursuing the same procedure defined above, we obtain the 
-linear order expression of time evolution of left vectors:
-\be\lb{leftVectTimeEvol2}
-\bra{\psi(t_{0},t)} = \bra{\psi_0} \left( \op{U}_0(t_0-t) + \ii \intdef{t_0}{t}{t'} \op{U}_0(t_0-t') 
-\hone{t'} \op{U}_0(t'-t) \right) 
-\ee
-It is immediate to check that, in order to preserve the norm vectors during the time evolution, it is sufficient that $\op{U}_I$ 
-possesses the  semi-group structure $\op{U}_I(t_2,t_1) \op{U}_I(t_1,t_0) = \op{U}_I(t_2,t_0)$. An inspection of \eqref{UiLinOrderSol1}
-evidences that this condition is satisfied in the linear response regime.
-
-\subsubsection{Time evolution of stationary states. Adiabatic limit vs finite time switch-on procedure}
-
-We are interested in determining the time evolution of an eigenstate of $\hnot$ under the action of the perturbation $\hone{t}$ in the linear 
-response regime. A proper statement of the problem requires the specification of the way in which the perturbation is switched on.
-Possible choice of the switching on protocol are, for instance, the \emph{adiabatic limit} and the \emph{sudden limit} protocols. In the first
-case the perturbation is switched on at $t_0=-\infty$, but the intrinsic time structure of $\hone{}$ is modified by the damping function 
-$e^{-\eta_a |t|}$. In the second one the perturbation is abruptly switched on at the finite time $t_0$, so that the time structure of
-$\hone{}$ is multiplied times the $\theta$-function $\theta(t-t_0)$.
-
-Starting from the generic time evolution equation \eqref{ketTimeEvol2} and choosing the initial condition in the form 
-$\ket{\psi_0} = e^{-\\i \eps_b t_0}\ket{\psi_b}$, we can write the time evolution of the generic $\ket{\psi_b}$ eigenvector of $\hnot$ as:
-\be \lb{ketTimeEvol3} 
-\ket{\psi_b(t)} = e^{-\ii \eps_b t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_b} \; ,
-\ee
-where we have introduced the \emph{perturbing field operators}: 
-\be
-\op\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
-\op\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
-\ee
-that codify the effective of the perturbing Hamiltonian in the specific switch-on procedure. Making usage of elementary properties of $\theta$ functions allows us
-to rewrite the former time integral as:
-\be\lb{AopDef1}
-\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{+}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}^{-}_0(t'-t) \;,
-\ee
-so that the effect of the switch-on protocol are completely reabsorbed in the perturbing field. In the subsequent analysis we will omit the apex in the fields $\op\Phi$, 
-unless explicitly needed, to keep notations as simple as possible. Thanks to this definition we can express the time evolution of the eigenvectors of $\hnot$ in the 
-compact form:
-\be\lb{ketBraTimeEvol1}
-\ket{\psi_b(t)} = e^{-\ii \eps_b t}\left( \identity - \ii \op A(t)  \right)\ket{\psi_b} \; , \qq 
-\bra{\psi_b(t)} = \bra{\psi_b} \left( \identity + \ii \op A(t)  \right) e^{\ii \eps_b t} \; .
-\ee
-
-\subsection{Linear response on the density operator. Liouville equation in the time domain}
-
-We introduce the \emph{density operator} defined as the sum of the one-particle densities of all the states with energy lower than the \emph{chemical potential} 
-(Fermi energy):
-\be\label{rhodef1}
-\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
-\ee
-where the index $p$ labels the occupied state, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi energy.
-Clearly $\dmnot$ commutes with $\hnot$ and in the unperturbed case is a time-independent operator. When the perturbation is switched the system starts to evolve
-and we indicate with $\dm(t)$ the modified density of the perturbed system. We introduce the shorthand notation:
-\be\lb{rhodef2}
-\dm(t)  =  \dmnot + \dm'(t)\;,
-\ee
-where $\dm'(t)$ is called the \emph{response density operator} and represents the time dependent modification of the ground state density induced by the perturbation.
-Here we are assuming that the highest occupied energy level and the lowest unoccupied one will never intersect during the time evolution. Thanks to this condition, the 
-linear response regime the expression of $\dm'(t)$ can be readily derived using equations \eqref{ketBraTimeEvol1} and reads:  
-\be\lb{rhoTimeEvolutionDef3}
-\dm'(t) = \ii \commutator{\dmnot}{\op A(t)} \;.
-\ee
-The equation of motion (Liouville equation) for $\dm'$ is obtained by performing the time derivative of the previous equation. The derivative of $\op A(t)$ can be 
-computed starting from its definition and reads:
-\be
-\d_t\op A(t) = \op\Phi(t) -\ii \commutator{\hnot}{\op A(t)} \nn \;,
-\ee
-and using the Jacobi identity we have:
-\be\lb{LiouvilleRhoDef1}
-\ii \d_t \dm'(t) = \commutator{\op\Phi(t)}{\dmnot} + \ii\commutator{\hnot}{\commutator{\dmnot}{\op A(t)}} = 
-\commutator{\op\Phi(t)}{\dmnot} + \commutator{\hnot}{\dm'(t)} \;.
-\ee
-It is useful to introduce the \emph{Liouvillian} superoperator:
-\be\lb{L0sopDef1}
-\Liouvnot \equiv \commutator{\hnot}{\cdot} \;,
-\ee
-so that the Liouville equation can be written as:
-\be\lb{LiouvilleRhoDef2}
-\ii \d_t \dm'(t) = \Liouvnot \dm'(t) + \commutator{\op\Phi(t)}{\dmnot} \;.
-\ee
-
-\subsection{Self-consistent Hamiltonians. Generalized Liouville operator}
-
-Let us extend the the former analysis to self-consistent systems, \emph{i.e.} to the case in which the unperturbed Hamiltonian is itself a function of the density.
-In this case the perturbing field $\op\Phi$ has also the effect of adding a further perturbation operator to the perturbing Hamiltonian. In the linear response framework, 
-this latter quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel (evaluated at $\dm=\dmnot$) times the value of the
-induced density modification, that is:
-\be\label{Vptspacedef1}
-\op V'(t)= 
-\int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
-\trace{\dm'(t) \ket{\r} \bra{\r'}} \;.
-\ee
-The Liouville equation for self-consistent systems can be written by adding the contribution of $\op V'$ to $\op\Phi$ in \eqref{LiouvilleRhoDef2}. 
-It reads:
-\be\lb{LiouvilleRhoSelfDef1}
-\ii \d_t \dm'(t) = \Liouvnot \dm'(t) + \commutator{\op V'(t)}{\dmnot} + \commutator{\op \Phi(t)}{\dmnot} \;.
-\ee
-We point out that the response density operator obeys a self-consistent equation, since the  induced perturbing field $\op V'$ is itself a function of $\dm'$. 
-It is possible to formally recast \eqref{LiouvilleRhoSelfDef1} in the same form of \eqref{LiouvilleRhoDef2} by introducing the \emph{coupling}
-superoperator:
-\be\lb{couplingSopDef1}
-\coupl = 
-\int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
-\trace{\cdot \ket{\r} \bra{\r'}} \;,
-\ee
-in this way the first commutator in \eqref{LiouvilleRhoSelfDef1} can be written as the formal action of the coupling superoperator to $\dm'$ and \eqref{LiouvilleRhoSelfDef1}
-can be written as:
-\be\lb{LiouvilleRhoSelfDef2}
-\ii \d_t \dm'(t) = \Liouv \dm'(t) + \commutator{\op \Phi(t)}{\dmnot} \;, \qq
-\Liouv = \Liouvnot + \coupl \;.
-\ee
-
-\subsection{Formulation in the frequency domain}
-
-We reformulate the Liouville equation \eqref{LiouvilleRhoSelfDef2} in the frequency domain. In order to achieve this task it is
-preferable to directly compute the action of the Liouville operator on the Fourier transform of the response density, since in this
-way some subtleties that concerns the analytic structure in the $\omega$ complex plane can be properly taken into account.
-We first define the response density in the frequency domain that, staring from \eqref{rhoTimeEvolutionDef3}, is given by:
-\be\lb{rhoPrimeOmegaDef1}
-\dm'(\omega) \equiv \intover{t} e^{\ii \omega t} \dm'(t)
-= \ii \commutator{\dmnot}{\op A(\omega)} \;,
-\ee
-where $\op A(\omega)$ is The Fourier transform of \eqref{AopDef1} and reads:
-\be \lb{AomegaDef1}
-\op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
-\op G_0^+(\omega') \op \Phi(\omega) \op G_0^-(\omega'-\omega)\;.
-\ee
-The action of $\Liouvnot$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
-\be\lb{LiouvillianRhopomegaDef1}
-\Liouvnot \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
-\ii \commutator{\dmnot}{\commutator{\hnot}{\op A(\omega)}} \;,
-\ee
-and the commutator between the unperturbed Hamiltonian and $\op A(\omega)$ can be directly computed starting from \eqref{AomegaDef1}: 
-\be
-\commutator{\hnot }{\op A(\omega)} = \bbomega \op A(\omega) - \ii \op \Phi(\omega)\;, \nn
-\ee
-where $\bbomega \equiv \omega + 2\ii\eta$, so that:
-\be\lb{LiouvillianRhopomegaDef2}
-\Liouvnot \dm'(\omega) =  \bbomega\dm'(\omega) + \commutator{\dmnot}{\op\Phi(\omega)}\;.
-\ee
-The coupling superoperator has the same formal action on the response density both in the time and in the frequency domain, so the complete
-Liouville equation in $\omega$ space can be written as:
-\be\lb{LiouvillianRhopomegaDef3}
-\left(\bbomega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;.
-\ee
-
-\section{Critical Analysis of the linear response results}
-
-The main aim of this section is to discuss the reliability in the assessment of the results provided by the linear response formalism. In particular we are interested in 
-analyzing the \emph{linear response functional} defined as:
-\be\lb{LinearResponseFunctDef1}
-{\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
-\ee
-that represents the perturbation-induced modification of the expectation value of an observable $\op O$. Here, for a sake of concreteness, we are limiting our considerations 
-to observables that do not explicitly depend on time.
-
-We start this analysis by deriving an ulterior expression of the response density operator in the frequency space. We consider equation \eqref{rhoPrimeOmegaDef1} and observe that, for any 
-operator $\op O$, we may write:  
-\be
-\commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
-\ee
-where $\op Q_0= \identity - \dmnot$ is the projection operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
-\be
-\dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
-\ee
-This equation suggests us to define the \emph{fluctuation states}:
-\be\lb{fluctuationStateDef1}
-\ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \qq
-\bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
-\ee
-where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. An inspection of equation \eqref{ketBraTimeEvol1} 
-evidence that formulas \eqref{fluctuationStateDef1} are equivalent to the action of the $\op Q_0$ projector acting on the time evolution of the (occupied) eigenstates of $\hnot$, written 
-in the $\omega$ domain. Fluctuation states are, by definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
-\be
-\brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega \;.
-\ee
-The response density written in terms of the fluctuation states reads:
-\be\lb{rhoPrimeFluctuationStateDef1}
-\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
-\ee
-and consequently the linear response functional can be expressed as:
-\be\lb{LinearResponseFunctDef2}
-{\cal R}_{\op O}(\omega) = 
-\sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
-\ee
-Let us further investigate this formula pointing out some of the  computational aspects needed to explicitly perform the scalar products appearing in 
-\eqref{LinearResponseFunctDef2}. 
-We introduce a computational $\mu$-basis, composed by a finite set of $n_\mu$ basis elements $\{\ket{\mu}\}$, and assume that a reliable solution of the ground state problem has 
-been provided in this basis. This means that the feature of the basis (that, for instance, for real space basis are given by the grid spacing and number of points) are chosen so 
-that the coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, 
-under the hypothesis that the observable $\op O$ acts as a local operator on the occupied orbitals.
-
-The formal scalar products that express the linear response functional \eqref{LinearResponseFunctDef1} can be evaluated in the same basis introduced above, that is: 
-\be\lb{LinearResponseFunctDef3}
-{\cal R}_{\op O}(\omega) = 
-\sum_p\sum_\mu\left(\brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{\mu}\brket{\mu}{f_p(\omega)}\right) \;.
-\ee
-The task of the linear response formalism to provide reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
-expression for the numerical coefficients appearing in \eqref{LinearResponseFunctDef3}. The features of the computational basis described above ensures that this requirement should
-be satisfied for $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian conjugates). 
-On the contrary, the problem of the reliable reconstruction of the fluctuation states through the sampling of the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$
-turns out to be highly non-trivial, since the behavior of the fluctuation states strongly depends on $\omega$, as will be readily clarified in the next section.
-
-\subsection{Sternheimer equations and localization properties of the fluctuation states}
-\lb{LocalizationFluctuationStates}
-
-Starting from the Liouville equation \eqref{LiouvillianRhopomegaDef3} it is possible to derive a set of equation of motion for the fluctuation states. 
-The following equations are useful for this task: 
-\begin{align}
-\Liouvnot\dm'(\omega) & = \sum_p\left(-\ketbra{\psi_p}{f_p(-\omega)}\left(\hnot-\eps_p\right) + \left(\hnot-\eps_p\right)\ketbra{f_p(\omega)}{\psi_p}\right) \;, \nn \\
-\coupl\dm'(\omega) &= \commutator{\op V'(\omega)}{\dmnot} = \op Q_0 \op V'(\omega) \dmnot - \dmnot \op V'(\omega) \op Q_0 = \nn \\
-& = \sum_p\left( \op Q_0 \op V'(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op V'(\omega) \op Q_0 \right) \;, \nn \\
-\commutator{\op \Phi(\omega)}{\dmnot} & =  \sum_p\left( \op Q_0 \op \Phi(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op \Phi(\omega) \op Q_0 \right) \;. \nn
-\end{align} 
-Liouville equation written in this fashion implies the following equations for the fluctuation states, that can be extracted by multiplying from left and right for the 
-occupied eigenstates of $\hnot$:
-\begin{align}\lb{fluctuationStateEqMotion1}
-\left[\bbomega - \left(\hnot-\eps_p\right)\right]\ket{f_p(\omega)} &= \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;, \nn \\
-\bra{f_p(-\omega)}\left[-\bbomega - \left(\hnot-\eps_p\right)\right] &= \bra{\psi_p}\left(\op V'(\omega) + \op \Phi(\omega)\right)\op Q_0 \;.
-\end{align}
-Equations \eqref{fluctuationStateEqMotion1} have the form of a Sternheimer equation. Once projected in the $\{\ket{\mu}\}$ basis, and fixed the value of $\omega$, they can be solved 
-using a self-consistent procedure (add references). This approach provides a direct evaluation of the fluctuation states and thus the linear response functional \eqref{LinearResponseFunctDef3}
-can be computed.
-
-Much more interestingly for the main topic of the present discussion, and regardless from the detailed strategy of their solutions, equations \eqref{fluctuationStateEqMotion1} 
-allow us to present a \emph{localization argument} for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of \eqref{fluctuationStateEqMotion1}, 
-but the same argument holds also for the left ones. We split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term, so that the equation of motion 
-for $\ket{f_p(\omega)}$ is recasted as:
-\be\lb{fluctuationStateEqMotion}
-\left(\bbomega+\eps_p -\op T\right)\ket{f_p(\omega)} = \op V\ket{f_p(\omega)} + \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;.
-\ee
-This equation has the formal structure of an inhomogeneous Helmholtz equation and can be written in the coordinate representation as:
-\be
-\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k^2_p(\omega) = 2(\omega+\eps_p) \;.
-\ee
-The solution of this equation admits an integral representation in the form:
-\be\lb{fluctuationStateIntEq1}
-f_p(\omega,\r) = \int \dd\r' g_H(\r-\r')s(\r') \;,
-\ee
-where $g_H(\r)$ is the Green function of the Helmholtz operator in three dimensions. This integral representation allows us to assess the localization character 
-of the fluctuation states, \emph{i.e.} the behavior of $f_p(\omega,\r)$ when $\r$ becomes large. Indeed, assuming that the support of the source term is compact
-we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing, the leading contribution of the fluctuation states
-is given by:
-\be\lb{fluctuationStateIntEq2}
-f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \;.
-\ee
-We observe that the presence of the regularization parameter $\eta$ ensures a (slow) asymptotic convergence to zero, nonetheless the qualitative $\r$-dependence of the fluctuation 
-states is determined by the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an exponential damping for $\omega < |\eps_p|$ and an oscillating 
-power law behavior for $\omega \geq |\eps_p|$.
-This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef3}, so we conclude that
-the linear response functional is built in terms of localized fluctuation states for $\omega < |\eps_h|$. Instead, in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
-contributions from local and non-local quantities and, finally is composed only by non-local fluctuation states for $\omega\geq|\eps_0|$.
-
-\subsubsection{Criterion for the choice of the computational basis}
-
-The capability of the computational basis to express the results of the linear response can be analyzed using the localization argument previously discussed. 
-The first step needed to address this problem concerns with the evaluation of the reliability of the $\mu$-basis for $\omega=0$, \emph{i.e.} for a perturbing field that does 
-not depend on time. In this case the fluctuation states, as well as the expectation value of a given observable, can be computed performing a ground state calculation in which the perturbing 
-field $\op\Phi$ is added to the external potential of $\hnot$\footnote{We are interested in the linear response, so the magnitude of $\op\Phi$ has to be chosen in a way that respects this 
-regime. To check this point we can compute the perturbation-induced modification of an observable an verify that its value scales linearly with the magnitude of the field}. 
-The goodness of the $\mu$-basis can thus be verified as in the standard ground state calculation, for instance by checking that, given a certain level of completeness of the basis,
-the energy of the occupied (perturbed) orbitals is stable with respect to further refinements.
-
-Once that a basis with acceptable features has been chosen and verified for $\omega=0$ we can reasonably extend its reliability to $\omega>0$ by using the localization argument. 
-Indeed, we have argued that fluctuation states retain a local behavior up to $\omega=|\eps_h|$ and so we can expect that, up to this threshold value, the $\mu$-basis represents an 
-effective tool for a precise discretization of \eqref{LinearResponseFunctDef3}, thus providing a reliable estimate of the linear response.
-
-On the contrary, the situation becomes very less predictable for $\omega$ higher than the threshold $|\eps_h|$ since in this regime the fluctuation states start to delocalize in all the 
-accessible space and the spatial cutoff is provided only by the ground state matrix elements $\bra{\mu}\op O\ket{\psi_p}$.  
-In this case formula \eqref{LinearResponseFunctDef3} provides basis independent results only if the (partial) sampling of the fluctuation states is reconstructed in the domain in which
-$\bra{\mu}\op O\ket{\psi_p}$ are non vanishing. As we shall see through explicit computations this requirement turns out to be quite severe and choices of the basis that provide precise
-results below $|\eps_p|$ fails in the high-$\omega$ regime.
-
-\subsection{Linear response \emph{via} the construction of the excitation operators}
-
-The linear response presented so far is expressed in functions of the fluctuation states, that essentially describe the modification of the occupied eigenstates of $\hnot$ induced by 
-the perturbation. Fluctuation states depend explicitly on the perturbing field $\op\Phi(\omega)$ and, consequently, the analytic structure of the linear response written as in formula 
-\eqref{LinearResponseFunctDef2} emerge through a combination of the $\omega$ dependence of the perturbing field an on the intrinsic response of the system under inspection.
-
-It is however possible to present and equivalent but alternative formulation of the linear response that allows us to express the response density operator in term of the spectral
-decomposition of the Liouville superoperator. This approach naturally leads to the concept of \emph{excitation operators}, defined through a self-consistent operator eigenvalue equation,
-that codify the intrinsic capability of the system to respond to an arbitrary perturbation. Excitations behave as singularity of the response density operator and their knowledge provides a 
-deeper insight into the analytic structure of the linear response.
-
-The material presented in this section discusses a complete re-derivation of the linear response written in terms of excitation operators. Moreover, we will evidence that a \emph{localization 
-argument}, analogous to the one presented in section \ref{LocalizationFluctuationStates} for the fluctuation states, holds also for the excited states of the systems below a specific energetic
-threshold. This analysis has relevant consequence both under theoretical and computational point of view. Indeed, it provides a deeper understanding in the role of both localized and de-localized 
-excitations in determining the analytic structure of the linear response and it gives us clear indication in the level of refinement of the computational setup needed to obtain reliable results 
-from a linear response calculation.
-
-\subsubsection{Explicit sampling of the empty-states subspace}
-
-We now introduce the notion of $\alpha$-basis, that is a set of orthonormal vectors $\{\ket{\psi(\alpha)}\}$ that form a basis in the subspace of the empty-states, \emph{i.e.} in the subspace 
-orthogonal to the occupied eigenstates of $\hnot$. The elements of this set satisfy, by definition, the following orthonormality relation: 
-\be\lb{psiAlphaDef1}
-\brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq
-\brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;,
-\ee
-where we have parametrized the basis element through the multi-index $\alpha$, in the sense described in \ref{BasicDef}, since the associated vector can describe both a localized or a 
-de-localized state. The $\op Q_0$ projector as well as the completeness relation can be easily written in function of this basis: 
-\be\lb{psiAlphaQ0}
-\op Q_0 = \sint\dd\alpha\ketbra{\psi(\alpha)}{\psi(\alpha)} \;, \;\; 
-\identity = \sum_p\ketbra{\psi_p}{\psi_p} + \sint\dd\alpha\ketbra{\psi(\alpha)}{\psi(\alpha)} \;.
-\ee
-The $\alpha$-basis, defined through equations \eqref{psiAlphaDef1} and \eqref{psiAlphaQ0}, formally spans an infinite dimensional domain. However, for obvious computational reason it is 
-interesting to express the $\{\ket{\psi(\alpha)}\}$ in the same $\mu$-basis used to perform the ground states calculations. The discretization conditions imposed by the $\mu$-basis reduce 
-the $\{\ket{\psi(\alpha)}\}$ to a finite dimensional set. The dimension $n_\alpha$ of the basis can be computed by subtracting to the $n_\mu$ degrees of freedom the $n_{occ}$ constraints 
-needed to imposes the orthonormality of the $\{\ket{\psi(\alpha)}\}$ to the occupied states, so that $n_\alpha=n_\mu-n_{occ}$.
-
-\vspace{0.4cm}
-\emph{Quality assessment of the reduced $\alpha$-basis}
-\vspace{0.4cm}
-
-When the sampling of the empty state subspace is needed to perform practical calculations in realistic systems the construction of a complete $\alpha$-basis typically turns out to be 
-computationally unaffordable. In these cases it is possible to introduce a \emph{reduced} basis, denoted as $r\alpha$-basis, composed of a subset of dimension $n_{r\alpha}$ of the 
-$\{\ket{\psi(\alpha)}\}$ elements of the complete basis.
-
-The capability of the reduced basis to express the results of the linear response can be evaluated by using the results of a ground state calculation in which the time-independent 
-perturbing field $\op\Phi$ is added to the external potential of $\hnot$. We denote with $\ket{\psi_p^\Phi}$ the occupied eigenstate of the perturbed Hamiltonian and, using the 
-completeness relation of \eqref{psiAlphaQ0}, we can write the following expansion:
-\be\lb{PertPsiExpansion1}
-\ket{\psi_p^{\Phi}} = \sum_q a_{pq}\ket{\psi_q} + \sint\dd\alpha \,a_{p\alpha}\ket{\psi(\alpha)} \;,
-\ee
-where $a_{pq} = \brket{\psi_q}{\psi_p^{\Phi}}$ and $a_{p\alpha} = \brket{\psi(\alpha)}{\psi_p^{\Phi}}$. Equation \eqref{PertPsiExpansion1} holds exactly since the sum over the empty states
-is extended to the complete $\alpha$-basis. Taking the norm of $\ket{\psi_p^\Phi}$ and summing over $p$ provides:
-\be\lb{PertPsiExpansion2}
-n_{occ} = \sum_{pq} |a_{pq}|^2 + \sum_p\sint\dd\alpha\,|a_{p\alpha}|^2 \;,
-\ee
-the two addend of this equation measure the distribution of the total electronic charge of the perturbed system between the occupied and empty subspaces. Furthermore, we can use
-equation \eqref{PertPsiExpansion2} to build an estimator $C(n_{r\alpha})$ of the capability of the $r\alpha$-basis to describe the modification of the ground state density induced 
-by the time-independent perturbation. We define this estimator as follows:
-\be\lb{Cestimator1}
-C(n_{r\alpha}) = 1 - \frac{\sum_p\sum_\alpha^{n_{r\alpha}}|a_{p\alpha}|^2}{n_{occ} - \sum_{pq} |a_{pq}|^2} \;,
-\ee
-$C(n_{r\alpha})$ is by construction a positive function with values between 1, achieved when the sampling of the empty-states subspace is absent and 0, obtained when the reduced basis
-is complete. The normalization adopted in \eqref{Cestimator1} ensures that $C(n_{r\alpha})$ is an intensive estimator, so that its value does not depend on the number of occupied
-orbitals of the system.
-
-\subsubsection{Linear response in the basis of transitions}
-
-The defining equation of the linear response can be reformulated using the explicit sampling of the empty states defined above. The fundamental observation on the basis
-of this procedure regards the fact that both the response density operator \eqref{rhoPrimeOmegaDef1} and all the operators appearing in the Liouville equation 
-\eqref{LiouvillianRhopomegaDef3} are expressed as a commutator with $\dmnot$. This observation implies that all the operators $\op O$ appearing in the contest of the linear 
-response satisfy the formal relation:
-\be
-\op O = \dmnot\op O\op Q_0 + \op Q_0\op O\dmnot \;.
-\ee
-Plugging the operator expression of $\dmnot$ and $\op Q_0$ in terms of basis vector in the occupied and empty subspace provides:
-\be\lb{OperatorTransBasisExpDef1}
-\op O = \sum_p\sint \dd \alpha\left(
-\excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
-\right) \;,
-\ee
-where we have defined the \emph{transition operators}:
-\be
-\excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
-\decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;,
-\ee
-that thanks to \eqref{psiAlphaDef1} satisfy the orthonormality conditions:
-\be\lb{transitionOpOrthonormalityDef1}
-\trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
-\trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;.
-\ee
-Here we are assuming that the complete $\alpha$-basis is used, so the operator expansion in the basis of transition \eqref{OperatorTransBasisExpDef1} is exact. The effect of
-the adoption of a reduced basis will be analyzed when needed. 
-In order to recast this expansion in a simpler expression it turns out to be useful to define the rank-2 row vectors of the transition basis: 
-\be
-\sbra{p\alpha}{\cdot} \equiv 
-\mat{ \excite{p}{\alpha} \;, & \decay{\alpha}{p} }\;,
-\ee
-and we also introduce a vectorial notation to deal with the coefficients of the expansion of an operator in the transition basis, that is: 
-\be\lb{OperatorTransitionCoeffDef1}
-\sket{p\alpha}{\op O}  \equiv \mat{ \trace{\decay{\alpha}{p}\op O } \\ 
-\trace{\excite{p}{\alpha}\op O}} \; .
-\ee
-Thanks to this formalism we have that equation \eqref{OperatorTransBasisExpDef1} can be expressed as:
-\be\lb{OperatorTransBasisExpDef2}
-\op O = \sum_p\sint \dd \alpha \sbra{p\alpha}{\cdot}\sket{p\alpha}{\op O} = 
-\dbraket{\cdot}{\op O} \;,
-\ee
-where the last equality implicitly define the ulterior compact notation of the ``big-shaped'' vectors in which the summed indexes are omitted.  
-In the same fashion it will be also useful for the subsequent analysis to introduce a conjugate notation, in which the basis operators are expressed
-as column vector and the coefficients of the expanded operator as row ones, that is: 
-\be\lb{TransitionBasisConjugateDef1}
-\sket{p\alpha}{\cdot} \equiv 
-\mat{\decay{\alpha}{p} \\  \excite{p}{\alpha}} \;, \qq
-\sbra{p\alpha}{\op O}  \equiv 
-\mat{ \trace{\excite{\alpha}{p}\op O } \;, & \trace{\decay{p}{\alpha}\op O} }
-\;,
-\ee
-where the flip in the role of $\op e$ and $\op d$ in \eqref{TransitionBasisConjugateDef1} follows from the properties of excitation and decay operators
-under hermitian-conjugate operation. The expansion of an operator in the transition basis using the conjugate description reads: 
-\be\lb{OperatorTransBasisConjugateExpDef1}
-\op O = \sum_p\sint \dd \alpha \sbra{p\alpha}{\op O}\sket{p\alpha}{\cdot} = 
-\dbraket{\op O}{\cdot} \;.
-\ee
-The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis where it becomes a linear matrix equation for the 
-rank-2 vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side, that is:
-\be\lb{LiouvillianRhopomegaDef4}
-\omega\mat{ \trace{\decay{\alpha}{p}\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\dm'(\omega)}} - 
-\mat{ \trace{\decay{\alpha}{p}\Liouv\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\Liouv\dm'(\omega)}} =
-\mat{ \trace{\decay{\alpha}{p}\opskew{\Phi}(\omega)} \\ \trace{\excite{p}{\alpha}\opskew{\Phi}(\omega)}}
-\;,\nn
-\ee
-where we have introduced a compact notation to deal with the commutator of on operator with the unperturbed density: 
-\be
-\opskew{O} = \commutator{\op O}{\dmnot}\;.
-\ee
-The second addend in the l.h.s of \eqref{LiouvillianRhopomegaDef4} can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. 
-Performing this procedure we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
-\be\lb{LiouvilleTransBasisDef1}
-\sum_q\sint\dd\beta \left[\omega\delta_q^p\delta(\alpha-\beta)- \optr{L}^{p \alpha}_{q\beta} \right]\sket{q\beta}{\dm'(\omega)} =
-\sket{p\alpha}{\opskew{\Phi}(\omega)} \;.
-\ee
-with:
-\be\lb{LiouvilleMatrixTransBasisDef1}
-\optr{L}^{p \alpha}_{q\beta} \equiv \mat{\trace{\decay{\alpha}{p}\, \Liouv\, \excite{q}{\beta}} &
-\trace{\decay{\alpha}{p}\, \Liouv\, \decay{\beta}{q}} \\
-\trace{\excite{p}{\alpha}\, \Liouv\, \excite{q}{\beta}} &
-\trace{\excite{p}{\alpha}\, \Liouv\, \decay{\beta}{q}}} \;.
-\ee
-
-\subsubsection{Spectral decomposition of the response density in the transitions basis. Definition of excitation operators}
-
-The formulation of the Liouville equation in the basis of transitions is the starting point for the derivation of the spectral decomposition of the response density operator
-in terms of the eigenvectors if the Liouville operator. The first step in the achievement of this result is provided by the construction of the eigenvectors of the matrix 
-\eqref{LiouvilleMatrixTransBasisDef1}. Following the notation previously defined we introduce the rank-2 vectors $\sket{p\alpha}{E}$ and $\sbra{p\alpha}{\tilde E}$ that represent, 
-by definition, the right and left eigenvectors $\optr{L}$, respectively, so that:
-\be\lb{LiouvMatrixEigenvectorDef1}
-\sum_q \sint \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q \beta}{E} = E \sket{p\alpha}{E} \;, \quad
-\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \optr{L}^{p \alpha}_{q\beta} = E \sbra{q\beta}{\tilde E}\;.
-\ee
-In general, left and right eigenvectors do not coincide, but it is always possible to choose they normalization so that a orthonormality conditions among the
-elements of left and right spaces holds, namely:
-\be\lb{ExcitationOrthonormalityDef1}
-\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E}\sket{p\alpha}{E'} \equiv \dbraket{\tilde E}{E'} = \delta(E-E') \;.
-\ee
-Once that the eigenvectors are known, the spectral decomposition of the resolvent of $\optr{L}$ can be provided:  
-\be
-\left[\left(\bbomega-\optr{L}\right)^{-1}\right]^{p\alpha}_{q\beta} =\sint\dd E
-\frac{\sket{p\alpha}{E}\sbra{q\beta}{\tilde E}}{\bbomega-E} \;,
-\ee
-so equation \eqref{LiouvilleTransBasisDef1} can be inverted and we obtain the response density written in basis of transition, in the form:
-\be\lb{RhopExcitationTransBasisDef1}
-\sket{p\alpha}{\dm'(\omega)} = 
-\sint\dd E \sket{p\alpha}{E}
-\frac{\dbraket{\tilde E}{\opskew{\Phi}(\omega)}}{\bbomega-E} \;.
-\ee
-%\subsubsection{Definition of excitation operators}
-It is possible to express formula \eqref{RhopExcitationTransBasisDef1} as a true operator equation. First of all we show that the rank-2 vectors $\sket{p\alpha}{E}$ 
-and $\sbra{p\alpha}{\tilde E}$ can be interpreted as the transition basis coefficients of the right and left \emph{eigenstates} of the Liouville superoperator.   
-In order to do so we introduce the explicit representation of the eigenvectors op $\optr{L}$:
-\be\lb{XYcoeffDef1}
-\sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}} \;, \qq
-\sbra{p\alpha}{\tilde E} \equiv \mat{\tilde X_{E\,p\alpha} & \tilde Y_{E\,p\alpha}} \;,
-\ee
-and, on the basis of these elements, we define the \emph{excitation operators}:
-\begin{align}\lb{ExctitationOperatorsDef1}
-\op E &\equiv \dbraket{\cdot}{E} = 
-\sum_p \sint \dd \alpha \left(\excite{p}{\alpha} X_E^{p\alpha} + \decay{\alpha}{p} Y_E^{p\alpha}\right) 
-\;,\nn \\
-\op{\tilde E} &\equiv \dbraket{\tilde E}{\cdot} = \sum_p \sint \dd \alpha \left(\decay{\alpha}{p} \tilde X_{E\,p\alpha} + 
-\excite{p}{\alpha}\tilde Y_{E\,p\alpha}  \right)\;.
-\end{align}
-The orthonormality condition \eqref{ExcitationOrthonormalityDef1} implies that:
-\be
-\trace{\op{\tilde E} \op E'} = \sum_p\sint \dd\alpha \left(\tilde X_E^{p\alpha} X_{E'\,p\alpha} +
-\tilde Y_E^{p\alpha} Y_{E'\,p\alpha}\right) = \delta(E-E') \;. 
-\ee
-Excitation operators are the right and left eigenvectors of the Liouville superoperator, as directly follows from their
-definition. Indeed for $\op E$ we have:
-\begin{align}\lb{opEeigenvalueDef1}
-\Liouv \op E & = \sum_p \sint \dd \alpha \left(\trace{\decay{\alpha}{p} \Liouv \op E} \excite{p}{\alpha} + 
-\decay{\alpha}{p} \trace{ \excite{p}{\alpha} \Liouv \op E}  \right) = \nn \\
-&= \sum_p \sint  \dd \alpha \sbra{p\alpha}{\cdot} \sum_q \sint  \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q\beta}{E} 
-= E \sum_p \sint \dd \alpha \sbra{p\alpha}{\cdot} \sket{p\alpha}{E} = E \, \op E \;,	
-\end{align}
-whereas the left action on $\op{\tilde E}$ provides:
-\begin{align}\lb{optildeEeigenvalueDef1}
- \op{\tilde E} \Liouv &=  \sum_p \sint \dd \alpha \left(
-\trace{\op{\tilde E}\Liouv\excite{p}{\alpha}}\decay{\alpha}{p} +  
-\trace{\op{\tilde E}\sop{\mathcal L}\decay{\alpha}{p}} \excite{p}{\alpha} \right) = 
-\nn \\ &= \sum_p \sint  \dd \alpha  \sum_q \sint  \dd \beta
-\sbra{q\beta}{\tilde E}\optr{L}^{q\beta}_{p\alpha}\sket{p\alpha}{\cdot} = 
-E\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \sket{p\alpha}{\cdot}  =
-E \op{\tilde E} \;.
-\end{align}
-The introduction of the excitation operators allows us to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef1}, that is:
-\be\lb{RhopExcitationDef1}
-\dm'(\omega) = \dbraket{\cdot}{\dm'(\omega)} =
-\sint\dd E \op E
-\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \;,
-\ee
-where the algebraic equivalence between the trace written in \eqref{RhopExcitationDef1} and the numerator of \eqref{RhopExcitationTransBasisDef1}
-can be easily proved.
-
-Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitation operators. Now 
-we are interested in analyzing this restatement of the linear response under the perspective of the main topic of the paper, namely the critical assessment 
-of the results provided by the linear response formalism in a given computational setup. Our interests are mainly twofold. First, to analyze the localization 
-properties of the excitations, in a analogous fashion of what done in section \ref{LocalizationFluctuationStates} for the fluctuation states. Second, to determine 
-the precise nature of the formal sum over excitations written in \eqref{RhopExcitationDef1}, in order to be able to discriminate between the discrete and the 
-continuum sector of the excitation spectrum.
-
-\subsubsection{Excitation expansion of the fluctuation states. A localization argument for the excited states}
-
-%Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitations $\op E$. Now
-We push this formalism a little bit forward and derive the expansion of the fluctuation states \eqref{fluctuationStateDef1} in terms of the \emph{excited states} of the 
-system . Firstly, we introduce excited states, defined via the linear combination of the elements of the $\alpha$-basis with the coefficients that appears in 
-\eqref{XYcoeffDef1}, that is:
-\begin{align}\lb{ExcitedStatesDef1}
-\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
-\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
-\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
-\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;,
-\end{align}
-due to these definitions we can express excitation operators as follows:
-\be\lb{ExcitationOperatorsDef2}
-\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
-\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
-\ee
-Formulas \eqref{ExcitationOperatorsDef2} provides a clear representation of the physical meaning of excited states \eqref{ExcitedStatesDef1}, as can be seen by applying
-the excitation operators on the occupied eigenstates of the systems:
-\be
-\op E\ket{\psi_p} = \ket{\phi^E_p} \;, \quad \bra{\psi_p} \op E = \bra{\chi^E_p} \;, \quad
-\op {\tilde E}\ket{\psi_p} = \tket{\chi^E_p} \;, \quad \bra{\psi_p} \op {\tilde E} = \tbra{\phi^E_p} \;.
-\nn
-\ee
-The excited states expansion of fluctuation states can be easily derived.  Indeed an inspection of formula \eqref{rhoPrimeFluctuationStateDef1} show that fluctuation 
-states can be extracted from the response density operator as follows:
-\be
-\ket{f_p(\omega)} = \dm'(\omega)\ket{\psi_p} \;, \qq
-\bra{f_p(-\omega)} = \bra{\psi_p}\dm'(\omega) \;, \nn
-\ee
-so plugging the expression \eqref{ExcitationOperatorsDef2} inside \eqref{RhopExcitationDef1} and applying the response density to a occupied state provides:
-\be\lb{FluctStateExcitationDef1}
-\ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \ket{\phi^E_p} \;, \qq
-\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \;.
-\ee
-Fluctuation states emerge as a linear superposition of excited states. The $\omega$-dependent coefficients codify the effect of the perturbing field in determining the 
-relative contribution of each addend through the weighting coefficients in the numerators of \eqref{FluctStateExcitationDef1}.
-
-We perform a particular choice of the perturbing field:
-\be
-\op\Phi = \commutator{\op E}{\dmnot} \; \longrightarrow \; \opskew{\Phi} = 
-\commutator{\commutator{\op E}{\dmnot}}{\dmnot} = \op E
-\ee
-
-\subsubsection{Sternheimer equation for excited states. Localization argument revisited}
-
-The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated into a Schroedinger-like equations
-for the excitonic states.
-
-\vspace{0.5cm}
-\emph{Equations for $\coupl = 0$}
-\vspace{0.5cm}
-
-\noindent In this case the $\optr{L}_{q\beta}^{p\alpha}$ matrix has only diagonal non-vanishing elements, given by: 
-\be
-\trace{\decay{\alpha}{p}\Liouv\excite{q}{\beta}} = H_{0\alpha\beta}\delta_{pq} - \eps_p\delta_{pq}\delta(\alpha-\beta) \;, \qq
-\trace{\excite{\alpha}{p}\Liouv\decay{q}{\beta}} = \eps_p\delta_{pq}\delta(\alpha-\beta) - H_{0\beta\alpha}\delta_{pq} \;, 
-\ee
-where $H_{0\alpha\beta} = \bra{\psi(\alpha)}\hnot\ket{\psi(\beta)}$. The eigenvalue conditions \eqref{LiouvMatrixEigenvectorDef1} imply
-that the $Y$ and $\tilde Y$ coefficients introduced in \eqref{XYcoeffDef1} vanish so that both $\tket{\chi^E_p}$ and $\bra{\chi^E_p}$ do not
-contribute to the excitation operators \eqref{ExcitationOperatorsDef2}. The eigenvalue operator equation for $\op E$ reduces to:
-\be
-\sum_q\left(\hnot - \eps_q\right)\ket{\phi^E_q}\bra{\psi_q} = E \sum_q \ket{\phi^E_q}\bra{\psi_q} \;,
-\ee
-and projecting on $\ket{\psi_q}$ provides the eigenvalue condition for the excitonic state $\ket{\phi^E_p}$:
-\be
-\left(\hnot - \eps_p\right)\ket{\phi^E_p} = E \ket{\phi^E_p} \;.
-\ee
-In the same way, by using the eigenvalue condition for $\op{\tilde E}$, we can derive an analogous equation for $\tbra{\phi^E_p}$. To achieve this
-result we need the expression of the left action of the (unperturbed) Liouville superoperator defined in \eqref{L0sopDef1}, that can be derived by
-observing that:
-\be\lb{leftActionLouv0Def1}
-\trace{\op O' (\Liouvnot \op O)} = \trace{(\op O' \Liouvnot) \op O } =
-\trace{\commutator{\op O'}{\op H_0} \op O} \quad \Rightarrow \quad \op O \Liouvnot = 
-- \Liouvnot \op O \;.
-\ee
-So, the eigenvalue operator equation for $\op{\tilde E}$ provides:
-\be
-\sum_q  \ket{\psi_q} \tbra{\phi^E_q} \left( \hnot - \eps_q \right) =
-E \sum_q  \ket{\psi_q} \tbra{\phi^E_q} \;,
-\ee
-so that:
-\be
-\tbra{\phi^E_p} \left( \hnot - \eps_p \right) = E \tbra{\phi^E_p} \;.
-\ee
-So we find that the excitonic states are the left and right eigenvectors of $\hnot$ (that actually coincide since we are considering
-hermitian Hamiltonians). The energy eigenvalue is shifted by $\eps_p$, that is the energy of the occupied states involved in the 
-excitation.
-
-A last interesting comment regards the expression of the response density when the excitation operator $\op E$ itself is used as the source of the
-perturbation. In this case, denoting as $\op E'$ the given perturbing excitation, it is easy to see that:
-\be
-\trace{\op{\tilde E}\commutator{\op E'}{\dmnot}} = \trace{\op{\tilde E}\op E'} = \delta(E-E') \;, \nn 
-\ee
-and the response density generated by this perturbation is given by: 
-\be
-\dm'(\omega) = \frac{1}{\bbomega - E'} \op E'\;,
-\ee
-which represents a monochromatic term of energy $E'$. Under this perspective we can state that excitations constitute
-the \emph{resonant channels} for the construction  of the response density.
-
-\vspace{0.5cm}
-\emph{Generic equations for $\coupl \neq 0$}
-\vspace{0.5cm}
-
-To explicitly write the generic eigenvalue equations for the excitonic states it is useful to introduce some further formalism to express the 
-self-consistent part of the perturbing Hamiltonian \eqref{Vptspacedef1}. We start by expanding $\op V'$ in the coordinate representation, that is:
-\be
-\op V'(t)= 
-\int \dd \br \dd \br' \dd \r \dd \r' \bra{\br'}\frac{\delta\hnot}{\delta \rho_0(\r,\r')}\ket{\br}
-\trace{\dm'(t) \ket{\r} \bra{\r'}} \ketbra{\br'}{\br}\;, \nn
-\ee
-then we introduce the \emph{coupling kernel}, defined as:
-\be\lb{couplingKernelDef1}
-U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
-} \trace{\op O' \ket{\r} \bra{\r'}} \;,
-\ee
-using this quantity we can express $\op V'$ as:
-\be\lb{Vptspacedef2}
-\op V'(t)= 
-\int \dd \br \dd \br' U\left[\ketbra{\br}{\br'};\dm'(t)\right] \ketbra{\br'}{\br}\;,
-\ee
-and consequently the formal action of the coupling superoperator \eqref{couplingSopDef1} on a generic operator $\op O$ can be expressed as: 
-\be\lb{couplingSopDef2}
-\coupl\op O = 
-\int \dd \r \dd \r' \commutator{\ketbra{\r'}{\r}}{\dmnot} U\left[\ketbra{\r}{\r'};\op O\right] \;.
-\ee
-Using this formalism we can define the left action of the coupling superoperator, in analogous way of what done in \eqref{leftActionLouv0Def1}, 
-that is:
-\begin{align}\lb{leftActionCouplingDef1}
-\trace{\op O' (\coupl \op O)} &= \int \dd\r\dd\r'\trace{\ketbra{\r'}{\r}\commutator{\dmnot}{\op O'}}
-U\left[\ketbra{\r}{\r'};\op O\right]  = \nn \\ &= 
-U\left[\commutator{\dmnot}{\op O'};\op O\right] \doteq \trace{(\op O' \coupl) \op O } \;,
-\end{align}
-where the second equality follows from the linearity of the coupling kernel. The right action of the coupling superoperator consistent with this result is:
-\be\lb{leftActionCouplingDef2}
-(\op O \coupl) = \int \dd\r\dd\r'
-U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;.
-\ee
-This formalism allows us to provide a compact expression for the action of the Liouville superoperator on the excitation operators. For the left action we have:
-\begin{align}
-\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi^E_p}{\psi_p} - \sum_p\ketbra{\psi_p}{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
-&+ \sum_p \sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ketbra{\psi(\alpha)}{\psi_p}
-- \sum_p \sint \dd\alpha U\left[\excite{p}{\alpha}; \op E\right] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;, \nn
-\end{align}
-here the action of the coupling superoperator on $\op E$ has been computed imposing its expansion in the transition basis and computing the coefficients with formula 
-\eqref{leftActionCouplingDef1}. Projecting out the previous equation by multiplication with an occupied eigenstates from both the left and right provides the equations:
-\begin{align}\lb{PhipChipEqDef1}
-\left(\hnot-\eps_p\right)\ket{\phi^E_p} +\sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ket{\psi(\alpha)} &= E\ket{\phi^E_p} \;,\nn \\
-\bra{\chi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\excite{p}{\alpha}; \op E\right] &= -E\bra{\chi^E_p} \;.
-\end{align}
-We observe that the coupling kernel behaves as a (non-local) potential that depends on both the $X_{E}^{p \alpha}$ and $Y_{E}^{p \alpha}$ coefficients of \eqref{ExcitedStatesDef1}
-thus introducing a coupling between the $\phi$ and $\chi$ states.
-
-In the same way the right action provides:
-\begin{align}
-\op{\tilde E}\Liouv &= \sum_p\tketbra{\psi_p}{\phi^E_p}\left(\hnot-\eps_p\right) - \sum_p\left(\hnot-\eps_p\right)\tket{\chi^E_p}\bra{\psi^E_p} + \nn \\
-&+ \sum_p \sint \dd\alpha  U\left[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}\right] \ketbra{\psi(\alpha)}{\psi_p}
-+ \sum_p \sint \dd\alpha U\left[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}\right] \ketbra{\psi_p}{\psi(\alpha)} = E\op{\tilde E} \;, \nn
-\end{align}
-so that:
-\begin{align}\lb{TildePhipChipEqDef1}
-\tbra{\phi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}\right]  &= E\tbra{\phi^E_p} \;,\nn \\
-\left(\hnot-\eps_p\right)\tket{\chi^E_p} -\sint \dd\alpha \bra{\psi(\alpha)} U\left[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}\right] &= -E\tket{\chi^E_p} \;.
-\end{align}
-
-\subsubsection{Excitation expansion of the linear response functional}
-
-We have that:
-\be
-\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} = \sum_q\sint\dd\beta\, \optr{J}^{p\alpha}_{q\beta}
-\sket{q\beta}{\op\Phi(\omega)} \;\;, \;{\rm with} \;\;
-\optr{J}^{p\alpha}_{q\beta} = \delta_{pq}\delta(\alpha-\beta)\mat{1 & 0 \\ 0 & -1}
-\ee
-and the linear response functional \eqref{LinearResponseFunctDef1} can be written as:
-\be
-{\cal R}_{\op O}(\omega) = 
-\sint\dd E \dbraket{\op O}{E}
-\frac{\dbra{\tilde E}\optr{J}\dket{\op\Phi(\omega)}}{\bbomega-E} \;.
-\ee
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \section{Draft of the paper - old notes}
-% 
-% \begin{itemize}
-% \item Aim of the paper: Compute the electronic properties of a molecular system with the formalism of linear scaling using a LR-TDDFT inside BigDFT code. 
-% %We also want to define a set of computational tools that allow to check the reliability of the computation.  
-% \end{itemize}
-% 
-% \begin{itemize}
-% \item Motivation: the DFT code have reached reliable features of precision for the computation of the GS.
-The same probletic are instead needed in order to achieve the same type of results for spectroscopic
-% properties in large systems
-% \begin{itemize}
-% \item Quantify the impact of several modelling of a given systems (environment, disorder)
-% \item Systematic approach has proven its effectiveness for GS calculations (easy to handle)~\cite{deltatest2016}.
-The quality of localized basis function is therefore easy to quantify (variational theorem)
-% \item A challenge is represented by large scale computation for \emph{molecular} systems
-% \end{itemize}
-% \item State-of-the-art 
-% \begin{itemize}
-% \item localized basis set for representing the Hamiltonians (e.g. Fiesta (Blase, Olevano), FHI-Aims, GWMol)
-% \item This approach has been also generalized to LR calculation in the case of ONETEP \cite{Ratcliff2013}.
-However little is said about the reliability of the results in terms of the convergence of the spectra
-% \end{itemize}
-% \item Content of the paper: 
-% \begin{itemize}
-% \item Brief illustration of the support function approach in wavelets (Large systems are  accessible for the structure (Energy, Forces,\ldots)
-% \item We want to exploit the wavelet properties in the context of LR, \emph{by also providing some criteria} which may be of interest for the evaluation of the quality of the LR results.
-% \end{itemize}
-% \item Conclusions and implications
-% \begin{itemize}
-% \item We might apply this formalism also in the contect of MBPT and inspect the validity of the linear response functional for e.g.
-GW calcualtions (the perturbation operator will be different from the dipole)
-% \end{itemize}
-% \end{itemize}
-
-%\bibliographystyle{alpha}
-%\bibliography{sample}
+\section{Introduction}
 

### 2018-03-06 LRDraft.tex
Update on Overleaf.

@@
 \begin{abstract}
-By performing linear-response (LR)-TDDFT calculation of molecular systems within a highly complete real-space basis set, we analyze how the behavior of the dynamical 
-polarizability is influenced by the discretization conditions of the computational treatment.
-We show that optical excitations of energy below the LR ionization potential behave as observable, localized quantities, that can be studied with high precision, 
-provided an adequate level of completeness. We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
-in any discretization scheme. Under this light, we also show that excitation energies above ionization threshold do not exhibit such observable features and \emph{cannot} be 
-considered as poles of the dynamical polarizability. This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
+We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
+In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems.
+We show that optical excitations of energy below the LR ionization potential behave as observable, localized quantities, that can be computationally calculated with high precision, provided an adequate level of completeness.
+Above this energy threshold, the analytic structure of the susceptivity functional might be separated in two sectors: one can still be described in terms of observable excitation with discrete energies, that can be captured within computational setups tailored for localized states.
+However such excitations are embedded in a continuum of excited states that, on the contrary, behave as plane waves and cannot be described efficiently by the same computational techniques.
+Such excitations do not exhibit observable features and \emph{cannot} be considered as poles of the dynamical polarizability.
+Nonetheless, the contribution of such continuum of excitation reveals to be of paramount importance even for expressing LR quantities in the infrared regime like for example static polarizabilities.
+This is particularly evident for small molecules; we show how these considerations might be influenced by the size of molecular system.
+ We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
+in any discretization scheme.  This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
 unoccupied subspace.

### 2018-03-06 AnalyticStructure_main.tex
update

--- 2018-02-15 LRDraft.tex
@@
-\documentclass[a4paper]{article}
+\documentclass[reprint,aps,prb]{revtex4-1}
 
@@
 \usepackage[english]{babel}
-\usepackage[utf8x]{inputenc}
-\usepackage[T1]{fontenc}
-
-%% Sets page size and margins
-\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
+%\usepackage[utf8x]{inputenc}
+%\usepackage[T1]{fontenc}
 
 %% Useful packages
-\usepackage{amsmath}
 \usepackage{graphicx}
@@
 \usepackage{xifthen}
-\usepackage[colorinlistoftodos]{todonotes}
-\usepackage[colorlinks=true, allcolors=blue]{hyperref}
-\usepackage{authblk}
 
@@
 
-\title{Critical assessment of Linear-Response Excitations in Molecular system\\
-or \\
-On the Localization of the Linear-Response excitations in Open Systems}
-\author[1]{Luigi Genovese}
-\author[2]{Marco D'Alessandro}
-\affil[1]{Laboratoire de Simulation Atomistique (LSim), SP2M, INAC, CEA-UJF, 17 Av. des Martyrs,
+\begin{document}
+
+%\preprint{APS/123-QED}
+
+\title{On the analytic structure of the linear response susceptibility in open systems}
+
+\author{Luigi Genovese}
+\affiliation{Laboratoire de Simulation Atomistique (LSim), SP2M, INAC, CEA-UJF, 17 Av. des Martyrs,
 38054 Grenoble, France}
-\affil[2]{Istituto di Struttura della Materia-CNR (ISM-CNR), Via del Fosso del Cavaliere 100, 00133 Roma, Italia}
+\author{Marco D'Alessandro}%
+\affiliation{Istituto di Struttura della Materia-CNR (ISM-CNR), Via del Fosso del Cavaliere 100, 00133 Roma, Italia}
 
-\begin{document}
-\maketitle
+\date{\today}
 
@@
 
-\section{Reboot with recent considerations}
-Given a approximate eigenvector $\ket{\psi}$ we approximate its energy by $E=\bra{\psi} \op H \ket{\psi}$.
-This energy is an approximation of the true eigenvalue.
-We assume that the wavefunction gradient $\ket{g(E)}\equiv \left(\op H -E\right)\ket{\psi}$ indicates the distance from the solution of the Schroedinger Equation (SE) in a complete basis set.
-By imposing the solution of the SE for a better approximation of the wavefunction $\psi + \Delta \psi$
-we should obtain, self-consistently:
-\begin{align}
-\left(E -\op H \right)\ket{\Delta \psi} &= \ket{g(E+ \Delta E)}\;,\\
-\Delta E &= 2 \bra{\psi} \op H \ket{\Delta \psi}\;.
-\end{align}
-From the expression of $\Delta \psi$ we can recalculate another approximation for the wavefunction and, correspondingly, for the eigenvalue.
-By definition, the exact solution is reached only when $\ket{g}=0$, which implies that the norm of $\Delta \psi$ must decrease during the perturbative process.
+%\pacs{Valid PACS appear here}
+\maketitle
 
-\textbf{Theorem:} Only the eigenstates with negative energy might have a finite-size correction that can be expressed perturbatvely.
+\section{Introduction}
 
-\textbf{Proof}: 
-If we apply this process to estimate the finite-size correction to a numerical solution of the Schroedinger equation, as the eigenvalue should converge faster than the eigenvector, we conclude that the gradient $g$ becomes nonzero only in regions that  should be located far from the potential region.
-If this is true, at the next iteration the gradient would become $g + \op H \Delta \psi + \mathcal{O}(\Delta E)$.
-Therefore, for having a convergent perturbative process, also the ket $\ket{\Delta \psi}$ solution of the above equation should be localized far from the support of the potential.
-In other terms, the relation between $g$ and $\Delta \psi$ should be local in space.
+.....
 
-The Lippmann-Schwinger relation defines the Dyson series of the resolvent of the Hamiltonian in terms of the Helmholtz Green's function $\op G_0(E)$:
-\be 
-\op G(E) \equiv (E- \op H)^{-1} = \op G_0(E) + \op G_0(E) \op V \op G(E)\;.
+\section{Theory}
+
+In the framework of the linear response formalism one is typically interested in computing the \emph{linear response functional}:
+\be\lb{LinearResponseFunctDef1}
+{\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
 \ee
-We have therefore 
-\be 
-\ket{\Delta \psi} = 
-\sum_{p=0}^\infty \op G_0(E) 
-\left(\op V \op G_0(E)\right)^p \ket{g}\;.
-\ee
-For the properties of the Helmholtz equation, locality in space of $\Delta \psi$ might only be recovered for negative energy values.
-This equation proves that for positive values of the energy the finite-size corrections will \emph{always} provide fully delocalized corrections: it would be impossible to observe a convergence of the wavefunction in the interior region by simply increasing the size of the simulation domain.
-If the value of the approximate energy does not become negative during the perturbative process, 
-a modification of the domain boundaries will impact the wavefunction in the entire simulation region.
-In this case, convergence might only be achieved uniformly and there is no guarantee that a larger domain will provide similar energies.
-$\square$
-\begin{itemize}
-\item Write the excitations as the eigenstates of the Liouvillian:
-\begin{itemize}
-\item The Casida Matrix provides the eigenvectors in the basis of the unperturbed transitions
-\item From the Casida eigenproblem we 
-get the poles of the dynamical polarizability and we may reconstruct the perturbed wavefunctions
-\item Lot of solution in state of 
-the art to express \emph{the same information}, still by avoiding the explicit diagonalization of the problem
-\end{itemize}
-\item Such transitions might also be written in terms of the solutions of the eigenproblem for the perturbed hamiltonian
-\begin{itemize}
-\item There are therefore excitations which correspond to localized solutions of the above eigenproblems
-\item There is a \emph{energy threshold} above which the eigenfunction associated \emph{cannot be anymore} localized
-\end{itemize}
-\item Below threshold, the eigenfunction are localized and the energy values are \emph{observable} quantities (there is a convergence in terms of the simulation parameters)
-\begin{itemize}
-\item Casida treatments for different
-basis sets exhibit convergence of the low-energy excitations
-\item Still, even for such localized excitations, non-trivial dependence on the empty states on some of excitation value is observed (energies converge relatively slowly wrt $N_\alpha$)
-\item The locality of the excitation can be \emph{measured}
-{\bf NEW idea for the SoB: why not to consider}
-$$
-\int \mathrm d \mathbf r
-\rho(\mathbf r) |\phi_p^E(\mathbf r)|^2
-$$
-or similar quantities, that are independent on the number of empty and  bound states
-\item Localized Excitation are the  only one with an observable character (this is surely already known)
-\item The spectrum of the Liouvillian in this regime is a \emph{discrete} spectrum; the excitation energies are \emph{poles} of the dynamical polarizability
-nano\item We may associate the value of the threshold to the \emph{ionization potential}: This is a very interesting remark in my opinion: the physics of the optical excitation is observable 
-(and therefore localized) only if the energies are not higher than the energy needed to ionize the system. After this point, it seems normal to me that the ``optical'' excitations with 
-real value of the energy are not  meant to be observable anymore.
-\item Optical Excitations below threshold have therefore a (very) long lifetime (poles on the real axis), and they contribute to the analytic structure of the dynamical polarizability.
-\end{itemize}
-\item Above this threshold the energies have a strong dependence on the computational treatment
-\begin{itemize}
-\item The high-energy part of the 
-spectrum does not converge with the 
-boundary conditions, even though they converge wrt the empty states (established techniques \emph{do not solve} such problem)
-\item This is \emph{not} a problem that is related to the continuum collapse of the empty states.
-\item They belong to the continuum of  the Liouvillian $\rightarrow$ they collapse, or depend strongly on the basis set adopted
-\item They cannot be considered separately \emph{even when they are expressed in localized basis} as 
-their shape is dependent on the treatment
-\item They energies are not \emph{true} poles of the dynamical polarizability (the spectra converge only by superposition of deltas)
-\end{itemize}
-\item Optical excitation above Ionization threshold are therefore observable \emph{only} if they possess a lifetime (the peaks of the spectrum have a well-defined broadening). 
-In this way they might be expressed in terms of resonant wavefunctions
-\end{itemize}
+that represents the perturbation-induced modification of the expectation value of an observable $\op O$\footnote{For a sake of concreteness, we are limiting our considerations 
+to observables that do not explicitly depend on time}. Here $\dm'(\omega)$ is the \emph{response density operator} that describes the $\omega$-dependent modification of the density 
+operator induced by the perturbation.
 
-\section{General theoretical setup}
+\subsection{Basic equation for the linear response formalism for electronic excitations}
 
-\subsection{Basic definitions}\lb{BasicDef}
+The linear response formalism can be effectively applied to the analysis of the electronic excitations of molecular and condensed-matter systems, described by the (density-dependent) 
+ground-state hermitian Hamiltonian $\hnot$, coupled to an external perturbation described by the perturbing field $\op\Phi(\omega)$. The $\omega$ structure of $\op\Phi(\omega)$ codifies both 
+the intrinsic time dependence of the perturbation and the switching-on procedure, \emph{e.g.} adiabatic or sudden limit protocols.
 
-We consider a generic one-body quantum mechanical problem described by the hermitian Hamiltonian $\hnot$  written in terms of the standard 
-kinetic operator $\op T$ plus a one-body potential $\op V$, which we assume to be completely general, i.e. possibly nonlocal.
-We consider open systems, so that $\hnot$ is defined on $\mathbb L_2(\mathbb R_3)$ and the basis of its eigenfunctions spans this 
-functional space. Therefore, together with the discrete (bound) part of its spectrum $\eps_b$, the Hamiltonian may have an essential spectrum 
-$\eps(c)$, parametrized by the continuum label $c$.
-
-A generic state $\ket{f} \in \mathbb L_2(\mathbb R_3)$ can be expanded in the basis of the eigenstates of $\hnot$, that is:
-\be\lb{ketBasisExpDef1}
-\ket{f} = \sum_b f_b \ket{\psi_b} + \int \dd c f(c) \ket{\psi(c)}  = 
-\sint \dd s f(s) \ket{\psi(s)} \;,
-\ee
-where we have introduced the compact multi-index $s$ that collect both the discrete and continuum part of the spectrum of $\hnot$.
-The normalization of the basis can be chosen so that the standard orthonormality condition holds, that is: 
-\be
-\brket{\psi(s)}{\psi(s')} = \delta(s-s') \;,
-\ee
-and the completeness condition is written as:
-\be\lb{completenessH0basis1}
-\identity = \sint \dd s \ketbra{\psi(s)}{\psi(s)} = \sum_{b} \ketbra{\psi_b}{\psi_b} + \int \dd c \ketbra{\psi(c)}{\psi(c)} \;. 
-\ee
-Thanks to this condition the coefficients of the expansion \eqref{ketBasisExpDef1} can be expressed via a scalar products, namely $f_{b} = 
-\brket{\psi_b}{f}$ and $f(c) = \brket{\psi(c)}{f}$.
-
-\subsection{Time evolution of states in the linear response regime}
-
-We discuss the time evolution of a generic state vector in the case in which a hermitian time dependent perturbation $\hone{t}$ is added to $\hnot$. 
-To achieve this task we have to solve the time dependent Schroedinger equation supplied by the knowledge of the state at the ``initial'' time $t_0$.
-We seek for a solution of the form:
-\be\lb{ketTimeEvol1}
-\ket{\psi(t_{0},t)} = e^{-\ii \hnot t} \op{U}_{I}(t,t_0) e^{\ii \hnot t_0}\ket{\psi_0} \; . 
-\ee
-where $\op{U}_I(t,t_0)$ is the time evolution operator induced by $\hone{}$ that satisfies the ``initial'' time condition $\op{U}_I(t_0,t_0)=1$. 
-Plugging the expression \eqref{ketTimeEvol1} in the Schroedinger equation we obtain a differential equation for $\op{U}_I$ that can be solved 
-iteratively as a power series in $\hone{}$. Limiting to the linear order provides:
-\be \lb{UiLinOrderSol1}
-\op{U}_I(t,t_0) = \identity - \ii \intdef{t_0}{t}{t'} e^{\ii \hnot t'} \hone{t'} e^{-\ii \hnot t'} \; .
-\ee
-So, at the first order in $\hone{}$ equation \eqref{ketTimeEvol1} can thus be written as:
-\be \lb{ketTimeEvol2} 
-\ket{\psi(t_{0},t)} = \left( \op{U}_0(t-t_0) - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \hone{t'} 
-\op{U}_0(t'-t_0) \right)\ket{\psi_0} \; ,
-\ee
-were we have defined the time evolution operator of the unperturbed Hamiltonian by
-\be
-\op{U}_0(t-t_0)\equiv e^{-\ii \hnot(t -t_0)} \;.
-\ee
-The time evolution of left vectors can be derived in the same way. We can express the temporal evolution of the left 
-vectors in the form:
-\be \lb{braTimeEvol1}
-\bra{\psi(t_{0},t)} = \bra{\psi_0} e^{-\ii \hnot t_0} \op{U}_{I}(t_0,t) e^{\ii \hnot t} \;,
-\ee
-plugging this equation in the conjugate Schroedinger equation and pursuing the same procedure defined above, we obtain the 
-linear order expression of time evolution of left vectors:
-\be\lb{leftVectTimeEvol2}
-\bra{\psi(t_{0},t)} = \bra{\psi_0} \left( \op{U}_0(t_0-t) + \ii \intdef{t_0}{t}{t'} \op{U}_0(t_0-t') 
-\hone{t'} \op{U}_0(t'-t) \right) 
-\ee
-It is immediate to check that, in order to preserve the norm vectors during the time evolution, it is sufficient that $\op{U}_I$ 
-possesses the  semi-group structure $\op{U}_I(t_2,t_1) \op{U}_I(t_1,t_0) = \op{U}_I(t_2,t_0)$. An inspection of \eqref{UiLinOrderSol1}
-evidences that this condition is satisfied in the linear response regime.
-
-\subsubsection{Time evolution of stationary states. Adiabatic limit vs finite time switch-on procedure}
-
-We are interested in determining the time evolution of an eigenstate of $\hnot$ under the action of the perturbation $\hone{t}$ in the linear 
-response regime. A proper statement of the problem requires the specification of the way in which the perturbation is switched on.
-Possible choice of the switching on protocol are, for instance, the \emph{adiabatic limit} and the \emph{sudden limit} protocols. In the first
-case the perturbation is switched on at $t_0=-\infty$, but the intrinsic time structure of $\hone{}$ is modified by the damping function 
-$e^{-\eta_a |t|}$. In the second one the perturbation is abruptly switched on at the finite time $t_0$, so that the time structure of
-$\hone{}$ is multiplied times the $\theta$-function $\theta(t-t_0)$.
-
-Starting from the generic time evolution equation \eqref{ketTimeEvol2} and choosing the initial condition in the form 
-$\ket{\psi_0} = e^{-\\i \eps_b t_0}\ket{\psi_b}$, we can write the time evolution of the generic $\ket{\psi_b}$ eigenvector of $\hnot$ as:
-\be \lb{ketTimeEvol3} 
-\ket{\psi_b(t)} = e^{-\ii \eps_b t}\left( \identity - \ii \intdef{t_0}{t}{t'} \op{U}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}_0(t'-t)  \right)\ket{\psi_b} \; ,
-\ee
-where we have introduced the \emph{perturbing field operators}: 
-\be
-\op\Phi^{a.l.}(t) = e^{-\eta_a |t|} \hone{t} \;, \qq
-\op\Phi^{s.l.}(t) = \theta(t-t_0) \hone{t}
-\ee
-that codify the effective of the perturbing Hamiltonian in the specific switch-on procedure. Making usage of elementary properties of $\theta$ functions allows us
-to rewrite the former time integral as:
-\be\lb{AopDef1}
-\op A(t) = \intdef{-\infty}{\infty}{t'} \op{U}^{+}_0(t-t') \op\Phi^{a.l,s.l}(t') \op{U}^{-}_0(t'-t) \;,
-\ee
-so that the effect of the switch-on protocol are completely reabsorbed in the perturbing field. In the subsequent analysis we will omit the apex in the fields $\op\Phi$, 
-unless explicitly needed, to keep notations as simple as possible. Thanks to this definition we can express the time evolution of the eigenvectors of $\hnot$ in the 
-compact form:
-\be\lb{ketBraTimeEvol1}
-\ket{\psi_b(t)} = e^{-\ii \eps_b t}\left( \identity - \ii \op A(t)  \right)\ket{\psi_b} \; , \qq 
-\bra{\psi_b(t)} = \bra{\psi_b} \left( \identity + \ii \op A(t)  \right) e^{\ii \eps_b t} \; .
-\ee
-
-\subsection{Linear response on the density operator. Liouville equation in the time domain}
-
-We introduce the \emph{density operator} defined as the sum of the one-particle densities of all the states with energy lower than the \emph{chemical potential} 
-(Fermi energy):
+The response density is expressed as the first-order variation of ground state density
 \be\label{rhodef1}
@@
 \ee
-where the index $p$ labels the occupied state, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi energy.
-Clearly $\dmnot$ commutes with $\hnot$ and in the unperturbed case is a time-independent operator. When the perturbation is switched the system starts to evolve
-and we indicate with $\dm(t)$ the modified density of the perturbed system. We introduce the shorthand notation:
-\be\lb{rhodef2}
-\dm(t)  =  \dmnot + \dm'(t)\;,
+where $\{\psi_p\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi level.
+By considering the linear order time evolution of these states in presence of the perturbation we can express the response density in the $\omega$ domain as follows:
+\be\lb{rhoPrimeOmegaDef1}
+\dm'(\omega) = \ii \commutator{\dmnot}{\op A(\omega)} \;,
 \ee
-where $\dm'(t)$ is called the \emph{response density operator} and represents the time dependent modification of the ground state density induced by the perturbation.
-Here we are assuming that the highest occupied energy level and the lowest unoccupied one will never intersect during the time evolution. Thanks to this condition, the 
-linear response regime the expression of $\dm'(t)$ can be readily derived using equations \eqref{ketBraTimeEvol1} and reads:  
-\be\lb{rhoTimeEvolutionDef3}
-\dm'(t) = \ii \commutator{\dmnot}{\op A(t)} \;.
+where $\op A(\omega)$ is a sum of two terms, both written as a triple convolution with the retarded/advanced Green functions $\op G_0^{\pm}$ of the unperturbed Hamiltonian:
+\be
+\op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
+\op G_0^+(\omega') \left(\op \Phi(\omega)+\op V'(\omega)\right) \op G_0^-(\omega'-\omega)\;. \nn
 \ee
-The equation of motion (Liouville equation) for $\dm'$ is obtained by performing the time derivative of the previous equation. The derivative of $\op A(t)$ can be 
-computed starting from its definition and reads:
-\be
-\d_t\op A(t) = \op\Phi(t) -\ii \commutator{\hnot}{\op A(t)} \nn \;,
-\ee
-and using the Jacobi identity we have:
-\be\lb{LiouvilleRhoDef1}
-\ii \d_t \dm'(t) = \commutator{\op\Phi(t)}{\dmnot} + \ii\commutator{\hnot}{\commutator{\dmnot}{\op A(t)}} = 
-\commutator{\op\Phi(t)}{\dmnot} + \commutator{\hnot}{\dm'(t)} \;.
-\ee
-It is useful to introduce the \emph{Liouvillian} superoperator:
-\be\lb{L0sopDef1}
-\Liouvnot \equiv \commutator{\hnot}{\cdot} \;,
-\ee
-so that the Liouville equation can be written as:
-\be\lb{LiouvilleRhoDef2}
-\ii \d_t \dm'(t) = \Liouvnot \dm'(t) + \commutator{\op\Phi(t)}{\dmnot} \;.
+The presence of the second addend is due to the density dependence of the unperturbed Hamiltonian and describes the perturbation induced by the variation of $\hnot$ under the
+action of the perturbing field. In the linear response regime this quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel 
+(evaluated at $\dm=\dmnot$) times the value of the induced density modification, that is:
+\be\label{VpDef1}
+\op V'(\omega)= 
+\int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
+\trace{\dm'(\omega) \ket{\r} \bra{\r'}} \;.
 \ee
 
-\subsection{Self-consistent Hamiltonians. Generalized Liouville operator}
-
-Let us extend the the former analysis to self-consistent systems, \emph{i.e.} to the case in which the unperturbed Hamiltonian is itself a function of the density.
-In this case the perturbing field $\op\Phi$ has also the effect of adding a further perturbation operator to the perturbing Hamiltonian. In the linear response framework, 
-this latter quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel (evaluated at $\dm=\dmnot$) times the value of the
-induced density modification, that is:
-\be\label{Vptspacedef1}
-\op V'(t)= 
-\int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
-\trace{\dm'(t) \ket{\r} \bra{\r'}} \;.
-\ee
-The Liouville equation for self-consistent systems can be written by adding the contribution of $\op V'$ to $\op\Phi$ in \eqref{LiouvilleRhoDef2}. 
-It reads:
-\be\lb{LiouvilleRhoSelfDef1}
-\ii \d_t \dm'(t) = \Liouvnot \dm'(t) + \commutator{\op V'(t)}{\dmnot} + \commutator{\op \Phi(t)}{\dmnot} \;.
-\ee
-We point out that the response density operator obeys a self-consistent equation, since the  induced perturbing field $\op V'$ is itself a function of $\dm'$. 
-It is possible to formally recast \eqref{LiouvilleRhoSelfDef1} in the same form of \eqref{LiouvilleRhoDef2} by introducing the \emph{coupling}
-superoperator:
-\be\lb{couplingSopDef1}
-\coupl = 
-\int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
-\trace{\cdot \ket{\r} \bra{\r'}} \;,
-\ee
-in this way the first commutator in \eqref{LiouvilleRhoSelfDef1} can be written as the formal action of the coupling superoperator to $\dm'$ and \eqref{LiouvilleRhoSelfDef1}
-can be written as:
-\be\lb{LiouvilleRhoSelfDef2}
-\ii \d_t \dm'(t) = \Liouv \dm'(t) + \commutator{\op \Phi(t)}{\dmnot} \;, \qq
-\Liouv = \Liouvnot + \coupl \;.
-\ee
-
-\subsection{Formulation in the frequency domain}
-
-We reformulate the Liouville equation \eqref{LiouvilleRhoSelfDef2} in the frequency domain. In order to achieve this task it is
-preferable to directly compute the action of the Liouville operator on the Fourier transform of the response density, since in this
-way some subtleties that concerns the analytic structure in the $\omega$ complex plane can be properly taken into account.
-We first define the response density in the frequency domain that, staring from \eqref{rhoTimeEvolutionDef3}, is given by:
-\be\lb{rhoPrimeOmegaDef1}
-\dm'(\omega) \equiv \intover{t} e^{\ii \omega t} \dm'(t)
-= \ii \commutator{\dmnot}{\op A(\omega)} \;,
-\ee
-where $\op A(\omega)$ is The Fourier transform of \eqref{AopDef1} and reads:
-\be \lb{AomegaDef1}
-\op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
-\op G_0^+(\omega') \op \Phi(\omega) \op G_0^-(\omega'-\omega)\;.
-\ee
-The action of $\Liouvnot$ on $\dm'(\omega)$ follows from \eqref{L0sopDef1}:
-\be\lb{LiouvillianRhopomegaDef1}
-\Liouvnot \dm'(\omega) = \ii \commutator{\hnot}{\commutator{\dmnot}{\op A(\omega)}} = 
-\ii \commutator{\dmnot}{\commutator{\hnot}{\op A(\omega)}} \;,
-\ee
-and the commutator between the unperturbed Hamiltonian and $\op A(\omega)$ can be directly computed starting from \eqref{AomegaDef1}: 
-\be
-\commutator{\hnot }{\op A(\omega)} = \bbomega \op A(\omega) - \ii \op \Phi(\omega)\;, \nn
-\ee
-where $\bbomega \equiv \omega + 2\ii\eta$, so that:
-\be\lb{LiouvillianRhopomegaDef2}
-\Liouvnot \dm'(\omega) =  \bbomega\dm'(\omega) + \commutator{\dmnot}{\op\Phi(\omega)}\;.
-\ee
-The coupling superoperator has the same formal action on the response density both in the time and in the frequency domain, so the complete
-Liouville equation in $\omega$ space can be written as:
-\be\lb{LiouvillianRhopomegaDef3}
-\left(\bbomega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;.
-\ee
-
-\section{Critical Analysis of the linear response results}
-
-The main aim of this section is to discuss the reliability in the assessment of the results provided by the linear response formalism. In particular we are interested in 
-analyzing the \emph{linear response functional} defined as:
-\be\lb{LinearResponseFunctDef1}
-{\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
-\ee
-that represents the perturbation-induced modification of the expectation value of an observable $\op O$. Here, for a sake of concreteness, we are limiting our considerations 
-to observables that do not explicitly depend on time.
+\subsection{Fluctuation states. A localization argument for the linear response functional}
 
@@
 \be\lb{fluctuationStateDef1}
-\ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \qq
+\ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \quad
 \bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
 \ee
-where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. An inspection of equation \eqref{ketBraTimeEvol1} 
-evidence that formulas \eqref{fluctuationStateDef1} are equivalent to the action of the $\op Q_0$ projector acting on the time evolution of the (occupied) eigenstates of $\hnot$, written 
-in the $\omega$ domain. Fluctuation states are, by definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
+where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by 
+definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
 \be
@@
 \ee
-Let us further investigate this formula pointing out some of the  computational aspects needed to explicitly perform the scalar products appearing in 
-\eqref{LinearResponseFunctDef2}. 
-We introduce a computational $\mu$-basis, composed by a finite set of $n_\mu$ basis elements $\{\ket{\mu}\}$, and assume that a reliable solution of the ground state problem has 
-been provided in this basis. This means that the feature of the basis (that, for instance, for real space basis are given by the grid spacing and number of points) are chosen so 
-that the coefficients $\brket{\mu}{\psi_p}$ represent a valid discretization of the occupied orbitals. The same can be stated also for the matrix elements $\bra{\mu}\op O\ket{\psi_p}$, 
-under the hypothesis that the observable $\op O$ acts as a local operator on the occupied orbitals.
 
-The formal scalar products that express the linear response functional \eqref{LinearResponseFunctDef1} can be evaluated in the same basis introduced above, that is: 
-\be\lb{LinearResponseFunctDef3}
-{\cal R}_{\op O}(\omega) = 
-\sum_p\sum_\mu\left(\brket{f_p(-\omega)}{\mu}\bra{\mu}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{\mu}\brket{\mu}{f_p(\omega)}\right) \;.
-\ee
-The task of the linear response formalism to provide reliable results for the expectation value of $\op O$ can be reformulated in the problem of finding an accurate and unbiased
-expression for the numerical coefficients appearing in \eqref{LinearResponseFunctDef3}. The features of the computational basis described above ensures that this requirement should
-be satisfied for $\bra{\mu}\op O\ket{\psi_p}$ (and its hermitian conjugates). 
-On the contrary, the problem of the reliable reconstruction of the fluctuation states through the sampling of the coefficients $\brket{f_p(-\omega)}{\mu}$ and $\brket{\mu}{f_p(\omega)}$
-turns out to be highly non-trivial, since the behavior of the fluctuation states strongly depends on $\omega$, as will be readily clarified in the next section.
-
-\subsection{Sternheimer equations and localization properties of the fluctuation states}
-\lb{LocalizationFluctuationStates}
-
-Starting from the Liouville equation \eqref{LiouvillianRhopomegaDef3} it is possible to derive a set of equation of motion for the fluctuation states. 
-The following equations are useful for this task: 
-\begin{align}
-\Liouvnot\dm'(\omega) & = \sum_p\left(-\ketbra{\psi_p}{f_p(-\omega)}\left(\hnot-\eps_p\right) + \left(\hnot-\eps_p\right)\ketbra{f_p(\omega)}{\psi_p}\right) \;, \nn \\
-\coupl\dm'(\omega) &= \commutator{\op V'(\omega)}{\dmnot} = \op Q_0 \op V'(\omega) \dmnot - \dmnot \op V'(\omega) \op Q_0 = \nn \\
-& = \sum_p\left( \op Q_0 \op V'(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op V'(\omega) \op Q_0 \right) \;, \nn \\
-\commutator{\op \Phi(\omega)}{\dmnot} & =  \sum_p\left( \op Q_0 \op \Phi(\omega) \ketbra{\psi_p}{\psi_p} - \ketbra{\psi_p}{\psi_p} \op \Phi(\omega) \op Q_0 \right) \;. \nn
-\end{align} 
-Liouville equation written in this fashion implies the following equations for the fluctuation states, that can be extracted by multiplying from left and right for the 
-occupied eigenstates of $\hnot$:
-\begin{align}\lb{fluctuationStateEqMotion1}
-\left[\bbomega - \left(\hnot-\eps_p\right)\right]\ket{f_p(\omega)} &= \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;, \nn \\
-\bra{f_p(-\omega)}\left[-\bbomega - \left(\hnot-\eps_p\right)\right] &= \bra{\psi_p}\left(\op V'(\omega) + \op \Phi(\omega)\right)\op Q_0 \;.
-\end{align}
-Equations \eqref{fluctuationStateEqMotion1} have the form of a Sternheimer equation. Once projected in the $\{\ket{\mu}\}$ basis, and fixed the value of $\omega$, they can be solved 
-using a self-consistent procedure (add references). This approach provides a direct evaluation of the fluctuation states and thus the linear response functional \eqref{LinearResponseFunctDef3}
-can be computed.
-
-Much more interestingly for the main topic of the present discussion, and regardless from the detailed strategy of their solutions, equations \eqref{fluctuationStateEqMotion1} 
-allow us to present a \emph{localization argument} for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of \eqref{fluctuationStateEqMotion1}, 
-but the same argument holds also for the left ones. We split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term, so that the equation of motion 
-for $\ket{f_p(\omega)}$ is recasted as:
-\be\lb{fluctuationStateEqMotion}
-\left(\bbomega+\eps_p -\op T\right)\ket{f_p(\omega)} = \op V\ket{f_p(\omega)} + \op Q_0\left(\op V'(\omega) + \op \Phi(\omega)\right)\ket{\psi_p} \;.
-\ee
-This equation has the formal structure of an inhomogeneous Helmholtz equation and can be written in the coordinate representation as:
-\be
-\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;, {\rm with} \;\; k^2_p(\omega) = 2(\omega+\eps_p) \;.
-\ee
-The solution of this equation admits an integral representation in the form:
-\be\lb{fluctuationStateIntEq1}
-f_p(\omega,\r) = \int \dd\r' g_H(\r-\r')s(\r') \;,
-\ee
-where $g_H(\r)$ is the Green function of the Helmholtz operator in three dimensions. This integral representation allows us to assess the localization character 
-of the fluctuation states, \emph{i.e.} the behavior of $f_p(\omega,\r)$ when $\r$ becomes large. Indeed, assuming that the support of the source term is compact
-we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing, the leading contribution of the fluctuation states
-is given by:
-\be\lb{fluctuationStateIntEq2}
-f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \simeq 
-e^{-\frac{\eta}{2}|\r|} \frac{e^{\ii \sqrt{k^2_p(\omega)} |\r|}}{|\r|} \;.
-\ee
-We observe that the presence of the regularization parameter $\eta$ ensures a (slow) asymptotic convergence to zero, nonetheless the qualitative $\r$-dependence of the fluctuation 
-states is determined by the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an exponential damping for $\omega < |\eps_p|$ and an oscillating 
-power law behavior for $\omega \geq |\eps_p|$.
-This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef3}, so we conclude that
-the linear response functional is built in terms of localized fluctuation states for $\omega < |\eps_h|$. Instead, in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
-contributions from local and non-local quantities and, finally is composed only by non-local fluctuation states for $\omega\geq|\eps_0|$.
-
-\subsubsection{Criterion for the choice of the computational basis}
-
-The capability of the computational basis to express the results of the linear response can be analyzed using the localization argument previously discussed. 
-The first step needed to address this problem concerns with the evaluation of the reliability of the $\mu$-basis for $\omega=0$, \emph{i.e.} for a perturbing field that does 
-not depend on time. In this case the fluctuation states, as well as the expectation value of a given observable, can be computed performing a ground state calculation in which the perturbing 
-field $\op\Phi$ is added to the external potential of $\hnot$\footnote{We are interested in the linear response, so the magnitude of $\op\Phi$ has to be chosen in a way that respects this 
-regime. To check this point we can compute the perturbation-induced modification of an observable an verify that its value scales linearly with the magnitude of the field}. 
-The goodness of the $\mu$-basis can thus be verified as in the standard ground state calculation, for instance by checking that, given a certain level of completeness of the basis,
-the energy of the occupied (perturbed) orbitals is stable with respect to further refinements.
-
-Once that a basis with acceptable features has been chosen and verified for $\omega=0$ we can reasonably extend its reliability to $\omega>0$ by using the localization argument. 
-Indeed, we have argued that fluctuation states retain a local behavior up to $\omega=|\eps_h|$ and so we can expect that, up to this threshold value, the $\mu$-basis represents an 
-effective tool for a precise discretization of \eqref{LinearResponseFunctDef3}, thus providing a reliable estimate of the linear response.
-
-On the contrary, the situation becomes very less predictable for $\omega$ higher than the threshold $|\eps_h|$ since in this regime the fluctuation states start to delocalize in all the 
-accessible space and the spatial cutoff is provided only by the ground state matrix elements $\bra{\mu}\op O\ket{\psi_p}$.  
-In this case formula \eqref{LinearResponseFunctDef3} provides basis independent results only if the (partial) sampling of the fluctuation states is reconstructed in the domain in which
-$\bra{\mu}\op O\ket{\psi_p}$ are non vanishing. As we shall see through explicit computations this requirement turns out to be quite severe and choices of the basis that provide precise
-results below $|\eps_p|$ fails in the high-$\omega$ regime.
-
-\subsection{Linear response \emph{via} the construction of the excitation operators}
-
-The linear response presented so far is expressed in functions of the fluctuation states, that essentially describe the modification of the occupied eigenstates of $\hnot$ induced by 
-the perturbation. Fluctuation states depend explicitly on the perturbing field $\op\Phi(\omega)$ and, consequently, the analytic structure of the linear response written as in formula 
-\eqref{LinearResponseFunctDef2} emerge through a combination of the $\omega$ dependence of the perturbing field an on the intrinsic response of the system under inspection.
-
-It is however possible to present and equivalent but alternative formulation of the linear response that allows us to express the response density operator in term of the spectral
-decomposition of the Liouville superoperator. This approach naturally leads to the concept of \emph{excitation operators}, defined through a self-consistent operator eigenvalue equation,
-that codify the intrinsic capability of the system to respond to an arbitrary perturbation. Excitations behave as singularity of the response density operator and their knowledge provides a 
-deeper insight into the analytic structure of the linear response.
-
-The material presented in this section discusses a complete re-derivation of the linear response written in terms of excitation operators. Moreover, we will evidence that a \emph{localization 
-argument}, analogous to the one presented in section \ref{LocalizationFluctuationStates} for the fluctuation states, holds also for the excited states of the systems below a specific energetic
-threshold. This analysis has relevant consequence both under theoretical and computational point of view. Indeed, it provides a deeper understanding in the role of both localized and de-localized 
-excitations in determining the analytic structure of the linear response and it gives us clear indication in the level of refinement of the computational setup needed to obtain reliable results 
-from a linear response calculation.
-
-\subsubsection{Explicit sampling of the empty-states subspace}
-
-We now introduce the notion of $\alpha$-basis, that is a set of orthonormal vectors $\{\ket{\psi(\alpha)}\}$ that form a basis in the subspace of the empty-states, \emph{i.e.} in the subspace 
-orthogonal to the occupied eigenstates of $\hnot$. The elements of this set satisfy, by definition, the following orthonormality relation: 
-\be\lb{psiAlphaDef1}
-\brket{\psi(\alpha)}{\psi_p} = \brket{\psi_p}{\psi(\alpha)} = 0 \;, \qq
-\brket{\psi(\alpha)}{\psi(\beta)} = \delta(\alpha-\beta) \;,
-\ee
-where we have parametrized the basis element through the multi-index $\alpha$, in the sense described in \ref{BasicDef}, since the associated vector can describe both a localized or a 
-de-localized state. The $\op Q_0$ projector as well as the completeness relation can be easily written in function of this basis: 
-\be\lb{psiAlphaQ0}
-\op Q_0 = \sint\dd\alpha\ketbra{\psi(\alpha)}{\psi(\alpha)} \;, \;\; 
-\identity = \sum_p\ketbra{\psi_p}{\psi_p} + \sint\dd\alpha\ketbra{\psi(\alpha)}{\psi(\alpha)} \;.
-\ee
-The $\alpha$-basis, defined through equations \eqref{psiAlphaDef1} and \eqref{psiAlphaQ0}, formally spans an infinite dimensional domain. However, for obvious computational reason it is 
-interesting to express the $\{\ket{\psi(\alpha)}\}$ in the same $\mu$-basis used to perform the ground states calculations. The discretization conditions imposed by the $\mu$-basis reduce 
-the $\{\ket{\psi(\alpha)}\}$ to a finite dimensional set. The dimension $n_\alpha$ of the basis can be computed by subtracting to the $n_\mu$ degrees of freedom the $n_{occ}$ constraints 
-needed to imposes the orthonormality of the $\{\ket{\psi(\alpha)}\}$ to the occupied states, so that $n_\alpha=n_\mu-n_{occ}$.
-
-\vspace{0.4cm}
-\emph{Quality assessment of the reduced $\alpha$-basis}
-\vspace{0.4cm}
-
-When the sampling of the empty state subspace is needed to perform practical calculations in realistic systems the construction of a complete $\alpha$-basis typically turns out to be 
-computationally unaffordable. In these cases it is possible to introduce a \emph{reduced} basis, denoted as $r\alpha$-basis, composed of a subset of dimension $n_{r\alpha}$ of the 
-$\{\ket{\psi(\alpha)}\}$ elements of the complete basis.
-
-The capability of the reduced basis to express the results of the linear response can be evaluated by using the results of a ground state calculation in which the time-independent 
-perturbing field $\op\Phi$ is added to the external potential of $\hnot$. We denote with $\ket{\psi_p^\Phi}$ the occupied eigenstate of the perturbed Hamiltonian and, using the 
-completeness relation of \eqref{psiAlphaQ0}, we can write the following expansion:
-\be\lb{PertPsiExpansion1}
-\ket{\psi_p^{\Phi}} = \sum_q a_{pq}\ket{\psi_q} + \sint\dd\alpha \,a_{p\alpha}\ket{\psi(\alpha)} \;,
-\ee
-where $a_{pq} = \brket{\psi_q}{\psi_p^{\Phi}}$ and $a_{p\alpha} = \brket{\psi(\alpha)}{\psi_p^{\Phi}}$. Equation \eqref{PertPsiExpansion1} holds exactly since the sum over the empty states
-is extended to the complete $\alpha$-basis. Taking the norm of $\ket{\psi_p^\Phi}$ and summing over $p$ provides:
-\be\lb{PertPsiExpansion2}
-n_{occ} = \sum_{pq} |a_{pq}|^2 + \sum_p\sint\dd\alpha\,|a_{p\alpha}|^2 \;,
-\ee
-the two addend of this equation measure the distribution of the total electronic charge of the perturbed system between the occupied and empty subspaces. Furthermore, we can use
-equation \eqref{PertPsiExpansion2} to build an estimator $C(n_{r\alpha})$ of the capability of the $r\alpha$-basis to describe the modification of the ground state density induced 
-by the time-independent perturbation. We define this estimator as follows:
-\be\lb{Cestimator1}
-C(n_{r\alpha}) = 1 - \frac{\sum_p\sum_\alpha^{n_{r\alpha}}|a_{p\alpha}|^2}{n_{occ} - \sum_{pq} |a_{pq}|^2} \;,
-\ee
-$C(n_{r\alpha})$ is by construction a positive function with values between 1, achieved when the sampling of the empty-states subspace is absent and 0, obtained when the reduced basis
-is complete. The normalization adopted in \eqref{Cestimator1} ensures that $C(n_{r\alpha})$ is an intensive estimator, so that its value does not depend on the number of occupied
-orbitals of the system.
-
-\subsubsection{Linear response in the basis of transitions}
-
-The defining equation of the linear response can be reformulated using the explicit sampling of the empty states defined above. The fundamental observation on the basis
-of this procedure regards the fact that both the response density operator \eqref{rhoPrimeOmegaDef1} and all the operators appearing in the Liouville equation 
-\eqref{LiouvillianRhopomegaDef3} are expressed as a commutator with $\dmnot$. This observation implies that all the operators $\op O$ appearing in the contest of the linear 
-response satisfy the formal relation:
-\be
-\op O = \dmnot\op O\op Q_0 + \op Q_0\op O\dmnot \;.
-\ee
-Plugging the operator expression of $\dmnot$ and $\op Q_0$ in terms of basis vector in the occupied and empty subspace provides:
-\be\lb{OperatorTransBasisExpDef1}
-\op O = \sum_p\sint \dd \alpha\left(
-\excite{p}{\alpha}\trace{\decay{\alpha}{p}\op O} + \decay{\alpha}{p}\trace{\excite{p}{\alpha}\op O}
-\right) \;,
-\ee
-where we have defined the \emph{transition operators}:
-\be
-\excite{p}{\alpha} \equiv \ketbra{\psi(\alpha)}{\psi_p}\;, \qq
-\decay{\alpha}{p} \equiv \ketbra{\psi_p}{\psi(\alpha)} \;,
-\ee
-that thanks to \eqref{psiAlphaDef1} satisfy the orthonormality conditions:
-\be\lb{transitionOpOrthonormalityDef1}
-\trace{\excite{p}{\alpha}\excite{q}{\beta}} = \trace{\decay{\alpha}{p}\decay{\beta}{q}} = 0 \;, \qq
-\trace{\excite{p}{\alpha}\decay{\beta}{q}} = \delta_{pq}\delta(\alpha-\beta) \;.
-\ee
-Here we are assuming that the complete $\alpha$-basis is used, so the operator expansion in the basis of transition \eqref{OperatorTransBasisExpDef1} is exact. The effect of
-the adoption of a reduced basis will be analyzed when needed. 
-In order to recast this expansion in a simpler expression it turns out to be useful to define the rank-2 row vectors of the transition basis: 
-\be
-\sbra{p\alpha}{\cdot} \equiv 
-\mat{ \excite{p}{\alpha} \;, & \decay{\alpha}{p} }\;,
-\ee
-and we also introduce a vectorial notation to deal with the coefficients of the expansion of an operator in the transition basis, that is: 
-\be\lb{OperatorTransitionCoeffDef1}
-\sket{p\alpha}{\op O}  \equiv \mat{ \trace{\decay{\alpha}{p}\op O } \\ 
-\trace{\excite{p}{\alpha}\op O}} \; .
-\ee
-Thanks to this formalism we have that equation \eqref{OperatorTransBasisExpDef1} can be expressed as:
-\be\lb{OperatorTransBasisExpDef2}
-\op O = \sum_p\sint \dd \alpha \sbra{p\alpha}{\cdot}\sket{p\alpha}{\op O} = 
-\dbraket{\cdot}{\op O} \;,
-\ee
-where the last equality implicitly define the ulterior compact notation of the ``big-shaped'' vectors in which the summed indexes are omitted.  
-In the same fashion it will be also useful for the subsequent analysis to introduce a conjugate notation, in which the basis operators are expressed
-as column vector and the coefficients of the expanded operator as row ones, that is: 
-\be\lb{TransitionBasisConjugateDef1}
-\sket{p\alpha}{\cdot} \equiv 
-\mat{\decay{\alpha}{p} \\  \excite{p}{\alpha}} \;, \qq
-\sbra{p\alpha}{\op O}  \equiv 
-\mat{ \trace{\excite{\alpha}{p}\op O } \;, & \trace{\decay{p}{\alpha}\op O} }
-\;,
-\ee
-where the flip in the role of $\op e$ and $\op d$ in \eqref{TransitionBasisConjugateDef1} follows from the properties of excitation and decay operators
-under hermitian-conjugate operation. The expansion of an operator in the transition basis using the conjugate description reads: 
-\be\lb{OperatorTransBasisConjugateExpDef1}
-\op O = \sum_p\sint \dd \alpha \sbra{p\alpha}{\op O}\sket{p\alpha}{\cdot} = 
-\dbraket{\op O}{\cdot} \;.
-\ee
-The Liouville equation \eqref{LiouvillianRhopomegaDef3} can be consistently written in the transition basis where it becomes a linear matrix equation for the 
-rank-2 vectors of the coefficients \eqref{OperatorTransitionCoeffDef1} of the operators in its left and right side, that is:
-\be\lb{LiouvillianRhopomegaDef4}
-\omega\mat{ \trace{\decay{\alpha}{p}\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\dm'(\omega)}} - 
-\mat{ \trace{\decay{\alpha}{p}\Liouv\dm'(\omega)} \\ \trace{\excite{p}{\alpha}\Liouv\dm'(\omega)}} =
-\mat{ \trace{\decay{\alpha}{p}\opskew{\Phi}(\omega)} \\ \trace{\excite{p}{\alpha}\opskew{\Phi}(\omega)}}
-\;,\nn
-\ee
-where we have introduced a compact notation to deal with the commutator of on operator with the unperturbed density: 
-\be
-\opskew{O} = \commutator{\op O}{\dmnot}\;.
-\ee
-The second addend in the l.h.s of \eqref{LiouvillianRhopomegaDef4} can be further analyzed by writing the transition basis expansion of $\dm'$ inside the traces. 
-Performing this procedure we can recast this quantity as the action of a 2-dimensional matrix on the rank-2 vector of the response density. So we have: 
-\be\lb{LiouvilleTransBasisDef1}
-\sum_q\sint\dd\beta \left[\omega\delta_q^p\delta(\alpha-\beta)- \optr{L}^{p \alpha}_{q\beta} \right]\sket{q\beta}{\dm'(\omega)} =
-\sket{p\alpha}{\opskew{\Phi}(\omega)} \;.
-\ee
-with:
-\be\lb{LiouvilleMatrixTransBasisDef1}
-\optr{L}^{p \alpha}_{q\beta} \equiv \mat{\trace{\decay{\alpha}{p}\, \Liouv\, \excite{q}{\beta}} &
-\trace{\decay{\alpha}{p}\, \Liouv\, \decay{\beta}{q}} \\
-\trace{\excite{p}{\alpha}\, \Liouv\, \excite{q}{\beta}} &
-\trace{\excite{p}{\alpha}\, \Liouv\, \decay{\beta}{q}}} \;.
-\ee
-
-\subsubsection{Spectral decomposition of the response density in the transitions basis. Definition of excitation operators}
-
-The formulation of the Liouville equation in the basis of transitions is the starting point for the derivation of the spectral decomposition of the response density operator
-in terms of the eigenvectors if the Liouville operator. The first step in the achievement of this result is provided by the construction of the eigenvectors of the matrix 
-\eqref{LiouvilleMatrixTransBasisDef1}. Following the notation previously defined we introduce the rank-2 vectors $\sket{p\alpha}{E}$ and $\sbra{p\alpha}{\tilde E}$ that represent, 
-by definition, the right and left eigenvectors $\optr{L}$, respectively, so that:
-\be\lb{LiouvMatrixEigenvectorDef1}
-\sum_q \sint \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q \beta}{E} = E \sket{p\alpha}{E} \;, \quad
-\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \optr{L}^{p \alpha}_{q\beta} = E \sbra{q\beta}{\tilde E}\;.
-\ee
-In general, left and right eigenvectors do not coincide, but it is always possible to choose they normalization so that a orthonormality conditions among the
-elements of left and right spaces holds, namely:
-\be\lb{ExcitationOrthonormalityDef1}
-\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E}\sket{p\alpha}{E'} \equiv \dbraket{\tilde E}{E'} = \delta(E-E') \;.
-\ee
-Once that the eigenvectors are known, the spectral decomposition of the resolvent of $\optr{L}$ can be provided:  
-\be
-\left[\left(\bbomega-\optr{L}\right)^{-1}\right]^{p\alpha}_{q\beta} =\sint\dd E
-\frac{\sket{p\alpha}{E}\sbra{q\beta}{\tilde E}}{\bbomega-E} \;,
-\ee
-so equation \eqref{LiouvilleTransBasisDef1} can be inverted and we obtain the response density written in basis of transition, in the form:
-\be\lb{RhopExcitationTransBasisDef1}
-\sket{p\alpha}{\dm'(\omega)} = 
-\sint\dd E \sket{p\alpha}{E}
-\frac{\dbraket{\tilde E}{\opskew{\Phi}(\omega)}}{\bbomega-E} \;.
-\ee
-%\subsubsection{Definition of excitation operators}
-It is possible to express formula \eqref{RhopExcitationTransBasisDef1} as a true operator equation. First of all we show that the rank-2 vectors $\sket{p\alpha}{E}$ 
-and $\sbra{p\alpha}{\tilde E}$ can be interpreted as the transition basis coefficients of the right and left \emph{eigenstates} of the Liouville superoperator.   
-In order to do so we introduce the explicit representation of the eigenvectors op $\optr{L}$:
-\be\lb{XYcoeffDef1}
-\sket{p\alpha}{E} \equiv \mat{X_E^{p\alpha} \\ Y_E^{p\alpha}} \;, \qq
-\sbra{p\alpha}{\tilde E} \equiv \mat{\tilde X_{E\,p\alpha} & \tilde Y_{E\,p\alpha}} \;,
-\ee
-and, on the basis of these elements, we define the \emph{excitation operators}:
-\begin{align}\lb{ExctitationOperatorsDef1}
-\op E &\equiv \dbraket{\cdot}{E} = 
-\sum_p \sint \dd \alpha \left(\excite{p}{\alpha} X_E^{p\alpha} + \decay{\alpha}{p} Y_E^{p\alpha}\right) 
-\;,\nn \\
-\op{\tilde E} &\equiv \dbraket{\tilde E}{\cdot} = \sum_p \sint \dd \alpha \left(\decay{\alpha}{p} \tilde X_{E\,p\alpha} + 
-\excite{p}{\alpha}\tilde Y_{E\,p\alpha}  \right)\;.
-\end{align}
-The orthonormality condition \eqref{ExcitationOrthonormalityDef1} implies that:
-\be
-\trace{\op{\tilde E} \op E'} = \sum_p\sint \dd\alpha \left(\tilde X_E^{p\alpha} X_{E'\,p\alpha} +
-\tilde Y_E^{p\alpha} Y_{E'\,p\alpha}\right) = \delta(E-E') \;. 
-\ee
-Excitation operators are the right and left eigenvectors of the Liouville superoperator, as directly follows from their
-definition. Indeed for $\op E$ we have:
-\begin{align}\lb{opEeigenvalueDef1}
-\Liouv \op E & = \sum_p \sint \dd \alpha \left(\trace{\decay{\alpha}{p} \Liouv \op E} \excite{p}{\alpha} + 
-\decay{\alpha}{p} \trace{ \excite{p}{\alpha} \Liouv \op E}  \right) = \nn \\
-&= \sum_p \sint  \dd \alpha \sbra{p\alpha}{\cdot} \sum_q \sint  \dd \beta \optr{L}^{p \alpha}_{q\beta} \sket{q\beta}{E} 
-= E \sum_p \sint \dd \alpha \sbra{p\alpha}{\cdot} \sket{p\alpha}{E} = E \, \op E \;,	
-\end{align}
-whereas the left action on $\op{\tilde E}$ provides:
-\begin{align}\lb{optildeEeigenvalueDef1}
- \op{\tilde E} \Liouv &=  \sum_p \sint \dd \alpha \left(
-\trace{\op{\tilde E}\Liouv\excite{p}{\alpha}}\decay{\alpha}{p} +  
-\trace{\op{\tilde E}\sop{\mathcal L}\decay{\alpha}{p}} \excite{p}{\alpha} \right) = 
-\nn \\ &= \sum_p \sint  \dd \alpha  \sum_q \sint  \dd \beta
-\sbra{q\beta}{\tilde E}\optr{L}^{q\beta}_{p\alpha}\sket{p\alpha}{\cdot} = 
-E\sum_p \sint \dd \alpha \sbra{p\alpha}{\tilde E} \sket{p\alpha}{\cdot}  =
-E \op{\tilde E} \;.
-\end{align}
-The introduction of the excitation operators allows us to provide a complete operator version of equation \eqref{RhopExcitationTransBasisDef1}, that is:
-\be\lb{RhopExcitationDef1}
-\dm'(\omega) = \dbraket{\cdot}{\dm'(\omega)} =
-\sint\dd E \op E
-\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \;,
-\ee
-where the algebraic equivalence between the trace written in \eqref{RhopExcitationDef1} and the numerator of \eqref{RhopExcitationTransBasisDef1}
-can be easily proved.
-
-Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitation operators. Now 
-we are interested in analyzing this restatement of the linear response under the perspective of the main topic of the paper, namely the critical assessment 
-of the results provided by the linear response formalism in a given computational setup. Our interests are mainly twofold. First, to analyze the localization 
-properties of the excitations, in a analogous fashion of what done in section \ref{LocalizationFluctuationStates} for the fluctuation states. Second, to determine 
-the precise nature of the formal sum over excitations written in \eqref{RhopExcitationDef1}, in order to be able to discriminate between the discrete and the 
-continuum sector of the excitation spectrum.
-
-\subsubsection{Excitation expansion of the fluctuation states. A localization argument for the excited states}
-
-%Thanks to the usage of the basis of transition, we have been able to express the response density as a linear superposition of excitations $\op E$. Now
-We push this formalism a little bit forward and derive the expansion of the fluctuation states \eqref{fluctuationStateDef1} in terms of the \emph{excited states} of the 
-system . Firstly, we introduce excited states, defined via the linear combination of the elements of the $\alpha$-basis with the coefficients that appears in 
-\eqref{XYcoeffDef1}, that is:
-\begin{align}\lb{ExcitedStatesDef1}
-\ket{\phi^E_p} &\equiv \sint \dd \alpha X_{E}^{p \alpha} \ket{\psi(\alpha)} &
-\tbra{\phi^E_p} &\equiv \sint \dd \alpha {\tilde X_{E}^{p \alpha}} \bra{\psi(\alpha)} \;, \nn\\
-\bra{\chi^E_p} &\equiv \sint \dd \alpha  Y_{E}^{p \alpha} \bra{\psi(\alpha)} &
-\tket{\chi^E_p} &\equiv \sint \dd \alpha {\tilde Y}_{E}^{p\alpha} \ket{\psi(\alpha)} \;,
-\end{align}
-due to these definitions we can express excitation operators as follows:
-\be\lb{ExcitationOperatorsDef2}
-\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \qq
-\op {\tilde E} = \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
-\ee
-Formulas \eqref{ExcitationOperatorsDef2} provides a clear representation of the physical meaning of excited states \eqref{ExcitedStatesDef1}, as can be seen by applying
-the excitation operators on the occupied eigenstates of the systems:
-\be
-\op E\ket{\psi_p} = \ket{\phi^E_p} \;, \quad \bra{\psi_p} \op E = \bra{\chi^E_p} \;, \quad
-\op {\tilde E}\ket{\psi_p} = \tket{\chi^E_p} \;, \quad \bra{\psi_p} \op {\tilde E} = \tbra{\phi^E_p} \;.
-\nn
-\ee
-The excited states expansion of fluctuation states can be easily derived.  Indeed an inspection of formula \eqref{rhoPrimeFluctuationStateDef1} show that fluctuation 
-states can be extracted from the response density operator as follows:
-\be
-\ket{f_p(\omega)} = \dm'(\omega)\ket{\psi_p} \;, \qq
-\bra{f_p(-\omega)} = \bra{\psi_p}\dm'(\omega) \;, \nn
-\ee
-so plugging the expression \eqref{ExcitationOperatorsDef2} inside \eqref{RhopExcitationDef1} and applying the response density to a occupied state provides:
-\be\lb{FluctStateExcitationDef1}
-\ket{f_p(\omega)} = \sint\dd E \frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \ket{\phi^E_p} \;, \qq
-\bra{f_p(-\omega)} = \sint\dd E \bra{\chi^E_p}\frac{\trace{\op{\tilde E}\opskew{\Phi}(\omega)}}{\bbomega-E} \;.
-\ee
-Fluctuation states emerge as a linear superposition of excited states. The $\omega$-dependent coefficients codify the effect of the perturbing field in determining the 
-relative contribution of each addend through the weighting coefficients in the numerators of \eqref{FluctStateExcitationDef1}.
-
-We perform a particular choice of the perturbing field:
-\be
-\op\Phi = \commutator{\op E}{\dmnot} \; \longrightarrow \; \opskew{\Phi} = 
-\commutator{\commutator{\op E}{\dmnot}}{\dmnot} = \op E
-\ee
-...to be continued...we have to state precisely the time-dependence of $\hone{t}$...
-
-\subsubsection{Sternheimer equation for excited states. Localization argument revisited}
-
-The operator eigenvalue equations \eqref{opEeigenvalueDef1} and \eqref{optildeEeigenvalueDef1} can be translated into a Schroedinger-like equations
-for the excitonic states.
-
-\vspace{0.5cm}
-\emph{Equations for $\coupl = 0$}
-\vspace{0.5cm}
-
-\noindent In this case the $\optr{L}_{q\beta}^{p\alpha}$ matrix has only diagonal non-vanishing elements, given by: 
-\be
-\trace{\decay{\alpha}{p}\Liouv\excite{q}{\beta}} = H_{0\alpha\beta}\delta_{pq} - \eps_p\delta_{pq}\delta(\alpha-\beta) \;, \qq
-\trace{\excite{\alpha}{p}\Liouv\decay{q}{\beta}} = \eps_p\delta_{pq}\delta(\alpha-\beta) - H_{0\beta\alpha}\delta_{pq} \;, 
-\ee
-where $H_{0\alpha\beta} = \bra{\psi(\alpha)}\hnot\ket{\psi(\beta)}$. The eigenvalue conditions \eqref{LiouvMatrixEigenvectorDef1} imply
-that the $Y$ and $\tilde Y$ coefficients introduced in \eqref{XYcoeffDef1} vanish so that both $\tket{\chi^E_p}$ and $\bra{\chi^E_p}$ do not
-contribute to the excitation operators \eqref{ExcitationOperatorsDef2}. The eigenvalue operator equation for $\op E$ reduces to:
-\be
-\sum_q\left(\hnot - \eps_q\right)\ket{\phi^E_q}\bra{\psi_q} = E \sum_q \ket{\phi^E_q}\bra{\psi_q} \;,
-\ee
-and projecting on $\ket{\psi_q}$ provides the eigenvalue condition for the excitonic state $\ket{\phi^E_p}$:
-\be
-\left(\hnot - \eps_p\right)\ket{\phi^E_p} = E \ket{\phi^E_p} \;.
-\ee
-In the same way, by using the eigenvalue condition for $\op{\tilde E}$, we can derive an analogous equation for $\tbra{\phi^E_p}$. To achieve this
-result we need the expression of the left action of the (unperturbed) Liouville superoperator defined in \eqref{L0sopDef1}, that can be derived by
-observing that:
-\be\lb{leftActionLouv0Def1}
-\trace{\op O' (\Liouvnot \op O)} = \trace{(\op O' \Liouvnot) \op O } =
-\trace{\commutator{\op O'}{\op H_0} \op O} \quad \Rightarrow \quad \op O \Liouvnot = 
-- \Liouvnot \op O \;.
-\ee
-So, the eigenvalue operator equation for $\op{\tilde E}$ provides:
-\be
-\sum_q  \ket{\psi_q} \tbra{\phi^E_q} \left( \hnot - \eps_q \right) =
-E \sum_q  \ket{\psi_q} \tbra{\phi^E_q} \;,
-\ee
-so that:
-\be
-\tbra{\phi^E_p} \left( \hnot - \eps_p \right) = E \tbra{\phi^E_p} \;.
-\ee
-So we find that the excitonic states are the left and right eigenvectors of $\hnot$ (that actually coincide since we are considering
-hermitian Hamiltonians). The energy eigenvalue is shifted by $\eps_p$, that is the energy of the occupied states involved in the 
-excitation.
-
-A last interesting comment regards the expression of the response density when the excitation operator $\op E$ itself is used as the source of the
-perturbation. In this case, denoting as $\op E'$ the given perturbing excitation, it is easy to see that:
-\be
-\trace{\op{\tilde E}\commutator{\op E'}{\dmnot}} = \trace{\op{\tilde E}\op E'} = \delta(E-E') \;, \nn 
-\ee
-and the response density generated by this perturbation is given by: 
-\be
-\dm'(\omega) = \frac{1}{\bbomega - E'} \op E'\;,
-\ee
-which represents a monochromatic term of energy $E'$. Under this perspective we can state that excitations constitute
-the \emph{resonant channels} for the construction  of the response density.
-
-\vspace{0.5cm}
-\emph{Generic equations for $\coupl \neq 0$}
-\vspace{0.5cm}
-
-To explicitly write the generic eigenvalue equations for the excitonic states it is useful to introduce some further formalism to express the 
-self-consistent part of the perturbing Hamiltonian \eqref{Vptspacedef1}. We start by expanding $\op V'$ in the coordinate representation, that is:
-\be
-\op V'(t)= 
-\int \dd \br \dd \br' \dd \r \dd \r' \bra{\br'}\frac{\delta\hnot}{\delta \rho_0(\r,\r')}\ket{\br}
-\trace{\dm'(t) \ket{\r} \bra{\r'}} \ketbra{\br'}{\br}\;, \nn
-\ee
-then we introduce the \emph{coupling kernel}, defined as:
-\be\lb{couplingKernelDef1}
-U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
-} \trace{\op O' \ket{\r} \bra{\r'}} \;,
-\ee
-using this quantity we can express $\op V'$ as:
-\be\lb{Vptspacedef2}
-\op V'(t)= 
-\int \dd \br \dd \br' U\left[\ketbra{\br}{\br'};\dm'(t)\right] \ketbra{\br'}{\br}\;,
-\ee
-and consequently the formal action of the coupling superoperator \eqref{couplingSopDef1} on a generic operator $\op O$ can be expressed as: 
-\be\lb{couplingSopDef2}
-\coupl\op O = 
-\int \dd \r \dd \r' \commutator{\ketbra{\r'}{\r}}{\dmnot} U\left[\ketbra{\r}{\r'};\op O\right] \;.
-\ee
-Using this formalism we can define the left action of the coupling superoperator, in analogous way of what done in \eqref{leftActionLouv0Def1}, 
-that is:
-\begin{align}\lb{leftActionCouplingDef1}
-\trace{\op O' (\coupl \op O)} &= \int \dd\r\dd\r'\trace{\ketbra{\r'}{\r}\commutator{\dmnot}{\op O'}}
-U\left[\ketbra{\r}{\r'};\op O\right]  = \nn \\ &= 
-U\left[\commutator{\dmnot}{\op O'};\op O\right] \doteq \trace{(\op O' \coupl) \op O } \;,
-\end{align}
-where the second equality follows from the linearity of the coupling kernel. The right action of the coupling superoperator consistent with this result is:
-\be\lb{leftActionCouplingDef2}
-(\op O \coupl) = \int \dd\r\dd\r'
-U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;.
-\ee
-This formalism allows us to provide a compact expression for the action of the Liouville superoperator on the excitation operators. For the left action we have:
-\begin{align}
-\Liouv\op E &= \sum_p\left(\hnot-\eps_p\right)\ketbra{\phi^E_p}{\psi_p} - \sum_p\ketbra{\psi_p}{\chi^E_p}\left(\hnot-\eps_p\right) + \nn \\
-&+ \sum_p \sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ketbra{\psi(\alpha)}{\psi_p}
-- \sum_p \sint \dd\alpha U\left[\excite{p}{\alpha}; \op E\right] \ketbra{\psi_p}{\psi(\alpha)} = E\op E \;, \nn
-\end{align}
-here the action of the coupling superoperator on $\op E$ has been computed imposing its expansion in the transition basis and computing the coefficients with formula 
-\eqref{leftActionCouplingDef1}. Projecting out the previous equation by multiplication with an occupied eigenstates from both the left and right provides the equations:
-\begin{align}\lb{PhipChipEqDef1}
-\left(\hnot-\eps_p\right)\ket{\phi^E_p} +\sint \dd\alpha  U\left[\decay{\alpha}{p}; \op E\right] \ket{\psi(\alpha)} &= E\ket{\phi^E_p} \;,\nn \\
-\bra{\chi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\excite{p}{\alpha}; \op E\right] &= -E\bra{\chi^E_p} \;.
-\end{align}
-We observe that the coupling kernel behaves as a (non-local) potential that depends on both the $X_{E}^{p \alpha}$ and $Y_{E}^{p \alpha}$ coefficients of \eqref{ExcitedStatesDef1}
-thus introducing a coupling between the $\phi$ and $\chi$ states.
-
-In the same way the right action provides:
-\begin{align}
-\op{\tilde E}\Liouv &= \sum_p\tketbra{\psi_p}{\phi^E_p}\left(\hnot-\eps_p\right) - \sum_p\left(\hnot-\eps_p\right)\tket{\chi^E_p}\bra{\psi^E_p} + \nn \\
-&+ \sum_p \sint \dd\alpha  U\left[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}\right] \ketbra{\psi(\alpha)}{\psi_p}
-+ \sum_p \sint \dd\alpha U\left[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}\right] \ketbra{\psi_p}{\psi(\alpha)} = E\op{\tilde E} \;, \nn
-\end{align}
-so that:
-\begin{align}\lb{TildePhipChipEqDef1}
-\tbra{\phi^E_p}\left(\hnot-\eps_p\right) +\sint \dd\alpha \bra{\psi(\alpha)} U\left[\commutator{\dmnot}{\op{\tilde E}};\excite{p}{\alpha}\right]  &= E\tbra{\phi^E_p} \;,\nn \\
-\left(\hnot-\eps_p\right)\tket{\chi^E_p} -\sint \dd\alpha \bra{\psi(\alpha)} U\left[\commutator{\dmnot}{\op{\tilde E}};\decay{\alpha}{p}\right] &= -E\tket{\chi^E_p} \;.
-\end{align}
-
-\subsubsection{Excitation expansion of the linear response functional}
-
-We have that:
-\be
-\sket{p\alpha}{\commutator{\op\Phi(\omega)}{\dmnot}} = \sum_q\sint\dd\beta\, \optr{J}^{p\alpha}_{q\beta}
-\sket{q\beta}{\op\Phi(\omega)} \;\;, \;{\rm with} \;\;
-\optr{J}^{p\alpha}_{q\beta} = \delta_{pq}\delta(\alpha-\beta)\mat{1 & 0 \\ 0 & -1}
-\ee
-and the linear response functional \eqref{LinearResponseFunctDef1} can be written as:
-\be
-{\cal R}_{\op O}(\omega) = 
-\sint\dd E \dbraket{\op O}{E}
-\frac{\dbra{\tilde E}\optr{J}\dket{\op\Phi(\omega)}}{\bbomega-E} \;.
-\ee
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% \section{Draft of the paper - old notes}
-% 
-% \begin{itemize}
-% \item Aim of the paper: Compute the electronic properties of a molecular system with the formalism of linear scaling using a LR-TDDFT inside BigDFT code. 
-% %We also want to define a set of computational tools that allow to check the reliability of the computation.  
-% \end{itemize}
-% 
-% \begin{itemize}
-% \item Motivation: the DFT code have reached reliable features of precision for the computation of the GS.
-The same probletic are instead needed in order to achieve the same type of results for spectroscopic
-% properties in large systems
-% \begin{itemize}
-% \item Quantify the impact of several modelling of a given systems (environment, disorder)
-% \item Systematic approach has proven its effectiveness for GS calculations (easy to handle)~\cite{deltatest2016}.
-The quality of localized basis function is therefore easy to quantify (variational theorem)
-% \item A challenge is represented by large scale computation for \emph{molecular} systems
-% \end{itemize}
-% \item State-of-the-art 
-% \begin{itemize}
-% \item localized basis set for representing the Hamiltonians (e.g. Fiesta (Blase, Olevano), FHI-Aims, GWMol)
-% \item This approach has been also generalized to LR calculation in the case of ONETEP \cite{Ratcliff2013}.
-However little is said about the reliability of the results in terms of the convergence of the spectra
-% \end{itemize}
-% \item Content of the paper: 
-% \begin{itemize}
-% \item Brief illustration of the support function approach in wavelets (Large systems are  accessible for the structure (Energy, Forces,\ldots)
-% \item We want to exploit the wavelet properties in the context of LR, \emph{by also providing some criteria} which may be of interest for the evaluation of the quality of the LR results.
-% \end{itemize}
-% \item Conclusions and implications
-% \begin{itemize}
-% \item We might apply this formalism also in the contect of MBPT and inspect the validity of the linear response functional for e.g.
-GW calcualtions (the perturbation operator will be different from the dipole)
-% \end{itemize}
-% \end{itemize}
-
-%\bibliographystyle{alpha}
-%\bibliography{sample}
+\bibliography{Analytic_biblio}
 

### 2018-03-07 AnalyticStructure_main.tex
update

@@
 \begin{abstract}
-By performing linear-response (LR)-TDDFT calculation of molecular systems within a highly complete real-space basis set, we analyze how the behavior of the dynamical 
-polarizability is influenced by the discretization conditions of the computational treatment.
-We show that optical excitations of energy below the LR ionization potential behave as observable, localized quantities, that can be studied with high precision, 
-provided an adequate level of completeness. We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
-in any discretization scheme. Under this light, we also show that excitation energies above ionization threshold do not exhibit such observable features and \emph{cannot} be 
-considered as poles of the dynamical polarizability. This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
+We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
+In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems. We show that optical excitations of energy below the LR ionization potential 
+behave as observable, localized quantities, that can be computationally calculated with high precision, provided an adequate level of completeness.
+Above this energy threshold, the analytic structure of the susceptibility functional might be separated in two sectors: one can still be described in terms of observable excitation 
+with discrete energies, that can be captured within computational setups tailored for localized states. However such excitations are embedded in a continuum of excited states 
+that, on the contrary, behave as plane waves and cannot be described efficiently by the same computational techniques. Such excitations do not exhibit observable features and 
+\emph{cannot} be considered as poles of the dynamical polarizability. Nonetheless, the contribution of such continuum of excitation reveals to be of paramount importance even 
+for expressing LR quantities in the infrared regime like for example static polarizability.
+This is particularly evident for small molecules; we show how these considerations might be influenced by the size of molecular system.
+We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
+in any discretization scheme.  This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
 unoccupied subspace.
@@
 
-In the framework of the linear response formalism one is typically interested in computing the \emph{linear response functional}:
+Linear response can be effectively applied to the analysis of the electronic excitations in molecular and condensed-matter systems. In this framework one consider a system 
+described by the Hamiltonian $\hnot$ and assume that the ground-state density $\dmnot$ has been provided. Linear response formalism allows us to evaluate the modification 
+of the expectation value of a generic observable induced by a time-dependent perturbation acting on the system. This quantity, written in the frequency domain, can be expressed 
+through the evaluation of the \emph{linear response functional}:
 \be\lb{LinearResponseFunctDef1}
@@
 \ee
-that represents the perturbation-induced modification of the expectation value of an observable $\op O$\footnote{For a sake of concreteness, we are limiting our considerations 
-to observables that do not explicitly depend on time}. Here $\dm'(\omega)$ is the \emph{response density operator} that describes the $\omega$-dependent modification of the density 
-operator induced by the perturbation.
+where the operator $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
+under inspection and the \emph{response density operator} $\dm'(\omega)$ codifies the perturbation induced modification of the ground-state density.
 
-\subsection{Basic equation for the linear response formalism for electronic excitations}
+The analysis presented in this section is devoted to a critical review of the fundamental equations at the basis of the response density in the linear response framework.    
+The aim of this process is to....
 
-The linear response formalism can be effectively applied to the analysis of the electronic excitations of molecular and condensed-matter systems, described by the (density-dependent) 
-ground-state hermitian Hamiltonian $\hnot$, coupled to an external perturbation described by the perturbing field $\op\Phi(\omega)$. The $\omega$ structure of $\op\Phi(\omega)$ codifies both 
-the intrinsic time dependence of the perturbation and the switching-on procedure, \emph{e.g.} adiabatic or sudden limit protocols.
+%the construction of two different representations of the response density operator...
 
-The response density is expressed as the first-order variation of ground state density
+\subsection{Fluctuation states. A localization argument for the response density}
+
+The response density operator is expressed as the first-order variation of ground state density
 \be\label{rhodef1}
@@
 \ee
-where $\{\psi_p\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi level.
-By considering the linear order time evolution of these states in presence of the perturbation we can express the response density in the $\omega$ domain as follows:
-\be\lb{rhoPrimeOmegaDef1}
-\dm'(\omega) = \ii \commutator{\dmnot}{\op A(\omega)} \;,
+where $\{\ket{\psi_p}\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level.
+By considering the linear order time evolution of these states in presence of the perturbation we can derive the equation of motion of the response density in the form of 
+a quantum Liouville equation \cite{baroni2008}. This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
+$\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, as follows: 
+\be\lb{rhoPrimeFluctuationStateDef1}
+\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
 \ee
-where $\op A(\omega)$ is a sum of two terms, both written as a triple convolution with the retarded/advanced Green functions $\op G_0^{\pm}$ of the unperturbed Hamiltonian:
+An analysis of the Liouville equation for the response density written in this fashion evidences that fluctuation states are orthogonal to the occupied eigenstates 
+of $\hnot$ and satisfy the following equation of motion:
+\be\lb{fluctuationStateEqMotion1}
+\left[\bbomega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.
+\ee
+
+breve commento su sternheimer e significato lato destro equazione
+
+\vspace{1cm}
+Much more interestingly for the main topic of the present discussion, and regardless from the detailed strategy of their solutions, equations \eqref{fluctuationStateEqMotion1} 
+allow us to present a \emph{localization argument} for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of \eqref{fluctuationStateEqMotion1}, 
+but the same argument holds also for the left ones. We split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term, so that the equation of motion 
+for $\ket{f_p(\omega)}$ written in the coordinate representation has the formal structure of an inhomogeneous Helmholtz equation:
 \be
-\op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
-\op G_0^+(\omega') \left(\op \Phi(\omega)+\op V'(\omega)\right) \op G_0^-(\omega'-\omega)\;. \nn
+\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;,
 \ee
+where $k^2_p(\omega) = 2(\omega+\eps_p)$ and we have formally recognized a \emph{source} term of the form:
+\be
+s(\omega,\r) =  \bra{\r}\op V\ket{f_p(\omega)} + \bra{\r}\op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} 
+\ee
+The solution of this equation admits an integral representation in the form:
+\be\lb{fluctuationStateIntEq1}
+f_p(\omega,\r) = \int \dd\r' g_H(\r-\r')s(\r') \;,
+\ee
+where $g_H(\r)$ is the Green function of the Helmholtz operator in three dimensions. This integral representation allows us to assess the localization character 
+of the fluctuation states, \emph{i.e.} the behavior of $f_p(\omega,\r)$ when $\r$ becomes large. Indeed, assuming that the support of the source term is compact
+we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing, the leading contribution of the fluctuation states
+is given by:
+\be\lb{fluctuationStateIntEq2}
+f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \simeq 
+e^{-\frac{\eta}{2}|\r|} \frac{e^{\ii \sqrt{k^2_p(\omega)} |\r|}}{|\r|} \;.
+\ee
+We observe that the presence of the regularization parameter $\eta$ ensures a (slow) asymptotic convergence to zero, nonetheless the qualitative $\r$-dependence of the fluctuation 
+states is determined by the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an exponential damping for $\omega < |\eps_p|$ and an oscillating 
+power law behavior for $\omega \geq |\eps_p|$.
+This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef1}, so we conclude that
+the linear response functional is built in terms of localized fluctuation states for $\omega < |\eps_h|$. Instead, in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
+contributions from local and non-local quantities and, finally is composed only by non-local fluctuation states for $\omega\geq|\eps_0|$.
+
+\subsection{Excitation operators. A spectral decomposition representation for the response density}
+
+..........
+
+\subsection{Comments. The analytic structure of the linear response susceptibility}
+
+...........
+
+\subsection{...da togliere.......}
+
 The presence of the second addend is due to the density dependence of the unperturbed Hamiltonian and describes the perturbation induced by the variation of $\hnot$ under the
@@
 
-\subsection{Fluctuation states. A localization argument for the linear response functional}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-We start this analysis by deriving an ulterior expression of the response density operator in the frequency space. We consider equation \eqref{rhoPrimeOmegaDef1} and observe that, for any 
-operator $\op O$, we may write:  
-\be
-\commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
-\ee
-where $\op Q_0= \identity - \dmnot$ is the projection operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
-\be
-\dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
-\ee
-This equation suggests us to define the \emph{fluctuation states}:
-\be\lb{fluctuationStateDef1}
-\ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \quad
-\bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
-\ee
-where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by 
-definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
-\be
-\brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega \;.
-\ee
-The response density written in terms of the fluctuation states reads:
-\be\lb{rhoPrimeFluctuationStateDef1}
-\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
-\ee
-and consequently the linear response functional can be expressed as:
-\be\lb{LinearResponseFunctDef2}
-{\cal R}_{\op O}(\omega) = 
-\sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
-\ee
+% In the framework of the linear response formalism one is typically interested in computing the \emph{linear response functional}:
+% \be\lb{LinearResponseFunctDef1}
+% {\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
+% \ee
+% that represents the perturbation-induced modification of the expectation value of an observable $\op O$\footnote{For a sake of concreteness, we are limiting our considerations 
+% to observables that do not explicitly depend on time}. Here $\dm'(\omega)$ is the \emph{response density operator} that describes the $\omega$-dependent modification of the density 
+% operator induced by the perturbation.
+% 
+% \subsection{Basic equations for the linear response formalism for electronic excitations}
+% 
+% The linear response formalism can be effectively applied to the analysis of the electronic excitations of molecular and condensed-matter systems, described by the (density-dependent) 
+% ground-state hermitian Hamiltonian $\hnot$, coupled to an external perturbation described by the perturbing field $\op\Phi(\omega)$. The $\omega$ structure of $\op\Phi(\omega)$ codifies both 
+% the intrinsic time dependence of the perturbation and the switching-on procedure, \emph{e.g.} adiabatic or sudden limit protocols. 
+% 
+% The response density is expressed as the first-order variation of ground state density
+% \be\label{rhodef1}
+% \dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
+% \ee
+% where $\{\psi_p\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi level.
+% By considering the linear order time evolution of these states in presence of the perturbation we can express the response density in the $\omega$ domain as follows:
+% \be\lb{rhoPrimeOmegaDef1}
+% \dm'(\omega) = \ii \commutator{\dmnot}{\op A(\omega)} \;,
+% \ee
+% where $\op A(\omega)$ is a sum of two terms, both written as a triple convolution with the retarded/advanced Green functions $\op G_0^{\pm}$ of the unperturbed Hamiltonian:
+% \be
+% \op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
+% \op G_0^+(\omega') \left(\op \Phi(\omega)+\op V'(\omega)\right) \op G_0^-(\omega'-\omega)\;. \nn
+% \ee
+% The presence of the second addend is due to the density dependence of the unperturbed Hamiltonian and describes the perturbation induced by the variation of $\hnot$ under the
+% action of the perturbing field. In the linear response regime this quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel 
+% (evaluated at $\dm=\dmnot$) times the value of the induced density modification, that is:
+% \be\label{VpDef1}
+% \op V'(\omega)= 
+% \int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
+% \trace{\dm'(\omega) \ket{\r} \bra{\r'}} \;.
+% \ee
+% 
+% \subsection{Fluctuation states. A localization argument for the linear response functional}
+% 
+% We start this analysis by deriving an ulterior expression of the response density operator in the frequency space. We consider equation \eqref{rhoPrimeOmegaDef1} and observe that, for any 
+% operator $\op O$, we may write:  
+% \be
+% \commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
+% \ee
+% where $\op Q_0= \identity - \dmnot$ is the projection operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
+% \be
+% \dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
+% \ee
+% This equation suggests us to define the \emph{fluctuation states}:
+% \be\lb{fluctuationStateDef1}
+% \ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \quad
+% \bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
+% \ee
+% where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by 
+% definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
+% \be
+% \brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega \;.
+% \ee
+% The response density written in terms of the fluctuation states reads:
+% \be\lb{rhoPrimeFluctuationStateDef1}
+% \dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
+% \ee
+% and consequently the linear response functional can be expressed as:
+% \be\lb{LinearResponseFunctDef2}
+% {\cal R}_{\op O}(\omega) = 
+% \sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
+% \ee
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-03-08 AnalyticStructure_main.tex
update

@@
 described by the Hamiltonian $\hnot$ and assume that the ground-state density $\dmnot$ has been provided. Linear response formalism allows us to evaluate the modification 
-of the expectation value of a generic observable induced by a time-dependent perturbation acting on the system. This quantity, written in the frequency domain, can be expressed 
+of the expectation value of a generic observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed 
 through the evaluation of the \emph{linear response functional}:
@@
 where the operator $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
-under inspection and the \emph{response density operator} $\dm'(\omega)$ codifies the perturbation induced modification of the ground-state density.
+under inspection. The modification of the ground-state density induced by the perturbation is expressed by the \emph{response density operator} $\dm'(\omega)$ that, in the linear 
+response regime, is a linear function of the perturbing field $\op\Phi(\omega)$.
 
-The analysis presented in this section is devoted to a critical review of the fundamental equations at the basis of the response density in the linear response framework.    
+The analysis presented in this section is devoted to a critical review of the fundamental equations which define the response density operator in the linear response regime.    
 The aim of this process is to....
@@
 
-\subsection{Fluctuation states. A localization argument for the response density}
+\subsection{Fluctuation states. A (de-)localization argument for the response density}
 
-The response density operator is expressed as the first-order variation of ground state density
-\be\label{rhodef1}
-\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
-\ee
-where $\{\ket{\psi_p}\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level.
+The response density operator is expressed as the first-order variation of ground state density $\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$
+%\be\label{rhodef1}
+%\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
+%\ee
+where the set $\{\ket{\psi_p}\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level.
 By considering the linear order time evolution of these states in presence of the perturbation we can derive the equation of motion of the response density in the form of 
-a quantum Liouville equation \cite{baroni2008}. This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
+a quantum Liouville equation (for example see \cite{baroni2008}). This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
 $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, as follows: 
@@
 An analysis of the Liouville equation for the response density written in this fashion evidences that fluctuation states are orthogonal to the occupied eigenstates 
-of $\hnot$ and satisfy the following equation of motion:
+of $\hnot$ and their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
 \be\lb{fluctuationStateEqMotion1}
-\left[\bbomega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'(\omega))\ket{\psi_p} \;,
 \ee
+where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states and the operator $\op V'(\omega)$ is a perturbing term due to the density-dependence 
+of $\hnot$. %the unperturbed Hamiltonian. 
+%and describes the perturbation induced by the variation of $\hnot$ under the action of the perturbing field.
+%The  r.h.s of \eqref{fluctuationStateEqMotion1} expresses the complete perturbing potential
 
-breve commento su sternheimer e significato lato destro equazione
+The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a 
+\emph{localization argument} for the fluctuation states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential 
+$\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
+\be
+\ket{f_p(\omega)} = \op G_H(\omega)\ket{s(\omega)} \;,
+\ee
+where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (k^2_p(\omega)-\op T)^{-1}$ with $k^2_p(\omega) = (\omega+\eps_p)$,
+and the \emph{source term} is given by:
+\be
+\ket{s(\omega)} =  \op V\ket{f_p(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
+\ee
+For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
+% \be\lb{HelmholtzKernelDef1}
+% \bra{\r}\op G_H(\omega)\ket{\r'} = \frac{1}{4\pi} \left\{ 
+% \begin{matrix}
+% \frac{e^{-2k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
+% \frac{e^{\ii k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega > |\eps_p|
+% \end{matrix}
+% \right. \;,
+% \ee
+\be\lb{HelmholtzKernelDef1}
+G_H(\omega,\r) = \frac{1}{4\pi} \left\{ 
+\begin{matrix}
+\frac{e^{-2k_p(\omega)|\r|}}{|\r|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
+\frac{e^{2\ii k_p(\omega)|\r|}}{|\r|} \;,\; {\textrm for} \; \omega > |\eps_p|
+\end{matrix}
+\right. \;,
+\ee
+and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
+$\brket{\r}{s(\omega)}$. An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
+which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega,\r)$ behaves as a spherical wave and its
+convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
+$G_H(\omega,\r)$ contains an exponential damping factor and the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.
 
-\vspace{1cm}
-Much more interestingly for the main topic of the present discussion, and regardless from the detailed strategy of their solutions, equations \eqref{fluctuationStateEqMotion1} 
-allow us to present a \emph{localization argument} for the fluctuation states. We discuss this point for the right vectors, \emph{i.e.} for the first line of \eqref{fluctuationStateEqMotion1}, 
-but the same argument holds also for the left ones. We split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term, so that the equation of motion 
-for $\ket{f_p(\omega)}$ written in the coordinate representation has the formal structure of an inhomogeneous Helmholtz equation:
-\be
-\left(k^2_p(\omega)+\ii\eta + \nabla^2\right)f_p(\omega,\r) = s(\omega,\r) \;\;,
-\ee
-where $k^2_p(\omega) = 2(\omega+\eps_p)$ and we have formally recognized a \emph{source} term of the form:
-\be
-s(\omega,\r) =  \bra{\r}\op V\ket{f_p(\omega)} + \bra{\r}\op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} 
-\ee
-The solution of this equation admits an integral representation in the form:
-\be\lb{fluctuationStateIntEq1}
-f_p(\omega,\r) = \int \dd\r' g_H(\r-\r')s(\r') \;,
-\ee
-where $g_H(\r)$ is the Green function of the Helmholtz operator in three dimensions. This integral representation allows us to assess the localization character 
-of the fluctuation states, \emph{i.e.} the behavior of $f_p(\omega,\r)$ when $\r$ becomes large. Indeed, assuming that the support of the source term is compact
-we have that, for $\r$ outside the domain in which the integrand of \eqref{fluctuationStateIntEq1} is not vanishing, the leading contribution of the fluctuation states
-is given by:
-\be\lb{fluctuationStateIntEq2}
-f_p(\omega,\r) \sim \frac{e^{\ii \sqrt{k^2_p(\omega)+\ii\eta} |\r|}}{|\r|} \simeq 
-e^{-\frac{\eta}{2}|\r|} \frac{e^{\ii \sqrt{k^2_p(\omega)} |\r|}}{|\r|} \;.
-\ee
-We observe that the presence of the regularization parameter $\eta$ ensures a (slow) asymptotic convergence to zero, nonetheless the qualitative $\r$-dependence of the fluctuation 
-states is determined by the sign of $k^2_p(\omega)$. In particular equation \eqref{fluctuationStateIntEq2} describes an exponential damping for $\omega < |\eps_p|$ and an oscillating 
-power law behavior for $\omega \geq |\eps_p|$.
 This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef1}, so we conclude that
@@
 
+Comment of the reliability of the scalar product of the linear response functional.
+
+Numerical example (convergence below threshold of the Benzene spectrum computed in different computational setups).
+
 \subsection{Excitation operators. A spectral decomposition representation for the response density}
 
-..........
+Inizio a mettere le formule da usare...forse...
+
+Liouville equation:
+\be\lb{LiouvillianRhopomegaDef1}
+\left(\bbomega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;,\;\; 
+\Liouv = \Liouvnot + \coupl \;.
+\ee
+% by introducing the \emph{coupling}
+% superoperator:
+% \be\lb{couplingSopDef1}
+% \coupl = 
+% \int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
+% \trace{\cdot \ket{\r} \bra{\r'}} \;,
+% \ee
+Excitation operators as eigenstates of the Liouvillian:
+\be
+\Liouv \op E = E \op E \;, \qq
+ \op{\tilde E} \Liouv = E \op{\tilde E}
+\ee
 
@@
 ...........
-
-\subsection{...da togliere.......}
-
-The presence of the second addend is due to the density dependence of the unperturbed Hamiltonian and describes the perturbation induced by the variation of $\hnot$ under the
-action of the perturbing field. In the linear response regime this quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel 
-(evaluated at $\dm=\dmnot$) times the value of the induced density modification, that is:
-\be\label{VpDef1}
-\op V'(\omega)= 
-\int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
-\trace{\dm'(\omega) \ket{\r} \bra{\r'}} \;.
-\ee
 

### 2018-03-08 AnalyticStructure_main.tex
Update on Overleaf.

@@
 \be
-\ket{f_p(\omega)} = \op G_H(\omega)\ket{s(\omega)} \;,
+\ket{f_p(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s(\omega)} \;,
 \ee
-where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (k^2_p(\omega)-\op T)^{-1}$ with $k^2_p(\omega) = (\omega+\eps_p)$,
+where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (\omega-\op T)^{-1}$, % with $k^2_p(\omega) = (\omega+\eps_p)$,
 and the \emph{source term} is given by:
@@
 \be\lb{HelmholtzKernelDef1}
-G_H(\omega,\r) = \frac{1}{4\pi} \left\{ 
-\begin{matrix}
-\frac{e^{-2k_p(\omega)|\r|}}{|\r|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
-\frac{e^{2\ii k_p(\omega)|\r|}}{|\r|} \;,\; {\textrm for} \; \omega > |\eps_p|
-\end{matrix}
-\right. \;,
+\bra{\r'} \op G_H(k^2) \ket\r = \frac{1}{4\pi} \begin{cases}
+\frac{e^{-2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k < 0\; \\ 
+\frac{e^{2\ii k |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; k > 0
+\end{cases}
 \ee
-and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
-$\brket{\r}{s(\omega)}$. An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
+%and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
+%$\brket{\r}{s(\omega)}$.
+An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
 which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega,\r)$ behaves as a spherical wave and its

### 2018-03-09 AnalyticStructure_main.tex
update

@@
 \ee
-An analysis of the Liouville equation for the response density written in this fashion evidences that fluctuation states are orthogonal to the occupied eigenstates 
-of $\hnot$ and their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
+Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. Moreover, an analysis of the Liouville equation for the response density written in this fashion
+evidences that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
+%An analysis of the Liouville equation for the response density written in this fashion evidences that fluctuation states are orthogonal to the occupied eigenstates 
+%of $\hnot$ and their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
 \be\lb{fluctuationStateEqMotion1}
@@
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states and the operator $\op V'(\omega)$ is a perturbing term due to the density-dependence 
-of $\hnot$. %the unperturbed Hamiltonian. 
+where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and the operator $\op V'(\omega)$ is a perturbing term due to the density-dependence 
+of the unperturbed Hamiltonian. %$\hnot$. %the unperturbed Hamiltonian. 
 %and describes the perturbation induced by the variation of $\hnot$ under the action of the perturbing field.
@@
 \be\lb{HelmholtzKernelDef1}
-\bra{\r'} \op G_H(k^2) \ket\r = \frac{1}{4\pi} \begin{cases}
-\frac{e^{-2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k < 0\; \\ 
+\bra{\r} \op G_H(k^2) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+\frac{e^{2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k < 0\; \\ 
 \frac{e^{2\ii k |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; k > 0
-\end{cases}
+\end{cases} \;,
 \ee
-%and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
-%$\brket{\r}{s(\omega)}$.
+and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
+$\brket{\r'}{s(\omega)}$.
 An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
-which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega,\r)$ behaves as a spherical wave and its
+which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega)$ behaves as a spherical wave and its
 convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
-$G_H(\omega,\r)$ contains an exponential damping factor and the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.
+the kernel contains an exponential damping factor and the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.
+
+\vspace{0.3cm}
+\noindent{TODO: Add comment to support the localization below threshold}. Two possible way. First way, use the fact that the $\ket{f_p(0)}$ is the nothing but the $p$-\emph{th} 
+eigenstate of the perturbed Hamiltonian with perturbing field $\op\Phi(0)$. The localization of $\ket{f_p(0)}$ can be explicitly checked by solving the ground-state problem for
+this Hamiltonian. How to extended to finite values of $\omega$ below threshold? Second way. Try and iterative solution of the self-consistent Helmholtz equation (below threshold) 
+starting from a localized guess for the fluctuation state. Then state something about the the fact that is reasonable to believe that (for a proper choice of the perturbing field)
+the operators appearing in the source term keep its support compact. If we are able to state this in a appropriate way the localization argument below threshold hold. In my opinion
+this way is better.
+\vspace{0.3cm}
+
+The linear response functional can be expressed as:
+\be\lb{LinearResponseFunctDef2}
+{\cal R}_{\op O}(\omega) = 
+\sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
+\ee
 
@@
 
-Numerical example (convergence below threshold of the Benzene spectrum computed in different computational setups).
+\vspace{0.3cm}
+\noindent{TODO: Numerical example (convergence below threshold of the Benzene spectrum computed in different computational setup).}
 

### 2018-03-13 AnalyticStructure_main.tex
Update on Overleaf.
update

@@
 \be\lb{LinearResponseFunctDef1}
-{\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
+\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
 \ee
@@
 under inspection. The modification of the ground-state density induced by the perturbation is expressed by the \emph{response density operator} $\dm'(\omega)$ that, in the linear 
-response regime, is a linear function of the perturbing field $\op\Phi(\omega)$.
+response regime, is a linear function of the perturbing field $\op\Phi(\omega)$. For this reason it is possible to define the \emph{susceptibility} superoperator, as follows:
+\be\lb{SusceptibilityDef1}
+\dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
+\ee
+Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
+%ndependent from the specific perturbation that acts on the system and codifies the fundamental aspects which determine the response of the system. % is the fundamental object at the basis of
 
@@
 
-The response density operator is expressed as the first-order variation of ground state density $\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$
+The response density operator is expressed as the first-order variation of ground state density $\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$,
 %\be\label{rhodef1}
@@
 where the set $\{\ket{\psi_p}\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level.
-By considering the linear order time evolution of these states in presence of the perturbation we can derive the equation of motion of the response density in the form of 
+Using this notation we denote the energy of the HOMO level as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. 
+In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are real functions, when project in the $\r$-representation.
+
+By considering the linear order time evolution of the eigenstates of $\hnot$ in presence of the perturbation we can derive the equation of motion of the response density in the form of 
 a quantum Liouville equation (for example see \cite{baroni2008}). This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
@@
 \be\lb{HelmholtzKernelDef1}
-\bra{\r} \op G_H(k^2) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
-\frac{e^{2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k < 0\; \\ 
-\frac{e^{2\ii k |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; k > 0
+\bra{\r} \op G_H(\omega) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+\frac{e^{2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k^2 = \omega  < 0\; \\ 
+\frac{e^{2\ii k |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; k^2 = \omega > 0
 \end{cases} \;,
@@
 An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
-which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $G_H(\omega)$ behaves as a spherical wave and its
+which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ behaves as a spherical wave and its
 convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
-the kernel contains an exponential damping factor and the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.
+the kernel contains an exponential damping factor and %the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.  
+$f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
 
-\vspace{0.3cm}
-\noindent{TODO: Add comment to support the localization below threshold}. Two possible way. First way, use the fact that the $\ket{f_p(0)}$ is the nothing but the $p$-\emph{th} 
-eigenstate of the perturbed Hamiltonian with perturbing field $\op\Phi(0)$. The localization of $\ket{f_p(0)}$ can be explicitly checked by solving the ground-state problem for
-this Hamiltonian. How to extended to finite values of $\omega$ below threshold? Second way. Try and iterative solution of the self-consistent Helmholtz equation (below threshold) 
-starting from a localized guess for the fluctuation state. Then state something about the the fact that is reasonable to believe that (for a proper choice of the perturbing field)
-the operators appearing in the source term keep its support compact. If we are able to state this in a appropriate way the localization argument below threshold hold. In my opinion
-this way is better.
-\vspace{0.3cm}
+% \vspace{0.3cm}
+% \noindent{TODO: Add comment to support the localization below threshold}. Two possible way. First way, use the fact that the $\ket{f_p(0)}$ is the nothing but the $p$-\emph{th} 
+% eigenstate of the perturbed Hamiltonian with perturbing field $\op\Phi(0)$. The localization of $\ket{f_p(0)}$ can be explicitly checked by solving the ground-state problem for
+% this Hamiltonian. How to extended to finite values of $\omega$ below threshold? Second way. Try and iterative solution of the self-consistent Helmholtz equation (below threshold) 
+% starting from a localized guess for the fluctuation state. Then state something about the the fact that is reasonable to believe that (for a proper choice of the perturbing field)
+% the operators appearing in the source term keep its support compact. If we are able to state this in a appropriate way the localization argument below threshold hold. In my opinion
+% this way is better.
+% \vspace{0.3cm}
 
-The linear response functional can be expressed as:
+% The knowledge of the long range behavior of the fluctuation states allows us to perform an assessment on the reliability of the evaluation of the linear response functional 
+% \eqref{LinearResponseFunctDef1}. To elaborate this statement we make usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, 
+% so that:
+% The knowledge of the long range behavior of the fluctuation states allows us to assess the spatial localization properties of the basic objects relevant in the contest of the 
+% linear response. In particular, making usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear 
+% response functional \eqref{LinearResponseFunctDef1} as follows: 
+This analysis allows us to comprehend that the spatial localization features of the building blocks relevant for the linear response depend critically on $\omega$. 
+Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
 \be\lb{LinearResponseFunctDef2}
-{\cal R}_{\op O}(\omega) = 
-\sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
+\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
 \ee
-
-This argument holds for all the fluctuation states that contribute to the perturbation-induced expectation value \eqref{LinearResponseFunctDef1}, so we conclude that
-the linear response functional is built in terms of localized fluctuation states for $\omega < |\eps_h|$. Instead, in the range $\eps_h|\leq\omega<|\eps_0|$ it contains both
-contributions from local and non-local quantities and, finally is composed only by non-local fluctuation states for $\omega\geq|\eps_0|$.
-
-Comment of the reliability of the scalar product of the linear response functional.
+so we can identify two different regimes, depending on the value of $\omega$. In the first one, realized for $\omega<|\eps_h|$, all the terms contributing to \eqref{LinearResponseFunctDef2} 
+are expressed in terms of genuinely localized wave functions, while in the second one, for $\omega>|\eps_h|$, fluctuation states start behaving as unbound wave functions. 
+%and the scalar products appearing in \eqref{LinearResponseFunctDef2} are only regularized by the long range behavior of the $\ket{\psi_p}$.
+This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
+to the value of $\omega$. 
+This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....
 
@@
 \be\lb{LiouvillianRhopomegaDef1}
-\left(\bbomega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;,\;\; 
+\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;,\;\; 
 \Liouv = \Liouvnot + \coupl \;.

### 2018-03-14 AnalyticStructure_main.tex
update

@@
 % response functional \eqref{LinearResponseFunctDef1} as follows: 
-This analysis allows us to comprehend that the spatial localization features of the building blocks relevant for the linear response depend critically on $\omega$. 
-Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
+% This analysis indicates that the task of providing a reliable assessment of the linear response functional present a different level of complexity   .
+% Using the representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear response functional as
+% \be\lb{LinearResponseFunctDef2}
+% \braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
+% \ee
+This analysis allows us to determine the spatial localization features of the building blocks\footnote{This consideration holds for the class of observables that produces a localized state 
+$\bra{\psi_p}\op O$ when acts on a bound eigenstate of $\hnot$} relevant for the linear response.  
+%and provides indications on the da alcune indicazioni sulla difficoltà di ottenere una reliable evaluation of the linear response functional. %change in function of $\omega$. 
+Indeed, using the fluctuation states representation of the response density, we can express the linear response functional \eqref{LinearResponseFunctDef1} as
+%Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
 \be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
+\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
 \ee
-so we can identify two different regimes, depending on the value of $\omega$. In the first one, realized for $\omega<|\eps_h|$, all the terms contributing to \eqref{LinearResponseFunctDef2} 
+An inspection of \eqref{LinearResponseFunctDef2} evidences that we can identify two different regimes, depending on the value of $\omega$. In the first regime, realized for $\omega<|\eps_h|$, 
+the linear response is formulated in terms of genuinely quantities, each of which possess a physical cut-off radius. In this case it is possible to evaluate of the scalar products of 
+\eqref{LinearResponseFunctDef2} using a finite computational domain and the long range behavior of both $\{\ket{f_p(\omega)}\}$ and $\{\bra{\psi_p}\op O\}$ ensures that the result is not 
+affected by the specific choice of the domain. This is an argument in favor of the reliable evaluation of the linear response functional in the low-$\omega$ regime.    
+%is reasonable to expect that the result of () should be independent
+%from the computation domain used to evaluate the scalar products,  choosing a finite computational
+%domain to perform the scalar products of \eqref{LinearResponseFunctDef2} does not affect the result, provided that the degrees of freedom included are able to contain the waist of the elements
+%considered.
+
+scegliendo un dominio computazionale
+finito per eseguire i prodotti scalari espressi nella \eqref{LinearResponseFunctDef2}, i risultati ottenuti siano indipendenti dalla particolare scelta eseguita a patto che i gradi di libertà
+utilizzati permettano di contenere la taglia degli oggetti considerati.
+
+sia possibile ottenere una valutazione
+affidabile della risposta lineare eseguendo i prodotti scalari espressi nella \eqref{LinearResponseFunctDef2}  in un dominio computazione finito in grado di contenere i building blocks a reliable evaluation
+of \eqref{LinearResponseFunctDef2} can be provided if the building elements are computed in a finite domain which contains the cut.off
+
+\vspace{1cm}
 are expressed in terms of genuinely localized wave functions, while in the second one, for $\omega>|\eps_h|$, fluctuation states start behaving as unbound wave functions. 

### 2018-03-15 AnalyticStructure_main.tex
update

--- 2018-03-13 AnalyticStructure_main.tex
@@
 Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
-%ndependent from the specific perturbation that acts on the system and codifies the fundamental aspects which determine the response of the system. % is the fundamental object at the basis of
 
@@
 
-The response density operator is expressed as the first-order variation of ground state density $\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$,
-%\be\label{rhodef1}
-%\dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
-%\ee
-where the set $\{\ket{\psi_p}\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level.
-Using this notation we denote the energy of the HOMO level as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. 
-In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are real functions, when project in the $\r$-representation.
+The response density operator is expressed as the first-order variation of ground state density $\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$, where the set $\{\ket{\psi_p}\}$ denote the 
+occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
+as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are real functions, when 
+projected in the $\r$-representation.
 
@@
 \ee
-Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. Moreover, an analysis of the Liouville equation for the response density written in this fashion
-evidences that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
-%An analysis of the Liouville equation for the response density written in this fashion evidences that fluctuation states are orthogonal to the occupied eigenstates 
-%of $\hnot$ and their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
+Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. Moreover, an analysis of the Liouville equation for the response density written in this 
+fashion evidences that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
 \be\lb{fluctuationStateEqMotion1}
@@
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and the operator $\op V'(\omega)$ is a perturbing term due to the density-dependence 
-of the unperturbed Hamiltonian. %$\hnot$. %the unperturbed Hamiltonian. 
-%and describes the perturbation induced by the variation of $\hnot$ under the action of the perturbing field.
-%The  r.h.s of \eqref{fluctuationStateEqMotion1} expresses the complete perturbing potential
+where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and the operator $\op V'(\omega)$ is a perturbing term due to the 
+density-dependence of the unperturbed Hamiltonian.
 
-The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a 
-\emph{localization argument} for the fluctuation states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential 
-$\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
+The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a \emph{localization argument} 
+for the fluctuation states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and solve \eqref{fluctuationStateEqMotion1} 
+in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
 \be
@@
 convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
-the kernel contains an exponential damping factor and %the localization features of $f_p(\omega,\r)$ are determined by the spatial behavior of the source term.  
-$f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
+the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
 
@@
 % response functional \eqref{LinearResponseFunctDef1} as follows: 
-This analysis allows us to comprehend that the spatial localization features of the building blocks relevant for the linear response depend critically on $\omega$. 
+% This analysis indicates that the task of providing a reliable assessment of the linear response functional present a different level of complexity   .
+% Using the representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear response functional as
+% \be\lb{LinearResponseFunctDef2}
+% \braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
+% \ee
+This argument can be easily extended to the linear response functional and allows us to determine the spatial localization features of the building blocks relevant for the linear response.  
 Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
 \be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
+\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
 \ee
-so we can identify two different regimes, depending on the value of $\omega$. In the first one, realized for $\omega<|\eps_h|$, all the terms contributing to \eqref{LinearResponseFunctDef2} 
-are expressed in terms of genuinely localized wave functions, while in the second one, for $\omega>|\eps_h|$, fluctuation states start behaving as unbound wave functions. 
-%and the scalar products appearing in \eqref{LinearResponseFunctDef2} are only regularized by the long range behavior of the $\ket{\psi_p}$.
-This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
-to the value of $\omega$. 
-This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....
+An inspection of \eqref{LinearResponseFunctDef2} evidences that we can identify two different regimes, on the basis of the value of $\omega$. The first one, which we will refer to as the
+\emph{below threshold regime}, is realized for $\omega<|\eps_h|$. In this case the linear response functional is expressed in terms of genuinely localized quantities\footnote{This consideration 
+holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which possesses a physical cut-off radius. 
+Due to this behavior, the computational effort needed to provide a reliable evaluation of \eqref{LinearResponseFunctDef2} is determined by the capability of the chosen computational setup to 
+express bound-state like wave functions, in a analogous fashion of a ground state calculation.
+
+On the contrary, the evaluation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
+states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 
+\eqref{LinearResponseFunctDef2}, where the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. This observation indicates that, above threshold, a computational setup 
+provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
+
+As an explicit example in support of these arguments we compare the absorption spectrum of a benzene molecule computed in three distinct real-space basis set, which differs for the 
+dimension of the computational domain. Results evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational setup are clearly
+visible in the for values of $\omega$ that exceed the threshold value.
+
+% This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
+% to the value of $\omega$. 
+% This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....
 
@@
 \noindent{TODO: Numerical example (convergence below threshold of the Benzene spectrum computed in different computational setup).}
+\vspace{0.3cm}
+
+This analysis, carried out starting from the representation of the linear response functional in terms of fluctuation states, evidences some general properties of the linear response. 
+In the next sections we will reformulate an analogous procedure directly looking at the susceptibility. This analysis lead us to the core of the paper, namely the description of the
+analytical structure of the linear response susceptibility.
 

### 2018-03-16 AnalyticStructure_main.tex
update

@@
 
-.....
+State something about the assessment of physical reliability for a ground state calculation. Some comment on the setup independence of the results. Introduce the correspondence
+between localization properties and observable behavior or physicality. State the, at the present days, similar consideration for the results of linear response are still 
+missing...
+
+The basic motivation at the basis of the analysis discussed in this paper is to address to following question: which are the requirement that a computational setup has to
+satisfy in order to be able to provide physical results for a linear response calculation? Here with physical we meant that they depend only on the features of the system under
+inspection and on the perturbation acting on it. Physical results are unaffected by computational parameters, like the dimension of the computational domain or the nature of
+the basis set used to perform the calculations.
+
+To answer to this question we investigate the properties of the susceptibility, which represents the fundamental object in the contest of linear response.
 
@@
 
-This analysis, carried out starting from the representation of the linear response functional in terms of fluctuation states, evidences some general properties of the linear response. 
-In the next sections we will reformulate an analogous procedure directly looking at the susceptibility. This analysis lead us to the core of the paper, namely the description of the
-analytical structure of the linear response susceptibility.
+%This analysis, carried out starting from the representation of the linear response functional in terms of fluctuation states, evidences some general properties of the linear response. 
+%In the next sections we will reformulate an analogous procedure directly looking at the susceptibility. This analysis lead us to the core of the paper, namely the description of the
+%analytical structure of the linear response susceptibility.
 
@@
 
-Inizio a mettere le formule da usare...forse...
+The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states, has evidenced some general properties of the linear response
+for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
+$\omega<|\eps_h|$. consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.
 
-Liouville equation:
+Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
+operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
+into the analytic structure of the linear response.
+
+The starting point of this analysis is represented by the Liouville equation for the response density operator:
 \be\lb{LiouvillianRhopomegaDef1}
-\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot}\;,\;\; 
-\Liouv = \Liouvnot + \coupl \;.
+\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;.
 \ee
-% by introducing the \emph{coupling}
-% superoperator:
-% \be\lb{couplingSopDef1}
-% \coupl = 
-% \int \dd \r \dd \r' \commutator{\frac{\delta\hnot}{\delta \rho_0(\r,\r')}}{\dmnot}
-% \trace{\cdot \ket{\r} \bra{\r'}} \;,
-% \ee
-Excitation operators as eigenstates of the Liouvillian:
-\be
+Using the spectral decomposition of the resolvent of the Liouvillian we have:
+\be\lb{RhopExcitationDef1}
+\sop{{\cal R}}(\omega) \cdot   =
+\sint\dd E \, \op E
+\frac{\trace{\opskew{\tilde E}\cdot}}{\omega-E} \;,
+\ee
+with $\opskew{O} = \commutator{\op O}{\dmnot}$. 
+Excitation operators as eigenstates of the Liouvillian (keep left and right different or not?):
+\be\lb{ExcitationOperatorsDef1}
 \Liouv \op E = E \op E \;, \qq
@@
 \ee
+We can express excitation operators as follows:
+\begin{align}\lb{ExcitationOperatorsDef2}
+\op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \nn \\
+\op {\tilde E} &= \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
+\end{align}
 

### 2018-03-19 AnalyticStructure_main.tex
update

@@
 \section{Introduction}
+
+The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation in the linear response regime.
+
+The ground state properties of these systems are described within the standard DFT approach in which (valence) electrons are distributed on the Kohn-Sham orbitals. The stability of
+the ground state and the localized nature of the system ensures that the KS description of occupied states is represented by a discrete set of wave functions that becomes arbitrary 
+small far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide a reliable description of the ground state properties 
+if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}. %Results discussed in \cite{boffi2016} confirm this statement.
+
+The same arguments cannot be rigidly extended to the case in which an external time-dependent field starts acting on the system. Indeed, the perturbation drives the system out 
+from the equilibrium and the electrons sample a wider region of the state space, that will contains orbitals of both negative (bound) and positive (unbound) energies. Unbound orbitals 
+form a continuum of states in the true system with open boundaries, and the introduction of a finite computational domain has the effects of introducing a fictitious level discretization
+\cite{boffi2016}.
+
+%In this case the relevant physical quantities are the perturbation-induced
+%modification of the expectation values of the observable.  one is not dealing with a ground state property and
+
+The perturbation induces a modification on the ground state density and, choosing the
+eigenstates of the unperturbed KS Hamiltonian as a natural basis, one has to include also the virtual (unoccupied) states to described the perturbed density. Virtual states of
+positive energy constitute a continuum...
+
+Sebbene non ci sia necessità di usare gli autostati di KS per campionare lo spazio ortogonale a quello in cui si esprime la densità imperturbata, questo argomento solleva un potenziale
+problema: quale è la scelta di una basis set idonea per costruire la risposta lineare in modo affidabile?
+
+%a natural criterion for the choice of
+
+%This fact indicates that a computation basis that is able to sample a finite domain around the molecule will provide an unbiased estimate of ground states properties
+
+%This fact has also important consequences when one analyzes the effects of a finite computational domain on the reliable evaluation of the system's properties.
+
+\vspace{1cm}
 
@@
 
-The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states, has evidenced some general properties of the linear response
+The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
 for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
-$\omega<|\eps_h|$. consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.
+$\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.
 

### 2018-03-20 AnalyticStructure_main.tex
update

@@
 
-The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation in the linear response regime.
+The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
+This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT)\cite{runge1984,onida2002}, that allows one to establish the time-dependent 
+Kohn-Sham (KS) equations that determine the evolution of the one-particle properties of the system with respect to time. We focus our attention to the linear response regime (LR) 
+in which the theory can be conveniently expressed in the frequency domain and the time-dependent KS equation are reformulated as a quantum Liouville equation for the response 
+density operator. Different computational approaches have been developed in literature\cite{baroni2008,hubener2014,brabec2015}, principally with the aim of producing efficient algorithms 
+for the evaluation of the physical observables. These methods differ both for the procedure adopted to solve the Liouville equation (explicit diagonalization, self-consistent Sternheimer 
+equation, Lanczos chain-like procedure, etc.) and both for the choice of the basis set employed to perform the calculations. Nonetheless, in all the cases one is a dealing with a finite 
+basis set that, unavoidably, gives rise to a limited computational domain. It is then meaningful to try to understand under which extent and for which type of observables the artificial 
+truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR.
 
-The ground state properties of these systems are described within the standard DFT approach in which (valence) electrons are distributed on the Kohn-Sham orbitals. The stability of
-the ground state and the localized nature of the system ensures that the KS description of occupied states is represented by a discrete set of wave functions that becomes arbitrary 
-small far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide a reliable description of the ground state properties 
-if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}. %Results discussed in \cite{boffi2016} confirm this statement.
+A preliminary answer of this question can be formulated by considering results \cite{boffi2016}, that establish a clear correspondence between the orbital localization character, and 
+the independence of its properties (\emph{e.g.} energy) with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range 
+constitute a genuine discrete set and a finite basis is able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, 
+unbound (delocalized) orbitals form a continuum of states in the true system with open boundaries. For these class of objects the presence finite computational domain has a deeper 
+impact since introduces a fictitious discretization of the energy levels. Furthermore, all the energies of the unbound orbitals scale to zero as long as the computational domain is 
+increased.
+
+First of all it is useful to discuss the property of the ground state under this perspective. 
+Indeed, it is well known that the stability of the ground state and the localized nature of a molecular-like system ensures that the KS description of occupied states is represented 
+by a discrete set of wave functions that approaches to zero far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide 
+a reliable description of the ground state properties if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}.
+
+% A preliminary answer of this question can be formulated by considering results derived in \cite{boffi2016}, concerning the basis dependence of occupied and virtual molecular orbitals.   
+% First of all it is useful to discuss the property of the ground state under this perspective. 
+% Indeed, it is well known that the stability of the ground state and the localized nature of a molecular-like system ensures that the KS description of occupied states is represented 
+% by a discrete set of wave functions that approaches to zero far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide 
+% a reliable description of the ground state properties 
+% if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}.
 
 The same arguments cannot be rigidly extended to the case in which an external time-dependent field starts acting on the system. Indeed, the perturbation drives the system out 
-from the equilibrium and the electrons sample a wider region of the state space, that will contains orbitals of both negative (bound) and positive (unbound) energies. Unbound orbitals 
-form a continuum of states in the true system with open boundaries, and the introduction of a finite computational domain has the effects of introducing a fictitious level discretization
-\cite{boffi2016}.
+from the equilibrium and the electrons sample a wider region of the state space, that will contains orbitals of both negative (bound) and positive (unbound) energies. 
+% Unbound orbitals 
+% form a continuum of states in the true system with open boundaries, and the introduction of a finite computational domain has the effects of introducing a fictitious level discretization
+% \cite{boffi2016}.
 
@@
 
-The perturbation induces a modification on the ground state density and, choosing the
-eigenstates of the unperturbed KS Hamiltonian as a natural basis, one has to include also the virtual (unoccupied) states to described the perturbed density. Virtual states of
-positive energy constitute a continuum...
+% A preliminary answer of this question can be formulated by considering results derived in \cite{boffi2016}, concerning the basis dependence of occupied and virtual molecular orbitals.   
+% Indeed, the ground state properties of molecular-like systems are described within the standard DFT approach in which electrons are distributed on the Kohn-Sham orbitals. The stability of
+% the ground state and the localized nature of the system ensures that the KS description of occupied states is represented by a discrete set of wave functions that approaches to zero  
+% far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide a reliable description of the ground state properties 
+% if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}.
 
-Sebbene non ci sia necessità di usare gli autostati di KS per campionare lo spazio ortogonale a quello in cui si esprime la densità imperturbata, questo argomento solleva un potenziale
-problema: quale è la scelta di una basis set idonea per costruire la risposta lineare in modo affidabile?
+% The perturbation induces a modification on the ground state density and, choosing the
+% eigenstates of the unperturbed KS Hamiltonian as a natural basis, one has to include also the virtual (unoccupied) states to described the perturbed density. Virtual states of
+% positive energy constitute a continuum...
+
+% Sebbene non ci sia necessità di usare gli autostati di KS per campionare lo spazio ortogonale a quello in cui si esprime la densità imperturbata, questo argomento solleva un potenziale
+% problema: quale è la scelta di una basis set idonea per costruire la risposta lineare in modo affidabile?
 
@@
 
-State something about the assessment of physical reliability for a ground state calculation. Some comment on the setup independence of the results. Introduce the correspondence
-between localization properties and observable behavior or physicality. State the, at the present days, similar consideration for the results of linear response are still 
-missing...
+% State something about the assessment of physical reliability for a ground state calculation. Some comment on the setup independence of the results. Introduce the correspondence
+% between localization properties and observable behavior or physicality. State the, at the present days, similar consideration for the results of linear response are still 
+% missing...
 

### 2018-03-21 AnalyticStructure_main.tex
update

--- 2018-03-16 AnalyticStructure_main.tex
@@
 
-%% Language and font encodings
+% Language and font encodings
 \usepackage[english]{babel}
@@
 
-%% Useful packages
+% Useful packages
 \usepackage{graphicx}
@@
 
-State something about the assessment of physical reliability for a ground state calculation. Some comment on the setup independence of the results. Introduce the correspondence
-between localization properties and observable behavior or physicality. State the, at the present days, similar consideration for the results of linear response are still 
-missing...
+The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
+This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT)\cite{runge1984,onida2002}, that allows one to establish the time-dependent 
+Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time.
 
-The basic motivation at the basis of the analysis discussed in this paper is to address to following question: which are the requirement that a computational setup has to
-satisfy in order to be able to provide physical results for a linear response calculation? Here with physical we meant that they depend only on the features of the system under
-inspection and on the perturbation acting on it. Physical results are unaffected by computational parameters, like the dimension of the computational domain or the nature of
-the basis set used to perform the calculations.
+We focus our attention to the linear response regime (LR) in which the theory can be conveniently expressed in the frequency domain and the time-dependent KS equation are reformulated 
+as a quantum Liouville equation for the response density operator. Different computational approaches have been developed in literature\cite{baroni2008,hubener2014,brabec2015}, principally 
+with the aim of producing efficient algorithms for the evaluation of the physical observables. These methods differ both for the procedure adopted to solve the Liouville equation 
+(explicit diagonalization, self-consistent Sternheimer equation, Lanczos chain-like procedure, etc.) and both for the choice of the basis set employed to perform the calculations. 
+Nonetheless, in all the cases one is a dealing with a finite basis set that, unavoidably, gives rise to a limited computational domain. It is then meaningful to try to understand under 
+which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR.
 
-To answer to this question we investigate the properties of the susceptibility, which represents the fundamental object in the contest of linear response.
+A preliminary understanding of this problem can be achieved thanks to the results reported in\cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
+occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
+with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+
+In this paper we aim to reach a deeper understanding of the possible effects of a finite computational basis set on the LR regime in open systems. To achieve this task we try to
+reformulate the relation between localization properties and basis independence for the main actors of the LR formalism. We present a discussion based on a double level analysis. First, 
+we propose a localization argument directly based on the inspection of the response density operator. Then, we move to a deeper level and investigate the properties of the susceptibility 
+functional, which represents the fundamental object in the contest of the linear response. Pursuing this approach we are naturally led to investigate the localization properties of excitation 
+operators, that in turn emerge as the resonant channel of the spectral decomposition of the susceptibility. In this way we establish a direct relation between the concept of basis independence 
+and the analytic structure of the linear response susceptibility.
+
+% First of all it is useful to discuss the property of the ground state under this perspective. 
+% Indeed, it is well known that the stability of the ground state and the localized nature of a molecular-like system ensures that the KS description of occupied states is represented 
+% by a discrete set of wave functions that approaches to zero far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide 
+% a reliable description of the ground state properties if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}.
+% The same arguments cannot be rigidly extended to the case in which an external time-dependent field starts acting on the system. Indeed, the perturbation drives the system out 
+% from the equilibrium and the electrons sample a wider region of the state space, that will contains orbitals of both negative (bound) and positive (unbound) energies.
 
@@
 
-Linear response can be effectively applied to the analysis of the electronic excitations in molecular and condensed-matter systems. In this framework one consider a system 
+In this section we review the fundamental equations which govern the behavior of an open quantum system in the linear response regime. Our analysis starts with a brief description of 
+the notation adopted in the paper. Then we move on the analysis of the response density and of the excitation operators, with the aim to establish their localization character.
+
+%The analysis presented in this section is devoted to a critical review of the fundamental equations which define the response density operator in the linear response regime.
+
+Linear response can be effectively applied to the analysis of the electronic excitations in molecular systems. In this framework one consider a system 
 described by the Hamiltonian $\hnot$ and assume that the ground-state density $\dmnot$ has been provided. Linear response formalism allows us to evaluate the modification 
@@
 
-The analysis presented in this section is devoted to a critical review of the fundamental equations which define the response density operator in the linear response regime.    
-The aim of this process is to....
-
-%the construction of two different representations of the response density operator...
-
-\subsection{Fluctuation states. A (de-)localization argument for the response density}
+\subsection{Fluctuation states. A localization argument for the response density}
 
@@
 in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
-\be
+\be\lb{rhoPrimeFluctuationStateDef2}
 \ket{f_p(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s(\omega)} \;,
@@
 For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
-% \be\lb{HelmholtzKernelDef1}
-% \bra{\r}\op G_H(\omega)\ket{\r'} = \frac{1}{4\pi} \left\{ 
-% \begin{matrix}
-% \frac{e^{-2k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega \leq |\eps_p| \\ 
-% \frac{e^{\ii k_p(\omega)|\r-\r'|}}{|\r-\r'|} \;,\; {\textrm for} \; \omega > |\eps_p|
-% \end{matrix}
-% \right. \;,
-% \ee
 \be\lb{HelmholtzKernelDef1}
 \bra{\r} \op G_H(\omega) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
-\frac{e^{2k|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; k^2 = \omega  < 0\; \\ 
-\frac{e^{2\ii k |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; k^2 = \omega > 0
+\frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \omega  < 0\; \\ 
+\frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \omega \geq 0
 \end{cases} \;,
 \ee
-and the $\r$-representation of the fluctuation states $f_p(\omega,\r)$ is expressed through a convolution integral between the kernel \eqref{HelmholtzKernelDef1} and
-$\brket{\r'}{s(\omega)}$.
-An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, 
-which govern the localization properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ behaves as a spherical wave and its
-convolution with the source term always give raises to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
+where $\alpha = \sqrt{2|\omega|}$.
+
+The localization character of fluctuation states can be determined by looking at the long range behavior of \eqref{rhoPrimeFluctuationStateDef2}, projected in the $\r$-representation.
+An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, which govern the localization 
+properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ behaves as a spherical wave and its convolution with the source term  gives 
+raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
 the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
@@
 
-\subsection{Excitation operators. A spectral decomposition representation for the response density}
+\subsection{Excitation operators. Spectral decomposition of the susceptibility functional}
 
-The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states, has evidenced some general properties of the linear response
+The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
 for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
-$\omega<|\eps_h|$. consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.
+$\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.
 

### 2018-03-22 AnalyticStructure_main.tex
push

@@
 \title{On the analytic structure of the linear response susceptibility in open systems}
+%\title{Effects of the basis set on the linear response for open systems}
 
@@
 
-In this section we review the fundamental equations which govern the behavior of an open quantum system in the linear response regime. Our analysis starts with a brief description of 
-the notation adopted in the paper. Then we move on the analysis of the response density and of the excitation operators, with the aim to establish their localization character.
-
-%The analysis presented in this section is devoted to a critical review of the fundamental equations which define the response density operator in the linear response regime.
+In this section we review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
+out within a highly complete real-space basis set that provides a precise description of the system in a finite computational domain. The purpose of the analysis is to determine the 
+asymptotic behavior of the main building blocks of the LR in the long range. Then we discuss the relation between localization properties and dependence of the results of LR from the 
+specific choice of the basis set and, in particular, from the dimension of the computation  domain.
 
@@
 \ee
-Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. Moreover, an analysis of the Liouville equation for the response density written in this 
-fashion evidences that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
+Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. An analysis of the Liouville equation for the response density written in this fashion evidences 
+that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
 \be\lb{fluctuationStateEqMotion1}
@@
 
-The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a \emph{localization argument} 
-for the fluctuation states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and solve \eqref{fluctuationStateEqMotion1} 
-in the form of a self-consistent inhomogeneous Helmholtz equation by writing:
+The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation 
+states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form 
+of a self-consistent inhomogeneous Helmholtz equation by writing:
 \be\lb{rhoPrimeFluctuationStateDef2}
@@
 \ee
-where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (\omega-\op T)^{-1}$, % with $k^2_p(\omega) = (\omega+\eps_p)$,
+where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (\omega-\op T)^{-1}$,
 and the \emph{source term} is given by:
@@
 properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ behaves as a spherical wave and its convolution with the source term  gives 
-raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega$ below the threshold,
+raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega < |\eps_p|$, % below the threshold,
 the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
@@
 
-% The knowledge of the long range behavior of the fluctuation states allows us to perform an assessment on the reliability of the evaluation of the linear response functional 
-% \eqref{LinearResponseFunctDef1}. To elaborate this statement we make usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, 
-% so that:
-% The knowledge of the long range behavior of the fluctuation states allows us to assess the spatial localization properties of the basic objects relevant in the contest of the 
-% linear response. In particular, making usage of the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear 
-% response functional \eqref{LinearResponseFunctDef1} as follows: 
-% This analysis indicates that the task of providing a reliable assessment of the linear response functional present a different level of complexity   .
-% Using the representation of the response density \eqref{rhoPrimeFluctuationStateDef1}, we can express the linear response functional as
-% \be\lb{LinearResponseFunctDef2}
-% \braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
-% \ee
-This argument can be easily extended to the linear response functional and allows us to determine the spatial localization features of the building blocks relevant for the linear response.  
-Indeed, the fluctuation states representation of the response density \eqref{rhoPrimeFluctuationStateDef1} implies that
+The localization properties of fluctuation states allows us to assess the reliability of the linear response functional computed using the given basis set. Indeed, writing the response 
+density in terms of fluctuation states implies that 
 \be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;.
+\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
 \ee
-An inspection of \eqref{LinearResponseFunctDef2} evidences that we can identify two different regimes, on the basis of the value of $\omega$. The first one, which we will refer to as the
-\emph{below threshold regime}, is realized for $\omega<|\eps_h|$. In this case the linear response functional is expressed in terms of genuinely localized quantities\footnote{This consideration 
-holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which possesses a physical cut-off radius. 
-Due to this behavior, the computational effort needed to provide a reliable evaluation of \eqref{LinearResponseFunctDef2} is determined by the capability of the chosen computational setup to 
-express bound-state like wave functions, in a analogous fashion of a ground state calculation.
+so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. 
+We observe that there exists two distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ 
+is lower than the ionization potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms 
+of genuinely localized quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long 
+range}, each of which possesses a physical cut-off radius.
+Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain is suitable to express the
+bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
 
-On the contrary, the evaluation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
+On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
 states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 

### 2018-04-10 AnalyticStructure_main.tex
update

@@
 \usepackage[english]{babel}
-%\usepackage[utf8x]{inputenc}
-%\usepackage[T1]{fontenc}
 
@@
 \usepackage{mathtools,braket}
+\usepackage{tikz}%,pgfplots}
 \usepackage{xifthen}
+%\pgfplotsset{compat=1.15}
 
@@
 
-In this section we review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
+We start by reviewing review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
 out within a highly complete real-space basis set that provides a precise description of the system in a finite computational domain. The purpose of the analysis is to determine the 
@@
 of the expectation value of a generic observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed 
-through the evaluation of the \emph{linear response functional}:
+through the evaluation of the \emph{linear response functional}
 \be\lb{LinearResponseFunctDef1}
-\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
+\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;.
 \ee
-where the operator $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
-under inspection. The modification of the ground-state density induced by the perturbation is expressed by the \emph{response density operator} $\dm'(\omega)$ that, in the linear 
-response regime, is a linear function of the perturbing field $\op\Phi(\omega)$. For this reason it is possible to define the \emph{susceptibility} superoperator, as follows:
-\be\lb{SusceptibilityDef1}
-\dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
+% where $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
+% under inspection. The modification of the ground-state density induced by the perturbation is expressed by the \emph{response density operator} $\dm'(\omega)$ that, in the linear 
+% response regime, is a linear function of the perturbing field $\op\Phi(\omega)$. For this reason it is possible to define the \emph{susceptibility} superoperator, as follows:
+% \be\lb{SusceptibilityDef1}
+% \dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
+% \ee
+% Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
+Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
+under inspection while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest
+of the linear response this object satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
+\be\lb{LiouvillianRhopomegaDef1}
+\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
 \ee
-Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
+and $\op\Phi(\omega)$ represents the perturbing field acting on the system.
 
@@
 occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
-as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are real functions, when 
-projected in the $\r$-representation.
+as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are desbribe by real 
+functions, when projected in the $\r$-representation.
 
-By considering the linear order time evolution of the eigenstates of $\hnot$ in presence of the perturbation we can derive the equation of motion of the response density in the form of 
-a quantum Liouville equation (for example see \cite{baroni2008}). This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
-$\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, as follows: 
+% By considering the linear order time evolution of the eigenstates of $\hnot$ in presence of the perturbation we can derive the equation of motion of the response density in the form of 
+% a quantum Liouville equation (for example see \cite{baroni2008}). This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
+% $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, as follows: 
+% \be\lb{rhoPrimeFluctuationStateDef1}
+% \dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
+% \ee
+% Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. An analysis of the Liouville equation for the response density written in this fashion evidences 
+% that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
+% \be\lb{fluctuationStateEqMotion1}
+% \left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'(\omega))\ket{\psi_p} \;,
+% \ee
+% where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and the operator $\op V'(\omega)$ is a perturbing term due to the 
+% density-dependence of the unperturbed Hamiltonian.
+
+The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transitions operator, linking the occupied and empty subspaces 
+of $\hnot$, and satisfies the \emph{transverse} condition  
+\be\lb{RhopTransverseDef1}
+\dm' = \dm_{\perp} \doteq \dmnot\dm'\op Q_0 + \op Q_0\dm'\dmnot
+\ee
+where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. Due to this fact it is possible to introduce an explicit representation of the 
+response density as follows 
 \be\lb{rhoPrimeFluctuationStateDef1}
-\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
+\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
 \ee
-Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. An analysis of the Liouville equation for the response density written in this fashion evidences 
-that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
+where we have defined the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, that span the empty subspace of $\hnot$. 
+%Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$.
+%derive the equation of motion of the response density in the form of a quantum Liouville equation (for example see \cite{baroni2008}). 
+An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
+written as a modified Sternheimer equations \cite{mahan1980}. The first-order Hamiltonian contains, apart from the perturbing field, a further term $\op V'[\dm']$ due to the density-dependence 
+of $\hnot$, and the equations read
 \be\lb{fluctuationStateEqMotion1}
-\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'(\omega))\ket{\psi_p} \;,
+%\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'(\omega))\ket{\psi_p} \;,
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;.
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and the operator $\op V'(\omega)$ is a perturbing term due to the 
-density-dependence of the unperturbed Hamiltonian.
-
-The interesting aspect of equations \eqref{fluctuationStateEqMotion1} in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation 
+%where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and t
+%and the operator $\op V'[\dm']$ described the further perturbing term due to the density-dependence of $\hnot$. % the unperturbed Hamiltonian.
+The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation 
 states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form 
@@
 
-As an explicit example in support of these arguments we compare the absorption spectrum of a benzene molecule computed in three distinct real-space basis set, which differs for the 
+As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the 
 dimension of the computational domain. Results evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational setup are clearly
@@
 
-\vspace{0.3cm}
-\noindent{TODO: Numerical example (convergence below threshold of the Benzene spectrum computed in different computational setup).}
-\vspace{0.3cm}
+\begin{figure}
+\includegraphics[scale=0.56]{co_spectrum.eps}
+\caption{\label{fig1}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+\end{figure}
 
@@
 
+In the linear 
+response regime, is a linear function of the perturbing field $\op\Phi(\omega)$. For this reason it is possible to define the \emph{susceptibility} superoperator, as follows:
+\be\lb{SusceptibilityDef1}
+\dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
+\ee
+Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
+
 Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
@@
 
-The starting point of this analysis is represented by the Liouville equation for the response density operator:
-\be\lb{LiouvillianRhopomegaDef1}
-\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;.
-\ee
 Using the spectral decomposition of the resolvent of the Liouvillian we have:
@@
 \be\lb{ExcitationOperatorsDef1}
-\Liouv \op E = E \op E \;, \qq
- \op{\tilde E} \Liouv = E \op{\tilde E}
+\Liouv \op E = E \op E \;, %\qq \op{\tilde E} \Liouv = E \op{\tilde E}
 \ee
+with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$. 
 We can express excitation operators as follows:
-\begin{align}\lb{ExcitationOperatorsDef2}
-\op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \nn \\
-\op {\tilde E} &= \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
+% \begin{align}\lb{ExcitationOperatorsDef2}
+% \op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \nn \\
+% \op {\tilde E} &= \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
+% \end{align}
+\be\lb{ExcitationOperatorsDef2}
+\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, 
+\ee
+We should therefore have
+\begin{align}
+\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= E \ket{\phi_p^E} \;, \\
+\left(\hnot - \eps_p\right)\ket{\chi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= -E \ket{\chi_p^E} \;.
 \end{align}
+And the orthonormalization of the excitation operators is translated as: 
+\be
+\sum_p \left(\braket{\phi_p^E | \phi_p^{E'}} + \braket{\chi_p^E | \chi_p^{E'}}\right) = \delta(E-E')
+\ee
+
+\begin{figure}
+
+\begin{tikzpicture}[scale=0.8]
+% axes
+\draw[->] (0,0) -- (8,0); %node[below] {$x$};
+\draw[->] (0,0) -- (0,6); %node[left] {$y$};
+]
+\draw[dashed,thin,color=gray] (0,5) -- (2,5);
+\draw (2,5) -- (8,5);
+\draw[dashed,thin,color=gray] (0,3) -- (4,3);
+\draw (4,3) -- (8,3);
+\draw[dashed,thin,color=gray] (0,1) -- (6,1);
+\draw (6,1) -- (8,1);
+
+\draw[dashed,very thin,color=black] (2,0) -- (2,5);
+\draw[dashed,very thin,color=black] (4,0) -- (4,3);
+\draw[dashed,very thin,color=black] (6,0) -- (6,1);
+
+%\draw (0,1) -- (3,1);
+
+% Draw axes
+%\draw [<->,thick] (0,5) node (yaxis) [above] {$y$}
+%    |- (5,0) node (xaxis) [below] {energy};
+
+\end{tikzpicture}
+
+\caption{\label{fig2}Excitation landscape.}
+\end{figure}1
 

### 2018-04-11 AnalyticStructure_main.tex
update

@@
 
-Linear response can be effectively applied to the analysis of the electronic excitations in molecular systems. In this framework one consider a system 
-described by the Hamiltonian $\hnot$ and assume that the ground-state density $\dmnot$ has been provided. Linear response formalism allows us to evaluate the modification 
-of the expectation value of a generic observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed 
-through the evaluation of the \emph{linear response functional}
+Linear response can be effectively applied to the analysis of the electronic excitations in molecular systems. In this framework one consider a system described by the Hamiltonian 
+$\hnot$ and assume that the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic 
+observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the 
+\emph{linear response functional}
 \be\lb{LinearResponseFunctDef1}
@@
 % Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
-Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
-under inspection while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest
-of the linear response this object satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
+Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
+while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the linear response 
+the response satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
 \be\lb{LiouvillianRhopomegaDef1}
@@
 occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
-as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are desbribe by real 
+as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are described by real 
 functions, when projected in the $\r$-representation.
@@
 where we have defined the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, that span the empty subspace of $\hnot$. 
-%Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$.
-%derive the equation of motion of the response density in the form of a quantum Liouville equation (for example see \cite{baroni2008}). 
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
-written as a modified Sternheimer equations \cite{mahan1980}. The first-order Hamiltonian contains, apart from the perturbing field, a further term $\op V'[\dm']$ due to the density-dependence 
-of $\hnot$, and the equations read
+written as a modified Sternheimer equations \cite{mahan1980}
 \be\lb{fluctuationStateEqMotion1}
-%\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'(\omega))\ket{\psi_p} \;,
-\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;.
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;,
 \ee
-%where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and t
-%and the operator $\op V'[\dm']$ described the further perturbing term due to the density-dependence of $\hnot$. % the unperturbed Hamiltonian.
+and we observe that the first-order Hamiltonian contains, apart from the perturbing field, a further term $\op V'[\dm']$ due to the density-dependence of $\hnot$.
+
 The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation 
@@
 
-As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the 
-dimension of the computational domain. Results evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational setup are clearly
-visible in the for values of $\omega$ that exceed the threshold value.
+As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the dimension of 
+the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
+setup are clearly visible in the for values of $\omega$ that exceed the threshold value.
 
@@
 \includegraphics[scale=0.56]{co_spectrum.eps}
-\caption{\label{fig1}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+\caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
 \end{figure}
@@
 
-\subsection{Excitation operators. Spectral decomposition of the susceptibility functional}
+\subsection{Excitation operators. The analytic structure of the susceptibility functional} %Spectral decomposition of the susceptibility functional}
 
-The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
-for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
-$\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort.
-
-In the linear 
-response regime, is a linear function of the perturbing field $\op\Phi(\omega)$. For this reason it is possible to define the \emph{susceptibility} superoperator, as follows:
+The localization properties of the response density can be reformulated in terms of the \emph{susceptibility functional}, implicitly defined trough the operator equation  
 \be\lb{SusceptibilityDef1}
@@
 \ee
-Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
+The main advantage of this approach relies on the fact that the susceptibility describes an intrinsic feature of the unperturbed system and its knowledge determines the LR properties 
+independently from the specific choice of the perturbing field.
 
-Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
-operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
-into the analytic structure of the linear response.
+The analysis is based on the spectral decomposition of the Liouville equation \eqref{LiouvillianRhopomegaDef1} and the make usage of the \emph{excitation operators}, defined through the 
+operator eigenvalue equation
+\be\lb{ExcitationOperatorsDef1}
+\Liouv \op E = E \op E \;, %\qq \op{\tilde E} \Liouv = E \op{\tilde E}
+\ee
+with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$.
+%\be
+%\trace{\op E\op E'} = \delta(E-E') \;. \nn
+%\ee
+The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. 
+This condition allows us to introduce a dyadic representation of excitations as follows
+\be\lb{ExcitationOperatorsDef2}
+\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, 
+\ee
+where the \emph{excited states} $\ket{\phi^E_p}$ and $\bra{\chi^E_p}$ span the domain of $\op Q_0$, \emph{i.e} the empty subspace of $\hnot$. The eigenvalue condition \eqref{ExcitationOperatorsDef1} 
+can thus be recasted in the form of a Sternheimer-like equations for the excited states
+\begin{align}
+\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= E \ket{\phi_p^E} \;, \\
+\bra{\chi_p^E}\left(\hnot - \eps_p\right) + \bra{\psi_p}\op V'[\op E]\op Q_0   &= -\bra{\chi_p^E} E  \;, \nn
+\end{align}
+and the orthonormalization condition of the excitation operators is expressed as 
+\be
+\sum_p \left(\braket{\phi_p^E | \phi_p^{E'}} + \braket{\chi_p^E | \chi_p^{E'}}\right) = \delta(E-E') \;. \nn
+\ee
+
+\vspace{1cm}
+
+% Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
+% operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
+% into the analytic structure of the linear response.
 
@@
 \sop{{\cal R}}(\omega) \cdot   =
-\sint\dd E \, \op E
+\left(\sum_E + \int\dd E   \right) \op E
 \frac{\trace{\opskew{\tilde E}\cdot}}{\omega-E} \;,
@@
 with $\opskew{O} = \commutator{\op O}{\dmnot}$.
-Excitation operators as eigenstates of the Liouvillian (keep left and right different or not?):
-\be\lb{ExcitationOperatorsDef1}
-\Liouv \op E = E \op E \;, %\qq \op{\tilde E} \Liouv = E \op{\tilde E}
-\ee
-with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$. 
-We can express excitation operators as follows:
-% \begin{align}\lb{ExcitationOperatorsDef2}
-% \op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, \nn \\
-% \op {\tilde E} &= \sum_p \left( \ket{\psi_p} \tbra{\phi^E_p} + \tket{\chi^E_p}\bra{\psi_p} \right)\;.
-% \end{align}
-\be\lb{ExcitationOperatorsDef2}
-\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, 
-\ee
-We should therefore have
-\begin{align}
-\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= E \ket{\phi_p^E} \;, \\
-\left(\hnot - \eps_p\right)\ket{\chi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= -E \ket{\chi_p^E} \;.
-\end{align}
-And the orthonormalization of the excitation operators is translated as: 
-\be
-\sum_p \left(\braket{\phi_p^E | \phi_p^{E'}} + \braket{\chi_p^E | \chi_p^{E'}}\right) = \delta(E-E')
-\ee
 
 \begin{figure}
-
 \begin{tikzpicture}[scale=0.8]
@@
 \draw[->] (0,0) -- (0,6); %node[left] {$y$};
-]
-\draw[dashed,thin,color=gray] (0,5) -- (2,5);
-\draw (2,5) -- (8,5);
-\draw[dashed,thin,color=gray] (0,3) -- (4,3);
-\draw (4,3) -- (8,3);
-\draw[dashed,thin,color=gray] (0,1) -- (6,1);
-\draw (6,1) -- (8,1);
-
+% orizontal lines
+\draw[dashed,thick,color=gray] (0,5) -- (2,5);
+\draw[very thick](2,5) -- (8,5);
+\draw[dashed,thick,color=gray] (0,3) -- (4,3);
+\draw[very thick] (4,3) -- (8,3);
+\draw[dashed,thick,color=gray] (0,1) -- (6,1);
+\draw[very thick] (6,1) -- (8,1);
+% vertical lines
 \draw[dashed,very thin,color=black] (2,0) -- (2,5);
@@
 \draw[dashed,very thin,color=black] (6,0) -- (6,1);
+% threshold levels labels
+\node[left] at (0,5) {$h$};
+\node[left] at (0,3) {$i$};
+\node[left] at (0,1) {$1$};
+\node[below] at (2,0){$|\eps_h|$};
+\node[below] at (4,0){$|\eps_i|$};
+\node[below] at (6,0){$|\eps_1|$};
+\node[below] at (4,-0.5) {Excitation energy};
+% bars at thresholds
+%\foreach \Point in {(2,5),(4,3),(6,1)}{
+%   \node at \Point {{\textbar}};%$\times$};
+%}
+\draw [very thick] (2,4.9) -- (2,5.1);
+\draw [very thick] (4,2.9) -- (4,3.1);
+\draw [very thick] (6,0.9) -- (6,1.1);
 
-%\draw (0,1) -- (3,1);
+% dotted vertical lines
+\draw[dotted,thick,color=black] (-0.2,3.6) -- (-0.2,4.4);
+\draw[dotted,thick,color=black] (-0.2,1.6) -- (-0.2,2.4);
 
-% Draw axes
-%\draw [<->,thick] (0,5) node (yaxis) [above] {$y$}
-%    |- (5,0) node (xaxis) [below] {energy};
+% discrete excitations
+\foreach \Point in {(0.5,5),(1.0,5),(1.8,5),(0.8,3),(1.3,3),(1.8,3),(2.4,3),(2.8,3),(3.4,3),(3.8,3),(0.7,1),(1.5,1),(1.9,1),(2.6,1),(2.9,1),(3.5,1),(4.1,1),(4.7,1),(5.7,1)}{
+    \node at \Point {\textbullet};
+}
 
 \end{tikzpicture}
+\caption{\label{ExcitationLandscape} Excitation landscape.}
+\end{figure}
 
-\caption{\label{fig2}Excitation landscape.}
-\end{figure}1
+%\subsection{Comments. The analytic structure of the linear response susceptibility}
+%
+%...........
 
-\subsection{Comments. The analytic structure of the linear response susceptibility}
+\section{Applications}
 
 ...........
+
+\section{Comments and conclusions}
+
+The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
+for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
+$\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort...
 

### 2018-04-12 AnalyticStructure_main.tex
update

@@
 \ee
-with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$.
+with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$ (WRONG!!!).
 %\be
@@
 \ee
+
+\vspace{0.3cm}
+\noindent{TODO: Identify the more convenient equations to present the localization argument on the excited states. 
+\vspace{0.3cm}
+
+Due to the previous argument we can state that the localization feature of the excited states depend on the energy of the excitation to which they belong. In particular if $E<\eps_p$ the
+state $\ket{\phi^E_p}$ behaves as a bound-state
+
+%defined in the dyadic representation of the excitation operators possess  that 
+%state that the excitation spectrum is
 

### 2018-04-13 AnalyticStructure_main.tex
update

--- 2018-04-11 AnalyticStructure_main.tex
@@
 Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
-while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the linear response 
-the response satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
+while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the LR the response 
+density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
 \be\lb{LiouvillianRhopomegaDef1}
@@
 \ee
-and $\op\Phi(\omega)$ represents the perturbing field acting on the system.
+where $\op\Phi(\omega)$ represents the perturbing field acting on the system.
 
 \subsection{Fluctuation states. A localization argument for the response density}
+\lb{FluctuationState}
 
@@
 functions, when projected in the $\r$-representation.
-
-% By considering the linear order time evolution of the eigenstates of $\hnot$ in presence of the perturbation we can derive the equation of motion of the response density in the form of 
-% a quantum Liouville equation (for example see \cite{baroni2008}). This procedure suggests us to introduce an explicit representation of the response density in terms of a set of 
-% $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, as follows: 
-% \be\lb{rhoPrimeFluctuationStateDef1}
-% \dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
-% \ee
-% Fluctuation states are, by construction, orthogonal to the occupied eigenstates of $\hnot$. An analysis of the Liouville equation for the response density written in this fashion evidences 
-% that their equations of motion are written in the form of a modified Sternheimer equation \cite{mahan1980}:
-% \be\lb{fluctuationStateEqMotion1}
-% \left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'(\omega))\ket{\psi_p} \;,
-% \ee
-% where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$ and the operator $\op V'(\omega)$ is a perturbing term due to the 
-% density-dependence of the unperturbed Hamiltonian.
 
@@
 \be\lb{rhoPrimeFluctuationStateDef1}
-\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
+\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
 \ee
-where we have defined the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, that span the empty subspace of $\hnot$. 
+Here we have defined the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, that span the empty subspace of $\hnot$. 
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
@@
 The analysis is based on the spectral decomposition of the Liouville equation \eqref{LiouvillianRhopomegaDef1} and the make usage of the \emph{excitation operators}, defined through the 
-operator eigenvalue equation
+left and right action eigenvalue equations 
 \be\lb{ExcitationOperatorsDef1}
-\Liouv \op E = E \op E \;, %\qq \op{\tilde E} \Liouv = E \op{\tilde E}
+\Liouv \op E = E \op E \qq \op{\tilde E} \Liouv = E \op{\tilde E} \;,
 \ee
-with the normalization condition $\trace{\op E\op E'} = \delta(E-E')$.
-%\be
-%\trace{\op E\op E'} = \delta(E-E') \;. \nn
-%\ee
-The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. 
-This condition allows us to introduce a dyadic representation of excitations as follows
-\be\lb{ExcitationOperatorsDef2}
-\op E = \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^E_p}\right)\;, 
-\ee
-where the \emph{excited states} $\ket{\phi^E_p}$ and $\bra{\chi^E_p}$ span the domain of $\op Q_0$, \emph{i.e} the empty subspace of $\hnot$. The eigenvalue condition \eqref{ExcitationOperatorsDef1} 
-can thus be recasted in the form of a Sternheimer-like equations for the excited states
-\begin{align}
-\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} &= E \ket{\phi_p^E} \;, \\
-\bra{\chi_p^E}\left(\hnot - \eps_p\right) + \bra{\psi_p}\op V'[\op E]\op Q_0   &= -\bra{\chi_p^E} E  \;, \nn
+with the normalization condition $\trace{\op{\tilde E}\op E'} = \delta(E-E')$. The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse 
+operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. This condition allows us to introduce a dyadic representation of excitations as follows
+\begin{align}\lb{ExcitationOperatorsDef2}
+\op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\tilde\chi^E_p}\right)\;, \nn \\
+\op{\tilde E} &= \sum_p \left( \ket{\chi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\tilde\phi^E_p}\right)\;,
+\end{align}
+and the \emph{excited states} $\ket{\phi^E_p}$ and $\bra{\tilde\chi^E_p}$ and their conjugates span the domain of $\op Q_0$, \emph{i.e} the empty subspace of $\hnot$.
+
+We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). In this case excitation
+eigenvalues come in pair. It is possible to show that and if a couple of left and right eigenstates satisfy \eqref{ExcitationOperatorsDef1} with energy $E$ than their transpose 
+%$(\op E,\op{\tilde E})$ $(\op E^t,\op{\tilde E}^t)$ 
+are eigenstates of the same equations with eigenvalue $-E$. Equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. 
+In particular, the left action eigenvalue equation provides
+%We further analyze the first equation of \eqref{ExcitationOperatorsDef1} under a.   
+%In this case the excitation eigenvalues come in pair and for each 
+%that can be recasted in the form of a Sternheimer-like equations for the excited states. We assume that
+%the condition $(\op V'[\op E])^t=\op V'[\op E^t]$
+%The eigenvalue 
+%condition \eqref{ExcitationOperatorsDef1} 
+%can thus be recasted in the 
+% \begin{align}
+% &\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} = E \ket{\phi_p^E} \;, \nn\\
+% &\left(\hnot - \eps_p\right)\ket{\tilde\chi_p^E} + \op Q_0\op V'[\op E^t]\ket{\psi_p}   = -E\ket{\tilde\chi_p^E}  \;, 
+% \end{align}
+\begin{align}\lb{ExcitationOperatorsDef3}
+&\left[E-(\hnot - \eps_p)\right] \ket{\phi_p^E} = \op Q_0 \op V'[\op E] \ket{\psi_p} \;, \nn\\
+&\left[-E-(\hnot - \eps_p)\right]\ket{\tilde\chi_p^E} = \op Q_0\op V'[\op E^t]\ket{\psi_p}  \;, 
 \end{align}
 and the orthonormalization condition of the excitation operators is expressed as 
-\be
-\sum_p \left(\braket{\phi_p^E | \phi_p^{E'}} + \braket{\chi_p^E | \chi_p^{E'}}\right) = \delta(E-E') \;. \nn
+\be\lb{ExcitedStateOrthNormDef1}
+\sum_p \left(\brket{\tilde\phi_p^E}{\phi_p^{E'}} + \brket{\tilde\chi_p^{E'}}{\chi_p^E}\right) = \delta(E-E') \;. 
 \ee
+Equations \eqref{ExcitationOperatorsDef3} allows us to present a localization argument for the excited states using the same procedure adopted for fluctuation states in 
+section \ref{FluctuationState}. Pursing this strategy we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows 
+\begin{align}
+&\ket{\phi^E_p} = \op G_H(E+\eps_p)\ket{s_{\phi}} \;, \nn \\
+&\ket{\tilde\chi^E_p} = \op G_H(-E+\eps_p)\ket{s_{\tilde\chi}} \;,
+\end{align}
+where $\op G_H$ is the Helmholtz Green function and the (self-consistent) source term $s_\phi$ and $s_{\tilde\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
+plus the action of the KS potential on the excited states.
 
-\vspace{1cm}
+We focus our analysis on solutions with positive energy, \emph{i.e.} with $E>0$. Looking at the coordinate representation of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we conclude
+that the Helmholtz kernel evaluated in $-E+\eps_p$ contains an exponential damping factor for positive values of $E$. As a consequence all the $\ket{\tilde\chi^E_p}$ states
+exhibit a bound-state behavior in the long range. Instead, the asymptotic character of $\op G_H(E+\eps_p)$ depends from the value of $E$ and $\ket{\phi^E_p}$ varies from a bound-state 
+like behavior for $E<|\eps_p|$, to a delocalized spherical-wave like character for values of $E>|\eps_p|$. 
+%On the contrary, the localization character of $\ket{\phi^E_p}$ varies from bound-state like solutions, for $E<|\eps_p|$, to delocalized spherical-wave like 
+%behavior for values of $E>|\eps_p|$. 
+There is however a novel aspect which did not emerged in the analysis of fluctuation states and is determined by the presence of the further condition \eqref{ExcitedStateOrthNormDef1}.
+%The consequence of this condition 
+To understand this point we observe that Sternheimer equations \eqref{ExcitationOperatorsDef3} are the first order expansion of a set of Hamiltonian eigenvalue equations. It is well known 
+that the normalization constraints have the effect of determining the quantization of accessible energy levels for bound-state solutions. 
+Excited states with $E<|\eps_p|$ constitute a genuine \emph{discrete} set while the ones in the unbound energy range $E>|\eps_p|$ belong to a continuum.
+
+This considerations determine the structure of the excitations spectrum and essentially evidence that there exists two distinct sectors of the exctiation spectrum. The first one is composed by
+localized excitations built in terms of excited states below their threshold level. This set has a finite number of elements.
 
@@
 
-Using the spectral decomposition of the resolvent of the Liouvillian we have:
-\be\lb{RhopExcitationDef1}
-\sop{{\cal R}}(\omega) \cdot   =
-\left(\sum_E + \int\dd E   \right) \op E
-\frac{\trace{\opskew{\tilde E}\cdot}}{\omega-E} \;,
-\ee
-with $\opskew{O} = \commutator{\op O}{\dmnot}$.
-
-\begin{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
 \begin{tikzpicture}[scale=0.8]
 % axes
-\draw[->] (0,0) -- (8,0); %node[below] {$x$};
-\draw[->] (0,0) -- (0,6); %node[left] {$y$};
+\draw[->] (0,0) -- (8,0); 
+\draw[->] (0,0) -- (0,6);
 % orizontal lines
@@
 \draw[very thick] (6,1) -- (8,1);
-% vertical lines
+% % vertical lines
 \draw[dashed,very thin,color=black] (2,0) -- (2,5);
@@
 \draw[dashed,very thin,color=black] (6,0) -- (6,1);
-% threshold levels labels
+% % threshold levels labels
 \node[left] at (0,5) {$h$};
@@
 %}
-\draw [very thick] (2,4.9) -- (2,5.1);
-\draw [very thick] (4,2.9) -- (4,3.1);
-\draw [very thick] (6,0.9) -- (6,1.1);
-
+\draw[very thick] (2,4.9) -- (2,5.1);
+\draw[very thick] (4,2.9) -- (4,3.1);
+\draw[very thick] (6,0.9) -- (6,1.1);
 % dotted vertical lines
-\draw[dotted,thick,color=black] (-0.2,3.6) -- (-0.2,4.4);
-\draw[dotted,thick,color=black] (-0.2,1.6) -- (-0.2,2.4);
-
+%\draw[dotted,thick,color=black] (-0.2,3.6) -- (-0.2,4.4);
+%\draw[dotted,thick,color=black] (-0.2,1.6) -- (-0.2,2.4);
 % discrete excitations
@@
 }
-
 \end{tikzpicture}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Using the spectral decomposition of the resolvent of the Liouvillian we have
+\be\lb{RhopExcitationDef1}
+\sop{{\cal R}}(\omega) \cdot   =
+\left(\sum_E + \int\dd E   \right) \op E \,
+\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;.
+\ee
+%with $\opskew{O} = \commutator{\op O}{\dmnot}$.
 
@@
 
-...........
-
 \section{Comments and conclusions}
@@
 $\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort...
+
+\appendix
+\section{Eigenvalue equations of the Liouvillian superoperator}
+
+Derive the equations of motion for the excited states. Discussion of the effects of various supplementary conditions...
+
+\section{Casida equations}
+
+From the equations of motion for the excited states to the Casida equations...
 

### 2018-04-16 AnalyticStructure_main.tex
update

@@
 the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
-setup are clearly visible in the for values of $\omega$ that exceed the threshold value.
+setup are clearly visible for values of $\omega$ that exceed the threshold value.
 
@@
 
-%This analysis, carried out starting from the representation of the linear response functional in terms of fluctuation states, evidences some general properties of the linear response. 
-%In the next sections we will reformulate an analogous procedure directly looking at the susceptibility. This analysis lead us to the core of the paper, namely the description of the
-%analytical structure of the linear response susceptibility.
-
 \subsection{Excitation operators. The analytic structure of the susceptibility functional} %Spectral decomposition of the susceptibility functional}
 
-The localization properties of the response density can be reformulated in terms of the \emph{susceptibility functional}, implicitly defined trough the operator equation  
+The study of the localization properties of the LR functional, formerly discussed through the inspection of the response density operator, can be reformulated in terms of the 
+\emph{susceptibility functional}, defined trough the operator equation  
+%The localization properties of the response density can be reformulated in terms of the \emph{susceptibility functional}, implicitly defined trough the operator equation  
 \be\lb{SusceptibilityDef1}
@@
 \ee
-The main advantage of this approach relies on the fact that the susceptibility describes an intrinsic feature of the unperturbed system and its knowledge determines the LR properties 
-independently from the specific choice of the perturbing field.
+This reformulation of the problem has the advantage of providing some general information on the nature of the excitation spectrum of the system. Results achieved in this way thus 
+describes an intrinsic feature of the system and determine the properties of the LR independently from the specific choice of the perturbing field. 
+%The main advantage of this approach relies on the fact that the susceptibility describes an intrinsic feature of the unperturbed system and its knowledge determines the LR properties 
+%independently from the specific choice of the perturbing field.
 
@@
 \ee
-with the normalization condition $\trace{\op{\tilde E}\op E'} = \delta(E-E')$. The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse 
+together with the operator orthonormalization condition %$\trace{\op{\tilde E}\op E'} = \delta(E-E')$. 
+\be\lb{orthoExcitatioOpDef1}
+\trace{\op{\tilde E}\op E'} = \delta(E-E')
+\ee
+The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse 
 operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. This condition allows us to introduce a dyadic representation of excitations as follows
@@
 \end{align}
-and the \emph{excited states} $\ket{\phi^E_p}$ and $\bra{\tilde\chi^E_p}$ and their conjugates span the domain of $\op Q_0$, \emph{i.e} the empty subspace of $\hnot$.
+where both the \emph{excited states} $\ket{\phi^E_p}$, $\bra{\tilde\chi^E_p}$ and their conjugates span the empty subspace of $\hnot$.
 
-We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). In this case excitation
-eigenvalues come in pair. It is possible to show that and if a couple of left and right eigenstates satisfy \eqref{ExcitationOperatorsDef1} with energy $E$ than their transpose 
-%$(\op E,\op{\tilde E})$ $(\op E^t,\op{\tilde E}^t)$ 
-are eigenstates of the same equations with eigenvalue $-E$. Equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. 
+We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). 
+%In this case excitation eigenvalues come in pair. It is possible to show that and if a couple of left and right eigenstates satisfy \eqref{ExcitationOperatorsDef1} with energy $E$ 
+%than their transpose %$(\op E,\op{\tilde E})$ $(\op E^t,\op{\tilde E}^t)$ 
+%are eigenstates of the same equations with eigenvalue $-E$. 
+Equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. 
 In particular, the left action eigenvalue equation provides   
-%We further analyze the first equation of \eqref{ExcitationOperatorsDef1} under a.   
-%In this case the excitation eigenvalues come in pair and for each 
-%that can be recasted in the form of a Sternheimer-like equations for the excited states. We assume that
-%the condition $(\op V'[\op E])^t=\op V'[\op E^t]$
-%The eigenvalue 
-%condition \eqref{ExcitationOperatorsDef1} 
-%can thus be recasted in the 
-% \begin{align}
-% &\left(\hnot - \eps_p\right) \ket{\phi_p^E} + \op Q_0 \op V'[\op E] \ket{\psi_p} = E \ket{\phi_p^E} \;, \nn\\
-% &\left(\hnot - \eps_p\right)\ket{\tilde\chi_p^E} + \op Q_0\op V'[\op E^t]\ket{\psi_p}   = -E\ket{\tilde\chi_p^E}  \;, 
-% \end{align}
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 \end{align}
-and the orthonormalization condition of the excitation operators is expressed as 
+and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies %among the excitation operators is expressed as 
 \be\lb{ExcitedStateOrthNormDef1}
@@
 \end{align}
-where $\op G_H$ is the Helmholtz Green function and the (self-consistent) source term $s_\phi$ and $s_{\tilde\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
+where $\op G_H$ is the Helmholtz Green function, while the (self-consistent) source term $s_\phi$ and $s_{\tilde\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
 plus the action of the KS potential on the excited states.
 
-We focus our analysis on solutions with positive energy, \emph{i.e.} with $E>0$. Looking at the coordinate representation of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we conclude
-that the Helmholtz kernel evaluated in $-E+\eps_p$ contains an exponential damping factor for positive values of $E$. As a consequence all the $\ket{\tilde\chi^E_p}$ states
-exhibit a bound-state behavior in the long range. Instead, the asymptotic character of $\op G_H(E+\eps_p)$ depends from the value of $E$ and $\ket{\phi^E_p}$ varies from a bound-state 
-like behavior for $E<|\eps_p|$, to a delocalized spherical-wave like character for values of $E>|\eps_p|$. 
-%On the contrary, the localization character of $\ket{\phi^E_p}$ varies from bound-state like solutions, for $E<|\eps_p|$, to delocalized spherical-wave like 
-%behavior for values of $E>|\eps_p|$. 
-There is however a novel aspect which did not emerged in the analysis of fluctuation states and is determined by the presence of the further condition \eqref{ExcitedStateOrthNormDef1}.
-%The consequence of this condition 
-To understand this point we observe that Sternheimer equations \eqref{ExcitationOperatorsDef3} are the first order expansion of a set of Hamiltonian eigenvalue equations. It is well known 
-that the normalization constraints have the effect of determining the quantization of accessible energy levels for bound-state solutions. 
-Excited states with $E<|\eps_p|$ constitute a genuine \emph{discrete} set while the ones in the unbound energy range $E>|\eps_p|$ belong to a continuum.
+It is possible to show that excitation eigenvalues come in pair and we focus our analysis on solutions with positive energy, \emph{i.e.} with $E>0$. Looking at the coordinate representation 
+of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we observe that the Helmholtz kernel evaluated in $-E+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of $E$. 
+As a consequence all the $\ket{\tilde\chi^E_p}$ states exhibit a bound-state behavior in the long range. Instead, the asymptotic character of $\op G_H(E+\eps_p)$ depends from $E$ and we can 
+identify the threshold value $E=|\eps_p|$ in terms of which $\ket{\phi^E_p}$ changes from a bound-state like behavior to a delocalized spherical-wave like character.  
+Furthermore, the orthonormalization conditions \eqref{ExcitedStateOrthNormDef1} act as a ulterior constraint for the bound-state solutions and have the effect of determining the quantization of 
+the corresponding energy levels\footnote{Sternheimer equations represent the first order expansion of a set of Hamiltonian eigenvalue equations. Consequently the properties of their solution...}.
+We conclude that all the states $\ket{\tilde\chi^E_p}$ and the $\ket{\phi^E_p}$ with $E$ below the threshold value constitute a genuine \emph{discrete} set, while the ones in the unbound 
+energy range behaves as generalized eigenvectors associated to a continuum spectrum.
 
-This considerations determine the structure of the excitations spectrum and essentially evidence that there exists two distinct sectors of the exctiation spectrum. The first one is composed by
-localized excitations built in terms of excited states below their threshold level. This set has a finite number of elements.
+%To complete the analysis we have to take into account the orthonormalization constraints \eqref{ExcitedStateOrthNormDef1}. Sternheimer equations \eqref{ExcitationOperatorsDef3} are the 
+%first order expansion of a set of Hamiltonian eigenvalue equations.  
+%Moreover, there is a further consequence due to the orthonormalization condition \eqref{ExcitedStateOrthNormDef1}.
+%There is however a novel aspect which did not emerged in the analysis of fluctuation states and is 
+%To understand this point we observe that Sternheimer equations \eqref{ExcitationOperatorsDef3} are the first order expansion of a set of Hamiltonian eigenvalue equations. It is well known 
+%that the normalization constraints have the effect of determining the quantization of accessible energy levels for bound-state solutions.
+
+This considerations allows us to determine the structure of the excitations spectrum. To achieve this result we assume to have solved the equations \eqref{ExcitedStateOrthNormDef1} for a 
+value of $E$.
+
+%Given an excitation operator in the form \eqref{ExcitationOperatorsDef2}
+
+%and essentially evidence that there exists two distinct sectors of the exctiation spectrum. The first one is composed by
+%localized excitations built in terms of excited states below their threshold level. This set has a finite number of elements.
 
@@
 \begin{figure}[t]
-\begin{tikzpicture}[scale=0.8]
+\begin{tikzpicture}[scale=0.78]
 % axes
@@
 % % threshold levels labels
-\node[left] at (0,5) {$h$};
-\node[left] at (0,3) {$i$};
-\node[left] at (0,1) {$1$};
+\node[left] at (0,5) {$l_h$};
+\node[left] at (0,3) {$l_i$};
+\node[left] at (0,1) {$l_1$};
 \node[below] at (2,0){$|\eps_h|$};

### 2018-04-17 AnalyticStructure_main.tex
update

@@
 \emph{susceptibility functional}, defined trough the operator equation  
-%The localization properties of the response density can be reformulated in terms of the \emph{susceptibility functional}, implicitly defined trough the operator equation  
 \be\lb{SusceptibilityDef1}
@@
 \ee
-This reformulation of the problem has the advantage of providing some general information on the nature of the excitation spectrum of the system. Results achieved in this way thus 
-describes an intrinsic feature of the system and determine the properties of the LR independently from the specific choice of the perturbing field. 
-%The main advantage of this approach relies on the fact that the susceptibility describes an intrinsic feature of the unperturbed system and its knowledge determines the LR properties 
-%independently from the specific choice of the perturbing field.
+This reformulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
+feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field.
 
@@
 
-We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). 
-%In this case excitation eigenvalues come in pair. It is possible to show that and if a couple of left and right eigenstates satisfy \eqref{ExcitationOperatorsDef1} with energy $E$ 
-%than their transpose %$(\op E,\op{\tilde E})$ $(\op E^t,\op{\tilde E}^t)$ 
-%are eigenstates of the same equations with eigenvalue $-E$. 
-Equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. 
-In particular, the left action eigenvalue equation provides   
+We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). Equations 
+\eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. In particular, the left action eigenvalue equation provides   
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 
-%To complete the analysis we have to take into account the orthonormalization constraints \eqref{ExcitedStateOrthNormDef1}. Sternheimer equations \eqref{ExcitationOperatorsDef3} are the 
-%first order expansion of a set of Hamiltonian eigenvalue equations.  
-%Moreover, there is a further consequence due to the orthonormalization condition \eqref{ExcitedStateOrthNormDef1}.
-%There is however a novel aspect which did not emerged in the analysis of fluctuation states and is 
-%To understand this point we observe that Sternheimer equations \eqref{ExcitationOperatorsDef3} are the first order expansion of a set of Hamiltonian eigenvalue equations. It is well known 
-%that the normalization constraints have the effect of determining the quantization of accessible energy levels for bound-state solutions.
+The structure of the excitation spectrum follows from the properties of the excited states described above. To clarify this point we consider a value of $E$ for which equations 
+\eqref{ExcitationOperatorsDef1} admit a solution and, consequently, equations \eqref{ExcitationOperatorsDef3} possess a solution where \emph{at least} one of the excited states is non vanishing. 
+According to \eqref{ExcitationOperatorsDef2}, $\op E$ is expressed in terms of these states and we denote with $p=p_m$ the label of the non vanishing $\ket{\phi^E_p}$ state with the highest value 
+of $|\eps_p|$. From the previous considerations it emerge that if $E<|\eps_{p_m}|$ \emph{all} the excited states that contribute to the dyadic representation of the excitation operator possess a 
+bound-state like behavior. Excitations of this type thus represent localized quantities and the associated eigenvalue are discrete. On the contrary, for $E>|\eps_{p_m}|$, excitations have a 
+delocalized character and the corresponding eigenvalues belong to a continuum of accessible values.
 
-This considerations allows us to determine the structure of the excitations spectrum. To achieve this result we assume to have solved the equations \eqref{ExcitedStateOrthNormDef1} for a 
-value of $E$.
-
-%Given an excitation operator in the form \eqref{ExcitationOperatorsDef2}
-
-%and essentially evidence that there exists two distinct sectors of the exctiation spectrum. The first one is composed by
-%localized excitations built in terms of excited states below their threshold level. This set has a finite number of elements.
-
-% Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
-% operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
-% into the analytic structure of the linear response.
+The typical structure of the excitation spectrum is represented in figure \ref{ExcitationLandscape}. 
+Excitations are separated into two categories (add comment on the observable character of localized excitations). 
+The plot evidences that below the first ionization energy $|\eps_h|$ the spectrum is purely composed by a discrete set of localized excitations.
+Instead, in the intermediate energy interval that extends
+from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the discrete sector of the spectrum is embedded in a continuum of excitations delocalized in the whole accessible space. Lastly,
+for energies higher than $|\eps_1|$ only delocalized excitations are present.
 
@@
 % % threshold levels labels
-\node[left] at (0,5) {$l_h$};
-\node[left] at (0,3) {$l_i$};
-\node[left] at (0,1) {$l_1$};
+\node[left] at (0,5) {$p_h$};
+\node[left] at (0,3) {$p_i$};
+\node[left] at (0,1) {$p_1$};
 \node[below] at (2,0){$|\eps_h|$};
@@
 \node[below] at (6,0){$|\eps_1|$};
-\node[below] at (4,-0.5) {Excitation energy};
+\node[below] at (4,-0.5) {excitation energy};
 % bars at thresholds
@@
 \end{tikzpicture}
-\caption{\label{ExcitationLandscape} Excitation landscape.}
+\caption{\label{ExcitationLandscape} Excitation landscape. Excitation are split in horizontal line according to the threshold levels $p_m$. Filled bullet refers to localized
+excitations whereas the tick black lines describe delocalized excitation with a continuum spectrum.}
 \end{figure}
@@
 
-Using the spectral decomposition of the resolvent of the Liouvillian we have
+The knowledge of the excitations spectrum allows us to expand the LR susceptibility in terms of excitations. Indeed we can make usage of the spectral decomposition of the resolvent
+of the Liouvillian. This procedure allows us to formally solve the Liouville equation \eqref{LiouvillianRhopomegaDef1} and we have 
+%Using the spectral decomposition of the resolvent of the Liouvillian we have
 \be\lb{RhopExcitationDef1}
@@
 \ee
-%with $\opskew{O} = \commutator{\op O}{\dmnot}$.
 
-%\subsection{Comments. The analytic structure of the linear response susceptibility}
-%
-%...........
+% Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
+% operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
+% into the analytic structure of the linear response.
+
+\subsection{Comments. Physical meaning of the excitation spectrum}
+
+True poles vs spectral function....
 
 \section{Applications}
+
+% \begin{figure}{h}
+% \includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
+% \caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+% \end{figure}
 

### 2018-04-19 AnalyticStructure_main.tex
update

@@
-\documentclass[reprint,aps,prb]{revtex4-1}
+\documentclass[reprint,aps,prl]{revtex4-1}
 
@@
 The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
-This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT)\cite{runge1984,onida2002}, that allows one to establish the time-dependent 
+This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT) \cite{runge1984,onida2002}, that allows one to establish the time-dependent 
 Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time.
@@
 We focus our attention to the linear response regime (LR) in which the theory can be conveniently expressed in the frequency domain and the time-dependent KS equation are reformulated 
-as a quantum Liouville equation for the response density operator. Different computational approaches have been developed in literature\cite{baroni2008,hubener2014,brabec2015}, principally 
+as a quantum Liouville equation for the response density operator. Different computational approaches have been developed in literature \cite{baroni2008,hubener2014,brabec2015}, principally 
 with the aim of producing efficient algorithms for the evaluation of the physical observables. These methods differ both for the procedure adopted to solve the Liouville equation 
@@
 
-A preliminary understanding of this problem can be achieved thanks to the results reported in\cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
+A preliminary understanding of this problem can be achieved thanks to the results reported in \cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
 occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
@@
 % by a discrete set of wave functions that approaches to zero far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide 
-% a reliable description of the ground state properties if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals\cite{boffi2016}.
+% a reliable description of the ground state properties if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals \cite{boffi2016}.
 % The same arguments cannot be rigidly extended to the case in which an external time-dependent field starts acting on the system. Indeed, the perturbation drives the system out 
@@
 \ee
-so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. 
-We observe that there exists two distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ 
-is lower than the ionization potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms 
-of genuinely localized quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long 
-range}, each of which possesses a physical cut-off radius.
-Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain is suitable to express the
-bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
+so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. We observe that there exists two 
+distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ is lower than the ionization 
+potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms of genuinely localized 
+quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which 
+possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
+is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
 
@@
 
-\subsection{Excitation operators. The analytic structure of the susceptibility functional} %Spectral decomposition of the susceptibility functional}
+\subsection{Excitation operators. The analytic structure of the susceptibility functional} %The spectrum of the Liouville superoperator
 
@@
 
-The structure of the excitation spectrum follows from the properties of the excited states described above. To clarify this point we consider a value of $E$ for which equations 
-\eqref{ExcitationOperatorsDef1} admit a solution and, consequently, equations \eqref{ExcitationOperatorsDef3} possess a solution where \emph{at least} one of the excited states is non vanishing. 
-According to \eqref{ExcitationOperatorsDef2}, $\op E$ is expressed in terms of these states and we denote with $p=p_m$ the label of the non vanishing $\ket{\phi^E_p}$ state with the highest value 
-of $|\eps_p|$. From the previous considerations it emerge that if $E<|\eps_{p_m}|$ \emph{all} the excited states that contribute to the dyadic representation of the excitation operator possess a 
-bound-state like behavior. Excitations of this type thus represent localized quantities and the associated eigenvalue are discrete. On the contrary, for $E>|\eps_{p_m}|$, excitations have a 
-delocalized character and the corresponding eigenvalues belong to a continuum of accessible values.
+The structure of the excitation spectrum follows from the properties of the excited states described above. To clarify this point we consider a value of $E$ that satisfies equations
+\eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} possess a solution in which \emph{at least} one of the excited states 
+is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^E_p}$  with the highest value of $|\eps_p|$ among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
+considerations it emerge that if $E<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
+of this type thus represent localized quantities and the associated eigenvalue are discrete. On the contrary, for $E>|\eps_{p_m}|$ some (or all) of the excited states in the dyadic representation
+of the excitation behave as generalized eigenvectors and the corresponding eigenvalue belong to a continuum of accessible values.
+
+This analysis evidences that the spectrum of the excitation operators contains two distinct sectors. The first one is composed by a (finite) set of localized excitation with associated discrete 
+eigenvalues. Extending the results of \cite{boffi2016} to the equation of motion of \eqref{ExcitationOperatorsDef3} we conclude that the elements of this category behave as \emph{observables} 
+quantities and the associated excitation energies have a true physical meaning, independently from the computational setup used for their representation. Conversely, the second sector is made by 
+a dense set of delocalized excitations with a continuum spectrum. The elements of this set behaves as the unbound virtual orbitals analyzed in \cite{boffi2016}....
+
+The knowledge of the excitations spectrum allows us to expand the LR susceptibility in terms of excitations. Indeed we can make usage of the spectral decomposition of the resolvent
+of the Liouvillian. This procedure allows us to formally solve the Liouville equation \eqref{LiouvillianRhopomegaDef1} and we have 
+\be\lb{RhopExcitationDef1}
+\sop{{\cal R}}(\omega) \cdot   =
+\left(\sum_E + \int\dd E   \right) \op E \,
+\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;.
+\ee
 
 The typical structure of the excitation spectrum is represented in figure \ref{ExcitationLandscape}. 
-Excitations are separated into two categories (add comment on the observable character of localized excitations). 
+Excitations are separated into two categories. 
 The plot evidences that below the first ionization energy $|\eps_h|$ the spectrum is purely composed by a discrete set of localized excitations.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[ht]
 \begin{tikzpicture}[scale=0.78]
@@
 \node[left] at (0,1) {$p_1$};
-\node[below] at (2,0){$|\eps_h|$};
-\node[below] at (4,0){$|\eps_i|$};
-\node[below] at (6,0){$|\eps_1|$};
+\node[below] at (2,0) {$|\eps_h|$};
+\node[below] at (4,0) {$|\eps_i|$};
+\node[below] at (6,0) {$|\eps_1|$};
 \node[below] at (4,-0.5) {excitation energy};
@@
 
-The knowledge of the excitations spectrum allows us to expand the LR susceptibility in terms of excitations. Indeed we can make usage of the spectral decomposition of the resolvent
-of the Liouvillian. This procedure allows us to formally solve the Liouville equation \eqref{LiouvillianRhopomegaDef1} and we have 
-%Using the spectral decomposition of the resolvent of the Liouvillian we have
-\be\lb{RhopExcitationDef1}
-\sop{{\cal R}}(\omega) \cdot   =
-\left(\sum_E + \int\dd E   \right) \op E \,
-\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;.
-\ee
-
 % Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
@@
 
-\subsection{Comments. Physical meaning of the excitation spectrum}
+\subsection{Discrete poles and spectral function. Physical meaning of the excitation spectrum} %{Comments. Physical meaning of the excitation spectrum}
 
@@
 
-% \begin{figure}{h}
-% \includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
-% \caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
-% \end{figure}
+Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value
+obtained through a finite difference method.
+
+\subsection{Results for the benzene molecule}
+
+\begin{figure}[h]
+\includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
+\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+\end{figure}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% In the framework of the linear response formalism one is typically interested in computing the \emph{linear response functional}:
-% \be\lb{LinearResponseFunctDef1}
-% {\cal R}_{\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
-% \ee
-% that represents the perturbation-induced modification of the expectation value of an observable $\op O$\footnote{For a sake of concreteness, we are limiting our considerations 
-% to observables that do not explicitly depend on time}. Here $\dm'(\omega)$ is the \emph{response density operator} that describes the $\omega$-dependent modification of the density 
-% operator induced by the perturbation.
-% 
-% \subsection{Basic equations for the linear response formalism for electronic excitations}
-% 
-% The linear response formalism can be effectively applied to the analysis of the electronic excitations of molecular and condensed-matter systems, described by the (density-dependent) 
-% ground-state hermitian Hamiltonian $\hnot$, coupled to an external perturbation described by the perturbing field $\op\Phi(\omega)$. The $\omega$ structure of $\op\Phi(\omega)$ codifies both 
-% the intrinsic time dependence of the perturbation and the switching-on procedure, \emph{e.g.} adiabatic or sudden limit protocols. 
-% 
-% The response density is expressed as the first-order variation of ground state density
-% \be\label{rhodef1}
-% \dmnot = \sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}  \;,
-% \ee
-% where $\{\psi_p\}$ denote the occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy lower than the Fermi level.
-% By considering the linear order time evolution of these states in presence of the perturbation we can express the response density in the $\omega$ domain as follows:
-% \be\lb{rhoPrimeOmegaDef1}
-% \dm'(\omega) = \ii \commutator{\dmnot}{\op A(\omega)} \;,
-% \ee
-% where $\op A(\omega)$ is a sum of two terms, both written as a triple convolution with the retarded/advanced Green functions $\op G_0^{\pm}$ of the unperturbed Hamiltonian:
-% \be
-% \op A(\omega) = \frac{1}{2\pi} \int_{-\infty}^\infty  \dd \omega'
-% \op G_0^+(\omega') \left(\op \Phi(\omega)+\op V'(\omega)\right) \op G_0^-(\omega'-\omega)\;. \nn
-% \ee
-% The presence of the second addend is due to the density dependence of the unperturbed Hamiltonian and describes the perturbation induced by the variation of $\hnot$ under the
-% action of the perturbing field. In the linear response regime this quantity can be expressed as the functional derivatives of $\hnot$ with respect to the density kernel 
-% (evaluated at $\dm=\dmnot$) times the value of the induced density modification, that is:
-% \be\label{VpDef1}
-% \op V'(\omega)= 
-% \int \dd \r \dd \r' \frac{\delta\hnot}{\delta \rho_0(\r,\r')}
-% \trace{\dm'(\omega) \ket{\r} \bra{\r'}} \;.
-% \ee
-% 
-% \subsection{Fluctuation states. A localization argument for the linear response functional}
-% 
-% We start this analysis by deriving an ulterior expression of the response density operator in the frequency space. We consider equation \eqref{rhoPrimeOmegaDef1} and observe that, for any 
-% operator $\op O$, we may write:  
-% \be
-% \commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot\;,
-% \ee
-% where $\op Q_0= \identity - \dmnot$ is the projection operator in the subspace orthogonal to $\dmnot$. So, thanks to this relation we have that:
-% \be
-% \dm'(\omega) = \ii\sum_p\left(\ketbra{\psi_p}{\psi_p}\op A(\omega)\op Q_0 - \op Q_0\op A(\omega)\ketbra{\psi_p}{\psi_p}\right) \;.
-% \ee
-% This equation suggests us to define the \emph{fluctuation states}:
-% \be\lb{fluctuationStateDef1}
-% \ket{f_p(\omega)} \doteq -\ii\op Q_0\op A(\omega)\ket{\psi_p} \;, \quad
-% \bra{f_p(\omega)} \doteq \bra{\psi_p}\ii\op A(-\omega)\op Q_0 \;,
-% \ee
-% where the $\omega$ dependence of the bra is consistent with hermitian conjugation property of the Fourier transform of a hermitian operator. Fluctuation states are, by 
-% definition, orthogonal to the occupied eigenstates of $\hnot$, so that:
-% \be
-% \brket{f_p(\omega)}{\psi_q} = \brket{\psi_q}{f_p(\omega)} = 0 \;, \forall \, p,q,\omega \;.
-% \ee
-% The response density written in terms of the fluctuation states reads:
-% \be\lb{rhoPrimeFluctuationStateDef1}
-% \dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;,
-% \ee
-% and consequently the linear response functional can be expressed as:
-% \be\lb{LinearResponseFunctDef2}
-% {\cal R}_{\op O}(\omega) = 
-% \sum_p\left(\bra{f_p(-\omega)}\op O\ket{\psi_p} + \bra{\psi_p}\op O\ket{f_p(\omega)}\right) \;.
-% \ee
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+%\bibliographystyle{apsrev4-1}
 \bibliography{Analytic_biblio}

### 2018-04-23 AnalyticStructure_main.tex
update

@@
-\documentclass[reprint,aps,prl]{revtex4-1}
+\documentclass[reprint,aps,prb]{revtex4-1}
 
@@
 \subsection{Fluctuation states. A localization argument for the response density}
-\lb{FluctuationState}
+\label{FluctuationState}
 
@@
 Furthermore, the orthonormalization conditions \eqref{ExcitedStateOrthNormDef1} act as a ulterior constraint for the bound-state solutions and have the effect of determining the quantization of 
-the corresponding energy levels\footnote{Sternheimer equations represent the first order expansion of a set of Hamiltonian eigenvalue equations. Consequently the properties of their solution...}.
+the corresponding energy levels \footnote{Sternheimer equations represent the first order expansion of a set of Hamiltonian eigenvalue equations. Consequently the properties of their solution...}.
 We conclude that all the states $\ket{\tilde\chi^E_p}$ and the $\ket{\phi^E_p}$ with $E$ below the threshold value constitute a genuine \emph{discrete} set, while the ones in the unbound 
@@
 \eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} possess a solution in which \emph{at least} one of the excited states 
-is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^E_p}$  with the highest value of $|\eps_p|$ among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
+is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^E_p}$  with the highest value of $|\eps_p|$, among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
 considerations it emerge that if $E<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
@@
 
-This analysis evidences that the spectrum of the excitation operators contains two distinct sectors. The first one is composed by a (finite) set of localized excitation with associated discrete 
-eigenvalues. Extending the results of \cite{boffi2016} to the equation of motion of \eqref{ExcitationOperatorsDef3} we conclude that the elements of this category behave as \emph{observables} 
-quantities and the associated excitation energies have a true physical meaning, independently from the computational setup used for their representation. Conversely, the second sector is made by 
-a dense set of delocalized excitations with a continuum spectrum. The elements of this set behaves as the unbound virtual orbitals analyzed in \cite{boffi2016}....
-
-The knowledge of the excitations spectrum allows us to expand the LR susceptibility in terms of excitations. Indeed we can make usage of the spectral decomposition of the resolvent
-of the Liouvillian. This procedure allows us to formally solve the Liouville equation \eqref{LiouvillianRhopomegaDef1} and we have 
-\be\lb{RhopExcitationDef1}
-\sop{{\cal R}}(\omega) \cdot   =
-\left(\sum_E + \int\dd E   \right) \op E \,
-\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;.
-\ee
-
-The typical structure of the excitation spectrum is represented in figure \ref{ExcitationLandscape}. 
-Excitations are separated into two categories. 
-The plot evidences that below the first ionization energy $|\eps_h|$ the spectrum is purely composed by a discrete set of localized excitations.
-Instead, in the intermediate energy interval that extends
-from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the discrete sector of the spectrum is embedded in a continuum of excitations delocalized in the whole accessible space. Lastly,
-for energies higher than $|\eps_1|$ only delocalized excitations are present.
+% This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitation with associated discrete eigenvalues. 
+% Extending the results of \cite{boffi2016} to the equation of motion of \eqref{ExcitationOperatorsDef3} we conclude that the elements of this category behave as \emph{observables} 
+% quantities and the associated excitation energies have a true physical meaning, independently from the computational setup used for their representation. Conversely, the second sector is made by 
+% a dense set of delocalized excitations with a continuum spectrum. The elements of this set behaves as the unbound virtual orbitals analyzed in \cite{boffi2016}....
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[ht]
+\begin{figure}[t]
 \begin{tikzpicture}[scale=0.78]
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
+the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
+\emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation. 
+The second sector contains the dense set of delocalized excitations with an associated continuum spectrum. These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016} and 
+are deeply affected by the computational setup used to represent them. In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and 
+the associated spectrum exhibit an explicit dependence from the size of the domain. Excitations belonging to this sector thus lose their physical meaning and have to be only understood as a tool to 
+express the spectral decomposition of the Liouvillian superoperator.
+
+The typical structure of the excitation spectrum is depicted in figure \ref{ExcitationLandscape}.
+The plot evidences that below the first ionization energy $|\eps_h|$ only localized excitations contribute
+to the spectrum.
+Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the elements belonging to the discrete sector are embedded
+in a continuum of delocalized excitations. Lastly, for energies higher than $|\eps_1|$ only delocalized excitations are present.
+
+The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
+Liouvillian. Pursuing this procedure provides:
+%The knowledge of the excitations spectrum allows us to expand the LR susceptibility in terms of excitations. Indeed we can make usage of the spectral decomposition of the resolvent
+%of the Liouvillian. This procedure allows us to formally solve the Liouville equation \eqref{LiouvillianRhopomegaDef1} and we have 
+\be\lb{RhopExcitationDef1}
+\sop{{\cal R}}(\omega) \cdot   =
+\left(\sum_E + \int\dd E   \right) \op E \,
+\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;,
+\ee 
+where we have divided the two sectors in the sum.
 
@@
 
-True poles vs spectral function....
+We can express the fluctuation states in terms of the susceptibility functional
+\be\lb{FluctuationStateExcitationDef1}
+\ket{f_p(\omega)}   =
+\left(\sum_E + \int\dd E   \right) 
+\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
+\ee 
+This relation clarifies the role of the excitations in the spectral decomposition. We know from the analysis of section \ref{FluctuationState} that fluctuation states are localized
+up to $\omega=|\eps_h|$.
 
-\section{Applications}
+\section{Criterion for a reliable sampling of the excitation operators} %Applications
 
 Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value
-obtained through a finite difference method.
+obtained through a finite difference method. Remark the importance of using a systematic basis, only in this way the convergence of the statical polarizability turns out to 
+be a meaningful criterion for the evaluation of the basis that sample the empty state space. Refer to the paper of....
 
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}

### 2018-04-24 AnalyticStructure_main.tex
update

@@
 
-% This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitation with associated discrete eigenvalues. 
-% Extending the results of \cite{boffi2016} to the equation of motion of \eqref{ExcitationOperatorsDef3} we conclude that the elements of this category behave as \emph{observables} 
-% quantities and the associated excitation energies have a true physical meaning, independently from the computational setup used for their representation. Conversely, the second sector is made by 
-% a dense set of delocalized excitations with a continuum spectrum. The elements of this set behaves as the unbound virtual orbitals analyzed in \cite{boffi2016}....
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
@@
 \emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation.
-The second sector contains the dense set of delocalized excitations with an associated continuum spectrum. These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016} and 
-are deeply affected by the computational setup used to represent them. In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and 
-the associated spectrum exhibit an explicit dependence from the size of the domain. Excitations belonging to this sector thus lose their physical meaning and have to be only understood as a tool to 
+
+Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+and are deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
+the associated spectrum exhibit an explicit dependence from the size of the domain.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
 express the spectral decomposition of the Liouvillian superoperator.
 
-The typical structure of the excitation spectrum is depicted in figure \ref{ExcitationLandscape}.
-The plot evidences that below the first ionization energy $|\eps_h|$ only localized excitations contribute
-to the spectrum.
-Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the elements belonging to the discrete sector are embedded
+The typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}. The plot evidences that below the first ionization energy $|\eps_h|$ only localized excitations are 
+present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the elements belonging to the discrete sector are embedded 
 in a continuum of delocalized excitations. Lastly, for energies higher than $|\eps_1|$ only delocalized excitations are present.
@@
 
-% Now we reformulate an analogous analysis looking at the susceptibility superoperator, implicit defined through \eqref{SusceptibilityDef1}. This approach leads to the concept of \emph{excitation 
-% operators}, defined through a self-consistent operator eigenvalue equation. Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight 
-% into the analytic structure of the linear response.
+%Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight into the analytic structure of the linear response.
 
@@
 
+The analysis discussed above has evidenced that there exists both localized and delocalized excitations. While the role of the former is quite unambigous 
 We can express the fluctuation states in terms of the susceptibility functional
@@
 \left(\sum_E + \int\dd E   \right) 
-\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
+%\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
+\frac{t_\Phi(E)}{\omega-E} \ket{\phi^E_p} \;,
 \ee 
+with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$.
 This relation clarifies the role of the excitations in the spectral decomposition. We know from the analysis of section \ref{FluctuationState} that fluctuation states are localized
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %\bibliographystyle{apsrev4-1}
 \bibliography{Analytic_biblio}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2018-04-25 AnalyticStructure_main.tex
Update on Overleaf.

@@
 \section{Introduction}
-
 The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.

### 2018-04-26 AnalyticStructure_main.tex

@@
 We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). Equations 
-\eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. In particular, the left action eigenvalue equation provides   
+\eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. In particular, the left action eigenvalues equations provide   
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the elements belonging to the discrete sector are embedded 
-in a continuum of delocalized excitations. Lastly, for energies higher than $|\eps_1|$ only delocalized excitations are present.
+in a continuum of delocalized excitations. Lastly, for energies higher than $|\eps_1|$ the excitations landscape takes contributions only from the delocalized sector.
 
@@
 \ee 
-where we have divided the two sectors in the sum.
+%where we have divided the two sectors in the sum. 
+where we have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef1}. 
+The elements of the first sector correspond to the \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
 

### 2018-04-27 AnalyticStructure_main.tex
update

@@
 \section{Introduction}
+
 The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.

### 2018-05-02 AnalyticStructure_main.tex
update

@@
 \ee
-% where $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} 
-% under inspection. The modification of the ground-state density induced by the perturbation is expressed by the \emph{response density operator} $\dm'(\omega)$ that, in the linear 
-% response regime, is a linear function of the perturbing field $\op\Phi(\omega)$. For this reason it is possible to define the \emph{susceptibility} superoperator, as follows:
-% \be\lb{SusceptibilityDef1}
-% \dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
-% \ee
-% Susceptibility describes an intrinsic feature of the unperturbed system and determines its response to \emph{any} perturbations, in the linear response regime.
 Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
@@
 \ee 
-%where we have divided the two sectors in the sum. 
-where we have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef1}. 
-The elements of the first sector correspond to the \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
+where we have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef1}. The elements of the first sector 
+correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
 
-%Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight into the analytic structure of the linear response.
-
-\subsection{Discrete poles and spectral function. Physical meaning of the excitation spectrum} %{Comments. Physical meaning of the excitation spectrum}
-
-The analysis discussed above has evidenced that there exists both localized and delocalized excitations. While the role of the former is quite unambigous 
-We can express the fluctuation states in terms of the susceptibility functional
+Lastly, we establish a link between the fluctuation states and excitation operators based description of the LR. Indeed, thanks to the defining equation \eqref{SusceptibilityDef1} we can 
+easily express the excitations expansion of fluctuation states as follows 
 \be\lb{FluctuationStateExcitationDef1}
@@
 with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$. 
-This relation clarifies the role of the excitations in the spectral decomposition. We know from the analysis of section \ref{FluctuationState} that fluctuation states are localized
-up to $\omega=|\eps_h|$.
+%This formula shows that, for each value of $\omega$, both the sectors of the excitations spectrum contribute to the fluctuation state. 
+Thanks to the analysis presented in section \ref{FluctuationState} we know that fluctuation states possess a localized behavior up to $\omega=|\eps_h|$, so we conclude that 
+below this energy threshold the continuum sector of the excitation spectrum is able to resum in a localized way.
 
-\section{Criterion for a reliable sampling of the excitation operators} %Applications
+%Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight into the analytic structure of the linear response.
+
+%\subsection{Discrete poles and spectral function. Physical meaning of the excitation spectrum} %{Comments. Physical meaning of the excitation spectrum}
+
+% The analysis discussed above has evidenced that there exists both localized and delocalized excitations. While the role of the former is quite unambigous 
+% We can express the 
+% \be\lb{FluctuationStateExcitationDef1}
+% \ket{f_p(\omega)}   =
+% \left(\sum_E + \int\dd E   \right) 
+% %\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
+% \frac{t_\Phi(E)}{\omega-E} \ket{\phi^E_p} \;,
+% \ee 
+% with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$.
+% This relation clarifies the role of the excitations in the spectral decomposition. We know from the analysis of section \ref{FluctuationState} that fluctuation states are localized
+% up to $\omega=|\eps_h|$.
+
+\section{Quality indicator for the numerical convergence of the LR}   %{Criterion for a reliable sampling of the excitation operators}
+
+From the theoretical analysis of the previous section we can made two statements:
+\begin{itemize}
+ \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
+ wave functions for higher values of $\omega$. 
+ \item The excitation landscape is composed of two sectors with distinct properties. One made of a discrete set of localized excitations 
+\end{itemize}
 

### 2018-05-03 AnalyticStructure_main.tex
update

@@
  wave functions for higher values of $\omega$. 
- \item The excitation landscape is composed of two sectors with distinct properties. One made of a discrete set of localized excitations 
+ \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
+ poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
+ an effective representation of the spectral function. 
 \end{itemize}
+The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
+if so, up to which energy threshold can we assume that our computations do converge?
 
-Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value
-obtained through a finite difference method. Remark the importance of using a systematic basis, only in this way the convergence of the statical polarizability turns out to 
-be a meaningful criterion for the evaluation of the basis that sample the empty state space. Refer to the paper of....
+The first element of this discussion is the introduction of the computational basis $\{\mu\}$ used to perform the DFT calculations subjacent to the LR analysis. This basis is composed by a 
+finite set of elements (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) that are chosen to ensure an unbiased description 
+of the ground state properties of the system.
+
+FIRST QUESTION: The usage of the $\{\mu\}$ basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
+The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
+We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
+a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend this reliability of the result up to
+$\omega=|\eps_p|$.
+
+SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
+the $\{\mu\}$ basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of 
+$\bra{\psi_p}\op O$, in this case the computational setup provides reliable results if guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. 
+In this range there is no a priori indicator of the goodness of the results.
+
+%\vspace{0.3cm}
+\subsection{Choice of the $\alpha$-basis. Statical polarizability-driven criterion revised}
+
+The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\{\mu\}$ 
+basis. Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
+
+The construction of the excitation operators requires the explicit sampling of the empty state subspace. Definition of the $\{\alpha\}$-basis: choose the empty eigenstates of the KS Hamiltonian as a 
+basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. The elements $\{\alpha\}$-basis are expressed in the $\{\mu\}$-basis: since the $\{\mu\}$-basis is finite 
+dimensional so it is also the $\{\alpha\}$-basis. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
+
+% Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value obtained through a finite 
+% difference method. Remark the importance of using a systematic basis, only in this way the convergence of the statical polarizability turns out to be a meaningful criterion for the evaluation 
+% of the basis that sample the empty state space. Refer to the paper of....
 

### 2018-05-04 AnalyticStructure_main.tex
update

@@
 
-The first element of this discussion is the introduction of the computational basis $\{\mu\}$ used to perform the DFT calculations subjacent to the LR analysis. This basis is composed by a 
-finite set of elements (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) that are chosen to ensure an unbiased description 
+The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
+The properties of the $\mu$-basis (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description 
 of the ground state properties of the system.
 
-FIRST QUESTION: The usage of the $\{\mu\}$ basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
+FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
 The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
@@
 SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
-the $\{\mu\}$ basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of 
-$\bra{\psi_p}\op O$, in this case the computational setup provides reliable results if guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. 
-In this range there is no a priori indicator of the goodness of the results.
+the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
+in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
+priori indicator of the goodness of the results.
 
@@
 
-The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\{\mu\}$ 
-basis. Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
+The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\mu$-basis. 
+Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
 

### 2018-05-14 AnalyticStructure_main.tex
update

@@
 \ee
-This reformulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
+This alternative formulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
 feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field.
@@
 We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
-a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend this reliability of the result up to
+a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
 $\omega=|\eps_p|$.
@@
 
-The construction of the excitation operators requires the explicit sampling of the empty state subspace. Definition of the $\{\alpha\}$-basis: choose the empty eigenstates of the KS Hamiltonian as a 
-basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. The elements $\{\alpha\}$-basis are expressed in the $\{\mu\}$-basis: since the $\{\mu\}$-basis is finite 
-dimensional so it is also the $\{\alpha\}$-basis. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
+The construction of the excitation operators requires the explicit sampling of the empty state subspace. We introduce the notion of \emph{$\{\alpha\}$-basis}: choose the empty eigenstates of the KS 
+Hamiltonian as a basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. Excitations are written in the basis of transitions.
+
+COMMENT: The elements of the $\{\alpha\}$-basis are written in the (finite dimensional) $\{\mu\}$-basis.
+It follows that the $\{\alpha\}$-basis is finite dimensional too and has $n_\mu-n_{occ}$ degrees
+of freedom. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
 

### 2018-05-31 AnalyticStructure_main.tex
update

@@
 
-\title{On the analytic structure of the linear response susceptibility in open systems}
-%\title{Effects of the basis set on the linear response for open systems}
+%\title{On the analytic structure of the linear response susceptibility in open systems}
+\title{Localization properties, observable character and computational reliability of the linear response in open systems}
 
@@
 (explicit diagonalization, self-consistent Sternheimer equation, Lanczos chain-like procedure, etc.) and both for the choice of the basis set employed to perform the calculations. 
-Nonetheless, in all the cases one is a dealing with a finite basis set that, unavoidably, gives rise to a limited computational domain. It is then meaningful to try to understand under 
+Nonetheless, in all the cases one is a dealing with a finite basis set that, unavoidably, gives rise to a limited computational domain. 
+It is then meaningful to try to understand under 
 which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR.
@@
 
-\section{Theory}
+%\section{Theory}
+\section{Localization properties of the linear response actors in open systems}
 
-We start by reviewing review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
-out within a highly complete real-space basis set that provides a precise description of the system in a finite computational domain. The purpose of the analysis is to determine the 
-asymptotic behavior of the main building blocks of the LR in the long range. Then we discuss the relation between localization properties and dependence of the results of LR from the 
-specific choice of the basis set and, in particular, from the dimension of the computation  domain.
+% We start by reviewing review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
+% out within a highly complete real-space basis set that provides a precise description of the system in a finite computational domain. The purpose of the analysis is to determine the 
+% asymptotic behavior of the main building blocks of the LR in the long range. Then we discuss the relation between localization properties and dependence of the results of LR from the 
+% specific choice of the basis set and, in particular, from the dimension of the computation  domain. 
+% 
+% Linear response can be effectively applied to the analysis of the electronic excitations in molecular systems. In this framework one consider a system described by the Hamiltonian 
+% $\hnot$ and assume that the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic 
+% observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the 
+% \emph{linear response functional}
+% \be\lb{LinearResponseFunctDef1}
+% \braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;.
+% \ee
+% Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
+% while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the LR the response 
+% density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
+% \be\lb{LiouvillianRhopomegaDef1}
+% \left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
+% \ee
+% where $\op\Phi(\omega)$ represents the perturbing field acting on the system.
 
-Linear response can be effectively applied to the analysis of the electronic excitations in molecular systems. In this framework one consider a system described by the Hamiltonian 
-$\hnot$ and assume that the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic 
-observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the 
-\emph{linear response functional}
+In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
+characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
+principle free to explore the whole space.
+
+Linear response can be effectively applied to the analysis of the electronic excitations in open systems. In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that 
+the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic observable induced by a 
+time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the \emph{linear response functional}
 \be\lb{LinearResponseFunctDef1}
@@
 while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the LR the response 
-density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
+density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008})
 \be\lb{LiouvillianRhopomegaDef1}
@@
 \ee
-where $\op\Phi(\omega)$ represents the perturbing field acting on the system.
+where $\op\Phi(\omega)$ represents the perturbing field.
+
+The purpose of the present analysis is to determine the asymptotic behavior of the main building blocks of the LR in the long range, \emph{i.e.} outside the support domain of the potential. 
+%Then we discuss the relation between localization properties and dependence of the results of LR from the specific choice of the basis set and, in particular, from the dimension of the computation domain.
+
+%\subsection{Solution of the Schroedinger equation for open systems}
+\subsection{Long range behavior of the eigenvalue solution of the Schroedinger equation}
+\label{SEopenSystem}
+
+As a preliminary step for the forthcoming discussion we present a simple argument that allows us to determine the asymptotic character of the eigenvalue solution of the Schroedinger equation (SE) 
+$\op H\ket{\psi}=\eps\ket{\psi}$. The main aims of this analysis, apart from reproducing the well known behavior of the wave functions, is to introduce some tools and setting up notations and 
+terminology that will we widely used in the rest of the paper.
+
+We procede by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term.
+Since we are dealing with molecular-like systems $\op V$ has a compact support when projected in the
+$\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
+\be\lb{SEHelmholtz1}
+\ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
+\ee
+where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$. We observe that, due to the properties of $\op V$, the \emph{source term} $\ket{\op V\psi}$ 
+of equation \eqref{SEHelmholtz1} is localized in space and, for open boundary conditions in three dimensions, the kernel of $\op G_H(\eps)$ in the coordinate representation reads: 
+\be\lb{HelmholtzKernelDef1}
+\bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+\frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
+\frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \eps \geq 0
+\end{cases} \;,
+\ee
+where $\alpha = \sqrt{2|\eps|}$. 
+This representation of the eigenvalues solution of the SE evidences that the value $\eps=0$ represents the threshold level that determines the asymptotic character of the wave functions. 
+Indeed, for $\eps > 0$,  $\op G_H(\eps)$ behaves as a spherical wave and its convolution with the source term  gives raise to a $\psi(\r)$ delocalized in the whole accessible space. Instead, 
+for values of $\eps < 0$, the kernel contains an exponential damping factor and the associated wave functions exhibit a bound-state behavior in the long range. Finally, we observe that the 
+square-integrability and the continuity of the wave function and its derivatives poses further constrains responsible for the discretization of the energy spectrum for bound-states.
+
+The different asymptotic behavior of the wave functions has a deep impact on the possible computational induced error obtained when this quantities are evaluated using a (finite) computational
+setup. 
+A direct numerical evidence of this problem has been discussed in \cite{boffi2016}. The authors of this paper analyze the effects of a finite basis set on the 
+occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
+with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+
+% It is then meaningful to try to understand under 
+% which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR. 
+% A preliminary understanding of this problem can be achieved thanks to the results reported in \cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
+% occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
+% with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+% able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+% true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+% Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
 
@@
 
-The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transitions operator, linking the occupied and empty subspaces 
+The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition operator, linking the occupied and empty subspaces 
 of $\hnot$, and satisfies the \emph{transverse} condition  
@@
 
-The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation 
-states. To clarify this statement we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and solve \eqref{fluctuationStateEqMotion1} in the form 
-of a self-consistent inhomogeneous Helmholtz equation by writing:
+The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
+analogous to the one depicted in section \ref{SEopenSystem}. So we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and express the solution of 
+\eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
 \be\lb{rhoPrimeFluctuationStateDef2}
@@
 \ee
-where we have introduced the Green function of the Helmholtz operator $\op G_H(\omega) = (\omega-\op T)^{-1}$,
-and the \emph{source term} is given by:
+where in this case the source term contains further addend apart from the unperturbed potential and reads:
 \be
@@
 \ee
-For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
-\be\lb{HelmholtzKernelDef1}
-\bra{\r} \op G_H(\omega) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
-\frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \omega  < 0\; \\ 
-\frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \omega \geq 0
-\end{cases} \;,
-\ee
-where $\alpha = \sqrt{2|\omega|}$.
-
-The localization character of fluctuation states can be determined by looking at the long range behavior of \eqref{rhoPrimeFluctuationStateDef2}, projected in the $\r$-representation.
-An inspection of the structure of \eqref{HelmholtzKernelDef1} evidences that, for each value of $p$, there exist a threshold value $\omega = |\eps_p|$, which govern the localization 
-properties of the corresponding fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ behaves as a spherical wave and its convolution with the source term  gives 
-raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space. On the contrary, for values of $\omega < |\eps_p|$, % below the threshold,
-the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
+% For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
+% \be\lb{HelmholtzKernelDef1}
+% \bra{\r} \op G_H(\omega) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+% \frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \omega  < 0\; \\ 
+% \frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \omega \geq 0
+% \end{cases} \;,
+% \ee
+% where $\alpha = \sqrt{2|\omega|}$. 
+The localization character of fluctuation states can be determined by looking at the long range behavior of \eqref{rhoPrimeFluctuationStateDef2}.
+In this case it emerges that, for each value of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 
+fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ acts as a spherical wave kernel and  gives raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space,
+whereas for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
 
@@
 
-The localization properties of fluctuation states allows us to assess the reliability of the linear response functional computed using the given basis set. Indeed, writing the response 
-density in terms of fluctuation states implies that 
-\be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
-\ee
-so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. We observe that there exists two 
-distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ is lower than the ionization 
-potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms of genuinely localized 
-quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which 
-possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
-is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
+% The localization properties of fluctuation states allows us to assess the reliability of the linear response functional computed using the given basis set. Indeed, writing the response 
+% density in terms of fluctuation states implies that 
+% \be\lb{LinearResponseFunctDef2}
+% \braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
+% \ee
+% so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. We observe that there exists two 
+% distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ is lower than the ionization 
+% potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms of genuinely localized 
+% quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which 
+% possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
+% is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation. 
+% 
+% On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
+% states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 
+% \eqref{LinearResponseFunctDef2}, where the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. This observation indicates that, above threshold, a computational setup 
+% provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$. 
+% 
+% As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the dimension of 
+% the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
+% setup are clearly visible for values of $\omega$ that exceed the threshold value. 
+% 
+% % This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
+% % to the value of $\omega$. 
+% % This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....  
+% 
+% \begin{figure}
+% \includegraphics[scale=0.56]{co_spectrum.eps}
+% \caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+% \end{figure}
 
-On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
-states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 
-\eqref{LinearResponseFunctDef2}, where the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. This observation indicates that, above threshold, a computational setup 
-provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
-
-As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the dimension of 
-the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
-setup are clearly visible for values of $\omega$ that exceed the threshold value.
-
-% This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
-% to the value of $\omega$. 
-% This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....
+\vspace{0.3cm}
+TODO: identify fluctuation states at $\omega=0$ as the $\op Q_0$ projection of the KS occupied orbitals of the system with the static perturbation explicitly added to the unperturbed Hamiltonian.
+Evidence the localized character of $f_p(0,\r)$ through the convergence of the value of the statical polarizability w.r.t the dimension of the box.
+Comment the result of figure \ref{co_alphaStatic}.
+Insert citation of \cite{mahan1980}.
 
 \begin{figure}
-\includegraphics[scale=0.56]{co_spectrum.eps}
-\caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+\includegraphics[scale=0.56]{CO_alpha+D0_vsBoxSize.eps}
+\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability of the $CO$ with respect to the size of the computational domain.}
 \end{figure}
@@
 \be\lb{SusceptibilityDef1}
-\dm'(\omega) = \sop{{\cal R}}(\omega) \op\Phi(\omega) \;. 
+\dm'(\omega) = \sop{{\cal \chi}}(\omega) \op\Phi(\omega) \;. 
 \ee
@@
 \be\lb{ExcitationOperatorsDef1}
-\Liouv \op E = E \op E \qq \op{\tilde E} \Liouv = E \op{\tilde E} \;,
+\Liouv \op E_a = \Omega_a \op E_a \qq \op{\tilde E}_a \Liouv = \Omega_a \op{\tilde E}_a \;,
 \ee
@@
 \be\lb{orthoExcitatioOpDef1}
-\trace{\op{\tilde E}\op E'} = \delta(E-E')
+\trace{\op{\tilde E}_a\op E_b} = \delta_{ab}
 \ee
+The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
+\be\lb{RhopExcitationDef1}
+\sop{{\cal \chi}}(\omega) \cdot   = \sum_a \op E_{a} \,
+\frac{\trace{\commutator{\dmnot}{\op{\tilde E}_a}\cdot}}{\omega-\Omega_a} \;.
+\ee 
+The analysis presented in this section aims to clarify the meaning of the formal sum over excitation expressed in \eqref{RhopExcitationDef1} (discrete sum? integral over a continuum?).
+
 The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse 
@@
 
-The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
-Liouvillian. Pursuing this procedure provides:
-%The knowledge of the excitations spectrum allows us to expand the LR susceptibility in terms of excitations. Indeed we can make usage of the spectral decomposition of the resolvent
-%of the Liouvillian. This procedure allows us to formally solve the Liouville equation \eqref{LiouvillianRhopomegaDef1} and we have 
-\be\lb{RhopExcitationDef1}
-\sop{{\cal R}}(\omega) \cdot   =
-\left(\sum_E + \int\dd E   \right) \op E \,
-\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;,
-\ee 
-where we have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef1}. The elements of the first sector 
-correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
+% The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
+% Liouvillian. Pursuing this procedure provides:
+% \be\lb{RhopExcitationDef1}
+% \sop{{\cal R}}(\omega) \cdot   =
+% \left(\sum_E + \int\dd E   \right) \op E \,
+% \frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;,
+% \ee 
+% where we have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef1}. 
+% The elements of the first sector 
+% correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
 
@@
 
-\section{Quality indicator for the numerical convergence of the LR}   %{Criterion for a reliable sampling of the excitation operators}
+%\section{Quality indicator for the numerical convergence of the LR}   %{Criterion for a reliable sampling of the excitation operators}
+\section{Criterion of computational reliability for the numerical convergence of the LR}
 
@@
 priori indicator of the goodness of the results.
+
+\subsection{Strong and weak convergence}
+
+The localization properties of fluctuation states allows us to assess the reliability of the linear response functional computed using the given basis set. Indeed, writing the response 
+density in terms of fluctuation states implies that 
+\be\lb{LinearResponseFunctDef2}
+\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
+\ee
+so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. We observe that there exists two 
+distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ is lower than the ionization 
+potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms of genuinely localized 
+quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which 
+possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
+is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
+
+On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
+states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 
+\eqref{LinearResponseFunctDef2}, where the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. This observation indicates that, above threshold, a computational setup 
+provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
+
+As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the dimension of 
+the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
+setup are clearly visible for values of $\omega$ that exceed the threshold value.
+
+\begin{figure}
+\includegraphics[scale=0.56]{co_spectrum.eps}
+\caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+\end{figure}
 

### 2018-06-04 AnalyticStructure_main.tex
update

@@
 
-We procede by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term.
-Since we are dealing with molecular-like systems $\op V$ has a compact support when projected in the
-$\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
+The argument procedes by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term. Since we are dealing with molecular-like systems $\op V$ has a compact support when 
+projected in the $\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
 \be\lb{SEHelmholtz1}
@@
 \be\lb{RhopExcitationDef1}
-\sop{{\cal \chi}}(\omega) \cdot   = \sum_a \op E_{a} \,
+\sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
 \frac{\trace{\commutator{\dmnot}{\op{\tilde E}_a}\cdot}}{\omega-\Omega_a} \;.
@@
 The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse 
-operators so that $\op E = \dmnot\op E\op Q_0 + \op Q_0\op E\dmnot$. This condition allows us to introduce a dyadic representation of excitations as follows
+operators so that $\op E_a = \dmnot\op E_a\op Q_0 + \op Q_0\op E_a\dmnot$. This condition allows us to introduce a dyadic representation of excitations as follows
 \begin{align}\lb{ExcitationOperatorsDef2}
-\op E &= \sum_p \left( \ket{\phi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\tilde\chi^E_p}\right)\;, \nn \\
-\op{\tilde E} &= \sum_p \left( \ket{\chi^E_p}\bra{\psi_p} + \ket{\psi_p} \bra{\tilde\phi^E_p}\right)\;,
+\op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
+\op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;,
 \end{align}
-where both the \emph{excited states} $\ket{\phi^E_p}$, $\bra{\tilde\chi^E_p}$ and their conjugates span the empty subspace of $\hnot$.
+where the \emph{excited states} $\ket{\phi^E_p}$, $\bra{\chi^E_p}$ span the empty subspace of $\hnot$.
 
 We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). Equations 
-\eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states. In particular, the left action eigenvalues equations provide   
+\eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states, that is   
 \begin{align}\lb{ExcitationOperatorsDef3}
-&\left[E-(\hnot - \eps_p)\right] \ket{\phi_p^E} = \op Q_0 \op V'[\op E] \ket{\psi_p} \;, \nn\\
-&\left[-E-(\hnot - \eps_p)\right]\ket{\tilde\chi_p^E} = \op Q_0\op V'[\op E^t]\ket{\psi_p}  \;, 
+&\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
+&\left[-\Omega_a-(\hnot - \eps_p)\right]\ket{\chi_p^a} = \op Q_0\op V'[\op E^t_a]\ket{\psi_p}  \;, 
 \end{align}
@@
 \be\lb{ExcitedStateOrthNormDef1}
-\sum_p \left(\brket{\tilde\phi_p^E}{\phi_p^{E'}} + \brket{\tilde\chi_p^{E'}}{\chi_p^E}\right) = \delta(E-E') \;. 
+\sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
 \ee
@@
 \begin{align}
-&\ket{\phi^E_p} = \op G_H(E+\eps_p)\ket{s_{\phi}} \;, \nn \\
-&\ket{\tilde\chi^E_p} = \op G_H(-E+\eps_p)\ket{s_{\tilde\chi}} \;,
+&\ket{\phi^a_p} = \op G_H(\Omega_a+\eps_p)\ket{s_{\phi}} \;, \nn \\
+&\ket{\chi^a_p} = \op G_H(-\Omega_a+\eps_p)\ket{s_{\chi}} \;,
 \end{align}
-where $\op G_H$ is the Helmholtz Green function, while the (self-consistent) source term $s_\phi$ and $s_{\tilde\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
+where $\op G_H$ is the Helmholtz Green function, while the (self-consistent) source term $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
 plus the action of the KS potential on the excited states.
 
-It is possible to show that excitation eigenvalues come in pair and we focus our analysis on solutions with positive energy, \emph{i.e.} with $E>0$. Looking at the coordinate representation 
-of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we observe that the Helmholtz kernel evaluated in $-E+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of $E$. 
-As a consequence all the $\ket{\tilde\chi^E_p}$ states exhibit a bound-state behavior in the long range. Instead, the asymptotic character of $\op G_H(E+\eps_p)$ depends from $E$ and we can 
-identify the threshold value $E=|\eps_p|$ in terms of which $\ket{\phi^E_p}$ changes from a bound-state like behavior to a delocalized spherical-wave like character.  
+It is possible to show that excitation eigenvalues come in pair and we focus our analysis on solutions with positive energy, \emph{i.e.} with $\Omega_a>0$. Looking at the coordinate representation 
+of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we observe that the Helmholtz kernel evaluated in $-\Omega_a+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of 
+$\Omega_a$. As a consequence all the $\ket{\chi^a_p}$ states exhibit a bound-state behavior in the long range. Instead, the asymptotic character of $\op G_H(\Omega_a+\eps_p)$ depends from $\Omega_a$ 
+and we can identify the threshold value $\Omega_a=|\eps_p|$ in terms of which $\ket{\phi^a_p}$ changes from a bound-state like behavior to a delocalized spherical-wave like character.  
 Furthermore, the orthonormalization conditions \eqref{ExcitedStateOrthNormDef1} act as a ulterior constraint for the bound-state solutions and have the effect of determining the quantization of 
-the corresponding energy levels \footnote{Sternheimer equations represent the first order expansion of a set of Hamiltonian eigenvalue equations. Consequently the properties of their solution...}.
-We conclude that all the states $\ket{\tilde\chi^E_p}$ and the $\ket{\phi^E_p}$ with $E$ below the threshold value constitute a genuine \emph{discrete} set, while the ones in the unbound 
-energy range behaves as generalized eigenvectors associated to a continuum spectrum.
-
-The structure of the excitation spectrum follows from the properties of the excited states described above. To clarify this point we consider a value of $E$ that satisfies equations
-\eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} possess a solution in which \emph{at least} one of the excited states 
-is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^E_p}$  with the highest value of $|\eps_p|$, among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
-considerations it emerge that if $E<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
-of this type thus represent localized quantities and the associated eigenvalue are discrete. On the contrary, for $E>|\eps_{p_m}|$ some (or all) of the excited states in the dyadic representation
-of the excitation behave as generalized eigenvectors and the corresponding eigenvalue belong to a continuum of accessible values.
+the corresponding energy levels. We conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute a genuine \emph{discrete} set, while 
+the ones in the unbound energy range behaves as generalized eigenvectors associated to a continuum spectrum.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
+\begin{figure}[!t]
 \begin{tikzpicture}[scale=0.78]
@@
 
-This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
-the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
-\emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation.
+The structure of the excitation spectrum follows from the properties of the excited states described above. To clarify this point we consider a value of $\Omega_a$ that satisfies equations
+\eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} possess a solution in which \emph{at least} one of the excited states 
+is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^a_p}$  with the highest value of $|\eps_p|$, among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
+considerations it emerge that if $\Omega_a<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
+of this type thus represent localized quantities and the associated eigenvalue are discrete.
+On the contrary, for $\Omega_a>|\eps_{p_m}|$ some (or all) of the excited states in the dyadic representation
+of the excitation behave as generalized eigenvectors and the corresponding eigenvalue belong to a continuum of accessible values.
 
-Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+% This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
+% the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
+% \emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation. 
+% 
+% Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
 These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
-and are deeply affected by the computational setup used to represent them.
+% and are deeply affected by the computational setup used to represent them.
 In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-the associated spectrum exhibit an explicit dependence from the size of the domain.
+% the associated spectrum exhibit an explicit dependence from the size of the domain.
 Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
-express the spectral decomposition of the Liouvillian superoperator.
+% express the spectral decomposition of the Liouvillian superoperator.
 
@@
 
+Susceptibility written as
+\be\lb{RhopExcitationDef2}
+\sop{{\cal \chi}}(\omega) \cdot   = \left(\sum_a + \int\dd a   \right) \op W_{a} \,
+\frac{2\trace{\op W_a \cdot}}{\omega^2-\Omega_a^2} \;,
+\ee 
+with $\op W_a = \frac{1}{\sqrt{2}}(\op E_a + \op E_a^t)$. 
 % The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
@@
 
-Lastly, we establish a link between the fluctuation states and excitation operators based description of the LR. Indeed, thanks to the defining equation \eqref{SusceptibilityDef1} we can 
-easily express the excitations expansion of fluctuation states as follows 
-\be\lb{FluctuationStateExcitationDef1}
-\ket{f_p(\omega)}   =
-\left(\sum_E + \int\dd E   \right) 
-%\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
-\frac{t_\Phi(E)}{\omega-E} \ket{\phi^E_p} \;,
-\ee 
-with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$. 
-%This formula shows that, for each value of $\omega$, both the sectors of the excitations spectrum contribute to the fluctuation state. 
-Thanks to the analysis presented in section \ref{FluctuationState} we know that fluctuation states possess a localized behavior up to $\omega=|\eps_h|$, so we conclude that 
-below this energy threshold the continuum sector of the excitation spectrum is able to resum in a localized way.
+% Lastly, we establish a link between the fluctuation states and excitation operators based description of the LR. Indeed, thanks to the defining equation \eqref{SusceptibilityDef1} we can 
+% easily express the excitations expansion of fluctuation states as follows 
+% \be\lb{FluctuationStateExcitationDef1}
+% \ket{f_p(\omega)}   =
+% \left(\sum_E + \int\dd E   \right) 
+% %\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
+% \frac{t_\Phi(E)}{\omega-E} \ket{\phi^E_p} \;,
+% \ee 
+% with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$. 
+% %This formula shows that, for each value of $\omega$, both the sectors of the excitations spectrum contribute to the fluctuation state. 
+% Thanks to the analysis presented in section \ref{FluctuationState} we know that fluctuation states possess a localized behavior up to $\omega=|\eps_h|$, so we conclude that 
+% below this energy threshold the continuum sector of the excitation spectrum is able to resum in a localized way.
 
@@
 
-%\vspace{0.3cm}
-\subsection{Choice of the $\alpha$-basis. Statical polarizability-driven criterion revised}
+\subsection{Stability and convergence of the excitation spectrum}
 
-The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\mu$-basis. 
-Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
+This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
+the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
+\emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation.
 
-The construction of the excitation operators requires the explicit sampling of the empty state subspace. We introduce the notion of \emph{$\{\alpha\}$-basis}: choose the empty eigenstates of the KS 
-Hamiltonian as a basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. Excitations are written in the basis of transitions.
+Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+and are deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
+the associated spectrum exhibit an explicit dependence from the size of the domain.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
+express the spectral decomposition of the Liouvillian superoperator.
 
-COMMENT: The elements of the $\{\alpha\}$-basis are written in the (finite dimensional) $\{\mu\}$-basis.
+\begin{figure}[ht]
+\includegraphics[scale=0.24]{CO_exc.eps}
+\caption{(Color online) Excitation spectrum of $CO$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+\label{CO_exc}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[scale=0.24]{C6H6_exc.eps}
+\caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+\label{C6H6_exc}
+\end{figure}
+
+% \subsection{Choice of the $\alpha$-basis. Statical polarizability-driven criterion revised}
+% 
+% The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\mu$-basis. 
+% Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
+% 
+% The construction of the excitation operators requires the explicit sampling of the empty state subspace. We introduce the notion of \emph{$\{\alpha\}$-basis}: choose the empty eigenstates of the KS 
+% Hamiltonian as a basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. Excitations are written in the basis of transitions.  
+% 
+% COMMENT: The elements of the $\{\alpha\}$-basis are written in the (finite dimensional) $\{\mu\}$-basis.
 It follows that the $\{\alpha\}$-basis is finite dimensional too and has $n_\mu-n_{occ}$ degrees
-of freedom. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
+% of freedom. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
 
@@
 
-\subsection{Results for the benzene molecule}
+%\subsection{Results for the benzene molecule}
 

### 2018-06-05 AnalyticStructure_main.tex
update

@@
 \be\lb{LinearResponseFunctDef1}
-\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;.
+\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
 \ee
-Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
-while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the LR the response 
-density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008})
-\be\lb{LiouvillianRhopomegaDef1}
-\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
-\ee
-where $\op\Phi(\omega)$ represents the perturbing field.
+where $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
+and we have introduced the \emph{response density operator} $\dm'(\omega)$ that codifies the modification of the ground-state density induced by the perturbation.
 
-The purpose of the present analysis is to determine the asymptotic behavior of the main building blocks of the LR in the long range, \emph{i.e.} outside the support domain of the potential. 
+The main objective of this section is to investigate the structure of the building blocks needed to express the response density operator. In particular, we are interested in clarifying 
+the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential. 
+%Due to this analysis we aim to be able to understand if the objects we are dealing with behave as bound-state like functions or if 
+%This analysis allows us to establish comprehension of the type of objects one is dealing with when performing a LR calculation and
+
+%in determining the long range behavior, \emph{i.e.} outside the support domain of the potential. This analysis  
 %Then we discuss the relation between localization properties and dependence of the results of LR from the specific choice of the basis set and, in particular, from the dimension of the computation domain.
+%asymptotic behavior of the main building blocks of the LR in the
 
-%\subsection{Solution of the Schroedinger equation for open systems}
 \subsection{Long range behavior of the eigenvalue solution of the Schroedinger equation}
@@
 
-The argument procedes by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term. Since we are dealing with molecular-like systems $\op V$ has a compact support when 
+The argument proceeds by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term. Since we are dealing with molecular-like systems $\op V$ has a compact support when 
 projected in the $\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
@@
 
-The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition operator, linking the occupied and empty subspaces 
-of $\hnot$, and satisfies the \emph{transverse} condition  
+In the contest of the LR the response density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008})
+\be\lb{LiouvillianRhopomegaDef1}
+\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
+\ee
+where $\op\Phi(\omega)$ represents the perturbing field. The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
+operator, linking the occupied and empty subspaces of $\hnot$, and satisfies the \emph{transverse} condition  
 \be\lb{RhopTransverseDef1}
-\dm' = \dm_{\perp} \doteq \dmnot\dm'\op Q_0 + \op Q_0\dm'\dmnot
+\dm' = \dm_{\perp} \doteq \dmnot\dm'\op Q_0 + \op Q_0\dm'\dmnot \;,
 \ee
@@
 \end{align}
-where the \emph{excited states} $\ket{\phi^E_p}$, $\bra{\chi^E_p}$ span the empty subspace of $\hnot$.
+where we have defined the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals of $\hnot$.
 
@@
 with $\op W_a = \frac{1}{\sqrt{2}}(\op E_a + \op E_a^t)$. 
+We have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef2}. 
+The elements of the first sector 
+correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
+
+\subsubsection*{Results of this section}
+
+From the theoretical analysis of the previous section we can made two statements:
+\begin{itemize}
+ \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
+ wave functions for higher values of $\omega$. 
+ \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
+ poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
+ an effective representation of the spectral function. 
+\end{itemize}
+
 % The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
@@
 
-From the theoretical analysis of the previous section we can made two statements:
-\begin{itemize}
- \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
- wave functions for higher values of $\omega$. 
- \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
- poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
- an effective representation of the spectral function. 
-\end{itemize}
+% From the theoretical analysis of the previous section we can made two statements:
+% \begin{itemize}
+%  \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
+%  wave functions for higher values of $\omega$. 
+%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
+%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
+%  an effective representation of the spectral function. 
+% \end{itemize}
 The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
@@
 
+\begin{figure}[ht]
+\includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
+\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+\end{figure}
+
+\subsection{Fluctuation state and excitations}
+
+Express the fluctuation state in terms of excitation using the relation $\ket{f_p(\omega)} = \dm'(\omega)\ket{\psi_p}$ and using formula \eqref{SusceptibilityDef1} to express the excitation
+expansion of the response density. Due to this procedure we obtain
+\be\lb{FSExcitationDef1}
+\ket{f_p(\omega)}   = \left(\sum_a + \int\dd a   \right) \ket{w_p^a} \,
+\frac{\bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}}{\omega^2-\Omega_a^2} \;,
+\ee 
+with $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$. 
+Show the convergence of the statical polarizability of the $CO$ in function of the number of excitations. Write formula
+\be\lb{AlphaExcitationDef1}
+\alpha_{xx} =  \left(\sum_a + \int\dd a   \right) 2 \,
+\frac{\left[\trace{\op W_a \op X}\right]^2}{\Omega_a^2} \;,
+\ee 
+and add the plot that show the convergence rate of the statical polarizability to the reference (finite difference) value in functions of the number of excitations. The plot evidence that the
+continuum sector of the excitation spectrum is 
+\begin{figure}
+\includegraphics[scale=0.56]{CO_alphaX_isto.eps}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
+\end{figure}
+
 % \subsection{Choice of the $\alpha$-basis. Statical polarizability-driven criterion revised}
@@
 % of the basis that sample the empty state space. Refer to the paper of....
-
-%\subsection{Results for the benzene molecule}
-
-\begin{figure}[ht]
-\includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
-\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
-\end{figure}
 

### 2018-06-06 AnalyticStructure_main.tex
intriduction, first versions

@@
 \section{Introduction}
+Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the 
+computational reliability of the results. More specifically, a computational result may be considered as reliable for various reasons.
+It might be, for example, in agreement with some previously existing data that the employed computational model is susceptible to reproduce.
+The model itself can in this way be classified as ``accurate''; it may then be employed to extract, \textit{in silico},
+other quantities that might be then used to \emph{predict} or \emph{interpret} experimental data.
+Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
+that a given computational model provides for a specific set of quantities, regardless of their potential agreement with 
+experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertanties
+of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
+employing the same model can be compared.
 
-The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
-This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT) \cite{runge1984,onida2002}, that allows one to establish the time-dependent 
-Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time.
+A recent, remarkable exemple of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
+where a grassroot community of code-owners struggled to extract well-defined computational results in the context of 
+Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as Lattice constants and bulk modulus of 
+elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertanties 
+on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics computer code. 
+Any other code able to extract the same quantites with the same approximations might be compared with the 
+results of the community in order to assess its computational reliability.
 
-We focus our attention to the linear response regime (LR) in which the theory can be conveniently expressed in the frequency domain and the time-dependent KS equation are reformulated 
-as a quantum Liouville equation for the response density operator. Different computational approaches have been developed in literature \cite{baroni2008,hubener2014,brabec2015}, principally 
-with the aim of producing efficient algorithms for the evaluation of the physical observables. These methods differ both for the procedure adopted to solve the Liouville equation 
-(explicit diagonalization, self-consistent Sternheimer equation, Lanczos chain-like procedure, etc.) and both for the choice of the basis set employed to perform the calculations. 
-Nonetheless, in all the cases one is a dealing with a finite basis set that, unavoidably, gives rise to a limited computational domain. 
-It is then meaningful to try to understand under 
-which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR.
+For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists, 
+reducing the computational uncertainty is the only possible way to shed light on the predictivity power of the
+model. In other terms, the ``accuracy'' of a result with respect to experimental data may be reliably quantified
+only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
+For communities like DFT, such a ``calibration'' of computer codes among each other is a discipline that is still in its infancy;
+the DeltaCodes initiative and the foundations of DFT are separated in time by more than 50 years, and the computational
+model employed in the comparison (the Perdew-Burke-Erzerhof functional~\cite{PBE}) has been introduced more than 20 years ago.
 
-A preliminary understanding of this problem can be achieved thanks to the results reported in \cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
-occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
-with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
-able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
-true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
-Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+The problem is even more stringent for calculations that refer to quantities \emph{beyond} ground state, like
+for instance the time-dependent density functional theory (TDDFT) \cite{casida1995,runge1984,onida2002},
+from which quantities like optical excitations or polarizability tensors
+of a given system might be studied and put in relation with experimental data.
+Here also, a plethora of computational approaches exist, that employ different numerical formalism and
+basis sets, and it will be of great importance to identify quantities that can be ``measured'' in a given model, to assess
+and quantify their computational uncertainty.
 
-In this paper we aim to reach a deeper understanding of the possible effects of a finite computational basis set on the LR regime in open systems. To achieve this task we try to
-reformulate the relation between localization properties and basis independence for the main actors of the LR formalism. We present a discussion based on a double level analysis. First, 
-we propose a localization argument directly based on the inspection of the response density operator. Then, we move to a deeper level and investigate the properties of the susceptibility 
-functional, which represents the fundamental object in the contest of the linear response. Pursuing this approach we are naturally led to investigate the localization properties of excitation 
-operators, that in turn emerge as the resonant channel of the spectral decomposition of the susceptibility. In this way we establish a direct relation between the concept of basis independence 
-and the analytic structure of the linear response susceptibility.
+Moreover, wheareas for Ground-State calculations the quantities are relatively easy to identify and extract,
+TD-DFT and more generally, linear-response calculation present a further difficulty, which is the problem
+of \emph{numerical} convergence. In other terms, beyond ground state, 
+the absence of tools like the variational theorem imposes us to focus on \emph{well-defined} quantites,
+and to study the conditions under which numerical convergence of the results can be achieved.
+
+In this paper, we focus our attention to Linear-Response treatments of \emph{molecular} systems, 
+in particular referring to LR-TDDFT calculation. We will investigate the impact that 
+\emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the numerical convergence of LR quantites.
+In particular, we will discuss the interplay between the numerical convergence of LR quantities and the \emph{locality}
+of the related objects.
+In order to do this, we perform analytic considerations on the equations beyond LR treatment,
+which will help us identifying how to distinguish -- \textit{a priori} -- quantities that are susceptible to be 
+compared among different treatments, as they are \emph{intrinsically} associated to localized objects,
+from quantities that \emph{explicitly} depend of the the employed computational treatment.
+
+Our consideration will allso reveal useful for the understanding of the \emph{analytic structure} of LR quantities like
+the linear susceptibility of the system (i.e. the \emph{reducible} polarizability).
+Altough we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
+approaches, in the context Quasi-Particle equations.
+
+% The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
+% This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT) \cite{runge1984,onida2002}, that allows one to establish the time-dependent 
+% Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time. 
+% 
+% We focus our attention to the linear response regime (LR) in which the theory can be conveniently expressed in the frequency domain and the time-dependent KS equation are reformulated 
+% as a quantum Liouville equation for the response density operator. Different computational approaches have been developed in literature \cite{baroni2008,hubener2014,brabec2015}, principally 
+% with the aim of producing efficient algorithms for the evaluation of the physical observables. These methods differ both for the procedure adopted to solve the Liouville equation 
+% (explicit diagonalization, self-consistent Sternheimer equation, Lanczos chain-like procedure, etc.) and both for the choice of the basis set employed to perform the calculations. 
+% Nonetheless, in all the cases one is a dealing with a finite basis set that, unavoidably, gives rise to a limited computational domain. 
+% It is then meaningful to try to understand under 
+% which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR. 
+% 
+% A preliminary understanding of this problem can be achieved thanks to the results reported in \cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
+% occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
+% with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+% able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+% true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+% Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.  
+% 
+% In this paper we aim to reach a deeper understanding of the possible effects of a finite computational basis set on the LR regime in open systems. To achieve this task we try to
+% reformulate the relation between localization properties and basis independence for the main actors of the LR formalism. We present a discussion based on a double level analysis. First, 
+% we propose a localization argument directly based on the inspection of the response density operator. Then, we move to a deeper level and investigate the properties of the susceptibility 
+% functional, which represents the fundamental object in the contest of the linear response. Pursuing this approach we are naturally led to investigate the localization properties of excitation 
+% operators, that in turn emerge as the resonant channel of the spectral decomposition of the susceptibility. In this way we establish a direct relation between the concept of basis independence 
+% and the analytic structure of the linear response susceptibility.
 

### 2018-06-07 AnalyticStructure_main.tex
update

@@
 \appendix
-\section{Eigenvalue equations of the Liouvillian superoperator}
+\section{Left and right action of the Liouvillian superoperator}
 
-Derive the equations of motion for the excited states. Discussion of the effects of various supplementary conditions...
+% The Liouvillian superoperator for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term due the density dependence of the ground-state Hamiltonian.
+% Its left action reads
+% \begin{align}\lb{LiouvillianLeftActionDef1}
+% \Liouv\op O &= \commutator{\hnot}{O} + \commutator{\op V'[\op O]}{\dmnot}  = \nn \\
+% &=  \commutator{\hnot}{O} + \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;
+% \end{align}
+% thanks to the equivalence $\commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot$. 
+% It is also useful to define the scalar coupling kernel $U$
+% \be
+% U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
+% } \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
+% \ee
+% that allows us to express $\op V'[\op O]$ as:
+% \be\lb{VpDef1}
+% \op V'[\op O]= 
+% \int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
+% \ee
+% The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$ and provides:
+% \be
+% \op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
+% U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
+% \ee
+% Using the symmetry of the coupling kernel we have
+% \begin{align}%\lb{LiouvillianRightActionDef1}
+% \op O\Liouv &= -\commutator{\hnot}{\op O} + \nn \\ 
+% &+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot 
+% \end{align}
+
+The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term due
+the density dependence of the ground-state Hamiltonian. The left action of these terms reads, respectively
+\be\lb{LiouZeroDef1}
+\Liouvnot \op O = \commutator{\hnot}{O} \;,
+\ee
+and
+\be\lb{CouplDef1}
+\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;.
+\ee
+Here $\op V'$ can be conveniently expressed by defining the \emph{scalar coupling kernel}
+\be
+U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
+} \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
+\ee
+on the basis of which
+\be\lb{VpDef1}
+\op V'[\op O]= 
+\int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
+\ee
+In view of building the spectral decomposition we are interested in finding both the left and right eigenstates of $\Liouv$.   
+The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$, so that:
+\be
+\op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
+U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
+\ee
+In the cases relevant for the present analysis the coupling kernel is symmetric with respect to the exchange of its arguments so
+\begin{align}\lb{LiouvillianRightActionDef1}
+\op O\Liouv &= -\commutator{\hnot}{\op O} + V'\left[\commutator{{\dmnot}}{\op O}\right] = -\commutator{\hnot}{\op O} + \nn \\ 
+&+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot \;, 
+\end{align}
+where in the last equivalence we have made usage of the transverse property of the coupling superoperator. Formula \eqref{LiouZeroDef1},\eqref{CouplDef1}
+and \eqref{LiouvillianRightActionDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
 

### 2018-06-08 AnalyticStructure_main.tex
update

--- 2018-06-06 AnalyticStructure_main.tex
@@
 
-%\section{Theory}
 \section{Localization properties of the linear response actors in open systems}
-
-% We start by reviewing review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
-% out within a highly complete real-space basis set that provides a precise description of the system in a finite computational domain. The purpose of the analysis is to determine the 
-% asymptotic behavior of the main building blocks of the LR in the long range. Then we discuss the relation between localization properties and dependence of the results of LR from the 
-% specific choice of the basis set and, in particular, from the dimension of the computation  domain. 
-% 
-% Linear response can be effectively applied to the analysis of the electronic excitations in molecular systems. In this framework one consider a system described by the Hamiltonian 
-% $\hnot$ and assume that the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic 
-% observable induced by a time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the 
-% \emph{linear response functional}
-% \be\lb{LinearResponseFunctDef1}
-% \braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;.
-% \ee
-% Here $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
-% while the \emph{response density operator} $\dm'(\omega)$ describes the modification of the ground-state density induced by the perturbation. In the contest of the LR the response 
-% density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008}),
-% \be\lb{LiouvillianRhopomegaDef1}
-% \left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
-% \ee
-% where $\op\Phi(\omega)$ represents the perturbing field acting on the system.
 
@@
 the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential.
-%Due to this analysis we aim to be able to understand if the objects we are dealing with behave as bound-state like functions or if 
-%This analysis allows us to establish comprehension of the type of objects one is dealing with when performing a LR calculation and
-
-%in determining the long range behavior, \emph{i.e.} outside the support domain of the potential. This analysis  
-%Then we discuss the relation between localization properties and dependence of the results of LR from the specific choice of the basis set and, in particular, from the dimension of the computation domain.
-%asymptotic behavior of the main building blocks of the LR in the
 
@@
 
-% It is then meaningful to try to understand under 
-% which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR. 
-% A preliminary understanding of this problem can be achieved thanks to the results reported in \cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
-% occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
-% with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
-% able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
-% true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
-% Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
-
 \subsection{Fluctuation states. A localization argument for the response density}
@@
 
-The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
-analogous to the one depicted in section \ref{SEopenSystem}. So we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and express the solution of 
-\eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
+\begin{figure}[t]
+\includegraphics[scale=0.56]{CO_alpha+D0_vsBoxSize.eps}
+\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability of the $CO$ with respect to the size of the computational domain.}
+\end{figure}
+
+% The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
+% analogous to the one depicted in section \ref{SEopenSystem}. So we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and express the solution of 
+% \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
+The solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of a self-consistent inhomogeneous Helmholtz equation
 \be\lb{rhoPrimeFluctuationStateDef2}
@@
 \ee
-% For open boundary conditions in three dimensions, the kernel of $\op G_H(\omega)$ in the coordinate representation reads: 
-% \be\lb{HelmholtzKernelDef1}
-% \bra{\r} \op G_H(\omega) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
-% \frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \omega  < 0\; \\ 
-% \frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \omega \geq 0
-% \end{cases} \;,
-% \ee
-% where $\alpha = \sqrt{2|\omega|}$. 
-The localization character of fluctuation states can be determined by looking at the long range behavior of \eqref{rhoPrimeFluctuationStateDef2}.
-In this case it emerges that, for each value of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 
-fluctuation state. Indeed, for $\omega > |\eps_p|$,  $\op G_H(\omega)$ acts as a spherical wave kernel and  gives raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space,
+The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
+the source term depends also from the perturbation added to the system so this analysis applies only to the class of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
+in the $\r$-representation. 
+It emerges that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 
+fluctuation state. For $\omega > |\eps_p|$,  the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space,
 whereas for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
 
-% \vspace{0.3cm}
-% \noindent{TODO: Add comment to support the localization below threshold}. Two possible way. First way, use the fact that the $\ket{f_p(0)}$ is the nothing but the $p$-\emph{th} 
-% eigenstate of the perturbed Hamiltonian with perturbing field $\op\Phi(0)$. The localization of $\ket{f_p(0)}$ can be explicitly checked by solving the ground-state problem for
-% this Hamiltonian. How to extended to finite values of $\omega$ below threshold? Second way. Try and iterative solution of the self-consistent Helmholtz equation (below threshold) 
-% starting from a localized guess for the fluctuation state. Then state something about the the fact that is reasonable to believe that (for a proper choice of the perturbing field)
-% the operators appearing in the source term keep its support compact. If we are able to state this in a appropriate way the localization argument below threshold hold. In my opinion
-% this way is better.
-% \vspace{0.3cm}
+A direct confirmation of the localization character of fluctuation states at $\omega=0$ can be achieved through a ground-state calculation. Indeed, $\ket{f_p(\omega)}$ are nothing but the 
+perturbed KS eigenstates projected out from the domain of $\dmnot$, so for a constant perturbation $\op\Phi_s$ it turns out that $\ket{f_p(0)} = \op Q_0\ket{\psi_p^{\Phi_s}}$. The perturbed KS 
+states $\ket{\psi_p^{\Phi_s}}$ can be computed (beyond LR) by performing a DFT ground-state computation in which the constant perturbing field is added to the external potential and the 
+spatial extension of the fluctuation states can be directly measured. 
+The results of this procedure for a $CO$ molecule subjected to a static electric field are reported in figure \ref{co_alphaStatic}. The local character of the fluctuation states at $\omega=0$ is 
+probed by verifying the convergence of the statical polarizability versus the size of the computational domain used to express the fluctuation states. The convergence rate is compared with the 
+one of the static dipole of the molecule computed at zero external field. The plots evidence that the typical sizes of $\ket{f_p(0)}$ are analogous to the ones of the unperturbed KS orbitals.
 
-% The localization properties of fluctuation states allows us to assess the reliability of the linear response functional computed using the given basis set. Indeed, writing the response 
-% density in terms of fluctuation states implies that 
-% \be\lb{LinearResponseFunctDef2}
-% \braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
-% \ee
-% so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. We observe that there exists two 
-% distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ is lower than the ionization 
-% potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms of genuinely localized 
-% quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which 
-% possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
-% is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation. 
-% 
-% On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
-% states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 
-% \eqref{LinearResponseFunctDef2}, where the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. This observation indicates that, above threshold, a computational setup 
-% provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$. 
-% 
-% As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the dimension of 
-% the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
-% setup are clearly visible for values of $\omega$ that exceed the threshold value. 
-% 
-% % This fact implies that a computational setup has different chances of providing a reliable assessment of the linear response functional \eqref{LinearResponseFunctDef2} depending
-% % to the value of $\omega$. 
-% % This observation has relevant consequence on the capability of a computational setup to provide a reliable assessment of the linear response functional....  
-% 
-% \begin{figure}
-% \includegraphics[scale=0.56]{co_spectrum.eps}
-% \caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
-% \end{figure}
-
-\vspace{0.3cm}
-TODO: identify fluctuation states at $\omega=0$ as the $\op Q_0$ projection of the KS occupied orbitals of the system with the static perturbation explicitly added to the unperturbed Hamiltonian.
-Evidence the localized character of $f_p(0,\r)$ through the convergence of the value of the statical polarizability w.r.t the dimension of the box.
-Comment the result of figure \ref{co_alphaStatic}.
-Insert citation of \cite{mahan1980}.
-
-\begin{figure}
-\includegraphics[scale=0.56]{CO_alpha+D0_vsBoxSize.eps}
-\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability of the $CO$ with respect to the size of the computational domain.}
-\end{figure}
+\emph{(Tweet)} The analysis described in this section has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$ possess the same long-range properties of the bound KS
+orbitals for $\omega < |\eps_p|$, while behave as unbound states for values of $\omega$ above the threshold levels. In the next section we will discuss the implication of the existence of these
+two distinct regimes on the numerical convergence of the observables computed within the LR framework. Before doing this we propose an analogous analysis with the aim to understand the localization 
+properties of the excitation-based description of the LR.
 
@@
 \ee
-The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
-\be\lb{RhopExcitationDef1}
-\sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
-\frac{\trace{\commutator{\dmnot}{\op{\tilde E}_a}\cdot}}{\omega-\Omega_a} \;.
-\ee 
-The analysis presented in this section aims to clarify the meaning of the formal sum over excitation expressed in \eqref{RhopExcitationDef1} (discrete sum? integral over a continuum?).
-
-The properties of the Liouvillian superoperator (see appendix?) imply that excitations are transverse 
-operators so that $\op E_a = \dmnot\op E_a\op Q_0 + \op Q_0\op E_a\dmnot$. This condition allows us to introduce a dyadic representation of excitations as follows
+Excitations are transverse operators so that $\op E_a = \dmnot\op E_a\op Q_0 + \op Q_0\op E_a\dmnot$ and can be expressed through a dyadic representation as follows
 \begin{align}\lb{ExcitationOperatorsDef2}
@@
 \end{align}
-where we have defined the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals of $\hnot$.
-
-We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). Equations 
-\eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states, that is   
+where we have defined the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals of $\hnot$. We observe that
+right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties of the Liouvillian described in appendix \ref{LiouvillianAction}. 
+The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
+\be\lb{RhopExcitationDef1}
+\sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
+\frac{\trace{\op E_a^t\cdot}}{\omega-\Omega_a} \;.
+\ee 
+Equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states, that is   
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 \ee
-Equations \eqref{ExcitationOperatorsDef3} allows us to present a localization argument for the excited states using the same procedure adopted for fluctuation states in 
-section \ref{FluctuationState}. Pursing this strategy we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows 
+%The analysis presented in this section aims to clarify the meaning of the formal sum over excitation expressed in \eqref{RhopExcitationDef1} (discrete sum? integral over a continuum?).   
+% We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). Equations 
+% \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states, that is   
+% \begin{align}\lb{ExcitationOperatorsDef3}
+% &\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
+% &\left[-\Omega_a-(\hnot - \eps_p)\right]\ket{\chi_p^a} = \op Q_0\op V'[\op E^t_a]\ket{\psi_p}  \;, 
+% \end{align}
+% and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies %among the excitation operators is expressed as 
+% \be\lb{ExcitedStateOrthNormDef1}
+% \sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
+% \ee
+Once again we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows 
 \begin{align}
@@
 
-\subsubsection*{Results of this section}
-
-From the theoretical analysis of the previous section we can made two statements:
-\begin{itemize}
- \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
- wave functions for higher values of $\omega$. 
- \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
- poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
- an effective representation of the spectral function. 
-\end{itemize}
+% \subsubsection*{Results of this section}
+% 
+% From the theoretical analysis of the previous section we can made two statements:
+% \begin{itemize}
+%  \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
+%  wave functions for higher values of $\omega$. 
+%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
+%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
+%  an effective representation of the spectral function. 
+% \end{itemize}
 
@@
 
-% Discuss the criterion for a good choice of the basis of transition. Computation of the statical polarizability in the LR formalism compared to the reference value obtained through a finite 
-% difference method. Remark the importance of using a systematic basis, only in this way the convergence of the statical polarizability turns out to be a meaningful criterion for the evaluation 
-% of the basis that sample the empty state space. Refer to the paper of....
-
 \section{Comments and conclusions}
@@
 \appendix
-\section{Eigenvalue equations of the Liouvillian superoperator}
+\section{Left and right action of the Liouvillian superoperator}\lb{LiouvillianAction}
 
-Derive the equations of motion for the excited states. Discussion of the effects of various supplementary conditions...
+The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term. The left action of these 
+terms reads, respectively
+\be\lb{LiouZeroDef1}
+\Liouvnot \op O = \commutator{\hnot}{O} \;,
+\ee
+and
+\be\lb{CouplDef1}
+\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;.
+\ee
+$\op V'$ expresses the perturbation induced by the density dependence on ground state Hamiltonian and can be conveniently expressed by defining the 
+\emph{scalar coupling kernel}
+\be
+U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
+} \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
+\ee
+on the basis of which
+\be\lb{VpDef1}
+\op V'[\op O]= 
+\int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
+\ee
+In view of building the spectral decomposition we are interested in finding both the left and right eigenstates of $\Liouv$.   
+The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$, so that:
+\be
+\op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
+U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
+\ee
+In the cases relevant for the present analysis the coupling kernel is symmetric with respect to the exchange of its arguments so also the right action of the 
+Liouvillian is expressed in terms of $\op V'$, as follows
+\begin{align}\lb{LiouvillianRightActionDef1}
+\op O\Liouv &= -\commutator{\hnot}{\op O} + V'\left[\commutator{{\dmnot}}{\op O}\right] = -\commutator{\hnot}{\op O} + \nn \\ 
+&+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot \;.
+\end{align}
+In the last equivalence we have made usage of the transverse property (see equation \eqref{RhopTransverseDef1}) of the coupling superoperator. Formula 
+\eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
 

### 2018-06-11 AnalyticStructure_main.tex
update

@@
 \be\lb{orthoExcitatioOpDef1}
-\trace{\op{\tilde E}_a\op E_b} = \delta_{ab}
+\trace{\op{\tilde E}_a\op E_b} = \delta_{ab} \;.
 \ee
@@
 \end{align}
-where we have defined the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals of $\hnot$. We observe that
-right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties of the Liouvillian described in appendix \ref{LiouvillianAction}. 
-The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
-\be\lb{RhopExcitationDef1}
-\sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
-\frac{\trace{\op E_a^t\cdot}}{\omega-\Omega_a} \;.
-\ee 
-Equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states, that is   
+where we have defined the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals of $\hnot$. 
+% We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties of the Liouvillian described in appendix \ref{LiouvillianAction}. 
+% The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
+% \be\lb{RhopExcitationDef1}
+% \sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
+% \frac{\trace{\op E_a^t\cdot}}{\omega-\Omega_a} \;.
+% \ee 
+By applying equations \eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} presented in appendix \ref{LiouvillianAction} to the dyadic representations of the excitation 
+operators, it emerges that equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states 
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 \end{align}
-where $\op G_H$ is the Helmholtz Green function, while the (self-consistent) source term $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
-plus the action of the KS potential on the excited states.
+% where $\op G_H$ is the Helmholtz Green function, while the (self-consistent) source term $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
+% plus the action of the KS potential on the excited states. 
+where the source terms $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} plus the action of the KS potential on the excited states.
 
-It is possible to show that excitation eigenvalues come in pair and we focus our analysis on solutions with positive energy, \emph{i.e.} with $\Omega_a>0$. Looking at the coordinate representation 
-of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we observe that the Helmholtz kernel evaluated in $-\Omega_a+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of 
-$\Omega_a$. As a consequence all the $\ket{\chi^a_p}$ states exhibit a bound-state behavior in the long range. Instead, the asymptotic character of $\op G_H(\Omega_a+\eps_p)$ depends from $\Omega_a$ 
-and we can identify the threshold value $\Omega_a=|\eps_p|$ in terms of which $\ket{\phi^a_p}$ changes from a bound-state like behavior to a delocalized spherical-wave like character.  
-Furthermore, the orthonormalization conditions \eqref{ExcitedStateOrthNormDef1} act as a ulterior constraint for the bound-state solutions and have the effect of determining the quantization of 
-the corresponding energy levels. We conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute a genuine \emph{discrete} set, while 
-the ones in the unbound energy range behaves as generalized eigenvectors associated to a continuum spectrum.
+% The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and we focus our analysis on the sector with positive energy, \emph{i.e.} $\Omega_a>0$. 
+% Looking at the coordinate representation 
+% of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we observe that the Helmholtz kernel evaluated in $-\Omega_a+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of 
+% $\Omega_a$.
+As a consequence all the $\ket{\chi^a_p}$ states exhibit a bound-state behavior in the long range.
+Instead, the asymptotic character of $\op G_H(\Omega_a+\eps_p)$ depends from $\Omega_a$
+% and we can identify the threshold value $\Omega_a=|\eps_p|$ in terms of which $\ket{\phi^a_p}$ changes from a bound-state like behavior to a delocalized spherical-wave like character.  
+% Furthermore, the orthonormalization conditions \eqref{ExcitedStateOrthNormDef1} act as a ulterior constraint for the bound-state solutions and have the effect of determining the quantization of 
+% the corresponding energy levels. We conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute a genuine \emph{discrete} set, while 
+% the ones in the unbound energy range behaves as generalized eigenvectors associated to a continuum spectrum.
+
+The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and we focus our analysis on the sector with positive energies. The localization 
+character of $\op G_H(\Omega_a+\eps_p)$ depends from $\Omega_a$ and we identify the threshold level $\Omega_a=|\eps_p|$. At the same time we point out that the Helmholtz kernel evaluated in 
+$-\Omega_a+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.  As a consequence of these behaviors and assuming the spatial localization of 
+the source terms,  we observe that the asymptotic character of $\ket{\phi^a_p}$ changes from bound to unbound as the value of the excitation energy crosses the threshold $|\eps_p|$ while all 
+the $\ket{\chi^a_p}$ states exhibit a bound-state behavior for all the values of $a$. 
+Furthermore, excited states are subjected to the orthonormalization condition \eqref{ExcitedStateOrthNormDef1} that acts as a ulterior constraint and has the effect of determining the quantization 
+of the energy levels associated to the the bound-state solutions.
+Thus we can conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute
+a genuine \emph{discrete} set, while the ones in the unbound energy range behaves as generalized eigenvectors associated to a continuum spectrum.
 
@@
 
-% This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
-% the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
-% \emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation. 
-% 
-% Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
-These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
-% and are deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-% the associated spectrum exhibit an explicit dependence from the size of the domain.
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
-% express the spectral decomposition of the Liouvillian superoperator.
-
 The typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}. The plot evidences that below the first ionization energy $|\eps_h|$ only localized excitations are 
@@
 
-Susceptibility written as
+%The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
+%Susceptibility written as
+The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
+Liouvillian. Pursuing this procedure provides:
 \be\lb{RhopExcitationDef2}
@@
 We have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef2}. 
-The elements of the first sector 
-correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
-
-% \subsubsection*{Results of this section}
-% 
-% From the theoretical analysis of the previous section we can made two statements:
-% \begin{itemize}
-%  \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
-%  wave functions for higher values of $\omega$. 
-%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
-%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
-%  an effective representation of the spectral function. 
-% \end{itemize}
-
-% The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
-% Liouvillian. Pursuing this procedure provides:
-% \be\lb{RhopExcitationDef1}
-% \sop{{\cal R}}(\omega) \cdot   =
-% \left(\sum_E + \int\dd E   \right) \op E \,
-% \frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\cdot}}{\omega-E} \;,
-% \ee 
-% where we have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef1}. 
-% The elements of the first sector 
-% correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
+The elements of the first sector correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
 
@@
 
+This analysis has revealed that the excitations spectrum is composed by two distinct sectors.
+The first one is realized by the (finite) set of localized excitations with discrete eigenvalues.
+Extending
+the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
+\emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation.
+
+Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+and are deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
+the associated spectrum exhibit an explicit dependence from the size of the domain.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
+express the spectral decomposition of the Liouvillian superoperator.
+
+%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
+%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
+%  an effective representation of the spectral function.
+
 \appendix
@@
 \be\lb{CouplDef1}
-\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;.
+\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;,
 \ee
-$\op V'$ expresses the perturbation induced by the density dependence on ground state Hamiltonian and can be conveniently expressed by defining the 
+where $\op V'$ expresses the perturbation induced by the density dependence on ground state Hamiltonian and can be conveniently expressed by defining the 
 \emph{scalar coupling kernel}

### 2018-06-11 AnalyticStructure_main.tex
sec2a revisited

--- 2018-06-07 AnalyticStructure_main.tex
@@
 
-Moreover, wheareas for Ground-State calculations the quantities are relatively easy to identify and extract,
-TD-DFT and more generally, linear-response calculation present a further difficulty, which is the problem
-of \emph{numerical} convergence. In other terms, beyond ground state, 
-the absence of tools like the variational theorem imposes us to focus on \emph{well-defined} quantites,
-and to study the conditions under which numerical convergence of the results can be achieved.
-
 In this paper, we focus our attention to Linear-Response treatments of \emph{molecular} systems, 
 in particular referring to LR-TDDFT calculation. We will investigate the impact that 
-\emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the numerical convergence of LR quantites.
-In particular, we will discuss the interplay between the numerical convergence of LR quantities and the \emph{locality}
-of the related objects.
-In order to do this, we perform analytic considerations on the equations beyond LR treatment,
-which will help us identifying how to distinguish -- \textit{a priori} -- quantities that are susceptible to be 
-compared among different treatments, as they are \emph{intrinsically} associated to localized objects,
-from quantities that \emph{explicitly} depend of the the employed computational treatment.
+\emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantites.
+In order to do this, we perform analytic considerations on the equations beyond LR treatment.
+Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - 
+from others that would \emph{explicitly} depend of the the employed computational treatment. 
+In particular, we will discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+% In order to do this, we perform analytic considerations on the equations beyond LR treatment,
+% which will help us identifying how to distinguish -- \textit{a priori} -- quantities that are susceptible to be 
+% compared among different treatments, as they are \emph{intrinsically} associated to localized objects,
+% from quantities that \emph{explicitly} depend of the the employed computational treatment.
 
-Our consideration will allso reveal useful for the understanding of the \emph{analytic structure} of LR quantities like
+Our considerations will also reveal useful for the understanding of the \emph{analytic structure} of LR quantities like
 the linear susceptibility of the system (i.e. the \emph{reducible} polarizability).
@@
 approaches, in the context Quasi-Particle equations.
+
+% Moreover, wheareas for Ground-State calculations the quantities are relatively easy to identify and extract,
+% TD-DFT and more generally, linear-response calculation present a further difficulty, which is the problem
+% of \emph{numerical} convergence. In other terms, beyond ground state, 
+% the absence of tools like the variational theorem imposes us to focus on \emph{well-defined} quantites,
+% and to study the conditions under which numerical convergence of the results can be achieved.
 
@@
 
+Let us start our discussion by revisting the impact that the Isolated BC have on the 
+solutions of the time-independent Schr\"odinger Equation.
+We here present well-known concepts of elementary quantum mechanics, under a perspective that
+will turn out to be very useful in the forthcoming considerations about linear-response quantities.
+
+\subsection{Long range behavior of the eigenvalue solution of the Schroedinger equation}
+\label{SEopenSystem}
+Consider a (one-body) wavefunction $\ket{\psi}$ solution of the equation
+$\op H\ket{\psi}=\eps\ket{\psi}$, where we split the Hamiltonian operator into the sum of
+a kinetic $\op T$ and a potential $\op V \equiv \op H - \op T$ term.
+In view of analysing the impact of the BC, it is instructive to transform 
+the Schroedinger Equation in a \emph{scattering} problem, by writing
+\be\lb{SEHelmholtz1}
+\ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
+\ee
+where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$,
+resolvent of the free-particle hamltonian $H_s \equiv \op T$.
+
+When describing the Ground State of a molecule, we suppose that the potential operator, even if non-local,
+is associated to real-space elements $\bra{\r} \op V \ket{\r'}$ that can be considered as nonzero only on a
+bounded domain. In other terms, a molecule can be associated to a ``scatterer'' that has a \emph{finite} 
+spatial extension; if a state $\ket{\psi}$ is localized, it will be the same for the ket $\ket{\op V \psi}$, though 
+perhaps in a larger region.
+For a computational treatment of the problem, this property is fundamental in the 
+choice of the numerical treatment; we know that basis functions that are tailored to express asymptotically vanishing 
+wavefunctions are better suited for the solution of the problem.
+
+This fact is made apparent by the expression of 
+the kernel of $\op G_H(\eps)$ in the coordinate representation. 
+When dealing with Isolated BC, it is easy to see that the solution of Eq.~\eqref{SEHelmholtz1}
+can be expressed by:
+\be\lb{HelmholtzKernelDef1}
+\bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+\frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
+\frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \eps \geq 0
+\end{cases} \;,
+\ee
+where $\alpha = \sqrt{2|\eps|}$.
+
+From the above expressions we can see that, \emph{for molecular systems},
+the value $\epsilon=0$
+represents a \emph{threshold}~\footnote{The threshold value in general should correspond to asymptotic value of the potential at infinity.} 
+energy that separates two different classes of solutions.
+Negative-energy solutions are \emph{localized}, i.e. they exhibit bound-state behaviour far away from the scatterer.
+These are \emph{bound} states and, by means of their normalizability, they are associated to \emph{discrete}, well-defined energies.
+The bound states can be of course labelled by quantum numbers that are defined by the properties of the scatterer, namely the
+symmetries of the potential $\op V$.
+In a computational discretization of the Schroedinger equation, such states can be in principle expressed with arbitrary precision, 
+provided that the numerical treatment offers the adequate level of completeness. 
+Being discrete and well-identified, the bound-state energies are a property of the molecule and can be associated to \emph{observable}
+quantities. The values of their energies can be compared among different treatments and it is in principle possible to
+provide reference results on them.
+
+On the other hand, positive energy solutions behave differently. 
+Even though the potential is localized, their positive energy makes them behave 
+as spherical waves and its convolution with the source term  gives raise to a delocalized wavefunction $\psi(\r)$ 
+in the whole accessible space.
+As they cannot be normalized they belong to the essential spectrum of the hamiltonian operator and form a \emph{continuum} of states.
+Thanks to the Lippman-Schwinger relation of Eq.~\eqref{SEHelmholtz1} they can be put in bijection with the eigenstates of the 
+free-particle hamiltonian $\op H_s$. We may say that their quantum numbers are determined by the Laplacian operator, 
+regardless of the particular features of the potential.
+
+It is easy to see from these concepts that a computational treatment that is tailored for the discretization of bound states
+will not be effective for continuum states, due to the different long-range asymptotic behaviour - which in turn is a clear consequence of the 
+BC of the problem. In a numerical treatment, states with $\epsilon > 0$ will have a value of their energy that will \emph{always}
+depend on the computational setup.
+
+A direct numerical evidence of this problem has been discussed in \cite{boffi2016}. The authors of this paper analyze the effects of a finite basis set on the 
+occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
+with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+
 % We start by reviewing review the fundamental equations that govern the properties of an open quantum system in the linear response regime. We assume that our calculations are carried 
@@
 
-In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
-characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
-principle free to explore the whole space.
+% In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
+% characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
+% principle free to explore the whole space.
 
@@
 
-\subsection{Long range behavior of the eigenvalue solution of the Schroedinger equation}
-\label{SEopenSystem}
-
-As a preliminary step for the forthcoming discussion we present a simple argument that allows us to determine the asymptotic character of the eigenvalue solution of the Schroedinger equation (SE) 
-$\op H\ket{\psi}=\eps\ket{\psi}$. The main aims of this analysis, apart from reproducing the well known behavior of the wave functions, is to introduce some tools and setting up notations and 
-terminology that will we widely used in the rest of the paper.
-
-The argument proceeds by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term. Since we are dealing with molecular-like systems $\op V$ has a compact support when 
-projected in the $\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
-\be\lb{SEHelmholtz1}
-\ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
-\ee
-where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$. We observe that, due to the properties of $\op V$, the \emph{source term} $\ket{\op V\psi}$ 
-of equation \eqref{SEHelmholtz1} is localized in space and, for open boundary conditions in three dimensions, the kernel of $\op G_H(\eps)$ in the coordinate representation reads: 
-\be\lb{HelmholtzKernelDef1}
-\bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
-\frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
-\frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \eps \geq 0
-\end{cases} \;,
-\ee
-where $\alpha = \sqrt{2|\eps|}$. 
-This representation of the eigenvalues solution of the SE evidences that the value $\eps=0$ represents the threshold level that determines the asymptotic character of the wave functions. 
-Indeed, for $\eps > 0$,  $\op G_H(\eps)$ behaves as a spherical wave and its convolution with the source term  gives raise to a $\psi(\r)$ delocalized in the whole accessible space. Instead, 
-for values of $\eps < 0$, the kernel contains an exponential damping factor and the associated wave functions exhibit a bound-state behavior in the long range. Finally, we observe that the 
-square-integrability and the continuity of the wave function and its derivatives poses further constrains responsible for the discretization of the energy spectrum for bound-states.
-
-The different asymptotic behavior of the wave functions has a deep impact on the possible computational induced error obtained when this quantities are evaluated using a (finite) computational
-setup. 
-A direct numerical evidence of this problem has been discussed in \cite{boffi2016}. The authors of this paper analyze the effects of a finite basis set on the 
-occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
-with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
-able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
-true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
-Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+% As a preliminary step for the forthcoming discussion we present a simple argument that allows us to determine the asymptotic character of the eigenvalue solution of the Schroedinger equation (SE) 
+% $\op H\ket{\psi}=\eps\ket{\psi}$. The main aims of this analysis, apart from reproducing the well known behavior of the wave functions, is to introduce some tools and setting up notations and 
+% terminology that will we widely used in the rest of the paper. 
+% 
+% The argument proceeds by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term. Since we are dealing with molecular-like systems $\op V$ has a compact support when 
+% projected in the $\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
+% \be\lb{SEHelmholtz1}
+% \ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
+% \ee
+% where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$.
+We observe that, due to the properties of $\op V$, the \emph{source term} $\ket{\op V\psi}$
+% of equation \eqref{SEHelmholtz1} is localized in space and, for open boundary conditions in three dimensions, the kernel of $\op G_H(\eps)$ in the coordinate representation reads: 
+% \be\lb{HelmholtzKernelDef1}
+% \bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+% \frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
+% \frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \eps \geq 0
+% \end{cases} \;,
+% \ee
+% where $\alpha = \sqrt{2|\eps|}$. 
+% This representation of the eigenvalues solution of the SE evidences that the value $\eps=0$ represents the threshold level that determines the asymptotic character of the wave functions. 
+% Indeed, for $\eps > 0$,  $\op G_H(\eps)$ behaves as a spherical wave and its convolution with the source term  gives raise to a $\psi(\r)$ delocalized in the whole accessible space. Instead, 
+% for values of $\eps < 0$, the kernel contains an exponential damping factor and the associated wave functions exhibit a bound-state behavior in the long range. Finally, we observe that the 
+% square-integrability and the continuity of the wave function and its derivatives poses further constrains responsible for the discretization of the energy spectrum for bound-states.  
+% 
+% The different asymptotic behavior of the wave functions has a deep impact on the possible computational induced error obtained when this quantities are evaluated using a (finite) computational
+% setup.
 
@@
 \appendix
-\section{Left and right action of the Liouvillian superoperator}
+\section{Eigenvalue equations of the Liouvillian superoperator}
 
-% The Liouvillian superoperator for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term due the density dependence of the ground-state Hamiltonian.
-% Its left action reads
-% \begin{align}\lb{LiouvillianLeftActionDef1}
-% \Liouv\op O &= \commutator{\hnot}{O} + \commutator{\op V'[\op O]}{\dmnot}  = \nn \\
-% &=  \commutator{\hnot}{O} + \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;
-% \end{align}
-% thanks to the equivalence $\commutator{\dmnot}{\op O} = \dmnot \op O \op Q_0 - \op Q_0 \op O \dmnot$. 
-% It is also useful to define the scalar coupling kernel $U$
-% \be
-% U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
-% } \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
-% \ee
-% that allows us to express $\op V'[\op O]$ as:
-% \be\lb{VpDef1}
-% \op V'[\op O]= 
-% \int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
-% \ee
-% The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$ and provides:
-% \be
-% \op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
-% U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
-% \ee
-% Using the symmetry of the coupling kernel we have
-% \begin{align}%\lb{LiouvillianRightActionDef1}
-% \op O\Liouv &= -\commutator{\hnot}{\op O} + \nn \\ 
-% &+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot 
-% \end{align}
-
-The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term due
-the density dependence of the ground-state Hamiltonian. The left action of these terms reads, respectively
-\be\lb{LiouZeroDef1}
-\Liouvnot \op O = \commutator{\hnot}{O} \;,
-\ee
-and
-\be\lb{CouplDef1}
-\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;.
-\ee
-Here $\op V'$ can be conveniently expressed by defining the \emph{scalar coupling kernel}
-\be
-U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
-} \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
-\ee
-on the basis of which
-\be\lb{VpDef1}
-\op V'[\op O]= 
-\int \dd \r \dd \r' U\left[\ketbra{\r}{\r'};\op O\right] \ketbra{\r'}{\r}\;.
-\ee
-In view of building the spectral decomposition we are interested in finding both the left and right eigenstates of $\Liouv$.   
-The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$, so that:
-\be
-\op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
-U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
-\ee
-In the cases relevant for the present analysis the coupling kernel is symmetric with respect to the exchange of its arguments so
-\begin{align}\lb{LiouvillianRightActionDef1}
-\op O\Liouv &= -\commutator{\hnot}{\op O} + V'\left[\commutator{{\dmnot}}{\op O}\right] = -\commutator{\hnot}{\op O} + \nn \\ 
-&+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot \;, 
-\end{align}
-where in the last equivalence we have made usage of the transverse property of the coupling superoperator. Formula \eqref{LiouZeroDef1},\eqref{CouplDef1}
-and \eqref{LiouvillianRightActionDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
+Derive the equations of motion for the excited states. Discussion of the effects of various supplementary conditions...
 

### 2018-06-11 AnalyticStructure_main.tex

--- 2018-06-11 AnalyticStructure_main.tex
@@
 
-In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
-characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
-principle free to explore the whole space.
+Let us start our discussion by revisting the impact that the Isolated BC have on the 
+solutions of the time-independent Schr\"odinger Equation.
+We here present well-known concepts of elementary quantum mechanics, under a perspective that
+will turn out to be very useful in the forthcoming considerations about linear-response quantities.
+
+\subsection{Long range behavior of the eigenvalue solution of the Schroedinger equation}
+\label{SEopenSystem}
+Consider a (one-body) wavefunction $\ket{\psi}$ solution of the equation
+$\op H\ket{\psi}=\eps\ket{\psi}$, where we split the Hamiltonian operator into the sum of
+a kinetic $\op T$ and a potential $\op V \equiv \op H - \op T$ term.
+In view of analysing the impact of the BC, it is instructive to transform 
+the Schroedinger Equation in a \emph{scattering} problem, by writing
+\be\lb{SEHelmholtz1}
+\ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
+\ee
+where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$,
+resolvent of the free-particle hamltonian $H_s \equiv \op T$.
+
+When describing the Ground State of a molecule, we suppose that the potential operator, even if non-local,
+is associated to real-space elements $\bra{\r} \op V \ket{\r'}$ that can be considered as nonzero only on a
+bounded domain. In other terms, a molecule can be associated to a ``scatterer'' that has a \emph{finite} 
+spatial extension; if a state $\ket{\psi}$ is localized, it will be the same for the ket $\ket{\op V \psi}$, though 
+perhaps in a larger region.
+For a computational treatment of the problem, this property is fundamental in the 
+choice of the numerical treatment; we know that basis functions that are tailored to express asymptotically vanishing 
+wavefunctions are better suited for the solution of the problem.
+
+This fact is made apparent by the expression of 
+the kernel of $\op G_H(\eps)$ in the coordinate representation. 
+When dealing with Isolated BC, it is easy to see that the solution of Eq.~\eqref{SEHelmholtz1}
+can be expressed by:
+\be\lb{HelmholtzKernelDef1}
+\bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+\frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
+\frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \eps \geq 0
+\end{cases} \;,
+\ee
+where $\alpha = \sqrt{2|\eps|}$.
+
+From the above expressions we can see that, \emph{for molecular systems},
+the value $\epsilon=0$
+represents a \emph{threshold}~\footnote{The threshold value in general should correspond to asymptotic value of the potential at infinity.} 
+energy that separates two different classes of solutions.
+Negative-energy solutions are \emph{localized}, i.e. they exhibit bound-state behaviour far away from the scatterer.
+These are \emph{bound} states and, by means of their normalizability, they are associated to \emph{discrete}, well-defined energies.
+The bound states can be of course labelled by quantum numbers that are defined by the properties of the scatterer, namely the
+symmetries of the potential $\op V$.
+In a computational discretization of the Schroedinger equation, such states can be in principle expressed with arbitrary precision, 
+provided that the numerical treatment offers the adequate level of completeness. 
+Being discrete and well-identified, the bound-state energies are a property of the molecule and can be associated to \emph{observable}
+quantities. The values of their energies can be compared among different treatments and it is in principle possible to
+provide reference results on them.
+
+On the other hand, positive energy solutions behave differently. 
+Even though the potential is localized, their positive energy makes them behave 
+as spherical waves and its convolution with the source term  gives raise to a delocalized wavefunction $\psi(\r)$ 
+in the whole accessible space.
+As they cannot be normalized they belong to the essential spectrum of the hamiltonian operator and form a \emph{continuum} of states.
+Thanks to the Lippman-Schwinger relation of Eq.~\eqref{SEHelmholtz1} they can be put in bijection with the eigenstates of the 
+free-particle hamiltonian $\op H_s$. We may say that their quantum numbers are determined by the Laplacian operator, 
+regardless of the particular features of the potential.
+
+It is easy to see from these concepts that a computational treatment that is tailored for the discretization of bound states
+will not be effective for continuum states, due to the different long-range asymptotic behaviour - which in turn is a clear consequence of the 
+BC of the problem. In a numerical treatment, states with $\epsilon > 0$ will have a value of their energy that will \emph{always}
+depend on the computational setup.
+
+A direct numerical evidence of this problem has been discussed in \cite{boffi2016}. The authors of this paper analyze the effects of a finite basis set on the 
+occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
+with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+
+% In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
+% characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
+% principle free to explore the whole space.
 

### 2018-06-11 AnalyticStructure_main.tex
update

@@
 
-\subsection{Excitation operators. The analytic structure of the susceptibility functional} %The spectrum of the Liouville superoperator
+\subsection{Excitation operators. The analytic structure of the susceptibility functional}
 
@@
 \end{align}
-and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies %among the excitation operators is expressed as 
+and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
 \be\lb{ExcitedStateOrthNormDef1}
@@
 \ee
-%The analysis presented in this section aims to clarify the meaning of the formal sum over excitation expressed in \eqref{RhopExcitationDef1} (discrete sum? integral over a continuum?).   
-% We restrict our analysis assuming that a set of hypothesis commonly realized in DFT holds (symmetry of the transition basis, specify better? see appendix?). Equations 
-% \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states, that is   
-% \begin{align}\lb{ExcitationOperatorsDef3}
-% &\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
-% &\left[-\Omega_a-(\hnot - \eps_p)\right]\ket{\chi_p^a} = \op Q_0\op V'[\op E^t_a]\ket{\psi_p}  \;, 
-% \end{align}
-% and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies %among the excitation operators is expressed as 
-% \be\lb{ExcitedStateOrthNormDef1}
-% \sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
-% \ee
 Once again we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows 
@@
 \end{align}
-% where $\op G_H$ is the Helmholtz Green function, while the (self-consistent) source term $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} 
-% plus the action of the KS potential on the excited states. 
 where the source terms $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} plus the action of the KS potential on the excited states.
-
-% The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and we focus our analysis on the sector with positive energy, \emph{i.e.} $\Omega_a>0$. 
-% Looking at the coordinate representation 
-% of $\op G_H$ (see eq. \eqref{HelmholtzKernelDef1}) we observe that the Helmholtz kernel evaluated in $-\Omega_a+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of 
-% $\Omega_a$.
-As a consequence all the $\ket{\chi^a_p}$ states exhibit a bound-state behavior in the long range.
-Instead, the asymptotic character of $\op G_H(\Omega_a+\eps_p)$ depends from $\Omega_a$
-% and we can identify the threshold value $\Omega_a=|\eps_p|$ in terms of which $\ket{\phi^a_p}$ changes from a bound-state like behavior to a delocalized spherical-wave like character.  
-% Furthermore, the orthonormalization conditions \eqref{ExcitedStateOrthNormDef1} act as a ulterior constraint for the bound-state solutions and have the effect of determining the quantization of 
-% the corresponding energy levels. We conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute a genuine \emph{discrete} set, while 
-% the ones in the unbound energy range behaves as generalized eigenvectors associated to a continuum spectrum.
 
@@
 \ee 
-with $\op W_a = \frac{1}{\sqrt{2}}(\op E_a + \op E_a^t)$. 
-We have explicitly separated the contributions of the localized and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef2}. 
-The elements of the first sector correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
+where we have defined the symmetric operators $\op W_a = \frac{1}{\sqrt{2}}(\ketbra{w_p^a}{\psi_p}+\ketbra{\psi_p}{w_p^a})$ and states $\ket{w_p^a}=\ket{\psi_p^a}+\ket{\chi_p^a}$.
+
+On the basis of the present analysis we have explicitly separated the contributions of the discrete and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef2}. 
+The first sector is realized by the (finite) set of localized excitations with discrete eigenvalues that contribute as \emph{true poles} of the susceptibility. 
+Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum. Excitations belonging to this sector thus lose their intrinsic physical meaning 
+and have to be understood as a tool to express the spectral decomposition of the Liouvillian superoperator.
+
+% The elements of the first category correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
+
+% This analysis has revealed that the excitations spectrum is composed by two distinct sectors.
+The first one is realized by the (finite) set of localized excitations with discrete eigenvalues.
+Extending
+% the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
+% \emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation. 
+% 
+% Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+% and are deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
+% the associated spectrum exhibit an explicit dependence from the size of the domain.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
+% express the spectral decomposition of the Liouvillian superoperator.
 

### 2018-06-12 AnalyticStructure_main.tex
continuing

--- 2018-06-11 AnalyticStructure_main.tex
@@
 
-% In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
-% characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
-% principle free to explore the whole space.
+\subsection{Fluctuation states. A localization argument for the response density}
+It is evident that the arguments presented in the above section have a limited interest for the study
+of Ground State quantities of molecules. By definition, all these quantities can be expressed as a 
+functional which \emph{entirely} depends on bound states. As an illustration it is sufficient to recall
+the Hohenberg-Kohn theorem that states that the Ground-State (GS) energy is a functional of the GS
+charge density $\dmnot$. For molecular systems that are electronically stable (i.e. no anionic or metastable configurations),
+such quantity is localized, in the sense of the above section. Stated otherwise, 
+\emph{there is no need to express efficiently any portion of the continuum spectrum} to have a reliable GS treatment of molecules.
 
-Linear response can be effectively applied to the analysis of the electronic excitations in open systems. In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that 
-the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic observable induced by a 
-time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the \emph{linear response functional}
+Let us now inspect the case of LR calculations.
+%Linear response can be effectively applied to the analysis of the electronic excitations in open systems.
+In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that 
+the GS density $\dmnot$ is accessible and expressed in a given computational treatment. 
+The linear response formalism allows us to evaluate the modification of the expectation value of a generic observable induced by a 
+time (or frequency)-dependent perturbing field $\op\Phi(\omega)$ acting on the system. 
+This quantity, written in the frequency domain, can be expressed through the evaluation of the \emph{linear response functional}
 \be\lb{LinearResponseFunctDef1}
-\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
+\braket{\delta\op O}_\Phi(\omega) = \trace{\dm'_\Phi(\omega)\op O} \;,
 \ee
 where $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
-and we have introduced the \emph{response density operator} $\dm'(\omega)$ that codifies the modification of the ground-state density induced by the perturbation.
+and we have introduced the \emph{response density operator} $\dm'_\Phi(\omega)$ that codifies the modification of $\dmnot$ induced by the perturbation $\op\Phi(\omega)$.
 
-The main objective of this section is to investigate the structure of the building blocks needed to express the response density operator. In particular, we are interested in clarifying 
-the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential.
+%The main objective of this section is to investigate the structure of the building blocks needed to express the response density operator. In particular, we are interested in clarifying 
+%the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential.
 
@@
 
-\subsection{Fluctuation states. A localization argument for the response density}
 \label{FluctuationState}
 
-The response density operator is expressed as the first-order variation of ground state density $\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$, where the set $\{\ket{\psi_p}\}$ denote the 
-occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
-as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are described by real 
-functions, when projected in the $\r$-representation.
+The response density operator is expressed as the first-order variation of $\dmnot=\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$, where the set $\{\ket{\psi_p}\}$ denote the 
+occupied states, \emph{i.e} the subset of the bound eigenstates\footnote{In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are described by real 
+functions, when projected in the $\r$-representation.} of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
+as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$.
 
@@
 \ee
-where $\op\Phi(\omega)$ represents the perturbing field. The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
+where $\op\Phi(\omega)$ represents the perturbing field. 
+The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
 operator, linking the occupied and empty subspaces of $\hnot$, and satisfies the \emph{transverse} condition  
@@
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. Due to this fact it is possible to introduce an explicit representation of the 
-response density as follows 
+where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. 
+Due to this fact we can introduce an explicit representation of the 
+response density parametrized as
 \be\lb{rhoPrimeFluctuationStateDef1}
-\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
+\dm'_\Phi(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p^\Phi(-\omega)} + \ketbra{f_p^\Phi(\omega)}{\psi_p}\right) \;.
 \ee
-Here we have defined the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, that span the empty subspace of $\hnot$. 
+Here we have introduced the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p^\Phi(\omega)}\}$, 
+that have values in the \emph{unoccupied} subspace of $\hnot$. 
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
@@
 \be\lb{fluctuationStateEqMotion1}
-\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;,
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p^\Phi(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;,
 \ee
@@
 % \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
-The solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of a self-consistent inhomogeneous Helmholtz equation
+It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of
+a set of scattering problems:
+%a self-consistent inhomogeneous Helmholtz equation
 \be\lb{rhoPrimeFluctuationStateDef2}
-\ket{f_p(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s(\omega)} \;,
+\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s_p^\Phi(\omega)} \;,
 \ee
-where in this case the source term contains further addend apart from the unperturbed potential and reads:
+with:%here in this case the source term contains further addend apart from the unperturbed potential and reads:
 \be
-\ket{s(\omega)} =  \op V\ket{f_p(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
+\ket{s_p^\Phi(\omega)} =  \op V\ket{f_p^\Phi(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
 \ee
-The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
-the source term depends also from the perturbation added to the system so this analysis applies only to the class of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
-in the $\r$-representation. 
+As a stringent hypothesis, 
+let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, line $\op V$ nonzero on a bounded real-space domain.
+%The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
+%the source term depends also from the perturbation added to the system so this analysis applies only to the class 
+%of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
+%in the $\r$-representation. 
 It emerges that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 

### 2018-06-12 AnalyticStructure_main.tex
continuing

@@
 \ee
-As a stringent hypothesis, 
-let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, line $\op V$ nonzero on a bounded real-space domain.
+As a \emph{stringent} hypothesis, 
+let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, like $\op V$, localized, i.e. nonzero \emph{only}
+on a bounded real-space domain.
 %The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
@@
   %in the $\r$-representation. 
-It emerges that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 
-fluctuation state. For $\omega > |\eps_p|$,  the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ delocalized in the whole accessible space,
-whereas for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ exhibit a bound-state behavior in the long range.
+It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
+that govern the localization properties of the corresponding 
+fluctuation state. Even when the above locality argument holds true, for $\omega > |\eps_p|$, 
+the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ which is \emph{delocalized} in the whole accessible space.
+Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ \emph{may} 
+exhibit a bound-state behavior in the long range, once again provided that the above locality arguments on $\op V'$ and $\Phi$ are valid.
 

### 2018-06-13 AnalyticStructure_main.tex
continuing

@@
 When describing the Ground State of a molecule, we suppose that the potential operator, even if non-local,
-is associated to real-space elements $\bra{\r} \op V \ket{\r'}$ that can be considered as nonzero only on a
+can be effectively restricted on wavefunctions that can be considered as nonzero only on a
 bounded domain. In other terms, a molecule can be associated to a ``scatterer'' that has a \emph{finite} 
@@
 occupied states, \emph{i.e} the subset of the bound eigenstates\footnote{In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are described by real 
-functions, when projected in the $\r$-representation.} of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
+functions, when projected in the $\r$-representation.} of $\hnot$ with (negative) energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
 as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$.
@@
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
-written as a modified Sternheimer equations \cite{mahan1980}
+written as a modified Sternheimer equation~\cite{mahan1980}
 \be\lb{fluctuationStateEqMotion1}
-\left[\omega - (\hnot-\eps_p)\right]\ket{f_p^\Phi(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;,
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p^\Phi(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'_\Phi])\ket{\psi_p} \;,
 \ee
-and we observe that the first-order Hamiltonian contains, apart from the perturbing field, a further term $\op V'[\dm']$ due to the density-dependence of $\hnot$.
+and we observe that the first-order Hamiltonian contains, apart from the perturbing field, a further term $\op V'[\dm'_\Phi]$ due to the density-dependence of $\hnot$.
 
@@
 As a \emph{stringent} hypothesis, 
-let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, like $\op V$, localized, i.e. nonzero \emph{only}
-on a bounded real-space domain.
+let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, like $\op V$ such that its action
+can be restricted (if suitable) on a bounded real-space domain.
 %The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
@@
 fluctuation state. Even when the above locality argument holds true, for $\omega > |\eps_p|$, 
-the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ which is \emph{delocalized} in the whole accessible space.
+the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ which is \emph{delocalized} in the entire real-space domain.
+Such delocalization is an intrinsic consequence of the value of $\omega$, and it does not depend on the particular
+choice of the operators.
 Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ \emph{may} 
@@
 
-A direct confirmation of the localization character of fluctuation states at $\omega=0$ can be achieved through a ground-state calculation. Indeed, $\ket{f_p(\omega)}$ are nothing but the 
-perturbed KS eigenstates projected out from the domain of $\dmnot$, so for a constant perturbation $\op\Phi_s$ it turns out that $\ket{f_p(0)} = \op Q_0\ket{\psi_p^{\Phi_s}}$. The perturbed KS 
-states $\ket{\psi_p^{\Phi_s}}$ can be computed (beyond LR) by performing a DFT ground-state computation in which the constant perturbing field is added to the external potential and the 
-spatial extension of the fluctuation states can be directly measured. 
-The results of this procedure for a $CO$ molecule subjected to a static electric field are reported in figure \ref{co_alphaStatic}. The local character of the fluctuation states at $\omega=0$ is 
-probed by verifying the convergence of the statical polarizability versus the size of the computational domain used to express the fluctuation states. The convergence rate is compared with the 
-one of the static dipole of the molecule computed at zero external field. The plots evidence that the typical sizes of $\ket{f_p(0)}$ are analogous to the ones of the unperturbed KS orbitals.
+Such locality property of the fluctuation state can be directly confirmed for static perturbations at $\omega=0$.
+Let us consider a static perturbing operator $\op\Phi_s$ that can be restricted to a finite domain. 
+Any local operator, like e.g. a static electric field in the direction $\vec F$, $\Phi_s(\r) = -\vec F \cdot \r$, would satisfy such property.
+We consider the perturbed hamiltonian $\hnot[\rho_{\Phi_s}] + \Phi_s$, where we indicate with $\rho_{\Phi_s}$ the GS density of the
+perturbed system. We assume that the perturbation strength ($|\vec F|$ in the above exemple) is sufficiently small to be consistent with a LR 
+treatment of the problem. 
+In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian 
+can be extracted with traditional GS techniques, as by the hypothesis of Eq.~\eqref{SEHelmholtz1},
+they would exhibit bound-state behaviour.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
+is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
+solution exists, this cannot be found for energies above threshold.}
+
+It is then easy to see that the fluctuation state at $\omega=0$ can be expressed
+in terms of the corresponding bound state of the perturbed Hamiltonian, i.e.
+$\ket{f_p^{\Phi_s}(0)} \simeq \op Q_0 \ket{\psi_p^{\Phi_s}}$.
+For any value of $p$, the locality of the $\ket{f_p^{\Phi_s}(0)}$ therefore directly stems from the
+bound-state behaviour of $\ket{\psi_p^{\Phi_s}}$. As $\omega=0$ is by hypothesis 
+lower than $|\eps_p|$ this is consistent with the above observation.
+
+% A direct confirmation of the localization character of fluctuation states at $\omega=0$ can be achieved through a ground-state calculation. Indeed, $\ket{f_p(\omega)}$ are nothing but the 
+% perturbed KS eigenstates projected out from the domain of $\dmnot$, so for a constant perturbation $\op\Phi_s$ it turns out that $\ket{f_p(0)} = \op Q_0\ket{\psi_p^{\Phi_s}}$. The perturbed KS 
+% states $\ket{\psi_p^{\Phi_s}}$ can be computed (beyond LR) by performing a DFT ground-state computation in which the constant perturbing field is added to the external potential and the 
+% spatial extension of the fluctuation states can be directly measured. 
+In Fig.~\eqref{co_alphaStatic} illustrate this procedure for a $CO$ molecule 
+perturbed by a static electric field. The local character of the fluctuation states at $\omega=0$ is 
+probed by verifying the convergence of the statical polarizability versus 
+the size of the computational domain used to express the fluctuation states. The convergence rate is compared with the 
+one of the static dipole of the molecule computed at zero external field. 
+The plots evidence that the typical sizes of $\ket{f_p(0)}$ are analogous to the ones of the unperturbed KS orbitals.
 

### 2018-06-13 AnalyticStructure_main.tex
update

--- 2018-06-12 AnalyticStructure_main.tex
@@
 that a given computational model provides for a specific set of quantities, regardless of their potential agreement with 
-experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertanties
+experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
 of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
@@
 
-A recent, remarkable exemple of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
+A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
 where a grassroot community of code-owners struggled to extract well-defined computational results in the context of 
 Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as Lattice constants and bulk modulus of 
-elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertanties 
+elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties 
 on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics computer code. 
-Any other code able to extract the same quantites with the same approximations might be compared with the 
+Any other code able to extract the same quantities with the same approximations might be compared with the 
 results of the community in order to assess its computational reliability.
@@
 the linear susceptibility of the system (i.e. the \emph{reducible} polarizability).
-Altough we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
+Although we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
 approaches, in the context Quasi-Particle equations.
@@
 
-Let us start our discussion by revisting the impact that the Isolated BC have on the 
+Let us start our discussion by revisiting the impact that the Isolated BC have on the 
 solutions of the time-independent Schr\"odinger Equation.
@@
 
-\subsection{Fluctuation states. A localization argument for the response density}
-It is evident that the arguments presented in the above section have a limited interest for the study
-of Ground State quantities of molecules. By definition, all these quantities can be expressed as a 
-functional which \emph{entirely} depends on bound states. As an illustration it is sufficient to recall
-the Hohenberg-Kohn theorem that states that the Ground-State (GS) energy is a functional of the GS
-charge density $\dmnot$. For molecular systems that are electronically stable (i.e. no anionic or metastable configurations),
-such quantity is localized, in the sense of the above section. Stated otherwise, 
-\emph{there is no need to express efficiently any portion of the continuum spectrum} to have a reliable GS treatment of molecules.
+% In this section we review the fundamental equations that govern the linear response regime of molecular-like systems in vacuum. Due to their intrinsic nature, this class of systems is 
+% characterized by a potential energy localized in a finite region around system's atoms and free boundary conditions proper of the open systems are adopted, so the wave function is in 
+% principle free to explore the whole space.
 
-Let us now inspect the case of LR calculations.
-%Linear response can be effectively applied to the analysis of the electronic excitations in open systems.
-In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that 
-the GS density $\dmnot$ is accessible and expressed in a given computational treatment. 
-The linear response formalism allows us to evaluate the modification of the expectation value of a generic observable induced by a 
-time (or frequency)-dependent perturbing field $\op\Phi(\omega)$ acting on the system. 
-This quantity, written in the frequency domain, can be expressed through the evaluation of the \emph{linear response functional}
+Linear response can be effectively applied to the analysis of the electronic excitations in open systems. In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that 
+the ground-state density $\dmnot$ has been provided. The linear response formalism allows us to evaluate the modification of the expectation value of a generic observable induced by a 
+time-dependent perturbing field acting on the system. This quantity, written in the frequency domain, can be expressed through the evaluation of the \emph{linear response functional}
 \be\lb{LinearResponseFunctDef1}
-\braket{\delta\op O}_\Phi(\omega) = \trace{\dm'_\Phi(\omega)\op O} \;,
+\braket{\delta\op O}(\omega) = \trace{\dm'(\omega)\op O} \;,
 \ee
 where $\op O$ represents the observable\footnote{For a sake of concreteness, we are limiting our considerations to observables that do not explicitly depend on time} under inspection 
-and we have introduced the \emph{response density operator} $\dm'_\Phi(\omega)$ that codifies the modification of $\dmnot$ induced by the perturbation $\op\Phi(\omega)$.
+and we have introduced the \emph{response density operator} $\dm'(\omega)$ that codifies the modification of the ground-state density induced by the perturbation.
 
-%The main objective of this section is to investigate the structure of the building blocks needed to express the response density operator. In particular, we are interested in clarifying 
-%the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential.
+The main objective of this section is to investigate the structure of the building blocks needed to express the response density operator. In particular, we are interested in clarifying 
+the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential.
 
@@
 
+\subsection{Fluctuation states. A localization argument for the response density}
 \label{FluctuationState}
 
-The response density operator is expressed as the first-order variation of $\dmnot=\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$, where the set $\{\ket{\psi_p}\}$ denote the 
-occupied states, \emph{i.e} the subset of the bound eigenstates\footnote{In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are described by real 
-functions, when projected in the $\r$-representation.} of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
-as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$.
+The response density operator is expressed as the first-order variation of ground state density $\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$, where the set $\{\ket{\psi_p}\}$ denote the 
+occupied states, \emph{i.e} the subset of the bound eigenstates of $\hnot$ with energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
+as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$. In what follows we will assume that the set of states $\{\ket{\psi_p}\}$ are described by real 
+functions, when projected in the $\r$-representation.
 
@@
 \ee
-where $\op\Phi(\omega)$ represents the perturbing field. 
-The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
+where $\op\Phi(\omega)$ represents the perturbing field. The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
 operator, linking the occupied and empty subspaces of $\hnot$, and satisfies the \emph{transverse} condition  
@@
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. 
-Due to this fact we can introduce an explicit representation of the 
-response density parametrized as
+where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. Due to this fact it is possible to introduce an explicit representation of the 
+response density as follows 
 \be\lb{rhoPrimeFluctuationStateDef1}
-\dm'_\Phi(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p^\Phi(-\omega)} + \ketbra{f_p^\Phi(\omega)}{\psi_p}\right) \;.
+\dm'(\omega) = \sum_p\left(\ketbra{\psi_p}{f_p(-\omega)} + \ketbra{f_p(\omega)}{\psi_p}\right) \;.
 \ee
-Here we have introduced the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p^\Phi(\omega)}\}$, 
-that have values in the \emph{unoccupied} subspace of $\hnot$. 
+Here we have defined the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p(\omega)}\}$, that span the empty subspace of $\hnot$. 
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
@@
 \be\lb{fluctuationStateEqMotion1}
-\left[\omega - (\hnot-\eps_p)\right]\ket{f_p^\Phi(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;,
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'])\ket{\psi_p} \;,
 \ee
@@
 % \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
-It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of
-a set of scattering problems:
-%a self-consistent inhomogeneous Helmholtz equation
+The solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of a self-consistent inhomogeneous Helmholtz equation
 \be\lb{rhoPrimeFluctuationStateDef2}
-\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s_p^\Phi(\omega)} \;,
+\ket{f_p(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s(\omega)} \;,
 \ee
-with:%here in this case the source term contains further addend apart from the unperturbed potential and reads:
+where in this case the source term contains further addend apart from the unperturbed potential and reads:
 \be
-\ket{s_p^\Phi(\omega)} =  \op V\ket{f_p^\Phi(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
+\ket{s(\omega)} =  \op V\ket{f_p(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
 \ee
-As a stringent hypothesis, 
-let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, line $\op V$ nonzero on a bounded real-space domain.
-%The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
-%the source term depends also from the perturbation added to the system so this analysis applies only to the class 
-%of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
-%in the $\r$-representation. 
+The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
+the source term depends also from the perturbation added to the system so this analysis applies only to the class of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
+in the $\r$-representation. 
 It emerges that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that govern the localization properties of the corresponding 
@@
 
+From the analysis discussed in the previous section it emerges that the general treatment of the LR for open systems \emph{requires} to deal with delocalized
+objects. In facts, either if one choose the fluctuation states' formalism, or the ``sum over excitations'' (SOE) approach, it turns out that the main building blocks
+beyond a specific energetic threshold have an unbound behavior in the long range. 
+On the basis of this consideration is then reasonable to try to understand if a computational setup tailored to deal with the ground state problem is idoneous to provide
+reliable results for the LR.
+
+\vspace{0.3cm}
+
 % From the theoretical analysis of the previous section we can made two statements:

### 2018-06-13 AnalyticStructure_main.tex
continuing

@@
 
-\section{Localization properties of the linear response actors in open systems}
+%\section{Localization properties of the linear response actors in open systems}
 
@@
 
-\subsection{Fluctuation states. A localization argument for the response density}
+\section{Fluctuation states. A localization argument for the response density}
 It is evident that the arguments presented in the above section have a limited interest for the study
@@
 \be\lb{LiouvillianRhopomegaDef1}
-\left(\omega - \Liouv\right) \dm'(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
+\left(\omega - \Liouv\right) \dm'_\Phi(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
 \ee
@@
 \be\lb{RhopTransverseDef1}
-\dm' = \dm_{\perp} \doteq \dmnot\dm'\op Q_0 + \op Q_0\dm'\dmnot \;,
+\dm'_\Phi = \dm_{\perp} \doteq \dmnot\dm'_\Phi\op Q_0 + \op Q_0\dm'_\Phi\dmnot \;,
 \ee
@@
 
-\emph{(Tweet)} The analysis described in this section has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$ possess the same long-range properties of the bound KS
-orbitals for $\omega < |\eps_p|$, while behave as unbound states for values of $\omega$ above the threshold levels. In the next section we will discuss the implication of the existence of these
-two distinct regimes on the numerical convergence of the observables computed within the LR framework. Before doing this we propose an analogous analysis with the aim to understand the localization 
-properties of the excitation-based description of the LR.
+\subsection{Strong and weak convergence}
 
-\subsection{Excitation operators. The analytic structure of the susceptibility functional}
+The analysis described above has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$ 
+are susceptible to exhibit bound-state long-range behaviour \emph{only} when $\omega < |\eps_p|$, 
+while they behave as unbound states for values of $\omega$ above the threshold levels.
+
+This fact has interesting implication in the evaluation of LR quantities.
+%
+% In the next section we will discuss the implication of the existence of these
+% two distinct regimes on the numerical convergence of the observables computed within the LR framework. 
+% Before doing this we propose an analogous analysis with the aim to understand the localization 
+% properties of the excitation-based description of the LR.
+% 
+% The localization properties of fluctuation states allows us to assess the reliability of the linear response functional
+% computed using the given basis set. 
+%
+Indeed, writing the response 
+density in terms of fluctuation states implies that 
+\be\lb{LinearResponseFunctDef2}
+\braket{\delta\op O}_\Phi(\omega) = 2\mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
+\ee
+%so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}.
+Let us suppose that also the observable of interest $\op O$ exhibit the locality properties of the potentials $ \op V$, $\op \Phi$, $\op V'$.
+Once again, it would be enough to consider a local operator for this condition to be met.
+We observe that there exists two 
+distinct regimes, on the basis of value of $\omega$. 
+The first one, which we will refer to as the \emph{below threshold} regime, is realized when
+$\omega$ is lower than the ionization potential $|\eps_h|$.
+In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} 
+is expressed in terms of genuinely localized 
+quantities. The quantities $\braket{\psi_p \op O| f_p^\Phi(\omega)}$, 
+being scalr products of bound-state-like objects, may thus be evaluated with computational setup that
+are similar to the ones usually employed for GS calculations.
+This consideration proves why, when a given computer code employs established GS numerical techniques, 
+\emph{it is much easier to converge LR quantities for $\omega$ below threshold}.
+The convergence in this regime is ``strong'', in the sense that the basis functions employed are able to express
+wit arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
+
+% , each of which 
+% possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
+% is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
+
+On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
+states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in ``weak'' sense,
+\emph{i.e.} inside the scalar products of 
+\eqref{LinearResponseFunctDef2}. 
+In this case $\ket{f_p^\Phi(\omega)}$ is a unbound, delocalized function, and 
+the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. 
+In this regime \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
+This observation indicates that, above threshold, a computational setup 
+provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an
+unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
+The non-vanishing spherical-wave behaviour in the long range of $\ket{f_p^\Phi(\omega)}$ is therefore responsible
+of this convergence difficulties, especially for high frequencies.
+
+As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in 
+three distinct real-space computational setups, which differs for the dimension of 
+the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime,
+whereas the effect of the computational setup are clearly visible for values of $\omega$ that exceed the threshold value.
+For these ultraviolet regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
+which are more than sufficient below threshold.
+
+\begin{figure}
+\includegraphics[scale=0.56]{co_spectrum.eps}
+\caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+\end{figure}
+
+\section{Excitation operators. The analytic structure of the susceptibility functional}
 
@@
 %\section{Quality indicator for the numerical convergence of the LR}   %{Criterion for a reliable sampling of the excitation operators}
-\section{Criterion of computational reliability for the numerical convergence of the LR}
 
@@
 \vspace{0.3cm}
-
-% From the theoretical analysis of the previous section we can made two statements:
-% \begin{itemize}
-%  \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
-%  wave functions for higher values of $\omega$. 
-%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
-%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
-%  an effective representation of the spectral function. 
-% \end{itemize}
-The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
-if so, up to which energy threshold can we assume that our computations do converge?
-
-The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
-The properties of the $\mu$-basis (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description 
-of the ground state properties of the system.
-
-FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
-The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
-We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
-a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
-$\omega=|\eps_p|$.
-
-SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
-the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
-in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
-priori indicator of the goodness of the results.
-
-\subsection{Strong and weak convergence}
-
-The localization properties of fluctuation states allows us to assess the reliability of the linear response functional computed using the given basis set. Indeed, writing the response 
-density in terms of fluctuation states implies that 
-\be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = 2\sum_p \bra{\psi_p}\op O\ket{f_p(\omega)} \;,
-\ee
-so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}. We observe that there exists two 
-distinct regimes, on the basis of value of $\omega$. The first one, which we will refer to as the \emph{below threshold regime}, is realized when $\omega$ is lower than the ionization 
-potential $|\eps_h|$. In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} is expressed in terms of genuinely localized 
-quantities\footnote{This consideration holds for the class of observables for which $\bra{\psi_p}\op O$ is a localized state  with bound-state behavior in the long range}, each of which 
-possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
-is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
-
-On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
-states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in weak sense, \emph{i.e} inside the scalar products of 
-\eqref{LinearResponseFunctDef2}, where the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. This observation indicates that, above threshold, a computational setup 
-provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
-
-As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in three distinct real-space basis set, which differs for the dimension of 
-the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime, whereas the effect of the computational 
-setup are clearly visible for values of $\omega$ that exceed the threshold value.
-
-\begin{figure}
-\includegraphics[scale=0.56]{co_spectrum.eps}
-\caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
-\end{figure}
 
@@
 \end{figure}
+\section{Criterion of computational reliability for the numerical convergence of the LR}
+
+% From the theoretical analysis of the previous section we can made two statements:
+% \begin{itemize}
+%  \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
+%  wave functions for higher values of $\omega$. 
+%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
+%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
+%  an effective representation of the spectral function. 
+% \end{itemize}
+The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
+if so, up to which energy threshold can we assume that our computations do converge?
+
+The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
+The properties of the $\mu$-basis (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description 
+of the ground state properties of the system.
+
+FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
+The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
+We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
+a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
+$\omega=|\eps_p|$.
+
+SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
+the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
+in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
+priori indicator of the goodness of the results.
 
@@
 
-\section{Comments and conclusions}
+\subsection{Comments and conclusions}
 

### 2018-06-13 AnalyticStructure_main.tex
continuing

@@
 will not be effective for continuum states, due to the different long-range asymptotic behaviour - which in turn is a clear consequence of the 
-BC of the problem. In a numerical treatment, states with $\epsilon > 0$ will have a value of their energy that will \emph{always}
+BC of the problem. In a numerical treatment, discretizing the problem with a \emph{finite}
+number of degrees of freedom, we will only have acces to \emph{pseudo-} continuum states,
+whose energy values and density of states will depend on the representation of the kinetic operator
+in the basis set. As a consequence, numerical eigenstates with $\epsilon > 0$ will have a value of their energy that will \emph{always}
 depend on the computational setup.
@@
 A direct numerical evidence of this problem has been discussed in \cite{boffi2016}. The authors of this paper analyze the effects of a finite basis set on the 
-occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
-with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, 
+and the independence of its energy with respect to the basis set.
+It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is
 able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
@@
 \be\lb{fluctuationStateEqMotion1}
-\left[\omega - (\hnot-\eps_p)\right]\ket{f_p^\Phi(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'_\Phi])\ket{\psi_p} \;,
+\left[\omega - (\hnot-\eps_p)\right]\ket{f_p^\Phi(\omega)} = \op Q_0(\op\Phi(\omega)+\op V'[\dm'_\Phi](\omega))\ket{\psi_p} \;,
 \ee
-and we observe that the first-order Hamiltonian contains, apart from the perturbing field, a further term $\op V'[\dm'_\Phi]$ due to the density-dependence of $\hnot$.
-
-\begin{figure}[t]
-\includegraphics[scale=0.56]{CO_alpha+D0_vsBoxSize.eps}
-\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability of the $CO$ with respect to the size of the computational domain.}
-\end{figure}
-
+and we observe that the first-order Hamiltonian contains, 
+apart from the perturbing field, a further term $\op V'[\dm'_\Phi]$ due to the density-dependence of $\hnot$.
 % The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
@@
 \be\lb{rhoPrimeFluctuationStateDef2}
-\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\ket{s_p^\Phi(\omega)} \;,
+\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\left(\op V\ket{f_p^\Phi(\omega)} + \ket{s_p^\Phi(\omega)} \right)\;,
 \ee
-with:%here in this case the source term contains further addend apart from the unperturbed potential and reads:
-\be
-\ket{s_p^\Phi(\omega)} =  \op V\ket{f_p^\Phi(\omega)} + \op Q_0(\op V'(\omega) + \op \Phi(\omega))\ket{\psi_p} \;.\nn
-\ee
+with%:here in this case the source term contains further addend apart from the unperturbed potential and reads:
+$%\be
+\ket{s_p^\Phi(\omega)} = \op Q_0(\op V'[\dm'_\Phi](\omega) + \op \Phi(\omega))\ket{\psi_p}
+$. %\ee
+
+It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
+that govern the localization properties of the corresponding 
+fluctuation state.
 As a \emph{stringent} hypothesis, 
-let us now assume that the operator $\op Q_0(\op V'(\omega) + \op \Phi(\omega))$ is, like $\op V$ such that its action
-can be restricted (if suitable) on a bounded real-space domain.
+let us now assume that the ket $\ket{s_p^\Phi(\omega)}$ is localized, namely its evaluation can be
+restricted (if suitable) on a bounded real-space domain.
 %The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
@@
   %in the $\r$-representation. 
-It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
-that govern the localization properties of the corresponding 
-fluctuation state. Even when the above locality argument holds true, for $\omega > |\eps_p|$, 
+Even when such locality argument holds true, for $\omega > |\eps_p|$, 
 the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ which is \emph{delocalized} in the entire real-space domain.
@@
 Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ \emph{may} 
-exhibit a bound-state behavior in the long range, once again provided that the above locality arguments on $\op V'$ and $\Phi$ are valid.
+exhibit a bound-state behavior in the long range, once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ 
+-- hence on $\op V'$ and $\Phi$ -- are valid.
 
@@
 Let us consider a static perturbing operator $\op\Phi_s$ that can be restricted to a finite domain. 
-Any local operator, like e.g. a static electric field in the direction $\vec F$, $\Phi_s(\r) = -\vec F \cdot \r$, would satisfy such property.
+Any local operator, like e.g. a static electric field in the direction $\mathbf F$, $\Phi_s(\r) = -\mathbf F \cdot \r$, would satisfy such property.
 We consider the perturbed hamiltonian $\hnot[\rho_{\Phi_s}] + \Phi_s$, where we indicate with $\rho_{\Phi_s}$ the GS density of the
-perturbed system. We assume that the perturbation strength ($|\vec F|$ in the above exemple) is sufficiently small to be consistent with a LR 
+perturbed system. We assume that the perturbation strength ($F$ in the above exemple) is sufficiently small to be consistent with a LR 
 treatment of the problem. 
@@
 solution exists, this cannot be found for energies above threshold.}
+\begin{figure}[t]
+\includegraphics[scale=0.56]{CO_alpha+D0_vsBoxSize.eps}
+\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability of the $CO$ with respect to the size of the computational domain.}
+\end{figure}
 
-It is then easy to see that the fluctuation state at $\omega=0$ can be expressed
+From the linearized Schroedinger Equation of the perturbed problem, it is easy to see that the fluctuation state at $\omega=0$ can be expressed
 in terms of the corresponding bound state of the perturbed Hamiltonian, i.e.
@@
 bound-state behaviour of $\ket{\psi_p^{\Phi_s}}$. As $\omega=0$ is by hypothesis 
-lower than $|\eps_p|$ this is consistent with the above observation.
+lower than $|\eps_p|$, this is consistent with the above considerations.
 
@@
 The convergence in this regime is ``strong'', in the sense that the basis functions employed are able to express 
-wit arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
+with arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
+This is of course true even when the above states are only implicitly expressed by the employed LR treatment,
+ as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ (see.e.g. \cite{baroni2008,linlinKPM}).
 
@@
 For these ultraviolet regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
-which are more than sufficient below threshold.
+which in turn reveal more than sufficient below threshold.
 

### 2018-06-25 AnalyticStructure_main.tex
update

@@
 \emph{scalar coupling kernel}
-\be
+\be\lb{CouplingKernelDef1}
 U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
@@
 
-From the equations of motion for the excited states to the Casida equations...
+% We show that Casida equations are equivalent to the operator eigenvalue equations \eqref{ExcitationOperatorsDef1} when an explicit basis $\{\ket{\eta}\}$ for the empty states subspace is used,
+% so that $\op Q_0 = \sum_{\eta}\ketbra{\eta}{\eta}$. Operators $\op O$ satisfying the transverse condition $\op O = \op O_{\perp}$ (see eq. \eqref{RhopTransverseDef1}) can be represented as 
+% follows
+% \be\lb{OperatorTransBasisExpDef1}
+% \op O = \sum_{p\eta}\left(
+% \excite{p}{\eta}\trace{\decay{\eta}{p}\op O} + \decay{\eta}{p}\trace{\excite{p}{\eta}\op O}
+% \right) \;,
+% \ee
+% where the \emph{transition operators} $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$
+% are normalized as follows
+% \be
+% \trace{\excite{p}{\eta}\excite{q}{\rho}} = \trace{\decay{\eta}{p}\decay{\rho}{q}} = 0 \;, \quad
+% \trace{\excite{p}{\eta}\decay{\rho}{q}} = \delta_{pq}\delta_{\eta\rho} \;. \nonumber
+% \ee
+% Expanding equations \eqref{ExcitationOperatorsDef1} in the basis of transitions provides a matrix equation for the coefficients of the expansion. In particular from the left action equation
+% one has
+% \be
+% \sum_{q\rho}\mat{\trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
+% \trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \decay{\beta}{q}} \\
+% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
+% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \decay{\beta}{q}}}
+% \mat{X_a^{p\eta} \\ Y_a^{p\eta}} = \Omega_a \mat{X_a^{p\eta} \\ Y_a^{p\eta}}
+% \ee
+
+We show that Casida equations are equivalent to the equations of motion for the excited states \eqref{ExcitationOperatorsDef3}. To this scope we introduce an explicit basis $\{\ket{\eta}\}$
+in the subspace of empty states so that both $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ can be represented as
+\be
+\ket{\phi^a_p} = \sum_\eta X^a_{p\eta}\ket{\eta} \;, \q
+\bra{\chi^a_p} = \sum_\eta}\bra{\eta}Y^a_{p\eta} \;.
+\ee
+Plugging this expansion into equations \eqref{ExcitationOperatorsDef3} and projecting on a arbitrary element $\ket{\rho}$ of the basis provides a linear systems of equations for the coefficients
+$X^a_{p\eta}$ and $Y^a_{p\eta}$, namely
+\begin{align}
+ \sum_\eta(H_{0\rho\eta}-\eps_p\delta_{\rho\eta})X^a_{p\eta} + \bra{\rho}\op V'[\op E_a]\ket{\psi_p} &= \Omega_a X^a_{p\rho} \;, \nn \\
+ -\sum_\eta (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})Y^a_{p\eta} - \bra{\psi_p}\op V'[\op E_a]\ket{\rho}& = \Omega_a Y^a_{p\rho} \;. \nn
+\end{align}
+Using this basis, excitation operators are expressed as a linear combination of transition operators $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$,
+as follows
+\be\lb{ExcitationOpBasisTransition1}
+\op E_a = \sum_{p\eta}\excite{p}{\eta}X^a_{p\eta}+\decay{\eta}{p}Y^a_{p\eta} \;.
+\ee
+The contribution of the coupling operator in the equations of motion of excited states can expressed by means of the coupling kernel \eqref{CouplingKernelDef1} as
+\begin{align}
+& \bra{\rho}\op V'[\op E_a]\ket{\psi_p} = \sum_{q\eta}\left(U[\decay{\rho}{p};\excite{q}{\eta}]X^a_{q\eta} + U[\decay{\rho}{p};\decay{\eta}{q}]Y^a_{q\eta}\right) \;,\nn \\
+& \bra{\psi_p}\op V'[\op E_a]\ket{\rho} = \sum_{q\eta}\left(U[\excite{p}{\rho};\excite{q}{\eta}]X^a_{q\eta} + U[\excite{p}{\rho};\decay{\eta}{q}]Y^a_{q\eta}\right) \;, \nn
+\end{align}
+and so equations \eqref{ExcitationOperatorsDef3} can be recasted in matrix form
+\be\lb{ExcitationMatrixEq1}
+\sum_{q\eta}\mat{F_{p\rho}^{q\eta} &  D_{p\rho}^{q\eta}  \\
+- E_{p\rho}^{q\eta} & - G_{p\rho}^{q\eta} }
+\mat{X^a_{q\eta} \\ Y^a_{q\eta}} = \Omega_a \mat{X^a_{p\rho} \\ Y^a_{p\rho}}
+\ee
+where
+\begin{align}
+& F_{p\rho}^{q\eta} = (H_{0\rho\eta}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\decay{\rho}{p};\excite{q}{\eta}] \;,\nn \\
+& D_{p\rho}^{q\eta} = U[\decay{\rho}{p};\decay{\eta}{q}] \;,\nn \\
+& E_{p\rho}^{q\eta} = U[\excite{p}{\rho};\excite{q}{\eta}] \;,\nn \\
+& G_{p\rho}^{q\eta} = (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\excite{p}{\rho};\decay{\eta}{q}] \;. \nn
+\end{align}
+Finally, exploiting the symmetry properties of both the unperturbed Hamiltonian and of the coupling kernel it follows that $F=G$ and $D=E$ so that equations
+\eqref{ExcitationMatrixEq1} reduce to the usual formulation of the Casida equations in the basis of transitions.
 

### 2018-06-26 AnalyticStructure_main.tex
update

@@
 where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$,
-resolvent of the free-particle hamltonian $H_s \equiv \op T$.
+resolvent of the free-particle Hamiltonian $H_s \equiv \op T$.
 
@@
 BC of the problem. In a numerical treatment, discretizing the problem with a \emph{finite}
-number of degrees of freedom, we will only have acces to \emph{pseudo-} continuum states,
+number of degrees of freedom, we will only have access to \emph{pseudo-} continuum states,
 whose energy values and density of states will depend on the representation of the kinetic operator
@@
 We consider the perturbed hamiltonian $\hnot[\rho_{\Phi_s}] + \Phi_s$, where we indicate with $\rho_{\Phi_s}$ the GS density of the
-perturbed system. We assume that the perturbation strength ($F$ in the above exemple) is sufficiently small to be consistent with a LR 
+perturbed system. We assume that the perturbation strength ($F$ in the above example) is sufficiently small to be consistent with a LR 
 treatment of the problem. 
@@
 can be extracted with traditional GS techniques, as by the hypothesis of Eq.~\eqref{SEHelmholtz1},
-they would exhibit bound-state behaviour.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
+they would exhibit bound-state behavior.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
 is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
@@
 For any value of $p$, the locality of the $\ket{f_p^{\Phi_s}(0)}$ therefore directly stems from the
-bound-state behaviour of $\ket{\psi_p^{\Phi_s}}$. As $\omega=0$ is by hypothesis 
+bound-state behavior of $\ket{\psi_p^{\Phi_s}}$. As $\omega=0$ is by hypothesis 
 lower than $|\eps_p|$, this is consistent with the above considerations.
@@
 The analysis described above has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$ 
-are susceptible to exhibit bound-state long-range behaviour \emph{only} when $\omega < |\eps_p|$, 
+are susceptible to exhibit bound-state long-range behavior \emph{only} when $\omega < |\eps_p|$, 
 while they behave as unbound states for values of $\omega$ above the threshold levels.
@@
 This is of course true even when the above states are only implicitly expressed by the employed LR treatment,
- as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ (see.e.g. \cite{baroni2008,linlinKPM}).
+ as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
 
@@
 unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
-The non-vanishing spherical-wave behaviour in the long range of $\ket{f_p^\Phi(\omega)}$ is therefore responsible
+The non-vanishing spherical-wave behavior in the long range of $\ket{f_p^\Phi(\omega)}$ is therefore responsible
 of this convergence difficulties, especially for high frequencies.
@@
 \be
-\ket{\phi^a_p} = \sum_\eta X^a_{p\eta}\ket{\eta} \;, \q
-\bra{\chi^a_p} = \sum_\eta}\bra{\eta}Y^a_{p\eta} \;.
+\ket{\phi^a_p} = \sum_\eta X^a_{p\eta}\ket{\eta} \;, \qq
+\bra{\chi^a_p} = \sum_\eta\bra{\eta}Y^a_{p\eta} \;.
 \ee

### 2018-06-26 AnalyticStructure_main.tex
section three

--- 2018-06-13 AnalyticStructure_main.tex
@@
 \emph{it is much easier to converge LR quantities for $\omega$ below threshold}.
-The convergence in this regime is ``strong'', in the sense that the basis functions employed are able to express 
+The convergence in this regime is ``strong'', in the sense that the basis functions employed enable to express 
 with arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
@@
 \eqref{LinearResponseFunctDef2}. 
-In this case $\ket{f_p^\Phi(\omega)}$ is a unbound, delocalized function, and 
-the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator. 
-In this regime \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
+In this case $\ket{f_p^\Phi(\omega)}$ is a unbound, delocalized function; a numerical treatment tailored for localized
+functions will \emph{never} be able to discretise such function with arbitrary accuracy.  
+In this context, the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator:
+\emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
 This observation indicates that, above threshold, a computational setup 
-provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able to express an
+provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able (even implicitly) to express an
 unbiased description of the fluctuation states in the support of $\{\bra{\psi_p}\op O\}$.
@@
 
+Such concept of threshold has an evident physical interpretation: for energies in a range higher than the ionization potential,
+localized and delocalized states might be coupled by the perturbation. Obtaining convergence of the observable quantities at these energies is therefore much more challenging if one employs 
+numerical techniques which were originally tailored for GS calculations.
+
 \section{Excitation operators. The analytic structure of the susceptibility functional}
 
-The study of the localization properties of the LR functional, formerly discussed through the inspection of the response density operator, can be reformulated in terms of the 
-\emph{susceptibility functional}, defined trough the operator equation  
+In view of reproducibility, the scalar product of Eq.~\eqref{LinearResponseFunctDef1}, defining the observable fluctuation, may be compared among various numerical treatments.
+However, even though directly related to experimental results, such quantity is not by itself a property of the molecule, as it is a function of $\omega$ which explicitly depends on the perturbation operator $\op \Phi$, not to mention
+the target observable $\op O$.
+We may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction, that may be local and with a well-defined normalization only for $\omega$ below the ionization threshold.
+Comparing fluctuation states among diverse numerical treatments would be a challenging task.
+
+It is therefore much more interesting to concentrate on LR quantities that are
+defined independently on the perturbing operators and target observables.
+This can be achieved by studying the 
+\emph{susceptibility functional}, defined implicitly trough the operator equation  
 \be\lb{SusceptibilityDef1}
-\dm'(\omega) = \sop{{\cal \chi}}(\omega) \op\Phi(\omega) \;. 
+\dm'(\omega) = \left(\omega -\mathcal L \right)^{-1} \commutator{\op \Phi(\omega)}{\dmnot} = \sop{{\cal \chi}}(\omega) \op\Phi(\omega) \;. 
 \ee
-This alternative formulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
-feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field.
-
-The analysis is based on the spectral decomposition of the Liouville equation \eqref{LiouvillianRhopomegaDef1} and the make usage of the \emph{excitation operators}, defined through the 
-left and right action eigenvalue equations 
+%This alternative formulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
+%feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field. 
+The susceptivity (super)operator $\cal \chi(\omega)$ is therfore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined 
+from the molecule hamiltonian $\hnot[\dm]$.
+The ``excitation modes''  of the molecule are defined through the \emph{excitation operators}, satisfying
 \be\lb{ExcitationOperatorsDef1}
@@
 \ee
-Excitations are transverse operators so that $\op E_a = \dmnot\op E_a\op Q_0 + \op Q_0\op E_a\dmnot$ and can be expressed through a dyadic representation as follows
-\begin{align}\lb{ExcitationOperatorsDef2}
-\op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
-\op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;,
-\end{align}
-where we have defined the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals of $\hnot$. 
-% We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties of the Liouvillian described in appendix \ref{LiouvillianAction}. 
-% The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
-% \be\lb{RhopExcitationDef1}
-% \sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
-% \frac{\trace{\op E_a^t\cdot}}{\omega-\Omega_a} \;.
-% \ee 
-By applying equations \eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} presented in appendix \ref{LiouvillianAction} to the dyadic representations of the excitation 
-operators, it emerges that equations \eqref{ExcitationOperatorsDef1} can be recasted in the form of a Sternheimer-like equations for the excited states 
-\begin{align}\lb{ExcitationOperatorsDef3}
-&\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
-&\left[-\Omega_a-(\hnot - \eps_p)\right]\ket{\chi_p^a} = \op Q_0\op V'[\op E^t_a]\ket{\psi_p}  \;, 
-\end{align}
-and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
+The excitations defined in that way may be considered as a basis of the operators that satisfy the transverse condition as per 
+Eq.~\eqref{RhopTransverseDef1}, and enable us to express the suscpeptivity as a spectral decomposition:
+\be\lb{RhopExcitationDef1}
+\sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
+\frac{\trace{\commutator{\op{\tilde E}_a}{\dmnot}\cdot}}{\omega-\Omega_a} \;.
+\ee
+
+Being themselves transverse operators, we may parametrize the excitations by employing  
+the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
+$\psi_p$ and satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
 \be\lb{ExcitedStateOrthNormDef1}
@@
 \ee
-Once again we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows 
+In this way we may parametrize the excitation operators of the system as:
+\begin{align}\lb{ExcitationOperatorsDef2}
+\op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
+\op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;.
+\end{align}
+Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$,
+may then be associated to a set of states $\{\phi^a_p,\chi^a_p\}$,
+entirely defined in the unoccupied subspace.
+
+% We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties 
+% of the Liouvillian described in appendix \ref{LiouvillianAction}. 
+% By applying equations \eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} presented in 
+% appendix \ref{LiouvillianAction} to the dyadic representations of the excitation 
+% operators, 
+By applying the equations \eqref{ExcitationOperatorsDef1} to the above parametrization
+of the excitations, we obtain the following Sternheimer-like equations for the excited states 
+\begin{align}\lb{ExcitationOperatorsDef3}
+&\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
+&\left[-\Omega_a-(\hnot - \eps_p)\right]\ket{\chi_p^a} = \op Q_0\op V'[\op E^t_a]\ket{\psi_p}  \;.
+\end{align}
+By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation
+associated to the excitation energy $\Omega_a$.
+The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues 
+$\Omega_a \rightarrow -\Omega_a$; the associated excitation with negative energy will
+be then parametrized with the states $\{\chi^a_p,\phi^a_p\}$.
+We may concertrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
+
+With the same spirit of the previous sections, we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows 
 \begin{align}
-&\ket{\phi^a_p} = \op G_H(\Omega_a+\eps_p)\ket{s_{\phi}} \;, \nn \\
-&\ket{\chi^a_p} = \op G_H(-\Omega_a+\eps_p)\ket{s_{\chi}} \;,
+\ket{\phi^a_p} &= \op G_H(\Omega_a+\eps_p)\ket{s_{\phi}} \;, \nn \\
+\ket{\chi^a_p} &= \op G_H(-\Omega_a+\eps_p)\ket{s_{\chi}} \;,
 \end{align}
-where the source terms $s_\phi$ and $s_{\chi}$ collect the sum of the r.h.s of \eqref{ExcitationOperatorsDef3} plus the action of the KS potential on the excited states.
+where the source terms $s_\phi$ and $s_{\chi}$ are defined as:
+\begin{align}
+ \ket{s_{\phi}} &= \op V \ket{\phi^a_p} + \op Q_0 \op V'[\op E_a] \ket{\psi_p} \\
+ \ket{s_{\chi}} &= \op V \ket{\chi^a_p} + \op Q_0 \op V'[\op E^t_a] \ket{\psi_p}\;.
+\end{align}
+We first point out that the Helmholtz kernel for the $\ket{\chi^a_p}$ state 
+contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.
+The asymptotic long-range behaviour of $\ket{\chi^a_p}$ thus depends only on the locality properties of 
+$\ket{s_{\chi}}$, which in turn is related to the behaviour of the operator $\op V'[\op E^t_a]$.
 
-The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and we focus our analysis on the sector with positive energies. The localization 
-character of $\op G_H(\Omega_a+\eps_p)$ depends from $\Omega_a$ and we identify the threshold level $\Omega_a=|\eps_p|$. At the same time we point out that the Helmholtz kernel evaluated in 
-$-\Omega_a+\eps_p$ contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.  As a consequence of these behaviors and assuming the spatial localization of 
+On the other hand, the long-range behaviour of $\op G_H(\Omega_a+\eps_p)$ depends from 
+$\Omega_a$, with a threshold of value $\Omega_a=|\eps_p|$. 
+For energies above this value, the behviour
+As a consequence of these behaviors and assuming the spatial localization of 
 the source terms,  we observe that the asymptotic character of $\ket{\phi^a_p}$ changes from bound to unbound as the value of the excitation energy crosses the threshold $|\eps_p|$ while all 

### 2018-06-26 AnalyticStructure_main.tex

@@
 
-From the equations of motion for the excited states to the Casida equations...
+% We show that Casida equations are equivalent to the operator eigenvalue equations \eqref{ExcitationOperatorsDef1} when an explicit basis $\{\ket{\eta}\}$ for the empty states subspace is used,
+% so that $\op Q_0 = \sum_{\eta}\ketbra{\eta}{\eta}$. Operators $\op O$ satisfying the transverse condition $\op O = \op O_{\perp}$ (see eq. \eqref{RhopTransverseDef1}) can be represented as 
+% follows
+% \be\lb{OperatorTransBasisExpDef1}
+% \op O = \sum_{p\eta}\left(
+% \excite{p}{\eta}\trace{\decay{\eta}{p}\op O} + \decay{\eta}{p}\trace{\excite{p}{\eta}\op O}
+% \right) \;,
+% \ee
+% where the \emph{transition operators} $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$
+% are normalized as follows
+% \be
+% \trace{\excite{p}{\eta}\excite{q}{\rho}} = \trace{\decay{\eta}{p}\decay{\rho}{q}} = 0 \;, \quad
+% \trace{\excite{p}{\eta}\decay{\rho}{q}} = \delta_{pq}\delta_{\eta\rho} \;. \nonumber
+% \ee
+% Expanding equations \eqref{ExcitationOperatorsDef1} in the basis of transitions provides a matrix equation for the coefficients of the expansion. In particular from the left action equation
+% one has
+% \be
+% \sum_{q\rho}\mat{\trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
+% \trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \decay{\beta}{q}} \\
+% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
+% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \decay{\beta}{q}}}
+% \mat{X_a^{p\eta} \\ Y_a^{p\eta}} = \Omega_a \mat{X_a^{p\eta} \\ Y_a^{p\eta}}
+% \ee
+
+We show that Casida equations are equivalent to the equations of motion for the excited states \eqref{ExcitationOperatorsDef3}. To this scope we introduce an explicit basis $\{\ket{\eta}\}$
+in the subspace of empty states so that both $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ can be represented as
+\be
+\ket{\phi^a_p} = \sum_\eta X^a_{p\eta}\ket{\eta} \;, \qq
+\bra{\chi^a_p} = \sum_\eta\bra{\eta}Y^a_{p\eta} \;.
+\ee
+Plugging this expansion into equations \eqref{ExcitationOperatorsDef3} and projecting on a arbitrary element $\ket{\rho}$ of the basis provides a linear systems of equations for the coefficients
+$X^a_{p\eta}$ and $Y^a_{p\eta}$, namely
+\begin{align}
+ \sum_\eta(H_{0\rho\eta}-\eps_p\delta_{\rho\eta})X^a_{p\eta} + \bra{\rho}\op V'[\op E_a]\ket{\psi_p} &= \Omega_a X^a_{p\rho} \;, \nn \\
+ -\sum_\eta (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})Y^a_{p\eta} - \bra{\psi_p}\op V'[\op E_a]\ket{\rho}& = \Omega_a Y^a_{p\rho} \;. \nn
+\end{align}
+Using this basis, excitation operators are expressed as a linear combination of transition operators $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$,
+as follows
+\be\lb{ExcitationOpBasisTransition1}
+\op E_a = \sum_{p\eta}\excite{p}{\eta}X^a_{p\eta}+\decay{\eta}{p}Y^a_{p\eta} \;.
+\ee
+The contribution of the coupling operator in the equations of motion of excited states can expressed by means of the coupling kernel \eqref{CouplingKernelDef1} as
+\begin{align}
+& \bra{\rho}\op V'[\op E_a]\ket{\psi_p} = \sum_{q\eta}\left(U[\decay{\rho}{p};\excite{q}{\eta}]X^a_{q\eta} + U[\decay{\rho}{p};\decay{\eta}{q}]Y^a_{q\eta}\right) \;,\nn \\
+& \bra{\psi_p}\op V'[\op E_a]\ket{\rho} = \sum_{q\eta}\left(U[\excite{p}{\rho};\excite{q}{\eta}]X^a_{q\eta} + U[\excite{p}{\rho};\decay{\eta}{q}]Y^a_{q\eta}\right) \;, \nn
+\end{align}
+and so equations \eqref{ExcitationOperatorsDef3} can be recasted in matrix form
+\be\lb{ExcitationMatrixEq1}
+\sum_{q\eta}\mat{F_{p\rho}^{q\eta} &  D_{p\rho}^{q\eta}  \\
+- E_{p\rho}^{q\eta} & - G_{p\rho}^{q\eta} }
+\mat{X^a_{q\eta} \\ Y^a_{q\eta}} = \Omega_a \mat{X^a_{p\rho} \\ Y^a_{p\rho}}
+\ee
+where
+\begin{align}
+& F_{p\rho}^{q\eta} = (H_{0\rho\eta}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\decay{\rho}{p};\excite{q}{\eta}] \;,\nn \\
+& D_{p\rho}^{q\eta} = U[\decay{\rho}{p};\decay{\eta}{q}] \;,\nn \\
+& E_{p\rho}^{q\eta} = U[\excite{p}{\rho};\excite{q}{\eta}] \;,\nn \\
+& G_{p\rho}^{q\eta} = (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\excite{p}{\rho};\decay{\eta}{q}] \;. \nn
+\end{align}
+Finally, exploiting the symmetry properties of both the unperturbed Hamiltonian and of the coupling kernel it follows that $F=G$ and $D=E$ so that equations
+\eqref{ExcitationMatrixEq1} reduce to the usual formulation of the Casida equations in the basis of transitions.
 

### 2018-06-26 AnalyticStructure_main.tex
update plot and biblio

@@
 \usepackage{graphicx}
+\usepackage{subfig}
 \usepackage{amsmath,amsfonts,amssymb,amsthm}
@@
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
-written as a modified Sternheimer equation~\cite{mahan1980}
+written as a modified Sternheimer equation~\cite{mahan1980,giustino2012,giustino2014}
 \be\lb{fluctuationStateEqMotion1}
@@
 \begin{figure}[t]
-\includegraphics[scale=0.56]{CO_alpha+D0_vsBoxSize.eps}
-\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability of the $CO$ with respect to the size of the computational domain.}
+\includegraphics[scale=0.68]{CO_statPolvsBox.eps}
+\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability (blue continuous line) and of the ground state permanent dipole (red dotted line) 
+of the $CO$ molecule with respect to the size of the computational domain. The inset plot evidences the relative percentage convergence using the value associated to the largest 
+box as reference.}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.56]{co_spectrum.eps}
+\includegraphics[scale=0.6]{CO_spectrum.eps}
 \caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
@@
 \begin{figure}[ht]
-\includegraphics[scale=0.24]{CO_exc.eps}
+\includegraphics[scale=0.6]{CO_dos.eps}
 \caption{(Color online) Excitation spectrum of $CO$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
@@
 
+% \begin{figure}[ht]
+% \includegraphics[scale=0.6]{C6H6_dos.eps}
+% \caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+% \label{C6H6_exc}
+% \end{figure}
+% 
+% \begin{figure}[ht]
+% \includegraphics[scale=0.56]{C6H6_excLandscape.eps}
+% \caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+% \end{figure}
+
+% \begin{figure}[ht]
+% \centering
+% \begin{subfigure}[]{0.2\textwidth}
+% \includegraphics[scale=0.56]{C6H6_excLandscape.eps}
+% %\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+% \end{subfigure}
+% \centering
+% \begin{subfigure}[b]{0.2\textwidth}
+% \includegraphics[scale=0.6]{C6H6_dos.eps}
+% \end{subfigure}
+% \caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+% \end{figure}
+
 \begin{figure}[ht]
-\includegraphics[scale=0.24]{C6H6_exc.eps}
-\caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
-\label{C6H6_exc}
+\centering
+\subfloat[aaaa]
+{\label{c6h6_excLand}
+\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
+\centering
+\subfloat[bbbbb]
+{\label{C6H6_exc}
+\includegraphics[scale=0.6]{C6H6_dos.eps}}
+\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
 \end{figure}
 
-\begin{figure}[ht]
-\includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
-\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
-\end{figure}
 \section{Criterion of computational reliability for the numerical convergence of the LR}
@@
 \begin{figure}
-\includegraphics[scale=0.56]{CO_alphaX_isto.eps}
+\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
 \caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
@@
 \be\lb{LiouZeroDef1}
-\Liouvnot \op O = \commutator{\hnot}{O} \;,
+\Liouvnot \op O = \commutator{\hnot}{\op O} \;,
 \ee

### 2018-06-27 AnalyticStructure_main.tex
update

@@
 \usepackage{mathtools,braket}
-\usepackage{tikz}%,pgfplots}
+\usepackage{tikz}
 \usepackage{xifthen}
@@
 \newcommand{\rmat}[1]{\optr R}
+
+\captionsetup{justification=centerlast}
 
@@
 {\label{C6H6_exc}
-\includegraphics[scale=0.6]{C6H6_dos.eps}}
+\includegraphics[scale=0.58]{C6H6_dos.eps}}
 \caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
@@
 
-% We show that Casida equations are equivalent to the operator eigenvalue equations \eqref{ExcitationOperatorsDef1} when an explicit basis $\{\ket{\eta}\}$ for the empty states subspace is used,
-% so that $\op Q_0 = \sum_{\eta}\ketbra{\eta}{\eta}$. Operators $\op O$ satisfying the transverse condition $\op O = \op O_{\perp}$ (see eq. \eqref{RhopTransverseDef1}) can be represented as 
-% follows
-% \be\lb{OperatorTransBasisExpDef1}
-% \op O = \sum_{p\eta}\left(
-% \excite{p}{\eta}\trace{\decay{\eta}{p}\op O} + \decay{\eta}{p}\trace{\excite{p}{\eta}\op O}
-% \right) \;,
-% \ee
-% where the \emph{transition operators} $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$
-% are normalized as follows
-% \be
-% \trace{\excite{p}{\eta}\excite{q}{\rho}} = \trace{\decay{\eta}{p}\decay{\rho}{q}} = 0 \;, \quad
-% \trace{\excite{p}{\eta}\decay{\rho}{q}} = \delta_{pq}\delta_{\eta\rho} \;. \nonumber
-% \ee
-% Expanding equations \eqref{ExcitationOperatorsDef1} in the basis of transitions provides a matrix equation for the coefficients of the expansion. In particular from the left action equation
-% one has
-% \be
-% \sum_{q\rho}\mat{\trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
-% \trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \decay{\beta}{q}} \\
-% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
-% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \decay{\beta}{q}}}
-% \mat{X_a^{p\eta} \\ Y_a^{p\eta}} = \Omega_a \mat{X_a^{p\eta} \\ Y_a^{p\eta}}
-% \ee
-
 We show that Casida equations are equivalent to the equations of motion for the excited states \eqref{ExcitationOperatorsDef3}. To this scope we introduce an explicit basis $\{\ket{\eta}\}$
@@
 
+\section{Computational details}
+
+\subsection{$CO$}
+
+Both GS and LR calculations for the $CO$ molecule are performed in three distinct computational setup that differs for the dimension of the computational
+domain. The molecule is oriented along the $z$ axis and the $z$-dimension of the box is equal to 11.5, 15.1 and 16.6 \AA.
+
+Excitation energies and states are obtained through the explicit diagonalization of the Casida matrix. To this scope we have built a basis in the domain of $\op Q_0$ 
+by calculating the eigenvectors and associated energies of the empty virtual orbitals of $\hnot$. 280 states have been computed in each setup and the corresponding
+energy cutoff in the three simulation box is 30.7, 19.3 and 15.4 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
+
+The DOS reported in figure \ref{CO_exc} are obtained by adding a complex shift of $8\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
+
+\subsection{$C_6H_6$}
+
+Both GS and LR calculations for the $C_6H_6$ molecule are performed in three distinct computational setup that differs for the dimension of the computational
+domain. The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.
+
+Excitation energies and states are obtained through the explicit diagonalization of the Casida matrix. To this scope we have built a basis in the domain of $\op Q_0$ 
+by calculating the eigenvectors and associated energies of the empty virtual orbitals of $\hnot$. 220 states have been computed in each setup and the corresponding
+energy cutoff in the three simulation box is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
+
+The DOS reported in figure \ref{C6H6_exc} are obtained by adding a complex shift of $1.3\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-06-28 AnalyticStructure_main.tex
continuing sec 3

--- 2018-06-26 AnalyticStructure_main.tex
@@
 
-Being themselves transverse operators, we may parametrize the excitations by employing  
+\subsection{The analytic structure of linear susceptivity}
+Being themselves transverse operators, without loss of generality we may parametrize the excitations by employing  
 the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
@@
 Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$,
-may then be associated to a set of states $\{\phi^a_p,\chi^a_p\}$,
-entirely defined in the unoccupied subspace.
+may then be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
+entirely defined in the unoccupied subspace. For each $p,a$, these two states represent, 
+respectively, the state in which the occupied state $\ket{\psi_p}$
+is excited -- or from whom it decays -- when the system is subject to the perturbation $\op E_a^t$.
+We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
+is in general restricted only to a $a$-dependent subset of the occupied orbitals, depending on the particular symmetry 
+of the excitation.
 
@@
 \end{align}
-We first point out that the Helmholtz kernel for the $\ket{\chi^a_p}$ state 
+We first point out that the Helmholtz kernel associated to the $\ket{\chi^a_p}$ state 
 contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.
@@
 $\ket{s_{\chi}}$, which in turn is related to the behaviour of the operator $\op V'[\op E^t_a]$.
+% As in the previous section, we assume the hypothesis that such operator is such that
+% the state $\op Q_0 \op V'[\op E^t_a] \ket{\psi_p}$ is localized, at least when \emph{both}
+% the states $\phi_p^a$ $\chi_p^a$ have bound-state-like behaviour.
 
@@
 $\Omega_a$, with a threshold of value $\Omega_a=|\eps_p|$. 
-For energies above this value, the behviour
-As a consequence of these behaviors and assuming the spatial localization of 
-the source terms,  we observe that the asymptotic character of $\ket{\phi^a_p}$ changes from bound to unbound as the value of the excitation energy crosses the threshold $|\eps_p|$ while all 
-the $\ket{\chi^a_p}$ states exhibit a bound-state behavior for all the values of $a$. 
-Furthermore, excited states are subjected to the orthonormalization condition \eqref{ExcitedStateOrthNormDef1} that acts as a ulterior constraint and has the effect of determining the quantization 
-of the energy levels associated to the the bound-state solutions.
+For energies above this value, the behaviour of the state $\ket{\phi^a_p}$ is 
+delocalized regardless of the particular nature of the operators $\op V$ and $\op V'$.
+This means that, if an excitation operator $\op E_a$ has an energy such that
+$\Omega_a>|\eps_p|$  for \emph{at least one} of the $p \in a$ defining the excitation,
+such operator cannot be restricted to localized states.
+
+As a consequence, we deduce that a molecular excitation \emph{may} be expressed in terms of localized states
+\emph{only} when its energy is lower than \emph{all} the ionization potentials of the occupied states participating to the excitation,
+namely if $\Omega_a>|\eps_p|$ $\forall p \in a$. This will only be true if the operators
+$\op V'[\op E^t_a]$ and $\op V'[\op E_a]$ might be restricted to localized wavefunctions.
+If any of these hypothesis would not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
+% As a consequence of these behaviors and assuming the spatial localization of 
+% the source terms,  we observe that the asymptotic character of $\ket{\phi^a_p}$ changes from bound to unbound as the value of the excitation energy crosses the threshold $|\eps_p|$ while all 
+% the $\ket{\chi^a_p}$ states exhibit a bound-state behavior for all the values of $a$. 
+Furthermore, excited states are subjected to the orthonormalization condition 
+\eqref{ExcitedStateOrthNormDef1} that acts as a ulterior constraint and has the effect of determining the \emph{quantization}
+of the energy levels $\Omega_a$ associated to the bound-state-like objects.
+For delocalized states, as in the case of the continuum states of $\hnot$,
+such a condition has to be interpreted in disctributional sense and does not lead to quantization of $\Omega_a$.
 Thus we can conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute 
-a genuine \emph{discrete} set, while the ones in the unbound energy range behaves as generalized eigenvectors associated to a continuum spectrum.
+-- if localized -- a genuine \emph{discrete} set, while the ones in the unbound energy range behaves as generalized eigenvectors associated to a
+continuum spectrum.
 
@@
 % % threshold levels labels
-\node[left] at (0,5) {$p_h$};
-\node[left] at (0,3) {$p_i$};
-\node[left] at (0,1) {$p_1$};
+\node[left] at (0,5) {$p=h$};
+\node[left] at (0,3) {$p$};
+\node[left] at (0,1) {$p=1$};
 \node[below] at (2,0) {$|\eps_h|$};
-\node[below] at (4,0) {$|\eps_i|$};
+\node[below] at (4,0) {$|\eps_p|$};
 \node[below] at (6,0) {$|\eps_1|$};
@@
 
-The structure of the excitation spectrum follows from the properties of the excited states described above. To clarify this point we consider a value of $\Omega_a$ that satisfies equations
-\eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} possess a solution in which \emph{at least} one of the excited states 
-is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^a_p}$  with the highest value of $|\eps_p|$, among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
-considerations it emerge that if $\Omega_a<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
-of this type thus represent localized quantities and the associated eigenvalue are discrete.
+% The structure of the excitation spectrum follows from the properties of the excited states described above. 
+% To clarify this point we consider a value of $\Omega_a$ that satisfies equations
+% \eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} 
+% possess a solution in which \emph{at least} one of the excited states 
+% is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^a_p}$  with the highest value of $|\eps_p|$, among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
+% considerations it emerge that if $\Omega_a<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
+% of this type thus represent localized quantities and the associated eigenvalue are discrete.
 On the contrary, for $\Omega_a>|\eps_{p_m}|$ some (or all) of the excited states in the dyadic representation
-of the excitation behave as generalized eigenvectors and the corresponding eigenvalue belong to a continuum of accessible values.
+% of the excitation behave as generalized eigenvectors and the corresponding eigenvalue belong to a continuum of accessible values.
 
-The typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}. The plot evidences that below the first ionization energy $|\eps_h|$ only localized excitations are 
-present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest occupied orbital, the elements belonging to the discrete sector are embedded 
-in a continuum of delocalized excitations. Lastly, for energies higher than $|\eps_1|$ the excitations landscape takes contributions only from the delocalized sector.
+The susceptibility functional has therefore a peculiar analytic structure, that
+is made of multiple threshold energies, one for each of the ionization potentials
+associated to the occupied states. 
+If an excitation $\op E_a$ has a energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$,
+it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states.
+
+Following these observations, the typical structure of the excitations landscape 
+may be depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable behaviour of the
+perturbed potential $\op V'$.
+Below the first ionization energy $|\eps_h|$ only localized excitations are 
+present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest 
+occupied orbital, other discrete excitations may exist, and they would be embedded 
+in a continuum of delocalized excitations. 
+Lastly, for energies higher than $|\eps_1|$ \emph{no localized} excitations are anymore possible,
+regardless of the particular behaviour of $\op V'$. The excitations landscape is formed by only continuum energies.
+
+\subsection{Stability and convergence of the excitation spectrum}
+
+The analysis of the above section reveals that the excitation spectrum is composed by two distinct sectors. 
+The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. 
+Extending 
+the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states 
+\eqref{ExcitationOperatorsDef3}, we conclude that such localized excitations behave as 
+\emph{observable} quantities and the associated energies possess ideal features of reproducibility:
+if the numerical basis employed is complete enough to
+represent the states $\{\phi_p^a,\chi_p^a\}$, the energy $\Omega_a$ 
+should not depend from the computational setup used for their representation.
+
+Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+and are deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
+the associated spectrum exhibit an explicit dependence from the size of the domain.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
+express the spectral decomposition of the Liouvillian superoperator.
+
+In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the Density of States of the Liouvillian for the $CO$  and Benzene molecules, 
+for two different numerical setups of increasing simulation domains. 
+The figures show clearly that all the excitations of energy $\Omega_a$ lying below the 
+molecule ionization potential (IP) have a clear localized behaviour, as their energy does not vary with the size of the simulation domain.
+On the other hand, above the first ionization threshold the excitation energies have an energy that strongly depends on the computational
+setup, which is in line with the expected pseudo-continuum character of this sector. 
+In addition, for the benzene molecule it is also possible to 
+identify excitations of energy above IP that still possess a localized behaviour: these excitations satisfy the
+condition $\Omega_a < |\eps_a|$ presented in the above section.
+In Fig.~\ref{c6h6_excLand} we collecting the excitations of the benzene molecule following this criterion:
+the agreement with the expected analytic structure presented in Fig.~\ref{ExcitationLandscape} is impressive.
+
+\subsection{The importance of the continuum sector}
+We have presented formal arguments, confirmed by numerical calculations, that show that 
+the excitations belonging to the discrete sector of the spectrum have energies
+that may be \emph{quantitatively} compared between codes, thanks to their
+localized character. 
+Such objects are LR quantities, associated to the molecule, whose numerical convergence
+might be found by employing techniques which are very similar to 
+the one employed for GS calculations. Being expressed by localized excited states,
+computational setups with sufficient level of completeness will be such to
+express with high \emph{precision} such section of the excitation spectrum.
+
+It might be interesting to obtain information on whether such localized excitations
+will be sufficient to express LR quantities that are associated to localized
+fluctuation states.
 
@@
 \vspace{0.3cm}
-
-\subsection{Stability and convergence of the excitation spectrum}
-
-This analysis reveals that the excitations spectrum is composed by two distinct sectors. The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. Extending 
-the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
-\emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation.
-
-Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
-These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
-and are deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-the associated spectrum exhibit an explicit dependence from the size of the domain.
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
-express the spectral decomposition of the Liouvillian superoperator.
 

### 2018-06-28 AnalyticStructure_main.tex

@@
 \usepackage{graphicx}
+\usepackage{subfig}
 \usepackage{amsmath,amsfonts,amssymb,amsthm}
 \usepackage{mathtools,braket}
-\usepackage{tikz}%,pgfplots}
+\usepackage{tikz}
 \usepackage{xifthen}
@@
 
+\captionsetup{justification=centerlast}
+
 \begin{document}
@@
 
+% \begin{figure}[ht]
+% \includegraphics[scale=0.6]{C6H6_dos.eps}
+% \caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+% \label{C6H6_exc}
+% \end{figure}
+% 
+% \begin{figure}[ht]
+% \includegraphics[scale=0.56]{C6H6_excLandscape.eps}
+% \caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+% \end{figure}
+
+% \begin{figure}[ht]
+% \centering
+% \begin{subfigure}[]{0.2\textwidth}
+% \includegraphics[scale=0.56]{C6H6_excLandscape.eps}
+% %\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
+% \end{subfigure}
+% \centering
+% \begin{subfigure}[b]{0.2\textwidth}
+% \includegraphics[scale=0.6]{C6H6_dos.eps}
+% \end{subfigure}
+% \caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+% \end{figure}
+
 \begin{figure}[ht]
-\includegraphics[scale=0.24]{C6H6_exc.eps}
-\caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
-\label{C6H6_exc}
+\centering
+\subfloat[aaaa]
+{\label{c6h6_excLand}
+\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
+\centering
+\subfloat[bbbbb]
+{\label{C6H6_exc}
+\includegraphics[scale=0.58]{C6H6_dos.eps}}
+\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
 \end{figure}
 
-\begin{figure}[ht]
-\includegraphics[scale=0.56]{c6h6_excitationLandscape.eps}
-\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
-\end{figure}
 \section{Criterion of computational reliability for the numerical convergence of the LR}
@@
 \section{Casida equations}
-
-% We show that Casida equations are equivalent to the operator eigenvalue equations \eqref{ExcitationOperatorsDef1} when an explicit basis $\{\ket{\eta}\}$ for the empty states subspace is used,
-% so that $\op Q_0 = \sum_{\eta}\ketbra{\eta}{\eta}$. Operators $\op O$ satisfying the transverse condition $\op O = \op O_{\perp}$ (see eq. \eqref{RhopTransverseDef1}) can be represented as 
-% follows
-% \be\lb{OperatorTransBasisExpDef1}
-% \op O = \sum_{p\eta}\left(
-% \excite{p}{\eta}\trace{\decay{\eta}{p}\op O} + \decay{\eta}{p}\trace{\excite{p}{\eta}\op O}
-% \right) \;,
-% \ee
-% where the \emph{transition operators} $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$
-% are normalized as follows
-% \be
-% \trace{\excite{p}{\eta}\excite{q}{\rho}} = \trace{\decay{\eta}{p}\decay{\rho}{q}} = 0 \;, \quad
-% \trace{\excite{p}{\eta}\decay{\rho}{q}} = \delta_{pq}\delta_{\eta\rho} \;. \nonumber
-% \ee
-% Expanding equations \eqref{ExcitationOperatorsDef1} in the basis of transitions provides a matrix equation for the coefficients of the expansion. In particular from the left action equation
-% one has
-% \be
-% \sum_{q\rho}\mat{\trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
-% \trace{\decay{\alpha}{p}\, \sop{\mathcal L}\, \decay{\beta}{q}} \\
-% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \excite{q}{\beta}} &
-% \trace{\excite{p}{\alpha}\, \sop{\mathcal L}\, \decay{\beta}{q}}}
-% \mat{X_a^{p\eta} \\ Y_a^{p\eta}} = \Omega_a \mat{X_a^{p\eta} \\ Y_a^{p\eta}}
-% \ee
 

### 2018-07-04 AnalyticStructure_main.tex
first passage up to conclusions

@@
 \ee
-Here we have introduced the set of $\omega$-dependent \emph{fluctuation states} $\{\ket{f_p^\Phi(\omega)}\}$, 
+Here we have introduced the set of $\omega$-dependent \emph{fluctuation states} 
+$\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, 
 that have values in the \emph{unoccupied} subspace of $\hnot$. 
@@
 
+\begin{figure}[ht]
+\includegraphics[scale=0.6]{CO_dos.eps}
+\caption{(Color online) Excitation spectrum of $CO$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+\label{CO_exc}
+\end{figure}
+\begin{figure}[ht]
+\centering
+\subfloat[aaaa]
+{\label{c6h6_excLand}
+\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
+\centering
+\subfloat[bbbbb]
+{\label{C6H6_exc}
+\includegraphics[scale=0.58]{C6H6_dos.eps}}
+\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
+\end{figure}
+
 In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the Density of States of the Liouvillian for the $CO$  and Benzene molecules, 
@@
 condition $\Omega_a < |\eps_a|$ presented in the above section.
-In Fig.~\ref{c6h6_excLand} we collecting the excitations of the benzene molecule following this criterion:
+In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
 the agreement with the expected analytic structure presented in Fig.~\ref{ExcitationLandscape} is impressive.
@@
 fluctuation states.
+By recalling that $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$,
+considering Eq.~\eqref{SusceptibilityDef1} and
+expressing the spectral decomposition of the linear susceptivity we find:
+\begin{align}
+ \ket{f_p^\Phi(\omega)} &= \ket{f_p(\omega)^D} + \ket{f_p(\omega)^C} \lb{FSExcitationDef1} \\
+ \ket{f_p^\Phi(\omega)^D} &= \sum_a^{0<\Omega_a < |\eps_a|} \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \\
+ \ket{f_p^\Phi(\omega)^C} &= \int_{0<\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2}
+\end{align}
+where $f_p^a(\op \Phi,\omega) \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$,
+% \be
+% \ket{f_p(\omega)}   = \left(\sum_a + \int\dd a   \right) \ket{w_p^a} \,
+% \frac{\bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}}{\omega^2-\Omega_a^2} \;,
+% \ee 
+and $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$. 
+In the above equation we have explicitly separated the contributions of the discrete ($D$) and continuous ($C$) excitations 
+in the spectral decomposition \eqref{SusceptibilityDef1}.
+The summation and the integration run only on the positive values of $\Omega_a$.
+The states $\ket{w_p^a}$ that appear in the discrete sum 
+or in the integral are genuinely localized and delocalized, respectively.
+For \emph{any} value of $\omega$ the ket $\ket{f_p^\Phi(\omega)^D}$ has, by definition, a bound-state like
+character as it is expressed as a sum of localized contributions.
+
+We have seen in Sec.~\ref{FluctuationState} that 
+for values of $\omega$ below the first ionization potential we expect
+$\ket{f_p^\Phi(\omega)}$ to have bound-state like behavior.
+For this to be true, the contribution from the delocalized  continuum states defining the state
+$\ket{f_p^\Phi(\omega)^C}$ should resum into a localized, asymptotically vanishing state.
+\footnote{We might have locality of $\ket{f_p^\Phi}$ also when perturbation operator $\op \Phi$ is such that 
+$f_p^a(\op \Phi,\omega)=0$ for any $a$ labelling the continuum excitations. 
+However, this is not true in general: the plot in Fig.~\ref{co_AlphaExc}
+show this evidence when $\op \Phi$ is the dipole operator.}
+
+This means that, contrary to GS, \emph{for LR calculation,
+even when the response density is localized, the contribution coming from the 
+continuum sector of the exicitations can never be neglected}. 
+We are not referring here to the continuum eigenstates of the 
+unperturbed GS hamiltonian, %which is not in itself important for expressing the linear susceptivity, 
+but to the continuum of excitations expressed as eigenstate of the 
+Liouvillian superoperator of Eq.~\eqref{Liouvillian}, needed to 
+express the spectral representation of the linear susceptivity.
+A fluctuation state, even if genuinely localized, will \emph{always} have a nonzero projection
+in the essential part of the Liouvillan spectrum.
+
+\begin{figure}
+\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
+\end{figure}
+We show an evidence of the above statement in Fig.~\ref{co_AlphaExc}. Indeed,
+we may decompose the linear response functional of Eq.~\eqref{LinearResponseFunctDef1}
+for any operator $\op O$ as $\braket{\delta\op O}_\Phi=\braket{\delta\op O}^D_\Phi +
+\braket{\delta\op O}^C_\Phi$, where
+\be
+\braket{\delta\op O}^{D,C}_\Phi(\omega) = 
+2 \mathrm{Re}\left(\bra{\psi_p} \op O \ket{f_p^\Phi(\omega)^{D,C}} \right)\;,
+\ee
+And we show how the value of the static polarizability $\alpha_{zz}(\omega=0)$
+defined in Eq.~\eqref{staticpol} will depend on the set of excitations
+included in the integral defining $\ket{f_p^\Phi(\omega)^C}$.
+Such value is compared with the reference result where the 
+localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
+This is the well-know $S_{-2}$ sum-rule, that express the value of the static polarizability
+in terms of the molecule's oscillator strengths.
+We see that a considerable number of pseudo-continuum excitations is required
+to find the correct result; the sector of the discrete excitations, even though 
+parametrised by localized, observable (in the sense of reproducible) excited states,
+appears to be largely insufficient to express the reference fluctuation state.
+This seems to be independent on the number of atoms of the molecule, as the range in $\omega$ needed to 
+achieve satisfactory agreement is largely above the last valence ionization threshold, which is
+a intensive (i.e. independent on the number of atoms) quantity.
+The inclusion of core electrons in the calculation would have added a further set of localized
+excitations, but at much higher energies than the one needed for this test.
+
+This fact shows that it is \emph{impossible} to restrict the spectral representation
+of $\chi(\omega)$ only localized and discrete excitations, even for representing LR results in the $\omega=0$ limit.
+In addition, we can see that the above sum-rule \emph{cannot} be used to assess
+the correctness of $\chi(\omega)$ for values of $\omega$ above IP; it is enough to recall
+the strong dependency on the box size of the absorption spectra of Fig.~\ref{CO_exc}.
+For all these computational setups, the $S_{-2}$ sum rule is, on the contrary, perfectly satisfied.
+
+\section{Conclusions and Perspectives}
+In the analysis presented in this paper we have investigated how 
+computational results of linear-response calculations of molecular systems 
+might be compared among various formalisms.
+In particular, we have been interested in identifiying the quantities that can
+be expressed in computational setups that are originally conceived for 
+\emph{localised} objects, which are the \emph{only} quantities that
+play a significant role in GS calculations.
+
+We have shown that all response densities for $\omega$ above the first IP
+\emph{have} to be expressed in terms of genuinely delocalized states, whereas below this threshold,
+under reasonable assumptions on the perturbing operators,
+the perturbed density operator is genuinely localized.
+In this localized regime, it is possible to achieve convergence of the numerical result
+by increasing the completeness of the basis with the usual GS rationales.
+One might expect that more complete basis will give more precise results, regardless of their asymptotic behaviour.
+A comparison among various codes in view of reproducibility should therefore be performed 
+initially in this regime.
+
+The situation is not so simple in the above-threshold regime.
+In this case what is important is matrix element of the observable of interest
+between the bound, occupied state and the delocalized fluctuation state.
+To achieve convergence, care should be taken in expressing accurately the FS on the
+appropriate region of space. In view of reproducibility, computational setups which are able to express precisely
+delocalized states seem more interesting in this regime.
+
+Such point of view have also enabled us to shed light on the analytic structure of the 
+linear susceptivity, which is a intrinsic property of the molecule and does not depend on
+ the perturbing fields.
+ In particular, we have concentrated our interest in its spectral representation in
+ terms of ``free oscillation'' (i.e. excitations) of the system.
+ We have found that \emph{not all} the excitations have to be considered on equal footing.
+ As the excitation spectrum has several energy thresholds, one per quasi-particle IP,
+ there is a sector of \emph{discrete}, \emph{localized} excitations -- whose energies are 
+below the corresponding threshold -- which can be compared among different computational treatments.
+Their energies are \emph{true} poles of the linear susceptivity, the excited states being their residues.
+
+On the other hand, the excitation energies which lie above these thresholds are only pseudo-poles of $\chi(\omega)$, 
+and will \emph{strongly} depend on the computational setup. This is visible already for energies higher than
+IP, and it has been pointed out several times (see e.g. \ref{giustino}) in the literature.
+However, such part of the excitation spectrum has a prominent role in the
+great majority of LR quantities, \emph{even in the localised regime} of $\omega$.
+In other terms, the set of continuum excitations might only be \emph{effectively} represented
+in a computational approach, depending on the quantities of interest.
+As an example, we have shown that spectral representations of $\chi(\omega)$ tailored for static
+LR quantities are in general unreliable for absorbtion spectra above IP, whilst provide precise values
+of the excitation energies in the discrete sector.
+
+We believe that these considerations, based on simple manipulations on the fundamental LR equations, will help in increase
+the reliability of LR calculations in the community, and in building test-sets that would help in
+the \emph{calibration} of present and future computer codes, thereby increasing the predictivity of present-day theoretical approaches.
+The example of the static polarizability of molecules
+present ideal features as an initial playground. Work is ongoing in this direction.
+
+\section{Garbage Colllector}
+We have found that a given LR calculation might be decomposed in two different
+contributions. The first one originate from the 
+are two kind of there are two different regimes in which 
+LR results are
+
+In particular, when dealing with localized objects as molecules,
+we have investigated
+
+The first sector is realized by the (finite) set of localized excitations with discrete eigenvalues that contribute 
+as \emph{true poles} of the susceptibility. 
+Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
 
@@
 where we have defined the symmetric operators $\op W_a = \frac{1}{\sqrt{2}}(\ketbra{w_p^a}{\psi_p}+\ketbra{\psi_p}{w_p^a})$ and states $\ket{w_p^a}=\ket{\psi_p^a}+\ket{\chi_p^a}$.
-
-On the basis of the present analysis we have explicitly separated the contributions of the discrete and continuous excitations in the spectral decomposition \eqref{RhopExcitationDef2}. 
-The first sector is realized by the (finite) set of localized excitations with discrete eigenvalues that contribute as \emph{true poles} of the susceptibility. 
-Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum. Excitations belonging to this sector thus lose their intrinsic physical meaning 
-and have to be understood as a tool to express the spectral decomposition of the Liouvillian superoperator.
 
@@
 
-\begin{figure}[ht]
-\includegraphics[scale=0.6]{CO_dos.eps}
-\caption{(Color online) Excitation spectrum of $CO$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
-\label{CO_exc}
-\end{figure}
-
 % \begin{figure}[ht]
@@
 
-\begin{figure}[ht]
-\centering
-\subfloat[aaaa]
-{\label{c6h6_excLand}
-\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
-\centering
-\subfloat[bbbbb]
-{\label{C6H6_exc}
-\includegraphics[scale=0.58]{C6H6_dos.eps}}
-\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
-\end{figure}
-
 \section{Criterion of computational reliability for the numerical convergence of the LR}
@@
 
-Express the fluctuation state in terms of excitation using the relation $\ket{f_p(\omega)} = \dm'(\omega)\ket{\psi_p}$ and using formula \eqref{SusceptibilityDef1} to express the excitation
-expansion of the response density. Due to this procedure we obtain
-\be\lb{FSExcitationDef1}
-\ket{f_p(\omega)}   = \left(\sum_a + \int\dd a   \right) \ket{w_p^a} \,
-\frac{\bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}}{\omega^2-\Omega_a^2} \;,
-\ee 
-with $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$. 
 Show the convergence of the statical polarizability of the $CO$ in function of the number of excitations. Write formula
@@
 continuum sector of the excitation spectrum is
-\begin{figure}
-\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
-\end{figure}
 

### 2018-07-06 AnalyticStructure_main.tex
update

@@
 It might be, for example, in agreement with some previously existing data that the employed computational model is susceptible to reproduce.
-The model itself can in this way be classified as ``accurate''; it may then be employed to extract, \textit{in silico},
+The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
 other quantities that might be then used to \emph{predict} or \emph{interpret} experimental data.
@@
 in particular referring to LR-TDDFT calculation. We will investigate the impact that 
-\emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantites.
+\emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantities.
 In order to do this, we perform analytic considerations on the equations beyond LR treatment.
@@
 Our considerations will also reveal useful for the understanding of the \emph{analytic structure} of LR quantities like
-the linear susceptibility of the system (i.e. the \emph{reducible} polarizability).
+the linear susceptibility of the system (i.e. the reducible polarizability).
 Although we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
@@
 
-\subsection{Long range behavior of the eigenvalue solution of the Schroedinger equation}
+\subsection{Long range behavior of the eigenvalue solution of the Schr\"odinger equation}
 \label{SEopenSystem}
@@
 In view of analysing the impact of the BC, it is instructive to transform 
-the Schroedinger Equation in a \emph{scattering} problem, by writing
+the Schr\"odinger equation in a scattering problem, by writing
 \be\lb{SEHelmholtz1}
@@
 perhaps in a larger region.
-For a computational treatment of the problem, this property is fundamental in the 
-choice of the numerical treatment; we know that basis functions that are tailored to express asymptotically vanishing 
-wavefunctions are better suited for the solution of the problem.
+For a computational analysis of the problem, this property is fundamental in the choice of the numerical treatment as we know that basis functions 
+that are tailored to express asymptotically vanishing wavefunctions are better suited for the solution of the problem.
 
@@
 
-From the above expressions we can see that, \emph{for molecular systems},
-the value $\epsilon=0$
+From the above expressions we can see that, for molecular systems,the value $\epsilon=0$
 represents a \emph{threshold}~\footnote{The threshold value in general should correspond to asymptotic value of the potential at infinity.} 
 energy that separates two different classes of solutions.
-Negative-energy solutions are \emph{localized}, i.e. they exhibit bound-state behaviour far away from the scatterer.
-These are \emph{bound} states and, by means of their normalizability, they are associated to \emph{discrete}, well-defined energies.
+Negative-energy solutions are \emph{localized}, i.e. they exhibit bound-state behavior far away from the scatterer.
+These are bound states and, by means of their normalizability, they are associated to \emph{discrete}, well-defined energies.
 The bound states can be of course labelled by quantum numbers that are defined by the properties of the scatterer, namely the
 symmetries of the potential $\op V$.
-In a computational discretization of the Schroedinger equation, such states can be in principle expressed with arbitrary precision, 
+In a computational discretization of the Schr\"odinger equation, such states can be in principle expressed with arbitrary precision, 
 provided that the numerical treatment offers the adequate level of completeness. 
@@
 It is easy to see from these concepts that a computational treatment that is tailored for the discretization of bound states
-will not be effective for continuum states, due to the different long-range asymptotic behaviour - which in turn is a clear consequence of the 
+will not be effective for continuum states, due to the different long-range asymptotic behavior - which in turn is a clear consequence of the 
 BC of the problem. In a numerical treatment, discretizing the problem with a \emph{finite}
-number of degrees of freedom, we will only have access to \emph{pseudo-} continuum states,
+number of degrees of freedom, we will only have access to a \emph{pseudo}-continuum of states,
 whose energy values and density of states will depend on the representation of the kinetic operator
@@
 
-% As a preliminary step for the forthcoming discussion we present a simple argument that allows us to determine the asymptotic character of the eigenvalue solution of the Schroedinger equation (SE) 
+% As a preliminary step for the forthcoming discussion we present a simple argument that allows us to determine the asymptotic character of the eigenvalue solution of the Schr\"odinger equation (SE) 
 % $\op H\ket{\psi}=\eps\ket{\psi}$. The main aims of this analysis, apart from reproducing the well known behavior of the wave functions, is to introduce some tools and setting up notations and 
@@
 Here we have introduced the set of $\omega$-dependent \emph{fluctuation states} 
-$\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, 
-that have values in the \emph{unoccupied} subspace of $\hnot$. 
+$\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$. 
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
@@
 It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
-that govern the localization properties of the corresponding 
-fluctuation state.
-As a \emph{stringent} hypothesis, 
-let us now assume that the ket $\ket{s_p^\Phi(\omega)}$ is localized, namely its evaluation can be
+that govern the localization properties of the corresponding fluctuation state.
+As a \emph{stringent} hypothesis, let us now assume that the ket $\ket{s_p^\Phi(\omega)}$ is localized, namely its evaluation can be
 restricted (if suitable) on a bounded real-space domain.
@@
 Even when such locality argument holds true, for $\omega > |\eps_p|$, 
-the Helmholtz kernel behaves as a spherical wave and  gives raise to a $f_p(\omega,\r)$ which is \emph{delocalized} in the entire real-space domain.
-Such delocalization is an intrinsic consequence of the value of $\omega$, and it does not depend on the particular
-choice of the operators.
-Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $f_p(\omega,\r)$ \emph{may} 
-exhibit a bound-state behavior in the long range, once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ 
--- hence on $\op V'$ and $\Phi$ -- are valid.
+the Helmholtz kernel behaves as a spherical wave and  gives raise to a $\ket{f^\Phi_p(\omega)}$ which is \emph{delocalized} in the entire real-space domain.
+Such delocalization is an intrinsic consequence of the value of $\omega$, and does not depend on the particular choice of the operators.
+Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $\ket{f^\Phi_p(\omega)}$ exhibits a bound-state behavior in the long range, 
+once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ -- hence on $\op V'$ and $\Phi$ -- are valid.
 
@@
 Let us consider a static perturbing operator $\op\Phi_s$ that can be restricted to a finite domain. 
-Any local operator, like e.g. a static electric field in the direction $\mathbf F$, $\Phi_s(\r) = -\mathbf F \cdot \r$, would satisfy such property.
-We consider the perturbed hamiltonian $\hnot[\rho_{\Phi_s}] + \Phi_s$, where we indicate with $\rho_{\Phi_s}$ the GS density of the
-perturbed system. We assume that the perturbation strength ($F$ in the above example) is sufficiently small to be consistent with a LR 
-treatment of the problem. 
-In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian 
-can be extracted with traditional GS techniques, as by the hypothesis of Eq.~\eqref{SEHelmholtz1},
-they would exhibit bound-state behavior.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
+Any local operator, like \emph{e.g.} a static electric field $\mathbf F$, with associated scalar potential $\Phi_s(\r) = -\mathbf F \cdot \r$, would satisfy such property.
+We consider the perturbed hamiltonian $\hnot[\dm_{\Phi_s}] + \op\Phi_s$, where $\dm_{\Phi_s}$ represents the GS density of the perturbed system, and assume that the 
+perturbation strength ($|\mathbf F|$ in the above example) is sufficiently small to be consistent with a LR treatment of the problem. 
+In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian can be extracted with traditional GS techniques, as by the hypothesis 
+of Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
 is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
@@
 
-From the linearized Schroedinger Equation of the perturbed problem, it is easy to see that the fluctuation state at $\omega=0$ can be expressed
+From the linearized Schr\"odinger Equation of the perturbed problem, it is easy to see that the fluctuation state at $\omega=0$ can be expressed
 in terms of the corresponding bound state of the perturbed Hamiltonian, i.e.
@@
 one of the static dipole of the molecule computed at zero external field. 
-The plots evidence that the typical sizes of $\ket{f_p(0)}$ are analogous to the ones of the unperturbed KS orbitals.
+The plots evidence that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to the ones of the unperturbed KS orbitals.
 
@@
 
-This fact has interesting implication in the evaluation of LR quantities.
-%
-% In the next section we will discuss the implication of the existence of these
-% two distinct regimes on the numerical convergence of the observables computed within the LR framework. 
-% Before doing this we propose an analogous analysis with the aim to understand the localization 
-% properties of the excitation-based description of the LR.
-% 
-% The localization properties of fluctuation states allows us to assess the reliability of the linear response functional
-% computed using the given basis set. 
-%
-Indeed, writing the response 
+This fact has interesting implication in the evaluation of LR quantities. Indeed, writing the response 
 density in terms of fluctuation states implies that 
@@
 quantities. The quantities $\braket{\psi_p \op O| f_p^\Phi(\omega)}$, 
-being scalr products of bound-state-like objects, may thus be evaluated with computational setup that
+being scalar products of bound-state-like objects, may thus be evaluated with computational setup that
 are similar to the ones usually employed for GS calculations.
@@
 In view of reproducibility, the scalar product of Eq.~\eqref{LinearResponseFunctDef1}, defining the observable fluctuation, may be compared among various numerical treatments.
-However, even though directly related to experimental results, such quantity is not by itself a property of the molecule, as it is a function of $\omega$ which explicitly depends on the perturbation operator $\op \Phi$, not to mention
-the target observable $\op O$.
-We may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction, that may be local and with a well-defined normalization only for $\omega$ below the ionization threshold.
-Comparing fluctuation states among diverse numerical treatments would be a challenging task.
-
-It is therefore much more interesting to concentrate on LR quantities that are
-defined independently on the perturbing operators and target observables.
+However, even though directly related to experimental results, such quantity is not by itself a property of the molecule, as it is a function of $\omega$ that explicitly depends 
+on the perturbation operator $\op \Phi$, not to mention the target observable $\op O$. Alternatively, we may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction, 
+%that may be local and with a well-defined normalization 
+with a potential local behavior only for $\omega$ below the ionization threshold. So, Comparing fluctuation states among diverse numerical treatments would be a 
+challenging task.
+
+It is therefore much more interesting to concentrate on LR quantities that are defined independently from the perturbing operators and target observables.
 This can be achieved by studying the 
@@
 %feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field. 
-The susceptivity (super)operator $\cal \chi(\omega)$ is therfore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined 
+The susceptibility (super)operator $\cal \chi(\omega)$ is therefore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined 
 from the molecule hamiltonian $\hnot[\dm]$.
@@
 \ee
-The excitations defined in that way may be considered as a basis of the operators that satisfy the transverse condition as per 
-Eq.~\eqref{RhopTransverseDef1}, and enable us to express the suscpeptivity as a spectral decomposition:
+Excitations defined in that way may be considered as a basis of the operators that satisfy the transverse condition as in  
+Eq.~\eqref{RhopTransverseDef1}, and enable us to express the susceptibility as a spectral decomposition:
 \be\lb{RhopExcitationDef1}
@@
 
-\subsection{The analytic structure of linear susceptivity}
-Being themselves transverse operators, without loss of generality we may parametrize the excitations by employing  
+\subsection{The analytic structure of linear susceptibility}
+Being themselves transverse operators, without loss of generality we can parametrize excitations by employing  
 the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
-$\psi_p$ and satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
+$\ket{\psi_p}$ and satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
 \be\lb{ExcitedStateOrthNormDef1}
@@
 \ee
-In this way we may parametrize the excitation operators of the system as:
+In this way we can parametrize the excitation operators of the system as:
 \begin{align}\lb{ExcitationOperatorsDef2}
@@
 \end{align}
-Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$,
-may then be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
-entirely defined in the unoccupied subspace. For each $p,a$, these two states represent, 
-respectively, the state in which the occupied state $\ket{\psi_p}$
+Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can then be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
+entirely defined in the unoccupied subspace. For each choice of $p,a$, these objects represent, respectively, the state in which the occupied state $\ket{\psi_p}$
 is excited -- or from whom it decays -- when the system is subject to the perturbation $\op E_a^t$.
@@
 By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation
-associated to the excitation energy $\Omega_a$.
+associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).
 The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues 
-$\Omega_a \rightarrow -\Omega_a$; the associated excitation with negative energy will
-be then parametrized with the states $\{\chi^a_p,\phi^a_p\}$.
-We may concertrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
+$\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transpose pair $\{\chi^a_p,\phi^a_p\}$.
+We concentrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
 
@@
 \emph{only} when its energy is lower than \emph{all} the ionization potentials of the occupied states participating to the excitation,
-namely if $\Omega_a>|\eps_p|$ $\forall p \in a$. This will only be true if the operators
-$\op V'[\op E^t_a]$ and $\op V'[\op E_a]$ might be restricted to localized wavefunctions.
-If any of these hypothesis would not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
+namely if $\Omega_a<|\eps_p|$ $\forall p \in a$. This will only be true if the operators
+$\op V'[\op E^t_a]$ and $\op V'[\op E_a]$ can be restricted to localized wavefunctions.
+If any of these hypothesis does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
 % As a consequence of these behaviors and assuming the spatial localization of 
@@
 
-Following these observations, the typical structure of the excitations landscape 
-may be depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable behaviour of the
-perturbed potential $\op V'$.
-Below the first ionization energy $|\eps_h|$ only localized excitations are 
-present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest 
-occupied orbital, other discrete excitations may exist, and they would be embedded 
-in a continuum of delocalized excitations. 
+Following these observations, the typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable 
+behavior of the perturbed potential $\op V'$.
+Below the first ionization energy $|\eps_h|$ only localized excitations are present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the 
+absolute value of the deepest occupied orbital, other discrete excitations may exist, and are embedded in a continuum of delocalized excitations. 
 Lastly, for energies higher than $|\eps_1|$ \emph{no localized} excitations are anymore possible,
-regardless of the particular behaviour of $\op V'$. The excitations landscape is formed by only continuum energies.
-
-\subsection{Stability and convergence of the excitation spectrum}
+regardless of the particular behavior of $\op V'$ so the excitations landscape in this region is composed only by continuum energies.
+
+\subsection{Observable features of the excitation spectrum}
+%\subsection{Stability and convergence of the excitation spectrum}
 
@@
 The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. 
-Extending 
-the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states 
-\eqref{ExcitationOperatorsDef3}, we conclude that such localized excitations behave as 
+% Extending the results achieved in \cite{boffi2016} for the KS virtual orbitals, 
+%to the equations for excited states 
+%\eqref{ExcitationOperatorsDef3}, we conclude that such localized excitations behave as 
+Borrowing the terminology introduced in section \ref{SEopenSystem} to the present case, we can affirm that such localized excitations behaves as
 \emph{observable} quantities and the associated energies possess ideal features of reproducibility:
@@
 
-\subsection{The importance of the continuum sector}
+%\subsection{The importance of the continuum sector}
+\subsection{Physical relevance of the continuum sector}
+
 We have presented formal arguments, confirmed by numerical calculations, that show that 
 the excitations belonging to the discrete sector of the spectrum have energies
-that may be \emph{quantitatively} compared between codes, thanks to their
+that can be \emph{quantitatively} compared between codes, thanks to their
 localized character. 
 Such objects are LR quantities, associated to the molecule, whose numerical convergence
-might be found by employing techniques which are very similar to 
-the one employed for GS calculations. Being expressed by localized excited states,
-computational setups with sufficient level of completeness will be such to
+can be found by employing techniques which are very similar to 
+the one adopted for GS calculations. Being expressed by localized excited states,
+computational setups with sufficient level of completeness are able to
 express with high \emph{precision} such section of the excitation spectrum.
 
-It might be interesting to obtain information on whether such localized excitations
+It is interesting to obtain information on whether such localized excitations
 will be sufficient to express LR quantities that are associated to localized
@@
 considering Eq.~\eqref{SusceptibilityDef1} and
-expressing the spectral decomposition of the linear susceptivity we find:
+expressing the spectral decomposition of the linear susceptibility we find:
+% \begin{align}
+%  \ket{f_p^\Phi(\omega)} &= \ket{f^\Phi_p(\omega)^D} + \ket{f^Phi_p(\omega)^C} \lb{FSExcitationDef1} \\
+%  \ket{f_p^\Phi(\omega)^D} &= \sum_a^{0<\Omega_a < |\eps_a|} \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \\
+%  \ket{f_p^\Phi(\omega)^C} &= \int_{0<\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2}
+% \end{align}
+\be
+\ket{f_p^\Phi(\omega)} = \ket{f^{\Phi}_p(\omega)}_D + \ket{f^{\Phi}_p(\omega)}_C \lb{FSExcitationDef1} \;,
+\ee
+with
 \begin{align}
- \ket{f_p^\Phi(\omega)} &= \ket{f_p(\omega)^D} + \ket{f_p(\omega)^C} \lb{FSExcitationDef1} \\
- \ket{f_p^\Phi(\omega)^D} &= \sum_a^{0<\Omega_a < |\eps_a|} \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \\
- \ket{f_p^\Phi(\omega)^C} &= \int_{0<\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2}
+ \ket{f_p^\Phi(\omega)}_D &= \sum_a^{\Omega_a < |\eps_a|} \ket{w_p^a} \frac{\varphi_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \;, \nn \\
+ \ket{f_p^\Phi(\omega)}_C &= \int_{\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{\varphi_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \;, \nn
 \end{align}
-where $f_p^a(\op \Phi,\omega) \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$,
-% \be
-% \ket{f_p(\omega)}   = \left(\sum_a + \int\dd a   \right) \ket{w_p^a} \,
-% \frac{\bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}}{\omega^2-\Omega_a^2} \;,
-% \ee 
+where $\varphi_p^a(\op \Phi,\omega) \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$,
 and $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$. 
@@
 or in the integral are genuinely localized and delocalized, respectively.
-For \emph{any} value of $\omega$ the ket $\ket{f_p^\Phi(\omega)^D}$ has, by definition, a bound-state like
+For \emph{any} value of $\omega$ the ket $\ket{f_p^\Phi(\omega)}_D$ has, by definition, a bound-state like
 character as it is expressed as a sum of localized contributions.
@@
 $\ket{f_p^\Phi(\omega)}$ to have bound-state like behavior.
-For this to be true, the contribution from the delocalized  continuum states defining the state
-$\ket{f_p^\Phi(\omega)^C}$ should resum into a localized, asymptotically vanishing state.
+For this to be true, the contribution from the delocalized excited states defining
+$\ket{f_p^\Phi(\omega)}_C$ should resum into a localized, asymptotically vanishing state
 \footnote{We might have locality of $\ket{f_p^\Phi}$ also when perturbation operator $\op \Phi$ is such that 
@@
 However, this is not true in general: the plot in Fig.~\ref{co_AlphaExc}
-show this evidence when $\op \Phi$ is the dipole operator.}
+show this evidence when $\op \Phi$ is the dipole operator.}.
 
@@
 even when the response density is localized, the contribution coming from the 
-continuum sector of the exicitations can never be neglected}. 
+continuum sector of the excitations can never be neglected}. 
 We are not referring here to the continuum eigenstates of the 
@@
 Liouvillian superoperator of Eq.~\eqref{Liouvillian}, needed to 
-express the spectral representation of the linear susceptivity.
+express the spectral representation of the linear susceptibility.
 A fluctuation state, even if genuinely localized, will \emph{always} have a nonzero projection
-in the essential part of the Liouvillan spectrum.
+in the essential part of the Liouvillian spectrum.
 
@@
 \braket{\delta\op O}^{D,C}_\Phi(\omega) = 
-2 \mathrm{Re}\left(\bra{\psi_p} \op O \ket{f_p^\Phi(\omega)^{D,C}} \right)\;,
+2 \mathrm{Re}\left(\bra{\psi_p} \op O \ket{f_p^\Phi(\omega)}_{D,C} \right)\;,
 \ee
@@
 might be compared among various formalisms.
-In particular, we have been interested in identifiying the quantities that can
+In particular, we have been interested in identifying the quantities that can
 be expressed in computational setups that are originally conceived for 
@@
 by increasing the completeness of the basis with the usual GS rationales.
-One might expect that more complete basis will give more precise results, regardless of their asymptotic behaviour.
+One might expect that more complete basis will give more precise results, regardless of their asymptotic behavior.
 A comparison among various codes in view of reproducibility should therefore be performed 
@@
 Such point of view have also enabled us to shed light on the analytic structure of the 
-linear susceptivity, which is a intrinsic property of the molecule and does not depend on
+linear susceptibility, which is a intrinsic property of the molecule and does not depend on
  the perturbing fields.
@@
 below the corresponding threshold -- which can be compared among different computational treatments.
-Their energies are \emph{true} poles of the linear susceptivity, the excited states being their residues.
+Their energies are \emph{true} poles of the linear susceptibility, the excited states being their residues.
 
@@
 As an example, we have shown that spectral representations of $\chi(\omega)$ tailored for static
-LR quantities are in general unreliable for absorbtion spectra above IP, whilst provide precise values
+LR quantities are in general unreliable for absorption spectra above IP, whilst provide precise values
 of the excitation energies in the discrete sector.
@@
 \section{Casida equations}
+\label{casida}
 

### 2018-07-08 AnalyticStructure_main.tex
continuing

@@
 computational reliability of the results. More specifically, a computational result may be considered as reliable for various reasons.
-It might be, for example, in agreement with some previously existing data that the employed computational model is susceptible to reproduce.
+It might be, for example, in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
 The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
-other quantities that might be then used to \emph{predict} or \emph{interpret} experimental data.
+other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
 Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
@@
 where a grassroot community of code-owners struggled to extract well-defined computational results in the context of 
-Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as Lattice constants and bulk modulus of 
+Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of 
 elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties 
-on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics computer code. 
+on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code. 
 Any other code able to extract the same quantities with the same approximations might be compared with the 
@@
 
+The paper is organized as follows.
+Initially we will inspect how the question of reproducibility may be expressed 
+for ground state calculations of molecules. 
+Following these guidelines, we will then move to LR equations,
+by first considering the equations of motion of the response density operator, given
+the application of a perturbing field.
+Then we will consider the behaviour of the ``free oscillations'', i.e. the excited states
+of the molecule.
 Our considerations will also reveal useful for the understanding of the \emph{analytic structure} of LR quantities like
 the linear susceptibility of the system (i.e. the reducible polarizability).
+We support our considerations with numerical results on simple LR-TDDFT quantities.
+For readability purposes, the details of each calculation are explained in the appendix.
+
 Although we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
@@
 %\section{Localization properties of the linear response actors in open systems}
+\subsection{Long range behavior of the eigenvalue solution of the Schr\"odinger equation}
+\label{SEopenSystem}
 
@@
 
-\subsection{Long range behavior of the eigenvalue solution of the Schr\"odinger equation}
-\label{SEopenSystem}
 Consider a (one-body) wavefunction $\ket{\psi}$ solution of the equation
@@
 perhaps in a larger region.
-For a computational analysis of the problem, this property is fundamental in the choice of the numerical treatment as we know that basis functions 
+For a computational analysis of the problem, this property is fundamental in the choice of the numerical treatment as we know that
+computational basis sets 
 that are tailored to express asymptotically vanishing wavefunctions are better suited for the solution of the problem.
@@
 the Helmholtz kernel behaves as a spherical wave and  gives raise to a $\ket{f^\Phi_p(\omega)}$ which is \emph{delocalized} in the entire real-space domain.
-Such delocalization is an intrinsic consequence of the value of $\omega$, and does not depend on the particular choice of the operators.
+Such delocalization is an intrinsic consequence of the value of $\omega$, and does not depend on the particular choice of 
+$\op \Phi$.
 Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $\ket{f^\Phi_p(\omega)}$ exhibits a bound-state behavior in the long range, 
@@
 perturbation strength ($|\mathbf F|$ in the above example) is sufficiently small to be consistent with a LR treatment of the problem. 
-In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian can be extracted with traditional GS techniques, as by the hypothesis 
-of Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
+In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian can be extracted with traditional GS techniques, 
+as from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
 is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
@@
 quantities. The quantities $\braket{\psi_p \op O| f_p^\Phi(\omega)}$, 
-being scalar products of bound-state-like objects, may thus be evaluated with computational setup that
+being scalar products of bound-state-like objects, may thus be evaluated with computational setups that
 are similar to the ones usually employed for GS calculations.
 This consideration proves why, when a given computer code employs established GS numerical techniques, 
-\emph{it is much easier to converge LR quantities for $\omega$ below threshold}.
+\emph{it is much easier to converge LR quantities for $\omega$ below IP}.
 The convergence in this regime is ``strong'', in the sense that the basis functions employed enable to express 
@@
 entirely defined in the unoccupied subspace. For each choice of $p,a$, these objects represent, respectively, the state in which the occupied state $\ket{\psi_p}$
-is excited -- or from whom it decays -- when the system is subject to the perturbation $\op E_a^t$.
+is excited -- or from whom it decays -- when the system is subject to the perturbation $\Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
 We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
@@
 By applying the equations \eqref{ExcitationOperatorsDef1} to the above parametrization
-of the excitations, we obtain the following Sternheimer-like equations for the excited states 
+of the excitations, we obtain the following Sternheimer-like equations for the excited states:
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 \begin{align}
-\ket{\phi^a_p} &= \op G_H(\Omega_a+\eps_p)\ket{s_{\phi}} \;, \nn \\
-\ket{\chi^a_p} &= \op G_H(-\Omega_a+\eps_p)\ket{s_{\chi}} \;,
+\ket{\phi^a_p} &= \op G_H(\Omega_a+\eps_p)\left(\op V \ket{\phi^a_p} + \ket{s_{\phi}} \right) \;, \nn \\
+\ket{\chi^a_p} &= \op G_H(-\Omega_a+\eps_p)\left( \op V \ket{\chi^a_p} + \ket{s_{\chi}} \right)\;,
 \end{align}
@@
 \begin{align}
- \ket{s_{\phi}} &= \op V \ket{\phi^a_p} + \op Q_0 \op V'[\op E_a] \ket{\psi_p} \\
- \ket{s_{\chi}} &= \op V \ket{\chi^a_p} + \op Q_0 \op V'[\op E^t_a] \ket{\psi_p}\;.
+ \ket{s_{\phi}} &=  \op Q_0 \op V'[\op E_a] \ket{\psi_p} \\
+ \ket{s_{\chi}} &=  \op Q_0 \op V'[\op E^t_a] \ket{\psi_p}\;.
 \end{align}
@@
 $\Omega_a>|\eps_p|$  for \emph{at least one} of the $p \in a$ defining the excitation,
-such operator cannot be restricted to localized states.
+such operator cannot be parametrized by employing localized states only.
 
@@
 the associated spectrum exhibit an explicit dependence from the size of the domain. 
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
-express the spectral decomposition of the Liouvillian superoperator.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as
+a representation of the density of states of the Liouvillian superoperator.
 
@@
 For this to be true, the contribution from the delocalized excited states defining
-$\ket{f_p^\Phi(\omega)}_C$ should resum into a localized, asymptotically vanishing state
-\footnote{We might have locality of $\ket{f_p^\Phi}$ also when perturbation operator $\op \Phi$ is such that 
-$f_p^a(\op \Phi,\omega)=0$ for any $a$ labelling the continuum excitations. 
-However, this is not true in general: the plot in Fig.~\ref{co_AlphaExc}
-show this evidence when $\op \Phi$ is the dipole operator.}.
+$\ket{f_p^\Phi(\omega)}_C$ should resum into a localized, asymptotically vanishing state.
+Indeed, there is no particular reason to believe that $\ket{f_p^\Phi(\omega)}_C$ should be
+zero. The linear independence of the $\ket{w_p^a}$ states would imply that 
+$\varphi_p^a(\op \Phi,\omega)=0$ for any $a$ labelling the continuum excitations,
+which is too strong a condition for a general choice of $\op \Phi$.
+\footnote{The plot in Fig.~\ref{co_AlphaExc}
+show this evidence even in the simple case when $\op \Phi$ is the dipole operator.}.
 
@@
 express the spectral representation of the linear susceptibility.
-A fluctuation state, even if genuinely localized, will \emph{always} have a nonzero projection
+We \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
 in the essential part of the Liouvillian spectrum.

### 2018-07-09 AnalyticStructure_main.tex
Update on Overleaf.

@@
 \section{Conclusions and Perspectives}
-In the analysis presented in this paper we have investigated how 
-computational results of linear-response calculations of molecular systems 
-might be compared among various formalisms.
-In particular, we have been interested in identifying the quantities that can
-be expressed in computational setups that are originally conceived for 
-\emph{localised} objects, which are the \emph{only} quantities that
-play a significant role in GS calculations.
-
-We have shown that all response densities for $\omega$ above the first IP
-\emph{have} to be expressed in terms of genuinely delocalized states, whereas below this threshold,
+% In the analysis presented in this paper we have investigated how 
+% computational results of linear-response calculations of molecular systems 
+% might be compared among various formalisms.
+% In particular, we have been interested in identifying the quantities that can
+% be expressed in computational setups that are originally conceived for 
+% \emph{localised} objects, which are the \emph{only} quantities that
+% play a significant role in GS calculations.
+
+By analysing the fundamental equations of LR calculations of molecules, we have shown that the response density for values of $\omega$ above the first IP
+\emph{have} to be expressed in terms of genuinely delocalized states. %, whereas 
+Below this threshold,
 under reasonable assumptions on the perturbing operators,

### 2018-07-09 AnalyticStructure_main.tex
hello

--- 2018-07-08 AnalyticStructure_main.tex
@@
 
-\section{Garbage Colllector}
-We have found that a given LR calculation might be decomposed in two different
-contributions. The first one originate from the 
-are two kind of there are two different regimes in which 
-LR results are
-
-In particular, when dealing with localized objects as molecules,
-we have investigated
-
-The first sector is realized by the (finite) set of localized excitations with discrete eigenvalues that contribute 
-as \emph{true poles} of the susceptibility. 
-Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
+\section{Garbage Collector}
 
@@
 % \end{itemize}
-The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
-if so, up to which energy threshold can we assume that our computations do converge?
-
-The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
-The properties of the $\mu$-basis (state something about the systematic character the basis? comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description 
-of the ground state properties of the system.
-
-FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
-The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
-We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
-a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
-$\omega=|\eps_p|$.
-
-SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
-the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
-in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
-priori indicator of the goodness of the results.
+% The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
+% if so, up to which energy threshold can we assume that our computations do converge?
+% 
+% The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
+% The properties of the $\mu$-basis (state something about the systematic character the basis?
+comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description
+% of the ground state properties of the system. 
+% 
+% FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
+% The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
+% We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
+% a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
+% $\omega=|\eps_p|$. 
+% 
+% SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
+% the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
+% in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
+% priori indicator of the goodness of the results.
 
@@
 $\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort...
-
-This analysis has revealed that the excitations spectrum is composed by two distinct sectors.
-The first one is realized by the (finite) set of localized excitations with discrete eigenvalues.
-Extending
-the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
-\emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation.
-
-Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
-These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
-and are deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-the associated spectrum exhibit an explicit dependence from the size of the domain.
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
-express the spectral decomposition of the Liouvillian superoperator.
-
-%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
-%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
-%  an effective representation of the spectral function.
 

### 2018-07-09 AnalyticStructure_main.tex
hello

@@
 \begin{abstract}
+A reliable procedure for the analysis of a system within the framework of the linear response should include
+the study of the conditions under which numerical convergence of the results can be achieved. 
+Such considerations are important not only for reproducibility of the results among different computer codes 
+employing diverse formalisms, but also in view of providing a deeper understanding on the impact of models' 
+approximations on the scientific outcomes of the simulation.
+
+We discuss these aspects in the context of linear response treatment of molecular systems. 
+By analysing simple case-studies with a highly complete numerical formalism, 
+we explore the interplay between locality of the perturbed wavefunctions and the 
+numerical convergence of observable quantities.
+We identify some convergence indicators and discuss under which regimes they might be employed.
+This will enable us to draw some considerations on the analytic structure of the linear susceptivity for open systems and on the potential convergence issues that might arise in a given computational setup.
+
+We believe that such discussion could provide useful considerations and perspectives for the design of a effective approaches for the study of molecular excitations in realistic conditions.
+
 We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

--- 2018-07-09 AnalyticStructure_main.tex
@@
 \newcommand{\rmat}[1]{\optr R}
+\newcommand{\fscd}[1]{\ket{f_p^\Phi(\omega)^{#1}}}
 
@@
 %\title{On the analytic structure of the linear response susceptibility in open systems}
-\title{Localization properties, observable character and computational reliability of the linear response in open systems}
-
+\title{Locality and Computational Reliability of Linear Response Calculations for Molecular Systems}% Localization properties, observable character and computational reliability of the linear response in open systems}
+\author{Marco D'Alessandro}%
+\affiliation{Istituto di Struttura della Materia-CNR (ISM-CNR), Via del Fosso del Cavaliere 100, 00133 Roma, Italia}
 \author{Luigi Genovese}
@@
 38054 Grenoble, France}
-\author{Marco D'Alessandro}%
-\affiliation{Istituto di Struttura della Materia-CNR (ISM-CNR), Via del Fosso del Cavaliere 100, 00133 Roma, Italia}
-
 \date{\today}
@@
 \begin{abstract}
-We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
-In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems. We show that optical excitations of energy below the LR ionization potential 
-behave as observable, localized quantities, that can be computationally calculated with high precision, provided an adequate level of completeness.
-Above this energy threshold, the analytic structure of the susceptibility functional might be separated in two sectors: one can still be described in terms of observable excitation 
-with discrete energies, that can be captured within computational setups tailored for localized states. However such excitations are embedded in a continuum of excited states 
-that, on the contrary, behave as plane waves and cannot be described efficiently by the same computational techniques. Such excitations do not exhibit observable features and 
-\emph{cannot} be considered as poles of the dynamical polarizability. Nonetheless, the contribution of such continuum of excitation reveals to be of paramount importance even 
-for expressing LR quantities in the infrared regime like for example static polarizability.
-This is particularly evident for small molecules; we show how these considerations might be influenced by the size of molecular system.
-We then present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
-in any discretization scheme.  This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
-unoccupied subspace.
+By performing a critical analysis of the fundamental equations of linear-response  (LR) formalisms in molecules, 
+we explore the interplay between locality of the response density operator and  numerical convergence of LR-related quantities.
+We show that the first ionization potential of the system behaves as a threshold energy: for frequencies below this value, it is possible to parametrize the response density by employing localized states only.
+Above this threshold, such a locality property cannot be achieved.
+Such considerations may be transposed in terms of the molecule's excited states. We show that not all the system's excitations can be considered on equal footing.
+There is a discrete sector of excitations that can be parametrized by observable, localized states, which can be computationally expressed with high precision, provided an adequate level of completeness.
+We present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
+in any discretization scheme.  
+The remaining excitation modes belong to a continuum spectrum that, on the contrary, is not directly associated to observable properties and can only be effectively represented in a given computational setup.
+Such considerations are important not only for reproducibility of the results among different computer codes 
+employing diverse formalisms, but also in view of providing a deeper understanding on the impact of models' 
+approximations on the scientific outcomes of the simulation.
+
+% ---
+% We discuss these aspects in the context of linear response treatment of molecular systems. 
+% By analysing simple case-studies with a highly complete numerical formalism, 
+% we explore the interplay between locality of the perturbed wavefunctions and 
+% numerical convergence of observable quantities.
+This will enable us to draw some considerations on the analytic structure of the linear susceptivity for open systems and on the potential convergence issues that might arise in a given computational setup.
+
+% We believe that such discussion could provide useful considerations and perspectives for the design of a effective approaches for the study of molecular excitations in realistic conditions.
+
+% We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
+% In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems.
+% Above this energy threshold, the excitation spectrum may be separated in two sectors: one can still be described in terms of observable excitation 
+% with discrete energies, that can be captured within computational setups tailored for localized states. 
+% This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
+% unoccupied subspace.
 \end{abstract}
@@
 on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code. 
-Any other code able to extract the same quantities with the same approximations might be compared with the 
+Any other code able to extract the same quantities with the same approximations may be compared with the 
 results of the community in order to assess its computational reliability.
@@
 in the whole accessible space.
-As they cannot be normalized they belong to the essential spectrum of the hamiltonian operator and form a \emph{continuum} of states.
-Thanks to the Lippman-Schwinger relation of Eq.~\eqref{SEHelmholtz1} they can be put in bijection with the eigenstates of the 
-free-particle hamiltonian $\op H_s$. We may say that their quantum numbers are determined by the Laplacian operator, 
+As they cannot be normalized they belong to the essential spectrum of the Hamiltonian operator and form a \emph{continuum} of states.
+Thanks to the Lippmann-Schwinger relation of Eq.~\eqref{SEHelmholtz1} they can be put in bijection with the eigenstates of the 
+free-particle Hamiltonian $\op H_s$. We may say that their quantum numbers are determined by the Laplacian operator, 
 regardless of the particular features of the potential.
@@
 and the independence of its energy with respect to the basis set. 
-It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is
-able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
-true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
-Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+% It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
+% able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
+% true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
+On the contrary, it is clearly shown that the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
 
@@
 functions, when projected in the $\r$-representation.} of $\hnot$ with (negative) energy $\eps_p$ lower than the Fermi level. Using this notation we denote the energy of the HOMO level 
-as $\eps_h$ and identify the value of the first ionization potential with $|\eps_h|$.
-
-In the contest of the LR the response density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008})
+as $\eps_h$ and identify the value of the first ionization potential with IP~$\equiv|\eps_h|$.
+
+The response density satisfies an equation of motion written in the form of a quantum Liouville operator (for example see \cite{baroni2008})
 \be\lb{LiouvillianRhopomegaDef1}
@@
 where $\op\Phi(\omega)$ represents the perturbing field. 
+The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term. The action of these 
+terms reads, respectively
+\be\lb{LiouZeroDef1}
+\Liouv \op O \equiv \left(\Liouvnot + \coupl \right) \op O = \commutator{\hnot}{\op O} +\commutator{\op V'[\op O]}{\dmnot}  \;,
+\ee
+where $\op V'[\op O] \equiv \int \dd \r \dd \r'\frac{\delta \op V[\dmnot]}{\delta \rho(\r,\r')} O(\r,\r')$.
+
 The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
@@
 As a \emph{stringent} hypothesis, let us now assume that the ket $\ket{s_p^\Phi(\omega)}$ is localized, namely its evaluation can be
-restricted (if suitable) on a bounded real-space domain.
+restricted on a bounded real-space domain.
 %The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
@@
 Let us consider a static perturbing operator $\op\Phi_s$ that can be restricted to a finite domain. 
-Any local operator, like \emph{e.g.} a static electric field $\mathbf F$, with associated scalar potential $\Phi_s(\r) = -\mathbf F \cdot \r$, would satisfy such property.
-We consider the perturbed hamiltonian $\hnot[\dm_{\Phi_s}] + \op\Phi_s$, where $\dm_{\Phi_s}$ represents the GS density of the perturbed system, and assume that the 
+Any local operator, like \emph{e.g.} a static electric field $\mathbf F$, with associated scalar potential $\Phi_s[\mathbf F](\r) = -\mathbf F \cdot \r$, would satisfy such property.
+We consider the perturbed hamiltonian $\hnot[\dm_{\Phi_s}] + \op\Phi_s[\mathbf F]$, where $\dm_{\Phi_s}$ represents the GS density of the perturbed system, and assume that the 
 perturbation strength ($|\mathbf F|$ in the above example) is sufficiently small to be consistent with a LR treatment of the problem. 
@@
 bound-state behavior of $\ket{\psi_p^{\Phi_s}}$. As $\omega=0$ is by hypothesis 
-lower than $|\eps_p|$, this is consistent with the above considerations.
-
+lower than any of the $|\eps_p|$, this is consistent with the above considerations.
+
+Such observations enable us to express quantities like the static polarizability tensor $\alpha_{ij}$ from GS calculations of the perturbed Hamiltonian.
+By expressing the induced dipole $\braket{\delta \op{\mathbf r}}_{\Phi_s}$ in the form Eq.~\eqref{LinearResponseFunctDef1}, and identifying the static response density as $\dm'_{\Phi_s}(0) = \dm_{\Phi_s} -\dmnot $, we have
+\be \label{staticalpha}
+\alpha_{ij} = 
+-\frac{1}{F_j} \left(\trace{\op r_i \dm_{\Phi_s[F_j]}} - d^{\text{(GS)}}_i \right)\;,
+\ee
 % A direct confirmation of the localization character of fluctuation states at $\omega=0$ can be achieved through a ground-state calculation. Indeed, $\ket{f_p(\omega)}$ are nothing but the 
@@
 % spatial extension of the fluctuation states can be directly measured.
+where $\mathbf d^\text{(GS)}$ is the ground state dipole.
 In Fig.~\eqref{co_alphaStatic} illustrate this procedure for a $CO$ molecule 
@@
 \eqref{LinearResponseFunctDef2}. 
-In this case $\ket{f_p^\Phi(\omega)}$ is a unbound, delocalized function; a numerical treatment tailored for localized
-functions will \emph{never} be able to discretise such function with arbitrary accuracy.  
-In this context, the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator:
+Since $\ket{f_p^\Phi(\omega)}$ becomes an unbound, delocalized function, the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator:
 \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
@@
 whereas the effect of the computational setup are clearly visible for values of $\omega$ that exceed the threshold value.
-For these ultraviolet regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
+For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
 which in turn reveal more than sufficient below threshold.
@@
 %that may be local and with a well-defined normalization 
-with a potential local behavior only for $\omega$ below the ionization threshold. So, Comparing fluctuation states among diverse numerical treatments would be a 
+with a potential local behavior only for $\omega$ below the ionization threshold. Hence, comparing fluctuation states among diverse numerical treatments would be a 
 challenging task.
@@
 \begin{align}
- \ket{s_{\phi}} &=  \op Q_0 \op V'[\op E_a] \ket{\psi_p} \\
+ \ket{s_{\phi}} &=  \op Q_0 \op V'[\op E_a] \ket{\psi_p} \nn \\
  \ket{s_{\chi}} &=  \op Q_0 \op V'[\op E^t_a] \ket{\psi_p}\;.
@@
 In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
-the agreement with the expected analytic structure presented in Fig.~\ref{ExcitationLandscape} is impressive.
+the agreement with the expected analytic structure presented in Fig.~\ref{ExcitationLandscape} is remarkable.
 
@@
 \be
-\ket{f_p^\Phi(\omega)} = \ket{f^{\Phi}_p(\omega)}_D + \ket{f^{\Phi}_p(\omega)}_C \lb{FSExcitationDef1} \;,
+\ket{f_p^\Phi(\omega)} = \fscd{D} + \fscd{C}
+\lb{FSExcitationDef1} \;,
 \ee
@@
 \begin{align}
- \ket{f_p^\Phi(\omega)}_D &= \sum_a^{\Omega_a < |\eps_a|} \ket{w_p^a} \frac{\varphi_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \;, \nn \\
- \ket{f_p^\Phi(\omega)}_C &= \int_{\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{\varphi_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \;, \nn
+ \fscd{D} &= \sum_a^{\Omega_a < |\eps_a|} \ket{w_p^a} \frac{\varphi_p^a[\op \Phi(\omega)]}{\omega^2-\Omega_a^2} \;, \nn \\
+ \fscd{C}
+ &= \int_{\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{\varphi_p^a[\op \Phi(\omega)]}{\omega^2-\Omega_a^2} \;, \nn
 \end{align}
-where $\varphi_p^a(\op \Phi,\omega) \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$,
+where $\varphi_p^a[\op \Phi(\omega)] \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$,
 and $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$. 
@@
 or in the integral are genuinely localized and delocalized, respectively.
-For \emph{any} value of $\omega$ the ket $\ket{f_p^\Phi(\omega)}_D$ has, by definition, a bound-state like
+For \emph{any} value of $\omega$ the ket $\fscd{D}$ has, by definition, a bound-state like
 character as it is expressed as a sum of localized contributions.
@@
 $\ket{f_p^\Phi(\omega)}$ to have bound-state like behavior.
-For this to be true, the contribution from the delocalized excited states defining
-$\ket{f_p^\Phi(\omega)}_C$ should resum into a localized, asymptotically vanishing state.
-Indeed, there is no particular reason to believe that $\ket{f_p^\Phi(\omega)}_C$ should be
-zero. The linear independence of the $\ket{w_p^a}$ states would imply that 
-$\varphi_p^a(\op \Phi,\omega)=0$ for any $a$ labelling the continuum excitations,
-which is too strong a condition for a general choice of $\op \Phi$.
+However, there is no particular reason to believe that $\fscd{C}$ should be
+zero. Since $\ket{w_p^a}$ states are linearly independent, 
+$\fscd{C}=0$ would imply
+$\varphi_p^a[\op \Phi(\omega)]=0$ for any $a$ labelling the continuum excitations,
+which is too strong a condition for a general choice of $\op \Phi$
 \footnote{The plot in Fig.~\ref{co_AlphaExc}
 show this evidence even in the simple case when $\op \Phi$ is the dipole operator.}.
+Therefore,  the contribution from the delocalized excited states defining
+$\fscd{C}$ should resum into a localized, asymptotically vanishing state.
 
@@
 continuum sector of the excitations can never be neglected}. 
-We are not referring here to the continuum eigenstates of the 
-unperturbed GS hamiltonian, %which is not in itself important for expressing the linear susceptivity, 
-but to the continuum of excitations expressed as eigenstate of the 
-Liouvillian superoperator of Eq.~\eqref{Liouvillian}, needed to 
-express the spectral representation of the linear susceptibility.
-We \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
+In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
 in the essential part of the Liouvillian spectrum.
@@
 \braket{\delta\op O}^{D,C}_\Phi(\omega) = 
-2 \mathrm{Re}\left(\bra{\psi_p} \op O \ket{f_p^\Phi(\omega)}_{D,C} \right)\;,
-\ee
-And we show how the value of the static polarizability $\alpha_{zz}(\omega=0)$
-defined in Eq.~\eqref{staticpol} will depend on the set of excitations
-included in the integral defining $\ket{f_p^\Phi(\omega)^C}$.
-Such value is compared with the reference result where the 
-localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
-This is the well-know $S_{-2}$ sum-rule, that express the value of the static polarizability
+2 \mathrm{Re}\left(\bra{\psi_p} \op O \fscd{D,C} \right)\;.
+\ee
+The static polarizability tensor $\alpha_{ij}$ can be easily expressed
+from the above quantities as
+\be
+\alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \varphi_p^a[\op r_i]\varphi_p^a[\op r_j]\;.
+\ee
+The above relation shows that the value of $\alpha_{ij}$ explicitly depends on the set of excitations
+included in the integral defining $\fscd{C}$.
++Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
+This is the well-know $S_{-2}$ sum-rule\cite{TDDFTBOOK}, that express the value of the static polarizability
 in terms of the molecule's oscillator strengths.
+
 We see that a considerable number of pseudo-continuum excitations is required
@@
 The situation is not so simple in the above-threshold regime.
-In this case what is important is matrix element of the observable of interest
-between the bound, occupied state and the delocalized fluctuation state.
-To achieve convergence, care should be taken in expressing accurately the FS on the
+In this case what is important is the matrix element of the observable of interest
+between the bound, occupied state and the fluctuation state (FS). 
+The FS is here an unbound, delocalized function, and a numerical treatment tailored for localized functions will \emph{never} be able to discretise such function with arbitrary accuracy.  
+To achieve numerical convergence, care should be taken in expressing accurately the FS on the
 appropriate region of space. In view of reproducibility, computational setups which are able to express precisely
@@
 On the other hand, the excitation energies which lie above these thresholds are only pseudo-poles of $\chi(\omega)$, 
-and will \emph{strongly} depend on the computational setup. This is visible already for energies higher than
-IP, and it has been pointed out several times (see e.g. \ref{giustino}) in the literature.
-However, such part of the excitation spectrum has a prominent role in the
-great majority of LR quantities, \emph{even in the localised regime} of $\omega$.
-In other terms, the set of continuum excitations might only be \emph{effectively} represented
-in a computational approach, depending on the quantities of interest.
-As an example, we have shown that spectral representations of $\chi(\omega)$ tailored for static
-LR quantities are in general unreliable for absorption spectra above IP, whilst provide precise values
-of the excitation energies in the discrete sector.
+and will \emph{strongly} depend on the computational setup. This is visible for energies higher than
+IP, and it has been pointed out several times (see e.g. \cite{giustino2012,giustino2014}) in the literature.
+These excitations belong to a continuum sector that embeds the above mentioned discrete excitations.
+We remark that we are not referring here to the continuum eigenstates of the 
+unperturbed GS hamiltonian, %which is not in itself important for expressing the linear susceptivity, 
+but to the continuum of excitations expressed as eigenstate of the 
+Liouvillian superoperator of Eq.~\eqref{LiouZeroDef1}, needed to 
+express the spectral representation of the linear susceptibility.
+
+Both the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities.
+We can \emph{quantify} the reliability of excitations belonging to the discrete sector, as the corresponding excited states and energies may be discretized with arbitrary accuracy on a localized region.
+For instance, absorption spectra \emph{below IP} are relatively easy to converge, as they are observables which depend only on localized quantities.
+
+We are, on the contrary, forced to provide effective representations for
+the delocalised excitations belonging to the (pseudo-) continuum sector.
+For generic LR quantities, which are functionals of the linear susceptivity, 
+the quality of the $\chi(\omega)$ (super)operator will depend
+on the frequency $\omega$ of interest: a given spectral representation may provide high-quality results for static $\omega=0$ regimes, while being
+unable to provide convergence for high-energy absorption spectra.
+
+% As an illustration, we have presented explicitly examples where the pseudo-contunuum sector is relevant: in the same 
+% We have shown computational setups in which convergence difficulties high-energy absorbption spectra are observed, whereas the $S_{-2}$ sum rule (meaningful in the $\omega=0$ regime) is precisely fulfilled.
+
+% However, this does not necessarily imply that for $\omega$ above thresholds 
+% the same pseudo-continuum expansion can be effectively employed: we have shown spectral representation of $\chi(\omega)$ which presents difficulties in convergence of high-energy absorbption spectra, whereas they provide precise values of the excitation energies in the discrete sector.
+% In other terms, the set of continuum excitations may only be \emph{effectively} represented
+% in a computational approach, depending on the quantities of interest.
 
@@
 The example of the static polarizability of molecules
-present ideal features as an initial playground. Work is ongoing in this direction.
-
-\section{Garbage Collector}
+presents ideal features as an initial playground. Work is ongoing in this direction.
+
+% \section{Garbage Collector}
 
@@
 %Susceptibility written as
-The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
-Liouvillian. Pursuing this procedure provides:
-\be\lb{RhopExcitationDef2}
-\sop{{\cal \chi}}(\omega) \cdot   = \left(\sum_a + \int\dd a   \right) \op W_{a} \,
-\frac{2\trace{\op W_a \cdot}}{\omega^2-\Omega_a^2} \;,
-\ee 
-where we have defined the symmetric operators $\op W_a = \frac{1}{\sqrt{2}}(\ketbra{w_p^a}{\psi_p}+\ketbra{\psi_p}{w_p^a})$ and states $\ket{w_p^a}=\ket{\psi_p^a}+\ket{\chi_p^a}$.
+% The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
+% Liouvillian. Pursuing this procedure provides:
+% \be\lb{RhopExcitationDef2}
+% \sop{{\cal \chi}}(\omega) \cdot   = \left(\sum_a + \int\dd a   \right) \op W_{a} \,
+% \frac{2\trace{\op W_a \cdot}}{\omega^2-\Omega_a^2} \;,
+% \ee 
+% where we have defined the symmetric operators $\op W_a = \frac{1}{\sqrt{2}}(\ketbra{w_p^a}{\psi_p}+\ketbra{\psi_p}{w_p^a})$ and states $\ket{w_p^a}=\ket{\psi_p^a}+\ket{\chi_p^a}$.
 
@@
 
-From the analysis discussed in the previous section it emerges that the general treatment of the LR for open systems \emph{requires} to deal with delocalized
-objects. In facts, either if one choose the fluctuation states' formalism, or the ``sum over excitations'' (SOE) approach, it turns out that the main building blocks
-beyond a specific energetic threshold have an unbound behavior in the long range. 
-On the basis of this consideration is then reasonable to try to understand if a computational setup tailored to deal with the ground state problem is idoneous to provide
-reliable results for the LR.
-
-\vspace{0.3cm}
+% From the analysis discussed in the previous section it emerges that the general treatment of the LR for open systems \emph{requires} to deal with delocalized
+% objects. In facts, either if one choose the fluctuation states' formalism, or the ``sum over excitations'' (SOE) approach, it turns out that the main building blocks
+% beyond a specific energetic threshold have an unbound behavior in the long range. 
+% On the basis of this consideration is then reasonable to try to understand if a computational setup tailored to deal with the ground state problem is idoneous to provide
+% reliable results for the LR.
+
+% \vspace{0.3cm}
 
@@
 % \end{figure}
-
-\section{Criterion of computational reliability for the numerical convergence of the LR}
 
@@
 
-\subsection{Fluctuation state and excitations}
-
-Show the convergence of the statical polarizability of the $CO$ in function of the number of excitations. Write formula
-\be\lb{AlphaExcitationDef1}
-\alpha_{xx} =  \left(\sum_a + \int\dd a   \right) 2 \,
-\frac{\left[\trace{\op W_a \op X}\right]^2}{\Omega_a^2} \;,
-\ee 
-and add the plot that show the convergence rate of the statical polarizability to the reference (finite difference) value in functions of the number of excitations. The plot evidence that the
-continuum sector of the excitation spectrum is
+% \subsection{Fluctuation state and excitations}
+
+% Show the convergence of the statical polarizability of the $CO$ in function of the number of excitations. Write formula
+% \be\lb{AlphaExcitationDef1}
+% \alpha_{xx} =  \left(\sum_a + \int\dd a   \right) 2 \,
+% \frac{\left[\trace{\op W_a \op X}\right]^2}{\Omega_a^2} \;,
+% \ee 
+% and add the plot that show the convergence rate of the statical polarizability to the reference (finite difference) value in functions of the number of excitations. The plot evidence that the
+% continuum sector of the excitation spectrum is
 
@@
 
-\subsection{Comments and conclusions}
-
-The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
-for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
-$\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort...
+% \subsection{Comments and conclusions}
+
+% The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
+% for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
+% $\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort...
 
 \appendix
-\section{Left and right action of the Liouvillian superoperator}\lb{LiouvillianAction}
-
-The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term. The left action of these 
-terms reads, respectively
-\be\lb{LiouZeroDef1}
-\Liouvnot \op O = \commutator{\hnot}{\op O} \;,
-\ee
-and
-\be\lb{CouplDef1}
-\coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;,
-\ee
-where $\op V'$ expresses the perturbation induced by the density dependence on ground state Hamiltonian and can be conveniently expressed by defining the 
+\section{Transverse operators and right action of the Liouvillian superoperator}\lb{LiouvillianAction}
+Given a unperturbed Hamiltonian and density operator, which satisfy $\commutator{\hnot}{\dmnot}=0$, we may decompose a generic operator in two contributions, $\op O=\op O_\parallel + \op O_\perp$, defined as:
+\begin{align}
+\op O_\parallel &\equiv \dmnot \op O \dmnot + \op Q_0 \op O \op Q_0 \nn \;,\\
+\op O_\perp &\equiv \dmnot \op O \op Q_0 + \dmnot \op O \op Q_0 = 
+\commutator{\dmnot}{\commutator{\dmnot}{\op O}} \;,
+\end{align}
+with $\op Q_0 =\identity - \dmnot$.
+The operator $\op O_\parallel$ is constructed to satisfy 
+$\commutator{\dmnot}{\op O_\parallel} = \commutator{\hnot}{\op O_\parallel} =0$.
+Also, it is easy to verify that given two generic $\op O$, $\op O'$, we have
+$\trace{\op O'_\parallel \op O_\perp} =0$.
+
+The projection $\op O_\perp$ is therefore the relevant part for the commutator:
+\begin{equation}
+\commutator{\dmnot}{\op O} = \commutator{\dmnot}{\op O_\perp} =
+\dmnot \op O \op Q_0  - \dmnot \op O \op Q_0 \;.
+\end{equation}
+The Liouvillian superoperator is therefore constructed such as $\Liouv \op O = \Liouv O_\perp$. In addition, the image operator satisfies the transverse condition
+$\left( \Liouv \op O \right)_\parallel =0$.
+% \be\lb{CouplDef1}
+% \coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;,
+% \ee
+
+Here $\op V'$, which expresses the perturbation induced by the density dependence on ground state Hamiltonian, can be conveniently expressed by defining the 
 \emph{scalar coupling kernel}
 \be\lb{CouplingKernelDef1}
-U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \hnot }{\delta \rho_0(\r,\r')}
-} \trace{\op O' \ket{\r} \bra{\r'}} \;, \nn
+U\left[\op O; \op O'\right] \equiv  \int \dd \r \dd \r' \trace{\op O \frac{\delta \op V[\dmnot] }{\delta \rho(\r,\r')}
+} \trace{\op O' \ket{\r} \bra{\r'}}\;, 
 \ee
@@
 \ee
-In view of building the spectral decomposition we are interested in finding both the left and right eigenstates of $\Liouv$.   
-The right action of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O}$, so that:
+We notice here in passing that in general $\op V'[\op O_\perp] \neq \op V'[\op O]$.
+We assume nonetheless that the scalar coupling kernel is symmetric, i.e. $U\left[\op O; \op O'\right] = U\left[\op O'; \op O\right]$, which is a condition generally satisfied in DFT Hamiltonians.
+
+The action from the right of $\Liouv$ can be assessed through the equivalence $\trace{\op O'(\Liouv\op O)} = \trace{(\op O'\Liouv)\op O_\perp}$, which implies that also
+$\left(\op O' \Liouv\right)_\parallel =0$. We obtain:
 \be
 \op O\Liouv = -\commutator{\hnot}{\op O} + \int \dd\r\dd\r'
-U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\ketbra{\r}{\r'} \;. \nn
-\ee
-In the cases relevant for the present analysis the coupling kernel is symmetric with respect to the exchange of its arguments so also the right action of the 
-Liouvillian is expressed in terms of $\op V'$, as follows
+U\left[\commutator{\dmnot}{\op O};\ketbra{\r'}{\r}\right]\left(\ketbra{\r}{\r'}\right)_\perp \;. \nn
+\ee
+With this definition it is explicitly apparent that $\op O\Liouv=\op O_\perp \Liouv$,
+similarly to the left action. The action of the Liouvillian reads
 \begin{align}\lb{LiouvillianRightActionDef1}
-\op O\Liouv &= -\commutator{\hnot}{\op O} + V'\left[\commutator{{\dmnot}}{\op O}\right] = -\commutator{\hnot}{\op O} + \nn \\ 
+\op O\Liouv &= -\commutator{\hnot}{\op O} + \left(V'\left[\commutator{{\dmnot}}{\op O}\right]\right)_\perp = -\commutator{\hnot}{\op O} + \nn \\ 
 &+ \dmnot\op V'\left[\commutator{{\dmnot}}{\op O}\right]\op Q_0 + \op Q_0\op V'\left[\commutator{\dmnot}{\op O}\right]\dmnot \;.
 \end{align}
-In the last equivalence we have made usage of the transverse property (see equation \eqref{RhopTransverseDef1}) of the coupling superoperator. Formula 
-\eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
+In the last equivalence we have made usage of the transverse property (see equation \eqref{RhopTransverseDef1}) of the coupling superoperator. The above formulae
+together with Eq.~\eqref{LiouZeroDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
 
@@
 
-We show that Casida equations are equivalent to the equations of motion for the excited states \eqref{ExcitationOperatorsDef3}. To this scope we introduce an explicit basis $\{\ket{\eta}\}$
+We show that Casida equations are equivalent to the equations of motion for the excited states \eqref{ExcitationOperatorsDef3}. To this aim we introduce an explicit basis $\{\ket{s}\}$
 in the subspace of empty states so that both $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ can be represented as
 \be
-\ket{\phi^a_p} = \sum_\eta X^a_{p\eta}\ket{\eta} \;, \qq
-\bra{\chi^a_p} = \sum_\eta\bra{\eta}Y^a_{p\eta} \;.
-\ee
-Plugging this expansion into equations \eqref{ExcitationOperatorsDef3} and projecting on a arbitrary element $\ket{\rho}$ of the basis provides a linear systems of equations for the coefficients
-$X^a_{p\eta}$ and $Y^a_{p\eta}$, namely
+\ket{\phi^a_p} = \sum_s X^a_{p s}\ket{s} \;, \qq
+\bra{\chi^a_p} = \sum_s\bra{s}Y^a_{p s} \;. \lb{phiandchi}
+\ee
+Plugging this expansion into equations \eqref{ExcitationOperatorsDef3} and projecting on a arbitrary element of the basis provides a linear systems of equations for the coefficients
+$X^a_{ps}$ and $Y^a_{ps}$, namely
 \begin{align}
- \sum_\eta(H_{0\rho\eta}-\eps_p\delta_{\rho\eta})X^a_{p\eta} + \bra{\rho}\op V'[\op E_a]\ket{\psi_p} &= \Omega_a X^a_{p\rho} \;, \nn \\
- -\sum_\eta (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})Y^a_{p\eta} - \bra{\psi_p}\op V'[\op E_a]\ket{\rho}& = \Omega_a Y^a_{p\rho} \;. \nn
+ \sum_{s'}(H_{0ss'}-\eps_p\delta_{ss'})X^a_{ps'} + \bra{s}\op V'[\op E_a]\ket{\psi_p} &= \Omega_a X^a_{ps} \;, \nn \\
+ -\sum_{s'} (H_{0 s' s}-\eps_p\delta_{s s'})Y^a_{ps'} - \bra{\psi_p}\op V'[\op E_a]\ket{s}& = \Omega_a Y^a_{ps} \;. \nn
 \end{align}
-Using this basis, excitation operators are expressed as a linear combination of transition operators $\excite{p}{\eta} \equiv \ketbra{\eta}{\psi_p}$ and $\decay{\eta}{p} \equiv \ketbra{\psi_p}{\eta}$,
+Using this basis, excitation operators are expressed as a linear combination of transition operators $\excite{p}{s} \equiv \ketbra{s}{\psi_p}$ and $\decay{s}{p} \equiv \ketbra{\psi_p}{s}$,
 as follows
 \be\lb{ExcitationOpBasisTransition1}
-\op E_a = \sum_{p\eta}\excite{p}{\eta}X^a_{p\eta}+\decay{\eta}{p}Y^a_{p\eta} \;.
+\op E_a = \sum_{ps}\excite{p}{s}X^a_{ps}+\decay{s}{p}Y^a_{ps} \;.
 \ee
@@
 \begin{align}
-& \bra{\rho}\op V'[\op E_a]\ket{\psi_p} = \sum_{q\eta}\left(U[\decay{\rho}{p};\excite{q}{\eta}]X^a_{q\eta} + U[\decay{\rho}{p};\decay{\eta}{q}]Y^a_{q\eta}\right) \;,\nn \\
-& \bra{\psi_p}\op V'[\op E_a]\ket{\rho} = \sum_{q\eta}\left(U[\excite{p}{\rho};\excite{q}{\eta}]X^a_{q\eta} + U[\excite{p}{\rho};\decay{\eta}{q}]Y^a_{q\eta}\right) \;, \nn
+& \bra{s}\op V'[\op E_a]\ket{\psi_p} = \sum_{qs'}\left(U[\decay{s}{p};\excite{q}{s'}]X^a_{qs'} + U[\decay{s}{p};\decay{s'}{q}]Y^a_{qs'}\right) \;,\nn \\
+& \bra{\psi_p}\op V'[\op E_a]\ket{s} = \sum_{qs'}\left(U[\excite{p}{s};\excite{q}{s'}]X^a_{qs'} + U[\excite{p}{s};\decay{s'}{q}]Y^a_{qs'}\right) \;, \nn
 \end{align}
+Give that we employ real functions both for $p$ and $s$ is real we also have $\excite{p}{s}(\r,\r') = \decay{s}{p}(\r',\r)$ and the density operator is symmetric in $\r \leftrightarrow \r'$.
+These conditions applied together imply that $U[\excite{p}{s};\excite{q}{s'}] = U[\decay{s}{p};\decay{s'}{q}]$, as well as $U[\decay{s}{p};\excite{q}{s'}] = U[\excite{p}{s};\decay{s'}{q}]$,
 and so equations \eqref{ExcitationOperatorsDef3} can be recasted in matrix form
 \be\lb{ExcitationMatrixEq1}
-\sum_{q\eta}\mat{F_{p\rho}^{q\eta} &  D_{p\rho}^{q\eta}  \\
-- E_{p\rho}^{q\eta} & - G_{p\rho}^{q\eta} }
-\mat{X^a_{q\eta} \\ Y^a_{q\eta}} = \Omega_a \mat{X^a_{p\rho} \\ Y^a_{p\rho}}
+\sum_{qs'}\mat{F_{ps}^{qs'} &  D_{ps}^{qs'}  \\
+- D_{ps}^{qs'} & - F_{ps}^{qs'} }
+\mat{X^a_{qs'} \\ Y^a_{qs'}} = \Omega_a \mat{X^a_{ps} \\ Y^a_{ps}}
 \ee
@@
 & F_{p\rho}^{q\eta} = (H_{0\rho\eta}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\decay{\rho}{p};\excite{q}{\eta}] \;,\nn \\
-& D_{p\rho}^{q\eta} = U[\decay{\rho}{p};\decay{\eta}{q}] \;,\nn \\
-& E_{p\rho}^{q\eta} = U[\excite{p}{\rho};\excite{q}{\eta}] \;,\nn \\
-& G_{p\rho}^{q\eta} = (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\excite{p}{\rho};\decay{\eta}{q}] \;. \nn
+& D_{p\rho}^{q\eta} = U[\decay{\rho}{p};\decay{\eta}{q}] \;.
+%& E_{p\rho}^{q\eta} = U[\excite{p}{\rho};\excite{q}{\eta}] \;,\nn \\
+%& G_{p\rho}^{q\eta} = (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\excite{p}{\rho};\decay{\eta}{q}] \;. \nn
 \end{align}
-Finally, exploiting the symmetry properties of both the unperturbed Hamiltonian and of the coupling kernel it follows that $F=G$ and $D=E$ so that equations
-\eqref{ExcitationMatrixEq1} reduce to the usual formulation of the Casida equations in the basis of transitions.
+This is the well-known Casida Equation in the basis of transitions for the excitation of energy $\Omega_a$. The computational reliability of the 
+eigenvalue $\Omega_a$ depends on the capability of the basis set $\ket{s}$ to fulfill of Eq.~\eqref{phiandchi}.
+Note that this may be valid only for a subset of the solutions of the eigenproblem \eqref{ExcitationMatrixEq1}.
 
 \section{Computational details}
+All the calcualtions presented in this paper are performed with the BigDFT code,
+which uses Daub
 

### 2018-07-11 AnalyticStructure_main.tex

@@
 \section{Computational details}
-All the calcualtions presented in this paper are performed with the BigDFT code,
-which uses Daub
+The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{bigdft},
+which employs Daubechies Wavelets as computational basis set.
+Such orthonormal basis present optimal features of in view of reproducibility of the results,
+and it has proven to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
+
+For Ground State results, the important parameters in the context of convergence of the calculations are the spacing of the wavelet grid and the size of the simulation domain: for bound-state like functions, convergence is achieved by reducing the grid spacing and increasing the simulation box size.
+Norm Conserving Pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proven to be able to provide all-electron accuracy for molecular systems.
+
+Our LR calculation are performed with the Casida formalism \cite{bhaarathi}, where it is also important to include a sufficient number of unoccupied states in the transition operators.
+As pointed out in the text such states behave as plane waves: the features of wavelets enable us to represent localized and delocalized states on equal footing.
+For each size of the simulation domain, the number of unoccupied states used for building the Casida' eigenproblem has been increased up to convergence of the presented results.
 
 \subsection{$CO$}
-
-Both GS and LR calculations for the $CO$ molecule are performed in three distinct computational setup that differs for the dimension of the computational
-domain. The molecule is oriented along the $z$ axis and the $z$-dimension of the box is equal to 11.5, 15.1 and 16.6 \AA.
-
-Excitation energies and states are obtained through the explicit diagonalization of the Casida matrix. To this scope we have built a basis in the domain of $\op Q_0$ 
-by calculating the eigenvectors and associated energies of the empty virtual orbitals of $\hnot$. 280 states have been computed in each setup and the corresponding
-energy cutoff in the three simulation box is 30.7, 19.3 and 15.4 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
-
-The DOS reported in figure \ref{CO_exc} are obtained by adding a complex shift of $8\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
-
-\subsection{$C_6H_6$}
-
-Both GS and LR calculations for the $C_6H_6$ molecule are performed in three distinct computational setup that differs for the dimension of the computational
-domain. The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.
-
-Excitation energies and states are obtained through the explicit diagonalization of the Casida matrix. To this scope we have built a basis in the domain of $\op Q_0$ 
-by calculating the eigenvectors and associated energies of the empty virtual orbitals of $\hnot$. 220 states have been computed in each setup and the corresponding
-energy cutoff in the three simulation box is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
+The molecule is oriented along the $z$ axis and the $z$-dimension of the box is equal to 11.5, 15.1 and 16.6 \AA.
+280 unoccupied states have been computed in each setup, which span an energy range of the empty KS orbitals of 30.7, 19.3 and 15.4 eV respectively. 
+Such energy values should not be confused with the excitations energy ranges reported in Figs.~\ref{co_spectrum} and \ref{CO_exc}. 
+Once again, such choices of unoccupied states ensures convergence in of excitations spectum in the presented range.
+
+The DOS reported in figure \ref{CO_exc} are obtained by adding a smearing parameter of $8\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
+
+\subsection{Benzene}
+The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.
+220 states have been computed in each setup and the corresponding
+energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV.
 

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

--- 2018-07-11 AnalyticStructure_main.tex
@@
 \section{Computational details}
-All the calcualtions presented in this paper are performed with the BigDFT code,
-which uses Daub
+The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{bigdft},
+which employs Daubechies Wavelets as computational basis set.
+Such basis present optimal features of in view of reproducibility of the results,
+ans it has proven to represent precisely and explicitly system with Free boundary conditions, without any basis set superposition error nor supercell aliasing.
+For Ground State results, the important parameters in the context of convergence of the calculations are the spacing of the wavelet grid and the size of the simulation domain: for bound-state like functions, convergence is achieved by reducing the grid spacing and increasing the simulation box size.
+Norm Conserving Pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proven to be able to provide all-electron accuracy for molecular systems.
+
+Our LR calculation are performed with the Casida formalism \cite{bhaarathi}, where
 

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

--- 2018-07-11 AnalyticStructure_main.tex
@@
 \subsection{Benzene}
+
 The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.
 220 states have been computed in each setup and the corresponding
-energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV.
+energy reange for the unoccupied statescutoff in the three simulation box is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
 

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

@@
 220 states have been computed in each setup and the corresponding
-energy reange for the unoccupied statescutoff in the three simulation box is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
+energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
 

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

@@
 220 states have been computed in each setup and the corresponding
-energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV (energy cutoff decreases as the box increases due to the collapse of the unbound virtual states).
+energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV.
 

### 2018-07-11 AnalyticStructure_main.tex
Update on Overleaf.

@@
 \author{Luigi Genovese}
-\affiliation{Laboratoire de Simulation Atomistique (LSim), SP2M, INAC, CEA-UJF, 17 Av. des Martyrs,
+\affiliation{Laboratoire de Simulation Atomistique (LSim), INAC, CEA-UGA, 17 Av. des Martyrs,
 38054 Grenoble, France}
@@
 Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the 
-computational reliability of the results. More specifically, a computational result may be considered as reliable for various reasons.
-It might be, for example, in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
+computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
+It may be, for example, in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
 The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
@@
 from which quantities like optical excitations or polarizability tensors
-of a given system might be studied and put in relation with experimental data.
+of a given system may be studied and put in relation with experimental data.
 Here also, a plethora of computational approaches exist, that employ different numerical formalism and
@@
 Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - 
-from others that would \emph{explicitly} depend of the the employed computational treatment. 
+from others that would \emph{explicitly} depend of the employed computational treatment. 
 In particular, we will discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
@@
 We support our considerations with numerical results on simple LR-TDDFT quantities.
-For readability purposes, the details of each calculation are explained in the appendix.
+For readability purposes, the details of each calculation are explained in the Appendix.
 
 Although we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
-approaches, in the context Quasi-Particle equations.
+approaches, in the context of Quasi-Particle equations.
 
@@
 On the other hand, positive energy solutions behave differently. 
-Even though the potential is localized, their positive energy makes them behave 
-as spherical waves and its convolution with the source term  gives raise to a delocalized wavefunction $\psi(\r)$ 
-in the whole accessible space.
+Even though the potential is localized, their positive energy are 
+ spherical waves and the convolution with the source term provides a delocalized wavefunction $\psi(\r)$ in the whole space.
 As they cannot be normalized they belong to the essential spectrum of the Hamiltonian operator and form a \emph{continuum} of states.
-Thanks to the Lippmann-Schwinger relation of Eq.~\eqref{SEHelmholtz1} they can be put in bijection with the eigenstates of the 
-free-particle Hamiltonian $\op H_s$. We may say that their quantum numbers are determined by the Laplacian operator, 
+Outside of the support of the $\ket{\op V \psi}$ the solutions of Eq.~\eqref{SEHelmholtz1} can be put in bijection with the eigenstates of the 
+free-particle Hamiltonian $\op H_s$. For positive energies, the quantum numbers of the eigenstates are determined by the Laplacian operator, 
 regardless of the particular features of the potential.
@@
 It is easy to see from these concepts that a computational treatment that is tailored for the discretization of bound states
-will not be effective for continuum states, due to the different long-range asymptotic behavior - which in turn is a clear consequence of the 
-BC of the problem. In a numerical treatment, discretizing the problem with a \emph{finite}
+will not be as effective for continuum states, due to the different long-range asymptotic behavior - which in turn is a clear consequence of the 
+BC of the problem. In a numerical treatment, where we discretize the problem with a \emph{finite}
 number of degrees of freedom, we will only have access to a \emph{pseudo}-continuum of states,
 whose energy values and density of states will depend on the representation of the kinetic operator
-in the basis set. As a consequence, numerical eigenstates with $\epsilon > 0$ will have a value of their energy that will \emph{always}
-depend on the computational setup.
-
-A direct numerical evidence of this problem has been discussed in \cite{boffi2016}. The authors of this paper analyze the effects of a finite basis set on the 
+in the basis set. As a consequence, the set of eigenstates with $\epsilon > 0$ expressed in a given computational setup depends on the features of the employed basis set.
+
+A direct numerical evidence of this problem has been discussed in \cite{boffi2016}, where the authors analyze the effects of a finite basis set on the 
 occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, 
@@
 % true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
-On the contrary, it is clearly shown that the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.
+Furthermore, it is clearly shown that the energies of the unbound orbitals are not stable with respect to parameters like the size of the computational domain.
 
 \section{Fluctuation states. A localization argument for the response density}
-It is evident that the arguments presented in the above section have a limited interest for the study
+It is evident that the arguments presented above have a limited interest for the study
 of Ground State quantities of molecules. By definition, all these quantities can be expressed as a 
@@
 \be\lb{LiouvillianRhopomegaDef1}
-\left(\omega - \Liouv\right) \dm'_\Phi(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;,
-\ee
-where $\op\Phi(\omega)$ represents the perturbing field. 
+\left(\omega - \Liouv\right) \dm'_\Phi(\omega) =  \commutator{\op\Phi(\omega)}{\dmnot} \;.
+\ee
 The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term. The action of these 
@@
 \ee
-where $\op V'[\op O] \equiv \int \dd \r \dd \r'\frac{\delta \op V[\dmnot]}{\delta \rho(\r,\r')} O(\r,\r')$.
-
+where $\op V'[\op O] \equiv \int \dd \r \dd \r'\frac{\delta \op V[\dmnot]}{\delta \rho(\r,\r')} O(\r,\r')$ encodes the response of the $\dm$-dependent potential to a modification of the density operator.
 The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
-operator, linking the occupied and empty subspaces of $\hnot$, and satisfies the \emph{transverse} condition  
+operator, linking the occupied and empty subspaces of $\hnot$.
+An operator $\op O_\perp$ with this feature satisfy the \emph{transverse} condition  
 \be\lb{RhopTransverseDef1}
-\dm'_\Phi = \dm_{\perp} \doteq \dmnot\dm'_\Phi\op Q_0 + \op Q_0\dm'_\Phi\dmnot \;,
+\op O_\perp \equiv 
+\dmnot\op O \op Q_0 + \op Q_0 \op O\dmnot \;,
 \ee
 where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. 
-Due to this fact we can introduce an explicit representation of the 
+Thus the condition $\dm'_\Phi = \dm_{\perp}$ holds.
+
+We can therefore introduce an explicit representation of the 
 response density parametrized as
@@
 $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$. 
-An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states are 
+An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states (FS) are 
 written as a modified Sternheimer equation~\cite{mahan1980,giustino2012,giustino2014}
@@
 \ee
-with%:here in this case the source term contains further addend apart from the unperturbed potential and reads:
-$%\be
+with the state%:here in this case the source term contains further addend apart from the unperturbed potential and reads:
+$
 \ket{s_p^\Phi(\omega)} = \op Q_0(\op V'[\dm'_\Phi](\omega) + \op \Phi(\omega))\ket{\psi_p} 
-$. %\ee
+$ as a source term.
 
 It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
-that govern the localization properties of the corresponding fluctuation state.
-As a \emph{stringent} hypothesis, let us now assume that the ket $\ket{s_p^\Phi(\omega)}$ is localized, namely its evaluation can be
+that governs the localization properties of the FS.
+As a \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is localized, \textit{i.e.} its evaluation can be
 restricted on a bounded real-space domain.
@@
 In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian can be extracted with traditional GS techniques, 
-as from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
-is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
-solution exists, this cannot be found for energies above threshold.}
+as from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.
+%\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
+% is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
+% solution exists, this cannot be found for energies above threshold.}
 \begin{figure}[t]
 \includegraphics[scale=0.68]{CO_statPolvsBox.eps}
-\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability (blue continuous line) and of the ground state permanent dipole (red dotted line) 
-of the $CO$ molecule with respect to the size of the computational domain. The inset plot evidences the relative percentage convergence using the value associated to the largest 
-box as reference.}
+\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ (blue continuous line) and of the ground state dipole $d_z$ (red dotted line) 
+of $CO$ molecule as a function of the size of the computational domain.
+The inset evidences the relative convergence (in percent) of the two quantities w.r.t.
+the corresponding value associated to the largest
+box.}
 \end{figure}
 
-From the linearized Schr\"odinger Equation of the perturbed problem, it is easy to see that the fluctuation state at $\omega=0$ can be expressed
+From the linearized Schr\"odinger Equation of the perturbed problem, it is easy to see that the FS at $\omega=0$ can be expressed
 in terms of the corresponding bound state of the perturbed Hamiltonian, i.e.
@@
 
-Such observations enable us to express quantities like the static polarizability tensor $\alpha_{ij}$ from GS calculations of the perturbed Hamiltonian.
+Thanks to such observations one can express quantities like the static polarizability tensor $\alpha_{ij}$ (see e.g.\cite{DebElecField}) from GS calculations of the perturbed Hamiltonian.
 By expressing the induced dipole $\braket{\delta \op{\mathbf r}}_{\Phi_s}$ in the form Eq.~\eqref{LinearResponseFunctDef1}, and identifying the static response density as $\dm'_{\Phi_s}(0) = \dm_{\Phi_s} -\dmnot $, we have
@@
 where $\mathbf d^\text{(GS)}$ is the ground state dipole.
-In Fig.~\eqref{co_alphaStatic} illustrate this procedure for a $CO$ molecule 
+Fig.~\eqref{co_alphaStatic} illustrates this procedure for a $CO$ molecule 
 perturbed by a static electric field. The local character of the fluctuation states at $\omega=0$ is 
@@
 one of the static dipole of the molecule computed at zero external field. 
-The plots evidence that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to the ones of the unperturbed KS orbitals.
+The results evidence that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to the ones of the unperturbed KS orbitals, which is a direct proof of the bound-state behaviour of the FS.
 
@@
 while they behave as unbound states for values of $\omega$ above the threshold levels.
-
-This fact has interesting implication in the evaluation of LR quantities. Indeed, writing the response 
-density in terms of fluctuation states implies that 
+This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response 
+density in terms of FS implies that 
 \be\lb{LinearResponseFunctDef2}
@@
 %so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}.
-Let us suppose that also the observable of interest $\op O$ exhibit the locality properties of the potentials $ \op V$, $\op \Phi$, $\op V'$.
+Let us suppose that also the observable of interest $\op O$ exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.
 Once again, it would be enough to consider a local operator for this condition to be met.
+
 We observe that there exists two 
@@
 $\omega$ is lower than the ionization potential $|\eps_h|$.
-In this case all the fluctuation states are below their threshold level and equation \eqref{LinearResponseFunctDef2} 
+In this case all the FS are below their threshold level and equation \eqref{LinearResponseFunctDef2} 
 is expressed in terms of genuinely localized 
-quantities. The quantities $\braket{\psi_p \op O| f_p^\Phi(\omega)}$, 
-being scalar products of bound-state-like objects, may thus be evaluated with computational setups that
+quantities. At these frequencies, the linear response functional $\braket{\delta\op O}_\Phi(\omega)$
+%The quantities $\braket{\psi_p \op O| f_p^\Phi(\omega)}$, 
+%being scalar products of bound-state-like objects, 
+may thus be evaluated with computational setups that
 are similar to the ones usually employed for GS calculations.
-This consideration proves why, when a given computer code employs established GS numerical techniques, 
-\emph{it is much easier to converge LR quantities for $\omega$ below IP}.
-The convergence in this regime is ``strong'', in the sense that the basis functions employed enable to express 
+The convergence in this regime is ``strong'', in the sense that the basis functions employed enables us to express 
 with arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
@@
 On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation 
-states start behaving as unbound wave functions. In this case a computational description of fluctuation states is only meaningful in ``weak'' sense,
-\emph{i.e.} inside the scalar products of 
-\eqref{LinearResponseFunctDef2}. 
-Since $\ket{f_p^\Phi(\omega)}$ becomes an unbound, delocalized function, the bound state character of $\{\bra{\psi_p}\op O\}$ behave as a regulator:
-\emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
-This observation indicates that, above threshold, a computational setup 
+states start behaving as unbound wave functions.
+As by hypothesis $\ket{\op O \psi_p}$ is bound-state like, \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
+In this case a computational description of fluctuation states is only meaningful in ``weak'' sense,
+%\emph{i.e.} inside the scalar products of 
+%\eqref{LinearResponseFunctDef2}. 
+%since $\ket{f_p^\Phi(\omega)}$ becomes an unbound, delocalized function, 
+where the bound state character of $\{\bra{\psi_p}\op O\}$ behaves as a regulator.
+
+These considerations prove why, when a given computer code employs established GS numerical techniques, 
+\emph{it is much easier to converge LR quantities for $\omega$ below IP}.
+Above the IP threshold, a computational setup 
 provides a reliable assessment of \eqref{LinearResponseFunctDef2} only if it is able (even implicitly) to express an
@@
 of this convergence difficulties, especially for high frequencies.
-
-As an explicit example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in 
+The IP threshold has an evident physical interpretation: for energies in a range higher than the ionization potential,
+localized and delocalized states might be coupled by the perturbation. Obtaining convergence of the observable quantities at these energies is therefore much more challenging if one employs 
+numerical techniques which were originally tailored for GS calculations.
+
+As an example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in 
 three distinct real-space computational setups, which differs for the dimension of 
-the computational domain. Results reported in figure \ref{co_spectrum} evidences that the curves are almost coincident in the below threshold regime,
+the computational domain. 
+Results reported in figure \ref{co_spectrum} evidences a typical behavior: the curves are almost coincident in the below threshold regime,
 whereas the effect of the computational setup are clearly visible for values of $\omega$ that exceed the threshold value.
 For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
-which in turn reveal more than sufficient below threshold.
+which are -- as already noticed -- more than sufficient below threshold.
 
@@
 \includegraphics[scale=0.6]{CO_spectrum.eps}
-\caption{\label{co_spectrum}(Color online) Convergence below threshold of the $CO$ spectrum computed in different computational setup.}
+\caption{\label{co_spectrum}(Color online) Illustrative LR absorption spectra of the $CO$ molecule in computational setups with different sizes of the simulation domain.
+The value of the IP threshold is indicated by a vertical dashed line.}
 \end{figure}
-
-Such concept of threshold has an evident physical interpretation: for energies in a range higher than the ionization potential,
-localized and delocalized states might be coupled by the perturbation. Obtaining convergence of the observable quantities at these energies is therefore much more challenging if one employs 
-numerical techniques which were originally tailored for GS calculations.
 
@@
 \subsection{The analytic structure of linear susceptibility}
-Being themselves transverse operators, without loss of generality we can parametrize excitations by employing  
-the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
-$\ket{\psi_p}$ and satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
-\be\lb{ExcitedStateOrthNormDef1}
-\sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
-\ee
-In this way we can parametrize the excitation operators of the system as:
+Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
+entirely defined in the unoccupied subspace. 
+In this way we can parametrize, without loss of generality, the excitation operators of the system as:
 \begin{align}\lb{ExcitationOperatorsDef2}
@@
 \end{align}
-Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can then be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
-entirely defined in the unoccupied subspace. For each choice of $p,a$, these objects represent, respectively, the state in which the occupied state $\ket{\psi_p}$
-is excited -- or from whom it decays -- when the system is subject to the perturbation $\Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
+For each choice of $p,a$, these objects represent, respectively, the state in which $\ket{\psi_p}$
+is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
 We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
@@
 of the excitation.
-
+% Being themselves transverse operators, without loss of generality we can parametrize excitations by employing  
+% the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
+% $\ket{\psi_p}$ 
+Excited states  satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
+\be\lb{ExcitedStateOrthNormDef1}
+\sum_p \left(\brket{\phi_p^a}{\phi_p^b} - \brket{\chi_p^b}{\chi_p^a}\right) = \delta_{ab} \;. 
+\ee
 % We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties 
@@
 % operators, 
-By applying the equations \eqref{ExcitationOperatorsDef1} to the above parametrization
+By applying \eqref{ExcitationOperatorsDef1} to the above parametrization
 of the excitations, we obtain the following Sternheimer-like equations for the excited states:
@@
 &\left[\Omega_a-(\hnot - \eps_p)\right] \ket{\phi_p^a} = \op Q_0 \op V'[\op E_a] \ket{\psi_p} \;, \nn\\
-&\left[-\Omega_a-(\hnot - \eps_p)\right]\ket{\chi_p^a} = \op Q_0\op V'[\op E^t_a]\ket{\psi_p}  \;.
+&\bra{\chi_p^a}\left[-\Omega_a-(\hnot - \eps_p)\right] = \bra{\psi_p} \op V'[\op E_a] \op Q_0  \;.
 \end{align}
@@
 associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).
-The excitation spectrum is symmetric w.r.t the inversion of the eigenvalues 
+The spectrum is symmetric w.r.t the inversion of the eigenvalues 
 $\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transpose pair $\{\chi^a_p,\phi^a_p\}$.
@@
 \begin{align}
-\ket{\phi^a_p} &= \op G_H(\Omega_a+\eps_p)\left(\op V \ket{\phi^a_p} + \ket{s_{\phi}} \right) \;, \nn \\
-\ket{\chi^a_p} &= \op G_H(-\Omega_a+\eps_p)\left( \op V \ket{\chi^a_p} + \ket{s_{\chi}} \right)\;,
+\ket{\phi^a_p} &= \op G_H(\Omega_a+\eps_p)\left(\op V \ket{\phi^a_p} + \ket{s_p[\op E_a]} \right) \;, \nn \\
+\bra {\chi^a_p} &=\left(\bra{\chi^a_p} \op V  + \bra{s_p[\op E_a]}\right)  \op G_H(-\Omega_a+\eps_p)\;,
 \end{align}
-where the source terms $s_\phi$ and $s_{\chi}$ are defined as:
-\begin{align}
- \ket{s_{\phi}} &=  \op Q_0 \op V'[\op E_a] \ket{\psi_p} \nn \\
- \ket{s_{\chi}} &=  \op Q_0 \op V'[\op E^t_a] \ket{\psi_p}\;.
-\end{align}
+where the source terms are here defined as:
+\be
+ \ket{s_p[\op O]} =  \op Q_0 \op V'[\op O] \ket{\psi_p}\,, \quad
+ \bra{s_p[\op O]} =   \bra{\psi_p} \op V'[\op O] \op Q_0 \nn \;.
+\ee
 We first point out that the Helmholtz kernel associated to the $\ket{\chi^a_p}$ state 
@@
 The asymptotic long-range behaviour of $\ket{\chi^a_p}$ thus depends only on the locality properties of 
-$\ket{s_{\chi}}$, which in turn is related to the behaviour of the operator $\op V'[\op E^t_a]$.
+$\bra{s_p[\op E_a]}$, which in turn is related to the behavior of the operator $\op V'[\op E_a]$.
 % As in the previous section, we assume the hypothesis that such operator is such that
@@
 This means that, if an excitation operator $\op E_a$ has an energy such that
-$\Omega_a>|\eps_p|$  for \emph{at least one} of the $p \in a$ defining the excitation,
-such operator cannot be parametrized by employing localized states only.
+$\Omega_a>|\eps_p|$  for at least one of the $p \in a$ defining the excitation,
+such operator \emph{cannot} be parametrized by employing localized states only.
 
@@
 \emph{only} when its energy is lower than \emph{all} the ionization potentials of the occupied states participating to the excitation,
-namely if $\Omega_a<|\eps_p|$ $\forall p \in a$. This will only be true if the operators
-$\op V'[\op E^t_a]$ and $\op V'[\op E_a]$ can be restricted to localized wavefunctions.
+namely if $\Omega_a<|\eps_p|$ $\forall p \in a$. This will only be true if the operator
+$\op V'[\op E_a]$ can be restricted to localized kets and bras.
 If any of these hypothesis does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
@@
 For delocalized states, as in the case of the continuum states of $\hnot$,
-such a condition has to be interpreted in disctributional sense and does not lead to quantization of $\Omega_a$.
+such a condition has to be interpreted in distributional sense and does not lead to quantization of $\Omega_a$.
 Thus we can conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute 
@@
 \end{tikzpicture}
-\caption{\label{ExcitationLandscape} Excitation landscape. Excitation are split in horizontal line according to the threshold levels $p_m$. Filled bullet refers to localized
-excitations whereas the tick black lines describe delocalized excitation with a continuum spectrum.}
+\caption{\label{ExcitationLandscape} Excitation landscape. Excitations are split in horizontal line according to the threshold levels $p$. Filled bullets refer to localized
+excitations whereas the thick black lines describe delocalized ones belonging a continuum spectrum.}
 \end{figure}
@@
 it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states. 
-
-Following these observations, the typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable 
+The typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable 
 behavior of the perturbed potential $\op V'$.
@@
 absolute value of the deepest occupied orbital, other discrete excitations may exist, and are embedded in a continuum of delocalized excitations. 
-Lastly, for energies higher than $|\eps_1|$ \emph{no localized} excitations are anymore possible,
-regardless of the particular behavior of $\op V'$ so the excitations landscape in this region is composed only by continuum energies.
+For energies higher than $|\eps_1|$ \emph{no localized} excitations are anymore possible,
+regardless of the particular behavior of $\op V'$: the excitation landscape in this region only contains continuum states.
 
@@
 represent the states $\{\phi_p^a,\chi_p^a\}$, the energy $\Omega_a$ 
-should not depend from the computational setup used for their representation.
-
-Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
-These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+converges to its reference value.
+
+The second sector contains a continuum spectrum of delocalized excitations. The associated states $\ket{\phi_p^a}$ behave as the unbound virtual orbitals analyzed in \cite{boffi2016} 
 and are deeply affected by the computational setup used to represent them.
@@
 Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as
-a representation of the density of states of the Liouvillian superoperator.
+a representation of the density of states (DOS) of the Liouvillian superoperator.
 
@@
 \includegraphics[scale=0.6]{CO_dos.eps}
-\caption{(Color online) Excitation spectrum of $CO$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
+\caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$.
+The two curves correspond to two computational domain of different sizes.
+The inset contains the sole contribution of localized excitations.
+The first IP threshold is depicted as the vertical dashed line.}
 \label{CO_exc}
@@
 \centering
-\subfloat[aaaa]
+\subfloat[Excitation landscape]
 {\label{c6h6_excLand}
@@
 \centering
-\subfloat[bbbbb]
+\subfloat[DOS of Excitation energies]
 {\label{C6H6_exc}
 \includegraphics[scale=0.58]{C6H6_dos.eps}}
-\caption{(Color online) Excitation landscape and DOS of $C_6H_6$.}
+\caption{(Color online) Benzene molecule.
+(a): Excitation Landscape: the excitations have been separated in discrete and continuum sector following the criteria of Sec.~\ref{ExcitationLandscape}.
+(b): DOS of excitation energies $\Omega_a$.
+The first IP threshold is depicted as the vertical dashed line.}
 \end{figure}
 
-In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the Density of States of the Liouvillian for the $CO$  and Benzene molecules, 
-for two different numerical setups of increasing simulation domains. 
+In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the DOS of the Liouvillian for the $CO$  and Benzene molecules, 
+for two different numerical setups of increasing size of the simulation domain. 
 The figures show clearly that all the excitations of energy $\Omega_a$ lying below the 
@@
 In addition, for the benzene molecule it is also possible to 
-identify excitations of energy above IP that still possess a localized behaviour: these excitations satisfy the
-condition $\Omega_a < |\eps_a|$ presented in the above section.
+identify excitations of energy above IP that still possess a localized behaviour, fulfilling the condition $\Omega_a < |\eps_a|$.
 In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
@@
 Such objects are LR quantities, associated to the molecule, whose numerical convergence
-can be found by employing techniques which are very similar to 
-the one adopted for GS calculations. Being expressed by localized excited states,
+can be found by employing techniques which can be mutuated from the ones adopted for GS calculations. Being expressed by localized excited states,
 computational setups with sufficient level of completeness are able to
@@
 
-It is interesting to obtain information on whether such localized excitations
-will be sufficient to express LR quantities that are associated to localized
-fluctuation states.
-By recalling that $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$,
-considering Eq.~\eqref{SusceptibilityDef1} and
+We have also seen in Sec.~\ref{FluctuationState} that
+there exist a sector where the fluctuation states are genuinely localized, thereby presenting reproducibility features. Therefore, 
+knowing that $\ket{f_p^\Phi(\omega)} =\sop \chi(\omega) \op \Phi(\omega) \ket{\psi_p}$, % \dm'_\Phi(\omega)
+it would be interesting to obtain information on whether the discrete, localized sector of the excitations which appear in the spectral decomposition of $\sop \chi(\omega)$
+will be sufficient to express a localized FS.
+Considering Eq.~\eqref{SusceptibilityDef1} and
 expressing the spectral decomposition of the linear susceptibility we find:
@@
 and $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
+
 In the above equation we have explicitly separated the contributions of the discrete ($D$) and continuous ($C$) excitations 
@@
 character as it is expressed as a sum of localized contributions.
-
-We have seen in Sec.~\ref{FluctuationState} that 
-for values of $\omega$ below the first ionization potential we expect
-$\ket{f_p^\Phi(\omega)}$ to have bound-state like behavior.
-However, there is no particular reason to believe that $\fscd{C}$ should be
+For $\omega <$ IP, the equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that the integral defining
+$\fscd{C}$ should resum into a localized, asymptotically vanishing state\footnote{There is no particular reason to believe that $\fscd{C}$ should be
 zero. Since $\ket{w_p^a}$ states are linearly independent, 
@@
 $\varphi_p^a[\op \Phi(\omega)]=0$ for any $a$ labelling the continuum excitations,
-which is too strong a condition for a general choice of $\op \Phi$
-\footnote{The plot in Fig.~\ref{co_AlphaExc}
-show this evidence even in the simple case when $\op \Phi$ is the dipole operator.}.
-Therefore,  the contribution from the delocalized excited states defining
-$\fscd{C}$ should resum into a localized, asymptotically vanishing state.
-
-This means that, contrary to GS, \emph{for LR calculation,
-even when the response density is localized, the contribution coming from the 
-continuum sector of the excitations can never be neglected}. 
-In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
-in the essential part of the Liouvillian spectrum.
-
-\begin{figure}
-\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
-\end{figure}
-We show an evidence of the above statement in Fig.~\ref{co_AlphaExc}. Indeed,
-we may decompose the linear response functional of Eq.~\eqref{LinearResponseFunctDef1}
+which is too strong a condition for a general choice of $\op \Phi$.}.
+
+We may then decompose the linear response functional of Eq.~\eqref{LinearResponseFunctDef1}
 for any operator $\op O$ as $\braket{\delta\op O}_\Phi=\braket{\delta\op O}^D_\Phi +
@@
 \ee
-The static polarizability tensor $\alpha_{ij}$ can be easily expressed
+For instance, the static polarizability tensor $\alpha_{ij}$ can be easily expressed
 from the above quantities as
@@
 \ee
-The above relation shows that the value of $\alpha_{ij}$ explicitly depends on the set of excitations
-included in the integral defining $\fscd{C}$.
-+Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
+Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
 This is the well-know $S_{-2}$ sum-rule\cite{TDDFTBOOK}, that express the value of the static polarizability
@@
 
-We see that a considerable number of pseudo-continuum excitations is required
+In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison in the case of the $CO$ molecule.
+We notice that a considerable number of pseudo-continuum excitations is required
 to find the correct result; the sector of the discrete excitations, even though 
 parametrised by localized, observable (in the sense of reproducible) excited states,
-appears to be largely insufficient to express the reference fluctuation state.
-This seems to be independent on the number of atoms of the molecule, as the range in $\omega$ needed to 
+appears to be largely insufficient to express the reference fluctuation state. Its contribution is even negligible w.r.t.
+the one coming from the continuum sector.
+
+% The inclusion of core electrons in the calculation would have added a further set of localized
+% excitations, but at much higher energies than the one needed for this test.
+
+\begin{figure}
+\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
+\end{figure}
+Hence, contrary to GS, \emph{for LR calculation,
+even when the response density is localized, the contribution coming from the 
+continuum sector of the excitations can never be neglected}. 
+In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
+in the essential part of the Liouvillian spectrum.
+This fact shows that it is \emph{impossible} to restrict the spectral representation
+of $\chi(\omega)$ only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
+
+Such considerations are independent on the number of atoms of the molecule, as the range in $\omega$ needed to 
 achieve satisfactory agreement is largely above the last valence ionization threshold, which is
-a intensive (i.e. independent on the number of atoms) quantity.
-The inclusion of core electrons in the calculation would have added a further set of localized
-excitations, but at much higher energies than the one needed for this test.
-
-This fact shows that it is \emph{impossible} to restrict the spectral representation
-of $\chi(\omega)$ only localized and discrete excitations, even for representing LR results in the $\omega=0$ limit.
-In addition, we can see that the above sum-rule \emph{cannot} be used to assess
+a intensive quantity.
+In addition, we can see that the $S_{-2}$ sum-rule \emph{cannot} be used to assess
 the correctness of $\chi(\omega)$ for values of $\omega$ above IP; it is enough to recall
@@
 Their energies are \emph{true} poles of the linear susceptibility, the excited states being their residues.
+We can \emph{quantify} the reliability of such discrete energies, as the corresponding excited states may be discretized with arbitrary accuracy on a localized region.
 
@@
 
-Both the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities.
-We can \emph{quantify} the reliability of excitations belonging to the discrete sector, as the corresponding excited states and energies may be discretized with arbitrary accuracy on a localized region.
-For instance, absorption spectra \emph{below IP} are relatively easy to converge, as they are observables which depend only on localized quantities.
-
-We are, on the contrary, forced to provide effective representations for
-the delocalised excitations belonging to the (pseudo-) continuum sector.
+Both the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this \emph{even below} the first IP.
 For generic LR quantities, which are functionals of the linear susceptivity, 
@@
 unable to provide convergence for high-energy absorption spectra.
+On the contrary, absorption spectra below IP are relatively easy to converge, as they are observables which depend only on localized quantities.
+
+% We are, on the contrary, forced to provide effective representations for
+% the delocalised excitations belonging to the (pseudo-) continuum sector.
 
@@
 which employs Daubechies Wavelets as computational basis set.
-Such orthonormal basis present optimal features of in view of reproducibility of the results,
+Such orthonormal basis presents optimal features of in view of reproducibility of the results,
 and it has proven to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
@@
 \subsection{Benzene}
-
 The molecule is oriented in the $xy$ plain and the $x$-dimension of the box is equal to 15.0, 18.2 and 19.7 \AA.

### 2018-07-12 AnalyticStructure_main.tex
update

@@
 
-%\title{On the analytic structure of the linear response susceptibility in open systems}
 \title{Locality and Computational Reliability of Linear Response Calculations for Molecular Systems}% Localization properties, observable character and computational reliability of the linear response in open systems}
@@
 the application of a perturbing field.
-Then we will consider the behaviour of the ``free oscillations'', i.e. the excited states
+Then we will consider the behavior of the ``free oscillations'', i.e. the excited states
 of the molecule.
@@
 Any local operator, like \emph{e.g.} a static electric field $\mathbf F$, with associated scalar potential $\Phi_s[\mathbf F](\r) = -\mathbf F \cdot \r$, would satisfy such property.
-We consider the perturbed hamiltonian $\hnot[\dm_{\Phi_s}] + \op\Phi_s[\mathbf F]$, where $\dm_{\Phi_s}$ represents the GS density of the perturbed system, and assume that the 
+We consider the perturbed Hamiltonian $\hnot[\dm_{\Phi_s}] + \op\Phi_s[\mathbf F]$, where $\dm_{\Phi_s}$ represents the GS density of the perturbed system, and assume that the 
 perturbation strength ($|\mathbf F|$ in the above example) is sufficiently small to be consistent with a LR treatment of the problem. 
-In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed hamiltonian can be extracted with traditional GS techniques, 
+In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed Hamiltonian can be extracted with traditional GS techniques, 
 as from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.
@@
 The susceptibility (super)operator $\cal \chi(\omega)$ is therefore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined 
-from the molecule hamiltonian $\hnot[\dm]$.
+from the molecule Hamiltonian $\hnot[\dm]$.
 The ``excitation modes''  of the molecule are defined through the \emph{excitation operators}, satisfying
@@
 contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.
-The asymptotic long-range behaviour of $\ket{\chi^a_p}$ thus depends only on the locality properties of 
+The asymptotic long-range behavior of $\ket{\chi^a_p}$ thus depends only on the locality properties of 
 $\bra{s_p[\op E_a]}$, which in turn is related to the behavior of the operator $\op V'[\op E_a]$.
@@
 
-On the other hand, the long-range behaviour of $\op G_H(\Omega_a+\eps_p)$ depends from 
+On the other hand, the long-range behavior of $\op G_H(\Omega_a+\eps_p)$ depends from 
 $\Omega_a$, with a threshold of value $\Omega_a=|\eps_p|$. 
-For energies above this value, the behaviour of the state $\ket{\phi^a_p}$ is 
+For energies above this value, the behavior of the state $\ket{\phi^a_p}$ is 
 delocalized regardless of the particular nature of the operators $\op V$ and $\op V'$.
@@
 The figures show clearly that all the excitations of energy $\Omega_a$ lying below the 
-molecule ionization potential (IP) have a clear localized behaviour, as their energy does not vary with the size of the simulation domain.
+molecule ionization potential (IP) have a clear localized behavior, as their energy does not vary with the size of the simulation domain.
 On the other hand, above the first ionization threshold the excitation energies have an energy that strongly depends on the computational
@@
 In addition, for the benzene molecule it is also possible to 
-identify excitations of energy above IP that still possess a localized behaviour, fulfilling the condition $\Omega_a < |\eps_a|$.
+identify excitations of energy above IP that still possess a localized behavior, fulfilling the condition $\Omega_a < |\eps_a|$.
 In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
@@
 We remark that we are not referring here to the continuum eigenstates of the 
-unperturbed GS hamiltonian, %which is not in itself important for expressing the linear susceptivity, 
+unperturbed GS Hamiltonian, %which is not in itself important for expressing the linear susceptivity, 
 but to the continuum of excitations expressed as eigenstate of the 
@@
 Both the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this \emph{even below} the first IP.
-For generic LR quantities, which are functionals of the linear susceptivity, 
+For generic LR quantities, which are functionals of the linear susceptibility, 
 the quality of the $\chi(\omega)$ (super)operator will depend
@@
 Such energy values should not be confused with the excitations energy ranges reported in Figs.~\ref{co_spectrum} and \ref{CO_exc}. 
-Once again, such choices of unoccupied states ensures convergence in of excitations spectum in the presented range.
+Once again, such choices of unoccupied states ensures convergence in of excitations spectrum in the presented range.
 

### 2018-07-12 AnalyticStructure_main.tex
update

@@
 
-\title{Locality and Computational Reliability of Linear Response Calculations for Molecular Systems}% Localization properties, observable character and computational reliability of the linear response in open systems}
-\author{Marco D'Alessandro}%
+\title{Locality and Computational Reliability of Linear Response Calculations for Molecular Systems}
+\author{Marco D'Alessandro}
 \affiliation{Istituto di Struttura della Materia-CNR (ISM-CNR), Via del Fosso del Cavaliere 100, 00133 Roma, Italia}
@@
 approximations on the scientific outcomes of the simulation.
-
-% ---
-% We discuss these aspects in the context of linear response treatment of molecular systems. 
-% By analysing simple case-studies with a highly complete numerical formalism, 
-% we explore the interplay between locality of the perturbed wavefunctions and 
-% numerical convergence of observable quantities.
-This will enable us to draw some considerations on the analytic structure of the linear susceptivity for open systems and on the potential convergence issues that might arise in a given computational setup.
-
-% We believe that such discussion could provide useful considerations and perspectives for the design of a effective approaches for the study of molecular excitations in realistic conditions.
-
-% We analyze how the fundamental equations which govern the linear response properties of a quantum system are influenced by the presence of open boundaries.
-% In particular we focus our attention on linear-response (LR)-TDDFT calculation of molecular systems.
-% Above this energy threshold, the excitation spectrum may be separated in two sectors: one can still be described in terms of observable excitation 
-% with discrete energies, that can be captured within computational setups tailored for localized states. 
-% This result is a inherent behavior of the system's Liouvillian, and does not depend on computational treatment of the 
-% unoccupied subspace.
 \end{abstract}
@@
 In particular, we will discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
-% In order to do this, we perform analytic considerations on the equations beyond LR treatment,
-% which will help us identifying how to distinguish -- \textit{a priori} -- quantities that are susceptible to be 
-% compared among different treatments, as they are \emph{intrinsically} associated to localized objects,
-% from quantities that \emph{explicitly} depend of the the employed computational treatment.
 
@@
 
-% Moreover, wheareas for Ground-State calculations the quantities are relatively easy to identify and extract,
-% TD-DFT and more generally, linear-response calculation present a further difficulty, which is the problem
-% of \emph{numerical} convergence. In other terms, beyond ground state, 
-% the absence of tools like the variational theorem imposes us to focus on \emph{well-defined} quantites,
-% and to study the conditions under which numerical convergence of the results can be achieved.
-
-% The subject of the present investigation concerns with the study of isolated molecular-like systems subjected to a time-dependent perturbation. % in the linear response regime.
-% This problem can be tackled within the contest of the time-dependent density functional theory (TD-DFT) \cite{runge1984,onida2002}, that allows one to establish the time-dependent 
-% Kohn-Sham (KS) equations which determine the evolution of the one-particle properties of the system with respect to time. 
-% 
-% We focus our attention to the linear response regime (LR) in which the theory can be conveniently expressed in the frequency domain and the time-dependent KS equation are reformulated 
-% as a quantum Liouville equation for the response density operator. Different computational approaches have been developed in literature \cite{baroni2008,hubener2014,brabec2015}, principally 
-% with the aim of producing efficient algorithms for the evaluation of the physical observables. These methods differ both for the procedure adopted to solve the Liouville equation 
-% (explicit diagonalization, self-consistent Sternheimer equation, Lanczos chain-like procedure, etc.) and both for the choice of the basis set employed to perform the calculations. 
-% Nonetheless, in all the cases one is a dealing with a finite basis set that, unavoidably, gives rise to a limited computational domain. 
-% It is then meaningful to try to understand under 
-% which extent the computational-induced truncation of the natural open boundaries condition could produce observable effects on the physical quantities computed in the LR. 
-% 
-% A preliminary understanding of this problem can be achieved thanks to the results reported in \cite{boffi2016}. The authors of this paper discuss the effects of a finite basis set on the 
-% occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character, and the independence of its properties (\emph{e.g.} energy) 
-% with respect to the basis set. It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
-% able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
-% true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
-% Furthermore, the energies of the unbound orbitals are not stable with respect to a change of the size of the computational domain and approach to zero as long as it is increased.  
-% 
-% In this paper we aim to reach a deeper understanding of the possible effects of a finite computational basis set on the LR regime in open systems. To achieve this task we try to
-% reformulate the relation between localization properties and basis independence for the main actors of the LR formalism. We present a discussion based on a double level analysis. First, 
-% we propose a localization argument directly based on the inspection of the response density operator. Then, we move to a deeper level and investigate the properties of the susceptibility 
-% functional, which represents the fundamental object in the contest of the linear response. Pursuing this approach we are naturally led to investigate the localization properties of excitation 
-% operators, that in turn emerge as the resonant channel of the spectral decomposition of the susceptibility. In this way we establish a direct relation between the concept of basis independence 
-% and the analytic structure of the linear response susceptibility.
-
-% First of all it is useful to discuss the property of the ground state under this perspective. 
-% Indeed, it is well known that the stability of the ground state and the localized nature of a molecular-like system ensures that the KS description of occupied states is represented 
-% by a discrete set of wave functions that approaches to zero far apart from a compact region around the system's atoms. This behavior indicates that a (finite) basis set will provide 
-% a reliable description of the ground state properties if it is able to sample a computational domain which contains the natural sizes of the occupied orbitals \cite{boffi2016}.
-% The same arguments cannot be rigidly extended to the case in which an external time-dependent field starts acting on the system. Indeed, the perturbation drives the system out 
-% from the equilibrium and the electrons sample a wider region of the state space, that will contains orbitals of both negative (bound) and positive (unbound) energies.
-
-%\section{Localization properties of the linear response actors in open systems}
 \subsection{Long range behavior of the eigenvalue solution of the Schr\"odinger equation}
@@
 and the independence of its energy with respect to the basis set. 
-% It is shown that (localized) orbitals with a bound-state behavior in the long range constitute a genuine discrete set and a finite basis is 
-% able to provide a reliable description of these states if the sampled domain contains their natural sizes. On the contrary, unbound (delocalized) orbitals form a continuum of states in the 
-% true system with open boundaries. For these class of objects the presence of a finite computational domain has a deeper impact since introduces a fictitious discretization of the energy levels. 
 Furthermore, it is clearly shown that the energies of the unbound orbitals are not stable with respect to parameters like the size of the computational domain.
@@
 \section{Fluctuation states. A localization argument for the response density}
+\label{FluctuationState}
 It is evident that the arguments presented above have a limited interest for the study
@@
 Let us now inspect the case of LR calculations.
-%Linear response can be effectively applied to the analysis of the electronic excitations in open systems.
 In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that 
@@
 
-%The main objective of this section is to investigate the structure of the building blocks needed to express the response density operator. In particular, we are interested in clarifying 
-%the behavior of the main actors of the LR in the long range, \emph{i.e.} outside from the support domain of the potential.
-
-% As a preliminary step for the forthcoming discussion we present a simple argument that allows us to determine the asymptotic character of the eigenvalue solution of the Schr\"odinger equation (SE) 
-% $\op H\ket{\psi}=\eps\ket{\psi}$. The main aims of this analysis, apart from reproducing the well known behavior of the wave functions, is to introduce some tools and setting up notations and 
-% terminology that will we widely used in the rest of the paper. 
-% 
-% The argument proceeds by splitting the Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term. Since we are dealing with molecular-like systems $\op V$ has a compact support when 
-% projected in the $\r$-representation. We can formally solve the SE as an inhomogeneous Helmholtz equation by writing
-% \be\lb{SEHelmholtz1}
-% \ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
-% \ee
-% where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$.
-We observe that, due to the properties of $\op V$, the \emph{source term} $\ket{\op V\psi}$
-% of equation \eqref{SEHelmholtz1} is localized in space and, for open boundary conditions in three dimensions, the kernel of $\op G_H(\eps)$ in the coordinate representation reads: 
-% \be\lb{HelmholtzKernelDef1}
-% \bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
-% \frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
-% \frac{e^{\ii \alpha |\r-\r' |}}{|\r-\r' |} \;, & {\textrm for} \; \eps \geq 0
-% \end{cases} \;,
-% \ee
-% where $\alpha = \sqrt{2|\eps|}$. 
-% This representation of the eigenvalues solution of the SE evidences that the value $\eps=0$ represents the threshold level that determines the asymptotic character of the wave functions. 
-% Indeed, for $\eps > 0$,  $\op G_H(\eps)$ behaves as a spherical wave and its convolution with the source term  gives raise to a $\psi(\r)$ delocalized in the whole accessible space. Instead, 
-% for values of $\eps < 0$, the kernel contains an exponential damping factor and the associated wave functions exhibit a bound-state behavior in the long range. Finally, we observe that the 
-% square-integrability and the continuity of the wave function and its derivatives poses further constrains responsible for the discretization of the energy spectrum for bound-states.  
-% 
-% The different asymptotic behavior of the wave functions has a deep impact on the possible computational induced error obtained when this quantities are evaluated using a (finite) computational
-% setup.
-
-\label{FluctuationState}
-
 The response density operator is expressed as the first-order variation of $\dmnot=\sum_{\{p\}} \ket{\psi_p} \bra{\psi_p}$, where the set $\{\ket{\psi_p}\}$ denote the 
@@
 \ee
-The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part plus a coupling term. The action of these 
+The Liouvillian superoperator $\Liouv$ for self-consistent systems is expressed as the sum of the unperturbed part $\Liouvnot$ plus a coupling term $ \coupl$. The action of these 
 terms reads, respectively
@@
 where $\op V'[\op O] \equiv \int \dd \r \dd \r'\frac{\delta \op V[\dmnot]}{\delta \rho(\r,\r')} O(\r,\r')$ encodes the response of the $\dm$-dependent potential to a modification of the density operator.
-The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidence that the response density acts as a transition 
+The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidences that the response density acts as a transition 
 operator, linking the occupied and empty subspaces of $\hnot$.
@@
 where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. 
-Thus the condition $\dm'_\Phi = \dm_{\perp}$ holds.
+In other terms, the condition $\dm'_\Phi = \dm'_{\Phi\,\perp}$ holds.
 
@@
 apart from the perturbing field, a further term $\op V'[\dm'_\Phi]$ due to the density-dependence of $\hnot$.
-% The interesting aspect of these equations in the perspective of the present analysis is that they allow us to present a localization argument for the fluctuation states using a procedure  
-% analogous to the one depicted in section \ref{SEopenSystem}. So we split the unperturbed Hamiltonian as the sum of the kinetic $\op T$ and potential $\op V$ term and express the solution of 
-% \eqref{fluctuationStateEqMotion1} in the form of a self-consistent inhomogeneous Helmholtz equation
 It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of
 a set of scattering problems:
-%a self-consistent inhomogeneous Helmholtz equation
 \be\lb{rhoPrimeFluctuationStateDef2}
@@
 \ee
-with the state%:here in this case the source term contains further addend apart from the unperturbed potential and reads:
+with the state
 $
@@
 restricted on a bounded real-space domain.
-%The localization character of fluctuation states can be assessed by following the same argument discussed in section \ref{SEopenSystem} for the eigenstates of the SE. In this case 
-%the source term depends also from the perturbation added to the system so this analysis applies only to the class 
-%of perturbing field for which $\ket{\op\Phi\psi_p}$ is localized, when projected
-%in the $\r$-representation. 
 Even when such locality argument holds true, for $\omega > |\eps_p|$, 
@@
 as from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.
-%\footnote{The fulfilling of Eq.~\eqref{SEHelmholtz1} for energies below threshold
-% is not \textit{per se} a guarantee of a localized $\ket{\psi}$. With such equation we demonstrate that, \emph{in the case when} a localized
-% solution exists, this cannot be found for energies above threshold.}
 \begin{figure}[t]
@@
 \ee
-% A direct confirmation of the localization character of fluctuation states at $\omega=0$ can be achieved through a ground-state calculation. Indeed, $\ket{f_p(\omega)}$ are nothing but the 
-% perturbed KS eigenstates projected out from the domain of $\dmnot$, so for a constant perturbation $\op\Phi_s$ it turns out that $\ket{f_p(0)} = \op Q_0\ket{\psi_p^{\Phi_s}}$. The perturbed KS 
-% states $\ket{\psi_p^{\Phi_s}}$ can be computed (beyond LR) by performing a DFT ground-state computation in which the constant perturbing field is added to the external potential and the 
-% spatial extension of the fluctuation states can be directly measured.
 where $\mathbf d^\text{(GS)}$ is the ground state dipole.
@@
 \ee
-%so the computation of the linear response functional passes through the evaluation of the scalar products indicated in \eqref{LinearResponseFunctDef2}.
 Let us suppose that also the observable of interest $\op O$ exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.
@@
 quantities. At these frequencies, the linear response functional $\braket{\delta\op O}_\Phi(\omega)$
-%The quantities $\braket{\psi_p \op O| f_p^\Phi(\omega)}$, 
-%being scalar products of bound-state-like objects, 
 may thus be evaluated with computational setups that
@@
  as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
-
-% , each of which 
-% possesses a physical cut-off radius. Due to this behavior we can affirm that given basis provides a reliable evaluation of \eqref{LinearResponseFunctDef2} if the chosen computational domain 
-% is suitable to express the bound-state like fluctuation states, in a analogous fashion of a ground state calculation.
 
@@
 on the perturbation operator $\op \Phi$, not to mention the target observable $\op O$. Alternatively, we may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction, 
-%that may be local and with a well-defined normalization 
 with a potential local behavior only for $\omega$ below the ionization threshold. Hence, comparing fluctuation states among diverse numerical treatments would be a 
@@
 \ee
-%This alternative formulation of the problem has the advantage of providing general information on the nature of the excitation spectrum. Results achieved in this way thus describes an intrinsic 
-%feature of the system under inspection and determine the properties of the LR independently from the specific choice of the perturbing field. 
 The susceptibility (super)operator $\cal \chi(\omega)$ is therefore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined 
@@
 of the excitation.
-% Being themselves transverse operators, without loss of generality we can parametrize excitations by employing  
-% the \emph{excited states} $\ket{\phi^a_p}$ and $\bra{\chi^a_p}$ that, by construction, are orthogonal to the occupied orbitals
-% $\ket{\psi_p}$ 
-Excited states  satisfy the normalization condition % and the orthonormalization condition \eqref{orthoExcitatioOpDef1} implies 
+Excited states  satisfy the normalization condition
 \be\lb{ExcitedStateOrthNormDef1}
@@
 \ee
-% We observe that right eigenvalues of $\Liouv$ can be written in terms of the left ones due to the properties 
-% of the Liouvillian described in appendix \ref{LiouvillianAction}. 
-% By applying equations \eqref{LiouZeroDef1},\eqref{CouplDef1} and \eqref{LiouvillianRightActionDef1} presented in 
-% appendix \ref{LiouvillianAction} to the dyadic representations of the excitation 
-% operators, 
 By applying \eqref{ExcitationOperatorsDef1} to the above parametrization
@@
 $\bra{s_p[\op E_a]}$, which in turn is related to the behavior of the operator $\op V'[\op E_a]$.
-% As in the previous section, we assume the hypothesis that such operator is such that
-% the state $\op Q_0 \op V'[\op E^t_a] \ket{\psi_p}$ is localized, at least when \emph{both}
-% the states $\phi_p^a$ $\chi_p^a$ have bound-state-like behaviour.
 
@@
 If any of these hypothesis does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
-% As a consequence of these behaviors and assuming the spatial localization of 
-% the source terms,  we observe that the asymptotic character of $\ket{\phi^a_p}$ changes from bound to unbound as the value of the excitation energy crosses the threshold $|\eps_p|$ while all 
-% the $\ket{\chi^a_p}$ states exhibit a bound-state behavior for all the values of $a$. 
 Furthermore, excited states are subjected to the orthonormalization condition 
@@
 
-% The structure of the excitation spectrum follows from the properties of the excited states described above. 
-% To clarify this point we consider a value of $\Omega_a$ that satisfies equations
-% \eqref{ExcitationOperatorsDef1}. In correspondence of this values equations \eqref{ExcitationOperatorsDef3} 
-% possess a solution in which \emph{at least} one of the excited states 
-% is not zero. We denote with $p=p_m$ the label of the $\ket{\phi^a_p}$  with the highest value of $|\eps_p|$, among the ones that contribute to \eqref{ExcitationOperatorsDef2}. From the previous 
-% considerations it emerge that if $\Omega_a<|\eps_{p_m}|$ \emph{all} the excited states in the dyadic representation of the excitation operator possess a bound-state like behavior. Excitations 
-% of this type thus represent localized quantities and the associated eigenvalue are discrete.
-On the contrary, for $\Omega_a>|\eps_{p_m}|$ some (or all) of the excited states in the dyadic representation
-% of the excitation behave as generalized eigenvectors and the corresponding eigenvalue belong to a continuum of accessible values.
-
 The susceptibility functional has therefore a peculiar analytic structure, that
@@
 \subsection{Observable features of the excitation spectrum}
-%\subsection{Stability and convergence of the excitation spectrum}
 
@@
 The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. 
-% Extending the results achieved in \cite{boffi2016} for the KS virtual orbitals, 
-%to the equations for excited states 
-%\eqref{ExcitationOperatorsDef3}, we conclude that such localized excitations behave as 
 Borrowing the terminology introduced in section \ref{SEopenSystem} to the present case, we can affirm that such localized excitations behaves as
@@
 The figures show clearly that all the excitations of energy $\Omega_a$ lying below the 
-molecule ionization potential (IP) have a clear localized behavior, as their energy does not vary with the size of the simulation domain.
-On the other hand, above the first ionization threshold the excitation energies have an energy that strongly depends on the computational
+molecule ionization potential (IP) have a localized behavior, as their energy does not vary with the size of the simulation domain.
+On the other hand, above the first ionization threshold the excitations have an energy that strongly depends on the computational
 setup, which is in line with the expected pseudo-continuum character of this sector. 
@@
 
-%\subsection{The importance of the continuum sector}
 \subsection{Physical relevance of the continuum sector}
@@
 Such objects are LR quantities, associated to the molecule, whose numerical convergence
-can be found by employing techniques which can be mutuated from the ones adopted for GS calculations. Being expressed by localized excited states,
+can be found by employing techniques which can be borrowed from the ones adopted for GS calculations. Being expressed by localized excited states,
 computational setups with sufficient level of completeness are able to
@@
 from the above quantities as
-\be
+\be\lb{sminus2}
 \alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \varphi_p^a[\op r_i]\varphi_p^a[\op r_j]\;.
@@
 Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
-This is the well-know $S_{-2}$ sum-rule\cite{TDDFTBOOK}, that express the value of the static polarizability
+This is the well-know $S_{-2}$ sum-rule (see e.g.\cite{Wagner2012}), that express the value of the static polarizability
 in terms of the molecule's oscillator strengths.
@@
 \includegraphics[scale=0.6]{CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,  w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}.
+The reference value obtained from Eq.~\eqref{staticalpha} is represented as a horizontal red dashed line.
+The value of the IP energy is indicated by a vertical black dashed line.
+For each excitation energy, the values of the oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted.
+}
 \end{figure}
@@
 \section{Computational details}
-The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{bigdft},
+The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{BigDFT},
 which employs Daubechies Wavelets as computational basis set.

### 2018-07-12 AnalyticStructure_main.tex

@@
 \end{align}
-By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation
+By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation\cite{CasidaBook}
 associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).

### 2018-07-12 AnalyticStructure_main.tex
Update on Overleaf.

--- 2018-07-12 AnalyticStructure_main.tex
@@
 \includegraphics[scale=0.6]{CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability of the $CO$ molecule w.r.t the number of excitations.}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}.
+The reference value obtained from Eq.~\eqref{staticalpha} is represented as a horizontal red dashed line.
+The value of the IP energy is indicated by a vertical black dashed line.
+For each excitation energy, the values of the oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted.
+}
 \end{figure}

### 2018-07-12 AnalyticStructure_main.tex
update

--- 2018-07-12 AnalyticStructure_main.tex
@@
 there exist a sector where the fluctuation states are genuinely localized, thereby presenting reproducibility features. Therefore, 
-knowing that $\ket{f_p^\Phi(\omega)} =\sop \chi(\omega) \op \Phi(\omega) \ket{\psi_p}$, % \dm'_\Phi(\omega)
+knowing that $\ket{f_p^\Phi(\omega)} =\sop \chi(\omega) \op \Phi(\omega) \ket{\psi_p}$,
 it would be interesting to obtain information on whether the discrete, localized sector of the excitations which appear in the spectral decomposition of $\sop \chi(\omega)$
@@
 expressing the spectral decomposition of the linear susceptibility we find:
-% \begin{align}
-%  \ket{f_p^\Phi(\omega)} &= \ket{f^\Phi_p(\omega)^D} + \ket{f^Phi_p(\omega)^C} \lb{FSExcitationDef1} \\
-%  \ket{f_p^\Phi(\omega)^D} &= \sum_a^{0<\Omega_a < |\eps_a|} \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2} \\
-%  \ket{f_p^\Phi(\omega)^C} &= \int_{0<\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{f_p^a(\op \Phi,\omega)}{\omega^2-\Omega_a^2}
-% \end{align}
 \be
@@
 the one coming from the continuum sector.
-
-% The inclusion of core electrons in the calculation would have added a further set of localized
-% excitations, but at much higher energies than the one needed for this test.
 
@@
 \section{Conclusions and Perspectives}
-% In the analysis presented in this paper we have investigated how 
-% computational results of linear-response calculations of molecular systems 
-% might be compared among various formalisms.
-% In particular, we have been interested in identifying the quantities that can
-% be expressed in computational setups that are originally conceived for 
-% \emph{localised} objects, which are the \emph{only} quantities that
-% play a significant role in GS calculations.
 
 By analysing the fundamental equations of LR calculations of molecules, we have shown that the response density for values of $\omega$ above the first IP
-\emph{have} to be expressed in terms of genuinely delocalized states. %, whereas 
+\emph{have} to be expressed in terms of genuinely delocalized states. 
 Below this threshold,
@@
 We remark that we are not referring here to the continuum eigenstates of the 
-unperturbed GS Hamiltonian, %which is not in itself important for expressing the linear susceptivity, 
+unperturbed GS Hamiltonian,
 but to the continuum of excitations expressed as eigenstate of the 
@@
 
-% We are, on the contrary, forced to provide effective representations for
-% the delocalised excitations belonging to the (pseudo-) continuum sector.
-
-% As an illustration, we have presented explicitly examples where the pseudo-contunuum sector is relevant: in the same 
-% We have shown computational setups in which convergence difficulties high-energy absorbption spectra are observed, whereas the $S_{-2}$ sum rule (meaningful in the $\omega=0$ regime) is precisely fulfilled.
-
-% However, this does not necessarily imply that for $\omega$ above thresholds 
-% the same pseudo-continuum expansion can be effectively employed: we have shown spectral representation of $\chi(\omega)$ which presents difficulties in convergence of high-energy absorbption spectra, whereas they provide precise values of the excitation energies in the discrete sector.
-% In other terms, the set of continuum excitations may only be \emph{effectively} represented
-% in a computational approach, depending on the quantities of interest.
-
 We believe that these considerations, based on simple manipulations on the fundamental LR equations, will help in increase
@@
 presents ideal features as an initial playground. Work is ongoing in this direction.
-
-% \section{Garbage Collector}
-
-%The introduction of the excitation operators allows us to express the spectral decomposition of the resolvent of the Liouvillian so that:
-%Susceptibility written as
-% The introduction of the excitation operators allows us to express the susceptibility functional \eqref{SusceptibilityDef1} through the spectral decomposition of the resolvent of the 
-% Liouvillian. Pursuing this procedure provides:
-% \be\lb{RhopExcitationDef2}
-% \sop{{\cal \chi}}(\omega) \cdot   = \left(\sum_a + \int\dd a   \right) \op W_{a} \,
-% \frac{2\trace{\op W_a \cdot}}{\omega^2-\Omega_a^2} \;,
-% \ee 
-% where we have defined the symmetric operators $\op W_a = \frac{1}{\sqrt{2}}(\ketbra{w_p^a}{\psi_p}+\ketbra{\psi_p}{w_p^a})$ and states $\ket{w_p^a}=\ket{\psi_p^a}+\ket{\chi_p^a}$.
-
-% The elements of the first category correspond to \emph{true poles} of the susceptibility while the others can be interpreted only in terms of the spectral function.
-
-% This analysis has revealed that the excitations spectrum is composed by two distinct sectors.
-The first one is realized by the (finite) set of localized excitations with discrete eigenvalues.
-Extending
-% the results achieved in \cite{boffi2016} for the KS virtual orbitals, to the equations for excited states \eqref{ExcitationOperatorsDef3}, we conclude that localized excitations behave as 
-% \emph{observable} quantities and the associated energies possess an absolute meaning, which should not depend from the computational setup used for their representation. 
-% 
-% Instead, the second sector contains the dense set of delocalized excitations with an associated continuum spectrum.
-These excitations behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
-% and are deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-% the associated spectrum exhibit an explicit dependence from the size of the domain.
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood as a tool to
-% express the spectral decomposition of the Liouvillian superoperator.
-
-% Lastly, we establish a link between the fluctuation states and excitation operators based description of the LR. Indeed, thanks to the defining equation \eqref{SusceptibilityDef1} we can 
-% easily express the excitations expansion of fluctuation states as follows 
-% \be\lb{FluctuationStateExcitationDef1}
-% \ket{f_p(\omega)}   =
-% \left(\sum_E + \int\dd E   \right) 
-% %\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
-% \frac{t_\Phi(E)}{\omega-E} \ket{\phi^E_p} \;,
-% \ee 
-% with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$. 
-% %This formula shows that, for each value of $\omega$, both the sectors of the excitations spectrum contribute to the fluctuation state. 
-% Thanks to the analysis presented in section \ref{FluctuationState} we know that fluctuation states possess a localized behavior up to $\omega=|\eps_h|$, so we conclude that 
-% below this energy threshold the continuum sector of the excitation spectrum is able to resum in a localized way.
-
-%Excitations behave as singularity of the susceptibility operator and their knowledge provides a deeper insight into the analytic structure of the linear response.
-
-%\subsection{Discrete poles and spectral function. Physical meaning of the excitation spectrum} %{Comments. Physical meaning of the excitation spectrum}
-
-% The analysis discussed above has evidenced that there exists both localized and delocalized excitations. While the role of the former is quite unambigous 
-% We can express the 
-% \be\lb{FluctuationStateExcitationDef1}
-% \ket{f_p(\omega)}   =
-% \left(\sum_E + \int\dd E   \right) 
-% %\frac{\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}}{\omega-E} \ket{\phi^E_p} \;. \nn
-% \frac{t_\Phi(E)}{\omega-E} \ket{\phi^E_p} \;,
-% \ee 
-% with $t_\Phi(E)=\trace{\commutator{\dmnot}{\op{\tilde E}}\op\Phi(\omega)}$.
-% This relation clarifies the role of the excitations in the spectral decomposition. We know from the analysis of section \ref{FluctuationState} that fluctuation states are localized
-% up to $\omega=|\eps_h|$.
-
-%\section{Quality indicator for the numerical convergence of the LR}   %{Criterion for a reliable sampling of the excitation operators}
-
-% From the analysis discussed in the previous section it emerges that the general treatment of the LR for open systems \emph{requires} to deal with delocalized
-% objects. In facts, either if one choose the fluctuation states' formalism, or the ``sum over excitations'' (SOE) approach, it turns out that the main building blocks
-% beyond a specific energetic threshold have an unbound behavior in the long range. 
-% On the basis of this consideration is then reasonable to try to understand if a computational setup tailored to deal with the ground state problem is idoneous to provide
-% reliable results for the LR.
-
-% \vspace{0.3cm}
-
-% \begin{figure}[ht]
-% \includegraphics[scale=0.6]{C6H6_dos.eps}
-% \caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
-% \label{C6H6_exc}
-% \end{figure}
-% 
-% \begin{figure}[ht]
-% \includegraphics[scale=0.56]{C6H6_excLandscape.eps}
-% \caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
-% \end{figure}
-
-% \begin{figure}[ht]
-% \centering
-% \begin{subfigure}[]{0.2\textwidth}
-% \includegraphics[scale=0.56]{C6H6_excLandscape.eps}
-% %\caption{\label{c6h6_excLand}(Color online) Excitation landscape of $C_6H_6$.}
-% \end{subfigure}
-% \centering
-% \begin{subfigure}[b]{0.2\textwidth}
-% \includegraphics[scale=0.6]{C6H6_dos.eps}
-% \end{subfigure}
-% \caption{(Color online) Excitation spectrum of $C_6H_6$. The two curves correspond to two computational domain of different sizes. The inset contains the sole contribution of localized excitations.}
-% \end{figure}
-
-% From the theoretical analysis of the previous section we can made two statements:
-% \begin{itemize}
-%  \item Fluctuation states, which constitute the building blocks of the response density, have a bound state-like character up to $\omega=|\eps_h|$ and behave as unbound delocalized
-%  wave functions for higher values of $\omega$. 
-%  \item The excitation landscape is composed of two sectors with distinct properties. The elements of the first one behave as localized, observable quantities and contribute as discrete 
-%  poles to the spectral decomposition of the susceptibility functional. The second sector contains a continuum of delocalized excitations which represents a tool to provide
-%  an effective representation of the spectral function. 
-% \end{itemize}
-% The topic to be discussed in this section is the following: on the basis of these statements can we define some indicator to evaluate the reliability of a linear response calculations? And, 
-% if so, up to which energy threshold can we assume that our computations do converge?
-% 
-% The first element of this discussion is the introduction of the computational basis, made of $n_\mu$ basis functions $\{\mu\}$, used to perform the DFT calculations subjacent to the LR analysis. 
-% The properties of the $\mu$-basis (state something about the systematic character the basis?
-comment on the finite dimension of the computational domain?) are chosen to ensure an unbiased description
-% of the ground state properties of the system. 
-% 
-% FIRST QUESTION: The usage of the $\mu$-basis allows us to obtain a reliable evaluation of the perturbation induced modification of an observable? 
-% The answer of this question is based on the analysis of equation \eqref{LinearResponseFunctDef2} and has been partially provided in section \ref{FluctuationState} (move that material in this section?).
-% We can complete the answer by observing that $\ket{f_p(0)}$ can be obtained through a ground state calculation with the explicit time independent perturbation added to the system. So we can perform
-% a check on the goodness of the basis in this case as in a ground state calculation. Then use the localization argument of the fluctuation states to extend the reliability of the result up to
-% $\omega=|\eps_p|$. 
-% 
-% SO TO SUMMARIZE: below the threshold the numerical convergence is regulated by the localization of the fluctuation states, in this range we can assess the reliability of the results provided by
-% the $\mu$-basis by looking at the basis-independence of the fluctuation states at $\omega=0$. Above the threshold the convergence can be reached due to the localized nature of $\bra{\psi_p}\op O$, 
-% in this case the computational setup provides reliable results if it guarantees the unbiased reconstruction of fluctuation states in the support of $\bra{\psi_p}\op O$. In this range there is no a 
-% priori indicator of the goodness of the results.
-
-% \subsection{Fluctuation state and excitations}
-
-% Show the convergence of the statical polarizability of the $CO$ in function of the number of excitations. Write formula
-% \be\lb{AlphaExcitationDef1}
-% \alpha_{xx} =  \left(\sum_a + \int\dd a   \right) 2 \,
-% \frac{\left[\trace{\op W_a \op X}\right]^2}{\Omega_a^2} \;,
-% \ee 
-% and add the plot that show the convergence rate of the statical polarizability to the reference (finite difference) value in functions of the number of excitations. The plot evidence that the
-% continuum sector of the excitation spectrum is
-
-% \subsection{Choice of the $\alpha$-basis. Statical polarizability-driven criterion revised}
-% 
-% The previous considerations regard the relation between the localization properties of the fluctuation states and the possibility of having a quality indicator for the goodness of the $\mu$-basis. 
-% Now we aim to extend/reformulate the question of the numerical convergence to the case in which the excitation-based representation of the LR is adopted.
-% 
-% The construction of the excitation operators requires the explicit sampling of the empty state subspace. We introduce the notion of \emph{$\{\alpha\}$-basis}: choose the empty eigenstates of the KS 
-% Hamiltonian as a basis-set to express the excited state $\ket{\phi^E_p},\bra{\tilde\chi^E_p}$ and their duals. Excitations are written in the basis of transitions.  
-% 
-% COMMENT: The elements of the $\{\alpha\}$-basis are written in the (finite dimensional) $\{\mu\}$-basis.
-It follows that the $\{\alpha\}$-basis is finite dimensional too and has $n_\mu-n_{occ}$ degrees
-% of freedom. Excitation index becomes discrete and the basis provide a partial sampling of the continuum sector of the excitation landscape.
-
-% \subsection{Comments and conclusions}
-
-% The analysis carried out starting from the representation of the linear response functional in terms of fluctuation states has evidenced some general properties of the linear response
-% for open systems. In particular, by analyzing the asymptotic behavior of fluctuation states in long range limit, we have showed that they exhibit a bound-state character in the regime  
-% $\omega<|\eps_h|$. Consequently we have argued that the linear response functional, in the same $\omega$ range, provides a setup-independent result with a modest computational effort...
 
@@
 $\left( \Liouv \op O \right)_\parallel =0$.
-% \be\lb{CouplDef1}
-% \coupl\op O = \commutator{\op V'[\op O]}{\dmnot}  = \op Q_0\op V'[\op O]\dmnot - \dmnot\op V'[\op O]\op Q_0 \;,
-% \ee
 
@@
 & D_{p\rho}^{q\eta} = U[\decay{\rho}{p};\decay{\eta}{q}] \;.
-%& E_{p\rho}^{q\eta} = U[\excite{p}{\rho};\excite{q}{\eta}] \;,\nn \\
-%& G_{p\rho}^{q\eta} = (H_{0\eta\rho}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\excite{p}{\rho};\decay{\eta}{q}] \;. \nn
 \end{align}

### 2018-07-12 AnalyticStructure_main.tex
Update on Overleaf.

--- 2018-07-12 AnalyticStructure_main.tex
@@
 \includegraphics[scale=0.6]{CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}.
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,  w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}.
 The reference value obtained from Eq.~\eqref{staticalpha} is represented as a horizontal red dashed line.

### 2018-07-12 AnalyticStructure_main.tex
update

--- 2018-07-12 AnalyticStructure_main.tex
@@
 \newcommand{\br}{\bar{\bf r}}
+\renewcommand{\AA}{{Angstr\"om}}
 \newcommand{\x}{{\bf x}}
@@
 \end{align}
-For each choice of $p,a$, these objects represent, respectively, the state in which $\ket{\psi_p}$
+For each choice of $\{\phi^a_p,\chi^a_p\}_{p \in a}$, these objects represent, respectively, the state in which $\ket{\psi_p}$
 is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
@@
 \ee
-Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as described in Sec.~\ref{FluctuationState}.
+Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as 
+described in Sec.~\ref{FluctuationState}.
 This is the well-know $S_{-2}$ sum-rule (see e.g.\cite{Wagner2012}), that express the value of the static polarizability
@@
 \includegraphics[scale=0.6]{CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,  w.r.t to excitations considered in the integral of Eq.~\eqref{sminus2}.
-The reference value obtained from Eq.~\eqref{staticalpha} is represented as a horizontal red dashed line.
-The value of the IP energy is indicated by a vertical black dashed line.
-For each excitation energy, the values of the oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted.
-}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,  
+w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a 
+horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the 
+oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
 \end{figure}

### 2018-07-12 AnalyticStructure_main.tex
update

--- 2018-07-12 AnalyticStructure_main.tex
@@
 \begin{figure}[t]
-\includegraphics[scale=0.68]{CO_statPolvsBox.eps}
+\includegraphics[scale=0.68]{Fig1_CO_statPolvsBox.eps}
 \caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ (blue continuous line) and of the ground state dipole $d_z$ (red dotted line) 
@@
 In this case a computational description of fluctuation states is only meaningful in ``weak'' sense,
-%\emph{i.e.} inside the scalar products of 
-%\eqref{LinearResponseFunctDef2}. 
-%since $\ket{f_p^\Phi(\omega)}$ becomes an unbound, delocalized function, 
 where the bound state character of $\{\bra{\psi_p}\op O\}$ behaves as a regulator.
@@
 \begin{figure}
-\includegraphics[scale=0.6]{CO_spectrum.eps}
+\includegraphics[scale=0.6]{Fig2_CO_spectrum.eps}
 \caption{\label{co_spectrum}(Color online) Illustrative LR absorption spectra of the $CO$ molecule in computational setups with different sizes of the simulation domain.
@@
 \begin{figure}[ht]
-\includegraphics[scale=0.6]{CO_dos.eps}
+\includegraphics[scale=0.6]{Fig4_CO_dos.eps}
 \caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$.
@@
 {\label{c6h6_excLand}
-\includegraphics[scale=0.56]{C6H6_excLandscape.eps}} \\
+\includegraphics[scale=0.56]{Fig5a_C6H6_excLandscape.eps}} \\
 \centering
@@
 {\label{C6H6_exc}
-\includegraphics[scale=0.58]{C6H6_dos.eps}}
+\includegraphics[scale=0.58]{Fig5b_C6H6_dos.eps}}
 \caption{(Color online) Benzene molecule.
@@
 \begin{figure}
-\includegraphics[scale=0.6]{CO_statPolvsExc.eps}
+\includegraphics[scale=0.6]{Fig6_CO_statPolvsExc.eps}
 \caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,  

### 2018-07-12 AnalyticStructure_main.tex
abstract

--- 2018-07-12 AnalyticStructure_main.tex
@@
 we explore the interplay between locality of the response density operator and  numerical convergence of LR-related quantities.
-We show that the first ionization potential of the system behaves as a threshold energy: for frequencies below this value, it is possible to parametrize the response density by employing localized states only.
-Above this threshold, such a locality property cannot be achieved.
+%We show that the first ionization potential of the system behaves as a threshold energy: for frequencies below this value, it is possible to parametrize the response density by employing localized states only.
+We show that for frequencies below the first ionization potential (IP) of the system, it is possible to parametrize the response density by employing localized states only.
+Above this threshold energy, such a locality property cannot be achieved. 
 Such considerations may be transposed in terms of the molecule's excited states. We show that not all the system's excitations can be considered on equal footing.
-There is a discrete sector of excitations that can be parametrized by observable, localized states, which can be computationally expressed with high precision, provided an adequate level of completeness.
+There is a discrete sector of excitations -- which may extend above IP -- that can be parametrized by observable, localized states, which can be computationally expressed with high precision, provided an adequate level of completeness.
 We present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated 
@@
 
+\begin{acknowledgments}
+We thank Thierry Deutsch for useful comments on the manuscript.
+\end{acknowledgments}
+
 \appendix

### 2018-07-12 AnalyticStructure_main.tex
last before arxiv

@@
 \newcommand{\coupl}{\sop{\mathcal K}}
-\newcommand{\honetmp}[1][]{\op{H_1}\argument{#1}} 
+\newcommand{\honetmp}[1]{\op{H_1}\argument{#1}} 
 \newcommand{\identity}{\op{\mathbb I}}
@@
 \newcommand{\fscd}[1]{\ket{f_p^\Phi(\omega)^{#1}}}
+\newcommand{\GH}{\op G_{\op T}}
 
@@
 \begin{abstract}
-By performing a critical analysis of the fundamental equations of linear-response  (LR) formalisms in molecules, 
+By performing a critical analysis of the fundamental equations of linear-response (LR) formalism in molecules, 
 we explore the interplay between locality of the response density operator and  numerical convergence of LR-related quantities.
-%We show that the first ionization potential of the system behaves as a threshold energy: for frequencies below this value, it is possible to parametrize the response density by employing localized states only.
-We show that for frequencies below the first ionization potential (IP) of the system, it is possible to parametrize the response density by employing localized states only.
+We show that for frequencies below the first ionization potential (IP) of the system, it is possible to express the response density by employing localized states only.
 Above this threshold energy, such a locality property cannot be achieved. 
@@
 computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
-It may be, for example, in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
+For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
 The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
@@
 We support our considerations with numerical results on simple LR-TDDFT quantities.
-For readability purposes, the details of each calculation are explained in the Appendix.
+For readability purposes, the details of each calculation are explained in Appendix~\ref{compdetails}.
 
@@
 solutions of the time-independent Schr\"odinger Equation.
-We here present well-known concepts of elementary quantum mechanics, under a perspective that
+We here present well-known concepts of quantum mechanics, under a perspective that
 will turn out to be very useful in the forthcoming considerations about linear-response quantities.
@@
 \be\lb{SEHelmholtz1}
-\ket{\psi} = \op G_H(\eps)\ket{\op V\psi}\;,
+\ket{\psi} = \GH(\eps)\ket{\op V\psi}\;,
 \ee
-where we have introduced the Green function of the Helmholtz operator $\op G_H(\eps) = (\eps-\op T)^{-1}$,
+where we have introduced the Green function of the Helmholtz operator $\GH(\eps) = (\eps-\op T)^{-1}$,
 resolvent of the free-particle Hamiltonian $H_s \equiv \op T$.
@@
 This fact is made apparent by the expression of 
-the kernel of $\op G_H(\eps)$ in the coordinate representation. 
+the kernel of $\GH(\eps)$ in the coordinate representation. 
 When dealing with Isolated BC, it is easy to see that the solution of Eq.~\eqref{SEHelmholtz1}
@@
 \be\lb{HelmholtzKernelDef1}
-\bra{\r} \op G_H(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
+\bra{\r} \GH(\eps) \ket{\r'} = \frac{1}{4\pi} \begin{cases}
 \frac{e^{-\alpha|\r - \r' |}}{|\r- \r' |} \;,\; & {\textrm for}\; \eps  < 0\; \\ 
@@
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in the subspace orthogonal to the occupied states of $\hnot$. 
+where $\op Q_0=\identity-\dmnot$ is the projector in empty subspace of $\hnot$
+(for more details see Appendix~\ref{LiouvillianAction}).
 In other terms, the condition $\dm'_\Phi = \dm'_{\Phi\,\perp}$ holds.
@@
 \be\lb{rhoPrimeFluctuationStateDef2}
-\ket{f_p^\Phi(\omega)} = \op G_H(\omega+\epsilon_p)\left(\op V\ket{f_p^\Phi(\omega)} + \ket{s_p^\Phi(\omega)} \right)\;,
+\ket{f_p^\Phi(\omega)} = \GH(\omega+\epsilon_p)\left(\op V\ket{f_p^\Phi(\omega)} + \ket{s_p^\Phi(\omega)} \right)\;,
 \ee
@@
 $
-\ket{s_p^\Phi(\omega)} = \op Q_0(\op V'[\dm'_\Phi](\omega) + \op \Phi(\omega))\ket{\psi_p} 
+\ket{s_p^\Phi(\omega)} = \op Q_0(\op \Phi(\omega) +\op V'[\dm'_\Phi](\omega) )\ket{\psi_p} 
 $ as a source term.
@@
 Fig.~\eqref{co_alphaStatic} illustrates this procedure for a $CO$ molecule 
-perturbed by a static electric field. The local character of the fluctuation states at $\omega=0$ is 
+perturbed by a static electric field. 
+Care has been taken in keeping the field strenghts $F_j$ small enough to 
+preseve the validity of the linear response regime.
+The local character of the fluctuation states at $\omega=0$ is 
 probed by verifying the convergence of the statical polarizability versus 
@@
 where the bound state character of $\{\bra{\psi_p}\op O\}$ behaves as a regulator.
+This is naturally achieved in the above mentioned Krylov space treatments, which
+explicitly deal with the expression of the scalar products. However
+it is important that the underlying basis set is able to express delocalised states.
 
@@
 The spectrum is symmetric w.r.t the inversion of the eigenvalues 
-$\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transpose pair $\{\chi^a_p,\phi^a_p\}$.
+$\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.
 We concentrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
@@
 \begin{align}
-\ket{\phi^a_p} &= \op G_H(\Omega_a+\eps_p)\left(\op V \ket{\phi^a_p} + \ket{s_p[\op E_a]} \right) \;, \nn \\
-\bra {\chi^a_p} &=\left(\bra{\chi^a_p} \op V  + \bra{s_p[\op E_a]}\right)  \op G_H(-\Omega_a+\eps_p)\;,
+\ket{\phi^a_p} &= \GH(\Omega_a+\eps_p)\left(\op V \ket{\phi^a_p} + \ket{s_p[\op E_a]} \right) \;, \nn \\
+\bra {\chi^a_p} &=\left(\bra{\chi^a_p} \op V  + \bra{s_p[\op E_a]}\right)  \GH(-\Omega_a+\eps_p)\;,
 \end{align}
@@
 
-On the other hand, the long-range behavior of $\op G_H(\Omega_a+\eps_p)$ depends from 
+On the other hand, the long-range behavior of $\GH(\Omega_a+\eps_p)$ depends from 
 $\Omega_a$, with a threshold of value $\Omega_a=|\eps_p|$. 
@@
 associated to the occupied states. 
-If an excitation $\op E_a$ has a energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$,
+If an excitation $\op E_a$ has an energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$,
 it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states. 
-The typical structure of the excitations landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable 
+The typical structure of the excitation landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable 
 behavior of the perturbed potential $\op V'$.
@@
 The first one is realized by the (finite) set of localized excitations with discrete eigenvalues. 
-Borrowing the terminology introduced in section \ref{SEopenSystem} to the present case, we can affirm that such localized excitations behaves as
+Borrowing the terminology introduced in section \ref{SEopenSystem} to the present case, we can affirm that such localized excitations behave as
 \emph{observable} quantities and the associated energies possess ideal features of reproducibility:
@@
 In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-the associated spectrum exhibit an explicit dependence from the size of the domain. 
+the associated spectrum exhibits an explicit dependence from the size of the domain. 
 Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as
@@
 In this localized regime, it is possible to achieve convergence of the numerical result
-by increasing the completeness of the basis with the usual GS rationales.
+by increasing the basis completeness in the same spirit of GS calculations.
 One might expect that more complete basis will give more precise results, regardless of their asymptotic behavior.
@@
 Such point of view have also enabled us to shed light on the analytic structure of the 
-linear susceptibility, which is a intrinsic property of the molecule and does not depend on
+linear susceptibility, which is an intrinsic property of the molecule and does not depend on
  the perturbing fields.
@@
 
-\section{Computational details}
+\section{Computational details} \lb{compdetails}
 The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{BigDFT},

### 2018-10-18 AnalyticStructure_main.tex
update

@@
 %\pgfplotsset{compat=1.15}
+\usepackage[markup=underlined]{changes}
+\definechangesauthor{dal}
+\definechangesauthor{gen}
 
@@
 \section{Introduction}
+\added[id=dal]{Testo nuovo}.
+\deleted[id=dal]{lallero}
+
 Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the 
@@
 This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response 
-density in terms of FS implies that 
+density in terms of FS implies that \added[id=dal]{(equation for the response density modified)}
+% \be\lb{LinearResponseFunctDef2}
+% \braket{\delta\op O}_\Phi(\omega) = 2 \mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
+% \ee
 \be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}_\Phi(\omega) = 2\mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
+\braket{\delta\op O} = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
 \ee
@@
 
-As an example in support of these arguments we compare the absorption spectrum of a $CO$ molecule computed in 
-three distinct real-space computational setups, which differs for the dimension of 
-the computational domain. 
-Results reported in figure \ref{co_spectrum} evidences a typical behavior: the curves are almost coincident in the below threshold regime,
+As an example in support of these arguments we compare the \replaced[id=dal]{dynamical polarizability $\alpha(\omega)$}{absorption spectrum} of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain.
+Results reported in \replaced[id=dal]{the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
+In all the cases a typical behavior emerges}{evidences a typical behavior}: the curves are almost coincident in the below threshold regime,
 whereas the effect of the computational setup are clearly visible for values of $\omega$ that exceed the threshold value.

### 2018-10-24 Response_referees.tex
add referees response

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage[english]{babel}

% Parametri di stampa
\setlength{\topmargin}{-2.5cm} \setlength{\oddsidemargin}{0.3cm}
\setlength{\evensidemargin}{0.3cm}
%
\textheight=23.0truecm \textwidth=16.0truecm
%
\headheight=1.0cm \headsep=1.0cm
%
\renewcommand{\baselinestretch}{1.1}
\setlength{\unitlength}{1mm}

\parindent=6pt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\al}{\alpha}
\newcommand{\br}{\bar{\rho}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bpi}{\bar{\pi}}
\newcommand{\bra}{\langle}
\newcommand{\ket}{\rangle}
\newcommand{\sst}{\scriptscriptstyle}

\newcommand{\op}[1]{\hat {#1}}

\def\sst{\scriptscriptstyle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Response to the first referee}

We wish to thank the referee for the positive review on the paper. Here we report a list of the modification performed in the text according
to his/her suggestions:
\begin{enumerate}
  \item \emph{point concerning the dimension of the simulation box needed to achieve the convergence of the delocalized states of the $CO$ molecule}.

  Clarify that delocalized (fluctuation) states never achieve convergence (continumm collapse). What is expected to converge is the spectral function, or declined in the present case the real and imaginary part of the dynamical polarizability. To give a reasonable value from the literature we can make usage of the results of achieved by Baroni for the benzene molecule... 
  \item \emph{point concerning the convergence rate of the delocalized vs. localized states (which one? fluctuation or excitation?) with respect
  to the grid spacing}

 Actually I don't know but I do not expected relevant differences, since localized and delocalized states differ in their asymptotic properties whereas the grid spacing convergence is influenced by the fast oscillation of the functions.

 To present a more detailed answer we could perform a convergence analysis w.r.t the gridspacing looking at the convergence rate of the energies of say 16 virtual orbitals of the $CO$ molecule. In this way we can see if the rate of the bound-state ones differs from the others.

 Lastly, the values of the grid spacing used for the calculations have been added in appendix C.

\item Answer to the other minor points...

\end{enumerate}

\section*{Response to the second referee}

We thank the referee for its comment and criticism of the paper.
We try to answer to the critical points raised out by the review:

\begin{enumerate}
 \item \emph{on the relevance of the symmetry of the molecule in determining the delocalized vs localized character of the an excitation}

 In the paper we have introduced a the dyadic representation of excitation $\op E_a$ operator (eq. 16) and we have presented an argument to
 demonstrate that the associated excited states $\phi_p^a,\chi_p^a$ are localized only if the condition $\Omega_a<\epsilon_p$ is satisfied. 
 The set of $p$ labels relevant for the construction of a specific excitation depends of the symmetry...

 %The structure of eq. 16 states that when both localized and delocalized excited states partecipate to the excitation

 \item \emph{regarding the localized excitations which can still be found above the IP threshold (Fig 5a), is there any scope to target these, to the exclusion of other states so that a set of just the localizedexcitations can be calculated at reduced computational cost compared to the whole set?}

 Answer using the results for the statical polarizability described in section III.C...

 \item \emph{exclusion ''by design'' of the delocalized part of the excitation spectrum}

 On the base of what written by the referee it seems to me that this sentence could be interpreted in two different way.

 The first one concerns with the removal of the contribution of the delocalized states in a specific excitation. This

 The second one indicate what happens when one uses a basis able to express localized states only...

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-05 AnalyticStructure_main.tex
update

@@
 \section{Introduction}
-\added[id=dal]{Testo nuovo}.
-\deleted[id=dal]{lallero}
 
-Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the 
-computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
-For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
-The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
-other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
-Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
-that a given computational model provides for a specific set of quantities, regardless of their potential agreement with 
-experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
-of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
-employing the same model can be compared.
-
-A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
-where a grassroot community of code-owners struggled to extract well-defined computational results in the context of 
-Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of 
-elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties 
-on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code. 
-Any other code able to extract the same quantities with the same approximations may be compared with the 
-results of the community in order to assess its computational reliability.
+% Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the
+% computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
+% For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
+% The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
+% other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
+% Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
+% that a given computational model provides for a specific set of quantities, regardless of their potential agreement with
+% experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
+% of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
+% employing the same model can be compared.
+% 
+% A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
+% where a grassroot community of code-owners struggled to extract well-defined computational results in the context of
+% Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of
+% elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties
+% on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
+% Any other code able to extract the same quantities with the same approximations may be compared with the
+% results of the community in order to assess its computational reliability.
+% 
+% For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists,
+% reducing the computational uncertainty is the only possible way to shed light on the predictivity power of the
+% model. In other terms, the ``accuracy'' of a result with respect to experimental data may be reliably quantified
+% only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
+% For communities like DFT, such a ``calibration'' of computer codes among each other is a discipline that is still in its infancy;
+% the DeltaCodes initiative and the foundations of DFT are separated in time by more than 50 years, and the computational
+% model employed in the comparison (the Perdew-Burke-Erzerhof functional~\cite{PBE}) has been introduced more than 20 years ago.
 
@@
 only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
-For communities like DFT, such a ``calibration'' of computer codes among each other is a discipline that is still in its infancy;
-the DeltaCodes initiative and the foundations of DFT are separated in time by more than 50 years, and the computational
-model employed in the comparison (the Perdew-Burke-Erzerhof functional~\cite{PBE}) has been introduced more than 20 years ago.
+For communities like DFT, the need of such a ``calibration'' of computer codes has led to the DeltaCodes project~\cite{deltaTest2016}. 
+This project represents a remarkable example of precision-driven initiative where a grassroot community of code-owners struggled to extract 
+well-defined computational results in the context of Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities 
+as lattice constants and bulk modulus of elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
+Any other code able to extract the same quantities with the same approximations may be compared with the
+results of the community in order to assess its computational reliability.
 
@@
 In order to do this, we perform analytic considerations on the equations beyond LR treatment.
+\added[id=dal]{This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalised
+degrees of freedom above a specific energetic threshold.}
 Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility -
-from others that would \emph{explicitly} depend of the employed computational treatment. 
-In particular, we will discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+from others that would \emph{explicitly} depend of the employed computational treatment. \added[id=dal]{Moreover on the basis of this analysis we can assess
+something about the reliability of the results provided by computational setups able to explicit include the presence of delocalised degrees of freedom compared
+to the ones in which these degrees of freedom are excluded by design.}
+\deleted[id=dal]{In particular, we will discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.}
 
@@
 
-Let us start our discussion by revisiting the impact that the Isolated BC have on the 
-solutions of the time-independent Schr\"odinger Equation.
-We here present well-known concepts of quantum mechanics, under a perspective that
-will turn out to be very useful in the forthcoming considerations about linear-response quantities.
+\replaced[id=dal]{Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that
+will turn out to be very useful in the forthcoming considerations about linear-response quantities. In particular we revisit the impact 
+that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation.}{Let us start our discussion by revisiting the 
+impact that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation. We here present well-known concepts of 
+quantum mechanics, under a perspective that will turn out to be very useful in the forthcoming considerations about linear-response quantities.}
 
@@
 $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$.
+\added[id=dal]{Fluctuation states are complex quantities and consequently $\dm'_\Phi(\omega)$ is not hermitian; nonetheless the $\omega$ dependence of \eqref{rhoPrimeFluctuationStateDef1} ensures that the hermitian nature of this operator is recovered in the time domain, as expected.}
+
 An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states (FS) are
@@
 
-It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level 
-that governs the localization properties of the FS.
-As a \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is localized, \textit{i.e.} its evaluation can be
-restricted on a bounded real-space domain.
+\replaced[id=dal]{Equation \eqref{rhoPrimeFluctuationStateDef2} is the convenient starting point to assess the localization properties of the FS as it is easy to see that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.}{It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level
+that governs the localization properties of the FS.}
+As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is \added[id=dal]{spatially} localized, \textit{i.e.} its evaluation can be restricted on a bounded real-space domain.
 Even when such locality argument holds true, for $\omega > |\eps_p|$,
@@
 
-Such locality property of the fluctuation state can be directly confirmed for static perturbations at $\omega=0$.
+\added[id=dal]{Added a subsection for static perturbations}
+
+\subsection{Localized behavior for static perturbations}
+
+The locality property of the fluctuation state can be directly confirmed for static perturbations at $\omega=0$.
 Let us consider a static perturbing operator $\op\Phi_s$ that can be restricted to a finite domain.
@@
 
-\subsection{Strong and weak convergence}
+\added[id=dal]{Modified the name of the subsection}
+
+\subsection{Localization propeties at finite $\omega$. Emergence of a strong and a weak regime}
+
+%\subsection{Strong and weak convergence at finite $\omega$}
 
@@
 
+\added[id=dal]{It is possible to reformulate this type of analysis by directly looking at LR quantities that are defined independently from the perturbing operators and target observables.
+This can be achieved by studying the
+\emph{susceptibility functional}, defined implicitly trough the operator equation}
+\deleted[id=dal]{
 In view of reproducibility, the scalar product of Eq.~\eqref{LinearResponseFunctDef1}, defining the observable fluctuation, may be compared among various numerical treatments.
@@
 with a potential local behavior only for $\omega$ below the ionization threshold. Hence, comparing fluctuation states among diverse numerical treatments would be a
-challenging task.
-
-It is therefore much more interesting to concentrate on LR quantities that are defined independently from the perturbing operators and target observables.
+challenging task.}
+\deleted[id=dal]{It is therefore much more interesting to concentrate on LR quantities that are defined independently from the perturbing operators and target observables.
 This can be achieved by studying the
-\emph{susceptibility functional}, defined implicitly trough the operator equation  
+\emph{susceptibility functional}, defined implicitly trough the operator equation}
 \be\lb{SusceptibilityDef1}
@@
 \ee
+\added[id=dal]{Here add a short justification for the expression of the real and imaginary part of the linear response functional written
+in terms of excitation operators. Principal part vs delta functions.}
 
-\subsection{The analytic structure of linear susceptibility}
+\added[id=dal]{Modified name of the subsection}
+
+\subsection{Localization features of the excitation operators. The analytic structure of linear susceptibility}
+
 Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
@@
 The second sector contains a continuum spectrum of delocalized excitations. The associated states $\ket{\phi_p^a}$ behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
-and are deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
+and are deeply affected by the computational setup used to represent them. In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
 the associated spectrum exhibits an explicit dependence from the size of the domain.

### 2018-11-07 AnalyticStructure_main.tex
update

@@
 \emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantities.
-In order to do this, we perform analytic considerations on the equations beyond LR treatment.
-\added[id=dal]{This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalised
-degrees of freedom above a specific energetic threshold.}
-Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility -
-from others that would \emph{explicitly} depend of the employed computational treatment. \added[id=dal]{Moreover on the basis of this analysis we can assess
-something about the reliability of the results provided by computational setups able to explicit include the presence of delocalised degrees of freedom compared
+In order to do this, we perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - from others that would \emph{explicitly} depend of the employed computational treatment.
+
+\added[id=dal]{This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalized
+degrees of freedom above a specific energetic threshold.
+Moreover on the basis of this analysis we can assess something about the reliability of the results provided by computational setups able to explicit include the presence of delocalized degrees of freedom compared
 to the ones in which these degrees of freedom are excluded by design.}
-\deleted[id=dal]{In particular, we will discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.}
 
@@
 a kinetic $\op T$ and a potential $\op V \equiv \op H - \op T$ term.
-In view of analysing the impact of the BC, it is instructive to transform
+In view of discussing the impact of the BC, it is instructive to transform
 the Schr\"odinger equation in a scattering problem, by writing
@@
 On the other hand, positive energy solutions behave differently.
-Even though the potential is localized, their positive energy are
- spherical waves and the convolution with the source term provides a delocalized wavefunction $\psi(\r)$ in the whole space.
+Even though the potential is localized \replaced[id=dal]{the associated Helmholtz kernel is a spherical wave and its}{, their positive energy are spherical waves and the} convolution with the source term provides a delocalized wavefunction $\psi(\r)$ in the whole space.
 As they cannot be normalized they belong to the essential spectrum of the Hamiltonian operator and form a \emph{continuum} of states.
@@
 \begin{figure}
-\includegraphics[scale=0.6]{Fig2_CO_spectrum.eps}
-\caption{\label{co_spectrum}(Color online) Illustrative LR absorption spectra of the $CO$ molecule in computational setups with different sizes of the simulation domain.
-The value of the IP threshold is indicated by a vertical dashed line.}
+\centering
+\subfloat
+{\includegraphics[scale=0.56]{Fig2a_CO_AlphaOmegaReal.eps}} \\
+\centering
+\subfloat
+{\includegraphics[scale=0.58]{Fig2b_CO_spectrum.eps}}
+\caption{\label{co_spectrum}(Color online) LR dynamical polarizability of the $CO$ molecule in computational setups with different 
+sizes of the simulation domain. The top panel displays the real part and the bottom one the imaginary part. The value of the IP threshold 
+is indicated by a vertical dashed line.}
 \end{figure}
+
+% \begin{figure}
+% \includegraphics[scale=0.6]{Fig2_CO_spectrum.eps}
+% \caption{\label{co_spectrum}(Color online) Illustrative LR absorption spectra of the $CO$ molecule in computational setups with different sizes of the simulation domain. 
+% The value of the IP threshold is indicated by a vertical dashed line.}
+% \end{figure}
 
@@
 The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{BigDFT},
-which employs Daubechies Wavelets as computational basis set.
-Such orthonormal basis presents optimal features of in view of reproducibility of the results,
-and it has proven to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
+that make usage of Daubechies Wavelets as computational basis set.
+This orthonormal basis presents optimal features of in view of reproducibility of the results, and it has proven to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
 

### 2018-11-07 AnalyticStructure_main.tex
update

@@
 
-Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
-entirely defined in the unoccupied subspace.
-In this way we can parametrize, without loss of generality, the excitation operators of the system as:
+\added[id=dal]{The properties of the Liouvillian superoperator $\Liouv$ (sketched in appendix \ref{LiouvillianAction}) imply that both the left and right operator-valued
+eigenstates \eqref{ExcitationOperatorsDef1} satisfy the transverse condition \eqref{RhopTransverseDef1} and can be parametrized as} 
 \begin{align}\lb{ExcitationOperatorsDef2}
@@
 \end{align}
-For each choice of $\{\phi^a_p,\chi^a_p\}_{p \in a}$, these objects represent, respectively, the state in which $\ket{\psi_p}$
-is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
+\added[id=dal]{Each excitation ``mode'' of the system with associated energy $\Omega_a$ is thus described by a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$, defined in the unoccupied subspace.
+These objects represent, respectively, the state in which $\ket{\psi_p}$
+is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.}
+% Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
+% entirely defined in the unoccupied subspace.
+% In this way we can parametrize, without loss of generality, the excitation operators of the system as:
+% \begin{align}\lb{ExcitationOperatorsDef2}
+% \op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
+% \op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;.
+% \end{align}
+% For each choice of $\{\phi^a_p,\chi^a_p\}_{p \in a}$, these objects represent, respectively, the state in which $\ket{\psi_p}$
+% is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
 We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
@@
 The spectrum is symmetric w.r.t the inversion of the eigenvalues
-$\Omega_a \rightarrow -\Omega_a$ and the associated excitation with negative energy are described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.
+$\Omega_a \rightarrow -\Omega_a$ and \replaced[id=dal]{given a specific excitation $\{\phi^a_p,\chi^a_p\}$ the associated solution with opposite  energy is described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.}{the associated excitation with negative energy are described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.}
 We concentrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
@@
 \ee
-We first point out that the Helmholtz kernel associated to the $\ket{\chi^a_p}$ state
+First, we point out that the Helmholtz kernel associated to the $\ket{\chi^a_p}$ state
 contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.
@@
 it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states.
-The typical structure of the excitation landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming a reasonable
-behavior of the perturbed potential $\op V'$.
+The typical structure of the excitation landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming \replaced[id=dal]{that the perturbed potential $\op V'[\op E]$ gives rise to a bound state when applied to $\ket{\psi_p}$.}{a reasonable behavior of the perturbed potential $\op V'$.}
 Below the first ionization energy $|\eps_h|$ only localized excitations are present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the
@@
 For energies higher than $|\eps_1|$ \emph{no localized} excitations are anymore possible,
-regardless of the particular behavior of $\op V'$: the excitation landscape in this region only contains continuum states.
+regardless of the particular behavior of $\op V'$: the excitation landscape in this region \replaced[id=dal]{contains a continuum set of delocalized states.}{only contains continuum states.}
 
@@
 \begin{figure}[ht]
-\includegraphics[scale=0.6]{Fig4_CO_dos.eps}
+\includegraphics[scale=0.6]{Fig4_CO_dos_rev1.eps} %{Fig4_CO_dos.eps}
 \caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$.
@@
 {\label{C6H6_exc}
-\includegraphics[scale=0.58]{Fig5b_C6H6_dos.eps}}
+\includegraphics[scale=0.58]{Fig5b_C6H6_dos_rev1.eps}} %{Fig5b_C6H6_dos.eps}
 \caption{(Color online) Benzene molecule.

### 2018-11-09 AnalyticStructure_main.tex
update

@@
 
+\vspace{1cm}
+\added[id=dal]{A proposal to reorganize the material of the following two subsection B e C in a different way}
+
+\section{Physical relevance of the excitation spectrum. A comparison among localized and continuum sectors}
+
+Comments on the features and the physical relevance of the two sector of the excitation spectrum
+
+\subsection{Localized sector}
+
+\begin{itemize}
+\item It is composed by a genuine set of discrete elements. 
+\item The values of the excitation energies do not depend on the computational setup (observable features) and so can be compared among different approaches. 
+\item The knowledge of this sector of the excitation spectrum allows us to express only the imaginary part of (proper equation that expresses the response functional written using Sokowsky-Plemely
+on the susceptibility functional). 
+\item A computational setup in which delocalized degrees of freedom are excluded by design can in principle describe to this sector in a exact way. 
+\end{itemize}
+
+\subsection{Continuum sector}
+
+\begin{itemize}
+ \item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).
+ \item Deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and the associated spectrum exhibits an explicit dependence from the size of the domain.
+ \item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
+Add examples on the statical polarizability.
+Can we comment
+ \item Make some statements on the features that a computational setup must have to guarantees that this sector provides converged results.
+Difference between systematic and localized basis setup.
+Can we comment about the needs to add ghost atoms for the evaluation of statical polarizability with gaussian basis?
+\end{itemize}
+
+\vspace{1cm}
+
 \subsection{Observable features of the excitation spectrum}
@@
 \begin{align}
-& F_{p\rho}^{q\eta} = (H_{0\rho\eta}-\eps_p\delta_{\rho\eta})\delta_{pq} + U[\decay{\rho}{p};\excite{q}{\eta}] \;,\nn \\
-& D_{p\rho}^{q\eta} = U[\decay{\rho}{p};\decay{\eta}{q}] \;.
+& F_{ps}^{qs'} = (H_{0 ss'}-\eps_p\delta_{ss'})\delta_{pq} + U[\decay{s}{p};\excite{q}{s'}] \;,\nn \\
+& D_{ps}^{qs'} = U[\decay{s}{p};\decay{s'}{q}] \;.
 \end{align}

### 2018-11-11 AnalyticStructure_main.tex
Further modifications. Almoste ready to insert larger molecules in the manuscript

--- 2018-11-07 AnalyticStructure_main.tex
@@
 %\pgfplotsset{compat=1.15}
-\usepackage[markup=underlined]{changes}
+% \usepackage[markup=underline]{changes}
+\usepackage[final]{changes}
 \definechangesauthor{dal}
@@
 \newcommand{\rmat}[1]{\optr R}
-\newcommand{\fscd}[1]{\ket{f_p^\Phi(\omega)^{#1}}}
+\newcommand{\fscd}[1]{\mathrm{Im}\ket{f_p^{\mathbf r_j}(\omega)^{#1}}}
 \newcommand{\GH}{\op G_{\op T}}
@@
 \section{Introduction}
-
-% Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the
-% computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
-% For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
-% The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
-% other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
-% Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
-% that a given computational model provides for a specific set of quantities, regardless of their potential agreement with
-% experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
-% of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
-% employing the same model can be compared.
+\deleted[id=gen]{%
+Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the
+computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
+For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
+The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
+other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
+Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
+that a given computational model provides for a specific set of quantities, regardless of their potential agreement with
+experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
+of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
+employing the same model can be compared.
 %
-% A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
-% where a grassroot community of code-owners struggled to extract well-defined computational results in the context of
-% Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of
-% elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties
-% on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
-% Any other code able to extract the same quantities with the same approximations may be compared with the
-% results of the community in order to assess its computational reliability.
+A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
+where a grassroot community of code-owners struggled to extract well-defined computational results in the context of
+Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of
+elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties
+on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
+Any other code able to extract the same quantities with the same approximations may be compared with the
+results of the community in order to assess its computational reliability.
 %
-% For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists,
-% reducing the computational uncertainty is the only possible way to shed light on the predictivity power of the
-% model. In other terms, the ``accuracy'' of a result with respect to experimental data may be reliably quantified
-% only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
-% For communities like DFT, such a ``calibration'' of computer codes among each other is a discipline that is still in its infancy;
-% the DeltaCodes initiative and the foundations of DFT are separated in time by more than 50 years, and the computational
-% model employed in the comparison (the Perdew-Burke-Erzerhof functional~\cite{PBE}) has been introduced more than 20 years ago.
-
 For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists,
@@
 only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
-For communities like DFT, the need of such a ``calibration'' of computer codes has led to the DeltaCodes project~\cite{deltaTest2016}. 
+For communities like DFT, such a ``calibration'' of computer codes among each other is a discipline that is still in its infancy;
+the DeltaCodes initiative and the foundations of DFT are separated in time by more than 50 years, and the computational
+model employed in the comparison (the Perdew-Burke-Erzerhof functional~\cite{PBE}) has been introduced more than 20 years ago.}
+
+For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists,
+reducing the computational uncertainty is the only possible way to shed light on the predictivity power of the
+model. In other terms, the ``accuracy'' of a result with respect to experimental data may be reliably quantified
+only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
+For communities employing Density Functional Theory (DFT), the need of such a ``calibration'' of computer codes has led to the DeltaCodes project~\cite{deltaTest2016}.
 This project represents a remarkable example of precision-driven initiative where a grassroot community of code-owners struggled to extract
-well-defined computational results in the context of Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities 
+well-defined computational results in the context of DFT calculations. Ground-State quantum mechanical quantities
 as lattice constants and bulk modulus of elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
@@
 \emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantities.
-In order to do this, we perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+\deleted[id=gen]{In order to do this}We perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
 Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - from others that would \emph{explicitly} depend of the employed computational treatment.
@@
 will turn out to be very useful in the forthcoming considerations about linear-response quantities. In particular we revisit the impact
-that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation.}{Let us start our discussion by revisiting the 
+that the Isolated BC have on the solutions of the Schr\"odinger Equation.}{Let us start our discussion by revisiting the
 impact that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation. We here present well-known concepts of
@@
 \ee
-Here we have introduced the set of $\omega$-dependent \emph{fluctuation states}
+Here we have introduced the set of $\omega$-dependent \emph{fluctuation states} (FS)
 $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$.
-\added[id=dal]{Fluctuation states are complex quantities and consequently $\dm'_\Phi(\omega)$ is not hermitian; nonetheless the $\omega$ dependence of \eqref{rhoPrimeFluctuationStateDef1} ensures that the hermitian nature of this operator is recovered in the time domain, as expected.}
-
-An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states (FS) are
+\added[id=gen]{
+However, non-hermiticity of $\dm'_\Phi(\omega)$ implies that the
+fluctuation states are complex quantities. Causality implies that the real and imaginary part of the states are related to each othe by the Kramers-Kronig relations}
+\be\lb{KKrel}
+\mathrm{Re}\left( \ket{f_p^\Phi(\omega)} \right) =
+\mathcal P \int \dd \omega'
+\frac{\mathrm{Im}\left(\ket{f_p^\Phi(\omega')}\right)}{\omega -\omega'}.
+\ee
+\added[id=gen]{We will come to these equations in the forthcoming sections.}
+%}
+
+An analysis of the Liouville equation \eqref{LiouvillianRhopomegaDef1} for the response density written in this fashion evidences that the equations of motion of fluctuation states  are
 written as a modified Sternheimer equation~\cite{mahan1980,giustino2012,giustino2014}
@@
 apart from the perturbing field, a further term $\op V'[\dm'_\Phi]$ due to the density-dependence of $\hnot$.
-It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be casted in the form of
-a set of scattering problems:
+It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be recast in a scattering problem:
 \be\lb{rhoPrimeFluctuationStateDef2}
@@
 once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ -- hence on $\op V'$ and $\Phi$ -- are valid.
-
-\added[id=dal]{Added a subsection for static perturbations}
+\added[id=gen]{These arguments demonstate that for frequencies above the IP threshold energy, the
+response density operator cannot be expressed in terms of localized states. Locality of
+FS (and therefore of $\dm'_\Phi(\omega)$) can be only recovered for frequencies below such threshold.}
+
+\deleted[id=dal]{Added a subsection for static perturbations}
 
 \subsection{Localized behavior for static perturbations}
-
 The locality property of the fluctuation state can be directly confirmed for static perturbations at $\omega=0$.
@@
 \ee
-where $\mathbf d^\text{(GS)}$ is the ground state dipole.
+where $\mathbf d^\text{(GS)}=\braket{\mathbf r}$ is the ground state dipole.
 Fig.~\eqref{co_alphaStatic} illustrates this procedure for a $CO$ molecule
@@
 
-\added[id=dal]{Modified the name of the subsection}
+\deleted[id=dal]{Modified the name of the subsection}
 
@@
 This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response
-density in terms of FS implies that \added[id=dal]{(equation for the response density modified)}
+density in terms of FS implies that \deleted[id=dal]{(equation for the response density modified)}
 % \be\lb{LinearResponseFunctDef2}
@@
 % \ee
-\be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O} = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
-\ee
-Let us suppose that also the observable of interest $\op O$ exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.
+\begin{multline}\lb{LinearResponseFunctDef2}
+\braket{\delta\op O} = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
+=2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
+\end{multline}
+Let us suppose that also the observable of interest $\op O$ \replaced[id=gen]{may be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.}{exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.}
 Once again, it would be enough to consider a local operator for this condition to be met.
 
-We observe that there exists two
-distinct regimes, on the basis of value of $\omega$.
+Two
+distinct regimes can be identified, on the basis of value of $\omega$.
 The first one, which we will refer to as the \emph{below threshold} regime, is realized when
@@
  as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
+ \added[id=gen]{In this regime, a computational treatment based on localized basis set is susceptible to provide a precise answer, assuming a reasonable level of completeness.}
 
@@
 This is naturally achieved in the above mentioned Krylov space treatments, which
-explicitly deal with the expression of the scalar products. However
-it is important that the underlying basis set is able to express delocalised states.
+explicitly deal with the expression of the scalar products.
+\added[id=gen]{However, in this regime, imposing \emph{by design} a localized
+behaviour of the FS might reveal very dangerous in view of convergence of the results:
+the computational basis set have to be able to express in the support domain of $\{\bra{\psi_p}\op O\}$ a asymptotically delocalized FS. The degrees of completeness
+of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalised states.}
 
@@
 \ee
-\added[id=dal]{Here add a short justification for the expression of the real and imaginary part of the linear response functional written
-in terms of excitation operators. Principal part vs delta functions.}
-
-\added[id=dal]{Modified name of the subsection}
+In this way Eq.~\eqref{LinearResponseFunctDef2} may be also written as:
+\begin{equation}\lb{deltaoexc}
+  \braket{\delta \op O} =  \sum_{\{a\}} \frac{\trace{\op O \sop B_a \op \Phi(\omega)}}{\omega -\Omega_a}
+\end{equation}
+where the action of the spectral operator $\sop B_a$ reads
+\begin{equation}
+  \trace{\op O \sop B_a \op \Phi(\omega)} = \trace{\op O \op E_a}
+  \trace{\op{\tilde E}_a \commutator{\dmnot}{\op \Phi(\omega)}}
+\end{equation}
+
+\deleted[id=dal]{Modified name of the subsection}
 
@@
 
+\vspace{1cm}
+\added[id=dal]{A proposal to reorganize the material of the following two subsection B e C in a different way}
+
+\section{Physical relevance of the excitation spectrum. A comparison among localized and continuum sectors}
+\deleted[id=dal]{
+Comments on the features and the physical relevance of the two sector of the excitation spectrum}
+
+%\subsection{Localized sector}
+
+%\begin{itemize}
+% \deleted[id=dal]{\item It is composed by a genuine set of discrete elements.}
+% \deleted[id=dal]{\item The values of the excitation energies do not depend on the computational setup (observable features) and so can be compared among different approaches.}
+% \deleted[id=dal]{\item The knowledge of this sector of the excitation spectrum allows us to express only the imaginary part of (proper equation that expresses the response functional written using Sokowsky-Plemely
+% on the susceptibility functional).}
+% \deleted[id=dal]{\item A computational setup in which delocalized degrees of freedom are excluded by design can in principle describe to this sector in a exact way.}
+%\end{itemize}
+
+\subsection{Continuum sector}
+
+\begin{itemize}
+ \deleted[id=dal]{\item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).}
+ \deleted[id=dal]{\item Deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and the associated spectrum exhibits an explicit dependence from the size of the domain.}
+ \deleted[id=dal]{\item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
+Add examples on the statical polarizability.
+Can we comment}
+ \item Make some statements on the features that a computational setup must have to guarantees that this sector provides converged results.
+Difference between systematic and localized basis setup.
+Can we comment about the needs to add ghost atoms for the evaluation of statical polarizability with gaussian basis?
+\end{itemize}
+
+\vspace{1cm}
+
 \subsection{Observable features of the excitation spectrum}
@@
 converges to its reference value.
+\added[id=gen]{A computational setup in which delocalized degrees of freedom are excluded by design can, in principle, describe excitations of this sector in a exact way.}
 
@@
 the associated spectrum exhibits an explicit dependence from the size of the domain.
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as
-a representation of the density of states (DOS) of the Liouvillian superoperator.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as objects providing an effective representation of the density of states (DOS) of the Liouvillian superoperator.
 
@@
 
-\subsection{Physical relevance of the continuum sector}
-
+\subsection{Relative importance of discrete and continuum excitations}
+\deleted[id=gen]{
 We have presented formal arguments, confirmed by numerical calculations, that show that
@@
 computational setups with sufficient level of completeness are able to
-express with high \emph{precision} such section of the excitation spectrum.
-
+express with high \emph{precision} such section of the excitation spectrum.}
+
+To better understand the interplay between the discrete and continuum sector of
+the excitations, it is interesting to apply the above arguments for the computational extraction of the dynamical polarizability tensor $\alpha_{ij}(\omega)$.
+Employing the formalism of Eq.~\eqref{deltaoexc} we obtain, for its real and imaginary part:
+\begin{align}
+  \mathrm{Im}\left(\alpha_{ij}(\omega) \right) &=
+  \sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a)\\
+   &= 2 \sum_p \bra{\psi_p} \mathbf r_i \left(\mathrm{Im}\ket{f_p^{\mathbf r_j}(\omega)}\right)\;,\\
+  \mathrm{Re}\left(\alpha_{ij}(\omega) \right) &= \mathcal P \int \dd \omega'
+  \frac{\mathrm{Im}\left(\alpha_{ij}(\omega')\right)}{\omega - \omega'} \\
+  & =2 \sum_p \bra{\psi_p} \op O \left(\mathrm{Re}\ket{f_p^\Phi(\omega)}\right)\;.
+\end{align}
+Such equations are in coherency with the Kramers-Kronig relations of the fluctuation states, see Eq.~\eqref{KKrel}.
+The imaginary part of the FS may be decomposed in two quantities:
+
+\deleted[id=gen]{
+Following the considerations of Sec.~\ref{FluctuationState}, we know that
+for $\omega$ below the IP threshold all these quantities may be expressed
+via asymptotically localized states.
 We have also seen in Sec.~\ref{FluctuationState} that
@@
 Considering Eq.~\eqref{SusceptibilityDef1} and
-expressing the spectral decomposition of the linear susceptibility we find:
+expressing the spectral decomposition of the linear susceptibility we find:}
 \be
-\ket{f_p^\Phi(\omega)} = \fscd{D} + \fscd{C}
+\mathrm{Im}\left(\ket{f_p^{\mathbf r_j}(\omega)} \right)= \fscd{D} + \fscd{C}
 \lb{FSExcitationDef1} \;,
@@
 \begin{align}
- \fscd{D} &= \sum_a^{\Omega_a < |\eps_a|} \ket{w_p^a} \frac{\varphi_p^a[\op \Phi(\omega)]}{\omega^2-\Omega_a^2} \;, \nn \\
+ \fscd{D} &= \sum_a^{|\Omega_a| < |\eps_a|} \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn \\
  \fscd{C}
- &= \int_{\Omega_a > |\eps_a|} \!\!\!\!\dd a \ket{w_p^a} \frac{\varphi_p^a[\op \Phi(\omega)]}{\omega^2-\Omega_a^2} \;, \nn
+ &= \int_{|\Omega_a| > |\eps_a|} \!\!\!\!\!\!\!\!\!\!\!\!\!\dd a \ket{w_p^a}  \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn
 \end{align}
-where $\varphi_p^a[\op \Phi(\omega)] \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$,
-and $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
+where %$\varphi_p^a[\op \Phi(\omega)] \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$, and
+$\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
 
@@
 in the spectral decomposition \eqref{SusceptibilityDef1}.
-The summation and the integration run only on the positive values of $\Omega_a$.
+\deleted[id=gen]{The summation and the integration run only on the positive values of $\Omega_a$.}
 The states $\ket{w_p^a}$ that appear in the discrete sum
@@
 character as it is expressed as a sum of localized contributions.
-For $\omega <$ IP, the equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that the integral defining
+
+It is easy to see that for $\omega$ below IP  we have $\fscd{C}=0$.
+Below threshold, continuum excitations \emph{do not} contribute to the imaginary part of the
+dynamical polarizability.
+
+For $\mathrm{Re}\ket{f_p^\Phi(\omega)}$ the situation is slightly more complicated.
+For $\omega <$ IP, we know that the entire FS is localized.
+The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that the integral of the Kramers-Kronig
+relation ~\eqref{KKrel} involving the delocalized states
 $\fscd{C}$ should resum into a localized, asymptotically vanishing state\footnote{There is no particular reason to believe that $\fscd{C}$ should be
@@
 $\fscd{C}=0$ would imply
-$\varphi_p^a[\op \Phi(\omega)]=0$ for any $a$ labelling the continuum excitations,
-which is too strong a condition for a general choice of $\op \Phi$.}.
-
-We may then decompose the linear response functional of Eq.~\eqref{LinearResponseFunctDef1}
-for any operator $\op O$ as $\braket{\delta\op O}_\Phi=\braket{\delta\op O}^D_\Phi +
-\braket{\delta\op O}^C_\Phi$, where
-\be
-\braket{\delta\op O}^{D,C}_\Phi(\omega) =
-2 \mathrm{Re}\left(\bra{\psi_p} \op O \fscd{D,C} \right)\;.
-\ee
-For instance, the static polarizability tensor $\alpha_{ij}$ can be easily expressed
-from the above quantities as
+$\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}$ for any $a$ labelling the continuum excitations, which is too strong a condition.}.
+
+% We may then decompose the linear response functional of Eq.~\eqref{LinearResponseFunctDef1}
+% for any operator $\op O$ as $\braket{\delta\op O}_\Phi=\braket{\delta\op O}^D_\Phi +
+% \braket{\delta\op O}^C_\Phi$, where
+% \be
+% \braket{\delta\op O}^{D,C}_\Phi(\omega) =
+% 2 \bra{\psi_p} \op O \fscd{D,C}\;.
+% \ee
+For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
 \be\lb{sminus2}
-\alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \varphi_p^a[\op r_i]\varphi_p^a[\op r_j]\;.
-\ee
+\alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \bra{\psi_p} \op {\mathbf r}_i \ket{w_p^a}\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}\;.
+\ee
+The summation above runs on both localized and delocalized sector of the excitations.
+
+We also know that $\alpha_{ij}$ might be expressed with arbitrary precision by only employing localized quantities.
 Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as
@@
 
+\subsection{Generality of the considerations: varying the size and the symmetry of the molecule}
+
 Such considerations are independent on the number of atoms of the molecule, as the range in $\omega$ needed to
@@
 For all these computational setups, the $S_{-2}$ sum rule is, on the contrary, perfectly satisfied.
+
+Here we may put other examples
 

### 2018-11-13 AnalyticStructure_main.tex
solved compilation problem

@@
 %\pgfplotsset{compat=1.15}
-% \usepackage[markup=underline]{changes}
-\usepackage[final]{changes}
+\usepackage[markup=underline]{changes}
+%\usepackage[final]{changes}
 \definechangesauthor{dal}
@@
 \begin{itemize}
- \deleted[id=dal]{\item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).}
- \deleted[id=dal]{\item Deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and the associated spectrum exhibits an explicit dependence from the size of the domain.}
- \deleted[id=dal]{\item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
-Add examples on the statical polarizability.
-Can we comment}
    \item Make some statements on the features that a computational setup must have to guarantees that this sector provides converged results.
@@
 Can we comment about the needs to add ghost atoms for the evaluation of statical polarizability with gaussian basis?
+ % \deleted[id=dal]{\item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).}
+ % \deleted[id=dal]{\item Deeply affected by the computational setup used to represent them.
+In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and the associated spectrum exhibits an explicit dependence from the size of the domain.}
+ % \deleted[id=dal]{\item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
+Add examples on the statical polarizability.
+Can we comment}
 \end{itemize}
@@
   \frac{\mathrm{Im}\left(\alpha_{ij}(\omega')\right)}{\omega - \omega'} \\
-  & =2 \sum_p \bra{\psi_p} \op O \left(\mathrm{Re}\ket{f_p^\Phi(\omega)}\right)\;.
+  & =2 \sum_p \bra{\psi_p} \op O \left(\mathrm{Re}\ket{f_p^{\mathbf r_j}(\omega)}\right)\;.
 \end{align}

### 2018-11-14 AnalyticStructure_main.tex
conclusions reworked

@@
 %\pgfplotsset{compat=1.15}
-\usepackage[markup=underline]{changes}
-%\usepackage[final]{changes}
+%\usepackage[markup=underline]{changes}
+\usepackage[final]{changes}
 \definechangesauthor{dal}
@@
 results of the community in order to assess its computational reliability.
-%
-For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists,
-reducing the computational uncertainty is the only possible way to shed light on the predictivity power of the
-model. In other terms, the ``accuracy'' of a result with respect to experimental data may be reliably quantified
-only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
-For communities like DFT, such a ``calibration'' of computer codes among each other is a discipline that is still in its infancy;
-the DeltaCodes initiative and the foundations of DFT are separated in time by more than 50 years, and the computational
-model employed in the comparison (the Perdew-Burke-Erzerhof functional~\cite{PBE}) has been introduced more than 20 years ago.}
+}
 
@@
 However, non-hermiticity of $\dm'_\Phi(\omega)$ implies that the
-fluctuation states are complex quantities. Causality implies that the real and imaginary part of the states are related to each othe by the Kramers-Kronig relations}
-\be\lb{KKrel}
-\mathrm{Re}\left( \ket{f_p^\Phi(\omega)} \right) =
-\mathcal P \int \dd \omega'
-\frac{\mathrm{Im}\left(\ket{f_p^\Phi(\omega')}\right)}{\omega -\omega'}.
-\ee
-\added[id=gen]{We will come to these equations in the forthcoming sections.}
+fluctuation states are complex quantities.}
+%  Causality implies that the real and imaginary part of FS are related each other by the Kramers-Kronig relations}
+% \be\lb{KKrel}
+% \mathrm{Re}\left( \ket{f_p^\Phi(\omega)} \right) =
+% \mathcal P \int \dd \omega'
+% \frac{\mathrm{Im}\left(\ket{f_p^\Phi(\omega')}\right)}{\omega -\omega'}.
+% \ee
+% \added[id=gen]{We will come to these equations in the forthcoming sections.}
 %}
@@
 \begin{multline}\lb{LinearResponseFunctDef2}
-\braket{\delta\op O} = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
+\braket{\delta\op O}(\omega) = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
 =2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
 \end{multline}
+In the second equality we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
 Let us suppose that also the observable of interest $\op O$ \replaced[id=gen]{may be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.}{exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.}
@@
 
-To better understand the interplay between the discrete and continuum sector of
-the excitations, it is interesting to apply the above arguments for the computational extraction of the dynamical polarizability tensor $\alpha_{ij}(\omega)$.
-Employing the formalism of Eq.~\eqref{deltaoexc} we obtain, for its real and imaginary part:
-\begin{align}
-  \mathrm{Im}\left(\alpha_{ij}(\omega) \right) &=
-  \sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a)\\
-   &= 2 \sum_p \bra{\psi_p} \mathbf r_i \left(\mathrm{Im}\ket{f_p^{\mathbf r_j}(\omega)}\right)\;,\\
-  \mathrm{Re}\left(\alpha_{ij}(\omega) \right) &= \mathcal P \int \dd \omega'
-  \frac{\mathrm{Im}\left(\alpha_{ij}(\omega')\right)}{\omega - \omega'} \\
-  & =2 \sum_p \bra{\psi_p} \op O \left(\mathrm{Re}\ket{f_p^{\mathbf r_j}(\omega)}\right)\;.
-\end{align}
-Such equations are in coherency with the Kramers-Kronig relations of the fluctuation states, see Eq.~\eqref{KKrel}.
-The imaginary part of the FS may be decomposed in two quantities:
-
-\deleted[id=gen]{
-Following the considerations of Sec.~\ref{FluctuationState}, we know that
-for $\omega$ below the IP threshold all these quantities may be expressed
-via asymptotically localized states.
-We have also seen in Sec.~\ref{FluctuationState} that
-there exist a sector where the fluctuation states are genuinely localized, thereby presenting reproducibility features. Therefore,
-knowing that $\ket{f_p^\Phi(\omega)} =\sop \chi(\omega) \op \Phi(\omega) \ket{\psi_p}$,
-it would be interesting to obtain information on whether the discrete, localized sector of the excitations which appear in the spectral decomposition of $\sop \chi(\omega)$
-will be sufficient to express a localized FS.
-Considering Eq.~\eqref{SusceptibilityDef1} and
-expressing the spectral decomposition of the linear susceptibility we find:}
-\be
-\mathrm{Im}\left(\ket{f_p^{\mathbf r_j}(\omega)} \right)= \fscd{D} + \fscd{C}
-\lb{FSExcitationDef1} \;,
-\ee
-with
-\begin{align}
- \fscd{D} &= \sum_a^{|\Omega_a| < |\eps_a|} \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn \\
- \fscd{C}
- &= \int_{|\Omega_a| > |\eps_a|} \!\!\!\!\!\!\!\!\!\!\!\!\!\dd a \ket{w_p^a}  \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn
-\end{align}
-where %$\varphi_p^a[\op \Phi(\omega)] \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$, and
-$\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
-
-In the above equation we have explicitly separated the contributions of the discrete ($D$) and continuous ($C$) excitations
-in the spectral decomposition \eqref{SusceptibilityDef1}.
-\deleted[id=gen]{The summation and the integration run only on the positive values of $\Omega_a$.}
-The states $\ket{w_p^a}$ that appear in the discrete sum
-or in the integral are genuinely localized and delocalized, respectively.
-For \emph{any} value of $\omega$ the ket $\fscd{D}$ has, by definition, a bound-state like
-character as it is expressed as a sum of localized contributions.
-
-It is easy to see that for $\omega$ below IP  we have $\fscd{C}=0$.
-Below threshold, continuum excitations \emph{do not} contribute to the imaginary part of the
-dynamical polarizability.
-
-For $\mathrm{Re}\ket{f_p^\Phi(\omega)}$ the situation is slightly more complicated.
-For $\omega <$ IP, we know that the entire FS is localized.
-The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that the integral of the Kramers-Kronig
-relation ~\eqref{KKrel} involving the delocalized states
-$\fscd{C}$ should resum into a localized, asymptotically vanishing state\footnote{There is no particular reason to believe that $\fscd{C}$ should be
-zero. Since $\ket{w_p^a}$ states are linearly independent,
-$\fscd{C}=0$ would imply
-$\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}$ for any $a$ labelling the continuum excitations, which is too strong a condition.}.
+% The sector of localized excitations is therefore potentially interesting
+% in view of reproducibility, as the associated excited states might be represented with arbitrary precision in bounded domains.
+Also the associated excitation energies can be compared among different computational treatments
+% as they are true poles of the linear susceptibility.
+
+We may ask which is the relative importance of the two sectors
+and in particular if there is the possiblity to express observable quantities
+in a suitable $\omega$ range, by only employing the sector of
+genuinely localized excitations.
+Stated otherwise, will the \emph{restriction} $\sop \chi(\omega)$
+to only the localized excitations be useful to some physical quantites?
+
+% To better understand the interplay between the discrete and continuum sector of
+% the excitations,
+
+In this regard it is illustrative to apply the above arguments for the computational extraction of the dynamical polarizability tensor $\alpha_{ij}(\omega)$.
+Employing the formalism of Eq.~\eqref{deltaoexc} we obtain:
+\be%gin{align}
+  \mathrm{Im}\left(\alpha_{ij}(\omega) \right) =
+  \sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a)\lb{imalpha}
+  %\\
+  % &= 2 \sum_p \bra{\psi_p} \mathbf r_i \left(\mathrm{Im}\ket{f_p^{\mathbf r_j}(\omega)}\right)\lb{imfs}\;,
+\ee%nd{align}
+
+The imaginary part of the dynamical polarizability tensor therefore can be
+seen as the partial density of states of the Liouvillian projected on
+$\op{\mathbf r}_i\op{\mathbf r}_j$.
+For this reason, it is evident that below the \emph{first} excitation
+threshold (IP), the contributions to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$
+can be expressed only in terms of observable excited states.
+On the contrary, the non-observable, basis dependent continuum sector of the excitation starts to
+contribute to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$
+above IP; the localized sector
+is not anymore sufficient to express Eq.~\eqref{imalpha} in this $\omega$ range.
+
+% Not surprisingly this behaviour is in coherency with the
+% localization properties of the FS below IP; Eq.~\eqref{imfs} show that
+% for its imaginary part.
+
+%
+% The imaginary part of the FS may be decomposed in two quantities:
+%
+%
+% \deleted[id=gen]{
+% Following the considerations of Sec.~\ref{FluctuationState}, we know that
+% for $\omega$ below the IP threshold all these quantities may be expressed
+% via asymptotically localized states.
+% We have also seen in Sec.~\ref{FluctuationState} that
+% there exist a sector where the fluctuation states are genuinely localized, thereby presenting reproducibility features. Therefore,
+% knowing that $\ket{f_p^\Phi(\omega)} =\sop \chi(\omega) \op \Phi(\omega) \ket{\psi_p}$,
+% it would be interesting to obtain information on whether the discrete, localized sector of the excitations which appear in the spectral decomposition of $\sop \chi(\omega)$
+% will be sufficient to express a localized FS.
+% Considering Eq.~\eqref{SusceptibilityDef1} and
+% expressing the spectral decomposition of the linear susceptibility we find:}
+% \be
+% \mathrm{Im}\left(\ket{f_p^{\mathbf r_j}(\omega)} \right)= \fscd{D} + \fscd{C}
+% \lb{FSExcitationDef1} \;,
+% \ee
+% with
+% \begin{align}
+%  \fscd{D} &= \sum_a^{|\Omega_a| < |\eps_a|} \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn \\
+%  \fscd{C}
+%  &= \int_{|\Omega_a| > |\eps_a|} \!\!\!\!\!\!\!\!\!\!\!\!\!\dd a \ket{w_p^a}  \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn
+% \end{align}
+% where %$\varphi_p^a[\op \Phi(\omega)] \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$, and
+% $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
+%
+% In the above equation we have explicitly separated the contributions of the discrete ($D$) and continuous ($C$) excitations
+% in the spectral decomposition \eqref{SusceptibilityDef1}.
+% \deleted[id=gen]{The summation and the integration run only on the positive values of $\Omega_a$.}
+% The states $\ket{w_p^a}$ that appear in the discrete sum
+% or in the integral are genuinely localized and delocalized, respectively.
+% For \emph{any} value of $\omega$ the ket $\fscd{D}$ has, by definition, a bound-state like
+% character as it is expressed as a sum of localized contributions.
+%
+% It is easy to see that for $\omega$ below IP  we have $\fscd{C}=0$.
+% Below threshold, continuum excitations \emph{do not} contribute to the imaginary part of the
+% dynamical polarizability.
+
+Let us now consider the features of the response density operator of Eq.~\eqref{rhoPrimeFluctuationStateDef1}.
+The fluctuation state in this case can be written as
+\be\lb{fsinexc}
+\ket{f_p^{\mathbf r_j}(\omega)}=
+\sop \chi(\omega) \op{\mathbf r_j} \ket{\psi_p}
+= \sum_a \frac{\bra{w_p^a} \op{\mathbf r_j} \ket{\psi_p}}{\omega^2 - \Omega_a^2}
+\ket{w_p^a}\;.
+\ee
+Here we have employed the notation $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
+The above equation shows that for \emph{any} value of $\omega$ both sectors of localized and delocalized states $\ket{w_p^a}$ contribute.
+However the discussion of Sec.~\ref{FluctuationState} has shown that
+the FS is a genuinely localized state below the IP threshold.
+The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that in this regime the contribution of the delocalized excitations in Eq.~\eqref{fsinexc} has to resum into a localized, asymptotically vanishing FS.
+Such a locality is evident for the imaginary part of the FS, which
+can be straightforwardly restricted to the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}). For the real part of FS the \emph{entire} spectrum
+of excitations contribute.
+
+Hence, contrary to GS, \emph{for LR calculation,
+even when the response density is localized, the contribution coming from the
+continuum sector of the excitations can never be neglected}.
+In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
+in the essential part of the Liouvillian spectrum.
+This fact shows that it is \emph{impossible} to restrict the spectral representation
+of $\chi(\omega)$ to only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
+
+% For $\mathrm{Re}\ket{f_p^{\mathbf r_j}(\omega)}$ the situation is slightly more complicated.
+% \begin{align}
+%   \mathrm{Re}\left(\alpha_{ij}(\omega) \right) &= \mathcal P \int \dd \omega'
+%   \frac{\mathrm{Im}\left(\alpha_{ij}(\omega')\right)}{\omega - \omega'} \\
+%   & =   \sum_{a} \mathcal P  \frac{\trace{\mathbf r_i \sop B_a \mathbf r_j}}{\omega - \Omega_a}\\
+%   & =2 \sum_p \bra{\psi_p} \op O \left(\mathrm{Re}\ket{f_p^{\mathbf r_j}(\omega)}\right)\;.
+% \end{align}
+% Such equations are in coherency with the Kramers-Kronig relations of the fluctuation states, see Eq.~\eqref{KKrel}.
+%
+%
+% For $\omega <$ IP, we know that the FS is localized.
+%
+%
+% The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that the integral of the Kramers-Kronig
+% relation ~\eqref{KKrel} involving the delocalized states
+% $\fscd{C}$ should resum into a localized, asymptotically vanishing state\footnote{There is no particular reason to believe that $\fscd{C}$ should be
+% zero. Since $\ket{w_p^a}$ states are linearly independent,
+% $\fscd{C}=0$ would imply
+% $\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}$ for any $a$ labelling the continuum excitations, which is too strong a condition.}.
 
@@
 % \ee
+
 For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
@@
 \ee
-The summation above runs on both localized and delocalized sector of the excitations.
-
-We also know that $\alpha_{ij}$ might be expressed with arbitrary precision by only employing localized quantities.
+% The summation above runs on both localized and delocalized sector of the excitations.
+%
+% We also know that $\alpha_{ij}$ might be expressed with arbitrary precision by only employing localized quantities.
 Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as
@@
 \end{figure}
-Hence, contrary to GS, \emph{for LR calculation,
-even when the response density is localized, the contribution coming from the
-continuum sector of the excitations can never be neglected}.
-In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
-in the essential part of the Liouvillian spectrum.
-This fact shows that it is \emph{impossible} to restrict the spectral representation
-of $\chi(\omega)$ only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
 
@@
 \section{Conclusions and Perspectives}
-
-By analysing the fundamental equations of LR calculations of molecules, we have shown that the response density for values of $\omega$ above the first IP
-\emph{have} to be expressed in terms of genuinely delocalized states.
-Below this threshold,
+We have performed a critical assessment of the fundamental equations
+that govern the Linear Response theory of molecular systems.
+We have
+%By analysing the fundamental equations of LR calculations of molecules, we have
+shown that the response density for values of $\omega$ above the first IP
+\emph{has} to be expressed in terms of genuinely delocalized states. This
+result
+has relevant consequences in the choice of the  approptiate computational
+basis set to be employed for the LR treatment.
+
+For frequencies below the IP threshold,
 under reasonable assumptions on the perturbing operators,
-the perturbed density operator is genuinely localized.
-In this localized regime, it is possible to achieve convergence of the numerical result
+the response density is genuinely localized.
+In this regime, it is possible to achieve convergence of the numerical result
 by increasing the basis completeness in the same spirit of GS calculations.
-One might expect that more complete basis will give more precise results, regardless of their asymptotic behavior.
-A comparison among various codes in view of reproducibility should therefore be performed
+More complete basis sets will provide more precise results, regardless of their asymptotic behavior.
+A comparison among various computer codes in view of reproducibility should therefore be performed
 initially in this regime.
 
-The situation is not so simple in the above-threshold regime.
-In this case what is important is the matrix element of the observable of interest
-between the bound, occupied state and the fluctuation state (FS).
-The FS is here an unbound, delocalized function, and a numerical treatment tailored for localized functions will \emph{never} be able to discretise such function with arbitrary accuracy.
-To achieve numerical convergence, care should be taken in expressing accurately the FS on the
-appropriate region of space. In view of reproducibility, computational setups which are able to express precisely
-delocalized states seem more interesting in this regime.
-
-Such point of view have also enabled us to shed light on the analytic structure of the
-linear susceptibility, which is an intrinsic property of the molecule and does not depend on
- the perturbing fields.
- In particular, we have concentrated our interest in its spectral representation in
- terms of ``free oscillation'' (i.e. excitations) of the system.
- We have found that \emph{not all} the excitations have to be considered on equal footing.
- As the excitation spectrum has several energy thresholds, one per quasi-particle IP,
- there is a sector of \emph{discrete}, \emph{localized} excitations -- whose energies are
-below the corresponding threshold -- which can be compared among different computational treatments.
-Their energies are \emph{true} poles of the linear susceptibility, the excited states being their residues.
+% The situation is not so simple in the above-threshold regime.
+%In this case what is important is the matrix element of the observable of interest
+%between the bound, occupied state and the fluctuation state (FS).
+%The FS is here an unbound, delocalized function, and a numerical treatment tailored for localized functions will \emph{never} be able to discretise such function with arbitrary accuracy.
+% To achieve numerical convergence, care should be taken in expressing accurately the FS on the
+% appropriate region of space.
+%In view of reproducibility, computational setups which are able to express precisely
+%delocalized states seem more interesting in this regime.
+
+From a computational perspective, a set of localized basis functions,
+which \emph{by design} excludes long-range oscillatory behaviour,
+may be complete enough to express $\sop \chi(\omega)$ \emph{below} IP,
+but it will never be able to capture the entire features of the
+response density operator above the ionization threshold:
+the system's excitations expressed in this basis are reliable \emph{only} in the optical regime. The excitation density of states for $\omega >$ IP
+has to be considered as a effective representation of $\sop \chi(\omega)$
+in order to fulfill Eq.~\eqref{fsinexc}. This fact has been pointed out several times (see e.g. \cite{giustino2012,giustino2014}) in the literature.
+High-energy excitations belong to a continuum sector, which should not be
+confused
+%that embeds the above mentioned discrete excitations.
+%We remark that we are not referring here to
+with the continuum eigenstates of the
+unperturbed GS Hamiltonian.
+% but to the continuum of excitations expressed as eigenstate of the
+% Liouvillian superoperator of Eq.~\eqref{LiouZeroDef1}, needed to
+% express the spectral representation of the linear susceptibility.
+
+On the contrary, computational treatments that are able to express
+delocalized states may be such to describe more efficiently the
+excitations DOS, especially because of the capability of the basis to
+capture oscillatory behaviour. Like in localized basis sets,
+excitations below threshold can be precisely calculated
+with the same paradigm of traditional GS calculations.
+However, in this computational setup, to correctly express
+the linear susceptibility below IP -- more specifically the real part of the fluctuation state -- care should be taken in considering enough delocalised excitations to guarantee fulfillment of sum-rules like Eq.~\eqref{sminus2}.
+
+%
+% Such point of view have also enabled us to shed light on the analytic structure of the
+% linear susceptibility, which is an intrinsic property of the molecule and does not depend on
+%  the perturbing fields.
+%  In particular, we have concentrated our interest in its spectral representation in
+%  terms of ``free oscillation'' (i.e. excitations) of the system.
+%  We have found that \emph{not all} the excitations have to be considered on equal footing.
+%  As the excitation spectrum has several energy thresholds, one per quasi-particle IP,
+%  there is a sector of \emph{discrete}, \emph{localized} excitations -- whose energies are
+% below the corresponding threshold -- which can be compared among different computational treatments.
+% Their energies are \emph{true} poles of the linear susceptibility, the excited states being their residues.
 We can \emph{quantify} the reliability of such discrete energies, as the corresponding excited states may be discretized with arbitrary accuracy on a localized region.
 
-On the other hand, the excitation energies which lie above these thresholds are only pseudo-poles of $\chi(\omega)$,
-and will \emph{strongly} depend on the computational setup. This is visible for energies higher than
-IP, and it has been pointed out several times (see e.g. \cite{giustino2012,giustino2014}) in the literature.
-These excitations belong to a continuum sector that embeds the above mentioned discrete excitations.
-We remark that we are not referring here to the continuum eigenstates of the
-unperturbed GS Hamiltonian,
-but to the continuum of excitations expressed as eigenstate of the
-Liouvillian superoperator of Eq.~\eqref{LiouZeroDef1}, needed to
-express the spectral representation of the linear susceptibility.
-
-Both the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this \emph{even below} the first IP.
+% On the other hand, the excitation energies which lie above these thresholds are only pseudo-poles of $\chi(\omega)$,
+% and will \emph{strongly} depend on the computational setup. This is visible for energies higher than
+% IP, and it has been pointed out several times (see e.g. \cite{giustino2012,giustino2014}) in the literature.
+% These excitations belong to a continuum sector that embeds the above mentioned discrete excitations.
+% We remark that we are not referring here to the continuum eigenstates of the
+% unperturbed GS Hamiltonian,
+% but to the continuum of excitations expressed as eigenstate of the
+% Liouvillian superoperator of Eq.~\eqref{LiouZeroDef1}, needed to
+% express the spectral representation of the linear susceptibility.
+
+Our result show that \emph{both} the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this even below the first IP.
 For generic LR quantities, which are functionals of the linear susceptibility,
@@
 unable to provide convergence for high-energy absorption spectra.
-On the contrary, absorption spectra below IP are relatively easy to converge, as they are observables which depend only on localized quantities.
+%On the contrary,
+Absorption spectra below IP are relatively easy to converge, as they are observables which depend only on localized quantities.
+However, the fulfillment of sum rules like the $S_{-2}$ is not \textit{per se}
+a guarantee of the quality of high energy absorption spectra.
 

### 2018-11-15 Response_referees.tex
update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+List of major changes apported to the paper:
+\begin{itemize}
+ \item The introduction has been deeply revised. In particular we have cut the first two
+ paragraph concerning the differences between accuracy and precision.
+ \item Added a comment after eq. (7) on the non-hermiticity of the response density and corrected
+ the equation (11).
+ \item Added a dedicated subsection (actually the IIA at page 4)  to discuss the localization properties of the FS states for static perturbations. 
+ \item Added a panel in figure 2 that contain the plot of the real part of $\alpha(\omega)$ in calculated in different computational domain. This new plot aims to evidence that the localization
+ properties of th FS affect, on equal footing, both the real and the imaginary part of the linear response functional.
+ \item The relation between localization properties and features of the computational basis needed to provide precise results has been discussed in a stronger way in all the text.
+Major modifications under this perspective have been done in section II before the analysis of fig.
+2 and....
+\end{itemize}
 

### 2018-11-15 AnalyticStructure_main.tex
update

@@
 %\pgfplotsset{compat=1.15}
-%\usepackage[markup=underline]{changes}
-\usepackage[final]{changes}
+\usepackage[markup=underline]{changes}
+%\usepackage[final]{changes}
 \definechangesauthor{dal}
@@
 \section{Introduction}
-\deleted[id=gen]{%
-Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the
-computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
-For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
-The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
-other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
-Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
-that a given computational model provides for a specific set of quantities, regardless of their potential agreement with
-experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
-of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
-employing the same model can be compared.
+
+% Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the
+% computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
+% For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
+% The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
+% other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
+% Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
+% that a given computational model provides for a specific set of quantities, regardless of their potential agreement with
+% experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
+% of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
+% employing the same model can be compared.
 % 
-A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
-where a grassroot community of code-owners struggled to extract well-defined computational results in the context of
-Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of
-elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties
-on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
-Any other code able to extract the same quantities with the same approximations may be compared with the
-results of the community in order to assess its computational reliability.
-}
+% A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
+% where a grassroot community of code-owners struggled to extract well-defined computational results in the context of
+% Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of
+% elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties
+% on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
+% Any other code able to extract the same quantities with the same approximations may be compared with the
+% results of the community in order to assess its computational reliability.
 
@@
 \emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantities.
-\deleted[id=gen]{In order to do this}We perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+We perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
 Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - from others that would \emph{explicitly} depend of the employed computational treatment.
 
-\added[id=dal]{This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalized
-degrees of freedom above a specific energetic threshold.
+This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalized degrees of freedom above a specific energetic threshold.
 Moreover on the basis of this analysis we can assess something about the reliability of the results provided by computational setups able to explicit include the presence of delocalized degrees of freedom compared
-to the ones in which these degrees of freedom are excluded by design.}
+to the ones in which these degrees of freedom are excluded by design.
 
@@
 
-\replaced[id=dal]{Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that
-will turn out to be very useful in the forthcoming considerations about linear-response quantities. In particular we revisit the impact
-that the Isolated BC have on the solutions of the Schr\"odinger Equation.}{Let us start our discussion by revisiting the
-impact that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation. We here present well-known concepts of
-quantum mechanics, under a perspective that will turn out to be very useful in the forthcoming considerations about linear-response quantities.}
+% {Let us start our discussion by revisiting the
+% impact that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation. We here present well-known concepts of
+% quantum mechanics, under a perspective that will turn out to be very useful in the forthcoming considerations about linear-response quantities.}
+Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that
+will turn out to be very useful in the forthcoming considerations about linear-response quantities.
+In particular we revisit the impact that the Isolated BC have on the solutions of the Schr\"odinger Equation.
 
@@
 On the other hand, positive energy solutions behave differently.
-Even though the potential is localized \replaced[id=dal]{the associated Helmholtz kernel is a spherical wave and its}{, their positive energy are spherical waves and the} convolution with the source term provides a delocalized wavefunction $\psi(\r)$ in the whole space.
+Even though the potential is localized the associated Helmholtz kernel is a spherical wave and its convolution with the source term provides a delocalized wavefunction $\psi(\r)$ in the whole space.
 As they cannot be normalized they belong to the essential spectrum of the Hamiltonian operator and form a \emph{continuum} of states.
@@
 $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$.
-\added[id=gen]{
-However, non-hermiticity of $\dm'_\Phi(\omega)$ implies that the
-fluctuation states are complex quantities.}
+However, non-hermiticity of $\dm'_\Phi(\omega)$ implies that the fluctuation states are complex quantities.
 %  Causality implies that the real and imaginary part of FS are related each other by the Kramers-Kronig relations}
@@
 
-\replaced[id=dal]{Equation \eqref{rhoPrimeFluctuationStateDef2} is the convenient starting point to assess the localization properties of the FS as it is easy to see that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.}{It can be seen that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level
-that governs the localization properties of the FS.}
-As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is \added[id=dal]{spatially} localized, \textit{i.e.} its evaluation can be restricted on a bounded real-space domain.
+Equation \eqref{rhoPrimeFluctuationStateDef2} is the convenient starting point to assess the localization properties of the FS as it is easy to see that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.
+As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is spatially localized, \textit{i.e.} its evaluation can be restricted on a bounded real-space domain.
 Even when such locality argument holds true, for $\omega > |\eps_p|$,
@@
 once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ -- hence on $\op V'$ and $\Phi$ -- are valid.
-\added[id=gen]{These arguments demonstate that for frequencies above the IP threshold energy, the
+These arguments demonstrate that for frequencies above the IP threshold energy, the
 response density operator cannot be expressed in terms of localized states. Locality of
-FS (and therefore of $\dm'_\Phi(\omega)$) can be only recovered for frequencies below such threshold.}
-
-\deleted[id=dal]{Added a subsection for static perturbations}
+FS (and therefore of $\dm'_\Phi(\omega)$) can be only recovered for frequencies below such threshold.
 
@@
 
-\deleted[id=dal]{Modified the name of the subsection}
-
-\subsection{Localization propeties at finite $\omega$. Emergence of a strong and a weak regime}
+\subsection{Localization properties at finite $\omega$. Emergence of a strong and a weak regime}
 
@@
 This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response
-density in terms of FS implies that \deleted[id=dal]{(equation for the response density modified)}
-% \be\lb{LinearResponseFunctDef2}
-% \braket{\delta\op O}_\Phi(\omega) = 2 \mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
-% \ee
-\begin{multline}\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
-=2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
-\end{multline}
-In the second equality we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
-Let us suppose that also the observable of interest $\op O$ \replaced[id=gen]{may be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.}{exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.}
+density in terms of FS implies that
+% \begin{align}\lb{LinearResponseFunctDef2}
+% \braket{\delta\op O}_\Phi(\omega) = &\sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \nn \\
+% = &2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;,
+% \end{align}
+\be\lb{LinearResponseFunctDef2}
+\braket{\delta\op O}_\Phi(\omega) = 2 \sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)} \;,
+\ee
+where we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
+Let us suppose that also the observable of interest $\op O$ may be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.
 Once again, it would be enough to consider a local operator for this condition to be met.
@@
 explicitly deal with the expression of the scalar products.
-\added[id=gen]{However, in this regime, imposing \emph{by design} a localized
+However, in this regime, imposing \emph{by design} a localized
 behaviour of the FS might reveal very dangerous in view of convergence of the results:
 the computational basis set have to be able to express in the support domain of $\{\bra{\psi_p}\op O\}$ a asymptotically delocalized FS. The degrees of completeness
-of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalised states.}
+of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalised states
 
@@
 
-As an example in support of these arguments we compare the \replaced[id=dal]{dynamical polarizability $\alpha(\omega)$}{absorption spectrum} of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain.
-Results reported in \replaced[id=dal]{the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
-In all the cases a typical behavior emerges}{evidences a typical behavior}: the curves are almost coincident in the below threshold regime,
+As an example in support of these arguments we compare the dynamical polarizability $\alpha(\omega)$ of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain.
+Results reported in the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
+In all the cases a typical behavior emerges: the curves are almost coincident in the below threshold regime,
 whereas the effect of the computational setup are clearly visible for values of  $\omega$ that exceed the threshold value.
-For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
-which are -- as already noticed -- more than sufficient below threshold.
+For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008}, which are -- as already noticed -- more than sufficient below
+threshold\footnote{Add the convergence domain for the benzene molecule by looking at the results of...}.
 
@@
 
-% \begin{figure}
-% \includegraphics[scale=0.6]{Fig2_CO_spectrum.eps}
-% \caption{\label{co_spectrum}(Color online) Illustrative LR absorption spectra of the $CO$ molecule in computational setups with different sizes of the simulation domain.
-% The value of the IP threshold is indicated by a vertical dashed line.}
-% \end{figure}
-
 \section{Excitation operators. The analytic structure of the susceptibility functional}
 
-\added[id=dal]{It is possible to reformulate this type of analysis by directly looking at LR quantities that are defined independently from the perturbing operators and target observables.
+It is possible to reformulate this type of analysis by directly looking at LR quantities that are defined independently from the perturbing operators and target observables.
 This can be achieved by studying the
-\emph{susceptibility functional}, defined implicitly trough the operator equation}
-\deleted[id=dal]{
-In view of reproducibility, the scalar product of Eq.~\eqref{LinearResponseFunctDef1}, defining the observable fluctuation, may be compared among various numerical treatments.
-However, even though directly related to experimental results, such quantity is not by itself a property of the molecule, as it is a function of $\omega$ that explicitly depends
-on the perturbation operator $\op \Phi$, not to mention the target observable $\op O$. Alternatively, we may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction,
-with a potential local behavior only for $\omega$ below the ionization threshold. Hence, comparing fluctuation states among diverse numerical treatments would be a
-challenging task.}
-\deleted[id=dal]{It is therefore much more interesting to concentrate on LR quantities that are defined independently from the perturbing operators and target observables.
-This can be achieved by studying the
-\emph{susceptibility functional}, defined implicitly trough the operator equation}
+\emph{susceptibility functional}, defined implicitly trough the operator equation
+% In view of reproducibility, the scalar product of Eq.~\eqref{LinearResponseFunctDef1}, defining the observable fluctuation, may be compared among various numerical treatments.
+% However, even though directly related to experimental results, such quantity is not by itself a property of the molecule, as it is a function of $\omega$ that explicitly depends
+% on the perturbation operator $\op \Phi$, not to mention the target observable $\op O$. Alternatively, we may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction,
+% with a potential local behavior only for $\omega$ below the ionization threshold. Hence, comparing fluctuation states among diverse numerical treatments would be a
+% challenging task.
+% It is therefore much more interesting to concentrate on LR quantities that are defined independently from 
+% the perturbing operators and target observables. This can be achieved by studying the \emph{susceptibility
+%functional}, defined implicitly trough the operator equation
 \be\lb{SusceptibilityDef1}
@@
 \ee
-Excitations defined in that way may be considered as a basis of the operators that satisfy the transverse condition as in
-Eq.~\eqref{RhopTransverseDef1}, and enable us to express the susceptibility as a spectral decomposition:
+Excitations defined in that way represent an operator basis that satisfy the transverse condition as in
+Eq.~\eqref{RhopTransverseDef1} (see appendix \ref{LiouvillianAction}), and enable us to express the susceptibility as a spectral decomposition:
 \be\lb{RhopExcitationDef1}

### 2018-11-16 AnalyticStructure_main.tex
introduction and S-2 reworkwd

--- 2018-11-14 AnalyticStructure_main.tex
@@
 
-\added[id=dal]{This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalized
-degrees of freedom above a specific energetic threshold.
+It is indeed relatively easy to have converged indicators for numerical Ground State (GS) quantities: on one side, the variational theorem
+guarantees that the lower the GS energy, the more precise the numerical result;
+on the other side, GS quantities of molecular system  can be expressed
+only in terms of localized (i.e. bound) states. Such considerations make relatively easy the increasing  of the basis set completeness in view of the extraction of reference results.
+
+We will see in what follows that the situation is not as simple in the context of LR.
+Here we will show that the response density -- even for molecular systems -- looses its localized behaviour for high frequencies,
+independently on the nature of the system and of the perturbation.
+Furthermore, we will demonstrate that to increase basis set completeness, delocalized oscillatory degrees of freedom cannot be
+excluded \textit{a priori}, even in the localized regime.
+
+We will also see that the reliabilty of the convergence criteria that can be established for LR -- where no variational theorem exists -- depends explictily on the target frequency range and on the features of the numberical basis set employed.
+
+% This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalized
+% degrees of freedom above a specific energetic threshold.
 Moreover on the basis of this analysis we can assess something about the reliability of the results provided by computational setups able to explicit include the presence of delocalized degrees of freedom compared
-to the ones in which these degrees of freedom are excluded by design.}
+% to the ones in which these degrees of freedom are excluded by design.
 
@@
 
+\subsection{Effective representation of $\sop \chi(\omega)$ for localized response densities}
+The above arguments have shown that the only quantity which can be expressed in terms
+of the localized sector of the excitation spectrum is the imaginary part of the
+susceptibility functional $\sop \chi(\omega)$ in the optical regime (i.e. $\omega <$  IP).
+The response densitites for a generic perturbation and $\omega$ value always require the
+inclusion in the Liouvillian DOS of the delocalized part of the excitation spectrum, even in view of expressing localized fluctuation states.
+
+It appears therefore important to identify indicators that might assess the capability of
+$\sop \chi(\omega)$ to express localised FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
 For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
@@
 in terms of the molecule's oscillator strengths.
-
+In the context of a numerical evaluation of the excitations, such sum rule can therefore interpreted as the capability of the pseudo-continuum sector of the excitation to
+express the localized FS -- and consequently the reference value of $\alpha_{ij}$ -- at $\omega=0$.
+
+We have analized the fullfillment of Eq.~\eqref{sminus2} for moeculs of various
+sizes and symmetries.
 In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison in the case of the $CO$ molecule.
@@
 
-\subsection{Generality of the considerations: varying the size and the symmetry of the molecule}
-
+Present the table of the other results.
+
+Such a scenario can be also found in the other molecules we have considered;
+varying the molecule size and symmetry seems not to modify the qualitative behaviour of the excitation landscape. In addition the
+localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
 Such considerations are independent on the number of atoms of the molecule, as the range in $\omega$ needed to
@@
 a intensive quantity.
-In addition, we can see that the $S_{-2}$ sum-rule \emph{cannot} be used to assess
-the correctness of $\chi(\omega)$ for values of $\omega$ above IP; it is enough to recall
+
+Once again, this proves that, for any numerical treatment,  pseudo-continuum excitations are fundamental in view of a correct expression
+of the response density below IP.
+However, the fulfillement of $S_{-2}$ is not a universal quality indicator of $\chi(\omega)$ as the latter may be still badly represented in the high frequency regime:
+it is enough to recall
 the strong dependency on the box size of the absorption spectra of Fig.~\ref{CO_exc}.
-For all these computational setups, the $S_{-2}$ sum rule is, on the contrary, perfectly satisfied.
-
-Here we may put other examples
+For all these computational setups, the $S_{-2}$ sum rule is, on the contrary, well satisfied.
 
@@
 
-Our result show that \emph{both} the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this even below the first IP.
+Our results show that \emph{both} the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this even below the first IP.
 For generic LR quantities, which are functionals of the linear susceptibility,
@@
 a guarantee of the quality of high energy absorption spectra.
+Moreover, if the basis set employed for the evaluation of the target $\alpha_{ij}$ in  Eq.~\eqref{sminus2} is identical to the one employed for the LR treatment the $S_{-2}$
+is trivially satisfied in the basis. It is therefore important to have a set of reference values
+in the complete basis set limit.
 

### 2018-11-19 AnalyticStructure_main.tex
removed changes and start review of the text

@@
 %\pgfplotsset{compat=1.15}
+
 %\usepackage[markup=underline]{changes}
-\usepackage[final]{changes}
-\definechangesauthor{dal}
-\definechangesauthor{gen}
+%\usepackage[final]{changes}
+%\definechangesauthor{dal}
+%\definechangesauthor{gen}
 
@@
 \section{Introduction}
-\deleted[id=gen]{%
-Since the days of their foundations, disciplines like Computational Physics or Quantum Chemistry always had to deal with the problem of the
-computational reliability of the results. More specifically, a computational result may be considered reliable for various reasons.
-For example, it may be in agreement with some previous observation or measurement that the employed computational model is susceptible to reproduce.
-The model itself may in this way be classified as ``accurate''; it can then be employed to extract, \textit{in silico},
-other quantities that might be then used to \emph{predict} or \emph{interpret} experiments.
-Another concept of reliability is the concept of  ``precision'', which is more focused to the actual results
-that a given computational model provides for a specific set of quantities, regardless of their potential agreement with
-experimental data. The aim of precise computational approach is to reduce the \emph{computational} uncertainties
-of quantities extracted out of a well-defined model, and provide reference results, to which other computer codes
-employing the same model can be compared.
-%
-A recent, remarkable example of precision-driven initiative is provided by the DeltaCodes project~\cite{deltaTest2016},
-where a grassroot community of code-owners struggled to extract well-defined computational results in the context of
-Density Functional Theory (DFT) calculations. Ground-State quantum mechanical quantities as lattice constants and bulk modulus of
-elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties
-on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
-Any other code able to extract the same quantities with the same approximations may be compared with the
-results of the community in order to assess its computational reliability.
-}
 
@@
 In this paper, we focus our attention to Linear-Response treatments of \emph{molecular} systems,
-in particular referring to LR-TDDFT calculation. We will investigate the impact that
-\emph{open} (i.e. Isolated) Boundary Conditions (BC) that have to be imposed to the system will have on the computational evaluation of LR quantities.
-\deleted[id=gen]{In order to do this}We perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+in particular referring to LR-TDDFT calculation.
+We will investigate the impact that \emph{open} (i.e.
+Isolated) Boundary Conditions (BC), that are imposed to the system, will have on the computational evaluation of LR quantities.
+We perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
 Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - from others that would \emph{explicitly} depend of the employed computational treatment.
@@
 It is indeed relatively easy to have converged indicators for numerical Ground State (GS) quantities: on one side, the variational theorem
-guarantees that the lower the GS energy, the more precise the numerical result;
-on the other side, GS quantities of molecular system  can be expressed
-only in terms of localized (i.e. bound) states. Such considerations make relatively easy the increasing  of the basis set completeness in view of the extraction of reference results.
+guarantees that the lower the GS energy, the more precise the numerical result; on the other side, GS quantities of molecular system  can be expressed
+only in terms of localized (i.e. bound) states. These considerations make relatively easy to increase the basis set completeness in view of the extraction of reference results.
 
 We will see in what follows that the situation is not as simple in the context of LR.
-Here we will show that the response density -- even for molecular systems -- looses its localized behaviour for high frequencies,
-independently on the nature of the system and of the perturbation.
-Furthermore, we will demonstrate that to increase basis set completeness, delocalized oscillatory degrees of freedom cannot be
-excluded \textit{a priori}, even in the localized regime.
-
-We will also see that the reliabilty of the convergence criteria that can be established for LR -- where no variational theorem exists -- depends explictily on the target frequency range and on the features of the numberical basis set employed.
+Indeed we will show that the response density -- even for molecular systems -- looses its localized behaviour for high frequencies, independently on the nature of the specific system and perturbation.
+Furthermore, we will demonstrate that to increase the basis set completeness, delocalized oscillatory degrees of freedom cannot be excluded \textit{a priori}, even in the localized regime.
+
+We will also see that the reliabilty of the convergence criteria that can be established for LR -- where no variational theorem exists -- depends explicitly on the target frequency range and on the features of the numerical basis set.
 
@@
 
-\replaced[id=dal]{Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that
-will turn out to be very useful in the forthcoming considerations about linear-response quantities. In particular we revisit the impact
-that the Isolated BC have on the solutions of the Schr\"odinger Equation.}{Let us start our discussion by revisiting the
-impact that the Isolated BC have on the solutions of the time-independent Schr\"odinger Equation. We here present well-known concepts of
-quantum mechanics, under a perspective that will turn out to be very useful in the forthcoming considerations about linear-response quantities.}
+Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that will turn out to be very useful 
+in the forthcoming considerations about linear-response quantities. In particular we revisit the impact that the Isolated BC have on the solutions 
+of the Schr\"odinger Equation.
 
@@
 $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$.
-\added[id=gen]{
 However, non-hermiticity of $\dm'_\Phi(\omega)$ implies that the
-fluctuation states are complex quantities.}
-%  Causality implies that the real and imaginary part of FS are related each other by the Kramers-Kronig relations}
-% \be\lb{KKrel}
-% \mathrm{Re}\left( \ket{f_p^\Phi(\omega)} \right) =
-% \mathcal P \int \dd \omega'
-% \frac{\mathrm{Im}\left(\ket{f_p^\Phi(\omega')}\right)}{\omega -\omega'}.
-% \ee
-% \added[id=gen]{We will come to these equations in the forthcoming sections.}
-%}
+fluctuation states are complex quantities.
 
@@
 once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ -- hence on $\op V'$ and $\Phi$ -- are valid.
-\added[id=gen]{These arguments demonstate that for frequencies above the IP threshold energy, the
-response density operator cannot be expressed in terms of localized states. Locality of
-FS (and therefore of $\dm'_\Phi(\omega)$) can be only recovered for frequencies below such threshold.}
-
-\deleted[id=dal]{Added a subsection for static perturbations}
+These arguments demonstrate that for frequencies above the IP threshold energy, the response density operator cannot be expressed in terms of localized states.
+Locality of FS (and therefore of $\dm'_\Phi(\omega)$) can be only recovered for frequencies below such threshold.
 
@@
 
-\deleted[id=dal]{Modified the name of the subsection}
-
 \subsection{Localization propeties at finite $\omega$. Emergence of a strong and a weak regime}
-
-%\subsection{Strong and weak convergence at finite $\omega$}
 
@@
 are susceptible to exhibit bound-state long-range behavior \emph{only} when $\omega < |\eps_p|$,
-while they behave as unbound states for values of $\omega$ above the threshold levels.
+while they behave as unbound states for values of $\omega$ above these threshold levels.
 This fact has interesting implications in the evaluation of LR quantities. Indeed, writing the response
-density in terms of FS implies that \deleted[id=dal]{(equation for the response density modified)}
-% \be\lb{LinearResponseFunctDef2}
-% \braket{\delta\op O}_\Phi(\omega) = 2 \mathrm{Re} \left(\sum_p \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \;.
-% \ee
-\begin{multline}\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}(\omega) = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
-=2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
-\end{multline}
+density in terms of FS implies that 
+\be\lb{LinearResponseFunctDef2}
+\braket{\delta\op O}_\Phi(\omega) = 2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
+\ee
+% \begin{multline}\lb{LinearResponseFunctDef2}
+% \braket{\delta\op O}_\Phi(\omega) = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
+% =2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
+% \end{multline}
 In the second equality we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
-Let us suppose that also the observable of interest $\op O$ \replaced[id=gen]{may be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.}{exhibits the locality properties introduced for the potentials $ \op V$, $\op \Phi$ and $\op V'$.}
+Let us suppose that also the observable of interest $\op O$ can be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.
 Once again, it would be enough to consider a local operator for this condition to be met.
 
-Two
-distinct regimes can be identified, on the basis of value of $\omega$.
+Two distinct regimes can be identified, on the basis of value of $\omega$.
 The first one, which we will refer to as the \emph{below threshold} regime, is realized when
@@
  as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
- \added[id=gen]{In this regime, a computational treatment based on localized basis set is susceptible to provide a precise answer, assuming a reasonable level of completeness.}
+ In this regime, a computational treatment based on localized basis set is susceptible to provide a precise answer, assuming a reasonable level of completeness.
 
@@
 As by hypothesis $\ket{\op O \psi_p}$ is bound-state like, \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
-In this case a computational description of fluctuation states is only meaningful in ``weak'' sense,
-where the bound state character of $\{\bra{\psi_p}\op O\}$ behaves as a regulator.
-This is naturally achieved in the above mentioned Krylov space treatments, which
-explicitly deal with the expression of the scalar products.
-\added[id=gen]{However, in this regime, imposing \emph{by design} a localized
-behaviour of the FS might reveal very dangerous in view of convergence of the results:
-the computational basis set have to be able to express in the support domain of $\{\bra{\psi_p}\op O\}$ a asymptotically delocalized FS. The degrees of completeness
-of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalised states.}
+In this case a computational description of fluctuation states is only meaningful in ``weak'' sense, where the bound state character of $\{\bra{\psi_p}\op O\}$ behaves as a regulator.
+This is naturally achieved in the above mentioned Krylov space treatments, which explicitly deal with the expression of the scalar products.
+However, in this regime, imposing \emph{by design} a localized behaviour of the FS might reveal very dangerous in view of convergence of the results:
+the computational basis set has to be able to express in the support domain of $\{\bra{\psi_p}\op O\}$ a asymptotically delocalized FS.
+The degrees of completeness of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalized states.
 
@@
 
-As an example in support of these arguments we compare the \replaced[id=dal]{dynamical polarizability $\alpha(\omega)$}{absorption spectrum} of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain.
-Results reported in \replaced[id=dal]{the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
-In all the cases a typical behavior emerges}{evidences a typical behavior}: the curves are almost coincident in the below threshold regime,
+As an example in support of these arguments we compare the {dynamical polarizability $\alpha(\omega)$} of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain.
+Results reported in the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
+In all the cases a typical behavior emerges: the curves are almost coincident in the below threshold regime,
 whereas the effect of the computational setup are clearly visible for values of  $\omega$ that exceed the threshold value.
@@
 
-% \begin{figure}
-% \includegraphics[scale=0.6]{Fig2_CO_spectrum.eps}
-% \caption{\label{co_spectrum}(Color online) Illustrative LR absorption spectra of the $CO$ molecule in computational setups with different sizes of the simulation domain.
-% The value of the IP threshold is indicated by a vertical dashed line.}
-% \end{figure}
-
 \section{Excitation operators. The analytic structure of the susceptibility functional}
 
-\added[id=dal]{It is possible to reformulate this type of analysis by directly looking at LR quantities that are defined independently from the perturbing operators and target observables.
-This can be achieved by studying the
-\emph{susceptibility functional}, defined implicitly trough the operator equation}
-\deleted[id=dal]{
-In view of reproducibility, the scalar product of Eq.~\eqref{LinearResponseFunctDef1}, defining the observable fluctuation, may be compared among various numerical treatments.
-However, even though directly related to experimental results, such quantity is not by itself a property of the molecule, as it is a function of $\omega$ that explicitly depends
-on the perturbation operator $\op \Phi$, not to mention the target observable $\op O$. Alternatively, we may consider only the fluctuation state, but it is still a $\op \Phi$-dependent wavefunction,
-with a potential local behavior only for $\omega$ below the ionization threshold. Hence, comparing fluctuation states among diverse numerical treatments would be a
-challenging task.}
-\deleted[id=dal]{It is therefore much more interesting to concentrate on LR quantities that are defined independently from the perturbing operators and target observables.
-This can be achieved by studying the
-\emph{susceptibility functional}, defined implicitly trough the operator equation}
-\be\lb{SusceptibilityDef1}
-\dm'(\omega) = \left(\omega -\mathcal L \right)^{-1} \commutator{\op \Phi(\omega)}{\dmnot} = \sop{{\cal \chi}}(\omega) \op\Phi(\omega) \;.
-\ee
-The susceptibility (super)operator $\cal \chi(\omega)$ is therefore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined
-from the molecule Hamiltonian $\hnot[\dm]$.
-The ``excitation modes''  of the molecule are defined through the \emph{excitation operators}, satisfying
+It is possible to reformulate this type of analysis by directly looking at LR quantities that are defined independently from the perturbing operators and target observable.
+This can be achieved by studying the \emph{susceptibility functional}, defined implicitly trough the operator equation
 \be\lb{ExcitationOperatorsDef1}
@@
 In this way Eq.~\eqref{LinearResponseFunctDef2} may be also written as:
-\begin{equation}\lb{deltaoexc}
-  \braket{\delta \op O} =  \sum_{\{a\}} \frac{\trace{\op O \sop B_a \op \Phi(\omega)}}{\omega -\Omega_a}
-\end{equation}
+\be\lb{deltaoexc}
+  \braket{\delta \op O} =  \sum_{\{a\}} \frac{\trace{\op O \sop B_a \op \Phi(\omega)}}{\omega -\Omega_a}\;,
+\ee
 where the action of the spectral operator $\sop B_a$ reads
-\begin{equation}
+\be
   \trace{\op O \sop B_a \op \Phi(\omega)} = \trace{\op O \op E_a}
-  \trace{\op{\tilde E}_a \commutator{\dmnot}{\op \Phi(\omega)}}
-\end{equation}
-
-\deleted[id=dal]{Modified name of the subsection}
+  \trace{\op{\tilde E}_a \commutator{\dmnot}{\op \Phi(\omega)}} \;. \nn
+\ee
 
@@
 
-\added[id=dal]{The properties of the Liouvillian superoperator $\Liouv$ (sketched in appendix \ref{LiouvillianAction}) imply that both the left and right operator-valued
-eigenstates \eqref{ExcitationOperatorsDef1} satisfy the transverse condition \eqref{RhopTransverseDef1} and can be parametrized as}
+The properties of the Liouvillian superoperator $\Liouv$ (sketched in appendix \ref{LiouvillianAction}) imply that both the left and right operator-valued
+eigenstates \eqref{ExcitationOperatorsDef1} satisfy the transverse condition \eqref{RhopTransverseDef1} and can be parametrized as
 \begin{align}\lb{ExcitationOperatorsDef2}
@@
 \end{align}
-\added[id=dal]{Each excitation ``mode'' of the system with associated energy $\Omega_a$ is thus described by a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$, defined in the unoccupied subspace.
-These objects represent, respectively, the state in which $\ket{\psi_p}$
-is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.}
-% Each excitation ``mode'' of the system $\op E_a$ with energy $\Omega_a$, can be associated to a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$,
-% entirely defined in the unoccupied subspace.
-% In this way we can parametrize, without loss of generality, the excitation operators of the system as:
-% \begin{align}\lb{ExcitationOperatorsDef2}
-% \op E_a &= \sum_p \left( \ket{\phi^a_p}\bra{\psi_p} + \ket{\psi_p} \bra{\chi^a_p}\right)\;, \nn \\
-% \op{\tilde E}_a = \commutator{\dmnot}{\op E^t_a} &= \sum_p \left( \ket{\psi_p}\bra{\phi^a_p} - \ket{\chi^a_p} \bra{\psi_p}\right)\;.
-% \end{align}
-% For each choice of $\{\phi^a_p,\chi^a_p\}_{p \in a}$, these objects represent, respectively, the state in which $\ket{\psi_p}$
-% is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
-We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2}
-is in general restricted only to a $a$-dependent subset of the occupied orbitals, depending on the particular symmetry
-of the excitation.
-Excited states  satisfy the normalization condition
+Each excitation ``mode'' of the system, with associated energy $\Omega_a$, is thus described by a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$, defined in the unoccupied subspace.
+These objects represent, respectively, the state in which $\ket{\psi_p}$ is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
+We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2} is in general restricted only to a $a$-dependent subset of the occupied orbitals, depending on the particular symmetry
+of the excitation. Excited states  satisfy the normalization condition
 \be\lb{ExcitedStateOrthNormDef1}
@@
 associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).
-The spectrum is symmetric w.r.t the inversion of the eigenvalues
-$\Omega_a \rightarrow -\Omega_a$ and \replaced[id=dal]{given a specific excitation $\{\phi^a_p,\chi^a_p\}$ the associated solution with opposite  energy is described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.}{the associated excitation with negative energy are described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.}
+The spectrum is symmetric w.r.t the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and, given a specific excitation $\{\phi^a_p,\chi^a_p\}$, 
+the associated solution with opposite energy is described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.
 We concentrate our analysis on the sector of positive energies, i.e. $\Omega_a > 0$.
@@
 
-The susceptibility functional has therefore a peculiar analytic structure, that
-is made of multiple threshold energies, one for each of the ionization potentials
-associated to the occupied states.
-If an excitation $\op E_a$ has an energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$,
-it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states.
-The typical structure of the excitation landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming \replaced[id=dal]{that the perturbed potential $\op V'[\op E]$ gives rise to a bound state when applied to $\ket{\psi_p}$.}{a reasonable behavior of the perturbed potential $\op V'$.}
-Below the first ionization energy $|\eps_h|$ only localized excitations are present. Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the
-absolute value of the deepest occupied orbital, other discrete excitations may exist, and are embedded in a continuum of delocalized excitations.
+The susceptibility functional has therefore a peculiar analytic structure made of multiple threshold energies, one for each of the ionization potentials associated to the occupied states.
+If an excitation $\op E_a$ has an energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$, it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states.
+The typical structure of the excitation landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming that the perturbed potential $\op V'[\op E]$ gives rise to a bound state when applied to $\ket{\psi_p}$.
+Below the first ionization energy $|\eps_h|$ only localized excitations are present.
+Conversely, in the intermediate energy interval that extends from $|\eps_h|$ to the absolute value of the deepest occupied orbital, other discrete excitations may exist, and are embedded in a continuum of delocalized excitations.
 For energies higher than $|\eps_1|$ \emph{no localized} excitations are anymore possible,
-regardless of the particular behavior of $\op V'$: the excitation landscape in this region \replaced[id=dal]{contains a continuum set of delocalized states.}{only contains continuum states.}
-
-\vspace{1cm}
-\added[id=dal]{A proposal to reorganize the material of the following two subsection B e C in a different way}
+regardless of the particular behavior of $\op V'$: the excitation landscape in this region contains a continuum set of delocalized states.
 
 \section{Physical relevance of the excitation spectrum. A comparison among localized and continuum sectors}
-\deleted[id=dal]{
-Comments on the features and the physical relevance of the two sector of the excitation spectrum}
-
-%\subsection{Localized sector}
-
-%\begin{itemize}
-% \deleted[id=dal]{\item It is composed by a genuine set of discrete elements.}
-% \deleted[id=dal]{\item The values of the excitation energies do not depend on the computational setup (observable features) and so can be compared among different approaches.}
-% \deleted[id=dal]{\item The knowledge of this sector of the excitation spectrum allows us to express only the imaginary part of (proper equation that expresses the response functional written using Sokowsky-Plemely
-% on the susceptibility functional).}
-% \deleted[id=dal]{\item A computational setup in which delocalized degrees of freedom are excluded by design can in principle describe to this sector in a exact way.}
-%\end{itemize}
-
-\subsection{Continuum sector}
-
-\begin{itemize}
-   \item Make some statements on the features that a computational setup must have to guarantees that this sector provides converged results.
+% \deleted[id=dal]{
+% Comments on the features and the physical relevance of the two sector of the excitation spectrum}
+% 
+% %\subsection{Localized sector}
+% 
+% %\begin{itemize}
+% % \deleted[id=dal]{\item It is composed by a genuine set of discrete elements.}
+% % \deleted[id=dal]{\item The values of the excitation energies do not depend on the computational setup (observable features) and so can be compared among different approaches.}
+% % \deleted[id=dal]{\item The knowledge of this sector of the excitation spectrum allows us to express only the imaginary part of (proper equation that expresses the response functional written using Sokowsky-Plemely
+% % on the susceptibility functional).}
+% % \deleted[id=dal]{\item A computational setup in which delocalized degrees of freedom are excluded by design can in principle describe to this sector in a exact way.}
+% %\end{itemize}
+% 
+% \subsection{Continuum sector}
+% 
+% \begin{itemize}
+%    \item Make some statements on the features that a computational setup must have to guarantees that this sector provides converged results.
 Difference between systematic and localized basis setup.
 Can we comment about the needs to add ghost atoms for the evaluation of statical polarizability with gaussian basis?
- % \deleted[id=dal]{\item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).}
- % \deleted[id=dal]{\item Deeply affected by the computational setup used to represent them.
+%  % \deleted[id=dal]{\item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).}
+%  % \deleted[id=dal]{\item Deeply affected by the computational setup used to represent them.
 In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and the associated spectrum exhibits an explicit dependence from the size of the domain.}
- % \deleted[id=dal]{\item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
+%  % \deleted[id=dal]{\item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
 Add examples on the statical polarizability.
 Can we comment}
-\end{itemize}
-
-\vspace{1cm}
+% \end{itemize}
+% 
+% 
+% \vspace{1cm}
 
@@
 converges to its reference value.
-\added[id=gen]{A computational setup in which delocalized degrees of freedom are excluded by design can, in principle, describe excitations of this sector in a exact way.}
+A computational setup in which delocalized degrees of freedom are excluded by design can, in principle, describe excitations of this sector in a exact way.
 
@@
 \subsection{Relative importance of discrete and continuum excitations}
-\deleted[id=gen]{
-We have presented formal arguments, confirmed by numerical calculations, that show that
-the excitations belonging to the discrete sector of the spectrum have energies
-that can be \emph{quantitatively} compared between codes, thanks to their
-localized character.
-Such objects are LR quantities, associated to the molecule, whose numerical convergence
-can be found by employing techniques which can be borrowed from the ones adopted for GS calculations. Being expressed by localized excited states,
-computational setups with sufficient level of completeness are able to
-express with high \emph{precision} such section of the excitation spectrum.}
-
-% The sector of localized excitations is therefore potentially interesting
-% in view of reproducibility, as the associated excited states might be represented with arbitrary precision in bounded domains.
-Also the associated excitation energies can be compared among different computational treatments
-% as they are true poles of the linear susceptibility.
-
-We may ask which is the relative importance of the two sectors
-and in particular if there is the possiblity to express observable quantities
-in a suitable $\omega$ range, by only employing the sector of
-genuinely localized excitations.
-Stated otherwise, will the \emph{restriction} $\sop \chi(\omega)$
-to only the localized excitations be useful to some physical quantites?
-
-% To better understand the interplay between the discrete and continuum sector of
-% the excitations,
-
-In this regard it is illustrative to apply the above arguments for the computational extraction of the dynamical polarizability tensor $\alpha_{ij}(\omega)$.
-Employing the formalism of Eq.~\eqref{deltaoexc} we obtain:
+% \deleted[id=gen]{
+% We have presented formal arguments, confirmed by numerical calculations, that show that
+% the excitations belonging to the discrete sector of the spectrum have energies
+% that can be \emph{quantitatively} compared between codes, thanks to their
+% localized character.
+% Such objects are LR quantities, associated to the molecule, whose numerical convergence
+% can be found by employing techniques which can be borrowed from the ones adopted for GS calculations. Being expressed by localized excited states,
+% computational setups with sufficient level of completeness are able to
+% express with high \emph{precision} such section of the excitation spectrum.}
+
+So far we have showed with both formal arguments and numerical calculations that the excitation spectrum split into two sectors with very different features.
+It is so reasonable to ask which is the relative importance of these two sectors and in particular if there is the possibility to express observable quantities
+in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
+% We may ask which is the relative importance of the two sectors and in particular if there is the possibility to express observable quantities
+% in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
+Stated otherwise, will the \emph{restriction} of $\sop \chi(\omega)$ to only localized excitations can be useful to extract some physical quantities?
+
+In this regard it is illustrative to apply the above arguments to the evaluation of the dynamical polarizability tensor $\alpha_{ij}(\omega)$.
+Employing the formalism of Eq.~\eqref{deltaoexc} provides
 \be%gin{align}
   \mathrm{Im}\left(\alpha_{ij}(\omega) \right) =
-  \sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a)\lb{imalpha}
+  \sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a)\lb{imalpha} \;.
   %\\
@@
 \ee%nd{align}
-
-The imaginary part of the dynamical polarizability tensor therefore can be
-seen as the partial density of states of the Liouvillian projected on
+The imaginary part of the dynamical polarizability tensor therefore can be seen as the partial density of states of the Liouvillian projected on
 $\op{\mathbf r}_i\op{\mathbf r}_j$.
-For this reason, it is evident that below the \emph{first} excitation
-threshold (IP), the contributions to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$
-can be expressed only in terms of observable excited states.
-On the contrary, the non-observable, basis dependent continuum sector of the excitation starts to
-contribute to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$
-above IP; the localized sector
-is not anymore sufficient to express Eq.~\eqref{imalpha} in this $\omega$ range.
+For this reason, it is evident that below the \emph{first} excitation threshold (IP), the contributions to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$ can be expressed only in terms of observable excited states.
+On the contrary, the non-observable, basis dependent continuum sector of the excitation starts to contribute to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$ above IP; the localized sector is not anymore sufficient to express Eq.~\eqref{imalpha} in this $\omega$ range.
 

### 2018-11-20 Response_referees.tex
text revised and update in the referees report

@@
 \usepackage{amssymb,amsmath}
+\usepackage{mathtools,braket}
 \usepackage[english]{babel}
@@
 \newcommand{\bpi}{\bar{\pi}}
-\newcommand{\bra}{\langle}
-\newcommand{\ket}{\rangle}
-\newcommand{\sst}{\scriptscriptstyle}
 
 \newcommand{\op}[1]{\hat {#1}}
-
-\def\sst{\scriptscriptstyle}
 
@@
 \begin{itemize}
- \item The introduction has been deeply revised. In particular we have cut the first two
- paragraph concerning the differences between accuracy and precision.
- \item Added a comment after eq. (7) on the non-hermiticity of the response density and corrected
- the equation (11).
+ \item Much efforts have been spent in trying to clarify better the relation between localization properties and features of the computational basis needed 
+ to provide precise results.
+This topic has been discussed in all the text.
+Major modifications under this perspective have been done in the introduction, in section II at pag.
+5 before the analysis of fig.
+2,in section IV and in the conclusions.
+ \item The introduction has been deeply revised. In particular we have reduced the length of the first two paragraph concerning the differences between accuracy and precision.
+ \item We added a comment after eq. (7) on the non-hermiticity of the response density and corrected the equation (11).
  \item Added a dedicated subsection (actually the IIA at page 4)  to discuss the localization properties of the FS states for static perturbations. 
@@
  properties of th FS affect, on equal footing, both the real and the imaginary part of the linear response functional.
- \item The relation between localization properties and features of the computational basis needed to provide precise results has been discussed in a stronger way in all the text.
-Major modifications under this perspective have been done in section II before the analysis of fig.
-2 and....
+ \item We have reorganized the material after section III A.
+In particular we have introduced a new section (number IV in the actual version of the paper) in which we have discussed both the physical features of the excitation spectrum and the relative importance of localized vs.
+delocalized sector in expressing the susceptibility functional.
+This section also collects computational results for molecules beyond the case of $CO$ and benzene, already discussed in the previous version of the paper.
 \end{itemize}
@@
 
-We wish to thank the referee for the positive review on the paper. Here we report a list of the modification performed in the text according
-to his/her suggestions:
+We wish to thank the referee for the positive review on the paper. The text has been deeply revised according to the suggestions of both the referees.
+
+Here we report some detailed answer concerning the main aspects raised in the referee's report:
 \begin{enumerate}
-  \item \emph{point concerning the dimension of the simulation box needed to achieve the convergence of the delocalized states of the $CO$ molecule}.
+  \item \emph{on the point concerning the dimension of the simulation box needed to achieve the convergence of the delocalized states of the $CO$ molecule}.
 
-  Clarify that delocalized (fluctuation) states never achieve convergence (continumm collapse).
+  Delocalized fluctuation states do not achieve convergence as long as the simulation box is increased.
+Since they behave as continuum states they suffer of the same continuum collapse behavior described in section IA for the unbound solution of the Schr\"odinger equation.
 What is expected to converge is the spectral function, or declined in the present case the real and imaginary part of the dynamical polarizability.
-To give a reasonable value from the literature we can make usage of the results of achieved by Baroni for the benzene molecule...
-  \item \emph{point concerning the convergence rate of the delocalized vs. localized states (which one? fluctuation or excitation?) with respect
+  The value of convergence is system/observable and perturbation dependent.
+It can be found through an explicit convergence analysis by introducing an acceptance tolerance, however this procedure is out of the scope of our analysis and has not been performed.
+
+  Nonetheless, to have an idea of the dimension of the box needed to achieve convergence we can refer to the case of the Benzene molecule and make usage
+  of the result found in our analysis, compared to the one reporte in fig.
+2 of \cite{baroni2008}.
+Within our analysis we show that a box linear size of about 18 Angostroem is sufficient to produce converged results for excitation spectrum below IP (around 6.5 eV in the present case).
+On the contrary, results of \cite{baroni2008} evidence that to achieve convergence up to 30 eV a box of linear dimension of more than 31 Angstroem is needed, so going from the localized to the delocalized sector of excitation spectrum requires a relevant increase in the simulation domain.
+
+  \item \emph{on the point concerning the convergence rate of the delocalized vs. localized states with respect
   to the grid spacing}
 
- Actually I don't know but I do not expected relevant differences, since localized and delocalized states differ in their asymptotic properties whereas the grid spacing convergence is influenced by the fast oscillation of the functions.
+ In presenting the results of this paper care has been taken to ensures the convergence of the results wrt the computational parameters.
+We have found that there are no relevant difference in the convergence rate of localized vs delocalized quantities (for instance excitations) in function of the grid spacing.
+This is due to the fact that localized and delocalized states differ in their asymptotic properties whereas the grid spacing convergence is influenced by the fast short-range oscillation of the functions.
 
- To present a more detailed answer we could perform a convergence analysis w.r.t the gridspacing looking at the convergence rate of the energies of say 16 virtual orbitals of the $CO$ molecule.
-In this way we can see if the rate of the bound-state ones differs from the others.
+ Add a comment in the text somewhere?
 
- Lastly, the values of the grid spacing used for the calculations have been added in appendix C.
+ The values of the grid spacing used for the calculations have been added in appendix C.
 
-\item Answer to the other minor points...
+\item Other minor corrections:
+\begin{itemize}
+ \item The insets of fig. 4 and 5 have been increased.
+ \item the \emph{reasonable behavior of the perturbed potential} at the end of section IIIA has been clarified. It simply means that the
+ the perturbed potential $\op V'[\op E]$ gives rise to a bound state when applied to $\ket{\psi_p}$.
+ \item explicit reference to the inset of fig. 5 has been performed in the text.
+\end{itemize}
 
@@
 
-We thank the referee for its comment and criticism of the paper.
+We thank the referee for its comment on the paper. Thank to his/her advice and criticism we have tried to clarify our message. 
 We try to answer to the critical points raised out by the review:
@@
 
+\bibliographystyle{elsarticle-num}
+\bibliography{Analytic_biblio}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-20 AnalyticStructure_main.tex
text revised and update in the referees report

@@
 %\pgfplotsset{compat=1.15}
-
-%\usepackage[markup=underline]{changes}
-%\usepackage[final]{changes}
-%\definechangesauthor{dal}
-%\definechangesauthor{gen}
 
@@
 
-\subsection{Localization propeties at finite $\omega$. Emergence of a strong and a weak regime}
+\subsection{Localization properties at finite $\omega$. Emergence of a strong and a weak regime}
 
@@
 \be\lb{LinearResponseFunctDef2}
-\braket{\delta\op O}_\Phi(\omega) = 2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
+\braket{\delta\op O}_\Phi(\omega) = 2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;,
 \ee
@@
 % \end{multline}
-In the second equality we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
+here we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
 Let us suppose that also the observable of interest $\op O$ can be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.
@@
 This can be achieved by studying the \emph{susceptibility functional}, defined implicitly trough the operator equation
+\be\lb{SusceptibilityDef1}
+\dm'(\omega) = \left(\omega -\mathcal L \right)^{-1} \commutator{\op \Phi(\omega)}{\dmnot} = \sop{{\cal \chi}}(\omega) \op\Phi(\omega) \;.
+\ee
+The susceptibility (super)operator $\cal \chi(\omega)$ is therefore closely related to the resolvent of the Liouvillian of Eq.~\eqref{LiouvillianRhopomegaDef1}, which is completely defined
+from the molecule Hamiltonian $\hnot[\dm]$.
+The ``excitation modes''  of the molecule are defined through the \emph{excitation operators}, satisfying
 \be\lb{ExcitationOperatorsDef1}
@@
 Excitations defined in that way may be considered as a basis of the operators that satisfy the transverse condition as in
-Eq.~\eqref{RhopTransverseDef1}, and enable us to express the susceptibility as a spectral decomposition:
+Eq.~\eqref{RhopTransverseDef1}, and enable us to express the susceptibility as a spectral decomposition
 \be\lb{RhopExcitationDef1}
 \sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
-\frac{\trace{\commutator{\op{\tilde E}_a}{\dmnot}\cdot}}{\omega-\Omega_a} \;.
+\frac{\trace{\commutator{\dmnot}{\op{\tilde E}_a}\cdot}}{\omega-\Omega_a} \;.
 \ee
@@
 \ee
-where the action of the spectral operator $\sop B_a$ reads
+where the action of the spectral (super)operator $\sop B_a$ reads
 \be
-  \trace{\op O \sop B_a \op \Phi(\omega)} = \trace{\op O \op E_a}
-  \trace{\op{\tilde E}_a \commutator{\dmnot}{\op \Phi(\omega)}} \;. \nn
-\ee
+  \sop B_a \cdot = \op E_a \trace{\commutator{\dmnot}{\op{\tilde E}_a} \cdot} \;. \nn
+\ee
+
+% \be
+%   \trace{\op O \sop B_a \op \Phi(\omega)} = \trace{\op O \op E_a}
+%   \trace{\op{\tilde E}_a \commutator{\dmnot}{\op \Phi(\omega)}} \;. \nn
+% \ee
 
@@
 Each excitation ``mode'' of the system, with associated energy $\Omega_a$, is thus described by a set of states $\{\phi^a_p,\chi^a_p\}_{p \in a}$, defined in the unoccupied subspace.
-These objects represent, respectively, the state in which $\ket{\psi_p}$ is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\dmnot}{\op E_a}$.
+These objects represent, respectively, the state in which $\ket{\psi_p}$ is excited -- or from whom it decays -- when the system is subject to the \emph{monochromatic} perturbation $\op \Phi_a \equiv \commutator{\op E_a}{\dmnot}$.
 We denote with the shorthand $p \in a$ the fact that the sum of Eq.~\eqref{ExcitationOperatorsDef2} is in general restricted only to a $a$-dependent subset of the occupied orbitals, depending on the particular symmetry
@@
 \section{Physical relevance of the excitation spectrum. A comparison among localized and continuum sectors}
-% \deleted[id=dal]{
-% Comments on the features and the physical relevance of the two sector of the excitation spectrum}
-% 
-% %\subsection{Localized sector}
-% 
-% %\begin{itemize}
-% % \deleted[id=dal]{\item It is composed by a genuine set of discrete elements.}
-% % \deleted[id=dal]{\item The values of the excitation energies do not depend on the computational setup (observable features) and so can be compared among different approaches.}
-% % \deleted[id=dal]{\item The knowledge of this sector of the excitation spectrum allows us to express only the imaginary part of (proper equation that expresses the response functional written using Sokowsky-Plemely
-% % on the susceptibility functional).}
-% % \deleted[id=dal]{\item A computational setup in which delocalized degrees of freedom are excluded by design can in principle describe to this sector in a exact way.}
-% %\end{itemize}
-% 
-% \subsection{Continuum sector}
-% 
-% \begin{itemize}
-%    \item Make some statements on the features that a computational setup must have to guarantees that this sector provides converged results.
-Difference between systematic and localized basis setup.
-Can we comment about the needs to add ghost atoms for the evaluation of statical polarizability with gaussian basis?
-%  % \deleted[id=dal]{\item Not true poles of the susceptibility (but only an effective tool to compute the spectral function).}
-%  % \deleted[id=dal]{\item Deeply affected by the computational setup used to represent them.
-In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and the associated spectrum exhibits an explicit dependence from the size of the domain.}
-%  % \deleted[id=dal]{\item This sector of the excitation spectrum is needed to compute imaginary parts above IP and real part for \emph{all} the values of $\omega$.
-Add examples on the statical polarizability.
-Can we comment}
-% \end{itemize}
-% 
-% 
-% \vspace{1cm}
 
@@
 In addition, for the benzene molecule it is also possible to
-identify excitations of energy above IP that still possess a localized behavior, fulfilling the condition $\Omega_a < |\eps_a|$.
-In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
+identify excitations of energy above IP that still possess a localized behavior, fulfilling the condition $\Omega_a < |\eps_a|$ (see the inset of 
+Fig.~\ref{C6H6_exc}). In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
 the agreement with the expected analytic structure presented in Fig.~\ref{ExcitationLandscape} is remarkable.
@@
 \subsection{Relative importance of discrete and continuum excitations}
-% \deleted[id=gen]{
-% We have presented formal arguments, confirmed by numerical calculations, that show that
-% the excitations belonging to the discrete sector of the spectrum have energies
-% that can be \emph{quantitatively} compared between codes, thanks to their
-% localized character.
-% Such objects are LR quantities, associated to the molecule, whose numerical convergence
-% can be found by employing techniques which can be borrowed from the ones adopted for GS calculations. Being expressed by localized excited states,
-% computational setups with sufficient level of completeness are able to
-% express with high \emph{precision} such section of the excitation spectrum.}
-
-So far we have showed with both formal arguments and numerical calculations that the excitation spectrum split into two sectors with very different features.
-It is so reasonable to ask which is the relative importance of these two sectors and in particular if there is the possibility to express observable quantities
-in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
-% We may ask which is the relative importance of the two sectors and in particular if there is the possibility to express observable quantities
-% in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
+
+So far we have showed with both formal arguments and numerical calculations that the excitation spectrum split into two sectors with very distinct features.
+It is then reasonable to ask which is their relative importance and, in particular, if there is the possibility to express observable quantities, in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
 Stated otherwise, will the \emph{restriction} of $\sop \chi(\omega)$ to only localized excitations can be useful to extract some physical quantities?
@@
 Employing the formalism of Eq.~\eqref{deltaoexc} provides
-\be%gin{align}
+\be\lb{imalpha}
 \mathrm{Im}\left(\alpha_{ij}(\omega) \right) =
-  \sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a)\lb{imalpha} \;.
-  %\\
-  % &= 2 \sum_p \bra{\psi_p} \mathbf r_i \left(\mathrm{Im}\ket{f_p^{\mathbf r_j}(\omega)}\right)\lb{imfs}\;,
-\ee%nd{align}
+\sum_{a} \trace{\mathbf r_i \sop B_a \mathbf r_j} \delta(\omega - \Omega_a) \;.
+\ee
 The imaginary part of the dynamical polarizability tensor therefore can be seen as the partial density of states of the Liouvillian projected on
@@
 
-% Not surprisingly this behaviour is in coherency with the
-% localization properties of the FS below IP; Eq.~\eqref{imfs} show that
-% for its imaginary part.
-
-%
-% The imaginary part of the FS may be decomposed in two quantities:
-%
-%
-% \deleted[id=gen]{
-% Following the considerations of Sec.~\ref{FluctuationState}, we know that
-% for $\omega$ below the IP threshold all these quantities may be expressed
-% via asymptotically localized states.
-% We have also seen in Sec.~\ref{FluctuationState} that
-% there exist a sector where the fluctuation states are genuinely localized, thereby presenting reproducibility features. Therefore,
-% knowing that $\ket{f_p^\Phi(\omega)} =\sop \chi(\omega) \op \Phi(\omega) \ket{\psi_p}$,
-% it would be interesting to obtain information on whether the discrete, localized sector of the excitations which appear in the spectral decomposition of $\sop \chi(\omega)$
-% will be sufficient to express a localized FS.
-% Considering Eq.~\eqref{SusceptibilityDef1} and
-% expressing the spectral decomposition of the linear susceptibility we find:}
-% \be
-% \mathrm{Im}\left(\ket{f_p^{\mathbf r_j}(\omega)} \right)= \fscd{D} + \fscd{C}
-% \lb{FSExcitationDef1} \;,
+To further address this point we exploit the formal relation between response density and susceptibility functional %established in ~\eqref{SusceptibilityDef1} 
+$\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the diadic representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
+Pursuing this procedure provides the excitation-based
+representation of FS as follows:
+% Let us now consider the features of the response density operator of Eq.~\eqref{rhoPrimeFluctuationStateDef1}.
+% The fluctuation state in this case can be written as
+% \be\lb{fsinexc}
+% \ket{f_p^{\mathbf r_j}(\omega)}=
+% \sop \chi(\omega) \op{\mathbf r_j} \ket{\psi_p}
+% = \sum_a \frac{\bra{w_p^a} \op{\mathbf r_j} \ket{\psi_p}}{\omega^2 - \Omega_a^2}
+% \ket{w_p^a}\;,
 % \ee
-% with
-% \begin{align}
-%  \fscd{D} &= \sum_a^{|\Omega_a| < |\eps_a|} \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn \\
-%  \fscd{C}
-%  &= \int_{|\Omega_a| > |\eps_a|} \!\!\!\!\!\!\!\!\!\!\!\!\!\dd a \ket{w_p^a}  \ket{w_p^a} \bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a} \delta\left(\omega-\Omega_a\right) \;, \nn
-% \end{align}
-% where %$\varphi_p^a[\op \Phi(\omega)] \equiv \bra{\psi_p}\op\Phi(\omega)\ket{w_p^a}$, and
-% $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
-%
-% In the above equation we have explicitly separated the contributions of the discrete ($D$) and continuous ($C$) excitations
-% in the spectral decomposition \eqref{SusceptibilityDef1}.
-% \deleted[id=gen]{The summation and the integration run only on the positive values of $\Omega_a$.}
-% The states $\ket{w_p^a}$ that appear in the discrete sum
-% or in the integral are genuinely localized and delocalized, respectively.
-% For \emph{any} value of $\omega$ the ket $\fscd{D}$ has, by definition, a bound-state like
-% character as it is expressed as a sum of localized contributions.
-%
-% It is easy to see that for $\omega$ below IP  we have $\fscd{C}=0$.
-% Below threshold, continuum excitations \emph{do not} contribute to the imaginary part of the
-% dynamical polarizability.
-
-Let us now consider the features of the response density operator of Eq.~\eqref{rhoPrimeFluctuationStateDef1}.
-The fluctuation state in this case can be written as
 \be\lb{fsinexc}
 \ket{f_p^{\mathbf r_j}(\omega)}=
-\sop \chi(\omega) \op{\mathbf r_j} \ket{\psi_p}
-= \sum_a \frac{\bra{w_p^a} \op{\mathbf r_j} \ket{\psi_p}}{\omega^2 - \Omega_a^2}
-\ket{w_p^a}\;.
-\ee
-Here we have employed the notation $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
-The above equation shows that for \emph{any} value of $\omega$ both sectors of localized and delocalized states $\ket{w_p^a}$ contribute.
-However the discussion of Sec.~\ref{FluctuationState} has shown that
-the FS is a genuinely localized state below the IP threshold.
+\sum_a \frac{\bra{w_p^a} \op{\mathbf r_j} \ket{\psi_p}}{\omega^2 - \Omega_a^2}
+\ket{w_p^a}\;,
+\ee
+where we have employed the notation $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
+%The above equation shows that for \emph{any} value of $\omega$ both sectors of localized and delocalized states $\ket{w_p^a}$ contribute.
+The above equation shows that both the sectors of localized and delocalized states $\ket{w_p^a}$ contribute to the FS for \emph{any} value of $\omega$.
+However the discussion of Sec.~\ref{FluctuationState} has shown that the FS is a genuinely localized state below the IP threshold.
 The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that in this regime the contribution of the delocalized excitations in Eq.~\eqref{fsinexc} has to resum into a localized, asymptotically vanishing FS.
-Such a locality is evident for the imaginary part of the FS, which
-can be straightforwardly restricted to the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}). For the real part of FS the \emph{entire} spectrum
-of excitations contribute.
-
-Hence, contrary to GS, \emph{for LR calculation,
-even when the response density is localized, the contribution coming from the
+% Such a locality is evident for the imaginary part of the FS, which can be straightforwardly restricted to the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
+For the real part of FS the \emph{entire} spectrum
+% of excitations contribute.
+The localization below threshold is manifest for the imaginary part of the FS, that is explicitly written as a the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
+Instead, for the real part of FS, the \emph{entire} excitation spectrum contributes to the construction of the FS and the localization
+\emph{has} to realize due to a non trivial cancellation of the unbound parts of the $\ket{w_p^a}$'s.
+
+Hence, contrary to GS, we conclude that \emph{for LR calculation, even when the response density is localized, the contribution coming from the
 continuum sector of the excitations can never be neglected}.
-In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection
-in the essential part of the Liouvillian spectrum.
-This fact shows that it is \emph{impossible} to restrict the spectral representation
-of $\chi(\omega)$ to only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
-
-% For $\mathrm{Re}\ket{f_p^{\mathbf r_j}(\omega)}$ the situation is slightly more complicated.
-% \begin{align}
-%   \mathrm{Re}\left(\alpha_{ij}(\omega) \right) &= \mathcal P \int \dd \omega'
-%   \frac{\mathrm{Im}\left(\alpha_{ij}(\omega')\right)}{\omega - \omega'} \\
-%   & =   \sum_{a} \mathcal P  \frac{\trace{\mathbf r_i \sop B_a \mathbf r_j}}{\omega - \Omega_a}\\
-%   & =2 \sum_p \bra{\psi_p} \op O \left(\mathrm{Re}\ket{f_p^{\mathbf r_j}(\omega)}\right)\;.
-% \end{align}
-% Such equations are in coherency with the Kramers-Kronig relations of the fluctuation states, see Eq.~\eqref{KKrel}.
-%
-%
-% For $\omega <$ IP, we know that the FS is localized.
-%
-%
-% The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that the integral of the Kramers-Kronig
-% relation ~\eqref{KKrel} involving the delocalized states
-% $\fscd{C}$ should resum into a localized, asymptotically vanishing state\footnote{There is no particular reason to believe that $\fscd{C}$ should be
-% zero. Since $\ket{w_p^a}$ states are linearly independent,
-% $\fscd{C}=0$ would imply
-% $\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}$ for any $a$ labelling the continuum excitations, which is too strong a condition.}.
-
-% We may then decompose the linear response functional of Eq.~\eqref{LinearResponseFunctDef1}
-% for any operator $\op O$ as $\braket{\delta\op O}_\Phi=\braket{\delta\op O}^D_\Phi +
-% \braket{\delta\op O}^C_\Phi$, where
-% \be
-% \braket{\delta\op O}^{D,C}_\Phi(\omega) =
-% 2 \bra{\psi_p} \op O \fscd{D,C}\;.
+In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection in the essential part of the Liouvillian spectrum.
+This fact shows that it is \emph{impossible} to restrict the spectral representation of $\chi(\omega)$ to only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
+
+\subsection{Effective representation of $\sop \chi(\omega)$ for localized response densities}
+The above arguments have shown that the only quantity which can be expressed in terms of the localized sector of the excitation spectrum is the imaginary part of the susceptibility functional $\sop \chi(\omega)$ in the optical regime (i.e.
+$\omega <$  IP).
+The response density for a generic perturbation and $\omega$ value requires the inclusion in the Liouvillian DOS of the delocalized part of the excitation spectrum, even in view of expressing localized fluctuation states.
+
+A given numerical treatment typically provides only an effective description of the sector of delocalized excitation which in turns give rise to an effective 
+representation of the susceptibility functional. It appears therefore important to identify indicators that enable us to validate the capability
+of $\sop \chi(\omega)$ to express the localised FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
+%It appears therefore important to identify indicators that might assess the capability of
+%$\sop \chi(\omega)$ to express localised FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
+For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
+% \be\lb{sminus2}
+% \alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \bra{\psi_p} \op {\mathbf r}_i \ket{w_p^a}\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}\;.
 % \ee
-
-\subsection{Effective representation of $\sop \chi(\omega)$ for localized response densities}
-The above arguments have shown that the only quantity which can be expressed in terms
-of the localized sector of the excitation spectrum is the imaginary part of the
-susceptibility functional $\sop \chi(\omega)$ in the optical regime (i.e. $\omega <$  IP).
-The response densitites for a generic perturbation and $\omega$ value always require the
-inclusion in the Liouvillian DOS of the delocalized part of the excitation spectrum, even in view of expressing localized fluctuation states.
-
-It appears therefore important to identify indicators that might assess the capability of
-$\sop \chi(\omega)$ to express localised FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
-For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
 \be\lb{sminus2}
-\alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \bra{\psi_p} \op {\mathbf r}_i \ket{w_p^a}\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}\;.
-\ee
-% The summation above runs on both localized and delocalized sector of the excitations.
-%
-% We also know that $\alpha_{ij}$ might be expressed with arbitrary precision by only employing localized quantities.
+\alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} |\bra{\psi_p} \op {\mathbf r}_i \ket{w_p^a}|^2 \;.
+\ee
 Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as
@@
 Such a scenario can be also found in the other molecules we have considered;
-varying the molecule size and symmetry seems not to modify the qualitative behaviour of the excitation landscape. In addition the
+varying the molecule size and symmetry seems not to modify the qualitative behavior of the excitation landscape. In addition the
 localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
@@
 \section{Conclusions and Perspectives}
-We have performed a critical assessment of the fundamental equations
-that govern the Linear Response theory of molecular systems.
-We have
-%By analysing the fundamental equations of LR calculations of molecules, we have
-shown that the response density for values of $\omega$ above the first IP
-\emph{has} to be expressed in terms of genuinely delocalized states. This
-result
-has relevant consequences in the choice of the  approptiate computational
-basis set to be employed for the LR treatment.
-
-For frequencies below the IP threshold,
-under reasonable assumptions on the perturbing operators,
-the response density is genuinely localized.
-In this regime, it is possible to achieve convergence of the numerical result
-by increasing the basis completeness in the same spirit of GS calculations.
+
+We have performed a critical assessment of the fundamental equations that govern the Linear Response theory of molecular systems.
+We have shown that the response density for values of $\omega$ above the first IP \emph{has} to be expressed in terms of genuinely delocalized states. 
+This result has relevant consequences in the choice of the  appropriate computational basis set to be employed for the LR treatment.
+
+For frequencies below the IP threshold, under reasonable assumptions on the perturbing operators, the response density is genuinely localized.
+In this regime, it is possible to achieve convergence of the numerical result by increasing the basis completeness in the same spirit of GS calculations.
 More complete basis sets will provide more precise results, regardless of their asymptotic behavior.
-A comparison among various computer codes in view of reproducibility should therefore be performed
-initially in this regime.
-
-% The situation is not so simple in the above-threshold regime.
-%In this case what is important is the matrix element of the observable of interest
-%between the bound, occupied state and the fluctuation state (FS).
-%The FS is here an unbound, delocalized function, and a numerical treatment tailored for localized functions will \emph{never} be able to discretise such function with arbitrary accuracy.
-% To achieve numerical convergence, care should be taken in expressing accurately the FS on the
-% appropriate region of space.
-%In view of reproducibility, computational setups which are able to express precisely
-%delocalized states seem more interesting in this regime.
-
-From a computational perspective, a set of localized basis functions,
-which \emph{by design} excludes long-range oscillatory behaviour,
-may be complete enough to express $\sop \chi(\omega)$ \emph{below} IP,
-but it will never be able to capture the entire features of the
-response density operator above the ionization threshold:
-the system's excitations expressed in this basis are reliable \emph{only} in the optical regime. The excitation density of states for $\omega >$ IP
-has to be considered as a effective representation of $\sop \chi(\omega)$
-in order to fulfill Eq.~\eqref{fsinexc}. This fact has been pointed out several times (see e.g. \cite{giustino2012,giustino2014}) in the literature.
-High-energy excitations belong to a continuum sector, which should not be
-confused
-%that embeds the above mentioned discrete excitations.
-%We remark that we are not referring here to
-with the continuum eigenstates of the
-unperturbed GS Hamiltonian.
-% but to the continuum of excitations expressed as eigenstate of the
-% Liouvillian superoperator of Eq.~\eqref{LiouZeroDef1}, needed to
-% express the spectral representation of the linear susceptibility.
-
-On the contrary, computational treatments that are able to express
-delocalized states may be such to describe more efficiently the
-excitations DOS, especially because of the capability of the basis to
-capture oscillatory behaviour. Like in localized basis sets,
-excitations below threshold can be precisely calculated
-with the same paradigm of traditional GS calculations.
-However, in this computational setup, to correctly express
-the linear susceptibility below IP -- more specifically the real part of the fluctuation state -- care should be taken in considering enough delocalised excitations to guarantee fulfillment of sum-rules like Eq.~\eqref{sminus2}.
-
-%
-% Such point of view have also enabled us to shed light on the analytic structure of the
-% linear susceptibility, which is an intrinsic property of the molecule and does not depend on
-%  the perturbing fields.
-%  In particular, we have concentrated our interest in its spectral representation in
-%  terms of ``free oscillation'' (i.e. excitations) of the system.
-%  We have found that \emph{not all} the excitations have to be considered on equal footing.
-%  As the excitation spectrum has several energy thresholds, one per quasi-particle IP,
-%  there is a sector of \emph{discrete}, \emph{localized} excitations -- whose energies are
-% below the corresponding threshold -- which can be compared among different computational treatments.
-% Their energies are \emph{true} poles of the linear susceptibility, the excited states being their residues.
-We can \emph{quantify} the reliability of such discrete energies, as the corresponding excited states may be discretized with arbitrary accuracy on a localized region.
-
-% On the other hand, the excitation energies which lie above these thresholds are only pseudo-poles of $\chi(\omega)$,
-% and will \emph{strongly} depend on the computational setup. This is visible for energies higher than
-% IP, and it has been pointed out several times (see e.g. \cite{giustino2012,giustino2014}) in the literature.
-% These excitations belong to a continuum sector that embeds the above mentioned discrete excitations.
-% We remark that we are not referring here to the continuum eigenstates of the
-% unperturbed GS Hamiltonian,
-% but to the continuum of excitations expressed as eigenstate of the
-% Liouvillian superoperator of Eq.~\eqref{LiouZeroDef1}, needed to
-% express the spectral representation of the linear susceptibility.
+A comparison among various computer codes in view of reproducibility should therefore be performed initially in this regime.
+
+From a computational perspective, a set of localized basis functions, which \emph{by design} excludes long-range oscillatory behaviour, may be complete 
+enough to express $\sop \chi(\omega)$ \emph{below} IP, but it will never be able to capture the entire features of the response density operator above 
+the ionization threshold: the system's excitations expressed in this basis are reliable \emph{only} in the optical regime. 
+High-energy excitations belong to a continuum sector (which should not be confused with the continuum eigenstates of the unperturbed GS Hamiltonian)
+and the excitation density of states for $\omega >$ IP provided by this type of basis-set has to be considered as a effective representation of $\sop \chi(\omega)$ in order to fulfill Eq.~\eqref{fsinexc}.
+This fact has been pointed out several times (see e.g.
+\cite{giustino2012,giustino2014}) in the literature.
+
+On the contrary, computational treatments that are able to express delocalized states may be such to describe more efficiently the excitations DOS, 
+especially because of the capability of the basis to capture oscillatory behavior. Like in localized basis sets, excitations below threshold can be 
+precisely calculated with the same paradigm of traditional GS calculations.
+However, in this computational setup, to correctly express the linear susceptibility below IP -- more specifically the real part of the fluctuation state -- care should be taken in considering enough delocalized excitations
+to guarantee fulfillment of sum-rules like Eq.~\eqref{sminus2}.
 
@@
 
-We believe that these considerations, based on simple manipulations on the fundamental LR equations, will help in increase
-the reliability of LR calculations in the community, and in building test-sets that would help in
-the \emph{calibration} of present and future computer codes, thereby increasing the predictivity of present-day theoretical approaches.
-The example of the static polarizability of molecules
+We believe that these considerations, based on simple manipulations on the fundamental LR equations, will help in increase the reliability of LR 
+calculations in the community, and in building test-sets that would help in the \emph{calibration} of present and future computer codes, thereby 
+increasing the predictivity of present-day theoretical approaches. The example of the static polarizability of molecules
 presents ideal features as an initial playground. Work is ongoing in this direction.
@@
 \op O_\parallel &\equiv \dmnot \op O \dmnot + \op Q_0 \op O \op Q_0 \nn \;,\\
-\op O_\perp &\equiv \dmnot \op O \op Q_0 + \dmnot \op O \op Q_0 =
+\op O_\perp &\equiv \dmnot \op O \op Q_0 +  \op Q_0 \op O \dmnot =
 \commutator{\dmnot}{\commutator{\dmnot}{\op O}} \;,
@@
 
-The projection $\op O_\perp$ is therefore the relevant part for the commutator:
+The projection $\op O_\perp$ is therefore the relevant part for the commutator
 \begin{equation}
 \commutator{\dmnot}{\op O} = \commutator{\dmnot}{\op O_\perp} =
-\dmnot \op O \op Q_0  - \dmnot \op O \op Q_0 \;.
+\dmnot \op O \op Q_0  - \op Q_0 \op O \dmnot  \;,
 \end{equation}
-The Liouvillian superoperator is therefore constructed such as $\Liouv \op O = \Liouv O_\perp$. In addition, the image operator satisfies the transverse condition
+consequently the Liouvillian superoperator, which contains by definition a commutator with $\hnot$ and $\dmnot$ in its bare and coupling part, is constructed such as $\Liouv \op O = \Liouv O_\perp$.
+In addition, the image operator satisfies the transverse condition
 $\left( \Liouv \op O \right)_\parallel =0$.

### 2018-11-21 Response_referees.tex
updated text and referee report

@@
 
-Here we report some detailed answer concerning the main aspects raised in the referee's report:
+Here we report the detailed answers concerning the main aspects raised in the referee's report:
 \begin{enumerate}
@@
 
- In presenting the results of this paper care has been taken to ensures the convergence of the results wrt the computational parameters.
+ In presenting the results of this paper care has been taken to ensure the convergence of the results wrt the computational parameters.
 We have found that there are no relevant difference in the convergence rate of localized vs delocalized quantities (for instance excitations) in function of the grid spacing.
@@
 
-We thank the referee for its comment on the paper. Thank to his/her advice and criticism we have tried to clarify our message. 
-We try to answer to the critical points raised out by the review:
+We thank the referee for his/her comment on the paper.
+The text has been deeply revised according to the suggestions of both the referees.
+To ease the comparison with the previous version a list of the major modifications apported to the paper is included in this report.
+
+We answer to the critical points raised out in the report of the referee:
 
 \begin{enumerate}
- \item \emph{on the relevance of the symmetry of the molecule in determining the delocalized vs localized character of the an excitation}
 
- In the paper we have introduced a the dyadic representation of excitation $\op E_a$ operator (eq. 16) and we have presented an argument to
- demonstrate that the associated excited states $\phi_p^a,\chi_p^a$ are localized only if the condition $\Omega_a<\epsilon_p$ is satisfied. 
- The set of $p$ labels relevant for the construction of a specific excitation depends of the symmetry...
+ \item \emph{On the localized sector of excitation. Dependence on the symmetry and dimension of the molecule.}
 
- %The structure of eq. 16 states that when both localized and delocalized excited states partecipate to the excitation
+ In section IIIA we have provided formal arguments that evidence that the excitation spectrum splits into two sectors with distinct features. The first one
+ is composed by a finite set of localized excitations with discrete eigenvalues, whereas the second one contains a continuum spectrum of delocalized objects.
+ For excitation energies lower than the ionization potential (IP) of the molecule all the excitations belong to the first sector.
+In the intermediate energy range which goes from IP to the absolute value of the energy of the deepest occupied orbital the two sectors compenetrate so that there are localized excitation embedded in a continuum of delocalized ones, and finally only elements of the second sector exist for higher values of the energy.
 
- \item \emph{regarding the localized excitations which can still be found above the IP threshold (Fig 5a), is there any scope to target these, to the exclusion of other states so that a set of just the localizedexcitations can be calculated at reduced computational cost compared to the whole set?}
+ These formal results have been supported by numerical calculations in which the excitation spectrum of several molecules has been explicitly computed.
+%through the diagonalization using a systematic (wavelet) basis)
+ The attribution of each excitation of the appropriate sector passes through the evaluation of the norm of the states $\phi_p^a$ and $\chi_p^a$ that build
+ the diadic representation of the excitation (see eq. 17). Only states with norm greater than a given tolerance value are considered and the associated 
+ excitation is attributed to the first sector if the condition $\Omega_a < |\epsilon_p|$ with $\epsilon_a = \mathrm{max}\left(\epsilon_p\right)_{p\in a}$.
+ This computational procedure provides results in optimum agreement with the formal arguments reported above. Indeed the excitation landscape of 
+ (for instace the panel a o fig. 5 for the case of Benzene) evidences the presence of discrete excitations (the black bullets) embedded in a pseudo-continuum 
+ represented by the blue filled square.
+Moreover the comparison between the excitation DOS computed in different computational domain shows that this way of labeling the excitation is correct since the elements attributed to the localized sector have energies that easily converge with respect to the increase of the simulation box, as expected.
 
- Answer using the results for the statical polarizability described in section III.C...
+ In the previous version of the paper this type of analysis was limited to the case of $CO$ and Benzene molecules.
+However the same structure of the excitation spectrum is quite general and turns out not to be affected by the size or symmetry of the molecule.
+To check this statement we have repeated
+ the same computational analysis for several other molecules of different shape and dimension like the Fullerene and the Aflatoxin. Results for this studies 
+ are presented as supplementary materials. Looking at the excitation landscape for these cases (extracted with the same procedure and tolerance parameters?) it...
 
- \item \emph{exclusion ''by design'' of the delocalized part of the excitation spectrum}
+\item \emph{Regarding the localized excitations which can still be found above the IP threshold (Fig 5a), is there any scope to target these, to the
+exclusion of other states, so that a set of just the localized excitations can be calculated at reduced computational cost compared to the whole set?}
 
- On the base of what written by the referee it seems to me that this sentence could be interpreted in two different way.
+ During the review process we have deeply revised the final part of the paper (in particular the section IVB in the actual version of the manuscript) in order to clarify which is the relevance the two excitation sectors for obtaining an effective representation of the susceptibility functional.
 
- The first one concerns with the removal of the contribution of the delocalized states in a specific excitation. This
+ \item \emph{On the exclusion ''by design'' of the delocalized part of the excitation spectrum}
 
- The second one indicate what happens when one uses a basis able to express localized states only...
+ ......................
+
+%  \vspace{2cm}
+%  
+%  
+%  \item \emph{on the relevance of the symmetry and dimension of the molecule in determining the delocalized vs localized character of the an excitation}
+%  
+%  In the paper we have introduced a the dyadic representation of excitation $\op E_a$ operator (eq. 16) and we have presented an argument to
+%  demonstrate that the associated excited states $\phi_p^a,\chi_p^a$ are localized only if the condition $\Omega_a<\epsilon_p$ is satisfied. 
+%  The set of $p$ labels relevant for the construction of a specific excitation depends of the symmetry...
+%  
+%  %The structure of eq. 16 states that when both localized and delocalized excited states partecipate to the excitation 
+%  
+%  \item \emph{regarding the localized excitations which can still be found above the IP threshold (Fig 5a), is there any scope to target these, to the exclusion of other states so that a set of just the localizedexcitations can be calculated at reduced computational cost compared to the whole set?}
+% 
+%  
+%  Answer using the results for the statical polarizability described in section III.C...
+%  
+% 
+%  
+%  On the base of what written by the referee it seems to me that this sentence could be interpreted in two different way. 
+%  
+%  The first one concerns with the removal of the contribution of the delocalized states in a specific excitation. This  
+%  
+%  The second one indicate what happens when one uses a basis able to express localized states only...
+%
 

### 2018-11-21 AnalyticStructure_main.tex
updated text and referee report

@@
 
-On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, realized for $\omega>|\eps_h|$, in which fluctuation
-states start behaving as unbound wave functions.
-As by hypothesis $\ket{\op O \psi_p}$ is bound-state like, \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} can be evaluated in a localized domain.
-In this case a computational description of fluctuation states is only meaningful in ``weak'' sense, where the bound state character of $\{\bra{\psi_p}\op O\}$ behaves as a regulator.
-This is naturally achieved in the above mentioned Krylov space treatments, which explicitly deal with the expression of the scalar products.
-However, in this regime, imposing \emph{by design} a localized behaviour of the FS might reveal very dangerous in view of convergence of the results:
-the computational basis set has to be able to express in the support domain of $\{\bra{\psi_p}\op O\}$ a asymptotically delocalized FS.
-The degrees of completeness of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalized states.
+On the contrary, the computation of the linear response functional can be much more demanding in the \emph{above threshold regime}, 
+realized for $\omega>|\eps_h|$, in which fluctuation states start behaving as unbound wave functions.
+As by hypothesis $\ket{\op O \psi_p}$ is bound-state like, \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2} 
+can be evaluated in a localized domain. In this case a computational description of fluctuation states is only meaningful in ``weak'' 
+sense, where the bound state character of $\bra{\psi_p\op O}$ behaves as a regulator. This is naturally achieved in the above mentioned 
+Krylov space treatments, which explicitly deal with the expression of the scalar products. However, in this regime, imposing \emph{by design} 
+a localized behaviour of the FS might reveal very dangerous in view of convergence of the results since the computational basis set has 
+to be able to express a delocalized FS in the support domain of $\bra{\psi_p\op O}$ . 
+This fact implies that the degrees of completeness of the computational basis should therefore be increased by adding the necessary degrees
+of freedom for describe the FS in all the relevant domain. Stated otherwise, in order to achieve precise results in in this regime the 
+underlying basis set has to able to express delocalized states.
+%The degrees of completeness of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to 
+%represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalized states.
 

### 2018-11-22 Response_referees.tex
paper review and update referee report

@@
 This section also collects computational results for molecules beyond the case of $CO$ and benzene, already discussed in the previous version of the paper.
+ \item State something about the inclusion of other molecules...
 \end{itemize}
@@
  These formal results have been supported by numerical calculations in which the excitation spectrum of several molecules has been explicitly computed.
-%through the diagonalization using a systematic (wavelet) basis)
  The attribution of each excitation of the appropriate sector passes through the evaluation of the norm of the states $\phi_p^a$ and $\chi_p^a$ that build
- the diadic representation of the excitation (see eq. 17). Only states with norm greater than a given tolerance value are considered and the associated 
+ the dyadic representation of the excitation (see eq. 17). Only states with norm greater than a given tolerance value are considered and the associated 
  excitation is attributed to the first sector if the condition $\Omega_a < |\epsilon_p|$ with $\epsilon_a = \mathrm{max}\left(\epsilon_p\right)_{p\in a}$.
@@
  are presented as supplementary materials. Looking at the excitation landscape for these cases (extracted with the same procedure and tolerance parameters?) it...
+ to be completed after the inclusion of the table.....
 
@@
  During the review process we have deeply revised the final part of the paper (in particular the section IVB in the actual version of the manuscript) in order to clarify which is the relevance the two excitation sectors for obtaining an effective representation of the susceptibility functional.
+
+ For a sake of concreteness this analysis has been declined for the relevant case of the computation of the dynamical polarizability. It emerges that the localized
+ sector of excitation is sufficient to express the imaginary part of $\alpha(\omega)$ \emph{only} for values of $\omega$ below IP (see eq. 21). The evaluation of
+ other quantities, namely $\mathrm{Im}(\alpha(\omega))$ above IP or $\mathrm{Re}(\alpha(\omega))$ in all the $\omega$ range requires a relevant contribution from
+ both the sectors of excitation spectrum.
+So, to answer to the question raised by the referee we can state that localized excitations above IP can be isolated and computed using the procedure described in the previous point of this report, but their knowledge alone is not useful to extract any physical quantities.
+ We can state that the multi-threshold structure of the excitation spectrum is surely interesting but is not very relevant for computational purposes.
 

### 2018-11-22 AnalyticStructure_main.tex
paper review and update referee report

@@
 This fact implies that the degrees of completeness of the computational basis should therefore be increased by adding the necessary degrees
-of freedom for describe the FS in all the relevant domain. Stated otherwise, in order to achieve precise results in in this regime the 
+of freedom for describe the FS in all the relevant domain. Stated otherwise, to achieve precise results in this regime the 
 underlying basis set has to able to express delocalized states.
@@
 To further address this point we exploit the formal relation between response density and susceptibility functional %established in ~\eqref{SusceptibilityDef1} 
-$\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the diadic representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
+$\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the dyadic representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
 Pursuing this procedure provides the excitation-based
@@
 \end{equation}
-consequently the Liouvillian superoperator, which contains by definition a commutator with $\hnot$ and $\dmnot$ in its bare and coupling part, is constructed such as $\Liouv \op O = \Liouv O_\perp$.
-In addition, the image operator satisfies the transverse condition
+consequently the Liouvillian superoperator, which contains by definition a commutator with $\hnot$ and $\dmnot$ in its unperturbed and coupling part respectively,
+is constructed such as $\Liouv \op O = \Liouv O_\perp$. In addition, the image operator satisfies the transverse condition
 $\left( \Liouv \op O \right)_\parallel =0$.

### 2018-11-26 AnalyticStructure_main.tex
added linguistic revision of the paper

@@
 Let us now inspect the case of LR calculations.
-In this framework one consider the unperturbed Hamiltonian $\hnot$ and assume that
+In this framework one considers the unperturbed Hamiltonian $\hnot$ and assumes that
 the GS density $\dmnot$ is accessible and expressed in a given computational treatment.
@@
 are similar to the ones usually employed for GS calculations.
-The convergence in this regime is ``strong'', in the sense that the basis functions employed enables us to express
+The convergence in this regime is ``strong'', in the sense that the basis functions employed enable us to express
 with arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
@@
 In all the cases a typical behavior emerges: the curves are almost coincident in the below threshold regime,
-whereas the effect of the computational setup are clearly visible for values of  $\omega$ that exceed the threshold value.
+whereas the effects of the computational setup are clearly visible for values of  $\omega$ that exceed the threshold value.
 For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
@@
 Thus we can conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute
--- if localized -- a genuine \emph{discrete} set, while the ones in the unbound energy range behaves as generalized eigenvectors associated to a
+-- if localized -- a genuine \emph{discrete} set, while the ones in the unbound energy range behave as generalized eigenvectors associated to a
 continuum spectrum.
@@
 
-So far we have showed with both formal arguments and numerical calculations that the excitation spectrum split into two sectors with very distinct features.
+So far we have showed with both formal arguments and numerical calculations that the excitation spectrum splits into two sectors with very distinct features.
 It is then reasonable to ask which is their relative importance and, in particular, if there is the possibility to express observable quantities, in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
-Stated otherwise, will the \emph{restriction} of $\sop \chi(\omega)$ to only localized excitations can be useful to extract some physical quantities?
+Stated otherwise, can the \emph{restriction} of $\sop \chi(\omega)$ to only localized excitations be useful to extract some physical quantities?
 
@@
 
-A given numerical treatment typically provides only an effective description of the sector of delocalized excitation which in turns give rise to an effective 
+A given numerical treatment typically provides only an effective description of the sector of delocalized excitation which in turns gives rise to an effective 
 representation of the susceptibility functional. It appears therefore important to identify indicators that enable us to validate the capability
@@
 described in Sec.~\ref{FluctuationState}.
-This is the well-know $S_{-2}$ sum-rule (see e.g.\cite{Wagner2012}), that express the value of the static polarizability
+This is the well-know $S_{-2}$ sum-rule (see e.g.\cite{Wagner2012}), that expresses the value of the static polarizability
 in terms of the molecule's oscillator strengths.
-In the context of a numerical evaluation of the excitations, such sum rule can therefore interpreted as the capability of the pseudo-continuum sector of the excitation to
+In the context of a numerical evaluation of the excitations, such sum rule can therefore be interpreted as the capability of the pseudo-continuum sector of the excitation to
 express the localized FS -- and consequently the reference value of $\alpha_{ij}$ -- at $\omega=0$.
 
-We have analized the fullfillment of Eq.~\eqref{sminus2} for moeculs of various
+We have analized the fullfillment of Eq.~\eqref{sminus2} for molecules of various
 sizes and symmetries.
@@
 achieve satisfactory agreement is largely above the last valence ionization threshold, which is
-a intensive quantity.
+an intensive quantity.
 
@@
 \ee
-The contribution of the coupling operator in the equations of motion of excited states can expressed by means of the coupling kernel \eqref{CouplingKernelDef1} as
+The contribution of the coupling operator in the equations of motion of excited states can be expressed by means of the coupling kernel \eqref{CouplingKernelDef1} as
 \begin{align}
@@
 \end{align}
-Give that we employ real functions both for $p$ and $s$ is real we also have $\excite{p}{s}(\r,\r') = \decay{s}{p}(\r',\r)$ and the density operator is symmetric in $\r \leftrightarrow \r'$.
+Given that we employ real functions both for $p$ and $s$ is real we also have $\excite{p}{s}(\r,\r') = \decay{s}{p}(\r',\r)$ and the density operator is symmetric in $\r \leftrightarrow \r'$.
 These conditions applied together imply that $U[\excite{p}{s};\excite{q}{s'}] = U[\decay{s}{p};\decay{s'}{q}]$, as well as $U[\decay{s}{p};\excite{q}{s'}] = U[\excite{p}{s};\decay{s'}{q}]$,
@@
 The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{BigDFT},
-that make usage of Daubechies Wavelets as computational basis set.
-This orthonormal basis presents optimal features of in view of reproducibility of the results, and it has proven to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
+that makes usage of Daubechies Wavelets as computational basis set.
+This orthonormal basis presents optimal features in view of reproducibility of the results, and it has proved to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
 
 For Ground State results, the important parameters in the context of convergence of the calculations are the spacing of the wavelet grid and the size of the simulation domain: for bound-state like functions, convergence is achieved by reducing the grid spacing and increasing the simulation box size.
-Norm Conserving Pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proven to be able to provide all-electron accuracy for molecular systems.
+Norm Conserving Pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proved to be able to provide all-electron accuracy for molecular systems.
 
@@
 220 states have been computed in each setup and the corresponding
-energy reange for the unoccupied states is 16.9, 11.6 and 9.7 eV.
+energy range for the unoccupied states is 16.9, 11.6 and 9.7 eV.
 

### 2018-11-28 AnalyticStructure_main.tex
corrected paper and added excitation table

@@
 Such considerations may be transposed in terms of the molecule's excited states. We show that not all the system's excitations can be considered on equal footing.
-There is a discrete sector of excitations -- which may extend above IP -- that can be parametrized by observable, localized states, which can be computationally expressed with high precision, provided an adequate level of completeness.
+There is a discrete sector of excitations -- which may also extend above IP -- that can be parametrized by observable, localized states, which can be computationally expressed with high precision, provided an adequate level of completeness.
 We present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated
@@
 
-Equation \eqref{rhoPrimeFluctuationStateDef2} is the convenient starting point to assess the localization properties of the FS as it is easy to see that, for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.
+From equation \eqref{rhoPrimeFluctuationStateDef2} we see that
+%is the convenient starting point to assess the localization properties of the FS as it is easy to see that,
+for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.
 As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is spatially localized, \textit{i.e.} its evaluation can be restricted on a bounded real-space domain.
@@
 once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ -- hence on $\op V'$ and $\Phi$ -- are valid.
+
 These arguments demonstrate that for frequencies above the IP threshold energy, the response density operator cannot be expressed in terms of localized states.
@@
 to be able to express a delocalized FS in the support domain of $\bra{\psi_p\op O}$ .
-This fact implies that the degrees of completeness of the computational basis should therefore be increased by adding the necessary degrees
-of freedom for describe the FS in all the relevant domain. Stated otherwise, to achieve precise results in this regime the 
-underlying basis set has to able to express delocalized states.
+This fact implies that the degrees of completeness of the computational basis should be increased by adding
+the oscillatory degrees of freedom needed to describe the FS in the relevant domain.
+Stated otherwise, to achieve precise results in this regime the
+underlying basis set has to be able to express delocalized states.
 %The degrees of completeness of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to
@@
 \be\lb{RhopExcitationDef1}
-\sop{{\cal \chi}}(\omega) \cdot   = \sum_{\{a\}} \op E_{a} \,
-\frac{\trace{\commutator{\dmnot}{\op{\tilde E}_a}\cdot}}{\omega-\Omega_a} \;.
+\sop{{\cal \chi}}(\omega) = \sum_{\{a\}} \,
+\frac{\sop B_a}{\omega-\Omega_a} \;,
+\ee
+where the action of the spectral (super)operator $\sop B_a$ reads
+\be\lb{spectralop}
+  \sop B_a \cdot = \op E_a \trace{\commutator{\dmnot}{\op{\tilde E}_a} \cdot} \;. \nn
 \ee
@@
   \braket{\delta \op O} =  \sum_{\{a\}} \frac{\trace{\op O \sop B_a \op \Phi(\omega)}}{\omega -\Omega_a}\;,
-\ee
-where the action of the spectral (super)operator $\sop B_a$ reads
-\be
-  \sop B_a \cdot = \op E_a \trace{\commutator{\dmnot}{\op{\tilde E}_a} \cdot} \;. \nn
 \ee
@@
 If any of these hypothesis does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
-Furthermore, excited states are subjected to the orthonormalization condition
+Furthermore, excited states undergo the orthonormalization condition
 \eqref{ExcitedStateOrthNormDef1} that acts as a ulterior constraint and has the effect of determining the \emph{quantization}
@@
 
-The second sector contains a continuum spectrum of delocalized excitations. The associated states $\ket{\phi_p^a}$ behave as the unbound virtual orbitals analyzed in \cite{boffi2016}
+The second sector contains a continuum spectrum of delocalized excitations.
+The associated states $\ket{\phi_p^a}$ behave as the unbound virtual orbitals analyzed in \cite{boffi2016} (see Sec.\ref{SEopenSystem})
 and are deeply affected by the computational setup used to represent them. In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
 the associated spectrum exhibits an explicit dependence from the size of the domain.
-Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as objects providing an effective representation of the density of states (DOS) of the Liouvillian superoperator.
+Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as objects providing an effective representation of the density of states (DOS) of the Liouvillian superoperator, by means of the spectral operators $\sop B_a$ of Eq.~\eqref{spectralop}.
 
@@
 $\op{\mathbf r}_i\op{\mathbf r}_j$.
-For this reason, it is evident that below the \emph{first} excitation threshold (IP), the contributions to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$ can be expressed only in terms of observable excited states.
+For this reason, it is evident that below the \emph{first} excitation threshold (IP), the contributions to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$ can be expressed only in terms of localized, thus observable, excited states.
 On the contrary, the non-observable, basis dependent continuum sector of the excitation starts to contribute to $\mathrm{Im}\left(\alpha_{ij}(\omega)\right)$ above IP; the localized sector is not anymore sufficient to express Eq.~\eqref{imalpha} in this $\omega$ range.
@@
 To further address this point we exploit the formal relation between response density and susceptibility functional %established in ~\eqref{SusceptibilityDef1}
-$\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the dyadic representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
+$\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
 Pursuing this procedure provides the excitation-based
@@
 \ket{f_p^{\mathbf r_j}(\omega)}=
-\sum_a \frac{\bra{w_p^a} \op{\mathbf r_j} \ket{\psi_p}}{\omega^2 - \Omega_a^2}
+\sum_a \frac{\bra{w_p^a} \op{\mathbf r}_j \ket{\psi_p}}{\omega^2 - \Omega_a^2}
 \ket{w_p^a}\;,
@@
 where we have employed the notation $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
+This is the well-known equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility,
+that is always valid in any computational basis set provided the the full spectrum of excited states (including the pseudo-continuum ones) is considered.
 %The above equation shows that for \emph{any} value of $\omega$ both sectors of localized and delocalized states $\ket{w_p^a}$ contribute.
@@
 However the discussion of Sec.~\ref{FluctuationState} has shown that the FS is a genuinely localized state below the IP threshold.
-The equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility implies that in this regime the contribution of the delocalized excitations in Eq.~\eqref{fsinexc} has to resum into a localized, asymptotically vanishing FS.
+The equivalence implies that in this regime the contribution of the delocalized excitations in Eq.~\eqref{fsinexc} has to resum into a localized, asymptotically vanishing FS.
 % Such a locality is evident for the imaginary part of the FS, which can be straightforwardly restricted to the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
@@
 % of excitations contribute.
-The localization below threshold is manifest for the imaginary part of the FS, that is explicitly written as a the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
-Instead, for the real part of FS, the \emph{entire} excitation spectrum contributes to the construction of the FS and the localization
-\emph{has} to realize due to a non trivial cancellation of the unbound parts of the $\ket{w_p^a}$'s.
+The localization below threshold is manifest for the imaginary part of the FS, that is explicitly written as the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
+Instead, for the real part of FS, the \emph{entire} excitation spectrum contributes to the construction of the FS,
+which has to be interpreted as a localized wavepacket in the basis of the pseudo-continuum excitations.
+% and the localization
+%\emph{has} to realize due to a non trivial cancellation of the unbound parts of the $\ket{w_p^a}$'s.
 
@@
 continuum sector of the excitations can never be neglected}.
-In other terms, we \emph{cannot} exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection in the essential part of the Liouvillian spectrum.
+In other terms, we cannot exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection in the essential part of the Liouvillian spectrum, which in turn cannot be expressed by only employing localized states.
 This fact shows that it is \emph{impossible} to restrict the spectral representation of $\chi(\omega)$ to only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
@@
 
-Present the table of the other results.
+\begin{table}
+\begin{tabular}{c|cc||cc}
+  Mol. & $\braket{\alpha}_\text{ref}$ & $ \braket{\text{Eq.~\eqref{sminus2}}}$ & \% LS & \% $\Omega_a <$ IP  \\
+  \hline
+  \hline
+  N$_2$ &12.49 & 12.38 & $1.6\cdot 10^{-6}$ & $1.6\cdot 10^{-6}$ \\
+  CO & 15.07 & 14.79 & 8.6 & 8.6 \\
+  H$_2$O & 10.87 & 10.72 & 0.1 & 0.1 \\
+  Benzene & 71.11 & 70.32 & 3.0 & $7.2 \cdot 10^{-5}$\\
+  Aflatoxin & N/A   & 226.27 & 15.87 & 14.84 \\
+  C$_{60}$ & 561.59 & 509.60 & 38.47 & 34.41
+\end{tabular}\caption{Present the table here}
+\end{table}
 
@@
 High-energy excitations belong to a continuum sector (which should not be confused with the continuum eigenstates of the unperturbed GS Hamiltonian)
-and the excitation density of states for $\omega >$ IP provided by this type of basis-set has to be considered as a effective representation of $\sop \chi(\omega)$ in order to fulfill Eq.~\eqref{fsinexc}.
+and the excitation density of states for $\omega >$ IP provided in this way has to be considered as a effective representation of $\sop \chi(\omega)$ in order to fulfill Eq.~\eqref{fsinexc}.
 This fact has been pointed out several times (see e.g.
@@
 
-Our results show that \emph{both} the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this even below the first IP.
+%Our results show that \emph{both} the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this even below the first IP.
 For generic LR quantities, which are functionals of the linear susceptibility,
-the quality of the $\chi(\omega)$ (super)operator will depend
+the quality of the $\chi(\omega)$ (super)operator will then depend
 on the frequency $\omega$ of interest: a given spectral representation may provide high-quality results for static $\omega=0$ regimes, while being

### 2018-11-29 AnalyticStructure_main.tex
corrected paper and added excitation table

@@
 \author{Luigi Genovese}
-\affiliation{Laboratoire de Simulation Atomistique (LSim), INAC, CEA-UGA, 17 Av. des Martyrs,
-38054 Grenoble, France}
+\affiliation{Laboratoire de Simulation Atomistique (LSim), Univ. Grenoble Alpes, CEA, INAC-MEM, 38000 Grenoble, France}
 \date{\today}
@@
 Care has been taken in keeping the field strenghts $F_j$ small enough to
-preseve the validity of the linear response regime.
+preserve the validity of the linear response regime.
 The local character of the fluctuation states at $\omega=0$ is
@@
 It is possible to reformulate this type of analysis by directly looking at LR quantities that are defined independently from the perturbing operators and target observable.
-This can be achieved by studying the \emph{susceptibility functional}, defined implicitly trough the operator equation
+This can be achieved by studying the \emph{susceptibility functional}, defined implicitly through the operator equation
 \be\lb{SusceptibilityDef1}
@@
 This fact shows that it is \emph{impossible} to restrict the spectral representation of $\chi(\omega)$ to only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
+The basis-dependent sector of the excitation will be needed to
+represent the linear susceptibility in the appropriate region of space.
 
@@
 
-We have analized the fullfillment of Eq.~\eqref{sminus2} for molecules of various
+We have analyzed the fullfillment of Eq.~\eqref{sminus2} for molecules of various
 sizes and symmetries.
@@
 \begin{tabular}{c|cc||cc}
-  Mol. & $\braket{\alpha}_\text{ref}$ & $ \braket{\text{Eq.~\eqref{sminus2}}}$ & \% LS & \% $\Omega_a <$ IP  \\
+  Mol. ($N_{at}$) & $\braket{\alpha}_\text{ref}$ & $ \braket{\text{Eq.~\eqref{sminus2}}}$ & \% LS & \% $\Omega_a <$ IP  \\
   \hline
   \hline
-  N$_2$ &12.49 & 12.38 & $1.6\cdot 10^{-6}$ & $1.6\cdot 10^{-6}$ \\
-  CO & 15.07 & 14.79 & 8.6 & 8.6 \\
-  H$_2$O & 10.87 & 10.72 & 0.1 & 0.1 \\
-  Benzene & 71.11 & 70.32 & 3.0 & $7.2 \cdot 10^{-5}$\\
-  Aflatoxin & N/A   & 226.27 & 15.87 & 14.84 \\
-  C$_{60}$ & 561.59 & 509.60 & 38.47 & 34.41
-\end{tabular}\caption{Present the table here}
+  N$_2 (2)$ &12.49 & 12.38 & $1.6\cdot 10^{-6}$ & $1.6\cdot 10^{-6}$ \\
+  CO (2)& 15.07 & 14.79 & 8.6 & 8.6 \\
+  H$_2$O (3) & 10.87 & 10.72 & 0.1 & 0.1 \\
+  Benzene (12)& 71.11 & 70.32 & 3.0 & $7.2 \cdot 10^{-5}$\\
+  Aflatoxin (35)& N/A   & 226.27 & 15.87 & 14.84 \\
+  C$_{60}$ (60)& 561.59 & 509.60 & 38.47 & 34.41
+\end{tabular}\caption{Comparison of the average static polarizabilities for molecules of various sizes (indicated by the number of atoms $N_{at}$) and symmetries, obtained from the reference calculations of Eq.~\eqref{staticalpha} and from the sum over the excitations extracted from the Casida coupling matrix.
+The last two columns show the percentage of the contribution to Eq.~\eqref{sminus2} which
+come from the Localized Sector (LS) of the excitations, by focusing also on the LS before the first IP, where all the excitated states are localized.
+We see that by increasing the molecules' sizes the LS contribution increases in percentage, however being always largely insufficient; the contribution coming from the pseudocontinuum excitations can never be neglected.}
 \end{table}
@@
 Such a scenario can be also found in the other molecules we have considered;
-varying the molecule size and symmetry seems not to modify the qualitative behavior of the excitation landscape. In addition the
+varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape. In addition the
 localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
@@
 High-energy excitations belong to a continuum sector (which should not be confused with the continuum eigenstates of the unperturbed GS Hamiltonian)
-and the excitation density of states for $\omega >$ IP provided in this way has to be considered as a effective representation of $\sop \chi(\omega)$ in order to fulfill Eq.~\eqref{fsinexc}.
+and the excitation density of states for $\omega >$ IP provided in this way has to be considered as an effective representation of $\sop \chi(\omega)$ in order to fulfill Eq.~\eqref{fsinexc}.
 This fact has been pointed out several times (see e.g.

### 2018-11-30 AnalyticStructure_main.tex
implemented minus corrections and clean-up of the tex. Update of the appendix is still missing

@@
 It is indeed relatively easy to have converged indicators for numerical Ground State (GS) quantities: on one side, the variational theorem
-guarantees that the lower the GS energy, the more precise the numerical result; on the other side, GS quantities of molecular system  can be expressed
-only in terms of localized (i.e. bound) states. These considerations make relatively easy to increase the basis set completeness in view of the extraction of reference results.
+guarantees that the lower the GS energy, the more precise the numerical result; on the other side, GS quantities of molecular system  can be expressed only in terms of localized (i.e.
+bound) states.
+These considerations make relatively easy to increase the basis set completeness in view of the extraction of reference results.
 
 We will see in what follows that the situation is not as simple in the context of LR.
-Indeed we will show that the response density -- even for molecular systems -- looses its localized behaviour for high frequencies, independently on the nature of the specific system and perturbation.
+Indeed the response density -- even for molecular systems -- looses its localized behavior for high frequencies, independently on the nature of the specific system and perturbation.
 Furthermore, we will demonstrate that to increase the basis set completeness, delocalized oscillatory degrees of freedom cannot be excluded \textit{a priori}, even in the localized regime.
 
-We will also see that the reliabilty of the convergence criteria that can be established for LR -- where no variational theorem exists -- depends explicitly on the target frequency range and on the features of the numerical basis set.
-
-% This analysis evidences that the description of molecular systems beyond the ground state unavoidably leads to the inclusion of delocalized
-% degrees of freedom above a specific energetic threshold.
-Moreover on the basis of this analysis we can assess something about the reliability of the results provided by computational setups able to explicit include the presence of delocalized degrees of freedom compared
-% to the ones in which these degrees of freedom are excluded by design.
+Lastly, we will show that the reliability of the convergence criteria that can be established for LR -- where no variational theorem exists -- depends explicitly on the target frequency range and on the features of the numerical basis set.
 
@@
 
-From equation \eqref{rhoPrimeFluctuationStateDef2} we see that
-%is the convenient starting point to assess the localization properties of the FS as it is easy to see that,
-for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.
+From equation \eqref{rhoPrimeFluctuationStateDef2} we see that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.
 As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is spatially localized, \textit{i.e.} its evaluation can be restricted on a bounded real-space domain.
@@
 perturbed by a static electric field.
-Care has been taken in keeping the field strenghts $F_j$ small enough to
+Care has been taken in keeping the field strengths $F_j$ small enough to
 preserve the validity of the linear response regime.
@@
 one of the static dipole of the molecule computed at zero external field.
-The results evidence that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to the ones of the unperturbed KS orbitals, which is a direct proof of the bound-state behaviour of the FS.
+The results evidence that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to the ones of the unperturbed KS orbitals, which is a direct proof of the bound-state behavior of the FS.
 
@@
 \ee
-% \begin{multline}\lb{LinearResponseFunctDef2}
-% \braket{\delta\op O}_\Phi(\omega) = \sum_p \left( \bra{f_p^\Phi(-\omega)}\op O\ket{\psi_p}+ \bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}\right) \\
-% =2 \sum_p\bra{\psi_p}\op O\ket{f_p^\Phi(\omega)}  \;.
-% \end{multline}
 here we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
@@
 with arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
-This is of course true even when the above states are only implicitly expressed by the employed LR treatment,
- as e.g. in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
+This is of course true even when the above states are only implicitly expressed by the employed LR treatment, as e.g.
+in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
 In this regime, a computational treatment based on localized basis set is susceptible to provide a precise answer, assuming a reasonable level of completeness.
@@
 underlying basis set has to be able to express delocalized states.
-%The degrees of completeness of the computational basis should therefore be increased by imposing oscillatory degrees of freedom needed to
-%represent the FS at the border of the simulation domain: it is important that the underlying basis set is able to express delocalized states.
 
@@
 \ee
-In this way Eq.~\eqref{LinearResponseFunctDef2} may be also written as:
+These formulae allows us to present an excitation-based description of Eq.~\eqref{LinearResponseFunctDef2} as follows
 \be\lb{deltaoexc}
-  \braket{\delta \op O} =  \sum_{\{a\}} \frac{\trace{\op O \sop B_a \op \Phi(\omega)}}{\omega -\Omega_a}\;,
+  \braket{\delta \op O} =  \sum_{\{a\}} \frac{\trace{\op O \sop B_a \op \Phi(\omega)}}{\omega -\Omega_a}\;.
 \ee
-
-% \be
-%   \trace{\op O \sop B_a \op \Phi(\omega)} = \trace{\op O \op E_a}
-%   \trace{\op{\tilde E}_a \commutator{\dmnot}{\op \Phi(\omega)}} \;. \nn
-% \ee
 
@@
 
-To further address this point we exploit the formal relation between response density and susceptibility functional %established in ~\eqref{SusceptibilityDef1}
-$\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
-Pursuing this procedure provides the excitation-based
-representation of FS as follows:
-% Let us now consider the features of the response density operator of Eq.~\eqref{rhoPrimeFluctuationStateDef1}.
-% The fluctuation state in this case can be written as
-% \be\lb{fsinexc}
-% \ket{f_p^{\mathbf r_j}(\omega)}=
-% \sop \chi(\omega) \op{\mathbf r_j} \ket{\psi_p}
-% = \sum_a \frac{\bra{w_p^a} \op{\mathbf r_j} \ket{\psi_p}}{\omega^2 - \Omega_a^2}
-% \ket{w_p^a}\;,
-% \ee
+To further address this point we exploit the formal relation between response density and susceptibility functional $\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
+Pursuing this procedure provides the excitation-based representation of FS as follows:
 \be\lb{fsinexc}
@@
 where we have employed the notation $\ket{w_p^a}=\ket{\phi_p^a}+\ket{\chi_p^a}$.
-This is the well-known equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility,
-that is always valid in any computational basis set provided the the full spectrum of excited states (including the pseudo-continuum ones) is considered.
-%The above equation shows that for \emph{any} value of $\omega$ both sectors of localized and delocalized states $\ket{w_p^a}$ contribute.
+This is the well-known equivalence of the Sternheimer formalism with the spectral representation of the LR susceptibility, that is always valid 
+in any computational basis set provided the the full spectrum of excited states (including the pseudo-continuum ones) is considered.
 The above equation shows that both the sectors of localized and delocalized states $\ket{w_p^a}$ contribute to the FS for \emph{any} value of $\omega$.
@@
 The equivalence implies that in this regime the contribution of the delocalized excitations in Eq.~\eqref{fsinexc} has to resum into a localized, asymptotically vanishing FS.
-% Such a locality is evident for the imaginary part of the FS, which can be straightforwardly restricted to the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
-For the real part of FS the \emph{entire} spectrum
-% of excitations contribute.
 The localization below threshold is manifest for the imaginary part of the FS, that is explicitly written as the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}). 
 Instead, for the real part of FS, the \emph{entire} excitation spectrum contributes to the construction of the FS,
-which has to be interpreted as a localized wavepacket in the basis of the pseudo-continuum excitations.
-% and the localization
-%\emph{has} to realize due to a non trivial cancellation of the unbound parts of the $\ket{w_p^a}$'s.
+which has to be interpreted as a localized wave-packet in the basis of the pseudo-continuum excitations.
 
@@
 \subsection{Effective representation of $\sop \chi(\omega)$ for localized response densities}
+
 The above arguments have shown that the only quantity which can be expressed in terms of the localized sector of the excitation spectrum is the imaginary part of the susceptibility functional $\sop \chi(\omega)$ in the optical regime (i.e.
@@
 representation of the susceptibility functional. It appears therefore important to identify indicators that enable us to validate the capability
-of $\sop \chi(\omega)$ to express the localised FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
-%It appears therefore important to identify indicators that might assess the capability of
-%$\sop \chi(\omega)$ to express localised FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
+of $\sop \chi(\omega)$ to express the localized FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
 For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
-% \be\lb{sminus2}
-% \alpha_{ij} = \sint \dd a \frac{w^a_{ij}}{\Omega_a^2}\,, \quad w^a_{ij} \equiv \sum_{p\in a} \bra{\psi_p} \op {\mathbf r}_i \ket{w_p^a}\bra{\psi_p} \op {\mathbf r}_j \ket{w_p^a}\;.
-% \ee
 \be\lb{sminus2}
@@
 The last two columns show the percentage of the contribution to Eq.~\eqref{sminus2} which
-come from the Localized Sector (LS) of the excitations, by focusing also on the LS before the first IP, where all the excitated states are localized.
+come from the Localized Sector (LS) of the excitations, by focusing also on the LS before the first IP, where all the excited states are localized.
 We see that by increasing the molecules' sizes the LS contribution increases in percentage, however being always largely insufficient; the contribution coming from the pseudocontinuum excitations can never be neglected.}
+\label{alphaTable}
 \end{table}
 
-Such a scenario can be also found in the other molecules we have considered;
+This scenario can be also found for the other molecules presented in Table \ref{alphaTable};
 varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape. In addition the
@@
 of the response density below IP.
-However, the fulfillement of $S_{-2}$ is not a universal quality indicator of $\chi(\omega)$ as the latter may be still badly represented in the high frequency regime:
+However, the fulfillment of $S_{-2}$ is not a universal quality indicator of $\chi(\omega)$ as the latter may be still badly represented in the high frequency regime:
 it is enough to recall
@@
 
-From a computational perspective, a set of localized basis functions, which \emph{by design} excludes long-range oscillatory behaviour, may be complete
+From a computational perspective, a set of localized basis functions, which \emph{by design} excludes long-range oscillatory behavior, may be complete
 enough to express $\sop \chi(\omega)$ \emph{below} IP, but it will never be able to capture the entire features of the response density operator above
@@
 
-On the contrary, computational treatments that are able to express delocalized states may be such to describe more efficiently the excitations DOS,
-especially because of the capability of the basis to capture oscillatory behavior. Like in localized basis sets, excitations below threshold can be
+On the contrary, computational treatments that are able to express delocalized states may be adeguate to describe more efficiently the excitations DOS,
+especially due to the capability of the basis to capture oscillatory behavior. Like in localized basis sets, excitations below threshold can be
 precisely calculated with the same paradigm of traditional GS calculations.
@@
 
-%Our results show that \emph{both} the sectors of the excitations energies have to be considered in view of the extraction of computationally reliable quantities, and this even below the first IP.
-For generic LR quantities, which are functionals of the linear susceptibility,
-the quality of the $\chi(\omega)$ (super)operator will then depend
+For generic LR quantities, which are functionals of the linear susceptibility, the quality of $\sop \chi(\omega)$ will then depend
 on the frequency $\omega$ of interest: a given spectral representation may provide high-quality results for static $\omega=0$ regimes, while being
 unable to provide convergence for high-energy absorption spectra.
-%On the contrary,
 Absorption spectra below IP are relatively easy to converge, as they are observables which depend only on localized quantities.

### 2018-11-30 Response_referees.tex
added futher modifications

@@
 \begin{itemize}
- \item Much efforts have been spent in trying to clarify better the relation between localization properties and features of the computational basis needed 
- to provide precise results.
-This topic has been discussed in all the text.
-Major modifications under this perspective have been done in the introduction, in section II at pag.
-5 before the analysis of fig.
-2,in section IV and in the conclusions.
+ \item We have further clarified the relation between localization properties and features of the computational basis needed
+ to provide precise results. Major modifications under this perspective have been done in the introduction, in section II at pag. 5 before the analysis of fig. 2,in section IV and in the conclusions.
  \item The introduction has been deeply revised. In particular we have reduced the length of the first two paragraph concerning the differences between accuracy and precision.
@@
 This section also collects computational results for molecules beyond the case of $CO$ and benzene, already discussed in the previous version of the paper.
- \item State something about the inclusion of other molecules...
+ \item We have also included in our analysis the treatment of various molecular systems, of various sizes and symmetries, such as to further illustrate the generality of our assumptions.
+A table has been added for comparing the excitation landscape of the molecules, in particular related to the ability of the numerical excitations to
+ express the static polarizability tensor.
 \end{itemize}
@@
   The value of convergence is system/observable and perturbation dependent.
-It can be found through an explicit convergence analysis by introducing an acceptance tolerance, however this procedure is out of the scope of our analysis and has not been performed.
+  % It can be found through an explicit convergence analysis by introducing an acceptance tolerance, however this procedure is out of the scope of our analysis and has not been performed.
 
@@
 Within our analysis we show that a box linear size of about 18 Angostroem is sufficient to produce converged results for excitation spectrum below IP (around 6.5 eV in the present case).
-On the contrary, results of \cite{baroni2008} evidence that to achieve convergence up to 30 eV a box of linear dimension of more than 31 Angstroem is needed, so going from the localized to the delocalized sector of excitation spectrum requires a relevant increase in the simulation domain.
+On the contrary, results of \cite{baroni2008} evidence that to achieve convergence up to 30 eV a box of linear dimension of more than 30 Angstroem is needed, so going from the localized to the delocalized sector of excitation spectrum requires a relevant increase in the simulation domain.
 
@@
 We have found that there are no relevant difference in the convergence rate of localized vs delocalized quantities (for instance excitations) in function of the grid spacing.
-This is due to the fact that localized and delocalized states differ in their asymptotic properties whereas the grid spacing convergence is influenced by the fast short-range oscillation of the functions.
-
- Add a comment in the text somewhere?
+This is due to the fact that localized and delocalized states differ in their asymptotic properties whereas the grid spacing convergence is influenced by the short-range oscillation of the functions.
 
@@
 
- In section IIIA we have provided formal arguments that evidence that the excitation spectrum splits into two sectors with distinct features. The first one
- is composed by a finite set of localized excitations with discrete eigenvalues, whereas the second one contains a continuum spectrum of delocalized objects.
- For excitation energies lower than the ionization potential (IP) of the molecule all the excitations belong to the first sector.
+ % In section IIIA we have provided formal arguments that evidence that the excitation spectrum splits into two sectors with distinct features. The first one
+ % is composed by a finite set of localized excitations with discrete eigenvalues, whereas the second one contains a continuum spectrum of delocalized objects.
+ % For excitation energies lower than the ionization potential (IP) of the molecule all the excitations belong to the first sector.
 In the intermediate energy range which goes from IP to the absolute value of the energy of the deepest occupied orbital the two sectors compenetrate so that there are localized excitation embedded in a continuum of delocalized ones, and finally only elements of the second sector exist for higher values of the energy.
-
- These formal results have been supported by numerical calculations in which the excitation spectrum of several molecules has been explicitly computed.
+ %
+ % These formal results have been supported by numerical calculations in which the excitation spectrum of several molecules has been explicitly computed.
  The attribution of each excitation of the appropriate sector passes through the evaluation of the norm of the states $\phi_p^a$ and $\chi_p^a$ that build

### 2018-11-30 AnalyticStructure_main.tex
added futher modifications

--- 2018-11-29 AnalyticStructure_main.tex
@@
 The molecule is oriented along the $z$ axis and the $z$-dimension of the box is equal to 11.5, 15.1 and 16.6 \AA.
+Bond length is 1.235\AA, stretched wrt the equilibrium LDA position such as to increase the value of the polarizability.
 280 unoccupied states have been computed in each setup, which span an energy range of the empty KS orbitals of 30.7, 19.3 and 15.4 eV respectively.
@@
 
+\subsection{Excitation Landscapes}
+The attribution of each excitation of the appropriate sector passes through the evaluation of the norm of the states $\phi_p^a$ and $\chi_p^a$, in the form of Eq.~\eqref{phiandchi}.
+Only states with norm greater than a given tolerance value(taken as the 1\% of the total norm) are considered and the associated
+excitation is attributed to the first sector if the condition $\Omega_a < |\epsilon_p|$ with $\epsilon_a = \mathrm{max}\left(\epsilon_p\right)_{p\in a}$.
+This computational procedure provides results in optimum agreement with the formal arguments reported above. Indeed the excitation landscape of
+(for instace the panel a of Fig.~\eqref{c6h6_excLand} for the case of Benzene) evidences the presence of discrete excitations (the black bullets) embedded in a pseudo-continuum
+represented by the blue filled square.
+The comparison between the excitation DOS computed in different computational domain shows that this way of labeling the excitation is in line with the locality of the corresponding states since the corresponding energies easily converge with respect to the increase of the simulation domain.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-11-30 Response_referees.tex
response to referees drafted, only the git repo has to be created

@@
 
-List of major changes apported to the paper:
+List of major changes:
 \begin{itemize}
@@
  \item Added a dedicated subsection (actually the IIA at page 4)  to discuss the localization properties of the FS states for static perturbations.
- \item Added a panel in figure 2 that contain the plot of the real part of $\alpha(\omega)$ in calculated in different computational domain. This new plot aims to evidence that the localization
+ \item Added a panel in figure 2 that contains the plot of the real part of $\alpha(\omega)$ in calculated in different computational domains. This new plot aims to evidence that the localization
  properties of th FS affect, on equal footing, both the real and the imaginary part of the linear response functional.
@@
 delocalized sector in expressing the susceptibility functional.
-This section also collects computational results for molecules beyond the case of $CO$ and benzene, already discussed in the previous version of the paper.
+This section also collects computational results for molecules beyond the case of $CO$ and benzene.
  \item We have also included in our analysis the treatment of various molecular systems, of various sizes and symmetries, such as to further illustrate the generality of our assumptions.
@@
 Since they behave as continuum states they suffer of the same continuum collapse behavior described in section IA for the unbound solution of the Schr\"odinger equation.
-What is expected to converge is the spectral function, or declined in the present case the real and imaginary part of the dynamical polarizability.
+What is expected to converge is the response functional, in the particular case presented here the real and imaginary part of the dynamical polarizability.
   The value of convergence is system/observable and perturbation dependent.
@@
   Nonetheless, to have an idea of the dimension of the box needed to achieve convergence we can refer to the case of the Benzene molecule and make usage
-  of the result found in our analysis, compared to the one reporte in fig.
+  of the result found in our analysis, compared to the one reported in fig.
 2 of \cite{baroni2008}.
@@
  % These formal results have been supported by numerical calculations in which the excitation spectrum of several molecules has been explicitly computed.
- The attribution of each excitation of the appropriate sector passes through the evaluation of the norm of the states $\phi_p^a$ and $\chi_p^a$ that build
- the dyadic representation of the excitation (see eq. 17). Only states with norm greater than a given tolerance value are considered and the associated
- excitation is attributed to the first sector if the condition $\Omega_a < |\epsilon_p|$ with $\epsilon_a = \mathrm{max}\left(\epsilon_p\right)_{p\in a}$.
- This computational procedure provides results in optimum agreement with the formal arguments reported above. Indeed the excitation landscape of
- (for instace the panel a o fig. 5 for the case of Benzene) evidences the presence of discrete excitations (the black bullets) embedded in a pseudo-continuum
- represented by the blue filled square.
-Moreover the comparison between the excitation DOS computed in different computational domain shows that this way of labeling the excitation is correct since the elements attributed to the localized sector have energies that easily converge with respect to the increase of the simulation box, as expected.
+ We have added in the Appendix the explaination
+ of the procedure we employed for the determination of the excitation landscape.
+  In the previous version of the paper this type of analysis was limited to the case of CO and Benzene molecules.
 
- In the previous version of the paper this type of analysis was limited to the case of $CO$ and Benzene molecules.
-However the same structure of the excitation spectrum is quite general and turns out not to be affected by the size or symmetry of the molecule.
-To check this statement we have repeated
- the same computational analysis for several other molecules of different shape and dimension like the Fullerene and the Aflatoxin. Results for this studies
- are presented as supplementary materials. Looking at the excitation landscape for these cases (extracted with the same procedure and tolerance parameters?) it...
- to be completed after the inclusion of the table.....
+  However the same structure of the excitation spectrum is quite general and turns out not to be affected by the size or symmetry of the molecule. To check this statement we have repeated
+ the same computational analysis for several other molecules of different shape and dimension like the Fullerene and the Aflatoxin, a low-symmetry molecule of 35 atoms which is not as little and exhibit generic features.
+Results for this studies
+ are presented as supplementary materials. See Ref.XXX
+
+ Looking at the excitation landscape for these cases, extracted with the same procedure and tolerance parameters of the cases presented in the paper we see that our consideration are relatively independent from the molecule symmetry: in particular, the number of excitations which
+ belong to the localized sector, even above the first IP
+ seems to _increase_ with the molecule's size.
+ This is due to the increasing of the KS density of states below the continuum threshold which ensures the realization of more localized excitations.
+
+However, see answer below, such a behaviour is not particularly relevant as we have demonstratated that the
+localized sector alone is --- in most of the cases of interest --- not sufficient to represent the properties of the linear susceptibility.
 
@@
 
- During the review process we have deeply revised the final part of the paper (in particular the section IVB in the actual version of the manuscript) in order to clarify which is the relevance the two excitation sectors for obtaining an effective representation of the susceptibility functional.
+In the previous version of the manuscript the answer to this question was adressed in the last section before the conclusions.
 
- For a sake of concreteness this analysis has been declined for the relevant case of the computation of the dynamical polarizability. It emerges that the localized
+ During the review process we have deeply revised the final part of the paper (in particular the section IVB in the actual version of the manuscript) in order to further  clarify which is the relevance the two excitation sectors for obtaining an effective representation of the susceptibility functional.
+ For a sake of concreteness this analysis is declined for the relevant case of the computation of the dynamical polarizability.
+
+ It emerges that the localized
  sector of excitation is sufficient to express the imaginary part of $\alpha(\omega)$ \emph{only} for values of $\omega$ below IP (see eq. 21). The evaluation of
@@
  both the sectors of excitation spectrum.
-So, to answer to the question raised by the referee we can state that localized excitations above IP can be isolated and computed using the procedure described in the previous point of this report, but their knowledge alone is not useful to extract any physical quantities.
- We can state that the multi-threshold structure of the excitation spectrum is surely interesting but is not very relevant for computational purposes.
+So, to answer to the question raised by the referee we can state that localized excitations above IP can be isolated and computed using the procedure described in the previous point of this report, but their knowledge alone is only useful for the extraction of absorption spectra in the optical regime.
 
  \item \emph{On the exclusion ''by design'' of the delocalized part of the excitation spectrum}
+
+ For this reason, we have further clarified the
+ importance of a computational setup that does not exclude ``by design'' the long-range oscillatory behaviour of the localized excitations, especially for the representation
+ of the fluctuation states above threshold.
+ Nonetheless, in the optical regime the FS are localized quantities, and it is thus possible -in principle - to express them precisely, in localized basis sets.
+However, such a representation is \emph{doomed to fail} for frequencies above IP, due to the incorrect asymptotic behaviour of  states above threshold.
 

### 2018-12-03 AnalyticStructure_main.tex
response to referees drafted, only the git repo has to be created
revision

@@
 increasing the predictivity of present-day theoretical approaches. The example of the static polarizability of molecules
-presents ideal features as an initial playground. Work is ongoing in this direction.
+presents ideal features as an initial playground, as it has already been pointed out recently~\cite{HeadGordon}. Work is ongoing in this direction.
 
@@
 
+All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the supplementary informations, may be found at the URL~\footnote{\texttt{https://github.com/luigigenovese/LR-nb/blob/master/ POLARIZABILITY/nb\_paper/LR\_Analysis.ipynb}, or \texttt{https://gitlab.com/luigigenovese/ localization-of-excitations/ blob/master/LR\_Analysis.ipynb}}
+
 \subsection{$CO$}

### 2019-01-18 AnalyticStructure_main.tex
added the C60 panel in figure 6 and the supplementary file

--- 2018-11-30 AnalyticStructure_main.tex
@@
 These are bound states and, by means of their normalizability, they are associated to \emph{discrete}, well-defined energies.
-The bound states can be of course labelled by quantum numbers that are defined by the properties of the scatterer, namely the
+The bound states can be of course labeled by quantum numbers that are defined by the properties of the scatterer, namely the
 symmetries of the potential $\op V$.
@@
 \begin{figure}[ht]
-\includegraphics[scale=0.6]{Fig4_CO_dos_rev1.eps} %{Fig4_CO_dos.eps}
+\includegraphics[scale=0.6]{Fig4_CO_dos_rev1.eps}
 \caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$.
@@
 {\label{C6H6_exc}
-\includegraphics[scale=0.58]{Fig5b_C6H6_dos_rev1.eps}} %{Fig5b_C6H6_dos.eps}
+\includegraphics[scale=0.58]{Fig5b_C6H6_dos_rev1.eps}}
 \caption{(Color online) Benzene molecule.
@@
 
-We have analyzed the fullfillment of Eq.~\eqref{sminus2} for molecules of various
+We have analyzed the fulfillment of Eq.~\eqref{sminus2} for molecules of various
 sizes and symmetries.
-In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison in the case of the $CO$ molecule.
+In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison for the $CO$ and $C_{60}$ molecules.
 We notice that a considerable number of pseudo-continuum excitations is required
 to find the correct result; the sector of the discrete excitations, even though
-parametrised by localized, observable (in the sense of reproducible) excited states,
+parametrized by localized, observable (in the sense of reproducible) excited states,
 appears to be largely insufficient to express the reference fluctuation state. Its contribution is even negligible w.r.t.
@@
 
+% \begin{figure}
+% \includegraphics[scale=0.6]{Fig6_CO_statPolvsExc.eps}
+% \caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,
+% w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
+% horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the
+% oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
+% \end{figure}
+
 \begin{figure}
-\includegraphics[scale=0.6]{Fig6_CO_statPolvsExc.eps}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,
+\centering
+\subfloat[$CO$]
+{\label{CO_alphavsExc}
+\includegraphics[scale=0.6]{Fig6a_CO_statPolvsExc.eps}} \\
+\centering
+\subfloat[$C_{60}$]
+{\label{C60_alphavsExc}
+\includegraphics[scale=0.2]{Fig6b_C60_statPolvsExc.eps}}
+\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ (panel a) and $C_{60}$ (panel b) molecules,
 w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
@@
 
-On the contrary, computational treatments that are able to express delocalized states may be adeguate to describe more efficiently the excitations DOS,
+On the contrary, computational treatments that are able to express delocalized states may be adequate to describe more efficiently the excitations DOS,
 especially due to the capability of the basis to capture oscillatory behavior. Like in localized basis sets, excitations below threshold can be
@@
 
+All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the supplementary information, may be found at the URL~\footnote{\texttt{https://github.com/luigigenovese/LR-nb/blob/master/ POLARIZABILITY/nb\_paper/LR\_Analysis.ipynb}, or \texttt{https://gitlab.com/luigigenovese/ localization-of-excitations/ blob/master/LR\_Analysis.ipynb}}
+
 \subsection{$CO$}
 The molecule is oriented along the $z$ axis and the $z$-dimension of the box is equal to 11.5, 15.1 and 16.6 \AA.
-Bond length is 1.235\AA, stretched wrt the equilibrium LDA position such as to increase the value of the polarizability.
+Bond length is 1.235\AA, stretched w.r.t. the equilibrium LDA position such as to increase the value of the polarizability.
 280 unoccupied states have been computed in each setup, which span an energy range of the empty KS orbitals of 30.7, 19.3 and 15.4 eV respectively.
-Such energy values should not be confused with the excitations energy ranges reported in Figs.~\ref{co_spectrum} and \ref{CO_exc}.
-Once again, such choices of unoccupied states ensures convergence in of excitations spectrum in the presented range.
+These energy values should not be confused with the excitations energy ranges reported in Figs.~\ref{co_spectrum} and \ref{CO_exc}.
+Once again, such choices of unoccupied states ensures convergence of the excitation spectrum in the presented range.
 

### 2019-01-18 Supplementary_material.tex
added the C60 panel in figure 6 and the supplementary file

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{mathtools,braket}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}

% Parametri di stampa
\setlength{\topmargin}{-2.5cm} \setlength{\oddsidemargin}{0.3cm}
\setlength{\evensidemargin}{0.3cm}
%
\textheight=23.0truecm \textwidth=16.0truecm
%
\headheight=1.0cm \headsep=1.0cm
%
\renewcommand{\baselinestretch}{1.1}
\setlength{\unitlength}{1mm}

\parindent=6pt

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bea}{\begin{eqnarray}}
\newcommand{\eea}{\end{eqnarray}}
\newcommand{\al}{\alpha}
\newcommand{\br}{\bar{\rho}}
\newcommand{\bg}{\bar{g}}
\newcommand{\bpi}{\bar{\pi}}

\newcommand{\op}[1]{\hat {#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Supplementary}

As stated in the main text we have investigated the effects of the size and dimension of a molecule in terms of the multi-threshold
structure of the excitation landscape. 
We may affirm that the number of localized excitations above the first ionization potential of the molecule typically grows with the
number of atoms of the molecule. This is simply due to the fact the bigger molecules behave as wider potential well and so the number of
(localized) empty KS states grows with the size....

\begin{figure}[h]
    \centering
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
        \caption{Aflatoxin} \label{fig:a}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.48\textwidth}
        \centering
        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
        \caption{$C_{60}$} \label{fig:b}
    \end{subfigure}

%     \vspace{1cm}
%     \begin{subfigure}[t]{\textwidth}
%     \centering
%         \includegraphics[width=\linewidth]{example-image-c.pdf} 
%         \caption{Price regulation} \label{fig:timing3}
%     \end{subfigure}
    \caption{Some general caption of all the figures....}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2019-01-21 AnalyticStructure_main.tex
update of supplementary and paper

@@
 \caption{(Color online) Benzene molecule.
-(a): Excitation Landscape: the excitations have been separated in discrete and continuum sector following the criteria of Sec.~\ref{ExcitationLandscape}.
+(a): Excitation Landscape: the excitations have been separated in discrete (black circle) and continuum (blue square) sectors following the criteria of Sec.~\ref{ExcitationLandscape}.
 (b): DOS of excitation energies $\Omega_a$.
@@
 In Fig.~\ref{co_AlphaExc} we show explicitly such a comparison for the $CO$ and $C_{60}$ molecules.
-We notice that a considerable number of pseudo-continuum excitations is required
-to find the correct result; the sector of the discrete excitations, even though
-parametrized by localized, observable (in the sense of reproducible) excited states,
-appears to be largely insufficient to express the reference fluctuation state. Its contribution is even negligible w.r.t.
+We notice that, in both the cases, a considerable number of pseudo-continuum excitations is required
+to find the correct result; the sector of the discrete excitations
+%, even though parametrized by localized, observable (in the sense of reproducible) excited states,
+appears to be largely insufficient to express the reference fluctuation state.
+In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t.
 the one coming from the continuum sector.
@@
 
-This scenario can be also found for the other molecules presented in Table \ref{alphaTable};
-varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape. In addition the
+%This scenario can be also found for the other molecules presented in Table \ref{alphaTable};
+This scenario is confirmed by the results for the other molecules presented in Table \ref{alphaTable};
+varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape (for further details
+about the dependence of the excitation landscape on the size of the molecule see the supplementary material). In addition the
 localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.

### 2019-01-21 Supplementary_material.tex
update of supplementary and paper

@@
 \newcommand{\eea}{\end{eqnarray}}
-\newcommand{\al}{\alpha}
-\newcommand{\br}{\bar{\rho}}
-\newcommand{\bg}{\bar{g}}
-\newcommand{\bpi}{\bar{\pi}}
 
@@
 
-\section*{Supplementary}
+\section*{Supplementary material}
 
-As stated in the main text we have investigated the effects of the size and dimension of a molecule in terms of the multi-threshold
-structure of the excitation landscape. 
-We may affirm that the number of localized excitations above the first ionization potential of the molecule typically grows with the
-number of atoms of the molecule. This is simply due to the fact the bigger molecules behave as wider potential well and so the number of
-(localized) empty KS states grows with the size....
+We report the results of the excitation landscape for the $C_{60}$ and the Aflatoxin molecules.
+This analysis allows us to investigate the multi-threshold structure for systems with larger number of atoms and/or lower degrees of symmetry respect to the ones presented in the main text.
+The plots of Fig.
+\ref{exc-land} evidence that, in both the cases, the sector of localized excitations is very rich and extends well above the first ionization potential of the molecule.
+These results provide a further confirmation of the behavior already observed in the Table I.
+
+The growth of the localized sector with the number of atoms of the molecule seems to be a general feature.
+It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
+In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq.
+(17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$.
+In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
+When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig.
+\ref{exc-land}.
 
@@
         \centering
-        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
-        \caption{Aflatoxin} \label{fig:a}
+        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
+        \caption{$C_{60}$} \label{fig:b}
     \end{subfigure}
@@
         \centering
-        \includegraphics[width=\linewidth]{C60_ExcitationLandscape.eps} 
-        \caption{$C_{60}$} \label{fig:b}
+        \includegraphics[width=\linewidth]{Aflatoxin_ExcitationLandscape.eps} 
+        \caption{Aflatoxin} \label{fig:a}
     \end{subfigure}
-
-%     \vspace{1cm}
-%     \begin{subfigure}[t]{\textwidth}
-%     \centering
-%         \includegraphics[width=\linewidth]{example-image-c.pdf} 
-%         \caption{Price regulation} \label{fig:timing3}
-%     \end{subfigure}
-    \caption{Some general caption of all the figures....}
+    \caption{Excitation landscape for the $C_{60}$ (panel a) and the Aflatoxin (panel b) molecules computed accordingly to the procedure described  in the appendix C.
+Black circles represent the localized sector and blue squares describe the pseudo-continuum one.
+}
+\label{exc-land}
 \end{figure}

### 2019-01-22 AnalyticStructure_main.tex
update plot and supplementary

@@
 We notice that, in both the cases, a considerable number of pseudo-continuum excitations is required
-to find the correct result; the sector of the discrete excitations
-%, even though parametrized by localized, observable (in the sense of reproducible) excited states,
-appears to be largely insufficient to express the reference fluctuation state.
-In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t.
-the one coming from the continuum sector.
-
-% \begin{figure}
-% \includegraphics[scale=0.6]{Fig6_CO_statPolvsExc.eps}
-% \caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ molecule, in a box of $11.5$ \AA,
-% w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
-% horizontal red dashed line. The value of the IP energy is indicated by a vertical black dashed line. For each excitation energy, the values of the
-% oscillator strengths $w^a_{zz}$ of Eq.~\eqref{sminus2} are also plotted. }
-% \end{figure}
+to find the correct result; the sector of the discrete excitations appears to be largely insufficient to express the 
+reference fluctuation state. 
+%In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t. the one coming from the continuum sector.
+In particular, in the case of $CO$, the complete excitation set is able to reproduce the reference value of $\alpha_{zz}$, but the contribution of localized sector is negligible w.r.t.
+the one coming from the continuum one.
+Instead, for the $C_{60}$, the localized sector provides a more significant contribution but a higher number of the psuedo-continuum excitations should be included in the sum of \eqref{sminus2} to satisfy the $S_{-2}$ sum-rule.
 
@@
 {\label{C60_alphavsExc}
-\includegraphics[scale=0.2]{Fig6b_C60_statPolvsExc.eps}}
+\includegraphics[scale=0.6]{Fig6b_C60_statPolvsExc.eps}}
 \caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ (panel a) and $C_{60}$ (panel b) molecules,

### 2019-01-23 Supplementary_material.tex
update plot and supplementary
update

@@
 It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
+A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.  
 In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq.
@@
     \caption{Excitation landscape for the $C_{60}$ (panel a) and the Aflatoxin (panel b) molecules computed accordingly to the procedure described  in the appendix C.
-Black circles represent the localized sector and blue squares describe the pseudo-continuum one.
-}
+Black circles represent the localized sector and blue squares describe the pseudo-continuum one.}
 \label{exc-land}
+\end{figure}
+
+\begin{figure}[h]
+    \centering
+    \includegraphics[width=9cm]{DOS_Afla&CO.eps} 
+    \caption{DOS of the (bound) KS states for the Aflatoxin and the $CO$ molecules. }
+\label{dos}
 \end{figure}

### 2019-01-23 Supplementary_material.tex
modification of suypplementary

@@
 
-We report the results of the excitation landscape for the $C_{60}$ and the Aflatoxin molecules.
-This analysis allows us to investigate the multi-threshold structure for systems with larger number of atoms and/or lower degrees of symmetry respect to the ones presented in the main text.
+We have investigated how the multi-threshold structure of the localized excitations might be put in relation with respect to
+the number of atoms and/or the symmetry of the molecule.
+To this end, we have considered two case-studies, the carbon Fullerene, a highly symmetric structure made of 60 atoms, and the B1 Aflatoxin, depicted in Fig.~\ref{aflab1}, which has 35 atoms in a low-symmetric configuration.
+
 The plots of Fig.
-\ref{exc-land} evidence that, in both the cases, the sector of localized excitations is very rich and extends well above the first ionization potential of the molecule.
-These results provide a further confirmation of the behavior already observed in the Table I.
+\ref{exc-land} evidence that, in both cases, the sector of localized excitations is very rich and extends well above the first ionization potential of the molecule.
+These results provide a further confirmation of the behavior already observed in Table I.
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.4\textwidth]{AflaB1.eps}
+    \caption{Equilibrium position of the Aflatoxin B1}
+\label{aflab1}
+\end{figure}
 
-The growth of the localized sector with the number of atoms of the molecule seems to be a general feature.
-It can simply explained by observing that bigger molecules behave as wider potential wells and possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
+It may be noticed that the number of localized excitations, either below or above the first ionization potentials is much higher than
+the one of Fig.~5 of the paper, in the case of the Benzene molecule. This holds also for the low-symmetry aflatoxin molecule.
+
+The growth of the localized sector with the number of atoms of the molecule seems thus to be a general feature.
+A simple interpretation of this fact may be provided by considering perturbatively the coupling term $\op V'=0$ in Eq.~19 of the paper.
+Indeed, larger molecules behave possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
 A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.

### 2019-02-04 Response_referees.tex
Update on Overleaf.

@@
  express the static polarizability tensor.
+ \item we have added a reference to the URL of the supplementary material which contains the data analysis and further results in support of our findings
 \end{itemize}
@@
 
- The values of the grid spacing used for the calculations have been added in appendix C.
+ The values of the grid spacing used for the calculations may be found in the supplementary material.
 
@@
 Results for this studies
- are presented as supplementary materials. See Ref.XXX
+ are presented as supplementary materials. See Ref.22 of the revised manuscript.
 
@@
  belong to the localized sector, even above the first IP
- seems to _increase_ with the molecule's size.
+ seems to increase with the molecule's size.
  This is due to the increasing of the KS density of states below the continuum threshold which ensures the realization of more localized excitations.

### 2019-02-04 AnalyticStructure_main.tex

@@
 There is a discrete sector of excitations -- which may also extend above IP -- that can be parametrized by observable, localized states, which can be computationally expressed with high precision, provided an adequate level of completeness.
-We present indicators that can help to quantify such potential observable property of an excitation, that can be evaluated
+We present indicators that can help to quantify such potential observable properties of an excitation, that can be evaluated
 in any discretization scheme.
@@
 For a theoretical approach that is based on numerical calculations, for which no analytic reference solution exists,
-reducing the computational uncertainty is the only possible way to shed light on the predictivity power of the
+reducing the computational uncertainty is the only possible way to shed light on the predictive power of the
 model. In other terms, the ``accuracy'' of a result with respect to experimental data may be reliably quantified
-only when the computational uncertainty is guaranteed to be significantly lower than the found discrepancy.
+only when the computational uncertainty is guaranteed to be significantly lower than the observed discrepancy.
 For communities employing Density Functional Theory (DFT), the need of such a ``calibration'' of computer codes has led to the DeltaCodes project~\cite{deltaTest2016}.
@@
 
-In this paper, we focus our attention to Linear-Response treatments of \emph{molecular} systems,
+In this paper, we focus our attention on Linear-Response treatments of \emph{molecular} systems,
 in particular referring to LR-TDDFT calculation.
 We will investigate the impact that \emph{open} (i.e.
-Isolated) Boundary Conditions (BC), that are imposed to the system, will have on the computational evaluation of LR quantities.
-We perform analytic considerations on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
-Such considerations will enable us to distinguish quantities that \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - from others that would \emph{explicitly} depend of the employed computational treatment.
+Isolated) Boundary Conditions (BC), which are imposed to the system, will have on the computational evaluation of LR quantities.
+We perform analytic analysis on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
+Such considerations will enable us to distinguish quantities which \textit{a priori} can be compared among different treatments - and therefore tested for reproducibility - from others which would \emph{explicitly} depend of the employed computational treatment.
 
@@
 of the molecule.
-Our considerations will also reveal useful for the understanding of the \emph{analytic structure} of LR quantities like
+Our considerations will prove to be useful for the understanding of the \emph{analytic structure} of LR quantities like
 the linear susceptibility of the system (i.e. the reducible polarizability).
@@
 Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that will turn out to be very useful
-in the forthcoming considerations about linear-response quantities. In particular we revisit the impact that the Isolated BC have on the solutions
+in the forthcoming discussions about linear-response quantities. In particular we revisit the impact that the Isolated BC have on the solutions
 of the Schr\"odinger Equation.
@@
 
-When describing the Ground State of a molecule, we suppose that the potential operator, even if non-local,
-can be effectively restricted on wavefunctions that can be considered as nonzero only on a
+When describing the ground state of a molecule, we suppose that the potential operator, even if non-local,
+can be effectively restricted to wavefunctions that can be considered as nonzero only on a
 bounded domain. In other terms, a molecule can be associated to a ``scatterer'' that has a \emph{finite}
@@
 perhaps in a larger region.
-For a computational analysis of the problem, this property is fundamental in the choice of the numerical treatment as we know that
+For a computational analysis of the problem, this property is fundamental to the choice of the numerical treatment as we know that
 computational basis sets
-that are tailored to express asymptotically vanishing wavefunctions are better suited for the solution of the problem.
+which are tailored to express asymptotically vanishing wavefunctions are better suited for the solution of the problem.
 
@@
 These are bound states and, by means of their normalizability, they are associated to \emph{discrete}, well-defined energies.
-The bound states can be of course labeled by quantum numbers that are defined by the properties of the scatterer, namely the
+The bound states can be of course labeled by quantum numbers which are defined by the properties of the scatterer, namely the
 symmetries of the potential $\op V$.
-In a computational discretization of the Schr\"odinger equation, such states can be in principle expressed with arbitrary precision,
-provided that the numerical treatment offers the adequate level of completeness.
+In a computational discretization of the Schr\"odinger equation, such states can in principle be expressed with arbitrary precision,
+provided that the numerical treatment offers an adequate level of completeness.
 Being discrete and well-identified, the bound-state energies are a property of the molecule and can be associated to \emph{observable}
-quantities. The values of their energies can be compared among different treatments and it is in principle possible to
-provide reference results on them.
+quantities. Their energies can be compared among different treatments and it is in principle possible to
+provide reference values.
 
@@
 
-A direct numerical evidence of this problem has been discussed in \cite{boffi2016}, where the authors analyze the effects of a finite basis set on the
+Direct numerical evidence of this problem has been discussed in \cite{boffi2016}, where the authors analyze the effects of a finite basis set on the
 occupied and virtual orbitals of a molecular system and establish a clear correspondence between the orbital localization character,
@@
 the Hohenberg-Kohn theorem that states that the Ground-State (GS) energy is a functional of the GS
-charge density $\dmnot$. For molecular systems that are electronically stable (i.e. no anionic or metastable configurations),
-such quantity is localized, in the sense of the above section. Stated otherwise,
+charge density $\dmnot$. For molecular systems which are electronically stable (i.e. no anionic or metastable configurations),
+such a quantity is localized, in the sense defined in the above section. Stated otherwise,
 \emph{there is no need to express efficiently any portion of the continuum spectrum} to have a reliable GS treatment of molecules.
@@
 Let us now inspect the case of LR calculations.
-In this framework one considers the unperturbed Hamiltonian $\hnot$ and assumes that
+In this framework we consider the unperturbed Hamiltonian $\hnot$ and assumes that
 the GS density $\dmnot$ is accessible and expressed in a given computational treatment.
@@
 where $\op V'[\op O] \equiv \int \dd \r \dd \r'\frac{\delta \op V[\dmnot]}{\delta \rho(\r,\r')} O(\r,\r')$ encodes the response of the $\dm$-dependent potential to a modification of the density operator.
-The inspection of the linear order time evolution of the eigenstates of $\hnot$ evidences that the response density acts as a transition
+The inspection of the linear order time evolution of the eigenstates of $\hnot$ shows that the response density acts as a transition
 operator, linking the occupied and empty subspaces of $\hnot$.
-An operator $\op O_\perp$ with this feature satisfy the \emph{transverse} condition
+An operator $\op O_\perp$ with this feature satisfies the \emph{transverse} condition
 \be\lb{RhopTransverseDef1}
@@
 \ee
-where $\op Q_0=\identity-\dmnot$ is the projector in empty subspace of $\hnot$
+where $\op Q_0=\identity-\dmnot$ is the projector to the empty subspace of $\hnot$
 (for more details see Appendix~\ref{LiouvillianAction}).
@@
 From equation \eqref{rhoPrimeFluctuationStateDef2} we see that for each choice of $p$, the value $\omega = |\eps_p|$ represents the threshold level that governs the asymptotic behavior of the associated Helmholtz kernel.
-As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is spatially localized, \textit{i.e.} its evaluation can be restricted on a bounded real-space domain.
-Even when such locality argument holds true, for $\omega > |\eps_p|$,
-the Helmholtz kernel behaves as a spherical wave and  gives raise to a $\ket{f^\Phi_p(\omega)}$ which is \emph{delocalized} in the entire real-space domain.
+As a ulterior \emph{stringent} hypothesis, let us now assume that the source term $\ket{s_p^\Phi(\omega)}$ is spatially localized, \textit{i.e.} its evaluation can be restricted to a bounded real-space domain.
+Even when such a locality argument holds true, for $\omega > |\eps_p|$,
+the Helmholtz kernel behaves as a spherical wave and  gives raise to a $\ket{f^\Phi_p(\omega)}$ which is \emph{delocalized} over the entire real-space domain.
 Such delocalization is an intrinsic consequence of the value of $\omega$, and does not depend on the particular choice of
 $\op \Phi$.
-Only for $\omega < |\eps_p|$ the kernel contains an exponential damping factor and $\ket{f^\Phi_p(\omega)}$ exhibits a bound-state behavior in the long range,
+Only for $\omega < |\eps_p|$ the kernel has an exponential damping factor and $\ket{f^\Phi_p(\omega)}$ exhibits a bound-state behavior in the long range,
 once again provided that the above locality arguments on $\ket{s_p^\Phi(\omega)}$ -- hence on $\op V'$ and $\Phi$ -- are valid.
@@
 Let us consider a static perturbing operator $\op\Phi_s$ that can be restricted to a finite domain.
-Any local operator, like \emph{e.g.} a static electric field $\mathbf F$, with associated scalar potential $\Phi_s[\mathbf F](\r) = -\mathbf F \cdot \r$, would satisfy such property.
+Any local operator, \emph{e.g.} a static electric field $\mathbf F$, with associated scalar potential $\Phi_s[\mathbf F](\r) = -\mathbf F \cdot \r$, would satisfy such a property.
 We consider the perturbed Hamiltonian $\hnot[\dm_{\Phi_s}] + \op\Phi_s[\mathbf F]$, where $\dm_{\Phi_s}$ represents the GS density of the perturbed system, and assume that the
@@
 In this case, the occupied eigenfunction $\ket{\psi_p^{\Phi_s}}$ of the perturbed Hamiltonian can be extracted with traditional GS techniques,
-as from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.
+since from the discussion around Eq.~\eqref{SEHelmholtz1}, they exhibit bound-state behavior.
 \begin{figure}[t]
 \includegraphics[scale=0.68]{Fig1_CO_statPolvsBox.eps}
-\caption{\label{co_alphaStatic}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ (blue continuous line) and of the ground state dipole $d_z$ (red dotted line)
-of $CO$ molecule as a function of the size of the computational domain.
+\caption{\label{co_alphaStatic}(Color online) Convergence of the static polarizability $\alpha_{zz}$ (blue continuous line) and of the ground state dipole $d_z$ (red dotted line)
+of a $CO$ molecule as a function of the size of the computational domain.
 The inset evidences the relative convergence (in percent) of the two quantities w.r.t.
-the corresponding value associated to the largest
+the corresponding value associated with the largest
 box.}
@@
 one of the static dipole of the molecule computed at zero external field.
-The results evidence that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to the ones of the unperturbed KS orbitals, which is a direct proof of the bound-state behavior of the FS.
+The results show that the typical sizes of $\ket{f^\Phi_p(0)}$ are analogous to those of the unperturbed KS orbitals, which is a direct proof of the bound-state behavior of the FS.
 
@@
 The analysis described above has shown that the building blocks of the response density $\{\ket{f_p(\omega)}\}$
-are susceptible to exhibit bound-state long-range behavior \emph{only} when $\omega < |\eps_p|$,
+exhibit bound-state long-range behavior \emph{only} when $\omega < |\eps_p|$,
 while they behave as unbound states for values of $\omega$ above these threshold levels.
@@
 here we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
-Let us suppose that also the observable of interest $\op O$ can be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.
+Let us suppose that the observable of interest $\op O$ also can be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.
 Once again, it would be enough to consider a local operator for this condition to be met.
 
-Two distinct regimes can be identified, on the basis of value of $\omega$.
+Two distinct regimes can be identified, on the basis of the value of $\omega$.
 The first one, which we will refer to as the \emph{below threshold} regime, is realized when
@@
 may thus be evaluated with computational setups that
-are similar to the ones usually employed for GS calculations.
+are similar to those usually employed for GS calculations.
 The convergence in this regime is ``strong'', in the sense that the basis functions employed enable us to express
@@
 The non-vanishing spherical-wave behavior in the long range of $\ket{f_p^\Phi(\omega)}$ is therefore responsible
-of this convergence difficulties, especially for high frequencies.
+for these convergence difficulties, especially for high frequencies.
 The IP threshold has an evident physical interpretation: for energies in a range higher than the ionization potential,
@@
 
-As an example in support of these arguments we compare the {dynamical polarizability $\alpha(\omega)$} of a $CO$ molecule computed in three distinct real-space computational setups, which differs for the dimension of the computational domain.
+As an example in support of these arguments we compare the {dynamical polarizability $\alpha(\omega)$} of a $CO$ molecule computed in three distinct real-space computational setups, which differ in the dimension of the computational domain.
 Results reported in the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
 In all the cases a typical behavior emerges: the curves are almost coincident in the below threshold regime,
-whereas the effects of the computational setup are clearly visible for values of  $\omega$ that exceed the threshold value.
-For these high-frequency regions, convergence might be reached for domains of much larger sizes than what presented here~\cite{baroni2008},
+whereas the effects of the computational setup are clearly visible for values of  $\omega$ which exceed the threshold value.
+For these high-frequency regions, convergence might be reached for domains of much larger sizes than those presented here~\cite{baroni2008},
 which are -- as already noticed -- more than sufficient below threshold.
@@
 \ee
-Excitations defined in that way may be considered as a basis of the operators that satisfy the transverse condition as in
+Excitations defined in this way may be considered as a basis of the operators that satisfy the transverse condition as in
 Eq.~\eqref{RhopTransverseDef1}, and enable us to express the susceptibility as a spectral decomposition
@@
 
-With the same spirit of the previous sections, we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows
+In the same spirit as the previous sections, we present a formal solution of \eqref{ExcitationOperatorsDef3} as follows
 \begin{align}
@@
 \ee
-First, we point out that the Helmholtz kernel associated to the $\ket{\chi^a_p}$ state
+First, we point out that the Helmholtz kernel associated with the $\ket{\chi^a_p}$ state
 contains an exponential damping factor for \emph{all} the positive values of $\Omega_a$.
 The asymptotic long-range behavior of $\ket{\chi^a_p}$ thus depends only on the locality properties of
-$\bra{s_p[\op E_a]}$, which in turn is related to the behavior of the operator $\op V'[\op E_a]$.
+$\bra{s_p[\op E_a]}$, which in turn are related to the behavior of the operator $\op V'[\op E_a]$.
 
-On the other hand, the long-range behavior of $\GH(\Omega_a+\eps_p)$ depends from
+On the other hand, the long-range behavior of $\GH(\Omega_a+\eps_p)$ depends on
 $\Omega_a$, with a threshold of value $\Omega_a=|\eps_p|$.
@@
 $\Omega_a>|\eps_p|$  for at least one of the $p \in a$ defining the excitation,
-such operator \emph{cannot} be parametrized by employing localized states only.
+such an operator \emph{cannot} be parametrized by employing localized states only.
 
@@
 $\op V'[\op E_a]$ can be restricted to localized kets and bras.
-If any of these hypothesis does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
+If any of these hypotheses does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
 Furthermore, excited states undergo the orthonormalization condition
-\eqref{ExcitedStateOrthNormDef1} that acts as a ulterior constraint and has the effect of determining the \emph{quantization}
+\eqref{ExcitedStateOrthNormDef1} that acts as an ulterior constraint and has the effect of determining the \emph{quantization}
 of the energy levels $\Omega_a$ associated to the bound-state-like objects.
 For delocalized states, as in the case of the continuum states of $\hnot$,
-such a condition has to be interpreted in distributional sense and does not lead to quantization of $\Omega_a$.
+such a condition has to be interpreted in a distributional sense and does not lead to quantization of $\Omega_a$.
 Thus we can conclude that all the states $\ket{\chi^a_p}$ and the $\ket{\phi^a_p}$ with $\Omega_a$ below the threshold value constitute
--- if localized -- a genuine \emph{discrete} set, while the ones in the unbound energy range behave as generalized eigenvectors associated to a
+-- if localized -- a genuine \emph{discrete} set, while those in the unbound energy range behave as generalized eigenvectors associated to a
 continuum spectrum.
@@
 \end{tikzpicture}
-\caption{\label{ExcitationLandscape} Excitation landscape. Excitations are split in horizontal line according to the threshold levels $p$. Filled bullets refer to localized
+\caption{\label{ExcitationLandscape} Excitation landscape. Excitations are split in horizontal lines according to the threshold levels $p$. Filled bullets refer to localized
 excitations whereas the thick black lines describe delocalized ones belonging a continuum spectrum.}
@@
 
-The susceptibility functional has therefore a peculiar analytic structure made of multiple threshold energies, one for each of the ionization potentials associated to the occupied states.
+The susceptibility functional has therefore a peculiar analytic structure made of multiple threshold energies, one for each of the ionization potentials associated with the occupied states.
 If an excitation $\op E_a$ has an energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$, it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states.
@@
 
-The analysis of the above section reveals that the excitation spectrum is composed by two distinct sectors.
+The analysis of the above section reveals that the excitation spectrum is composed of two distinct sectors.
 The first one is realized by the (finite) set of localized excitations with discrete eigenvalues.
-Borrowing the terminology introduced in section \ref{SEopenSystem} to the present case, we can affirm that such localized excitations behave as
+Applying the terminology introduced in section \ref{SEopenSystem} to the present case, we can affirm that such localized excitations behave as
 \emph{observable} quantities and the associated energies possess ideal features of reproducibility:
@@
 and are deeply affected by the computational setup used to represent them. In particular, the presence of a finite computational domain implies a fictitious discretization of the excitation levels and
-the associated spectrum exhibits an explicit dependence from the size of the domain.
+the associated spectrum exhibits an explicit dependence on the size of the domain.
 Excitations belonging to this sector thus lose their intrinsic physical meaning and have to be understood simply as objects providing an effective representation of the density of states (DOS) of the Liouvillian superoperator, by means of the spectral operators $\sop B_a$ of Eq.~\eqref{spectralop}.
@@
 \caption{(Color online) Benzene molecule.
-(a): Excitation Landscape: the excitations have been separated in discrete (black circle) and continuum (blue square) sectors following the criteria of Sec.~\ref{ExcitationLandscape}.
+(a): Excitation Landscape: the excitations have been separated into discrete (black circle) and continuum (blue square) sectors following the criteria of Sec.~\ref{ExcitationLandscape}.
 (b): DOS of excitation energies $\Omega_a$.
@@
 In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the DOS of the Liouvillian for the $CO$  and Benzene molecules,
-for two different numerical setups of increasing size of the simulation domain.
+for two different numerical setups of increasing simulation domain size.
 The figures show clearly that all the excitations of energy $\Omega_a$ lying below the
@@
 
-So far we have showed with both formal arguments and numerical calculations that the excitation spectrum splits into two sectors with very distinct features.
+So far we have showed with both formal arguments and numerical calculations which show that the excitation spectrum splits into two sectors with very distinct features.
 It is then reasonable to ask which is their relative importance and, in particular, if there is the possibility to express observable quantities, in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
@@
 
-Hence, contrary to GS, we conclude that \emph{for LR calculation, even when the response density is localized, the contribution coming from the
+Hence, contrary to GS, we conclude that \emph{for LR calculations, even when the response density is localized, the contribution coming from the
 continuum sector of the excitations can never be neglected}.
-In other terms, we cannot exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection in the essential part of the Liouvillian spectrum, which in turn cannot be expressed by only employing localized states.
+In other terms, we cannot exclude that a fluctuation state, even if genuinely localized, will have a nonzero projection into the essential part of the Liouvillian spectrum, which in turn cannot be expressed by only employing localized states.
 This fact shows that it is \emph{impossible} to restrict the spectral representation of $\chi(\omega)$ to only localized, discrete, \emph{code-independent} excitations, even for representing LR results in the $\omega=0$ limit.
@@
 \ee
-Such value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as
+Such a value can be straightforwardly compared with results of Eq.~\eqref{staticalpha}, where the localized FS is obtained from GS techniques as
 described in Sec.~\ref{FluctuationState}.
@@
 \includegraphics[scale=0.6]{Fig6b_C60_statPolvsExc.eps}}
-\caption{\label{co_AlphaExc}(Color online) Convergence of the statical polarizability $\alpha_{zz}$ of the $CO$ (panel a) and $C_{60}$ (panel b) molecules,
+\caption{\label{co_AlphaExc}(Color online) Convergence of the static polarizability $\alpha_{zz}$ of the $CO$ (panel a) and $C_{60}$ (panel b) molecules,
 w.r.t the excitations considered in the integral of Eq.~\eqref{sminus2}. The reference value obtained from Eq.~\eqref{staticalpha} is represented as a
@@
 localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
-Such considerations are independent on the number of atoms of the molecule, as the range in $\omega$ needed to
+Such considerations are independent of the number of atoms of the molecule, as the range in $\omega$ needed to
 achieve satisfactory agreement is largely above the last valence ionization threshold, which is
@@
 For frequencies below the IP threshold, under reasonable assumptions on the perturbing operators, the response density is genuinely localized.
-In this regime, it is possible to achieve convergence of the numerical result by increasing the basis completeness in the same spirit of GS calculations.
+In this regime, it is possible to achieve convergence of the numerical result by increasing the basis completeness in the same spirit as GS calculations.
 More complete basis sets will provide more precise results, regardless of their asymptotic behavior.
@@
 \begin{acknowledgments}
-We thank Thierry Deutsch for useful comments on the manuscript.
+We thank Thierry Deutsch for useful comments on the manuscript and Laura Ratcliff for proofreading.
 \end{acknowledgments}

### 2019-02-04 AnalyticStructure_main.tex
corrected URL for the SI

@@
 \usepackage{xifthen}
+\usepackage{url}
 %\pgfplotsset{compat=1.15}
@@
 
-All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the supplementary information, may be found at the URL~\footnote{\texttt{https://github.com/luigigenovese/LR-nb/blob/master/ POLARIZABILITY/nb\_paper/LR\_Analysis.ipynb}, or \texttt{https://gitlab.com/luigigenovese/ localization-of-excitations/ blob/master/LR\_Analysis.ipynb}}
+All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the ones presented in the Supplementary Information, may be found at the URL~\footnote{\protect\url{https://github.com/luigigenovese/LR-nb/blob/master/POLARIZABILITY/nb_paper/LR_Analysis.ipynb}}
 

### 2019-02-04 Supplementary_material.tex
Update on Overleaf.
corrected URL for the SI

@@
 \usepackage{graphicx}
-\usepackage{amssymb,amsmath}
+\usepackage{amssymb,amsmath,url}
 \usepackage{mathtools,braket}
@@
 A simple interpretation of this fact may be provided by considering perturbatively the coupling term $\op V'=0$ in Eq.~19 of the paper.
-Indeed, larger molecules behave possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
+Indeed, larger molecules possess a high number of localized Kohn-Sham (KS) orbitals that span a wide energy range.
 A numerical evidence in support of this argument is presented in Fig. \ref{dos}, where the DOS of the KS (bound) orbitals of the Aflatoxin and $CO$ molecules are directly compared.
-In a simplified two-levels picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq.
-(17) and the associated energy is parametrized as $\Omega_a=\epsilon_a-\epsilon_p$.
-In this case to the increase of the energy range spanned by the localized orbitals it directly corresponds a richer sector of localized excitations.
-When $\op V'$ is switched on the excitation modes are expressed as a combination of KS orbitals but the presence of a high number of localized orbitals allows for a rich sector of localized excitations, as confirmed by the results of Fig.
-\ref{exc-land}.
+
+In a simplified two-orbitals picture, in which $\op V'=0$, the KS empty orbitals $\psi_a$ coincide with the excitation modes defined in eq.
+(17) and the associated energy is given by $\Omega_a=\epsilon_a-\epsilon_p$.
+The increase of the KS DOS below the continuum threshold is therefore directly responsible of the increase of the number of localized excitations above IP.
+
+ Such a two-orbital picture is of course not valid anymore when the coupling $\op V'$ is switched on.
+Yet, by interpreting perturbatively the action of the coupling term the same arguments hold true; larger molecule seem to have higher rate of  localized excitations as their DOS of KS bound states is higher.
+
+ All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis of all the molecules considered in this study may be found at the URL~\url{https://github.com/luigigenovese/LR-nb/blob/master/POLARIZABILITY/nb_paper/LR_Analysis.ipynb}.
 

### 2019-02-11 AnalyticStructure_main.tex
fig3 converted in eps and ref to supplementary material

--- 2019-02-04 AnalyticStructure_main.tex
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \begin{figure}[!t]
+% \begin{tikzpicture}[scale=0.78]
+% % axes
+% \draw[->] (0,0) -- (8,0);
+% \draw[->] (0,0) -- (0,6);
+% % orizontal lines
+% \draw[dashed,thick,color=gray] (0,5) -- (2,5);
+% \draw[very thick](2,5) -- (8,5);
+% \draw[dashed,thick,color=gray] (0,3) -- (4,3);
+% \draw[very thick] (4,3) -- (8,3);
+% \draw[dashed,thick,color=gray] (0,1) -- (6,1);
+% \draw[very thick] (6,1) -- (8,1);
+% % % vertical lines
+% \draw[dashed,very thin,color=black] (2,0) -- (2,5);
+% \draw[dashed,very thin,color=black] (4,0) -- (4,3);
+% \draw[dashed,very thin,color=black] (6,0) -- (6,1);
+% % % threshold levels labels
+% \node[left] at (0,5) {$p=h$};
+% \node[left] at (0,3) {$p$};
+% \node[left] at (0,1) {$p=1$};
+% \node[below] at (2,0) {$|\eps_h|$};
+% \node[below] at (4,0) {$|\eps_p|$};
+% \node[below] at (6,0) {$|\eps_1|$};
+% \node[below] at (4,-0.5) {excitation energy};
+% % bars at thresholds
+% %\foreach \Point in {(2,5),(4,3),(6,1)}{
+% %   \node at \Point {{\textbar}};%$\times$};
+% %}
+% \draw[very thick] (2,4.9) -- (2,5.1);
+% \draw[very thick] (4,2.9) -- (4,3.1);
+% \draw[very thick] (6,0.9) -- (6,1.1);
+% % dotted vertical lines
+% %\draw[dotted,thick,color=black] (-0.2,3.6) -- (-0.2,4.4);
+% %\draw[dotted,thick,color=black] (-0.2,1.6) -- (-0.2,2.4);
+% % discrete excitations
+% \foreach \Point in {(0.5,5),(1.0,5),(1.8,5),(0.8,3),(1.3,3),(1.8,3),(2.4,3),(2.8,3),(3.4,3),(3.8,3),(0.7,1),(1.5,1),(1.9,1),(2.6,1),(2.9,1),(3.5,1),(4.1,1),(4.7,1),(5.7,1)}{
+%     \node at \Point {\textbullet};
+% }
+% \end{tikzpicture}
+% \caption{\label{ExcitationLandscape} Excitation landscape. Excitations are split in horizontal lines according to the threshold levels $p$. Filled bullets refer to localized
+% excitations whereas the thick black lines describe delocalized ones belonging a continuum spectrum.}
+% \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \begin{figure}[!t]
-\begin{tikzpicture}[scale=0.78]
-% axes
-\draw[->] (0,0) -- (8,0);
-\draw[->] (0,0) -- (0,6);
-% orizontal lines
-\draw[dashed,thick,color=gray] (0,5) -- (2,5);
-\draw[very thick](2,5) -- (8,5);
-\draw[dashed,thick,color=gray] (0,3) -- (4,3);
-\draw[very thick] (4,3) -- (8,3);
-\draw[dashed,thick,color=gray] (0,1) -- (6,1);
-\draw[very thick] (6,1) -- (8,1);
-% % vertical lines
-\draw[dashed,very thin,color=black] (2,0) -- (2,5);
-\draw[dashed,very thin,color=black] (4,0) -- (4,3);
-\draw[dashed,very thin,color=black] (6,0) -- (6,1);
-% % threshold levels labels
-\node[left] at (0,5) {$p=h$};
-\node[left] at (0,3) {$p$};
-\node[left] at (0,1) {$p=1$};
-\node[below] at (2,0) {$|\eps_h|$};
-\node[below] at (4,0) {$|\eps_p|$};
-\node[below] at (6,0) {$|\eps_1|$};
-\node[below] at (4,-0.5) {excitation energy};
-% bars at thresholds
-%\foreach \Point in {(2,5),(4,3),(6,1)}{
-%   \node at \Point {{\textbar}};%$\times$};
-%}
-\draw[very thick] (2,4.9) -- (2,5.1);
-\draw[very thick] (4,2.9) -- (4,3.1);
-\draw[very thick] (6,0.9) -- (6,1.1);
-% dotted vertical lines
-%\draw[dotted,thick,color=black] (-0.2,3.6) -- (-0.2,4.4);
-%\draw[dotted,thick,color=black] (-0.2,1.6) -- (-0.2,2.4);
-% discrete excitations
-\foreach \Point in {(0.5,5),(1.0,5),(1.8,5),(0.8,3),(1.3,3),(1.8,3),(2.4,3),(2.8,3),(3.4,3),(3.8,3),(0.7,1),(1.5,1),(1.9,1),(2.6,1),(2.9,1),(3.5,1),(4.1,1),(4.7,1),(5.7,1)}{
-    \node at \Point {\textbullet};
-}
-\end{tikzpicture}
-\caption{\label{ExcitationLandscape} Excitation landscape. Excitations are split in horizontal lines according to the threshold levels $p$. Filled bullets refer to localized
-excitations whereas the thick black lines describe delocalized ones belonging a continuum spectrum.}
+\includegraphics[scale=0.12]{Fig3_ExcitationLandscape.eps}
+\caption{\label{ExcitationLandscape} Excitation landscape. Excitations are split in horizontal lines according to the threshold
+levels $p$. Filled bullets refer to localized excitations whereas the thick black lines describe delocalized ones belonging a
+continuum spectrum.}
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 If an excitation $\op E_a$ has an energy $\Omega_a < |\eps_a|$ with $\eps_a = \mathrm{max}\left(\eps_p\right)_{p\in a}$, it may belong to a discrete spectrum; otherwise it \emph{has} to belong to a continuum of states.
-The typical structure of the excitation landscape is depicted in figure \ref{ExcitationLandscape}, once again assuming that the perturbed potential $\op V'[\op E]$ gives rise to a bound state when applied to $\ket{\psi_p}$.
+The typical structure of the excitation landscape is depicted in Fig.~\ref{ExcitationLandscape}, once again assuming that the perturbed potential $\op V'[\op E]$ gives rise to a bound state when applied to $\ket{\psi_p}$.
 Below the first ionization energy $|\eps_h|$ only localized excitations are present.
@@
 reference fluctuation state. 
-%In particular, in the case of $CO$, the contribution of localized excitations is even negligible w.r.t. the one coming from the continuum sector.
 In particular, in the case of $CO$, the complete excitation set is able to reproduce the reference value of $\alpha_{zz}$, but the contribution of localized sector is negligible w.r.t.
@@
 
-%This scenario can be also found for the other molecules presented in Table \ref{alphaTable};
-This scenario is confirmed by the results for the other molecules presented in Table \ref{alphaTable};
-varying the molecule size and symmetry does not modify the qualitative behavior of the excitation landscape (for further details
-about the dependence of the excitation landscape on the size of the molecule see the supplementary material). In addition the
-localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$.
-Such considerations are independent of the number of atoms of the molecule, as the range in $\omega$ needed to
-achieve satisfactory agreement is largely above the last valence ionization threshold, which is
-an intensive quantity.
+This scenario is confirmed by the results for the other molecules presented in Table \ref{alphaTable}; varying the molecule size
+and symmetry does not modify the qualitative behavior of the excitation landscape (see Supplementary Material at~\footnote{\texttt{URL insert by the publisher}} for further details about the dependence of the excitation landscape on the size of the molecule).
+In addition the localized sector of the excitations alone is largely insufficient to express $\alpha_{ij}$. Such considerations 
+are independent of the number of atoms of the molecule, as the range in $\omega$ needed to achieve satisfactory agreement is largely above the last valence ionization threshold, which is an intensive quantity.
 

### 2019-02-11 AnalyticStructure_main.tex
Typo removed

@@
 \end{align}
-Given that we employ real functions both for $p$ and $s$ is real we also have $\excite{p}{s}(\r,\r') = \decay{s}{p}(\r',\r)$ and the density operator is symmetric in $\r \leftrightarrow \r'$.
+Given that we employ real functions both for $p$ and $s$ we also have $\excite{p}{s}(\r,\r') = \decay{s}{p}(\r',\r)$ and the density operator is symmetric in $\r \leftrightarrow \r'$.
 These conditions applied together imply that $U[\excite{p}{s};\excite{q}{s'}] = U[\decay{s}{p};\decay{s'}{q}]$, as well as $U[\decay{s}{p};\excite{q}{s'}] = U[\excite{p}{s};\decay{s'}{q}]$,

### 2019-02-19 AnalyticStructure_main.tex
implemented proofs corrections

@@
 only when the computational uncertainty is guaranteed to be significantly lower than the observed discrepancy.
-For communities employing Density Functional Theory (DFT), the need of such a ``calibration'' of computer codes has led to the DeltaCodes project~\cite{deltaTest2016}.
-This project represents a remarkable example of precision-driven initiative where a grassroot community of code-owners struggled to extract
-well-defined computational results in the context of DFT calculations. Ground-State quantum mechanical quantities
-as lattice constants and bulk modulus of elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties on such data, and in some sense, to define a \emph{calibration} procedure for a Solid-State Physics DFT code.
+For communities employing density functional theory (DFT), the need of such a ``calibration'' of computer codes has led to the DELTACODES project~\cite{deltaTest2016}.
+This project represents a remarkable example of precision-driven initiative where a grassroots community of code-owners struggled to extract
+well-defined computational results in the context of DFT calculations. Ground-state quantum mechanical quantities
+as lattice constants and bulk modulus of elementary crystals extracted from different codes were compared with each other, with the objective of reducing the uncertainties on such data, and in some sense, to define a \emph{calibration} procedure for a solid-state Physics DFT code.
 Any other code able to extract the same quantities with the same approximations may be compared with the
@@
 
-In this paper, we focus our attention on Linear-Response treatments of \emph{molecular} systems,
+In this paper, we focus our attention on linear-response (LR) treatments of \emph{molecular} systems,
 in particular referring to LR-TDDFT calculation.
-We will investigate the impact that \emph{open} (i.e.
-Isolated) Boundary Conditions (BC), which are imposed to the system, will have on the computational evaluation of LR quantities.
+We will investigate the impact that \emph{open} (i.e., isolated) boundary conditions (BC), which are imposed to the system, will have on the computational evaluation of LR quantities.
 We perform analytic analysis on the equations beyond LR treatment and discuss the interplay between reproducible LR quantities and the \emph{locality} of the related objects.
@@
 
-It is indeed relatively easy to have converged indicators for numerical Ground State (GS) quantities: on one side, the variational theorem
+It is indeed relatively easy to have converged indicators for numerical ground-state (GS) quantities: on one side, the variational theorem
 guarantees that the lower the GS energy, the more precise the numerical result; on the other side, GS quantities of molecular system  can be expressed only in terms of localized (i.e.
 bound) states.
-These considerations make relatively easy to increase the basis set completeness in view of the extraction of reference results.
+These considerations make it relatively easy to increase the basis set completeness in view of the extraction of reference results.
 
 We will see in what follows that the situation is not as simple in the context of LR.
-Indeed the response density -- even for molecular systems -- looses its localized behavior for high frequencies, independently on the nature of the specific system and perturbation.
+Indeed the response density -- even for molecular systems -- loses its localized behavior for high frequencies, independently on the nature of the specific system and perturbation.
 Furthermore, we will demonstrate that to increase the basis set completeness, delocalized oscillatory degrees of freedom cannot be excluded \textit{a priori}, even in the localized regime.
 
-Lastly, we will show that the reliability of the convergence criteria that can be established for LR -- where no variational theorem exists -- depends explicitly on the target frequency range and on the features of the numerical basis set.
+Lastly, we will show that the reliability of the convergence criteria that can be established for LR, where no variational theorem exists -- depends explicitly on the target frequency range and on the features of the numerical basis set.
 
 The paper is organized as follows.
-Initially we will inspect how the question of reproducibility may be expressed
+Initially, we will inspect how the question of reproducibility may be expressed
 for ground state calculations of molecules.
@@
 the application of a perturbing field.
-Then we will consider the behavior of the ``free oscillations'', i.e. the excited states
+Then, we will consider the behavior of the ``free oscillations'', i.e. the excited states
 of the molecule.
@@
 
-Although we refer, as anticipated, to TDDFT models, such considerations might also be transposed to Many-Body Perturbation Theory
-approaches, in the context of Quasi-Particle equations.
+Although we refer, as anticipated, to TDDFT models, such considerations might also be transposed to many-body perturbation theory
+approaches, in the context of quasiparticle equations.
 
@@
 
-Let us start our discussion by reviewing some well-known concepts of quantum mechanic under a perspective that will turn out to be very useful
-in the forthcoming discussions about linear-response quantities. In particular we revisit the impact that the Isolated BC have on the solutions
-of the Schr\"odinger Equation.
+Let us start our discussion by reviewing some well-known concepts of quantum mechanics under a perspective that will turn out to be very useful
+in the forthcoming discussions about linear-response quantities. In particular we revisit the impact that the isolated BC have on the solutions
+of the Schr\"odinger equation.
 
-Consider a (one-body) wavefunction $\ket{\psi}$ solution of the equation
+Consider a (one-body) wave function $\ket{\psi}$ solution of the equation
 $\op H\ket{\psi}=\eps\ket{\psi}$, where we split the Hamiltonian operator into the sum of
@@
 When describing the ground state of a molecule, we suppose that the potential operator, even if non-local,
-can be effectively restricted to wavefunctions that can be considered as nonzero only on a
+can be effectively restricted to wave functions that can be considered as nonzero only on a
 bounded domain. In other terms, a molecule can be associated to a ``scatterer'' that has a \emph{finite}
@@
 computational basis sets
-which are tailored to express asymptotically vanishing wavefunctions are better suited for the solution of the problem.
+which are tailored to express asymptotically vanishing wave functions are better suited for the solution of the problem.
 
@@
 It is evident that the arguments presented above have a limited interest for the study
-of Ground State quantities of molecules. By definition, all these quantities can be expressed as a
+of ground-state quantities of molecules. By definition, all these quantities can be expressed as a
 functional which \emph{entirely} depends on bound states. As an illustration it is sufficient to recall
-the Hohenberg-Kohn theorem that states that the Ground-State (GS) energy is a functional of the GS
+the Hohenberg-Kohn theorem that states that the ground-state (GS) energy is a functional of the GS
 charge density $\dmnot$. For molecular systems which are electronically stable (i.e. no anionic or metastable configurations),
@@
 Let us now inspect the case of LR calculations.
-In this framework we consider the unperturbed Hamiltonian $\hnot$ and assumes that
+In this framework, we consider the unperturbed Hamiltonian $\hnot$ and assumes that
 the GS density $\dmnot$ is accessible and expressed in a given computational treatment.
 The linear response formalism allows us to evaluate the modification of the expectation value of a generic observable induced by a
-time (or frequency)-dependent perturbing field $\op\Phi(\omega)$ acting on the system.
+time- (or frequency-) dependent perturbing field $\op\Phi(\omega)$ acting on the system.
 This quantity, written in the frequency domain, can be expressed through the evaluation of the \emph{linear response functional}
@@
 $\ket{f_p^\Phi(\omega)} = \dm'_\Phi(\omega) \ket{\psi_p}$, that have values in the unoccupied subspace of $\hnot$.
-However, non-hermiticity of $\dm'_\Phi(\omega)$ implies that the
+However, non-Hermiticity of $\dm'_\Phi(\omega)$ implies that the
 fluctuation states are complex quantities.
@@
 apart from the perturbing field, a further term $\op V'[\dm'_\Phi]$ due to the density-dependence of $\hnot$.
-It is easy to see that the solution of equation \eqref{fluctuationStateEqMotion1} can be recast in a scattering problem:
+It is easy to see that the solution of Eq. \eqref{fluctuationStateEqMotion1} can be recast in a scattering problem:
 \be\lb{rhoPrimeFluctuationStateDef2}
@@
 Even when such a locality argument holds true, for $\omega > |\eps_p|$,
-the Helmholtz kernel behaves as a spherical wave and  gives raise to a $\ket{f^\Phi_p(\omega)}$ which is \emph{delocalized} over the entire real-space domain.
+the Helmholtz kernel behaves as a spherical wave and  gives rise to a $\ket{f^\Phi_p(\omega)}$ which is \emph{delocalized} over the entire real-space domain.
 Such delocalization is an intrinsic consequence of the value of $\omega$, and does not depend on the particular choice of
@@
 of a $CO$ molecule as a function of the size of the computational domain.
-The inset evidences the relative convergence (in percent) of the two quantities w.r.t.
-the corresponding value associated with the largest
+The inset evidences the relative convergence (in percent) of the two quantities with respect to the corresponding value associated with the largest
 box.}
@@
 
-From the linearized Schr\"odinger Equation of the perturbed problem, it is easy to see that the FS at $\omega=0$ can be expressed
+From the linearized Schr\"odinger equation of the perturbed problem, it is easy to see that the FS at $\omega=0$ can be expressed
 in terms of the corresponding bound state of the perturbed Hamiltonian, i.e.
@@
 where $\mathbf d^\text{(GS)}=\braket{\mathbf r}$ is the ground state dipole.
-Fig.~\eqref{co_alphaStatic} illustrates this procedure for a $CO$ molecule
+Figure~\ref{co_alphaStatic} illustrates this procedure for a $CO$ molecule
 perturbed by a static electric field.
@@
 \ee
-here we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
+where we have assumed that $\op O$ is a real symmetric operator and chosen a real set of occupied molecular states.
 Let us suppose that the observable of interest $\op O$ also can be restricted to localized domains in the same way as the potentials $ \op V$ and $\op \Phi$.
@@
 $\omega$ is lower than the ionization potential $|\eps_h|$.
-In this case all the FS are below their threshold level and equation \eqref{LinearResponseFunctDef2}
+In this case all the FS are below their threshold level and Eq. \eqref{LinearResponseFunctDef2}
 is expressed in terms of genuinely localized
@@
 with arbitrary precision \emph{both} the states $\ket{\op O \psi_p}$ and $\ket{f_p^\Phi(\omega)}$.
-This is of course true even when the above states are only implicitly expressed by the employed LR treatment, as e.g.
+This is, of course, true even when the above states are only implicitly expressed by the employed LR treatment, as e.g.
 in the case of Krylov spaces generated from the states $\ket{\op\Phi(\omega) \psi_p}$ \cite{baroni2006,baroni2008,linlinKPM}.
@@
 As by hypothesis $\ket{\op O \psi_p}$ is bound-state like, \emph{only} the scalar products of Eq.~\eqref{LinearResponseFunctDef2}
-can be evaluated in a localized domain. In this case a computational description of fluctuation states is only meaningful in ``weak''
+can be evaluated in a localized domain. In this case a computational description of fluctuation states is only meaningful in the ``weak''
 sense, where the bound state character of $\bra{\psi_p\op O}$ behaves as a regulator. This is naturally achieved in the above mentioned
 Krylov space treatments, which explicitly deal with the expression of the scalar products. However, in this regime, imposing \emph{by design}
-a localized behaviour of the FS might reveal very dangerous in view of convergence of the results since the computational basis set has
+a localized behavior of the FS might reveal very dangerous in view of convergence of the results since the computational basis set has
 to be able to express a delocalized FS in the support domain of $\bra{\psi_p\op O}$ .
@@
 As an example in support of these arguments we compare the {dynamical polarizability $\alpha(\omega)$} of a $CO$ molecule computed in three distinct real-space computational setups, which differ in the dimension of the computational domain.
-Results reported in the two panels of figure \ref{co_spectrum} show the real and imaginary part of $\alpha(\omega)$, respectively.
-In all the cases a typical behavior emerges: the curves are almost coincident in the below threshold regime,
+Results reported in the two panels of Fig.
+\ref{co_spectrum} show the real and imaginary parts of $\alpha(\omega)$, respectively.
+In all the cases, a typical behavior emerges: the curves are almost coincident in the below threshold regime,
 whereas the effects of the computational setup are clearly visible for values of  $\omega$ which exceed the threshold value.
 For these high-frequency regions, convergence might be reached for domains of much larger sizes than those presented here~\cite{baroni2008},
-which are -- as already noticed -- more than sufficient below threshold.
+which are, as already noticed, more than sufficient below threshold.
 
@@
 \ee
-These formulae allows us to present an excitation-based description of Eq.~\eqref{LinearResponseFunctDef2} as follows
+These formulas allow us to present an excitation-based description of Eq.~\eqref{LinearResponseFunctDef2} as follows
 \be\lb{deltaoexc}
@@
 
-The properties of the Liouvillian superoperator $\Liouv$ (sketched in appendix \ref{LiouvillianAction}) imply that both the left and right operator-valued
+The properties of the Liouvillian superoperator $\Liouv$ (sketched in Appendix \ref{LiouvillianAction}) imply that both the left and right operator-valued
 eigenstates \eqref{ExcitationOperatorsDef1} satisfy the transverse condition \eqref{RhopTransverseDef1} and can be parametrized as
@@
 By applying \eqref{ExcitationOperatorsDef1} to the above parametrization
-of the excitations, we obtain the following Sternheimer-like equations for the excited states:
+of the excitations, we obtain the following Sternheimer-type equations for the excited states:
 \begin{align}\lb{ExcitationOperatorsDef3}
@@
 \end{align}
-By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation\cite{CasidaBook}
-associated to the excitation energy $\Omega_a$ (see appendix \ref{casida}).
-The spectrum is symmetric w.r.t the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and, given a specific excitation $\{\phi^a_p,\chi^a_p\}$,
+By writing these equations in a basis set of virtual states we obtain the well-known Casida's eigenvalue equation\cite{casida1995}
+associated to the excitation energy $\Omega_a$ (see Appendix \ref{casida}).
+The spectrum is symmetric with respect to the inversion of the eigenvalues $\Omega_a \rightarrow -\Omega_a$ and, given a specific excitation $\{\phi^a_p,\chi^a_p\}$,
 the associated solution with opposite energy is described by the transposed pair $\{\chi^a_p,\phi^a_p\}$.
@@
 \emph{only} when its energy is lower than \emph{all} the ionization potentials of the occupied states participating to the excitation,
-namely if $\Omega_a<|\eps_p|$ $\forall p \in a$. This will only be true if the operator
+namely, if $\Omega_a<|\eps_p|$ $\forall p \in a$. This will only be true if the operator
 $\op V'[\op E_a]$ can be restricted to localized kets and bras.
-If any of these hypotheses does not hold, the excitations of the systems are defined via genuinely delocalized wavefunctions.
+If any of these hypotheses does not hold, the excitations of the systems are defined via genuinely delocalized wave functions.
 Furthermore, excited states undergo the orthonormalization condition
@@
 converges to its reference value.
-A computational setup in which delocalized degrees of freedom are excluded by design can, in principle, describe excitations of this sector in a exact way.
+A computational setup in which delocalized degrees of freedom are excluded by design can, in principle, describe excitations of this sector in an exact way.
 
@@
 \caption{(Color online) DOS of $CO$ excitation energies $\Omega_a$.
-The two curves correspond to two computational domain of different sizes.
+The two curves correspond to two computational domains of different sizes.
 The inset contains the sole contribution of localized excitations.
@@
 \caption{(Color online) Benzene molecule.
-(a): Excitation Landscape: the excitations have been separated into discrete (black circle) and continuum (blue square) sectors following the criteria of Sec.~\ref{ExcitationLandscape}.
+(a): Excitation Landscape: the excitations have been separated into discrete (black circle) and continuum (blue square) sectors following the criteria of Appendix~\ref{ExcitationLandscape}.
 (b): DOS of excitation energies $\Omega_a$.
@@
 
-In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the DOS of the Liouvillian for the $CO$  and Benzene molecules,
+In Fig.~\ref{CO_exc} and \ref{C6H6_exc} we plot the DOS of the Liouvillian for the $CO$ and benzene molecules,
 for two different numerical setups of increasing simulation domain size.
@@
 In addition, for the benzene molecule it is also possible to
-identify excitations of energy above IP that still possess a localized behavior, fulfilling the condition $\Omega_a < |\eps_a|$ (see the inset of
-Fig.~\ref{C6H6_exc}). In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
+identify excitations of energy above IP that still possess a localized behavior, fulfilling the condition $\Omega_a < |\eps_a|$ [see the inset of
+Fig.~\ref{C6H6_exc}]. In Fig.~\ref{c6h6_excLand} we collect the excitations of the benzene molecule following this criterion:
 the agreement with the expected analytic structure presented in Fig.~\ref{ExcitationLandscape} is remarkable.
@@
 
-So far we have showed with both formal arguments and numerical calculations which show that the excitation spectrum splits into two sectors with very distinct features.
+So far, we have showed with both formal arguments and numerical calculations which show that the excitation spectrum splits into two sectors with very distinct features.
 It is then reasonable to ask which is their relative importance and, in particular, if there is the possibility to express observable quantities, in a suitable $\omega$ range, by only employing the sector of genuinely localized excitations.
@@
 
-To further address this point we exploit the formal relation between response density and susceptibility functional $\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
+To further address this point, we exploit the formal relation between response density and susceptibility functional $\dm'(\omega) = \sop \chi(\omega)\op\Phi(\omega)$ and make usage of the representation ~\eqref{rhoPrimeFluctuationStateDef1} of the response density.
 Pursuing this procedure provides the excitation-based representation of FS as follows:
@@
 The above equation shows that both the sectors of localized and delocalized states $\ket{w_p^a}$ contribute to the FS for \emph{any} value of $\omega$.
-However the discussion of Sec.~\ref{FluctuationState} has shown that the FS is a genuinely localized state below the IP threshold.
+However, the discussion of Sec.~\ref{FluctuationState} has shown that the FS is a genuinely localized state below the IP threshold.
 The equivalence implies that in this regime the contribution of the delocalized excitations in Eq.~\eqref{fsinexc} has to resum into a localized, asymptotically vanishing FS.
-The localization below threshold is manifest for the imaginary part of the FS, that is explicitly written as the sum over $\ket{w_p^a}$ below IP (see Eq.~\eqref{imalpha}).
+The localization below threshold is manifest for the imaginary part of the FS, that is explicitly written as the sum over $\ket{w_p^a}$ below IP [see Eq.~\eqref{imalpha}].
 Instead, for the real part of FS, the \emph{entire} excitation spectrum contributes to the construction of the FS,
@@
 representation of the susceptibility functional. It appears therefore important to identify indicators that enable us to validate the capability
-of $\sop \chi(\omega)$ to express the localized FS (and thus the complete response density $\dm'_\Phi(\omega)$) below the IP threshold.
+of $\sop \chi(\omega)$ to express the localized FS [and thus the complete response density $\dm'_\Phi(\omega)$] below the IP threshold.
 For instance, the static polarizability tensor $\alpha_{ij}$ can be calculated as
@@
 described in Sec.~\ref{FluctuationState}.
-This is the well-know $S_{-2}$ sum-rule (see e.g.\cite{Wagner2012}), that expresses the value of the static polarizability
+This is the well-known $S_{-2}$ sum-rule (see, e.g.,\cite{Wagner2012}), that expresses the value of the static polarizability
 in terms of the molecule's oscillator strengths.
 In the context of a numerical evaluation of the excitations, such sum rule can therefore be interpreted as the capability of the pseudo-continuum sector of the excitation to
-express the localized FS -- and consequently the reference value of $\alpha_{ij}$ -- at $\omega=0$.
+express the localized FS -- and consequently the reference value of $\alpha_{ij}$, at $\omega=0$.
 
@@
 The last two columns show the percentage of the contribution to Eq.~\eqref{sminus2} which
-come from the Localized Sector (LS) of the excitations, by focusing also on the LS before the first IP, where all the excited states are localized.
+come from the localized sector (LS) of the excitations, by focusing also on the LS before the first IP, where all the excited states are localized.
 We see that by increasing the molecules' sizes the LS contribution increases in percentage, however being always largely insufficient; the contribution coming from the pseudocontinuum excitations can never be neglected.}
@@
 
-We have performed a critical assessment of the fundamental equations that govern the Linear Response theory of molecular systems.
+We have performed a critical assessment of the fundamental equations that govern the linear response theory of molecular systems.
 We have shown that the response density for values of $\omega$ above the first IP \emph{has} to be expressed in terms of genuinely delocalized states.
@@
 and the excitation density of states for $\omega >$ IP provided in this way has to be considered as an effective representation of $\sop \chi(\omega)$ in order to fulfill Eq.~\eqref{fsinexc}.
-This fact has been pointed out several times (see e.g.
-\cite{giustino2012,giustino2014}) in the literature.
+This fact has been pointed out several times (see, e.g., \cite{giustino2012,giustino2014}) in the literature.
 
@@
 a guarantee of the quality of high energy absorption spectra.
-Moreover, if the basis set employed for the evaluation of the target $\alpha_{ij}$ in  Eq.~\eqref{sminus2} is identical to the one employed for the LR treatment the $S_{-2}$
+Moreover, if the basis set employed for the evaluation of the target $\alpha_{ij}$ in  Eq.~\eqref{sminus2} is identical to the one employed for the LR treatment, the $S_{-2}$
 is trivially satisfied in the basis. It is therefore important to have a set of reference values
@@
 
-We believe that these considerations, based on simple manipulations on the fundamental LR equations, will help in increase the reliability of LR
+We believe that these considerations, based on simple manipulations on the fundamental LR equations, will help to increase the reliability of LR
 calculations in the community, and in building test-sets that would help in the \emph{calibration} of present and future computer codes, thereby
@@
 \section{Transverse operators and right action of the Liouvillian superoperator}\lb{LiouvillianAction}
-Given a unperturbed Hamiltonian and density operator, which satisfy $\commutator{\hnot}{\dmnot}=0$, we may decompose a generic operator in two contributions, $\op O=\op O_\parallel + \op O_\perp$, defined as:
+Given an unperturbed Hamiltonian and density operator, which satisfy $\commutator{\hnot}{\dmnot}=0$, we may decompose a generic operator in two contributions, $\op O=\op O_\parallel + \op O_\perp$, defined as:
 \begin{align}
@@
 With this definition it is explicitly apparent that $\op O\Liouv=\op O_\perp \Liouv$,
-similarly to the left action. The action of the Liouvillian reads
+similarly to the left action. The action of the Liouvillian reads as
 \begin{align}\lb{LiouvillianRightActionDef1}
@@
 \end{align}
-In the last equivalence we have made usage of the transverse property (see equation \eqref{RhopTransverseDef1}) of the coupling superoperator. The above formulae
+In the last equivalence we have made usage of the transverse property [see Eq. \eqref{RhopTransverseDef1}] of the coupling superoperator. The above formulas
 together with Eq.~\eqref{LiouZeroDef1} are the starting point for the solution of the eigenvalues equations \eqref{ExcitationOperatorsDef1}.
@@
 \ee
-Plugging this expansion into equations \eqref{ExcitationOperatorsDef3} and projecting on a arbitrary element of the basis provides a linear systems of equations for the coefficients
+Plugging this expansion into Eqs. \eqref{ExcitationOperatorsDef3} and projecting on a arbitrary element of the basis provides a linear systems of equations for the coefficients
 $X^a_{ps}$ and $Y^a_{ps}$, namely
@@
 These conditions applied together imply that $U[\excite{p}{s};\excite{q}{s'}] = U[\decay{s}{p};\decay{s'}{q}]$, as well as $U[\decay{s}{p};\excite{q}{s'}] = U[\excite{p}{s};\decay{s'}{q}]$,
-and so equations \eqref{ExcitationOperatorsDef3} can be recasted in matrix form
+and so Eqs. \eqref{ExcitationOperatorsDef3} can be recasted in matrix form
 \be\lb{ExcitationMatrixEq1}
@@
 \end{align}
-This is the well-known Casida Equation in the basis of transitions for the excitation of energy $\Omega_a$. The computational reliability of the
+This is the well-known Casida equation in the basis of transitions for the excitation of energy $\Omega_a$. The computational reliability of the
 eigenvalue $\Omega_a$ depends on the capability of the basis set $\ket{s}$ to fulfill of Eq.~\eqref{phiandchi}.
@@
 \section{Computational details} \lb{compdetails}
-The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BigDFT code \cite{BigDFT},
+The illustrative calculations presented in this paper are all KS-DFT calculations at the LDA level of theory. We employed the BIGDFT code \cite{BigDFT},
 that makes usage of Daubechies Wavelets as computational basis set.
-This orthonormal basis presents optimal features in view of reproducibility of the results, and it has proved to represent precisely and explicitly system with Free as well as Periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for Free BC.
+This orthonormal basis presents optimal features in view of reproducibility of the results, and it has proved to represent precisely and explicitly a system with free as well as periodic boundary conditions (BC), without any basis set superposition error nor supercell aliasing, for free BC.
 
-For Ground State results, the important parameters in the context of convergence of the calculations are the spacing of the wavelet grid and the size of the simulation domain: for bound-state like functions, convergence is achieved by reducing the grid spacing and increasing the simulation box size.
-Norm Conserving Pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proved to be able to provide all-electron accuracy for molecular systems.
+For ground-state results, the important parameters in the context of convergence of the calculations are the spacing of the wavelet grid and the size of the simulation domain: for bound-state like functions, convergence is achieved by reducing the grid spacing and increasing the simulation box size.
+Norm-conserving pseudopotentials (PSP) of the HGH \cite{NLCCPSP} type are employed to remove the core electrons. Such PSP have proved to be able to provide all-electron accuracy for molecular systems.
 
-Our LR calculation are performed with the Casida formalism \cite{bhaarathi}, where it is also important to include a sufficient number of unoccupied states in the transition operators.
+Our LR calculation is performed with the Casida formalism \cite{bhaarathi}, where it is also important to include a sufficient number of unoccupied states in the transition operators.
 As pointed out in the text such states behave as plane waves: the features of wavelets enable us to represent localized and delocalized states on equal footing.
@@
 
-All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the ones presented in the Supplementary Information, may be found at the URL~\footnote{\protect\url{https://github.com/luigigenovese/LR-nb/blob/master/POLARIZABILITY/nb_paper/LR_Analysis.ipynb}}
+All the details of the calculations, the \textsl{Jupyter} notebooks of the data analysis, including the ones presented in the Supplementary Material, may be found at the URL~\footnote{\protect\url{https://github.com/luigigenovese/LR-nb/blob/master/POLARIZABILITY/nb_paper/LR_Analysis.ipynb}}
 
@@
 
-The DOS reported in figure \ref{CO_exc} are obtained by adding a smearing parameter of $8\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
+The DOS reported in figure \ref{CO_exc} are obtained by adding a smearing parameter of $8\times 10^{-2}$ eV whereas in the inset the shift is $5\times 10^{-3}$ eV.
 
@@
 
-The DOS reported in figure \ref{C6H6_exc} are obtained by adding a complex shift of $1.3\times 10^{-2}$ eV whereas in the inset shift is $5\times 10^{-3}$ eV.
+The DOS reported in Fig. \ref{C6H6_exc} are obtained by adding a complex shift of $1.3\times 10^{-2}$ eV whereas in the inset the shift is $5\times 10^{-3}$ eV.
 
@@
 This computational procedure provides results in optimum agreement with the formal arguments reported above. Indeed the excitation landscape of
-(for instace the panel a of Fig.~\eqref{c6h6_excLand} for the case of Benzene) evidences the presence of discrete excitations (the black bullets) embedded in a pseudo-continuum
+[for instance, Fig.~\eqref{c6h6_excLand} for the case of benzene] evidences the presence of discrete excitations (the black bullets) embedded in a pseudo-continuum
 represented by the blue filled square.
